### 2018-08-12 WRITEUP/ms.tex
fix conflict and added some text

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
\documentclass[apj]{emulateapj} %iop
\usepackage{amsmath}

\input{preamble}
\slugcomment{To be Submitted}

\makeatletter
\renewcommand\normalsize{\@setfontsize\normalsize\@xpt{12.5}}
% \renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}      % 11.5, 12.5
\makeatother

\citestyle{aa}
\shorttitle{Dynamical Properties of Molecular Gas Complexes in $z$\ssim6 Prototypical Galaxy
}
\shortauthors{Leung et al.}

\begin{document}
\title{
Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization
}

\author{T. K. Daisy Leung\altaffilmark{1, 2}}
\author{Andrea Pallottini \altaffilmark{3, 4}}
\author{Andrea Ferrara \altaffilmark{4, 5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}

\altaffiltext{1}{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli IPMU, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
\email{tleung@astro.cornell.edu}

\begin{abstract}
We present results from the first study investigating the dynamical properties of molecular clouds 
and their evolution in galaxies at Epoch of Reionization using state-of-the-art cosmological 
zoom-in simulation, which includes a chemical network to determine the formation of molecular 
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via 
kinetic and thermal energies. We..
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

\def\figpath{./Fig}

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}    \label{sec:intro}

The growth of galaxies and their subsequent evolution are governed by the baryonic/baryon cycle ---
galaxies accrete gas from the intergalactic medium to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered/supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the intergalactic 
medium and galaxies themselves are more gas-rich in their star-forming molecular 
gas contents compared to present-day galaxies.
 % while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when 
% the gravitational potential is still increasing), but their gas reservoirs 
% are continuously being replenished. 
These massive gas inflows in turn trigger gravitational instability, and thus, lead
to the formation of clouds/structures that are typically more massive and denser than those 
observed in nearby galaxies, with cloud masses of $M_{\rm cloud}$\eq10$^9$\,\Msun 
and sizes on sub-kpc scales (e.g. \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%In cosmological context, minor mergers and external gas accretion can
%significantly impact on disc dynamics and clump formation
%(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
Some theoretical works postulate that it is in fact the
migration of such giant massive clumps that are responsible for contributing to the 
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

At high redshifts, galaxies are expected to have lower metallicity, 
% stronger and harder radiation fields),
more {\sc HII} regions and ionized gas 
(given their much higher star formation rates; SFR), and 
more intense radiation stellar feedbacks.
Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
and thus, their multi-phase ISM differ from nearby galaxies.
Since \highz galaxies are the early stages of evolution of present-day galaxies, 
studying their ISM properties is essential for understanding how \SF proceed under these more extreme
conditions, thereby driving the evolution and assembly history 
of galaxies since the cosmic dark ages.
% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for 
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized, 
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies 
have informed us on their galaxy-wide properties (e.g., 
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and 
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies 
have only been studied observationally in a handful of (strongly-lensed) 
galaxies, using spatially resolved tracers such as 
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more 
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 
that dominates  \SF at the epoch of reionization which is responsible for producing the 
ionizing photons that reionized the universe.

While ALMA has enabled the detections of 
ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in 
normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
we are still far from mapping their molecular ISM.
In particular, their star-forming gas conditions, due to the stupid stingy ALMA TAC.
As such, we have undertaken a study, exploiting 
state-of-the-art cosmological zoom-in hydrodynamic simulation 
\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine 
the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) lyman-break
galaxy (LBG).

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower).
In \Sec{method}, we describe the method used to identify its molecular gas complexes (MC). 
In \Sec{results}, we present scaling relations found based on the properties of 
the identified MC and compare them with observations of molecular 
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
In \Sec{diss}, we discuss the results and implication of our findings,
and conclude in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities 
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, 
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, 
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Simulations} \label{sec:sim}

\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn 
dictates the formation of CO.
}}  
The simulation used in this work is described by \citealt{Pallottini17a} and is briefly summarized here.

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and 
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} as the AMR backend.
\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and 
photoevaporation feedback in the neutral diffuse and molecular gas. 
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving 
down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the 
finest level.
Such a physical scale is close to the size scale of molecular cloud complexes and
giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace 
$\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that 
our simulation includes non-equilibrium formation of molecular 
hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of 
chemistry affected by non-equilibrium versus equilibrium H$_2$ formation). 
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
We adopt stellar tracks from \ncode{starburst99} and 
include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
Radiation pressure (on the dust and gas) is also included.  % radiative feedback --> NT pressure
To couple the feedback to the gas, we 
employ sub-grid modeling for blastwaves to account for the potential lost of energy inside the cell when
supernovae are exploded.

Details of how \flower, the main galaxy in our simulation,
was identified is discussed in detail by \citet{Pallottini17a}.
Briefly, by \z$\sim$6, \flower is a LBG hosted in 
a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and 
accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun,
metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$,
a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun,
and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne\footnote{This includes contributions from its nearby massive satellite galaxies.}.
It is therefore a prototypical galaxy at \z$\sim$6.

\section{Method} \label{sec:method}

To identify the molecular complexes, we use a customized version of the clump finder algorithm 
available in the \ncode{python} package \ncode{yt}, which was initially described in \citet{Smith09a}
but this function has been modified since then.
The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation
into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across 
the tiles. In the customized version used for this study, we modified \ncode{yt} in order for it to actually work.

In the clump-finding process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (especially between $z\eq$6\,$-$\,15, {\bf Pallo, check this pls}).
We note that this is in essence similar to 
identifying structures based on the noise levels of observational data,
as commonly adopted in the literature (e.g., identifying 
``clumps'' based on/after applying $\sigma$-clipping, 
using tools such as e.g., \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
and \ncode{cprops}; \citealt{Willams94a, Rosolowsky06a}).

We investigate the possible variations in the molecular structure properties to test 
the robustness of our results against the choice of density threshold in \Sec{ncut}.
That is, how sensitive are the structure properties, and thus, the conclusion of our study
dependent on the choice of density thresholds.
We note that due to the limited spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
impose an addition condition on the identified structure such that the said structures only survive if they
span at least 10 cells in 3D position-position-position (PPP) space. 
We caution that one caveats of such condition is that 
we can only examine the parameter space of ``cloud'' scaling
relations at ``cloud'' size $R\gtrsim100$\,pc.

% --------------------
\section{Cloud scaling relations} \label{sec:results}
Upon identified the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$), 
the cloud mass ($M_{\rm cl}$), 
the Mach number ($\mathcal{M}$), 
the velocity dispersion ($\sigma_v$), and the 
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We find that the thermal sound speed ($c_s$) 
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
We find comparable velocity dispersion derived by taking the root mean square ($\sigma_v^{\rm rms}$) versus
that derived using thermal and non-thermal pressure ($\sigma_v^{P+P_{\rm nt}}$), indicating that 
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma_v$\eq$\sigma_v^{\rm rms}$).

\begin{figure}[htbp]
 \centering
\includegraphics[width=0.5\textwidth]{\figpath/}  
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

\begin{figure}[htbp]
 \centering
\includegraphics[width=0.5\textwidth]{\figpath/}  
\caption{
MC identified by applying 
volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
\label{fig:MC}}
\end{figure}

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
in a given snapshot, including contributions from its surrounding 7\,kpc.
In \Fig{MC}, we show an example of
the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
Based on 10 elements spanning between [$-0.5, 1.5$] equally spaced in linear space 
We also vary the range of 
$n_{\rm cut}$ adopted but find no appreciated differences in the results.}
overlaid on a H$_2$ surface density map of a single snapshot.
The molecular structures identified could appear as overlapping structures depending on projections, we 
therefore also show them in different three dimensional projections (\Fig{}) --- so that one can more 
easily see that they are collections of disjoint structures.

We identify a population of molecular structures that are largely similar to those observed 
in \z\ssim2 spatially resolved \obs of gas-rich SFGs in
terms of their velocity dispersions, sizes, and gas surface densities \citep[e.g.,][]{Swinbank11a}.
As we increase the density threshold, we effectively select a population of 
denser molecular structures that have similar to.... 
Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely the collapsing structures (\Fig{alphavir}). 
The MCs that remain at high/increasing density thresholds
are also molecular structures at the center of \flower,
as they systematically have higher surface densities 
and enhanced turbulence, which are expected in the nuclear regions of 
galaxies given the deeper potential wells.
These more massive molecular structures are indeed also evident in \obs (see e.g., 
\citealt{Freeman17a}).

\subsection{Variation in Properties depending on ncut, single snapshot}	 \label{sec:ncut}

We find no appreciative differences in the cloud scaling relations (relative to the clouds 
observed in galaxies) by changing the different adopted choice of H$_2$ density cuts. 
We interpret this lack of variation a manifestation of ..., and that, at least on the scales studied here, the cloud properties are what we found ... 
Our results is therefore robust, haha.

%\begin{figure*}[tbph]
% \centering
%\includegraphics[width=\textwidth]{\figpath/.pdf}  
%\caption{\label{fig:}}
%\end{figure*}

\subsubsection{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.

\subsubsection{SFR-Mach Relation}

We calculate the SFR based on the existing young stellar population of age $t_{\rm age}<$\,10\,Myr.
In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
complexes identified. 
We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
massive stars.

\subsection{MC Properties Evolution}
One of the advantage of studying the dynamical properties of molecular structures at 
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
as a function of time. 
Especially at early epochs, where the densest structures are beginning to form; 
gas is constantly being accreted onto the central galaxy from the cosmic web and 
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting interactions with these surrounding 
galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

To examine the difference in dynamical properties in the molecular structures as they 
evolve over the few 100\,Myr simulated in our simulation,
we repeat the analysis for a set of $\sim$14 snapshots, spaced by $\Delta t$\eq50\,Myr. 
These snapshots include snapshots at different phases, from actively accreting phase 
to a starburst phase, and relatively quiescent phase (we see that their SFRs vary from 
$\sim$50\,\Msun\,yr\pmOne 
to $\sim$100\,\Msun\,yr\pmOne and back to $\sim$30\,\Msun\,yr\pmOne).

TODO: 0.1\,Myr (500 snapshots at $z$\eq$9)

\subsection{Clump Mass Function}
Noisy due to resolution effect, since we only have one galaxy here. However, 
we could improve the ``signal-to-noise'' ratio by including clouds identified from different 
snapshots (valid unless in some snapshots, the galaxy experience a violent event).

We find a shallower slope in the CMF compared to those observed in nearby galaxies (
based on a sample of $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds\citealt{Blitz07a}).

While our result, of particular relevance here is the slope of the CMF, is subject 
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is 
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on 
the evolving dynamical properties of the lower-mass molecular structures in 
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how 
the molecular complexes' properties vary under the influence of gas inflow/outflow.

\subsection{Mass Scales set by Toomre and Jeans Instabilities}

In the limit of a thin rotating disk, rotation can help stabilizes self-gravitational contraction for wavelengths greater than the Toomre length:
\begin{equation}
\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
\end{equation} 
where $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
However, if the condition $Q<Q_{\rm crit}$ is satisfied, where the latter is set by 
the thermal pressure, then fragmentation can happen 
(e.g., instability impose by angular momentum from gas accretion from the cosmic web and 
satellite galaxies and stellar feedback).

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussions and Implications}     \label{sec:diss}
Yet.... at the epoch of reionization.... For instance, to resolve the 
\aco line emission in a $L^*$ prototypical galaxy at \z$\sim$6 on xxx\,pc 
require .... on-source time even with ALMA.

Connection to observations

The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller 
spatial and mass structures that are also denser as we increase $n_{\rm cut}$. In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with 
those observed in \z$\sim$2\,$-$\,4 galaxies with spatially resolved \obs.

Looking at correlations between physical parameters such as xx, yy, zz and the CMF 
can provide valuable information for developing models of \SF at EoR and 
galaxy evolution.

\subsection{Virial Parameter}
We quantify how stable a molecular structure is using the virial parameter, which 
describes the balance between pressure support and gravity.

The high $\alpha_{\rm vir}$ suggest that the majority of the MCs identified are not collapsing. 
The largest structures are presumably supported by galactic rotation and turbulence from the feedback of 
multiple episodes of \SF.
Turbulence in the smaller denser clouds are expected to cascade down over a timescale of $\sim$xxx\,Myr, after which the cloud will collapse 
(its substructure likely collapses earlier than this timescale since turbulences would have dissipated).

While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$ 
nature of the majority of the molecular gas in \flower and its SFR. 
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways. 
First, our results are limited by the resolution of the simulation, such that, in each MC, there 
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores), 
as in the classical MC hierarchy. These smaller structures likely no longer supported by large-scale gravitational potential and differential rotation, 
and turbulence has dissipated rapidly on these scales to enable collapse \citep{Clark04a}.
Non-axisymmetric perturbations (e.g., arms) to the gravitational potential 
can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
Note also that \citet{Pettitt18a} report that the virial parameter could be a poor indicator 
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. They 
do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass 
and the star formation efficiency ($M_*/M_{\rm cl}$).

\subsection{Larson's Relation}
The Larson's relation... empirically-motivated.

\subsection{CMF and IMF at EoR}

While first stars and galaxies are cooled predominated via H$_2$ lines. 
As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, metals also play an important role in the cooling of early galaxies.

CMF influences the IMF because .. different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  For instance, massive protostellar clumps are always supersonic, thus their internal structure are complex. They may form multiple stars.

The minimum clump mass M$_{\rm min}$ is limited by numerical resolution of our simulation. We do not have a resolution study (in hand) and so we cannot quantitatively evaluate this at the moment. The minimum clump mass allowed 
by our clump finding algorithm is the mass over 10 cells that exceeds the given threshold density.

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}      \label{sec:conclusion}

We study the dynamical properties of molecular complexes in a \z$\sim$6 lyman-break galaxy, 
at the end of the epoch of reionization, using state-of-the-art cosmological zoom-in simulation 
(\ncode{Serra}). We identify molecular cloud complexes in the main galaxy of the 
simulated 20\,Mpc h\pmOne box (aka \flower; \citealt{Pallottini17a}) using a method analogues 
to the ``kd-tree'' idea. We decompose the molecular structures into non-overlapping tiles 
% (stored in a kd-tree)
by identifying a set of different density contours at different snapshots. 
Using volumetric H$_2$ is essentially the same as identified molecular structures using
different contours in line emission (e.g., CO, CS, NH$_3$) since the line luminosity scales with the molecular gas density.
Our simulations include the effect of feedback from .... .and ....., which are the main source 
of non-thermal pressure ejected into the ISM.
We examine the properties of the complexes' at different evolutionary stages and compare 
them with nearby and \highz observations. In particular,
the scaling relations between velocity dispersion, complex size, gas mass, 
and SFRs.

We find that our results are robust to the various density cuts of choice. 
This stems from the 
fact that ..... Our choice of density cut is analogues to the inherent problem of limited S/N 
in observations.
However, our results are dependent on the numerical resolution of the simulation.

Utilizing high-resolution realistic hydrodynamics simulation with 
detailed physics (e.g., feedback and chemical evolution), we 
..... , which will become possible to confirm and ... by tracing 
the molecular gas emission with future .... such as the Next Generation Very Large Array (ngVLA).
High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy 
statistics, provides a way to examine and postulate the morphology and dynamics of  
the multi-phase ISM structures of the first galaxies and their satellite galaxies.

Determining the multi-phase ISM properties of early galaxies 
is a critical piece to understanding the evolution and 
assembly history of galaxies, since they set the pace 
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation). 
Observations leveraging the combination of spatio-spectral imaging of 
multi-band continuum and spectral line emission are crucial for better understanding 
the role of \highz galaxy populations 
(e.g., LBGs, BzKs, and DSFGs) in 
galaxy evolution and the ISM physics behind their intense star formation in the early universe 
(if only the ALMA TAC will give us to the time to do so)...

%==============================================================================
%                                Back matters
%==============================================================================
% ACKNOWLEDGEMENTS
%-------------------------------------
\acknowledgements

We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
T.K.D.L. acknowledges support by the NSF through award SOSPA4-009
from the NRAO.
A.F. acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
This work was initiated as a project for the Kavli Summer Program in Astrophysics (KSPA) 
held at the Center for 
Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli 
Foundation and the Simons Foundation. 
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, 
Pascale Garaud for supporting the genesis of this work. 
We also thank the New York University CCPP for their hospitality in hosting us, the refugees, after the steam pipe explosion in NYC during the KSPA.
\bibliographystyle{yahapj}
\bibliography{master_cleanup}
\end{document}

%

%

### 2018-08-13 WRITEUP/ms.tex
wrote some more

@@
 
-In the clump-finding process, we employ a set of different density thresholds defined based on the
-molecular hydrogen density of \flower taken at different cosmic times (especially between $z\eq$6\,$-$\,15, {\bf Pallo, check this pls}).
-We note that this is in essence similar to 
-identifying structures based on the noise levels of observational data,
-as commonly adopted in the literature (e.g., identifying 
+In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
+molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6\,$-$\,15, {\bf Pallo, check this pls}).
+We note that this process is in essence similar to 
+identifying molecular structures based on the noise levels of surface density maps 
+observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
+as commonly adopted in observational studies (e.g., identifying 
 ``clumps'' based on/after applying $\sigma$-clipping, 
-using tools such as e.g., \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
-and \ncode{cprops}; \citealt{Willams94a, Rosolowsky06a}).
+using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
+and \ncode{cprops}; \citealt{Williams94a, Rosolowsky06a}).
 
-We investigate the possible variations in the molecular structure properties to test 
-the robustness of our results against the choice of density threshold in \Sec{ncut}.
-That is, how sensitive are the structure properties, and thus, the conclusion of our study
-dependent on the choice of density thresholds.
-We note that due to the limited spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
-impose an addition condition on the identified structure such that the said structures only survive if they
-span at least 10 cells in 3D position-position-position (PPP) space. 
-We caution that one caveats of such condition is that 
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}  
+\caption{
+Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
+\label{fig:h2density}}
+\end{figure}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png} 
+  \\[-5.5em]
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png} 
+\caption{
+MC identified by applying 
+volumetric H$_2$ density cuts of 
+$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
+Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!}
+% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
+\label{fig:MC}}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.88}.png}
+    \\[-5.5em]
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_1.47}.png}
+\caption{
+Continued.}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_2.45}.png}
+  \\[-5.5em]
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_4.08}.png}
+\caption{
+Continued.}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_6.81}.png} 
+  \\[-5.5em] 
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_11.36}.png}
+\caption{
+Continued.}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_18.96}.png} 
+  \\[-5.5em]  
+  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_31.62}.png} 
+\caption{
+Continued.}
+\end{figure*}
+
+In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
+for a given snapshot which includes contributions from its surrounding 7\,kpc.
+In \Fig{MC}, we show an example of
+the molecular structures identified by applying volumetric H$_2$ density cuts of 
+$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
+Based on 10$^n$, where $n$ represents the 10 elements that are 
+uniformly spaced between [$-0.5, 1.5$] in linear space.
+We also vary the range of 
+$n_{\rm cut}$ adopted and find no significant differences 
+affecting the results and conclusions of this work (see \Sec{ncut}).}
+to the same snapshot as that 
+used to plot \Fig{h2density}.
+Since the molecular structures identified could 
+easily appear as overlapping structures depending on the viewing angle, we 
+also plot them in different three-dimensional projections --- so that one can more 
+easily see that they are collections of disjoint structures.
+We repeat this identification process for 14 snapshots, spaced by $\Delta t$\eq50\,Myr. 
+{\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
+Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
+impose an addition constraint such that an identified structure only survives if it
+spans at least 10 cells in 3D position-position-position (PPP) space. 
+We caution that one caveats of such constraint is that 
 we can only examine the parameter space of ``cloud'' scaling
@@
 % --------------------
+\section{Star Formation History and Cloud Evolution} \label{sec:sfh}
+
+One of the advantage of studying the dynamical properties of molecular structures at 
+$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
+as a function of time. 
+Especially at early epochs, where the densest structures are beginning to form; 
+gas is constantly being accreted onto the central galaxy from the cosmic web and 
+satellite galaxies, thereby leading to bursts of \SF.
+Meanwhile, tidal forces resulting from interactions with these surrounding 
+galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
+for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
+structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
+
+We show the \SF history of \flower in \Fig{SFH}, where 
+the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
+The SFR plotted in Figure 2 of \citet{Pallottini17b}
+is a factor of two higher than shown here since they also include contributions from 
+massive satellites galaxies within the surrounding xxx\,kpc.}
+as it evolves from an actively accreting phase to 
+a starburst phase after a major merger and then back to a relatively quiescent phase
+over the few hundred Myr simulated in our simulation.
+The SFR of \flower is calculated based on existing young stellar population, which is 
+defined to have an age of $t_{\rm age}<$\,10\,Myr.
+
+Given the stochasticity in the \SF history of \flower, 
+we show the scaling relations found for two particular snapshots as examples in \Sec{singless},
+since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
+most extreme variations in the cloud dynamics) --- one of which \flower is 
+actively accreting materials from its surrounding (top panel of \Fig{phases}) 
+and another of which \flower is undergoing 
+a starburst phase after a major merger (bottom panel of \Fig{phases}).
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
+\caption{
+Star formation history of \flower.
+\label{fig:SFH}}
+\end{figure*}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
+\\ [-5em]
+\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
+\caption{
+Projected stellar mass distribution of \flower during one of its accretion phases 
+at an early stage of its evolution (top) and during one of its major starburst phases 
+after a major merger (bottom).
+\label{fig:phases}}
+\end{figure}
+
 \section{Cloud scaling relations} \label{sec:results}
@@
 
-\begin{figure}[htbp]
+\subsection{Single snapshots}  \label{sec:singless}
+In each snapshot (see \Fig{MC} for example), 
+we identify a set of MCs with consistently high turbulences and surface densities 
+regardless of the H$_2$ density cuts adopted. 
+These are the MCs at the center of the main disk of \flower.
+Their high velocity dispersions and surface densities are expected since 
+they are located in the nuclear regions of the 
+galaxy, where the potential well is also deeper.
+
+As we increase the density threshold, some of the MC within the main disk break 
+into multiple sub-MCs.
+As such, we effectively identify a population of denser molecular structures. 
+This population of sub-MCs has dynamics largely
+similar to those observed 
+in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
+terms of their velocity dispersions, sizes, and gas surface densities \citep[e.g.,][]{Swinbank11a}.
+
+We also identify MCs in the satellite galaxies of \flower. These MCs 
+tend to have lower virial parameters compared to the (sub-)MCs in the main disk of \flower, 
+with $\alpha_{\rm vir}\simeq$1.
+Given their low $\alpha_{\rm vir}$ parameter,
+these structures are likely collapsing structures (\Fig{alpha16}).
+
+\begin{figure*}[htbp]
 \centering
-\includegraphics[width=0.5\textwidth]{\figpath/}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}  
 \caption{
-Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
-\label{fig:h2density}}
-\end{figure}
+Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
+\label{fig:alpha16}}
+\end{figure*}
 
-\begin{figure}[htbp]
- \centering
-\includegraphics[width=0.5\textwidth]{\figpath/}  
-\caption{
-MC identified by applying 
-volumetric H$_2$ density cuts of 
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
-\label{fig:MC}}
-\end{figure}
-
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
-in a given snapshot, including contributions from its surrounding 7\,kpc.
-In \Fig{MC}, we show an example of
-the molecular structures identified by applying volumetric H$_2$ density cuts of 
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
-Based on 10 elements spanning between [$-0.5, 1.5$] equally spaced in linear space 
-We also vary the range of 
-$n_{\rm cut}$ adopted but find no appreciated differences in the results.}
-overlaid on a H$_2$ surface density map of a single snapshot.
-The molecular structures identified could appear as overlapping structures depending on projections, we 
-therefore also show them in different three dimensional projections (\Fig{}) --- so that one can more 
-easily see that they are collections of disjoint structures.
-
-We identify a population of molecular structures that are largely similar to those observed 
-in \z\ssim2 spatially resolved \obs of gas-rich SFGs in
-terms of their velocity dispersions, sizes, and gas surface densities \citep[e.g.,][]{Swinbank11a}.
-As we increase the density threshold, we effectively select a population of 
-denser molecular structures that have similar to.... 
-Given their low $\alpha_{\rm vir}$ parameter,
-these structures are likely the collapsing structures (\Fig{alphavir}). 
-The MCs that remain at high/increasing density thresholds
-are also molecular structures at the center of \flower,
-as they systematically have higher surface densities 
-and enhanced turbulence, which are expected in the nuclear regions of 
-galaxies given the deeper potential wells.
-These more massive molecular structures are indeed also evident in \obs (see e.g., 
-\citealt{Freeman17a}).
-
-\subsection{Variation in Properties depending on ncut, single snapshot}	 \label{sec:ncut}
-
-We find no appreciative differences in the cloud scaling relations (relative to the clouds 
-observed in galaxies) by changing the different adopted choice of H$_2$ density cuts. 
+\subsection{Variation in MC Properties Depending on Choice of Density Cuts}	 \label{sec:ncut}
+% single Snapshot
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites 
+to test 
+the robustness of our results against the choice of density threshold in \Sec{ncut}.
+That is, how sensitive are the structure properties, and thus, the conclusion of our study
+dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the snapshots and 
+find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 
+MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of 
+cloud scaling relations).
 We interpret this lack of variation a manifestation of ..., and that, at least on the scales studied here, the cloud properties are what we found ... 
@@
 
-\subsubsection{Schmidt-Kennicutt Relation}
+\subsection{Schmidt-Kennicutt Relation}
 As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
 
-\subsubsection{SFR-Mach Relation}
-
-We calculate the SFR based on the existing young stellar population of age $t_{\rm age}<$\,10\,Myr.
+\subsection{SFR-Mach Relation}
 In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
@@
 
-\subsection{MC Properties Evolution}
-One of the advantage of studying the dynamical properties of molecular structures at 
-$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
-as a function of time. 
-Especially at early epochs, where the densest structures are beginning to form; 
-gas is constantly being accreted onto the central galaxy from the cosmic web and 
-satellite galaxies, thereby leading to bursts of \SF.
-Meanwhile, tidal forces resulting interactions with these surrounding 
-galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
-for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
-structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
+\subsection{Clump Mass Function}
 
-To examine the difference in dynamical properties in the molecular structures as they 
-evolve over the few 100\,Myr simulated in our simulation,
-we repeat the analysis for a set of $\sim$14 snapshots, spaced by $\Delta t$\eq50\,Myr. 
-These snapshots include snapshots at different phases, from actively accreting phase 
-to a starburst phase, and relatively quiescent phase (we see that their SFRs vary from 
-$\sim$50\,\Msun\,yr\pmOne 
-to $\sim$100\,\Msun\,yr\pmOne and back to $\sim$30\,\Msun\,yr\pmOne).
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}  
+\caption{
+CMF of MCs in \flower and best-fit power law.
+\label{fig:cmf}}
+\end{figure*}
 
-TODO: 0.1\,Myr (500 snapshots at $z$\eq$9)
-
-\subsection{Clump Mass Function}
 Noisy due to resolution effect, since we only have one galaxy here. However, 
@@
 snapshots (valid unless in some snapshots, the galaxy experience a violent event).
-
-We find a shallower slope in the CMF compared to those observed in nearby galaxies (
-based on a sample of $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds\citealt{Blitz07a}).
+We find a shallower slope in the CMF of \flower (\Fig{cmf}) 
+compared to those observed in nearby galaxies (based on a sample of 
+$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}).
 
@@
 
-\subsection{Mass Scales set by Toomre and Jeans Instabilities}
+\section{Mass Scales set by Toomre and Jeans Instabilities}
 
@@
 simulated 20\,Mpc h\pmOne box (aka \flower; \citealt{Pallottini17a}) using a method analogues 
-to the ``kd-tree'' idea. We decompose the molecular structures into non-overlapping tiles 
+to the kd-tree idea. We decompose the molecular structures into non-overlapping tiles 
 % (stored in a kd-tree)
@@
 T.K.D.L. acknowledges support by the NSF through award SOSPA4-009
-from the NRAO.
+from the NRAO and support from the Simons Foundation.
 A.F. acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
@@
 We also thank the New York University CCPP for their hospitality in hosting us, the refugees, after the steam pipe explosion in NYC during the KSPA.
+
 \bibliographystyle{yahapj}

### 2018-08-13 WRITEUP/ms.tex
add some figures

@@
 \includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
 \caption{
-Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
+Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
+Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
 \label{fig:alpha16}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
+\caption{
+Top: Virial parameter and cloud mass of \flower of a given snapshot (starburst phase).
+Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
+\label{fig:alpha27}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
+\caption{
+Larson's relation of \flower in 
+accreting phase (top) and
+starburst phase(bottom) and 
+those observed in nearby and the \z$\sim$2 star-forming galaxy.
+\label{fig:larsons_single}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
+\caption{
+Top: Virial parameter and cloud mass of MCs in \flower identified across all snapshots.
+Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs.
+\label{fig:alpha16-28}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}  
+\caption{
+Larson's relation of \flower across all snapshots (showing MC properties in different evolutionary 
+phases) and 
+those observed in nearby and the \z$\sim$2 star-forming galaxy.
+\label{fig:larsons16-28}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\caption{
+Same as \Fig{alpha16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
+where only denser substructures of the main disk of \flower are included. 
+\label{fig:alpha16-28-highncut}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}  
+\caption{
+Same as \Fig{larsons16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
+where only denser substructures of the main disk of \flower are included. 
+\label{fig:larsons16-28-highncut}}
 \end{figure*}

### 2018-08-20 WRITEUP/ms.tex
some comments (and structural changes) up to the section method

@@
 \makeatother
+
+\usepackage{xcolor}
+\definecolor{apcolor}{HTML}{b3003b}
+\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
 
@@
 %(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
-Some theoretical works postulate that it is in fact the
+Some theoretical works argues that it is in fact the
 migration of such giant massive clumps that are responsible for contributing to the 
@@
 
-At high redshifts, galaxies are expected to have lower metallicity, 
-% stronger and harder radiation fields),
-more {\sc HII} regions and ionized gas 
-(given their much higher star formation rates; SFR), and 
-more intense radiation stellar feedbacks.
-Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
-and thus, their multi-phase ISM differ from nearby galaxies.
-Since \highz galaxies are the early stages of evolution of present-day galaxies, 
-studying their ISM properties is essential for understanding how \SF proceed under these more extreme
-conditions, thereby driving the evolution and assembly history 
-of galaxies since the cosmic dark ages.
-% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
+At high redshifts, galaxies have higher star formation rates (SFR) and smaller sizes {\bf cite needed?}, thus are expected to have more {\sc HII} regions and ionized gas, and more intense radiation stellar feedbacks.
+Since also the metallicity and dust content should be lower {\bf cite?}, this affects the shielding of UV photons, heating and cooling mechanisms.
+Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
+%
+Since \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies since the cosmic dark ages.
 
@@
 molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+\AP{i think the passage to "why we focus on eor galaxies" should be detailed a bit more}
 However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 
@@
 This paper is structured as follows.
+\AP{TBM}
 In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower).
@@
 % ------------------
-\section{Simulations} \label{sec:sim}
+\section{Method} \label{sec:sim}
 
-\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
+\subsection{\ncode{Serra} Simulation\footnote{\AP{is the footnote really needed?}Serra means greenhouse in Italian which is motivated by the
 fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn 
@@
 adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
-In particular, it uses a modified version of \ncode{ramses} as the AMR backend.
-\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and 
-photoevaporation feedback in the neutral diffuse and molecular gas. 
-Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving 
-down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the 
-finest level.
-Such a physical scale is close to the size scale of molecular cloud complexes and
-giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
+%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas. 
+Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level.
+Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
 % (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
-We include chemical network in the simulation to trace 
-$\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance to our study here is that 
-our simulation includes non-equilibrium formation of molecular 
-hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of 
-chemistry affected by non-equilibrium versus equilibrium H$_2$ formation). 
+We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
+%
+Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).
+
+% radiative feedback --> NT pressure
 Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and 
-include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
-The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
-Radiation pressure (on the dust and gas) is also included.  % radiative feedback --> NT pressure
-To couple the feedback to the gas, we 
-employ sub-grid modeling for blastwaves to account for the potential lost of energy inside the cell when
-supernovae are exploded.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
+To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g.
+to account for the potential lost of energy inside the cell when supernovae explode.
+The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy and radiation pressure (on the dust and gas) is also included \citep[see][for details]{Pallottini17a}.
 
-Details of how \flower, the main galaxy in our simulation,
-was identified is discussed in detail by \citet{Pallottini17a}.
-Briefly, by \z$\sim$6, \flower is a LBG hosted in 
-a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and 
-accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
-At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun,
-metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$,
-a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun,
-and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne\footnote{This includes contributions from its nearby massive satellite galaxies.}.
+Details on the properties of \flower, the main galaxy in our simulation, are discussed in \citet{Pallottini17b}.
+%
+Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
+At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
 It is therefore a prototypical galaxy at \z$\sim$6.
 
-\section{Method} \label{sec:method}
+\subsection{Star Formation History and Cloud Evolution} \label{sec:sfh}
 
-To identify the molecular complexes, we use a customized version of the clump finder algorithm 
-available in the \ncode{python} package \ncode{yt}, which was initially described in \citet{Smith09a}
-but this function has been modified since then.
-The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation
-into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
-It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across 
-the tiles. In the customized version used for this study, we modified \ncode{yt} in order for it to actually work.
+\AP{i moved the section here, as I see it as part of motivation for the workflow; however, at the moment I do not see the stellar mass maps as figure that are needed; if they stay i would label their evolutionary stage in the SFR history plot; additionaly \quotes{cloud evolutiion} is in the sec title but not in the text, I would remove it}
 
-In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
-molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6\,$-$\,15, {\bf Pallo, check this pls}).
-We note that this process is in essence similar to 
-identifying molecular structures based on the noise levels of surface density maps 
-observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
-as commonly adopted in observational studies (e.g., identifying 
-``clumps'' based on/after applying $\sigma$-clipping, 
-using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
-and \ncode{cprops}; \citealt{Williams94a, Rosolowsky06a}).
+One of the advantage of studying the dynamical properties of molecular structures at 
+$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
+as a function of time. 
+Especially at early epochs, where the densest structures are beginning to form; 
+gas is constantly being accreted onto the central galaxy from the cosmic web and 
+satellite galaxies, thereby leading to bursts of \SF.
+Meanwhile, tidal forces resulting from interactions with these surrounding 
+galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
+for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
+structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
+
+We show the \SF history of \flower in \Fig{SFH}, where 
+the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
+The SFR plotted in Figure 2 of \citet{Pallottini17b}
+is a factor of two higher than shown here since they also include contributions from 
+massive satellites galaxies within the surrounding xxx\,kpc.}
+as it evolves from an actively accreting phase to 
+a starburst phase after a major merger and then back to a relatively quiescent phase
+over the few hundred Myr simulated in our simulation.
+The SFR of \flower is calculated based on existing young stellar population, which is 
+defined to have an age of $t_{\rm age}<$\,10\,Myr.
+
+Given the stochasticity in the \SF history of \flower, 
+we show the scaling relations found for two particular snapshots \AP{in the text I would refer to snapshots as to evolutionary stages of the galaxy (and make the link between the two in the method section)} as examples in \Sec{singless},
+since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
+most extreme variations in the cloud dynamics) --- one of which \flower is 
+actively accreting materials from its surrounding (top panel of \Fig{phases}) 
+and another of which \flower is undergoing 
+a starburst phase after a major merger (bottom panel of \Fig{phases}).
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
+\caption{
+	Star formation history of \flower \AP{if possible I would combine it with Fig. \ref{fig:phases} (as in the talk), or remove 
+	Fig. \ref{fig:phases}, as at the moment it does not add much to the discussion.
+	}.
+\label{fig:SFH}}
+\end{figure*}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
+\\ [-5em]
+\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
+\caption{
+Projected stellar mass distribution of \flower during one of its accretion phases 
+at an early stage of its evolution (top) and during one of its major starburst phases 
+after a major merger (bottom).
+\label{fig:phases}}
+\end{figure}
+
+\subsection{Structure identification} \label{sec:method}
+
+To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a} but this function has been modified since then.
+%
+The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
+It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles.
+In the customized version used for this study, \AP{the following is true but I do not think we should write it in this way ...} we modified \ncode{yt} in order for it to actually work.
+
+In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6\,$-$\,15).
+
+\AP{maybe we can refer to the PPP vs PPV method discussion in Mordecai's paper}
+We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying
+``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Rosolowsky06a}).
 
@@
 $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
-Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!}
+	Color shows the projected H$_2$ surface density.
+{\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field.
+in any case, we should compress the information, by having a less figures showing multplie cuts (e.g.
+3 of them by using thinner lines should suffice in conveining the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
 % yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
@@
 
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
-for a given snapshot which includes contributions from its surrounding 7\,kpc.
-In \Fig{MC}, we show an example of
-the molecular structures identified by applying volumetric H$_2$ density cuts of 
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
-Based on 10$^n$, where $n$ represents the 10 elements that are 
-uniformly spaced between [$-0.5, 1.5$] in linear space.
-We also vary the range of 
-$n_{\rm cut}$ adopted and find no significant differences 
-affecting the results and conclusions of this work (see \Sec{ncut}).}
-to the same snapshot as that 
-used to plot \Fig{h2density}.
-Since the molecular structures identified could 
-easily appear as overlapping structures depending on the viewing angle, we 
-also plot them in different three-dimensional projections --- so that one can more 
-easily see that they are collections of disjoint structures.
+In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower for a given snapshot which includes contributions from its surrounding 7\,kpc.
+\AP{I would note that the distribution is almost flat for $n_{H2}>1\,\cc$ and it samples the range where clumps are found with the Minkovsky analysis of Pallottini2017b}
+
+In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of \AP{I would directly use labels in logspace} $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
+We also vary the range of $n_{\rm cut}$ adopted and find no significant differences affecting the results and conclusions of this work (see \Sec{ncut}).} to the same snapshot as that used to plot \Fig{h2density}.
+
+Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections --- so that one can more easily see that they are collections of disjoint structures.
 We repeat this identification process for 14 snapshots, spaced by $\Delta t$\eq50\,Myr.
-{\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
-Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
-impose an addition constraint such that an identified structure only survives if it
-spans at least 10 cells in 3D position-position-position (PPP) space. 
-We caution that one caveats of such constraint is that 
-we can only examine the parameter space of ``cloud'' scaling
-relations at ``cloud'' size $R\gtrsim100$\,pc.
+{\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}\AP{I am not sure anymore that it is needed; if we want to procede this way, we have to find a way to link the clumps in different snapshots to track their evolution}
+
+Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in 3D position-position-position (PPP) space.
+We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.
 
 % --------------------
-\section{Star Formation History and Cloud Evolution} \label{sec:sfh}
-
-One of the advantage of studying the dynamical properties of molecular structures at 
-$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
-as a function of time. 
-Especially at early epochs, where the densest structures are beginning to form; 
-gas is constantly being accreted onto the central galaxy from the cosmic web and 
-satellite galaxies, thereby leading to bursts of \SF.
-Meanwhile, tidal forces resulting from interactions with these surrounding 
-galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
-for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
-structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
-
-We show the \SF history of \flower in \Fig{SFH}, where 
-the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
-The SFR plotted in Figure 2 of \citet{Pallottini17b}
-is a factor of two higher than shown here since they also include contributions from 
-massive satellites galaxies within the surrounding xxx\,kpc.}
-as it evolves from an actively accreting phase to 
-a starburst phase after a major merger and then back to a relatively quiescent phase
-over the few hundred Myr simulated in our simulation.
-The SFR of \flower is calculated based on existing young stellar population, which is 
-defined to have an age of $t_{\rm age}<$\,10\,Myr.
-
-Given the stochasticity in the \SF history of \flower, 
-we show the scaling relations found for two particular snapshots as examples in \Sec{singless},
-since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
-most extreme variations in the cloud dynamics) --- one of which \flower is 
-actively accreting materials from its surrounding (top panel of \Fig{phases}) 
-and another of which \flower is undergoing 
-a starburst phase after a major merger (bottom panel of \Fig{phases}).
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
-\caption{
-Star formation history of \flower.
-\label{fig:SFH}}
-\end{figure*}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
-\\ [-5em]
-\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
-\caption{
-Projected stellar mass distribution of \flower during one of its accretion phases 
-at an early stage of its evolution (top) and during one of its major starburst phases 
-after a major merger (bottom).
-\label{fig:phases}}
-\end{figure}
 

### 2018-08-20 WRITEUP/ms.tex
comments up to conclusions (escluded)

@@
 \section{Cloud scaling relations} \label{sec:results}
+
+\AP{I see 2 main possible approaches to the presentation of the results
+%
+(a) focus on a single snapshot, analyze the cloud scaling relation by varing the cuts and then by varing the snapshot; after that one can discuss the stability (toomre analysis) of the clumps (that should help in discussing the origin) and the CMF (more speculative, because of the resolution issues).
+%
+(b) discuss each scaling relation one at a time; probabily in this case an introductionary subsection is needed to explain that different cuts yields no qualitative differences; toomre and CMF as before.
+%
+Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s). 
+%
+I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g.
+the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
+%
+Of course alternative approaches are possible, but right now these two seem to be the more natural ones.
+}
+
 Upon identified the molecular structures, we extract parameters such as
@@
 to describe/characterize their dynamics.
-We find that the thermal sound speed ($c_s$) 
-of all identified molecular complexes are generally much smaller compared to the their
+%
+\AP{I would move the following when discussing the velocity dispersion; additionally, the large velocity dispersions was also noted in Vallini2018a, we can use some of those results to complement the discussion (e.g.
+shift for the CO sled at higher J then local galaxies).}
+We find that the thermal sound speed ($c_s$) of all identified molecular complexes are generally much smaller compared to the their
 turbulent velocities.
-We find comparable velocity dispersion derived by taking the root mean square ($\sigma_v^{\rm rms}$) versus
-that derived using thermal and non-thermal pressure ($\sigma_v^{P+P_{\rm nt}}$), indicating that 
-rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
-In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion (i.e., $\sigma_v$\eq$\sigma_v^{\rm rms}$).
+\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis} We find comparable velocity dispersion derived by taking the root mean square ($\sigma_v^{\rm rms}$) versus that derived using thermal and non-thermal pressure \AP{i would not introduce additional symbols if they are not used elsewhere} ($\sigma_v^{P+P_{\rm nt}}$), indicating that rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
+In the subsequent sections, we adopt the root mean square of the velocity field as the velocity dispersion (i.e., $\sigma_v$\eq$\sigma_v^{\rm rms}$).
 
@@
 These are the MCs at the center of the main disk of \flower.
+\AP{however a plot showing the clump stats has not been show yet at this point}
 Their high velocity dispersions and surface densities are expected since 
@@
 As such, we effectively identify a population of denser molecular structures. 
+\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
 This population of sub-MCs has dynamics largely
@@
 \subsection{Schmidt-Kennicutt Relation}
+\AP{I would merge this sub with Sec. \ref{sec:ncut} (and maybe move this stuff into the appendix)}
 As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
 
+\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot; in any case, here I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
+
 \subsection{SFR-Mach Relation}
+\AP{here (or before) we should explain how the sfr is calculated (i.e. integrating over the recent sfr history of star within the clump)}
 In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
@@
 \end{figure*}
+
+\AP{i think this section should be just before the conclusion/discussion}
 
@@
 
+\AP{i guess that we can either choose to put it at the beginning of the results or at the end (before the CMF), to explain the origin of the clumps; in ancy case, the strategy should be to select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}
+
 In the limit of a thin rotating disk, rotation can help stabilizes self-gravitational contraction for wavelengths greater than the Toomre length:
@@
 \section{Discussions and Implications}     \label{sec:diss}
+
+\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
+
 Yet.... at the epoch of reionization.... For instance, to resolve the 
@@
 \subsection{Virial Parameter}
+
+\AP{I would move it to the previous section; since it is not easy to condense the toomre analysis for different snapshots in a single plot, I would use the virial parameter analysis to discuss the gravitational instability point on more then on evolutionary state of the galaxy}
+
 We quantify how stable a molecular structure is using the virial parameter, which 
@@
 \subsection{Larson's Relation}
+
+\AP{I would move it to the previous section}
+
 The Larson's relation... empirically-motivated.

### 2018-08-20 WRITEUP/ms.tex
write some more

--- 2018-08-13 WRITEUP/ms.tex
@@
 % stronger and harder radiation fields),
-more {\sc HII} regions and ionized gas 
+more \ion{H}{2} regions and ionized gas 
 (given their much higher star formation rates; SFR), and 
@@
 This paper is structured as follows.
-In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower).
-In \Sec{method}, we describe the method used to identify its molecular gas complexes (MC). 
-In \Sec{results}, we present scaling relations found based on the properties of 
-the identified MC and compare them with observations of molecular 
+In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
+and describe the method used to identify its molecular gas complexes (MC). 
+In \Sec{results}, we present scaling relations based on 
+the MC identified and compare them with observations of molecular 
 (sub-)structures seen in nearby and \z$>$\,0 galaxies.
-In \Sec{diss}, we discuss the results and implication of our findings,
-and conclude in \Sec{conclusion}.
+We present Toomre stability analysis in \Sec{Q} and 
+the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
+In \Sec{diss}, we discuss the results and implications of our findings,
+and present our conclusions in \Sec{conclusion}.
 Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities 
@@
 % ------------------
-\section{Simulations} \label{sec:sim}
+\section{Method: Simulation and ``Clump''-finding} \label{sec:sim}
 
@@
 
-\section{Method} \label{sec:method}
+\subsection{``Clump''-finding} \label{sec:method}
 
@@
 In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
-molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6\,$-$\,15, {\bf Pallo, check this pls}).
+molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
 We note that this process is in essence similar to 
@@
 using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
-and \ncode{cprops}; \citealt{Williams94a, Rosolowsky06a}).
+and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
 
-\begin{figure}[htbp]
+\begin{figure}[Htbp]
 \centering
@@
 $n_{\rm cut}$ adopted and find no significant differences 
-affecting the results and conclusions of this work (see \Sec{ncut}).}
+affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
 to the same snapshot as that 
@@
 easily see that they are collections of disjoint structures.
-We repeat this identification process for 14 snapshots, spaced by $\Delta t$\eq50\,Myr. 
-{\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
+We repeat this identification process for 14 snapshots between 
+redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr. 
+% {\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
+
 Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
@@
 % --------------------
-\section{Star Formation History and Cloud Evolution} \label{sec:sfh}
+\section{Results}     \label{sec:results}
+\subsection{Star Formation History and Cloud Evolution} \label{sec:sfh}
 
-One of the advantage of studying the dynamical properties of molecular structures at 
-$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
+One of the advantages in studying the properties of MCs at 
+$z$\ssim6 using simulations is that we can examine how their properties evolve 
 as a function of time. 
-Especially at early epochs, where the densest structures are beginning to form; 
+This is advantageous especially at early cosmic epochs, 
+when the densest structures are beginning to form; 
 gas is constantly being accreted onto the central galaxy from the cosmic web and 
@@
 galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
-for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
+for the molecular structures (e.g., some may disperse while others may agglomerate into more massive 
 structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
@@
 is a factor of two higher than shown here since they also include contributions from 
-massive satellites galaxies within the surrounding xxx\,kpc.}
+massive satellites galaxies within the surrounding $\approx$50\,kpc, which 
+are accreted onto \flower at \z$\lesssim$\,2.}
 as it evolves from an actively accreting phase to 
@@
 Star formation history of \flower.
+% f_gas history? 
 \label{fig:SFH}}
@@
 \caption{
-Projected stellar mass distribution of \flower during one of its accretion phases 
-at an early stage of its evolution (top) and during one of its major starburst phases 
+Projected stellar mass distribution of \flower during the accretion phase
+in its early stage of evolution (top) and during a major starburst phase 
 after a major merger (bottom).
@@
 
-\section{Cloud scaling relations} \label{sec:results}
-Upon identified the molecular structures, we extract parameters such as
+\subsection{Cloud Scaling Relations} 
+Molecular clouds are the natal place for \SF, and thus,
+their structure and dynamics hold important clues to understanding 
+the mechanisms and physics of formation and evolution of molecular structures and \SF.
+Upon identifying the molecular structures, we extract parameters such as
 the virial parameter ($\alpha_{\rm vir}$), 
-the cloud mass ($M_{\rm cl}$), 
+the ``cloud'' mass ($M_{\rm cl}$), 
+the ``cloud'' size ($R$),  
 the Mach number ($\mathcal{M}$), 
-the velocity dispersion ($\sigma_v$), and the 
+the velocity dispersion ($\sigma$), and the 
 gas surface density ($\Sigma_{\rm gas}$)
 to describe/characterize their dynamics.
-We find that the thermal sound speed ($c_s$) 
+We show in \Fig{} the MC distributions in terms of their 
+molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ + 
+$M_*$)). 
+% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
+% plt.hist($R_{\rm cl}$), using same color scheme
+% for f_gas, same color scheme
+We note that the distributions vary for different snapshots, depending on
+the gas surface density, the morphology, and the evolutionary stage of \flower.
+The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
+the order of 10$^{6.5}$\,\Msun for the densest MC identified.
+Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx. 
+% which may determine the ``cloud'' mass if these MCs are formed due to gravitational 
+% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
+We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the 
+snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).
+
+We find that the local sound speed ($c_s$) 
 of all identified molecular complexes are generally much smaller compared to the their
 turbulent velocities.
-We find comparable velocity dispersion derived by taking the root mean square ($\sigma_v^{\rm rms}$) versus
-that derived using thermal and non-thermal pressure ($\sigma_v^{P+P_{\rm nt}}$), indicating that 
+We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
+that derived using thermal and non-thermal pressure ($\sigma^{P+P_{\rm nt}}$), indicating that 
 rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
 In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion (i.e., $\sigma_v$\eq$\sigma_v^{\rm rms}$).
+as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
+In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the 
+MCs due to galactic rotation and shear.
 
-\subsection{Single snapshots}  \label{sec:singless}
+In the following subsections, 
+we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which 
+describe interactions between gravity and turbulence and is one of the ``fundamental''/first 
+relations for studying star-forming molecular structure formation (linewidth-size, 
+density-size, and mass-size relations) and for comparing properties of molecular structures
+in different galactic environments.
+In particular, the Larson's relations attempt to understand the physics behind molecular 
+structures via observables (e.g., $\sigma$, $R$, and $M_{\rm cl}$).
+% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
+Observations of nearby gas-rich galaxies such as M64 and NGC\,253 
+show higher velocity dispersions compared 
+to the disk/mid-plane of the Milky Way which 
+are more consistent with those observed in the inner regions of 
+Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$, 
+% which is $\propto\rho\sigma^2$
+While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
+to the inner regions of Milky Way, they are found to be bigger in size (approximately 
+an order of magnitude) and mass (approximately two orders of magnitude).
+These bigger clouds have been interpreted as a results of their higher gas mass fractions and 
+surface densities and velocity dispersions, since 
+fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ 
+and Jeans mass $M_J\propto\sigma^4/\Sigma$
+for dispersion-supported structures.
+
+% Relating Larson's law to stability and pressure (perhaps move this to other section?).
+A spherically symmetric cloud of mass $M$ and radius $R$ embedded within 
+a medium of pressure $P$ is described using the virial theorem
+\begin{equation}
+\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
+\end{equation}
+where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
+$T$ is the volume term of the total kinetic energy (including thermal and 
+bulk motions), $T_s$ is the surface term due to external thermal pressure, 
+$W$ is the gravity term, and $B$ is the magnetic term.
+In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
+\begin{equation}
+\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
+\label{eqn:virial}
+\end{equation}
+where the first term on the right hand side (RHS) is the pressure from velocity dispersion, second 
+term is the gravity term, and the third term is the external pressure term.
+For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), 
+the LHS vanishes and the equation becomes:
+\begin{equation}
+\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
+\end{equation}
+where $\Gamma$ is set to 3/5 for a uniform sphere, and we can define
+\begin{equation}
+V_0^2\equiv\frac{\sigma^2}{R},
+\end{equation}
+which is related to the scaling in one of the Larson's relations (linewidth-size), 
+and can re-written in the form of: 
+\begin{equation}
+\sigma^2/R = \pi G \Sigma/5.
+\end{equation}
+For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), Equation~\ref{eqn:virial} becomes 
+\begin{equation}
+P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
+\label{eqn:pext}
+\end{equation}
+which describes the external pressure needed to confine the gas inside a volume $V$.
+Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express 
+this equation using the following:
+\begin{equation}
+\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
+\label{eqn:v0}
+\end{equation}
+For a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
+$\sigma^2/R\propto\Sigma$, whereas 
+Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are 
+needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. 
+In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$ 
+is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
+varies depending on $P_{\rm ext}$; cf. expectation for SVE
+$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+
+\subsubsection{Single Snapshots: Larson's Relations and Virial Parameter}  \label{sec:singless}
+
 In each snapshot (see \Fig{MC} for example), 
 we identify a set of MCs with consistently high turbulences and surface densities 
-regardless of the H$_2$ density cuts adopted. 
-These are the MCs at the center of the main disk of \flower.
+regardless of the choice of H$_2$ density threshold ($n_{\rm cut}$) adopted.
+These are the MCs at the center of the main disk of \flower and 
+occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
 Their high velocity dispersions and surface densities are expected since 
 they are located in the nuclear regions of the 
-galaxy, where the potential well is also deeper.
+galaxy, where the potential well is also deeper. The higher velocity dispersions 
+in these MCs can also be understood as they have experienced more recent episodes 
+of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60). 
+In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
+to the top panel of \Fig{phases} and \Fig{larsons_single}), \flower has assembled 
+a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion 
+is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
+The virial parameter of the MC identified in (the densest region of) the main disk of \flower 
+indicate that the MC itself is gravitationally unbound.
 
@@
 into multiple sub-MCs.
-As such, we effectively identify a population of denser molecular structures. 
+As such, we effectively identify a population of denser molecular structures (\Fig{MC}). 
 This population of sub-MCs has dynamics largely
@@
 in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
-terms of their velocity dispersions, sizes, and gas surface densities \citep[e.g.,][]{Swinbank11a}.
+terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see 
+e.g., \citealt{Swinbank11a}),
+with cloud sizes on the order of $R\simeq$100\,pc and velocity 
+dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$ 
+are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
+the conventional wisdom that collapsing structures result from local gravitational 
+instability within globally stable structures, which are supported by 
+turbulence and rotation on large scales.
 
 We also identify MCs in the satellite galaxies of \flower. These MCs 
-tend to have lower virial parameters compared to the (sub-)MCs in the main disk of \flower, 
-with $\alpha_{\rm vir}\simeq$1.
-Given their low $\alpha_{\rm vir}$ parameter,
-these structures are likely collapsing structures (\Fig{alpha16}).
+tend to have lower velocity dispersions compared to those of \flower which are more comparable
+to those observed in the inner Milky way and 
+nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), 
+along the locus of $\sigma\propto R^{0.56}$.
+These MCs in the satellite galaxies also have 
+lower virial parameters compared to the (sub-)MCs in the main disk of \flower, 
+with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker 
+stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
+\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
+these structures are likely collapsing structures. 
+Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter, 
+the MCs of the satellite galaxies of 
+\flower are close to being in virial equilibrium
+and are not supported against collapse by external pressure. % are bound
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
+\caption{
+Larson's (linewidth-size) relation of \flower in 
+accreting phase (top) and
+starburst phase(bottom) and 
+those observed in nearby and the \z$\sim$2 star-forming galaxy.
+\label{fig:larsons_single}}
+\end{figure*}
 
@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
-\caption{
-Larson's relation of \flower in 
-accreting phase (top) and
-starburst phase(bottom) and 
-those observed in nearby and the \z$\sim$2 star-forming galaxy.
-\label{fig:larsons_single}}
-\end{figure*}
+% -------------- all snapshots -----------
 
@@
 
-\subsection{Variation in MC Properties Depending on Choice of Density Cuts}	 \label{sec:ncut}
+% \subsubsection{Single Snapshots: Size Mass Relation} to merge with section 3.2.1
+
+\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
+%M~ 30 in normal spirals \citep{McKee99a}
+%M~ 100 in SBs \citep{Downes98a}
+In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
+complexes identified. 
+We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
+which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
+the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
+massive stars.
+
+\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
 % single Snapshot
@@
 to test 
-the robustness of our results against the choice of density threshold in \Sec{ncut}.
-That is, how sensitive are the structure properties, and thus, the conclusion of our study
+the robustness of our results against the choice of density threshold by adopting 
+different sets of $n_{\rm cut}$ in identifying the MCs.
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
 dependent on the choice of density thresholds.
@@
 cloud scaling relations). 
-We interpret this lack of variation a manifestation of ..., and that, at least on the scales studied here, the cloud properties are what we found ... 
+In addition, for the densest MC in the main disk of \flower, we find that while 
+its cloud size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, 
+its velocity dispersion remain 
+approximately $\sigma\simeq$200\,\kms (\Fig{larsons_single}). 
+This lack of variation is reassuring, in the sense that at least on the scales studied here, 
+the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
 Our results is therefore robust, haha.
@@
 
-\subsection{Schmidt-Kennicutt Relation}
-As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
+\section{Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
+For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk 
+of finite thickness $h$ 
+is described by:
+\begin{equation}
+\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
+\label{eqn:3Ddisp}
+\end{equation}
+where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
+The first term on the RHS describes rotation support, second term describes self-gravity, and 
+the third term describes pressure support.
+The epicyclic frequency is defined as:
+\begin{equation}
+\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
+\label{eqn:kappa}
+\end{equation}
+% \kappa\propto\Omega 
+One can then define the so-called Toomre-Q parameter/criterion for stability as
+\begin{equation}
+Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
+\label{eqn:Q}
+\end{equation}
+We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of 
+\begin{equation}
+\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
+\end{equation}
+Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
+and fragmentation can happen 
+(e.g., instability impose by angular momentum from gas accretion from the cosmic web and 
+satellite galaxies and stellar feedback).
+That is, local fragmentation takes place when gravity overcomes pressure support
+from turbulence (thermal is small here) and shearing of differential rotation.
 
-\subsection{SFR-Mach Relation}
-In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
-complexes identified. 
-We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
-which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
-the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
-massive stars.
+In the limit of a thin rotating disk, rotation can help stabilizes 
+self-gravitational contraction for wavelengths greater than the Toomre length:
+\begin{equation}
+\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
+\end{equation} 
+yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
+which is the ``upper limit'' to which MCs can form in a shearing disk.
 
-\subsection{Clump Mass Function}
+\section{Cumulative Mass Distribution}   \label{sec:cmf}
 
@@
 
+Consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible), 
+between $M_{\rm cl}\approx$10$^{7-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
+
+% slope
 Noisy due to resolution effect, since we only have one galaxy here. However, 
 we could improve the ``signal-to-noise'' ratio by including clouds identified from different 
-snapshots (valid unless in some snapshots, the galaxy experience a violent event).
+snapshots\footnote{This approach is valid unless in some snapshots, 
+the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
 We find a shallower slope in the CMF of \flower (\Fig{cmf}) 
@@
 $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}).
+The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the 
+highest $n_{\rm cut}$ adopted in this study.
+The uncertainties here are the formal fitting uncertainties.
 
+% interpretation
+A higher $\sigma$ and $\Sigma_{\rm gas}$ is related to the higher 
+pressure. The higher $\Sigma_{\rm gas}$ is also related to more massive clouds being formed.
+In M64, there are few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun, such massive molecular 
+structures are unknown to local group, and are likely the ... from which massive clusters or OB associations are to be formed.
+In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$.
+
+% a bit on caveat
 While our result, of particular relevance here is the slope of the CMF, is subject 
@@
 the molecular complexes' properties vary under the influence of gas inflow/outflow.
-
-\section{Mass Scales set by Toomre and Jeans Instabilities}
-
-In the limit of a thin rotating disk, rotation can help stabilizes self-gravitational contraction for wavelengths greater than the Toomre length:
-\begin{equation}
-\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
-\end{equation} 
-where $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
-However, if the condition $Q<Q_{\rm crit}$ is satisfied, where the latter is set by 
-the thermal pressure, then fragmentation can happen 
-(e.g., instability impose by angular momentum from gas accretion from the cosmic web and 
-satellite galaxies and stellar feedback).
 
@@
 
-\subsection{Larson's Relation}
-The Larson's relation... empirically-motivated.
-
 \subsection{CMF and IMF at EoR}
@@
 We study the dynamical properties of molecular complexes in a \z$\sim$6 lyman-break galaxy, 
-at the end of the epoch of reionization, using state-of-the-art cosmological zoom-in simulation 
+at the end of the epoch of reionization using state-of-the-art cosmological zoom-in simulation 
 (\ncode{Serra}). We identify molecular cloud complexes in the main galaxy of the 
@@
 Using volumetric H$_2$ is essentially the same as identified molecular structures using
-different contours in line emission (e.g., CO, CS, NH$_3$) since the line luminosity scales with the molecular gas density.
+different contours in line emission (e.g., CO, CS, NH$_3$) 
+% and different molecular line tracers trace different MCs on different scales due to their 
+% different critical densities.
+since the line luminosity scales with the molecular gas density.
 Our simulations include the effect of feedback from .... .and ....., which are the main source 

### 2018-08-20 WRITEUP/ms.tex
fixed some redudancy after last commit merge

@@
 \makeatother
+
+\usepackage{xcolor}
+\definecolor{apcolor}{HTML}{b3003b}
+\definecolor{dlcolor}{HTML}{FF7F00}
+\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
+\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
 
@@
 hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
-kinetic and thermal energies. We..
+kinetic and thermal energies. We find that ..
 \end{abstract}
@@
 %(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
-Some theoretical works postulate that it is in fact the
+Some theoretical works argues that it is in fact the
 migration of such giant massive clumps that are responsible for contributing to the
@@
 
-At high redshifts, galaxies are expected to have lower metallicity, 
-% stronger and harder radiation fields),
-more \ion{H}{2} regions and ionized gas 
-(given their much higher star formation rates; SFR), and 
-more intense radiation stellar feedbacks.
-Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
-and thus, their multi-phase ISM differ from nearby galaxies.
-Since \highz galaxies are the early stages of evolution of present-day galaxies, 
-studying their ISM properties is essential for understanding how \SF proceed under these more extreme
-conditions, thereby driving the evolution and assembly history 
-of galaxies since the cosmic dark ages.
-% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
+At high redshifts, galaxies have higher star formation rates (SFR) and smaller sizes {\bf cite needed?}, thus are expected to have more \ion{H}{2} regions and ionized gas, and more intense radiation stellar feedbacks.
+Since also the metallicity and dust content should be lower {\bf cite?}, this affects the shielding of UV photons, heating and cooling mechanisms.
+Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
+%
+Since \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies since the cosmic dark ages.
 
@@
 molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+\AP{i think the passage to "why we focus on eor galaxies" should be detailed a bit more}
 However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
@@
 This paper is structured as follows.
+\AP{TBM}
 In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
@@
 adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
-In particular, it uses a modified version of \ncode{ramses} as the AMR backend.
-\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and 
-photoevaporation feedback in the neutral diffuse and molecular gas. 
-Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving 
-down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the 
-finest level.
-Such a physical scale is close to the size scale of molecular cloud complexes and
-giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
+%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
+Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level.
+Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
 % (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
-We include chemical network in the simulation to trace 
-$\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance to our study here is that 
-our simulation includes non-equilibrium formation of molecular 
-hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of 
-chemistry affected by non-equilibrium versus equilibrium H$_2$ formation). 
+We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
+Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).
+
+% radiative feedback --> NT pressure
 Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and 
-include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
-The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
-Radiation pressure (on the dust and gas) is also included.  % radiative feedback --> NT pressure
-To couple the feedback to the gas, we 
-employ sub-grid modeling for blastwaves to account for the potential lost of energy inside the cell when
-supernovae are exploded.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
+To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode.
+The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy, and radiation pressure (on the dust and gas) is also included \citep[see][for details]{Pallottini17a}.
 
-Details of how \flower, the main galaxy in our simulation,
-was identified is discussed in detail by \citet{Pallottini17a}.
-Briefly, by \z$\sim$6, \flower is a LBG hosted in 
-a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and 
-accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
-At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun,
-metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$,
-a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun,
-and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne\footnote{This includes contributions from its nearby massive satellite galaxies.}.
+Details on the properties of \flower, the main galaxy in our simulation, are discussed in \citet{Pallottini17b}.
+%
+Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
+At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
 It is therefore a prototypical galaxy at \z$\sim$6.
 
-\subsection{``Clump''-finding} \label{sec:method}
+\subsection{Star Formation History} \label{sec:sfh}
 
-To identify the molecular complexes, we use a customized version of the clump finder algorithm 
-available in the \ncode{python} package \ncode{yt}, which was initially described in \citet{Smith09a}
-but this function has been modified since then.
-The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation
-into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
-It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across 
-the tiles. In the customized version used for this study, we modified \ncode{yt} in order for it to actually work.
+\AP{i moved the section here, as I see it as part of motivation for the workflow; however, at the moment I do not see the stellar mass maps as figure that are needed; if they stay i would label their evolutionary stage in the SFR history plot.}
+
+One of the advantage of studying the dynamical properties of molecular structures at
+$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
+as a function of time.
+This is advantageous especially at early cosmic epochs,
+when the densest structures are beginning to form;
+gas is constantly being accreted onto the central galaxy from the cosmic web and
+satellite galaxies, thereby leading to bursts of \SF.
+Meanwhile, tidal forces resulting from interactions with these surrounding
+galaxies can disrupt the main disk and arms, likely leading to different dynamical states
+for the molecular structures (e.g., some may disperse while others may agglomerate into more massive
+structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
+
+We show the \SF history of \flower in \Fig{SFH}, where
+the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
+The SFR plotted in Figure 2 of \citet{Pallottini17b}
+is a factor of two higher than shown here since they also include contributions from
+massive satellites galaxies within the surrounding $\approx$50\,kpc, which
+are accreted onto \flower at \z$\lesssim$\,2.}
+as it evolves from an actively accreting phase to
+a starburst phase after a major merger and then back to a relatively quiescent phase
+over the few hundred Myr simulated in our simulation.
+The SFR of \flower is calculated based on existing young stellar population, which is
+defined to have an age of $t_{\rm age}<$\,10\,Myr.
+
+Given the stochasticity in the \SF history of \flower,
+we show the scaling relations found for two particular snapshots \AP{in the text I would refer to snapshots as to evolutionary stages of the galaxy (and make the link between the two in the method section)} as examples in \Sec{singless},
+since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
+most extreme variations in the cloud dynamics) --- one of which \flower is
+actively accreting materials from its surrounding (top panel of \Fig{phases})
+and another of which \flower is undergoing
+a starburst phase after a major merger (bottom panel of \Fig{phases}).
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}
+\caption{
+	Star formation history of \flower \AP{if possible I would combine it with Fig. \ref{fig:phases} (as in the talk), or remove
+	Fig. \ref{fig:phases}, as at the moment it does not add much to the discussion.
+	}.
+% f_gas history?
+\label{fig:SFH}}
+\end{figure*}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}
+\\ [-5em]
+\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}
+\caption{
+Projected stellar mass distribution of \flower during one of its accretion phases
+at an early stage of its evolution (top) and during one of its major starburst phases
+after a major merger (bottom).
+\label{fig:phases}}
+\end{figure}
+
+\subsection{Structure identification} \label{sec:method}
+
+To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a} but this function has been modified since then.
+%
+The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
+It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles.
+In the customized version used for this study, \AP{the following is true but I do not think we should write it in this way ...} \DL{right, will change when we submit paper, just being sarcastic here.} we modified \ncode{yt} in order for it to actually work.
 
@@
 molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
+
+\AP{maybe we can refer to the PPP vs PPV method discussion in Mordecai's paper}
 We note that this process is in essence similar to
@@
 
-\begin{figure}[Htbp]
+\begin{figure}[htbp]
 \centering
@@
 for a given snapshot which includes contributions from its surrounding 7\,kpc.
-In \Fig{MC}, we show an example of
-the molecular structures identified by applying volumetric H$_2$ density cuts of 
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
-Based on 10$^n$, where $n$ represents the 10 elements that are 
-uniformly spaced between [$-0.5, 1.5$] in linear space.
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
+found based on the Minkovsky analysis presented by \citet{Pallottini17b}.
+In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of \AP{I would directly use labels in logspace} $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
 We also vary the range of
@@
 redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
-% {\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
 
-Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
-impose an addition constraint such that an identified structure only survives if it
-spans at least 10 cells in 3D position-position-position (PPP) space. 
-We caution that one caveats of such constraint is that 
-we can only examine the parameter space of ``cloud'' scaling
-relations at ``cloud'' size $R\gtrsim100$\,pc.
+Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in 3D position-position-position (PPP) space.
+We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.
 
-% --------------------
 \section{Results}     \label{sec:results}
-\subsection{Star Formation History and Cloud Evolution} \label{sec:sfh}
-
-One of the advantages in studying the properties of MCs at 
-$z$\ssim6 using simulations is that we can examine how their properties evolve 
-as a function of time. 
-This is advantageous especially at early cosmic epochs, 
-when the densest structures are beginning to form; 
-gas is constantly being accreted onto the central galaxy from the cosmic web and 
-satellite galaxies, thereby leading to bursts of \SF.
-Meanwhile, tidal forces resulting from interactions with these surrounding 
-galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
-for the molecular structures (e.g., some may disperse while others may agglomerate into more massive 
-structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
-
-We show the \SF history of \flower in \Fig{SFH}, where 
-the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
-The SFR plotted in Figure 2 of \citet{Pallottini17b}
-is a factor of two higher than shown here since they also include contributions from 
-massive satellites galaxies within the surrounding $\approx$50\,kpc, which 
-are accreted onto \flower at \z$\lesssim$\,2.}
-as it evolves from an actively accreting phase to 
-a starburst phase after a major merger and then back to a relatively quiescent phase
-over the few hundred Myr simulated in our simulation.
-The SFR of \flower is calculated based on existing young stellar population, which is 
-defined to have an age of $t_{\rm age}<$\,10\,Myr.
-
-Given the stochasticity in the \SF history of \flower, 
-we show the scaling relations found for two particular snapshots as examples in \Sec{singless},
-since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
-most extreme variations in the cloud dynamics) --- one of which \flower is 
-actively accreting materials from its surrounding (top panel of \Fig{phases}) 
-and another of which \flower is undergoing 
-a starburst phase after a major merger (bottom panel of \Fig{phases}).
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
-\caption{
-Star formation history of \flower.
-% f_gas history? 
-\label{fig:SFH}}
-\end{figure*}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
-\\ [-5em]
-\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
-\caption{
-Projected stellar mass distribution of \flower during the accretion phase
-in its early stage of evolution (top) and during a major starburst phase 
-after a major merger (bottom).
-\label{fig:phases}}
-\end{figure}
 
 \subsection{Cloud Scaling Relations}
+\AP{I see 2 main possible approaches to the presentation of the results
+%
+(a) focus on a single snapshot, analyze the cloud scaling relation by varing the cuts and then by varing the snapshot; after that one can discuss the stability (toomre analysis) of the clumps (that should help in discussing the origin) and the CMF (more speculative, because of the resolution issues).
+%
+(b) discuss each scaling relation one at a time; probabily in this case an introductionary subsection is needed to explain that different cuts yields no qualitative differences; toomre and CMF as before.
+%
+Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
+%
+I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g.
+the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
+%
+Of course alternative approaches are possible, but right now these two seem to be the more natural ones.
+}
+
 Molecular clouds are the natal place for \SF, and thus,
@@
 turbulent velocities.
+\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
 We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
-that derived using thermal and non-thermal pressure ($\sigma^{P+P_{\rm nt}}$), indicating that 
+that derived using thermal and non-thermal pressure \AP{i would not introduce additional symbols if they are not used elsewhere} ($\sigma^{P+P_{\rm nt}}$), indicating that
 rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
@@
 
+%
+\AP{I would move the following when discussing the velocity dispersion; additionally, the large velocity dispersions was also noted in Vallini2018a, we can use some of those results to complement the discussion (e.g.
+shift for the CO sled at higher J then local galaxies).}
+
 In each snapshot (see \Fig{MC} for example),
 we identify a set of MCs with consistently high turbulences and surface densities
-regardless of the choice of H$_2$ density threshold ($n_{\rm cut}$) adopted.
+regardless of the H$_2$ density cuts adopted.
 These are the MCs at the center of the main disk of \flower and
 occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
+\AP{however a plot showing the clump stats has not been show yet at this point}
 Their high velocity dispersions and surface densities are expected since
@@
 As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
+\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
 This population of sub-MCs has dynamics largely
@@
 %M~ 100 in SBs \citep{Downes98a}
+\AP{here (or before) we should explain how the sfr is calculated (i.e. integrating over the recent sfr history of star within the clump)}
 In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
@@
 massive stars.
+
+\subsubsection{Schmidt-Kennicutt Relation}
+\AP{I would maybe move this stuff into the appendix}
+As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
+
+\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot; in any case, here I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
 
@@
 \section{Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
+
+\AP{i guess that we can either choose to put it at the beginning of the results or at the end (before the CMF), to explain the origin of the clumps; in ancy case, the strategy should be to select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}
+
 For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
@@
 
-Consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible), 
+The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible),
 between $M_{\rm cl}\approx$10$^{7-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
 
-% slope
 Noisy due to resolution effect, since we only have one galaxy here. However,
@@
 \section{Discussions and Implications}     \label{sec:diss}
+
+\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
+
 Yet.... at the epoch of reionization.... For instance, to resolve the
@@
 \subsection{Virial Parameter}
+
+\AP{I would move it to the previous section; since it is not easy to condense the toomre analysis for different snapshots in a single plot, I would use the virial parameter analysis to discuss the gravitational instability point on more then on evolutionary state of the galaxy}
+
 We quantify how stable a molecular structure is using the virial parameter, which

### 2018-08-20 plotSS.py
plot MC basic distributions

@@ -2,43 +2,66 @@
 
 plot physical properties of clouds across all snapshots, identified using same way (ncut, steps, etc).
 
-last mod: 24 July 2018
+last mod: 18 Aug 2018
 
 
 '''
 
 import os
 from plot_modules.plot_cloud_prop import setup_plot
-plt = setup_plot()
+setup_plot()
+import matplotlib.pyplot as plt
 
-here      = os.path.dirname(os.path.abspath(__file__))
-std_pickle= here+'/test_brute/'
 
-def plotting_procedure(minss, maxss, fname ,pickle_base_fold= std_pickle):
-    from plot_modules.plot_cloud_prop import unpack_xy, plot_stuff, plot_stuff_3dim
+def load_pickleTOplot(minss, maxss, fname):
+    from plot_modules.plot_cloud_prop import unpack_xy
     from io_modules.leaf_pickle import load_in_pickle_SS
 
-    ss = load_in_pickle_SS(pickle_base_fold+'leaf_fields_', fname, minss, maxss)
+    here = os.path.dirname(os.path.abspath(__file__))
+    pickle_base_fold = here + '/test_brute/'
+
+    ss = load_in_pickle_SS(pickle_base_fold + 'leaf_fields_', \
+                                fname, minss, maxss)
     to_plot = unpack_xy(ss)
 
-    outleafdir = pickle_base_fold+'leaf_fields_ss' + \
-                 str(minss) + '-' + str(maxss) + '/'
+    outleafdir = pickle_base_fold + 'leaf_fields_ss' + \
+        str(minss) + '-' + str(maxss) + '/'
     leafdir_out = outleafdir + fname[:fname.find('.p')] + '/'
     if not os.path.isdir(leafdir_out):
         os.system('mkdir -p ' + leafdir_out)
 
-    plot_stuff("cloud mass", "mass over jeans mass", leglabel="sfr: ", to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("cloud mass", "jeans mass",  leglabel="sfr: ", to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("cloud mass", "alpha vir", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
[…]

### 2018-09-07 WRITEUP/ms.tex
write some more

@@
 \author{T. K. Daisy Leung\altaffilmark{1, 2}}
-\author{Andrea Pallottini \altaffilmark{3, 4}}
-\author{Andrea Ferrara \altaffilmark{4, 5}}
-\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}
+\author{Andrea Pallottini\altaffilmark{3, 4}}
+\author{Andrea Ferrara\altaffilmark{4, 5}}
+\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7, 8}}
 
@@
 \altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
-\altaffiltext{5}{Kavli IPMU, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
+\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
 \altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
 \altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
+\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
 \email{tleung@astro.cornell.edu}
@@
 \begin{abstract}
-We present results from the first study investigating the dynamical properties of molecular clouds
-and their evolution in galaxies at Epoch of Reionization using state-of-the-art cosmological
-zoom-in simulation, which includes a chemical network to determine the formation of molecular
+We study the dynamical properties of molecular clouds and their temporal evolution in a prototypical galaxy 
+at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
+which includes a chemical network to determine the formation of molecular
 hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
-kinetic and thermal energies. We find that ..
+kinetic and thermal energies. 
+We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
+to identify molecular complexes (MC) and their sub-structures.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
+We find that the MC of \flower are highly supersonic, with large velocity dispersion ($\sigma\approx$\,200\,\kms) comparable to 
+those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
+The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
+corresponds to the arms of the main disk of \flower and breaks down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
+We find that the ...
+The MCs in the satellites..
+consistent with PVE.
+We find no temporal variations in the MC physical properties over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
+Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
+mass distribution, which steepens as we increase $n_{\rm cut}$. Higher resolution cosmological zoom-in simulations 
+will shed light into ... , as we .... from observations.
 \end{abstract}
@@
 
-At high redshifts, galaxies have higher star formation rates (SFR) and smaller sizes {\bf cite needed?}, thus are expected to have more \ion{H}{2} regions and ionized gas, and more intense radiation stellar feedbacks.
-Since also the metallicity and dust content should be lower {\bf cite?}, this affects the shielding of UV photons, heating and cooling mechanisms.
+Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies
+since the cosmic dark ages.
+Current consensus is that at higher redshifts, galaxies have higher 
+star formation rates (SFR) \citep{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
+smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to galaxies found in the local Universe, 
+and thus, they are expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
+Since their metallicity and dust content are also expected to be lower as they are assembling, 
+this affects the shielding of UV photons, heating and cooling mechanisms in this early systems.
 Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
 %
-Since \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies since the cosmic dark ages.
+% talk about dynamical states of MCs of different galaxies?
+Even in the local universe, where the most detailed \obs can be done, we see variations in cloud properties in different galaxy populations (see e.g., Hughes10a, MNRAS, 406, 2065; Hughes+13b, ApJ, 779, 46), maybe also Meidt+13, apj, 779,45?.
+Thus, obvious to pose the question what are the dynamical states of the MCs of the first galaxies and how do they differ from nearby universe, and analogous to any of the nearby \galpop?
+%
 
@@
 molecular gas-rich, turbulent, and clumpy than nearby galaxies.
-\AP{i think the passage to "why we focus on eor galaxies" should be detailed a bit more}
-However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
+On the other hand, the main source of reionization --- the first stars and first galaxies --- 
+are ......
+it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
 that dominates  \SF at the epoch of reionization which is responsible for producing the
@@
 Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations.
 To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode.
-The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy, and radiation pressure (on the dust and gas) is also included \citep[see][for details]{Pallottini17a}.
+The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
+Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).
 
-Details on the properties of \flower, the main galaxy in our simulation, are discussed in \citet{Pallottini17b}.
-%
+Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
 Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
@@
 
+The simulation data contain information such as the density ($\rho$) and velocity ($v_x$, $v_y$, and $v_z$) fields, from which we calculate 
+the physical properties of each MC, such as mass and velocity dispersion.
+Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids for the analysis presented in this paper. 
+The grid size is defined 
+based on the highest resolution of the simulation data (i.e., the less refined regions are supersampled in the resulting uniform grids).
+
 \subsection{Star Formation History} \label{sec:sfh}
-
-\AP{i moved the section here, as I see it as part of motivation for the workflow; however, at the moment I do not see the stellar mass maps as figure that are needed; if they stay i would label their evolutionary stage in the SFR history plot.}
-
 One of the advantage of studying the dynamical properties of molecular structures at
@@
 galaxies can disrupt the main disk and arms, likely leading to different dynamical states
-for the molecular structures (e.g., some may disperse while others may agglomerate into more massive
-structures). % mainly expecting differences in alpha_vir, sigma, M_cl.
+for the molecular structures compared to more evolved galaxies found at 
+a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
+ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
 
@@
 as it evolves from an actively accreting phase to
-a starburst phase after a major merger and then back to a relatively quiescent phase
+a starburst phase after a major merger, and then back to a relatively quiescent phase
 over the few hundred Myr simulated in our simulation.
@@
 Given the stochasticity in the \SF history of \flower,
-we show the scaling relations found for two particular snapshots \AP{in the text I would refer to snapshots as to evolutionary stages of the galaxy (and make the link between the two in the method section)} as examples in \Sec{singless},
+we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
+as examples in \Sec{singless} to illustrate the salient points of the discussion,
 since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
 most extreme variations in the cloud dynamics) --- one of which \flower is
-actively accreting materials from its surrounding (top panel of \Fig{phases})
+actively accreting materials from its surrounding (top panel of \Fig{SFH})
 and another of which \flower is undergoing
-a starburst phase after a major merger (bottom panel of \Fig{phases}).
+a starburst phase after a major merger (bottom panel of \Fig{SFH}).
 
@@
 \centering
-\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}
+\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/daisyleung2.pdf}
 \caption{
-	Star formation history of \flower \AP{if possible I would combine it with Fig. \ref{fig:phases} (as in the talk), or remove
-	Fig. \ref{fig:phases}, as at the moment it does not add much to the discussion.
-	}.
+	Top right: Star formation history of \flower.
+	Projected stellar mass distribution of \flower during one of its accretion phases
+	at its early stage of evolution {\it (a)}; during one of its major starburst phases
+	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
 % f_gas history?
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}
-\\ [-5em]
-\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}
-\caption{
-Projected stellar mass distribution of \flower during one of its accretion phases
-at an early stage of its evolution (top) and during one of its major starburst phases
-after a major merger (bottom).
-\label{fig:phases}}
-\end{figure}
-
 \subsection{Structure identification} \label{sec:method}
-
-To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a} but this function has been modified since then.
+To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
 %
-The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
+The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree).
 It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles.
-In the customized version used for this study, \AP{the following is true but I do not think we should write it in this way ...} \DL{right, will change when we submit paper, just being sarcastic here.} we modified \ncode{yt} in order for it to actually work.
+In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).
 
@@
 molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
-
-\AP{maybe we can refer to the PPP vs PPV method discussion in Mordecai's paper}
 We note that this process is in essence similar to
@@
 and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
+We note that, owing to the nature of \obs, such structures are identified 
+in position-position-velocity (PPV) space in observational studies, whereas in simulations, one has the 
+full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
+% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
+Existing studies find a good correspondence in the dynamical properties extracted in
+PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
+Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
+% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
+1 of Beaumount13a).
+(may be worth putting more thoughts on this after the report is due).
 
@@
 \caption{
-Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
+Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the 
+accreting phase shown in \Fig{SFH}.
 \label{fig:h2density}}
@@
 in any case, we should compress the information, by having a less figures showing multplie cuts (e.g.
-3 of them by using thinner lines should suffice in conveining the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
+3 of them by using thinner lines should suffice in conveying the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
 % yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
@@
 We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
-found based on the Minkovsky analysis presented by \citet{Pallottini17b}.
-In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of \AP{I would directly use labels in logspace} $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
+found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see analysis presented by \citealt{Pallottini17b}).
+In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
+$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
 We also vary the range of
-$n_{\rm cut}$ adopted and find no significant differences
+$n_{\rm cut}$ adopted and find no qualitative differences
 affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
@@
 
-Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in 3D position-position-position (PPP) space.
+Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in PPP space.
 We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.
@@
 \subsection{Cloud Scaling Relations}
+
 \AP{I see 2 main possible approaches to the presentation of the results
 %
-(a) focus on a single snapshot, analyze the cloud scaling relation by varing the cuts and then by varing the snapshot; after that one can discuss the stability (toomre analysis) of the clumps (that should help in discussing the origin) and the CMF (more speculative, because of the resolution issues).
+(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
 %
-(b) discuss each scaling relation one at a time; probabily in this case an introductionary subsection is needed to explain that different cuts yields no qualitative differences; toomre and CMF as before.
+(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
 %
@@
 the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
-%
-Of course alternative approaches are possible, but right now these two seem to be the more natural ones.
 }
+\DL{agreed, but will move things around later, after the report and after most of the content is ready.}
 
@@
 to describe/characterize their dynamics.
-We show in \Fig{} the MC distributions in terms of their
-molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
+
+The mass of an MC is calculated from the uniformly-gridded 3D density field,
+integrating over all zones of the MC, multiplied by its volume. 
+The size of an MC ($R$) is defined assuming spherical geometry (i.e., 
+the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
+Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
+the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
+\end{equation}
+where $N$ is the number of zones of each MC.
+The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
+\begin{equation}
+\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
+\end{equation}
+The local sound speed ($c_s$)
+of all identified molecular complexes are generally much smaller compared to the their
+turbulent velocities.
+\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
+We find comparable velocity dispersion derived by taking the root mean square versus
+that derived using thermal and non-thermal pressure, indicating that
+rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
+We quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
+In the subsequent sections, we adopt the root mean square of the velocity field
+as the velocity dispersion ($\sigma$).
+
+We show in \Fig{dist} the MC distributions in terms of their
+molecular gas masses, radii, gas mass fraction ($sf_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
 $M_*$)).
-% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
-% plt.hist($R_{\rm cl}$), using same color scheme
-% for f_gas, same color scheme
-We note that the distributions vary for different snapshots, depending on
-the gas surface density, the morphology, and the evolutionary stage of \flower.
+We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
 The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
 the order of 10$^{6.5}$\,\Msun for the densest MC identified.
-Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx.
-% which may determine the ``cloud'' mass if these MCs are formed due to gravitational
-% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
 We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
@@
 
-We find that the local sound speed ($c_s$)
-of all identified molecular complexes are generally much smaller compared to the their
-turbulent velocities.
-\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
-We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
-that derived using thermal and non-thermal pressure \AP{i would not introduce additional symbols if they are not used elsewhere} ($\sigma^{P+P_{\rm nt}}$), indicating that
-rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
-In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
-In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the
-MCs due to galactic rotation and shear.
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
+\caption{
+Distributions of masses, sizes, and gas mass fractions of MCs identified using 
+the lowest $n_{\rm cut}$ (left panels) and the highest $n_{\rm ncut}$ (right panels).
+Note the y-axis scales are different between the left and the right panels, as less MCs are identified 
+at higher $n_{\rm cut}$.
+\label{fig:dist}}
+\end{figure*}
 
@@
 \end{equation}
-For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), Equation~\ref{eqn:virial} becomes
+For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
+Equation~\ref{eqn:virial} becomes
 \begin{equation}
@@
 In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
-to the top panel of \Fig{phases} and \Fig{larsons_single}), \flower has assembled
+to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
 a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
@@
 
-% \subsubsection{Single Snapshots: Size Mass Relation} to merge with section 3.2.1
+% cloud structures at large and small scale
+% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
+% column density) as fundamental properties of molecular cloud structure.
+Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales 
+via two physical properties: mass and size \citep{Larson81a, Mckee07a}. This is also known as the law of constant column density, 
+since cloud mass in \obs is sometimes derived by integrating
+over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).   
+That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
+Therefore, cloud mass is related to $N_{\rm H2}$ and $A_V$.
 
-\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
-%M~ 30 in normal spirals \citep{McKee99a}
-%M~ 100 in SBs \citep{Downes98a}
-\AP{here (or before) we should explain how the sfr is calculated (i.e. integrating over the recent sfr history of star within the clump)}
-In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
-complexes identified.
-We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx,
-which is unsurprising given that our simulations include the effect of stellar feedback. That is,
-the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from
-massive stars.
+We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
+compared to the empirical relation obtained based on 
+Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
+which we extrapolate to match the mass and size scales of the MCs of \flower.
+By comparing the masses and sizes found in clouds without massive \SF ($<$10\,\Msun) 
+in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
+Pipe Nebula) and those with massive \SF in the Milky Way, \citet{Kauffmann10c} find a 
+mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
+That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
+at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
+with visual extinction of $A_V$\eq4\,mag. This may suggest that xyzxyz.
+We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
+parameter space as the accreting phase.
 
-\subsubsection{Schmidt-Kennicutt Relation}
-\AP{I would maybe move this stuff into the appendix}
-As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
+\caption{
+Size-mass relation of MCs in \flower compared to data and empirical established based on Milky Way \obs.
+Star symbols show MCs identified in the accreting phase of \flower in our simulation, color-coded by increasing $n_{\rm cut}$.
+Other symbols show the masses and sizes of molecular clouds with massive \SF observed in the 
+Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a}.
+Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
+\label{fig:MR}}
+\end{figure*}
 
-\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot; in any case, here I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
+%\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
+%%M~ 30 in normal spirals \citep{McKee99a}
+%%M~ 100 in SBs \citep{Downes98a}
+%In the following, SFR of each MC is calculated by integrating over the recent \SF history of stars within each MC. 
+%More specifically, we sum up all the stellar masses with stellar age of $<$10\,Myr and  normalized 
+%the mass over this period of time.
+%In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
+%complexes identified.
+%We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx,
+%which is unsurprising given that our simulations include the effect of stellar feedback. That is,
+%the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from
+%massive stars.
 
@@
 
-\section{Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
+\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
 
-\AP{i guess that we can either choose to put it at the beginning of the results or at the end (before the CMF), to explain the origin of the clumps; in ancy case, the strategy should be to select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}
+\AP{select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}
 
+The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
+and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
 For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
@@
 \end{equation}
-where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
+where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
 The first term on the RHS describes rotation support, second term describes self-gravity, and
@@
 
+{\bf still yet to make the ``Q''-map}
+
 \section{Cumulative Mass Distribution}   \label{sec:cmf}
@@
 the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
-We find a shallower slope in the CMF of \flower (\Fig{cmf})
-compared to those observed in nearby galaxies (based on a sample of
-$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}).
+We fit a power-law to the cumulative mass function (CMF), expressed in the form of 
+\begin{equation}
+n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
+\end{equation}
+where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
 The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the
@@
 The uncertainties here are the formal fitting uncertainties.
+Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
+is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
+$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
 
@@
 structures are unknown to local group, and are likely the ... from which massive clusters or OB associations are to be formed.
-In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$.
+In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$. % also, seen in massive star-forming regions, such as 30 Doradus.
 
@@
 those observed in \z$\sim$2\,$-$\,4 galaxies with spatially resolved \obs.
+The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
+molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
+\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are 
+found throughout the disk. This difference likely stems from the different physical mechanisms giving rise 
+to the formation (and thus the nature) of these molecular structures. 
+For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud 
+collision after the large amount of gas from the progenitor galaxy merger 
+is being funneled toward the central region \citep{Tan00a, Wu18a}, 
+whereas in \flower, which is actively accreting gaseous materials 
+from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
+funneling into the center).
+This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
+in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
 
@@
 
-The minimum clump mass M$_{\rm min}$ is limited by numerical resolution of our simulation.
+The minimum clump mass $M_{\rm min}$ is limited by numerical resolution of our simulation.
 We do not have a resolution study (in hand) and so we cannot quantitatively evaluate this at the moment.
@@
 \bibliography{master_cleanup}
-\end{document}
+
+\appendix
+\section{Schmidt-Kennicutt Relation}
+As benchmarking, we check the SK relation of the MCs identified based on their SFR and gas surface densities.
+We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
+(see \Sec{sfh} for details) compared to those reported in \obs.
+
+\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot}
+\DL{by running test\_brute.py}
+
+\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
+\DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
+\caption{
+SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (xxx symbol) compared to those 
+observed in 0$\lesssim$\,\z$\lesssim$2 galaxies (xxx symbol). 
+The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} and references therein, and Sharon et al. in prep.
+\label{fig:sk}}
+\end{figure*}
 
@@
 %
+\end{document}

### 2018-09-07 plotsingleSS.py
plot M-R relation

@@ -43,6 +43,7 @@ def plotting_procedure(snapshot_num):
 #     plot_stuff("gas sd", "sfr sd", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("gas sd", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("size pc", "cloud mass", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
     plot_stuff_3dim("tff Myr", "size pc", "cloud mass", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
 
 

### 2018-09-07 WRITEUP/ms.tex
abstract

@@
 We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
-We find that the MC of \flower are highly supersonic, with large velocity dispersion ($\sigma\approx$\,200\,\kms) comparable to 
+We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) that are comparable to 
 those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
 The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
-corresponds to the arms of the main disk of \flower and breaks down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
-We find that the ...
-The MCs in the satellites..
-consistent with PVE.
-We find no temporal variations in the MC physical properties over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
+correspond to the arms of the main disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
+The more massive and bigger MCs in \flower likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
+which sets the scales for fragmentation.
+We compare the dynamics of MCs in \flower and those observed in the local Universe in the context of the Larson's relation.
+The MCs of \flower are systematically found to have higher $\sigma$ and $\Sigma$ regardless of the $n_{\rm cut}$ adopted.
+The higher velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the molecular substructures, likely 
+because \flower has experienced more episodes of recent \SF, and thus stronger SNe and stellar feedback.
+Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
+This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
+supported by turbulence and rotation on large scale.
+On the other hand, we find $\alpha_{\rm vir}$\ssim1 for MCs in the satellite galaxies. We interpret this as a result of the weaker stellar feedback as they have
+experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
+MCs in the satellites are therefore likely collapsing structures. This paints a picture, where at the EoR, \SF continues as gas is being accretion from the IGM.
+We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
 Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
-mass distribution, which steepens as we increase $n_{\rm cut}$. Higher resolution cosmological zoom-in simulations 
-will shed light into ... , as we .... from observations.
+mass distribution, which steepens as we increase $n_{\rm cut}$. 
+Higher resolution cosmological zoom-in simulations will ... shed light into ... , as we .... from observations with ALMA.
 \end{abstract}

### 2018-09-07 WRITEUP/ms.tex
finished long abstract

--- 2018-09-07 WRITEUP/ms.tex
@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of Molecular Gas Complexes in $z$\ssim6 Prototypical Galaxy
+\shorttitle{Dynamical Properties of Molecular Cloud Complexes in $z$\ssim6 Prototypical Galaxy
 }
@@
 \title{
-Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization
+Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization
 }
@@
 \begin{abstract}
-We study the dynamical properties of molecular clouds and their temporal evolution in a prototypical galaxy 
+We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
 at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
 which includes a chemical network to determine the formation of molecular
-hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
-kinetic and thermal energies. 
+hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
 We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
@@
 We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
-We find that the MC of \flower are highly supersonic, with large velocity dispersion ($\sigma\approx$\,200\,\kms) comparable to 
-those observed in gas-rich galaxies in the local universe as well as at the peak epoch of cosmic \SF. 
-The mass scale of the MCs is of the order $10^{6.5-8}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
-corresponds to the arms of the main disk of \flower and breaks down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
-We find that the ...
-The MCs in the satellites..
-consistent with PVE.
-We find no temporal variations in the MC physical properties over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
+We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
+those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
+The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
+correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
+The more massive and bigger MCs in \flower compared to the Milky Way 
+likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
+which set the scale for fragmentation.
+% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
+% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
+We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
+The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
+The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
+the molecular substructures, likely resulting from 
+the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
+Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
+This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
+supported by turbulence and rotation on large scale.
+We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
+experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
+MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
+as gas is being accreted from the IGM.
+We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
 Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
-mass distribution, which steepens as we increase $n_{\rm cut}$. Higher resolution cosmological zoom-in simulations 
-will shed light into ... , as we .... from observations.
+mass distribution, which steepens as we increase $n_{\rm cut}$. 
+High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
+light on \SF since the cosmic dark ages.
 \end{abstract}
-%\keywords{infrared: galaxies --
-%          galaxies: high-redshift --
-%          galaxies: ISM --
-%          galaxies: evolution --
-%          galaxies: starburst --
-%          radio lines: ISM}
+\keywords{methods: data analysis --
+          galaxies: high-redshift --
+          galaxies: ISM --
+          galaxies: evolution --
+          galaxies: formation --
+          galaxies: starburst --
+          stars: formation}
 
@@
 We show in \Fig{dist} the MC distributions in terms of their
-molecular gas masses, radii, gas mass fraction ($sf_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
+molecular gas masses, radii, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
 $M_*$)).
@@
 we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
-describe interactions between gravity and turbulence and is one of the ``fundamental''/first
-relations for studying star-forming molecular structure formation (linewidth-size,
+describe interactions between gravity and turbulence and is the first set of 
+relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
 density-size, and mass-size relations) and for comparing properties of molecular structures
 in different galactic environments.
-In particular, the Larson's relations attempt to understand the physics behind molecular
-structures via observables (e.g., $\sigma$, $R$, and $M_{\rm cl}$).
 % Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.

### 2018-09-07 WRITEUP/ms.tex
typesetting

@@
 % \documentclass[twocolumn]{aastex6}
-\documentclass[apj]{emulateapj} %iop
+% \documentclass[apj]{emulateapj}
+\documentclass[iop]{emulateapj} %iop
 \usepackage{amsmath}
@@
 We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
-at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
+at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
 which includes a chemical network to determine the formation of molecular

### 2018-09-07 WRITEUP/ms.tex

@@
 The more massive and bigger MCs in \flower compared to the Milky Way 
-likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
+likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
 which set the scale for fragmentation.
@@
 
-The growth of galaxies and their subsequent evolution are governed by the baryonic/baryon cycle ---
-galaxies accrete gas from the intergalactic medium to fuel \SF (and feed their supermassive blackholes)
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
+galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
 and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
-The general consensus is that the growth of \highz galaxies are triggered/supported by massive
-gas inflows from mergers and/or the cosmic web at early cosmic time, when the intergalactic
-medium and galaxies themselves are more gas-rich in their star-forming molecular
+The general consensus is that the growth of \highz galaxies are triggered and supported by massive
+gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
+are more gas-rich in their star-forming molecular
 gas contents compared to present-day galaxies.
@@
 % are continuously being replenished.
-These massive gas inflows in turn trigger gravitational instability, and thus, lead
-to the formation of clouds/structures that are typically more massive and denser than those
-observed in nearby galaxies, with cloud masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
-and sizes on sub-kpc scales (e.g. \citealt{Gabor13a, Hopkins14a, Inoue16a}).
-%In cosmological context, minor mergers and external gas accretion can
-%significantly impact on disc dynamics and clump formation
-%(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
-Some theoretical works argues that it is in fact the
-migration of such giant massive clumps that are responsible for contributing to the
+These massive gas inflows in turn trigger gravitational instability and lead
+to the formation of gas structures that are typically more massive and denser than those
+observed in nearby galaxies, with masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
+and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+Some theoretical works argue that the
+migration of such giant massive clumps are responsible for contributing to the
 buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.
@@
 Current consensus is that at higher redshifts, galaxies have higher 
-star formation rates (SFR) \citep{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
-smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to galaxies found in the local Universe, 
-and thus, they are expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
+star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and 
+smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
+The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks. 
 Since their metallicity and dust content are also expected to be lower as they are assembling, 
-this affects the shielding of UV photons, heating and cooling mechanisms in this early systems.
-Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
-%
-% talk about dynamical states of MCs of different galaxies?
-Even in the local universe, where the most detailed \obs can be done, we see variations in cloud properties in different galaxy populations (see e.g., Hughes10a, MNRAS, 406, 2065; Hughes+13b, ApJ, 779, 46), maybe also Meidt+13, apj, 779,45?.
-Thus, obvious to pose the question what are the dynamical states of the MCs of the first galaxies and how do they differ from nearby universe, and analogous to any of the nearby \galpop?
+this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn 
+affect the regulation of thermal and chemical structures of their ISM. 
+Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
+are therefore expected to differ from nearby galaxies.
+Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been 
+observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
+It is thus obvious and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
+how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
 %
@@
 the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
-To date, the ISM properties of \highz galaxies
-have only been studied observationally in a handful of (strongly-lensed)
-galaxies, using spatially resolved tracers such as
-dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
+To date, spatially resolved ISM properties of \highz galaxies
+have only been examine observationally in a handful of (strongly-lensed)
+galaxies, using tracers such as
+dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
 Leung et al. 2018, submitted).
-These studies find that the ISM of $z$\ssim2 galaxies are more
+These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
 molecular gas-rich, turbulent, and clumpy than nearby galaxies.
-On the other hand, the main source of reionization --- the first stars and first galaxies --- 
-are ......
-it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
-that dominates  \SF at the epoch of reionization which is responsible for producing the
-ionizing photons that reionized the universe.
+That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
+at the epoch of reionization  ---
+which is responsible for producing the
+ionizing photons that reionized the Universe.
 
@@
 normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
-we are still far from mapping their molecular ISM.
-In particular, their star-forming gas conditions, due to the stupid stingy ALMA TAC.
+we are still far from mapping their molecular ISM due to the cosmological dimming.
 As such, we have undertaken a study, exploiting
@@
 \ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
-the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) lyman-break
-galaxy (LBG).
+the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$) 
+galaxy.
 
@@
 Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
-Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
-At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
+Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG) hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
 It is therefore a prototypical galaxy at \z$\sim$6.
@@
 most extreme variations in the cloud dynamics) --- one of which \flower is
-actively accreting materials from its surrounding (top panel of \Fig{SFH})
+actively accreting materials from its surrounding 
 and another of which \flower is undergoing
-a starburst phase after a major merger (bottom panel of \Fig{SFH}).
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/daisyleung2.pdf}
-\caption{
-	Top right: Star formation history of \flower.
-	Projected stellar mass distribution of \flower during one of its accretion phases
+a starburst phase after a major merger (see \Fig{SFH}).
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\caption{
+	Star formation history of \flower (top right) and
+	projected stellar mass distribution of \flower during one of its accretion phases
 	at its early stage of evolution {\it (a)}; during one of its major starburst phases
@@
 The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree).
-It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles.
+It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
 In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).
@@
 We note that, owing to the nature of \obs, such structures are identified 
-in position-position-velocity (PPV) space in observational studies, whereas in simulations, one has the 
+in position-position-velocity (PPV) space, whereas in simulations, one has the 
 full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
@@
 
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower
-for a given snapshot which includes contributions from its surrounding 7\,kpc.
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
-found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see analysis presented by \citealt{Pallottini17b}).
+In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
+for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
+the half mass radius of \flower is $\sim$0.5\,kpc and the $r_{\rm 200}$ dark matter radius is $\sim$15\,kpc.}.
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
+where ``clumps/structures'' are 
+found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
 In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 

### 2018-09-08 WRITEUP/ms.tex
write some more

@@
 mass distribution, which steepens as we increase $n_{\rm cut}$. 
-High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
+High resolution imaging of the first galaxies with ALMA and the ngVLA 
+will be useful to test our findings and the validity of our simulation to shed
 light on \SF since the cosmic dark ages.
@@
  \centering
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png}
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
   \\[-5.5em]
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png}
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
+  \\[-5.5em]
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
 \caption{
@@
 	Color shows the projected H$_2$ surface density.
-{\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field.
-in any case, we should compress the information, by having a less figures showing multplie cuts (e.g.
-3 of them by using thinner lines should suffice in conveying the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
+{\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field; additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
+hmm..
+Not worth my time to fix this for the report.}
 % yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
 \label{fig:MC}}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.88}.png}
-    \\[-5.5em]
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_1.47}.png}
-\caption{
-Continued.}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_2.45}.png}
-  \\[-5.5em]
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_4.08}.png}
-\caption{
-Continued.}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_6.81}.png}
-  \\[-5.5em]
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_11.36}.png}
-\caption{
-Continued.}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_18.96}.png}
-  \\[-5.5em]
-  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_31.62}.png}
-\caption{
-Continued.}
+% \addtocounter{figure}{-1}
 \end{figure*}
@@
 for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
-the half mass radius of \flower is $\sim$0.5\,kpc and the $r_{\rm 200}$ dark matter radius is $\sim$15\,kpc.}.
+the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter ``virial radius'' at which the mean enclosed density is 200 times 
+the critical density of the Universe % presumably defined at the redshift of \flower here?
+is $r_{\rm 200}$\ssim15\,kpc.}.
 We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
@@
 gas surface density ($\Sigma_{\rm gas}$)
-to describe/characterize their dynamics.
+to examine their dynamics.
 
@@
 
+\subsubsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
 % Relating Larson's law to stability and pressure (perhaps move this to other section?).
 A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
-a medium of pressure $P$ is described using the virial theorem
+a medium of pressure $P$ is described using the virial theorem:
 \begin{equation}
@@
 \end{equation}
-where the first term on the right hand side (RHS) is the pressure from velocity dispersion, second
+where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
 term is the gravity term, and the third term is the external pressure term.
 For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
-the LHS vanishes and the equation becomes:
+the LHS and the last term on the RHS vanish. The equation becomes:
 \begin{equation}
@@
 \end{equation}
-where $\Gamma$ is set to 3/5 for a uniform sphere, and we can define
+where $\Gamma$ is set to 3/5 for a uniform sphere.
+We can define
 \begin{equation}
@@
 \end{equation}
-which is related to the scaling in one of the Larson's relations (linewidth-size),
-and can re-written in the form of:
+which is related to the scaling in one of the Larson's relations (linewidth-size)
+and can be re-written in the form of:
 \begin{equation}
@@
 \end{equation}
-For a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
+Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
 $\sigma^2/R\propto\Sigma$, whereas
@@
 
-\subsubsection{Single Snapshots: Larson's Relations and Virial Parameter}  \label{sec:singless}
+\subsubsection{Single Snapshots}  \label{sec:singless}
 
@@
 is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
-The virial parameter of the MC identified in (the densest region of) the main disk of \flower
-indicate that the MC itself is gravitationally unbound.
+Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
+would indicate that the MC itself is gravitationally unbound, and is supported/confined 
+by turbulence and rotation on large scales.
+% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.
 
@@
 the conventional wisdom that collapsing structures result from local gravitational
-instability within globally stable structures, which are supported by
-turbulence and rotation on large scales.
+instability within globally non-collapsing structures,
+which are supported by turbulence and rotation.
+These
 
@@
 the MCs of the satellite galaxies of
-\flower are close to being in virial equilibrium
-and are not supported against collapse by external pressure. % are bound
+\flower are close to being in virial equilibrium and are unlikely supported against collapse by external pressure.
 
@@
 accreting phase (top) and
-starburst phase(bottom) and
+starburst phase (bottom) compared to
 those observed in nearby and the \z$\sim$2 star-forming galaxy.
@@
 Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
+The V-shaped dashed lines show locii along which the given external pressures
+are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
 \label{fig:alpha16}}
@@
 in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
-Pipe Nebula) and those with massive \SF in the Milky Way, \citet{Kauffmann10c} find a 
+Pipe Nebula) with those with massive \SF in the Milky Way, \citet{Kauffmann10c} report a 
 mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
@@
 at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
-with visual extinction of $A_V$\eq4\,mag. This may suggest that xyzxyz.
+with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
 We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
@@
 \section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
-
-\AP{select a snapshot, put it face on and calculate the toomre parameter map similarly to what done in \citet{Inoue16a}}
-
 The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
@@
 yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
-which is the ``upper limit'' to which MCs can form in a shearing disk.
+which sets the ``upper limit'' to which MCs can form in a shearing disk.
 
@@
 collision after the large amount of gas from the progenitor galaxy merger 
-is being funneled toward the central region \citep{Tan00a, Wu18a}, 
+is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
 whereas in \flower, which is actively accreting gaseous materials 

### 2018-09-08 plot_modules/test_fig9.py
to reproduce Fig 9 of Pallo+17b

@@ -1,0 +1,67 @@
+'''
+
+Reproduce Pallottini17b Fig. 9
+
+Last mod: 7 Sept 2018
+
+'''
+
+import numpy as np
+import matplotlib.pyplot as plt
+from plot_modules.plot_cloud_prop import setup_plot
+
+setup_plot()
+
+path = '../literature/data/'
+
+
+plt.close('all')
+plt.figure()
+# Althaea
+tff = 1.0
+plt.plot(np.log10(222.02/tff), np.log10(0.83), marker='*', markersize=15, color='red', label=r'Alth{\ae}a', linestyle='None', zorder=30)
+
+
+file_list = ['sk_kennicutt1998.dat', 'sk_bouche07a.dat',  'sk_daddi10b.dat',
+             'sk_daddi10a.dat', 'sk_tacconi10a.dat', 'sk_genzel10a.dat']
+label_list = ['Kennicutt+98', r"Bouch\'e+07",
+              r'Daddi+10', '', 'Tacconi+10', 'Genzel+10']
+list_2 = ['sk_Heiderman10.dat', 'sk_Lada10.dat']
+label_list_2 = ['Heiderman+10', 'Lada+10']
+
+colors = ('k', 'g', 'darkred', 'c', 'blue', 'orange')
+markers = ('.', 's', 'D', 'v', 'h', '8', '1')
+morecolors = ('darkolivegreen', 'brown')
+moremarkers = ('x', '+')
+
+for i in xrange(len(file_list)):
+
+    f_in = path + file_list[i]
+    ss = np.loadtxt(f_in, usecols=(2, 3, 4, 5, 6, 7, 8, 9))
+    x = ss[:, 6]
+    y = ss[:, 3]
+
+    plt.plot(x, y, label=label_list[i], marker=markers[i], linestyle='None', color=colors[i], markersize=5)
+
+
+for i in xrange(len(list_2)):
+    f_in = path + list_2[i]
+    ss = np.loadtxt(f_in, usecols=(5, 8))
+
+    x = np.log10(ss[:, 1])
+    y = np.log10(ss[:, 0])
+    plt.plot(x, y, marker=moremarkers[i], linestyle='None', label=label_list_2[i], color=morecolors[i], markersize=8)
+
+
+plt.legend(loc="best")
+
+from matplotlib.ticker import MultipleLocator
[…]

### 2018-09-08 WRITEUP/ms.tex
write some more

@@
 \caption{
-Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
-Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
+Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
+Literature data are compiled from \citealt{Kauffmann17b} and references therein.
+Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs (star symbols) 
+compared to those observed in the Milky Way (black dot markers).
 The V-shaped dashed lines show locii along which the given external pressures
 are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
+In both panels, the star symbols are color-coded by the $n_{\rm cut}$ adopted to identify the corresponding MCs.
 \label{fig:alpha16}}
@@
 \caption{
-Top: Virial parameter and cloud mass of \flower of a given snapshot (starburst phase).
-Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
+Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
 \label{fig:alpha27}}
@@
 \caption{
-Top: Virial parameter and cloud mass of MCs in \flower identified across all snapshots.
-Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs.
+Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
+Star symbols are color-coded by increasing SFR.
 \label{fig:alpha16-28}}
@@
 
-The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible),
-between $M_{\rm cl}\approx$10$^{7-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
-
+The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band 
+(i.e., rest-frame visible) which is between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
+Observational studies.. the ... distribution as the cumulative mass function (CMF).
 Noisy due to resolution effect, since we only have one galaxy here. However,
@@
 the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
-We fit a power-law to the cumulative mass function (CMF), expressed in the form of 
+We fit a power-law to the CMF, expressed in the form of 
 \begin{equation}
@@
 \AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
+\DL{maybe just merge in the previous sections when we present the results?}
 
@@
 require .... on-source time even with ALMA.
-
-Connection to observations
+ngVLA
 
@@
 in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
-
-Looking at correlations between physical parameters such as xx, yy, zz and the CMF
-can provide valuable information for developing models of \SF at EoR and
-galaxy evolution.
 
@@
 \section{Summary and Conclusions}      \label{sec:conclusion}
+Looking at correlations between physical parameters such as xx, yy, zz and the CMF
+can provide valuable information for developing models of \SF at EoR and
+galaxy evolution.
 
@@
 to the kd-tree idea. We decompose the molecular structures into non-overlapping tiles
-% (stored in a kd-tree)
 by identifying a set of different density contours at different snapshots.
@@
 (if only the ALMA TAC will give us to the time to do so)...
+ngVLA.
 
@@
 \section{Schmidt-Kennicutt Relation}
-As benchmarking, we check the SK relation of the MCs identified based on their SFR and gas surface densities.
+As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
 We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
@@
 
-\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
+\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17a}}
 \DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}
@@
 \caption{
-SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (xxx symbol) compared to those 
-observed in 0$\lesssim$\,\z$\lesssim$2 galaxies (xxx symbol). 
-The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} and references therein, and Sharon et al. in prep.
+SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
+observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
+Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
+\citealt{Pallottini17b}.
+%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
+%and references therein, and Sharon et al. in prep.
 \label{fig:sk}}

### 2018-09-08 WRITEUP/ms.tex
wrote some more in summary and conclusions

@@
 \input{preamble}
-\slugcomment{To be Submitted}
+\slugcomment{Paper draft for the project developed at the Kavli Summer Program in Astrophysics 2018. 
+To be Submitted.}
 
@@
 to identify molecular complexes (MC) and their sub-structures.
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
+compare them with those observed in the Milky Way disk, the Galactic center,
+and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
 We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
-those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
+those observed in starburst galaxies.
 The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
@@
 which set the scale for fragmentation.
-% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
-% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
-We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
+We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
 The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
@@
 High resolution imaging of the first galaxies with ALMA and the ngVLA 
-will be useful to test our findings and the validity of our simulation to shed
+has the potential to provide useful observational data to test our findings and the validity of our simulation to shed
 light on \SF since the cosmic dark ages.
@@
 \section{Summary and Conclusions}      \label{sec:conclusion}
-Looking at correlations between physical parameters such as xx, yy, zz and the CMF
-can provide valuable information for developing models of \SF at EoR and
-galaxy evolution.
 
-We study the dynamical properties of molecular complexes in a \z$\sim$6 lyman-break galaxy,
-at the end of the epoch of reionization using state-of-the-art cosmological zoom-in simulation
-(\ncode{Serra}). We identify molecular cloud complexes in the main galaxy of the
-simulated 20\,Mpc h\pmOne box (aka \flower; \citealt{Pallottini17a}) using a method analogues
-to the kd-tree idea. We decompose the molecular structures into non-overlapping tiles
+We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy 
+at the EoR using state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
+which includes a chemical network to determine the formation of molecular
+hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
+We use a clump finder algorithm and a set of H$_2$ volumetric densities
+to identify MCs and their sub-structures in the main galaxy --- \flower\ --- of the
+simulated 20\,Mpc h\pmOne box and in its satellites.
+We decompose the molecular structures into non-overlapping tiles
 by identifying a set of different density contours at different snapshots.
@@
 since the line luminosity scales with the molecular gas density.
-Our simulations include the effect of feedback from .... .and ....., which are the main source
-of non-thermal pressure ejected into the ISM.
-We examine the properties of the complexes' at different evolutionary stages and compare
-them with nearby and \highz observations. In particular,
-the scaling relations between velocity dispersion, complex size, gas mass,
-and SFRs.
+% Our choice of density cut is analogues to the .... in \obs. It should be ... that both suffer from problem .... For instance, in \obs.. limited S/N.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
+compare them with those observed in the Milky Way disk, the Galactic center,
+and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
+We also examine their properties at the different evolutionary stages of \flower and compare
+them with observations.
 
-We find that our results are robust to the various density cuts of choice.
-This stems from the
-fact that ..... Our choice of density cut is analogues to the inherent problem of limited S/N
-in observations.
-However, our results are dependent on the numerical resolution of the simulation.
+We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
+those observed in starburst galaxies.
+The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
+correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
+The more massive and bigger MCs in \flower compared to the Milky Way 
+likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
+which set the scale for fragmentation.
+This is consistent with what has been found previously in higher resolution isolated simulation.
+Here, our cosmological zoom-in simulation allows us to examine 
+the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM.
 
-Utilizing high-resolution realistic hydrodynamics simulation with
-detailed physics (e.g., feedback and chemical evolution), we
-..... , which will become possible to confirm and ... by tracing
-the molecular gas emission with future .... such as the Next Generation Very Large Array (ngVLA).
-High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics, provides a way to examine and postulate the morphology and dynamics of
-the multi-phase ISM structures of the first galaxies and their satellite galaxies.
+We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
+The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
+Our results are thus robust/insensitive to the various density cuts of choice.
+%However, our results are dependent on the numerical resolution of the simulation.
+The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
+the molecular substructures, likely resulting from 
+the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
+Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
+This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
+supported by turbulence and rotation on large scale.
+We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
+experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
+MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
+as gas is being accreted from the IGM.
+We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
+Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
+mass distribution, which steepens as we increase $n_{\rm cut}$.
 
@@
 (if only the ALMA TAC will give us to the time to do so)...
-ngVLA.
+
+High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
+statistics and is subject to the input model/sub-grid models adopted, 
+provides a way to examine and postulate the morphology and dynamics of
+the multi-phase ISM structures of the first galaxies and their satellite galaxies.
+High resolution imaging of the first galaxies with ALMA and the ngVLA 
+has the potential to provide useful observational data to test our findings and the validity of our simulation to shed
+light on \SF since the cosmic dark ages.
+
+In this work, we utilize high-resolution realistic hydrodynamics simulation with
+detailed physics (e.g., feedback and chemical evolution), we
+..... , which will become possible to confirm and ... by tracing
+the molecular gas emission with future .... such as the Next Generation Very Large Array (ngVLA), 
+which ....
+% model can guide and interpret observations and provide new testable predictions. 
+% refine models using these new observations and test where models fail.
+% The opposite is true, where can use models to make predictions for the first galaxies, 
+% where future obs w/ ALMA and ngVLA will help discriminate and better understand xxx.
 

### 2018-09-08 WRITEUP/ms.tex
minor edits on conclusion sec

@@
 The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
-The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
+The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
 the molecular substructures, likely resulting from 
@@
 High resolution imaging of the first galaxies with ALMA and the ngVLA 
-has the potential to provide useful observational data to test our findings and the validity of our simulation to shed
+will provide useful observational data to test our findings and the validity of our simulation to shed
 light on \SF since the cosmic dark ages.
@@
 % different critical densities.
-since the line luminosity scales with the molecular gas density.
+since the line luminosity scales with the molecular gas density (modulo optical depth effects).
 % Our choice of density cut is analogues to the .... in \obs. It should be ... that both suffer from problem .... For instance, in \obs.. limited S/N.
@@
 We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
-those observed in starburst galaxies.
+those observed in $z$\ssim2 starburst galaxies.
 The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
@@
 which set the scale for fragmentation.
-This is consistent with what has been found previously in higher resolution isolated simulation.
-Here, our cosmological zoom-in simulation allows us to examine 
+This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
+That said, our cosmological zoom-in simulation here allows us to examine 
 the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM.
@@
 %However, our results are dependent on the numerical resolution of the simulation.
-The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
+The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
 the molecular substructures, likely resulting from 
@@
 the role of \highz galaxy populations
-(e.g., LBGs, BzKs, and DSFGs) in
-galaxy evolution and the ISM physics behind their intense star formation in the early universe
+in the context of galaxy evolution and the ISM physics behind their intense star formation in the early universe
 (if only the ALMA TAC will give us to the time to do so)...
@@
 statistics and is subject to the input model/sub-grid models adopted, 
-provides a way to examine and postulate the morphology and dynamics of
+provide an avenue to examine and postulate/make testable predictions on the morphology and dynamics of
 the multi-phase ISM structures of the first galaxies and their satellite galaxies.
-High resolution imaging of the first galaxies with ALMA and the ngVLA 
-has the potential to provide useful observational data to test our findings and the validity of our simulation to shed
+High resolution imaging of the molecular gas content in the first galaxies with ALMA and the Next Generation Very Large Array (ngVLA), on the other hand,
+have the potential to provide useful observational data to test our findings and the validity of our simulation to shed
 light on \SF since the cosmic dark ages.
 
-In this work, we utilize high-resolution realistic hydrodynamics simulation with
-detailed physics (e.g., feedback and chemical evolution), we
-..... , which will become possible to confirm and ... by tracing
-the molecular gas emission with future .... such as the Next Generation Very Large Array (ngVLA), 
-which ....
 % model can guide and interpret observations and provide new testable predictions. 

### 2018-09-09 WRITEUP/ms.tex
polish a bit up to sec 3.3

@@
 \begin{abstract}
-We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
-at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
-which includes a chemical network to determine the formation of molecular
-hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
+We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
+at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
 We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
-to identify molecular complexes (MC) and their sub-structures.
+to identify MCs and their sub-structures.
 We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
 compare them with those observed in the Milky Way disk, the Galactic center,
-and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
-We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
+and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
+The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
 those observed in starburst galaxies.
 The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
-correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
+correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
 The more massive and bigger MCs in \flower compared to the Milky Way 
@@
 which set the scale for fragmentation.
-We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
 The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
@@
 the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
-Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
+Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
 This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
@@
 mass distribution, which steepens as we increase $n_{\rm cut}$. 
-High resolution imaging of the first galaxies with ALMA and the ngVLA 
+High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
+Next Generation Very Large Array (ngVLA)
 will provide useful observational data to test our findings and the validity of our simulation to shed
@@
 observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-It is thus obvious and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
+It is thus intuitive and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and 
 how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
@@
 That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 --- 
-at the epoch of reionization  ---
+the epoch of reionization  ---
 which is responsible for producing the
@@
 
+\begin{figure*}[!hHtbp]
+\centering
+\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\caption{
+	Star formation history of \flower (top right) and
+	projected stellar mass distribution of \flower during one of its accretion phases
+	at its early stage of evolution {\it (a)}; during one of its major starburst phases
+	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
+% f_gas history?
+\label{fig:SFH}}
+\end{figure*}
+
 We show the \SF history of \flower in \Fig{SFH}, where
@@
 a starburst phase after a major merger (see \Fig{SFH}).
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
-\caption{
-	Star formation history of \flower (top right) and
-	projected stellar mass distribution of \flower during one of its accretion phases
-	at its early stage of evolution {\it (a)}; during one of its major starburst phases
-	after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
-% f_gas history?
-\label{fig:SFH}}
-\end{figure*}
 
@@
 for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
-the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter ``virial radius'' at which the mean enclosed density is 200 times 
+the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
 the critical density of the Universe % presumably defined at the redshift of \flower here?
@@
 where ``clumps/structures'' are 
-found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see calculation presented by \citealt{Pallottini17b}).
+found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
 In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
@@
 
-\section{Results}     \label{sec:results}
-
-\subsection{Cloud Scaling Relations}
+\section{Results: Cloud Scaling Relations}     \label{sec:results}
 
@@
 the virial parameter ($\alpha_{\rm vir}$),
-the ``cloud'' mass ($M_{\rm cl}$),
-the ``cloud'' size ($R$),
-the Mach number ($\mathcal{M}$),
-the velocity dispersion ($\sigma$), and the
+mass ($M_{\rm cl}$),
+size ($R$),
+Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and 
 gas surface density ($\Sigma_{\rm gas}$)
@@
 of all identified molecular complexes are generally much smaller compared to the their
-turbulent velocities.
-\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
-We find comparable velocity dispersion derived by taking the root mean square versus
-that derived using thermal and non-thermal pressure, indicating that
-rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
-We quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
+turbulent velocities\footnote{We find comparable velocity dispersion between that derived from 
+taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
+rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
+We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
 In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion ($\sigma$).
+as the velocity dispersion ($\sigma$).}.
 
 We show in \Fig{dist} the MC distributions in terms of their
-molecular gas masses, radii, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
-$M_*$)).
+molecular gas masses, radii, and gas mass fractions, which we define as 
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
+\end{equation}
+where $M_*$ is the stellar mass.
 We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
@@
 Distributions of masses, sizes, and gas mass fractions of MCs identified using 
-the lowest $n_{\rm cut}$ (left panels) and the highest $n_{\rm ncut}$ (right panels).
-Note the y-axis scales are different between the left and the right panels, as less MCs are identified 
+the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
+Note the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
 at higher $n_{\rm cut}$.
@@
 show higher velocity dispersions compared
-to the disk/mid-plane of the Milky Way which
-are more consistent with those observed in the inner regions of
+to the disk/mid-plane of the Milky Way which are, on the other hand,
+more consistent with those observed in the inner regions of
 Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$,
@@
 
-\subsubsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
+\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
 % Relating Larson's law to stability and pressure (perhaps move this to other section?).
@@
 \alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
+\label{eqn:virial}
 \end{equation}
@@
 \end{equation}
-which is related to the scaling in one of the Larson's relations (linewidth-size)
-and can be re-written in the form of:
+which is related to one of the Larson's relations (linewidth-size relation), 
+which can be recast into the form of:
 \begin{equation}
@@
 In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
-is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
-varies depending on $P_{\rm ext}$; cf. expectation for SVE
+is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
+varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
 $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
 
-\subsubsection{Single Snapshots}  \label{sec:singless}
+\subsection{Single Snapshots}  \label{sec:singless}
 
@@
 in these MCs can also be understood as they have experienced more recent episodes
-of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60).
+of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
 In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
@@
 a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
-is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
+is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
 Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
-would indicate that the MC itself is gravitationally unbound, and is supported/confined 
+would indicate that the MC itself is gravitationally unbound and is supported/confined 
 by turbulence and rotation on large scales.
@@
 similar to those observed
-in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
+in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
 terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
 e.g., \citealt{Swinbank11a}),
-with cloud sizes on the order of $R\simeq$100\,pc and velocity
+with sizes of the order of $R\simeq$100\,pc and velocity
 dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
@@
 which are supported by turbulence and rotation.
-These
 
@@
 parameter space as the accreting phase. 
+{\bf so...}
 
@@
 
-\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
+\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
 % single Snapshot
@@
 
-Yet.... at the epoch of reionization.... For instance, to resolve the
-\aco line emission in a $L^*$ prototypical galaxy at \z$\sim$6 on xxx\,pc
-require .... on-source time even with ALMA.
-ngVLA
-
 The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller
@@
 
-\AP{I would move it to the previous section; since it is not easy to condense the toomre analysis for different snapshots in a single plot, I would use the virial parameter analysis to discuss the gravitational instability point on more then on evolutionary state of the galaxy}
+\AP{I would move it to the previous section; I would use the virial parameter analysis to discuss the gravitational instability point more than on evolutionary state of the galaxy}
 
 We quantify how stable a molecular structure is using the virial parameter, which
-describes the balance between pressure support and gravity.
+is defined using \Eqn{virial} and describes the balance between kinetic and gravitational potential energies.
+An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
+and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
+the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eqn{virial} 
+in \Sec{PVE})}.
 
-The high $\alpha_{\rm vir}$ suggest that the majority of the MCs identified are not collapsing.
+The high $\alpha_{\rm vir}$ found in the majority of MCs of \flower suggest that they are not collapsing.
 The largest structures are presumably supported by galactic rotation and turbulence from the feedback of

### 2018-09-09 WRITEUP/ms.tex
update sec 3.2

@@
 is $r_{\rm 200}$\ssim15\,kpc.}.
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range of density 
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density 
 where ``clumps/structures'' are 
@@
 \AP{however a plot showing the clump stats has not been show yet at this point}
-Their high velocity dispersions and surface densities are expected since
+Their velocity dispersions are comparable to those observed in the inner Milky way and
+nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
+along the locus of $\sigma\propto R^{0.56}$.
+Such high velocity dispersions and surface densities are expected since
 they are located in the nuclear regions of the
@@
 is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
-Based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
-would indicate that the MC itself is gravitationally unbound and is supported/confined 
-by turbulence and rotation on large scales.
-% clouds form in galactic disk typically have virial between 0.2-10 \citep{Dobbs08a, Tasker09a}.
 
@@
 As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
-\AP{the following will be manifest only after the presentation of some results, e.g. \Fig{alpha16}}
 This population of sub-MCs has dynamics largely
@@
 with sizes of the order of $R\simeq$100\,pc and velocity
-dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$
-are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
+dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
+As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
+are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
+%We note that previous studies by 
+%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
+%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
+This is consistent with
 the conventional wisdom that collapsing structures result from local gravitational
@@
 which are supported by turbulence and rotation.
-
-We also identify MCs in the satellite galaxies of \flower. These MCs
-tend to have lower velocity dispersions compared to those of \flower which are more comparable
-to those observed in the inner Milky way and
-nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
-along the locus of $\sigma\propto R^{0.56}$.
-These MCs in the satellite galaxies also have
+In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
+would indicate that the MC itself is gravitationally unbound and is supported/confined 
+by turbulence and rotation on large scales.
+On the other hand, the MCs in the satellite galaxies are found to have
 lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
@@
 stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
-\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
+\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
+Given the low $\alpha_{\rm vir}$ parameter
+and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
 these structures are likely collapsing structures.
-Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter,
-the MCs of the satellite galaxies of
-\flower are close to being in virial equilibrium and are unlikely supported against collapse by external pressure.
 
@@
 which we extrapolate to match the mass and size scales of the MCs of \flower.
-By comparing the masses and sizes found in clouds without massive \SF ($<$10\,\Msun) 
-in the solar neighborhood ($\lesssim 500$\,pc; Taurus, Perseus, Ophiuchus, and the 
-Pipe Nebula) with those with massive \SF in the Milky Way, \citet{Kauffmann10c} report a 
+By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
+in the Milky Way, \citet{Kauffmann10c} report a 
 mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
@@
 In addition, for the densest MC in the main disk of \flower, we find that while
-its cloud size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
+its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
 its velocity dispersion remain
-approximately $\sigma\simeq$200\,\kms (\Fig{larsons_single}).
+approximately $\sigma\simeq$200\,\kms (see \Fig{larsons_single}).
 This lack of variation is reassuring, in the sense that at least on the scales studied here,
@@
 
-The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band 
-(i.e., rest-frame visible) which is between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
-Observational studies.. the ... distribution as the cumulative mass function (CMF).
-Noisy due to resolution effect, since we only have one galaxy here. However,
-we could improve the ``signal-to-noise'' ratio by including clouds identified from different
-snapshots\footnote{This approach is valid unless in some snapshots,
+The range of masses of the MCs identified are comparable to those observed in \z$\sim$2 galaxies in $i$-band 
+(i.e., rest-frame visible), which is between $M_{\rm cl}\approx$10$^{6.5-9xx}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
+Observational studies often report the mass distribution in the form of a cumulative function (CMF).
+While the CMF of the MCs is quite noisy due to resolution effect and since we only have one galaxy here 
+in the cosmological zoom-in simulation, we could improve the ``signal-to-noise ratio'' by including 
+MCs identified from the different snapshots\footnote{This approach is valid unless in some snapshots,
 the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
-We fit a power-law to the CMF, expressed in the form of 
+We show the resulting CMF in \Fig{cmf}.
+Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
 \begin{equation}
@@
 where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
-The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the
-highest $n_{\rm cut}$ adopted in this study.
+The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 
+for MCs identified using the lowest and the highest $n_{\rm cut}$ adopted in this study.
 The uncertainties here are the formal fitting uncertainties.
@@
 $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
+{\bf This means ....}
 

### 2018-09-09 WRITEUP/ms.tex
type-setting author affiliation stuff

@@
 % \documentclass[apj]{emulateapj}
-\documentclass[iop]{emulateapj} %iop
+\documentclass[iop]{emulateapj} 
 \usepackage{amsmath}
@@
 
-\altaffiltext{1}{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA}
-\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}
+\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
+\email{tleung@astro.cornell.edu}
+\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
 \altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
@@
 \altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
-\email{tleung@astro.cornell.edu}
 
@@
 those observed in nearby and the \z$\sim$2 star-forming galaxy.
+Red lines show the relation obtained from 
+Literature data are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
 \label{fig:larsons_single}}
@@
 is that our computational boxes are not closed, allowing us to examine how
-the molecular complexes' properties vary under the influence of gas inflow/outflow.
+the molecular complexes' properties vary under the influence of gas inflow/outflow 
+(see e.g., \citealt{Klessen10a, Goldaum11a}). % turbulence when disk still accreting gas
 
@@
 That said, our cosmological zoom-in simulation here allows us to examine 
-the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM.
+the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldaum11a}).
 

### 2018-09-09 WRITEUP/ms.tex
polish fig cap and sec 5

@@
 to the formation of gas structures that are typically more massive and denser than those
-observed in nearby galaxies, with masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
+observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
 and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
@@
 \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
-Given the low $\alpha_{\rm vir}$ parameter
+Given the low virial parameter
 and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
@@
 those observed in nearby and the \z$\sim$2 star-forming galaxy.
-Red lines show the relation obtained from 
-Literature data are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
+% Red lines show the relation obtained from \citet{}.
+Literature data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
 \label{fig:larsons_single}}
@@
 Literature data are compiled from \citealt{Kauffmann17b} and references therein.
-Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs (star symbols) 
+Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
 compared to those observed in the Milky Way (black dot markers).
-The V-shaped dashed lines show locii along which the given external pressures
-are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
-In both panels, the star symbols are color-coded by the $n_{\rm cut}$ adopted to identify the corresponding MCs.
+The V-shaped dashed lines show the locii along which the given external pressures
+are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
+In both panels, the star symbols are color-coded by $n_{\rm cut}$.
+Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
+and the locus of $\log{P/\textrm{K cm}^{-3} = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
 \label{fig:alpha16}}
@@
 We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
-compared to the empirical relation obtained based on 
+compared to the 
+observational data of molecular clouds in the Milky Way associated with massive \SF 
+\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
 Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
@@
 That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
-at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
-with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
+at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along the locus 
+with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
+On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
+{\bf This may suggest ....}
 We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
@@
 \caption{
-Size-mass relation of MCs in \flower compared to data and empirical established based on Milky Way \obs.
-Star symbols show MCs identified in the accreting phase of \flower in our simulation, color-coded by increasing $n_{\rm cut}$.
-Other symbols show the masses and sizes of molecular clouds with massive \SF observed in the 
-Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a}.
+Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
+compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
+(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
+established based on \obs of the Milky Way.
+Star symbols are color-coded by increasing $n_{\rm cut}$.
+Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
 Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
@@
 \end{figure*}
-
-%\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
-%%M~ 30 in normal spirals \citep{McKee99a}
-%%M~ 100 in SBs \citep{Downes98a}
-%In the following, SFR of each MC is calculated by integrating over the recent \SF history of stars within each MC. 
-%More specifically, we sum up all the stellar masses with stellar age of $<$10\,Myr and  normalized 
-%the mass over this period of time.
-%In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
-%complexes identified.
-%We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx,
-%which is unsurprising given that our simulations include the effect of stellar feedback. That is,
-%the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from
-%massive stars.
 
@@
 Our results is therefore robust, haha.
-
-%\begin{figure*}[tbph]
-% \centering
-%\includegraphics[width=\textwidth]{\figpath/.pdf}
-%\caption{\label{fig:}}
-%\end{figure*}
 
@@
 
-The range of masses of the MCs identified are comparable to those observed in \z$\sim$2 galaxies in $i$-band 
-(i.e., rest-frame visible), which is between $M_{\rm cl}\approx$10$^{6.5-9xx}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
-Observational studies often report the mass distribution in the form of a cumulative function (CMF).
-While the CMF of the MCs is quite noisy due to resolution effect and since we only have one galaxy here 
-in the cosmological zoom-in simulation, we could improve the ``signal-to-noise ratio'' by including 
-MCs identified from the different snapshots\footnote{This approach is valid unless in some snapshots,
-the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
+The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
+consistent with those observed in \z$\sim$2 galaxies in
+rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+Observational studies in the nearby Universe, where 
+spatially resolution are better at revealing molecular (sub-)structures,
+often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
+While the CMF of the MCs for a given snapshot of our simulation is 
+quite noisy, since we have only one (main) galaxy, 
+we could improve the ``signal-to-noise ratio'' by including 
+MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
+the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
 We show the resulting CMF in \Fig{cmf}.
+
 Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
@@
 where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
-The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 
-for MCs identified using the lowest and the highest $n_{\rm cut}$ adopted in this study.
-The uncertainties here are the formal fitting uncertainties.
+The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 by adopting the lowest and the highest $n_{\rm cut}$ studied here.
+The uncertainties are the formal fitting uncertainties.
 Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
@@
 $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
-{\bf This means ....}
+This difference in slopes suggest that mo, albeit speculative due to resolution effects.
+In particular, it is possible that we may identify more substructures/smaller and less massive MCs if our simulation 
+was of higher resolution (but one must acknowledge that ..... is expeneisve to do zoom-in. This is what we have at best at the 
+moment with simulation power).
+That said, simularly massive moleuclar clouds have been reported in simulations of higher resolution (i.e., not zoom-in; \citealt{}).
+It is therefore conceivable that our results are not that far off.
 

### 2018-09-10 WRITEUP/ms.tex
polished up to sec 6

@@
 %\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
-Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level.
+Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level.
 Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
@@
 
-\begin{figure*}[!hHtbp]
+\begin{figure*}[!htbp]
 \centering
@@
 Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
-needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
+needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
+\Fig{alpha27}).
 In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
@@
 of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
-In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
-to the top panel of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
+In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding
+to the top panels of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
 a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
@@
 e.g., \citealt{Swinbank11a}),
-with sizes of the order of $R\simeq$100\,pc and velocity
-dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
-As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
+with sizes of the order of $R\simeq$\,100\,pc and velocity
+dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
+As shown in the top panel of \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
 are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
@@
 %clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
-This is consistent with
+
+% PVE
+We also compare the MCs identified in our simulations to 
+those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
+\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
+MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
+
+The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
 the conventional wisdom that collapsing structures result from local gravitational
@@
 which are supported by turbulence and rotation. 
-In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
-would indicate that the MC itself is gravitationally unbound and is supported/confined 
-by turbulence and rotation on large scales.
-On the other hand, the MCs in the satellite galaxies are found to have
+In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
+the MC itself is gravitationally unbound and is supported/confined 
+by turbulence and rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
+% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
+
+The MCs in the satellite galaxies are found to have
 lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
-with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
+with $\alpha_{\rm vir}\simeq$1.
 Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
@@
 \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
-Given the low virial parameter
-and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
+In addition, the MCs in the satellite galaxies follow the locus of 
+$\log{(P/\textrm{K cm}^{-3})}$\eq6 (see bottom panel of \Fig{alpha16}). 
+Given the low virial parameter and the $\sigma^2/R - \Sigma$ relation found for these MCs in the satellite galaxies, 
 these structures are likely collapsing structures.
+This paints a picture, in which \SF continues as gas from the satellite galaxies are being accreted onto the main galaxies during the EoR.
 
@@
 Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
-and the locus of $\log{P/\textrm{K cm}^{-3} = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
+and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
 \label{fig:alpha16}}
@@
 
+Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
+panel of \Fig{larsons_single} and \Fig{alpha27}).
+
 \begin{figure*}[htbp]
@@
 its velocity dispersion remain
-approximately $\sigma\simeq$200\,\kms (see \Fig{larsons_single}).
+approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
 This lack of variation is reassuring, in the sense that at least on the scales studied here,
@@
 $\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
-This difference in slopes suggest that mo, albeit speculative due to resolution effects.
-In particular, it is possible that we may identify more substructures/smaller and less massive MCs if our simulation 
-was of higher resolution (but one must acknowledge that ..... is expeneisve to do zoom-in. This is what we have at best at the 
-moment with simulation power).
-That said, simularly massive moleuclar clouds have been reported in simulations of higher resolution (i.e., not zoom-in; \citealt{}).
-It is therefore conceivable that our results are not that far off.
+This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.
 
 % interpretation
-A higher $\sigma$ and $\Sigma_{\rm gas}$ is related to the higher
-pressure. The higher $\Sigma_{\rm gas}$ is also related to more massive clouds being formed.
-In M64, there are few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun, such massive molecular
-structures are unknown to local group, and are likely the ... from which massive clusters or OB associations are to be formed.
-In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$. % also, seen in massive star-forming regions, such as 30 Doradus.
+Velocity dispersion and surface density are tightly connected to pressure. 
+That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
+since $P\propto\Sigma^2$).
+In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
+$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
+The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
+In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
+On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
+from which massive star clusters or OB associations are to be formed.
 
 % a bit on caveat
-While our result, of particular relevance here is the slope of the CMF, is subject
-to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is
-we are likely biased to finding more massive clouds.
-High resolution simulations will be useful to shed light on
+One should, however, keep in mind that 
+the slope of the CMF reported here is subject
+to the uncertainties in the analysis method and the resolution of our simulation. 
+That is, we are likely biased to finding more massive clouds due to resolution effects; 
+it is possible that we may identify more and less massive MCs if our simulation 
+was done at a higher resolution. 
+That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
+existing computational power.
+In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
+in closed box simulations; \citealt{}).
+It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
+Future higher resolution zoom-in simulations would certainly be useful to gunderstand
 the evolving dynamical properties of the lower-mass molecular structures in
-galaxies at EoR; however, they are more expensive to run.
-On the contrary, an advantage of using cosmological zoom-in simulations for this study
-is that our computational boxes are not closed, allowing us to examine how
-the molecular complexes' properties vary under the influence of gas inflow/outflow 
-(see e.g., \citealt{Klessen10a, Goldaum11a}). % turbulence when disk still accreting gas
+galaxies at EoR under the influence of gas inflow/outflow.
+%On the contrary, an advantage of using cosmological zoom-in simulations for this study
+%is that our computational boxes are not closed, allowing us to examine how
+%the molecular complexes' properties vary under the influence of gas inflow/outflow 
+%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas
 
@@
 We quantify how stable a molecular structure is using the virial parameter, which
-is defined using \Eqn{virial} and describes the balance between kinetic and gravitational potential energies.
+is defined using \Eq{virial} and describes the balance between kinetic and gravitational potential energies.
 An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
 and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
-the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eqn{virial} 
+the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial} 
 in \Sec{PVE})}.
@@
 That said, our cosmological zoom-in simulation here allows us to examine 
-the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldaum11a}).
+the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
 

### 2018-09-10 WRITEUP/ms.tex
updated sec 6.1 and polished previous sec a bit more

@@
 the mechanisms and physics of formation and evolution of molecular structures and \SF.
-Upon identifying the molecular structures, we extract parameters such as
-the virial parameter ($\alpha_{\rm vir}$),
+Upon identifying the molecular structures, we extract properties such as
 mass ($M_{\rm cl}$),
@@
 \alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
-\label{eqn:virial}
+\label{eqn:alpha}
 \end{equation}
@@
 $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+
+We use the virial parameter, which is defined using \Eq{alpha} and describes 
+the balance between kinetic and gravitational potential energies, 
+to quantify how stable an MC is. 
+An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
+and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that 
+the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
 
@@
 MCs to have linewidth for a given set of surface densities (see \Sec{PVE}). 
+% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
+Heyer+09).
 
@@
 the conventional wisdom that collapsing structures result from local gravitational
-instability within globally non-collapsing structures,
+instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
 which are supported by turbulence and rotation. 
@@
 the MC itself is gravitationally unbound and is supported/confined 
-by turbulence and rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
+by turbulence (from the feedback of multiple episodes of \SF) 
+and galactic rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
 % Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
@@
 lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
-with $\alpha_{\rm vir}\simeq$1.
+with $\alpha_{\rm vir}\approx$\,2.
 Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
@@
 \caption{
-Larson's relation of \flower across all snapshots (showing MC properties in different evolutionary
-phases) and
-those observed in nearby and the \z$\sim$2 star-forming galaxy.
+Comparison of the MCs of \flower identified across all snapshots over the course of 700\,Myr (star symbols)
+to those observed in nearby and the \z$\sim$2 star-forming galaxy
+in the context of the linewidth-size relation --- showing variations in their properties at 
+the different evolutionary phases of \flower and with varying SFRs.
 \label{fig:larsons16-28}}
@@
 \caption{
-Same as \Fig{alpha16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
-where only denser substructures of the main disk of \flower are included.
+Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
+(i.e., MCs here are identified with the highest $n_{\rm cut}$).
 \label{fig:alpha16-28-highncut}}
@@
 \caption{
-Same as \Fig{larsons16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
-where only denser substructures of the main disk of \flower are included.
+Same as \Fig{larsons16-28}, but only the denser substructures of the main disk of \flower are included
+(i.e., MCs here are identified with the highest $n_{\rm cut}$).
 \label{fig:larsons16-28-highncut}}
@@
 
-{\bf still yet to make the ``Q''-map}
+{\bf still yet to make the ``Q''-map} \\
+
+We overplot the MCs on the Toomre-Q map.
 
@@
 It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
-Future higher resolution zoom-in simulations would certainly be useful to gunderstand
+Future higher resolution zoom-in simulations would certainly be useful to understand
 the evolving dynamical properties of the lower-mass molecular structures in
-galaxies at EoR under the influence of gas inflow/outflow.
+galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
+% 
 %On the contrary, an advantage of using cosmological zoom-in simulations for this study
@@
 
-\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
-\DL{maybe just merge in the previous sections when we present the results?}
-
+\subsection{Origin of the MCs} \label{sec:origin}
 The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller
@@
 the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
-those observed in \z$\sim$2\,$-$\,4 galaxies with spatially resolved \obs.
+those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging.
+
 The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
@@
 from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
-funneling into the center).
+requiring gas to be funneled into the central region).
 This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
 in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
-
-\subsection{Virial Parameter}
-
-\AP{I would move it to the previous section; I would use the virial parameter analysis to discuss the gravitational instability point more than on evolutionary state of the galaxy}
-
-We quantify how stable a molecular structure is using the virial parameter, which
-is defined using \Eq{virial} and describes the balance between kinetic and gravitational potential energies.
-An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
-and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
-the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial} 
-in \Sec{PVE})}.
-
-The high $\alpha_{\rm vir}$ found in the majority of MCs of \flower suggest that they are not collapsing.
-The largest structures are presumably supported by galactic rotation and turbulence from the feedback of
-multiple episodes of \SF.
-Turbulence in the smaller denser clouds are expected to cascade down over a timescale of $\sim$xxx\,Myr, after which the cloud will collapse
-(its substructure likely collapses earlier than this timescale since turbulences would have dissipated).
+The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render 
+the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the 
+high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
+
+\subsection{Virial Parameter, Collapse, and high SFR at high-\z}
 
@@
 likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
-as in the classical MC hierarchy. These smaller structures likely no longer supported by large-scale gravitational potential and differential rotation,
-and turbulence has dissipated rapidly on these scales to enable collapse \citep{Clark04a}.
-Non-axisymmetric perturbations (e.g., arms) to the gravitational potential
+as in the classical MC hierarchy. These smaller structures are 
+no longer supported by large-scale gravitational potential and differential rotation,
+as turbulence has dissipated rapidly on these smaller scales to enable collapse \citep{Clark04a}.
+In addition, non-axisymmetric perturbations (e.g., arms) to the gravitational potential
 can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
@@
 the multi-phase ISM structures of the first galaxies and their satellite galaxies.
-High resolution imaging of the molecular gas content in the first galaxies with ALMA and the Next Generation Very Large Array (ngVLA), on the other hand,
+High resolution imaging of the molecular gas content in the first galaxies with ALMA and the ngVLA, on the other hand,
 have the potential to provide useful observational data to test our findings and the validity of our simulation to shed

### 2018-09-10 WRITEUP/ms.tex
updated sec 6.2

@@
 can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
-Note also that \citet{Pettitt18a} report that the virial parameter could be a poor indicator
-for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. They
-do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
+
+We note that in a recent study by \citet{Pettitt18a}, the authors report that the virial parameter could be a poor indicator
+for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. 
+In particular, these authors do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
 and the star formation efficiency ($M_*/M_{\rm cl}$).
+Identifying a new diagnostic tool is beyond the scope of this paper. Here, we are more interested in 
+comparing the clouds dynamics with observational studies, and thus, 
+part of the discussion presented in this paper is based on virial analysis.
+But just something to keep in mind.
 
@@
 
-While first stars and galaxies are cooled predominated via H$_2$ lines.
-As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, metals also play an important role in the cooling of early galaxies.
+While first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
+As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
+metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.
+
+Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe may
+suggest that ...
 

### 2018-09-10 WRITEUP/ms.tex
removed Drexel affiliation
change notation for eq 1

@@
 % \documentclass[apj]{emulateapj}
+%\documentclass[iop]{emulateapj_old} 
 \documentclass[iop]{emulateapj} 
@@
 \author{Andrea Ferrara\altaffilmark{4, 5}}
-\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7, 8}}
+\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7
+%mm, 8   [I only use the Drexel affiliation when working with folks
+%from there...]
+}}
 
@@
 \altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
-\altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
+%mm \altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
 
@@
 \begin{equation}
-\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
-\end{equation}
-where $N$ is the number of zones of each MC.
+\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the sum is done over the cells composing each MC.
 The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
-\caption{
-SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
-observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
-Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
-\citealt{Pallottini17b}.
-%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
-%and references therein, and Sharon et al. in prep.
-\label{fig:sk}}
-\end{figure*}
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
+%\caption{
+%SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
+%observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
+%Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
+%\citealt{Pallottini17b}.
+%%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
+%%and references therein, and Sharon et al. in prep.
+%\label{fig:sk}}
+%\end{figure*}
 

### 2018-09-10 WRITEUP/ms.tex
use alpha_vir\approx2 thruout paper for consistency

--- 2018-09-10 WRITEUP/ms.tex
@@
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
+We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
 experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).

### 2018-09-10 plot_modules/dual_view_plotter.py
workaround cause yt refuses to hide axes

@@ -151,14 +151,14 @@ def plot_face_edge(isnap=28, selected_field='h2density', sizekpc=7., cutLow=1.e-
     #
     grid = AxesGrid(fig, (0.075, 0.075, 0.85, 0.85),
                     nrows_ncols=(1, 2),
-                    axes_pad=0.05,
+                    axes_pad=0.7,
                     #label_mode = "L",
                     label_mode="1",
                     share_all=True,
                     cbar_location="right",
                     cbar_mode="single",
                     cbar_size="3%",
-                    cbar_pad=0.01)
+                    cbar_pad=0.03)
 
     # plot edge on and face on
     #
@@ -203,35 +203,28 @@ def plot_face_edge(isnap=28, selected_field='h2density', sizekpc=7., cutLow=1.e-
                                                       'edgecolor': 'white',
                                                       'alpha': 0.})
 
-        if iplot == 0:
-            prj.set_ylabel('kpc')
-            prj.set_xlabel('kpc')
-            # prj.set_font_size(15)
-            prj.set_font({'family': 'Times',  # 'style': 'italic',
+        prj.set_ylabel('kpc')
+        prj.set_xlabel('kpc')
+        prj.set_font({'family': 'Times',  # 'style': 'italic',
                           # 'weight': 'bold',
-                          'size': 30})
+                          'size': 26})
 
         # set the plot into the grid
         plot = prj.plots[selected_field]
         plot.figure = fig
         plot.axes = grid[iplot].axes
         plot.cax = grid.cbar_axes[iplot]
-        # Finally, this actually redraws the plot.
-        prj._setup_plots()
 
         if iplot == 1:
             plot.axes.set_axis_off()
             # plot.axes.set_label('')
             # plot.axes.set_visible(False)
             plot.axes.set_xlabel('')
-            plot.axes.set_ylabel('')
             plot.axes.set_xticks(())
-            plot.axes.set_yticks(())
-            plot.axes.set_yticklabels('')
             plot.axes.set_xticklabels('')
 
-        if iplot == 0:
-            plot.axes.set_axis_on()
+        # Finally, this actually redraws the plot.
+        prj._setup_plots()
 
     for cax in grid.cbar_axes:
         cax.toggle_label(True)

### 2018-09-10 WRITEUP/ms.tex
incooporated most of AP's comments

--- 2018-09-10 WRITEUP/ms.tex
@@
 those observed in starburst galaxies.
-The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
+The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
 correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
@@
 While ALMA has enabled the detections of
-ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
-normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Smit18a},
+ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission inr
+normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
 we are still far from mapping their molecular ISM due to the cosmological dimming.
@@
 }}
-The simulation used in this work is described by \citealt{Pallottini17a} and is briefly summarized here.
+The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
 
 \ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
-adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
+adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
 In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
@@
 as a function of time.
+% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
+% {\DL or maybe in the discussion section?}
 This is advantageous especially at early cosmic epochs,
@@
 %
-The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (aka k-d tree).
+The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree).
 It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
-In the customized version used for this study, we modify the function to enhance the stability of the code (which essentially means we fixed the bugs in order for it to actually work).
+In the customized version used for this study, we modify the function to enhance the stability of the code.
+% (which essentially means we fixed the bugs in order for it to actually work).
 
@@
 \caption{
-MC identified by applying
-volumetric H$_2$ density cuts of
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
-	Color shows the projected H$_2$ surface density.
-{\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field; additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
+Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
+$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
+	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
+	\AP{additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
 hmm..
 Not worth my time to fix this for the report.}
-% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
 \label{fig:MC}}
@@
 In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
-for a given snapshot which includes contributions from its surrounding 7\,kpc (in diameter)\footnote{For reference,
+for a given snapshot which includes contributions within $R\sim$3.5\,kpc from the galaxy center\footnote{For reference,
 the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
@@
 where ``clumps/structures'' are 
-found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see Appendix of \citealt{Pallottini17b}).
-In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of 
-$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
-We also vary the range of
+found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
+We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
+$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
 $n_{\rm cut}$ adopted and find no qualitative differences
@@
 used to plot \Fig{h2density}.
+
+In \Fig{MC}, we over-plotted the molecular structures identified using
+a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example.
+The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
+\begin{equation}
+{\rm pixel} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
+\label{eqn:integrate}
+\end{equation} 
+where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
+
 Since the molecular structures identified could
@@
 the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
+% {\AP The size is an effective radius, calculated from the total volume of the MC assuming spherical symmetry.}
 Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate 
-the one-dimensional non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
-\begin{equation}
-\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{xyz} \sum_{i}^N \rho_i \left(\mathbf{v} - \mathbf{\bar v}\right)_{xyz}^2}{\sum_i^N \rho_i},
-\end{equation}
-where $N$ is the number of zones of each MC.
+the non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+\end{equation}
+which is summed over the cells composing each MC.
 The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
@@
 as the velocity dispersion ($\sigma$).}.
+This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
 
@@
 the order of 10$^{6.5}$\,\Msun for the densest MC identified. 
+% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
 We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
@@
 \subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
+{\AP I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
+Maybe we can put it as an appendix and keep only eq.
+10 in the main text (a put it at when analysing the relevant plot)?
+}
+
 % Relating Larson's law to stability and pressure (perhaps move this to other section?).
@@
 
-\subsection{Single Snapshots}  \label{sec:singless}
+\subsection{MC Properties}
+\subsubsection{Single Snapshots}  \label{sec:singless}
 
@@
 occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-\AP{however a plot showing the clump stats has not been show yet at this point}
 Their velocity dispersions are comparable to those observed in the inner Milky way and
@@
 with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
+% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
 On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
@@
 
-\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
+\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
 % single Snapshot
@@
 the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
-Our results is therefore robust, haha.
+Our results are therefore robust.
 
@@
 and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
-For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
+For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
 of finite thickness $h$
@@
 in closed box simulations; \citealt{}). 
+{\DL I'm forgetting the paper I want to cite..}
 It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
@@
 and the star formation efficiency ($M_*/M_{\rm cl}$).
-Identifying a new diagnostic tool is beyond the scope of this paper. Here, we are more interested in 
+Identifying a new diagnostic tool 
+% would be interesting for the future, but is outside the aim of the present work
+is beyond the scope of this paper. Here, we are more interested in 
 comparing the clouds dynamics with observational studies, and thus, 
@@
 the role of \highz galaxy populations
-in the context of galaxy evolution and the ISM physics behind their intense star formation in the early universe
-(if only the ALMA TAC will give us to the time to do so)...
+in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
 

### 2018-09-10 WRITEUP/ms.tex
added ref

@@
 In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
-in closed box simulations; \citealt{}). 
-{\DL I'm forgetting the paper I want to cite..}
+in closed box simulations; \citealt{Behrendt16a}). 
 It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).

### 2018-09-10 WRITEUP/ms.tex
if condition for style (not compiling for me otherwise)

--- 2018-09-10 WRITEUP/ms.tex
@@
 % --------------------------------------------
-% \documentclass[twocolumn]{aastex6}
-% \documentclass[apj]{emulateapj}
-%\documentclass[iop]{emulateapj_old} 
-\documentclass[iop]{emulateapj} 
+
+% AP: I have some compatibility issues with the new style (i.e. \section does not work)
+\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
+
 \usepackage{amsmath}
-
 \input{preamble}
@@
 
+% it can be instead included as
+% \graphicspath{{Fig/}}
+% so that plots are automatically searched for in the given path
 \def\figpath{./Fig}
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
-\caption{
+%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
+\caption{
+\AP{figure not found in the path}
 SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 

### 2018-09-10 WRITEUP/ms.tex
polished a bit

@@
 In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
-for a given snapshot which includes contributions within $R\sim$3.5\,kpc from the galaxy center\footnote{For reference,
+for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
 the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times 
@@
 affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
-to the same snapshot as that
+to the same snapshot 
 used to plot \Fig{h2density}.
 
-In \Fig{MC}, we over-plotted the molecular structures identified using
-a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example.
+For visualization, we overplot the molecular structures identified using
+a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps 
+in \Fig{MC} as an example.
 The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
@@
 \end{equation} 
-where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
+where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
+to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
 
@@
 easily appear as overlapping structures depending on the viewing angle, we
-also plot them in different three-dimensional projections --- so that one can more
+also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more
 easily see that they are collections of disjoint structures.
@@
 \subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
-{\AP I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
+% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
 Maybe we can put it as an appendix and keep only eq.
@@
 those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
-\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
+\Fig{alpha16}). The V-shaped dashed lines in the figure show the loci along which the given external pressures are needed for 
 MCs to have linewidth for a given set of surface densities (see \Sec{PVE}). 
@@
 compared to those observed in the Milky Way (black dot markers).
-The V-shaped dashed lines show the locii along which the given external pressures
+The V-shaped dashed lines show the loci along which the given external pressures
 are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
@@
 Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
+% \citep{Lombardi10a}.
 \label{fig:MR}}
@@
 That is, we are likely biased to finding more massive clouds due to resolution effects; 
-it is possible that we may identify more and less massive MCs if our simulation 
+it is possible that we may identify more less massive MCs if our simulation 
 was done at a higher resolution. 
-That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
+That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
 existing computational power.
-In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
-in closed box simulations; \citealt{Behrendt16a}). 
+In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
+simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
+Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
+since they adopt non-cosmological initial conditions. 
 It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).

### 2018-09-10 plot_modules/test_fig9.py
update with Althaea data

@@ -2,13 +2,13 @@
 
 Reproduce Pallottini17b Fig. 9
 
-Last mod: 7 Sept 2018
+Last mod: 10 Sept 2018
 
 '''
 
 import numpy as np
 import matplotlib.pyplot as plt
-from plot_modules.plot_cloud_prop import setup_plot
+from plot_cloud_prop import setup_plot
 
 setup_plot()
 
@@ -18,8 +18,12 @@ path = '../literature/data/'
 plt.close('all')
 plt.figure()
 # Althaea
-tff = 1.0
-plt.plot(np.log10(222.02/tff), np.log10(0.83), marker='*', markersize=15, color='red', label=r'Alth{\ae}a', linestyle='None', zorder=30)
+
+f_in = path + 'simulations.dat'
+x, y = np.loadtxt(f_in, usecols=(1, 2))
+x_althaea, y_althaea = x[0], y[0]
+
+plt.plot(np.log10(x_althaea), np.log10(y_althaea), marker='*', markersize=15, color='red', label=r'Alth{\ae}a', linestyle='None', zorder=30, markeredgecolor='k')
 
 
 file_list = ['sk_kennicutt1998.dat', 'sk_bouche07a.dat',  'sk_daddi10b.dat',

### 2018-09-10 plot_modules/plot_cloud_prop.py
SK relation for MCs and Pallo+17b points

@@ -12,6 +12,7 @@ def setup_cmap(cm='gist_rainbow'):
 
 def setup_plot():
     import matplotlib
+    from cycler import cycler
     # print(matplotlib.matplotlib_fname())
 
     matplotlib.rcParams.update({'figure.figsize': (8, 5)    # inches
@@ -19,6 +20,7 @@ def setup_plot():
                                 , 'legend.fontsize': 10      # points
                                 , 'lines.linewidth': 2       # points
                                 , 'axes.linewidth': 1       # points
+                                , 'axes.prop_cycle': cycler('color', 'bgrcmyk')
                                 , 'text.usetex': True    # Use LaTeX to layout text
                                 , 'font.family': "serif"  # Use serifed fonts
                                 , 'xtick.major.size': 10     # length, points
@@ -88,6 +90,7 @@ def unpack_xy(ss):
         _tffMyr = []
         _mSD_cgs = []
         _sigma2oR = []
+        _mSD_per_ff = []   # Msun/pc^2/Myr
 
         for kkk in ss[ks].iterkeys():
             # print ss[ks][kkk]
@@ -112,6 +115,7 @@ def unpack_xy(ss):
                             ss[ks][kkk].Msun2g / (ss[ks][kkk].pc2cm)**2)
             _sigma2oR.append(ss[ks][kkk].sigmaSq / (1.e5)**2 /
                              (ss[ks][kkk].R_pc * 2.0))
+            _mSD_per_ff.append(ss[ks][kkk].massSD / (ss[ks][kkk].R_pc)**2 / ss[ks][kkk].tff_Myr)
 
         to_plot[ks] = {}
         to_plot[ks]['cloud mass'] = _m
@@ -131,6 +135,7 @@ def unpack_xy(ss):
         to_plot[ks]['tff Myr'] = _tffMyr
         to_plot[ks]['gas sd cgs'] = _mSD_cgs
         to_plot[ks]['sigmaSq over size'] = _sigma2oR
+        to_plot[ks]['gas sd per ff'] = _mSD_per_ff
 
     return to_plot
 
@@ -174,6 +179,47 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
 
     legend_h = []
 
+    if xstr == "gas sd per ff" and ystr == "sfr sd":
+        # data points from Pallottini+17b Fig. 9
[…]

### 2018-09-10 plotsingleSS.py

@@ -46,6 +46,7 @@ def plotting_procedure(snapshot_num):
 
     ss, to_plot, leafdir_out = load_pickleTOplot(snapshot_num)
 
+    plot_stuff("gas sd per ff", "sfr sd", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)    # SK
     plot_stuff('gas sd cgs', 'sigmaSq over size', leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff('alpha vir', 'sigmaSq over size', leglabel="ncut: ",
@@ -62,7 +63,6 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("stellar to gas mass", "sigma kms", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-#     plot_stuff("gas sd", "sfr sd", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("gas sd", "sigma kms", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",

### 2018-09-10 WRITEUP/ms.tex
update abstract

@@
 We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
-at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation.
+at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
 We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
 to identify MCs and their sub-structures.
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
+We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
+for each MC and 
 compare them with those observed in the Milky Way disk, the Galactic center,
@@
 the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
-Virial analysis indicates that the MC found in the arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
+Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
 This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
-experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
+due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
 MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
-as gas is being accreted from the IGM.
+as gas is being accreted from the intergalactic medium.
 We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
-Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
-mass distribution, which steepens as we increase $n_{\rm cut}$. 
+Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
+mass distribution, which steepens with $n_{\rm cut}$. 
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
@@
 migration of such giant massive clumps are responsible for contributing to the
-buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.
-
-Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies
+buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
+
+Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these relatively more extreme conditions, thereby driving the evolution and assembly
+of galaxies 
 since the cosmic dark ages.
@@
 gas masses, gas temperature, and radiation field intensity).
-However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
+However, spatially resolving their ISM is necessary to understand their roles in galaxy evolution and
 the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
@@
 While ALMA has enabled the detections of
-ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission inr
+ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
 normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
@@
 \AP{TBM}
-In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
-and describe the method used to identify its molecular gas complexes (MC).
+In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
+and describe the method used to identify its molecular gas complexes.
 In \Sec{results}, we present scaling relations based on
@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/CMF_.png}
 \caption{
@@
 \label{fig:cmf}}
-\end{figure*}
+\end{figure}
 
@@
 since they adopt non-cosmological initial conditions. 
-It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
+It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
 Future higher resolution zoom-in simulations would certainly be useful to understand
@@
 This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
-in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
+in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}).
 The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render 
@@
 which set the scale for fragmentation.
-This is consistent with what has been found previously in higher resolution simulation of isolated galaxies \citep{}.
+This is consistent with what has been found previously in higher resolution idealized simulation of isolated galaxies.
 That said, our cosmological zoom-in simulation here allows us to examine 
@@
 As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
-We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
-(see \Sec{sfh} for details) compared to those reported in \obs.
-
-\AP{i m currently a bit confused on how to re-generate pickle files to be used for the plot}
-\DL{by running test\_brute.py}
-
-\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17a}}
-\DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}
+We show in \Fig{sk} the MCs of \flower identified in the accreting phase using different $n_{\rm cut}$
+(see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}.
 
@@
 \centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/CMF_.png}
-\caption{
-\AP{figure not found in the path}
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
+\caption{
 SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 

### 2018-09-10 WRITEUP/ms.tex
update abstract more

@@
 which set the scale for fragmentation.
-The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
-The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
-the molecular substructures, likely resulting from 
+The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted,
+with $\sigma\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
+the molecular substructures.
+The high velocity dispersions likely result from 
 the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.

### 2018-09-10 WRITEUP/ms.tex
proof read and moved text a bit

@@
 (sub-)structures seen in nearby and \z$>$\,0 galaxies.
-We present Toomre stability analysis in \Sec{Q} and
-the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
+We present Toomre stability analysis in \Sec{Q}.
 In \Sec{diss}, we discuss the results and implications of our findings,
@@
 In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
-%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
-Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level.
-Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
-% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
+Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
+Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
 We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
@@
 We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations.
-To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode.
-The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
+To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell during a supernova explosion.
+The energy dissipated is then injected into the ISM in the form of kinetic and thermal energies.
 Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).
@@
 Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
-Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG) hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG), hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
 At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-It is therefore a prototypical galaxy at \z$\sim$6.
+It is therefore a prototypical galaxy at \z$\sim$\,6.
 
@@
 \subsection{Star Formation History} \label{sec:sfh}
-One of the advantage of studying the dynamical properties of molecular structures at
+One of the main advantages for studying the dynamical properties of molecular structures at
 $z$\ssim6 in simulation is the fact that we can examine how their properties evolve
@@
 is a factor of two higher than shown here since they also include contributions from
-massive satellites galaxies within the surrounding $\approx$50\,kpc, which
+massive satellite galaxies within the surrounding $\approx$50\,kpc, which
 are accreted onto \flower at \z$\lesssim$\,2.}
@@
 we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
-as examples in \Sec{singless} to illustrate the salient points of the discussion,
+as examples in \Sec{singless} to illustrate the salient points of the discussion presented in this paper,
 since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
@@
 Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the 
-accreting phase shown in \Fig{SFH}.
+accretion phase shown in \Fig{SFH}.
 \label{fig:h2density}}
@@
 We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
-The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
-the order of 10$^{6.5}$\,\Msun for the densest MC identified. 
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of
+the order of 10$^{6.5}$\,\Msun for the densest MC.
 % {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
@@
 \caption{
-Distributions of masses, sizes, and gas mass fractions of MCs identified using 
+Distributions of mass, size, and gas mass fraction of MCs identified using 
 the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
-Note the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
+Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
 at higher $n_{\rm cut}$.
@@
 $T$ is the volume term of the total kinetic energy (including thermal and
-bulk motions), $T_s$ is the surface term due to external thermal pressure,
+bulk motions), $T_s$ is the surface term due to external pressure,
 $W$ is the gravity term, and $B$ is the magnetic term.
@@
 to quantify how stable an MC is. 
-An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
+An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms 
 and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that 
@@
 \subsubsection{Single Snapshots}  \label{sec:singless}
-
-%
-\AP{I would move the following when discussing the velocity dispersion; additionally, the large velocity dispersions was also noted in Vallini2018a, we can use some of those results to complement the discussion (e.g.
-shift for the CO sled at higher J then local galaxies).}
 
@@
 Larson's (linewidth-size) relation of \flower in
-accreting phase (top) and
+accretion phase (top) and
 starburst phase (bottom) compared to
@@
 \caption{
-Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
+Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
+(other symbols).
 Literature data are compiled from \citealt{Kauffmann17b} and references therein.
 Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
-compared to those observed in the Milky Way (black dot markers).
+compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
 The V-shaped dashed lines show the loci along which the given external pressures
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
+We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
 compared to the 
@@
 That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
-at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along the locus 
+at a given radius. As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
 with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
@@
 We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
-parameter space as the accreting phase. 
+parameter space as the accretion phase. 
 {\bf so...}
@@
 \caption{
-Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
+Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
 compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
@@
 
-\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
+\subsubsection{Cumulative Mass Distribution}   \label{sec:cmf}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/CMF_.png}
+\caption{
+CMF of MCs in \flower and best-fit power law.
+\label{fig:cmf}}
+\end{figure}
+
+The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
+consistent with those observed in \z$\sim$2 galaxies in
+rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+Observational studies in the nearby Universe, where 
+spatially resolution are better at revealing molecular (sub-)structures,
+often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
+While the CMF of the MCs for a given snapshot of our simulation is 
+quite noisy, since we have only one (main) galaxy, 
+we can improve the ``signal-to-noise ratio'' by including 
+MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
+the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
+We show the resulting CMF in \Fig{cmf}.
+
+Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
+\begin{equation}
+n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
+\end{equation}
+where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
+We find that 
+the slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for the lowest and the highest $n_{\rm cut}$ adopted.
+The uncertainties are the formal fitting uncertainties.
+Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
+is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
+$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
+This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.
+
+\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
+The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
+and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
+For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
+of finite thickness $h$
+is described by:
+\begin{equation}
+\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
+\label{eqn:3Ddisp}
+\end{equation}
+where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
+The first term on the RHS describes rotation support, second term describes self-gravity, and
+the third term describes pressure support.
+The epicyclic frequency is defined as:
+\begin{equation}
+\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
+\label{eqn:kappa}
+\end{equation}
+% \kappa\propto\Omega
+One can then define the so-called Toomre-Q parameter/criterion for stability as
+\begin{equation}
+Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
+\label{eqn:Q}
+\end{equation}
+We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
+\begin{equation}
+\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
+\end{equation}
+Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
+and fragmentation can happen
+(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
+satellite galaxies and stellar feedback).
+That is, local fragmentation takes place when gravity overcomes pressure support
+from turbulence (thermal is small here) and shearing of differential rotation.
+
+In the limit of a thin rotating disk, rotation can help stabilizes
+self-gravitational contraction for wavelengths greater than the Toomre length:
+\begin{equation}
+\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
+\end{equation}
+yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
+which sets the ``upper limit'' to which MCs can form in a shearing disk.
+
+{\bf still yet to make the ``Q''-map} \\
+
+We overplot the MCs on the Toomre-Q map.
+
+%--------------------------------------------------------------------------
+%                                Discussion
+%--------------------------------------------------------------------------
+\section{Discussions and Implications}     \label{sec:diss}
+
+\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
 % single Snapshot
@@
 
-\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
-The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
-and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
-For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
-of finite thickness $h$
-is described by:
-\begin{equation}
-\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
-\label{eqn:3Ddisp}
-\end{equation}
-where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
-The first term on the RHS describes rotation support, second term describes self-gravity, and
-the third term describes pressure support.
-The epicyclic frequency is defined as:
-\begin{equation}
-\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
-\label{eqn:kappa}
-\end{equation}
-% \kappa\propto\Omega
-One can then define the so-called Toomre-Q parameter/criterion for stability as
-\begin{equation}
-Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
-\label{eqn:Q}
-\end{equation}
-We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
-\begin{equation}
-\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
-\end{equation}
-Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
-and fragmentation can happen
-(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
-satellite galaxies and stellar feedback).
-That is, local fragmentation takes place when gravity overcomes pressure support
-from turbulence (thermal is small here) and shearing of differential rotation.
-
-In the limit of a thin rotating disk, rotation can help stabilizes
-self-gravitational contraction for wavelengths greater than the Toomre length:
-\begin{equation}
-\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
-\end{equation}
-yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
-which sets the ``upper limit'' to which MCs can form in a shearing disk.
-
-{\bf still yet to make the ``Q''-map} \\
-
-We overplot the MCs on the Toomre-Q map.
-
-\section{Cumulative Mass Distribution}   \label{sec:cmf}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/CMF_.png}
-\caption{
-CMF of MCs in \flower and best-fit power law.
-\label{fig:cmf}}
-\end{figure}
-
-The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
-consistent with those observed in \z$\sim$2 galaxies in
-rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-Observational studies in the nearby Universe, where 
-spatially resolution are better at revealing molecular (sub-)structures,
-often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
-While the CMF of the MCs for a given snapshot of our simulation is 
-quite noisy, since we have only one (main) galaxy, 
-we could improve the ``signal-to-noise ratio'' by including 
-MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
-the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
-We show the resulting CMF in \Fig{cmf}.
-
-Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
-\begin{equation}
-n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
-\end{equation}
-where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
-The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 by adopting the lowest and the highest $n_{\rm cut}$ studied here.
-The uncertainties are the formal fitting uncertainties.
-Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
-is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
-$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
-This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.
-
-% interpretation
-Velocity dispersion and surface density are tightly connected to pressure. 
-That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
-since $P\propto\Sigma^2$).
-In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
-$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
-The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
-In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
-On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
-from which massive star clusters or OB associations are to be formed.
-
-% a bit on caveat
-One should, however, keep in mind that 
-the slope of the CMF reported here is subject
-to the uncertainties in the analysis method and the resolution of our simulation. 
-That is, we are likely biased to finding more massive clouds due to resolution effects; 
-it is possible that we may identify more less massive MCs if our simulation 
-was done at a higher resolution. 
-That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
-existing computational power.
-In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
-simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
-Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
-since they adopt non-cosmological initial conditions. 
-It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
-Future higher resolution zoom-in simulations would certainly be useful to understand
-the evolving dynamical properties of the lower-mass molecular structures in
-galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
-% 
-%On the contrary, an advantage of using cosmological zoom-in simulations for this study
-%is that our computational boxes are not closed, allowing us to examine how
-%the molecular complexes' properties vary under the influence of gas inflow/outflow 
-%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas
-
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
-\section{Discussions and Implications}     \label{sec:diss}
-
 \subsection{Origin of the MCs} \label{sec:origin}
-The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller
-spatial and mass structures that are also denser as we increase $n_{\rm cut}$. In any case,
+The largest molecular structure identified is essentially the main disk of \flower which breaks down into smaller
+substructures that are denser as we increase $n_{\rm cut}$. In any case,
 the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
-those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging.
+those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
 
@@
 
-\subsection{CMF and IMF at EoR}
-
-While first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
-As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
-metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.
-
-Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe may
-suggest that ...
-
-CMF influences the IMF because ..
-different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....
-For instance, massive protostellar clumps are always supersonic, thus their internal structure are complex.
-They may form multiple stars.
-
-The minimum clump mass $M_{\rm min}$ is limited by numerical resolution of our simulation.
-We do not have a resolution study (in hand) and so we cannot quantitatively evaluate this at the moment.
-The minimum clump mass allowed
-by our clump finding algorithm is the mass over 10 cells that exceeds the given threshold density.
+\subsection{MC Dynamics and CMF and IMF at EoR}
+
+Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
+suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe.
+% interpretation
+Velocity dispersion and surface density are tightly connected to pressure. 
+That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and 
+since $P\propto\Sigma^2$).
+In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of 
+$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
+The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
+In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
+On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
+from which massive star clusters or OB associations are to be formed.
+% 
+Therefore, speculatively... possible that ... the different CMF may suggest different IMF for \flower. 
+This could be understood as different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
+% (While the first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
+%As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
+%metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.)
+
+% a bit on caveat
+One should, however, keep in mind that 
+the slope of the CMF reported here is subject
+to the uncertainties in the analysis method and limitations in the numerical resolution of our simulation. 
+That is, we are likely biased to finding more massive clouds due to resolution effects; 
+it is possible that we may identify more less massive MCs if our simulation 
+was done at a higher resolution. 
+That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
+existing computational power.
+In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
+simulations done at higher resolution (e.g., \citealt{Behrendt16a}). 
+Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations 
+since they adopt non-cosmological initial conditions. 
+It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
+Future higher resolution zoom-in simulations would certainly be useful to understand
+the evolving dynamical properties of the lower-mass molecular structures in
+galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
 
@@
 As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
-We show in \Fig{sk} the MCs of \flower identified in the accreting phase using different $n_{\rm cut}$
+We show in \Fig{sk} the MCs of \flower identified in the accretion phase using different $n_{\rm cut}$
 (see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}.

### 2018-09-10 WRITEUP/ms.tex
move text a bit

@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_PVE.png}
 \caption{
@@
 \label{fig:alpha16}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_PVE.png}
 \caption{
@@
 \label{fig:alpha27}}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_PVE.png}
 \caption{
@@
 \label{fig:alpha16-28}}
-\end{figure*}
+\end{figure}
 
@@
 panel of \Fig{larsons_single} and \Fig{alpha27}).
+% 
+% \subsubsection{Temporal Evolution in Cloud Dynamics}
+% What about all snapshots, where should the results for that go... \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{larsons16-28-highncut} and \Fig{alpha16-28-highncut}.
 
@@
 the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
-Our results are therefore robust.
+Our results are therefore robust to the various density cuts of choice.
 
@@
 The largest molecular structure identified is essentially the main disk of \flower which breaks down into smaller
-substructures that are denser as we increase $n_{\rm cut}$. In any case,
+substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28} and \Fig{larsons16-28-highncut}). In any case,
 the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
@@
 
-Speculatively, the shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
-suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe.
 % interpretation
@@
 % 
-Therefore, speculatively... possible that ... the different CMF may suggest different IMF for \flower. 
-This could be understood as different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
+The shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
+suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe,
+notwithstanding the limited numerical resolution of our simulation.
+Together with the high $P_{\rm ext}$ may suggest different IMF for \flower compared to those observed in nearby galaxies.
+This could be understood in the context of .... different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
 % (While the first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
@@
 by identifying a set of different density contours at different snapshots.
-Using volumetric H$_2$ is essentially the same as identified molecular structures using
-different contours in line emission (e.g., CO, CS, NH$_3$)
-% and different molecular line tracers trace different MCs on different scales due to their
-% different critical densities.
+Using volumetric H$_2$ is essentially similar to identifying molecular structures using
+different contour levels on a surface brightness map of a molecular line tracer (e.g., CO, CS, NH$_3$),
 since the line luminosity scales with the molecular gas density (modulo optical depth effects).
@@
 compare them with those observed in the Milky Way disk, the Galactic center,
-and gas-rich starburst galaxies in the local universe and at the peak epoch of cosmic \SF.
+and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
 We also examine their properties at the different evolutionary stages of \flower and compare
@@
 The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
-Our results are thus robust/insensitive to the various density cuts of choice.
+Our results are thus insensitive to the various density cuts of choice.
 %However, our results are dependent on the numerical resolution of the simulation.
 The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
-the molecular substructures, likely resulting from 
+the molecular substructures.
+Such a high velocity dispersion likely results from 
 the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
@@
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\approx$2 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
+We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as 
+result of the weaker stellar feedback as they have
 experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).

### 2018-09-10 WRITEUP/ms.tex
minor fig size change

@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-PVE-highncut.png}
 \caption{
@@
 \label{fig:alpha16-28-highncut}}
-\end{figure*}
+\end{figure}
 
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
 \caption{

### 2018-09-11 WRITEUP/ms.tex
more polishing and add ref

@@
 \begin{equation}
-{\rm pixel} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
+{\rm voxel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
 \label{eqn:integrate}
 \end{equation} 
-where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
-to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
+where $\rho_{\rm H2, i}$ is the H$_2$ density of voxel $i$, $w_i$ is the weighted quantity in voxel $i$ which we adopt 
+to be the total gas density, and $\Delta z_i$ is the path length of voxel $i$ along the line-of-sight over which the quantities are integrated along.
 
@@
 more consistent with those observed in the inner regions of
-Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$,
+Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
 % which is $\propto\rho\sigma^2$
+% M51: Colombo+14
 While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
@@
 likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
-as in the classical MC hierarchy. These smaller structures are 
-no longer supported by large-scale gravitational potential and differential rotation,
-as turbulence has dissipated rapidly on these smaller scales to enable collapse \citep{Clark04a}.
-In addition, non-axisymmetric perturbations (e.g., arms) to the gravitational potential
-can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
+as in the classical MC hierarchy. 
+Second, due to 
+turbulence dissipation on small-scales, such (sub-)structures are no longer supported by 
+large-scale gravitational potential and differential rotation. 
+This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
+MCs \citep{Clark04a, Clark05a}.
+Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
+can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation.
 
@@
 The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
-In M64, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun. 
-On the other hand, such massive molecular structures are unknown to local group, and are likely the sites 
+In M64 and M51, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun \citep{Rosolowsky05a, Koda09a, Colombo14a}. 
+On the other hand, such massive molecular structures are unknown to Local Group \citep[e.g.,][]{Rice16a}, and are likely the sites 
 from which massive star clusters or OB associations are to be formed.
@@
 Using volumetric H$_2$ is essentially similar to identifying molecular structures using
-different contour levels on a surface brightness map of a molecular line tracer (e.g., CO, CS, NH$_3$),
+different contour levels/surfaces on a surface brightness map/cube of a molecular line tracer (e.g., CO, CS, NH$_3$),
 since the line luminosity scales with the molecular gas density (modulo optical depth effects).
@@
 as gas is being accreted from the IGM.
+
 We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
@@
 for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
-Observations leveraging the combination of spatio-spectral imaging of
+Observations leveraging the combination of spatial-spectral imaging of
 multi-band continuum and spectral line emission are crucial for better understanding
@@
 in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
-
 High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
@@
 
-% model can guide and interpret observations and provide new testable predictions. 
-% refine models using these new observations and test where models fail.
-% The opposite is true, where can use models to make predictions for the first galaxies, 
-% where future obs w/ ALMA and ngVLA will help discriminate and better understand xxx.
-
 %==============================================================================
@@
 A.F. acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
-This work was initiated as a project for the Kavli Summer Program in Astrophysics (KSPA)
+This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA)
 held at the Center for
@@
 We thank the KSPA Scientific and Local Organizing Committees, and the program founder,
-Pascale Garaud for supporting the genesis of this work.
-We also thank the New York University CCPP for their hospitality in hosting us, the refugees, after the steam pipe explosion in NYC during the KSPA.
+Pascale Garaud, for supporting the genesis of this work.
+We also thank the Center for Cosmology and Particle Physics (CCPP) 
+at the New York University
+for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
+This research has made use of NASA's Astrophysics Data System Bibliographic Services
+and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
 

### 2018-09-11 WRITEUP/ms.tex
update fig 3, resize fig, finished sec 5, finished sec 3.2.1 on MR relation, polished more

@@
 at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
-We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
+We use a clump-finding algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
 to identify MCs and their sub-structures.
@@
 This paper is structured as follows.
-\AP{TBM}
+% \AP{TBM}
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
@@
 In \Sec{results}, we present scaling relations based on
-the MC identified and compare them with observations of molecular
-(sub-)structures seen in nearby and \z$>$\,0 galaxies.
+the MC identified and compare them with observations of molecular clouds
+and structures seen in nearby and \z$>$\,0 galaxies.
 We present Toomre stability analysis in \Sec{Q}.
-In \Sec{diss}, we discuss the results and implications of our findings,
+We discuss the results % , robustness of our analysis, caveats, 
+and implications of our findings in \Sec{diss},
 and present our conclusions in \Sec{conclusion}.
@@
 \subsection{Structure identification} \label{sec:method}
-To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
+To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
 %
@@
 using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
-and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).
+and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
 We note that, owing to the nature of \obs, such structures are identified 
@@
 PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, 
-Pan15a, Ibanez-Mejia16a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
+Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations). 
 % large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
@@
  \centering
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.png}
-  \\[-5.5em]
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.png}
-  \\[-5.5em]
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.png}
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.pdf}
+  \\ [-2.9em]
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.pdf}
+  \\ [-2.9em] 
+  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.pdf}
 \caption{
@@
 	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
-	\AP{additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
+% 	\AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
 hmm..
@@
 \begin{equation}
-{\rm voxel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
+{\rm pixel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
 \label{eqn:integrate}
 \end{equation} 
-where $\rho_{\rm H2, i}$ is the H$_2$ density of voxel $i$, $w_i$ is the weighted quantity in voxel $i$ which we adopt 
-to be the total gas density, and $\Delta z_i$ is the path length of voxel $i$ along the line-of-sight over which the quantities are integrated along.
+where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
+to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
 
@@
 
-\AP{I see 2 main possible approaches to the presentation of the results
-%
-(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
-%
-(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
-%
-Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
-%
-I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g.
+%\AP{I see 2 main possible approaches to the presentation of the results
+%%
+%(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
+%%
+%(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
+%%
+%Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
+%%
+%I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g.
 the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
-}
-\DL{agreed, but will move things around later, after the report and after most of the content is ready.}
+%}
+%\DL{agreed, but will move things around later, after the report and after most of the content is ready.}
 
@@
 as the velocity dispersion ($\sigma$).}.
+On average, the Mach number of the MCs corresponds to about $\mathcal{M}\approx50$.
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
@@
 In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
-the MC itself is gravitationally unbound and is supported/confined 
+the MC itself is gravitationally unbound and is supported
 by turbulence (from the feedback of multiple episodes of \SF) 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16_PVE.png}
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
 \caption{
@@
 \label{fig:alpha16}}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss27_PVE.png}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
 \caption{
@@
 \label{fig:alpha27}}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28_PVE.png}
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_PVE.png}
 \caption{
@@
 \label{fig:alpha16-28}}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-PVE-highncut.png}
 \caption{
@@
 \label{fig:alpha16-28-highncut}}
-\end{figure}
+\end{figure*}
 
@@
 Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales 
-via two physical properties: mass and size \citep{Larson81a, Mckee07a}. This is also known as the law of constant column density, 
+via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the law of constant column density, 
 since cloud mass in \obs is sometimes derived by integrating
@@
 compared to the 
-observational data of molecular clouds in the Milky Way associated with massive \SF 
-\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
-Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
-which we extrapolate to match the mass and size scales of the MCs of \flower.
-By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
-in the Milky Way, \citet{Kauffmann10c} report a 
-mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
-That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
-at a given radius. As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
-with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
+observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF 
+\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and the empirical relation obtained based on 
+Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein).
+This relation is obtained by comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun). 
+\citet{Kauffmann10c} interpret this
+mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as
+the threshold for massive \SF.
+The implication of this result is that cluster-forming cloud fragments are 
+found to be more massive than those that are devoid of clusters 
+at a given radius.
+
+As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
+with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}, which 
 % {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
-On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
-{\bf This may suggest ....}
-We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
-parameter space as the accretion phase. 
-{\bf so...}
-
-Similar MC properties in relation to those observed in the nearby Universe are found for \flower in its starburst phase (see bottom 
-panel of \Fig{larsons_single} and \Fig{alpha27}).
-% 
-% \subsubsection{Temporal Evolution in Cloud Dynamics}
-% What about all snapshots, where should the results for that go... \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{larsons16-28-highncut} and \Fig{alpha16-28-highncut}.
+is below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
+This can be understood by acknowledging the fact that a H$_2$ molecular cloud 
+does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
+and that our simulation does not have enough resolution to directly form CO\footnote{
+In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we 
+model the internal structure of MC within each cell in our simulation.}.
+That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the 
+fact that the MCs in our simulation have lower column density compared to the star-forming cores observed in the Milky Way, which are 
+observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
+% unresolved CO?detected molecular clouds in other galaxies should have an average A_V = 4 mag.
+
+Similar MC properties in relation to those observed in the nearby Universe are found during the starburst phase of 
+\flower (see e.g., bottom panel of \Fig{larsons_single} and \Fig{alpha27}).
+On average, we do not find any quantitative differences in the MC properties in the accretion versus starburst phase.
 
@@
 
-The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
+The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, which is
 consistent with those observed in \z$\sim$2 galaxies in
@@
 which sets the ``upper limit'' to which MCs can form in a shearing disk.
-
-{\bf still yet to make the ``Q''-map} \\
+\DL{still yet to make the ``Q''-map}
 
@@
 
-\subsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
+\subsection{Variation in MC Properties Depending on the Choice of Density Cuts and 
+Temporal Evolution in Cloud Dynamics}	 \label{sec:ncut}
 % single Snapshot
@@
 
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCs identified across all snapshots
+in \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{alpha16-28-highncut},
+and \Fig{larsons16-28-highncut}.
+We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+% \DL{This suggests that, at least ...., the ... of the cloud dynamics in \flower... over the timescale..}
+
 \subsection{Origin of the MCs} \label{sec:origin}
@@
 for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. 
-In particular, these authors do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
-and the star formation efficiency ($M_*/M_{\rm cl}$).
+In particular, these authors do not find any significant correlations between the virial parameter, cloud mass,
+and star formation efficiency ($M_*/M_{\rm cl}$).
 Identifying a new diagnostic tool 
@@
 comparing the clouds dynamics with observational studies, and thus, 
-part of the discussion presented in this paper is based on virial analysis.
-But just something to keep in mind.
+part of the discussion of this paper is based on virial analysis.
 
@@
 In M64 and M51, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun \citep{Rosolowsky05a, Koda09a, Colombo14a}. 
-On the other hand, such massive molecular structures are unknown to Local Group \citep[e.g.,][]{Rice16a}, and are likely the sites 
+On the other hand, such massive molecular structures are unknown to Local Group galaxies 
+\citep[e.g.,][]{Rice16a}, and are likely the sites 
 from which massive star clusters or OB associations are to be formed.
@@
 notwithstanding the limited numerical resolution of our simulation.
-Together with the high $P_{\rm ext}$ may suggest different IMF for \flower compared to those observed in nearby galaxies.
-This could be understood in the context of .... different cooling properties will lead to different xxx, and thus, Jeans mass/thus determines the final properties of the cloud fragmentation....  
-% (While the first stars and galaxies are cooled predominated via atomic H and H$_2$ lines.
-%As shown in the $T-n$ phase plot in Fig. 8 of \citealt{Pallottini17b}, 
-%metals also play an important role in the cooling of the first galaxies soon after the first generation of stars have enriched the surrounding.)
+That said, the Jeans mass $M_J$\eq$\sigma^4/(G^2\Sigma)$ yields $\sim$\,8\E{8}\,\Msun 
+for a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of 
+$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$, which are typical of the MCs of \flower.
+This Jeans mass is in agreement with the mass range found (see \Fig{dist}).
+
+% CMF and IMF
+The CMF is related to the mass function of stars (IMF),
+since the former describes the mass distribution of 
+the materials for \SF (see e.g., \citet{McKee07a} for a review).
+Observational studies of a diverse range of environments suggest that the IMF is invariant 
+between star-forming regions, star clusters, and spiral galaxies 
+(see a review by \citealt{Bastian10a}; see also \citealt{Bochanski10a, AlvesdeOliveira13a, Calamida15b}), but is subject 
+to variation under extreme conditions (e.g., temperatures, densities, and radiation field intensities), such as  
+in the Galactic center (e.g., \citealt{Lu13a, Conroy13a}).  
+Speculatively, the different CMF slope found in \flower may suggest a different IMF compared to those observed in nearby galaxies.
+In particular, the steeper slope may indirectly translate into a top-heavy IMF (see \citealt{Alves07a, Anathpindika11a}), which is commonly assumed in most \highz studies to date\footnote{Since intuitively, we expect a higher Jeans mass at higher redshift, due to the lower metallicities and higher temperature
+expected in these first galaxies.}.
 
@@
 was done at a higher resolution. 
-That said, one must acknowledge that such a zoom-in simulation is currently quite expensive to perform with 
-existing computational power.
+That said, one must acknowledge that such a zoom-in simulation 
+is currently quite expensive to perform with 
+existing computational power. %, given the complexity of the physics invoked as input.
 In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy 
@@
 hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
-We use a clump finder algorithm and a set of H$_2$ volumetric densities
-to identify MCs and their sub-structures in the main galaxy --- \flower\ --- of the
-simulated 20\,Mpc h\pmOne box and in its satellites.
+We use a clump-finding algorithm and a set of H$_2$ volumetric densities
+to identify MCs and their sub-structures in the main galaxy of the
+simulated 20\,Mpc~$h$\pmOne box --- \flower\ --- and in its satellites.
 We decompose the molecular structures into non-overlapping tiles
@@
 Using volumetric H$_2$ is essentially similar to identifying molecular structures using
-different contour levels/surfaces on a surface brightness map/cube of a molecular line tracer (e.g., CO, CS, NH$_3$),
+different contour levels/surfaces on surface brightness maps/cubes of molecular line tracers (e.g., CO, CS, NH$_3$),
 since the line luminosity scales with the molecular gas density (modulo optical depth effects).
-% Our choice of density cut is analogues to the .... in \obs. It should be ... that both suffer from problem .... For instance, in \obs.. limited S/N.
 We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and 
@@
 Pascale Garaud, for supporting the genesis of this work.
-We also thank the Center for Cosmology and Particle Physics (CCPP) 
+We also thank the Center for Cosmology and Particle Physics 
 at the New York University
@@
 
-\appendix
-\section{Schmidt-Kennicutt Relation}
-As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
-We show in \Fig{sk} the MCs of \flower identified in the accretion phase using different $n_{\rm cut}$
-(see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}.
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
-\caption{
-SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
-observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
-Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
-\citealt{Pallottini17b}.
-%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
-%and references therein, and Sharon et al. in prep.
-\label{fig:sk}}
-\end{figure*}
+% \DL{to update}
+%\appendix
+%\section{Schmidt-Kennicutt Relation}
+%As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
+%We show in \Fig{sk} the MCs of \flower identified in the accretion phase using different $n_{\rm cut}$
+%(see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}. 
+%
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
+%\caption{
+%SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
+%observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
+%Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
+%\citealt{Pallottini17b}.
+%%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
+%%and references therein, and Sharon et al. in prep.
+%\label{fig:sk}}
+%\end{figure*}
+%
 

### 2018-09-12 WRITEUP/ms.tex
update MR relation caption

@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
-compared to the 
+We show in \Fig{MR} the size-mass relation of the MCs of \flower in its accretion phase (see \Sec{sfh})
+compared to 
 observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF 
-\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and the empirical relation obtained based on 
-Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein).
-This relation is obtained by comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun). 
-\citet{Kauffmann10c} interpret this
-mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as
-the threshold for massive \SF.
+\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on 
+Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
+\citet{Kauffmann10c} interpret this empirical relation 
+as the threshold for massive \SF.
 The implication of this result is that cluster-forming cloud fragments are 
@@
 at a given radius. 
+We also show the loci of constant surface densities in \Fig{MR}, parameterized through the visual extinction $A_V$.
 
@@
 That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the 
-fact that the MCs in our simulation have lower column density compared to the star-forming cores observed in the Milky Way, which are 
+fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are 
 observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
-% unresolved CO?detected molecular clouds in other galaxies should have an average A_V = 4 mag.
 
@@
 established based on \obs of the Milky Way.
+Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
 Star symbols are color-coded by increasing $n_{\rm cut}$.
 Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
-% \citep{Lombardi10a}.
+The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to 
+lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
 \label{fig:MR}}

### 2018-09-12 WRITEUP/ms.tex
clean up and hide toomre Q section for report

@@
 and structures seen in nearby and \z$>$\,0 galaxies.
-We present Toomre stability analysis in \Sec{Q}.
+% We present Toomre stability analysis in \Sec{Q}.
 We discuss the results % , robustness of our analysis, caveats, 
@@
 $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
-	Color shows the H$_2$ surface density, weighted by the column density. Specifically, this is calculated using \Eq{integrate}.
+	Color shows the H$_2$ surface density, weighted by the column density. 
 % 	\AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
@@
 in \Fig{MC} as an example.
-The plots shown in \Fig{MC} are weighted by the total gas density; that is, 
-\begin{equation}
-{\rm pixel_i} = \frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}, 
-\label{eqn:integrate}
-\end{equation} 
-where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
-to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
+The plots shown in \Fig{MC} are weighted by the column density of the total gas content.
+% equation below for bookkeeping: 
+% ${\rm pixel_i}$\eq$\frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}$,
+% where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt 
+% to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
 
@@
 rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
-We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
+% We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
 In the subsequent sections, we adopt the root mean square of the velocity field
@@
 The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
-the conventional wisdom that collapsing structures result from local gravitational
+the notion that collapsing structures result from local gravitational
 instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
@@
 
-\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
-The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
-and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
-For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
-of finite thickness $h$
-is described by:
-\begin{equation}
-\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
-\label{eqn:3Ddisp}
-\end{equation}
-where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
-The first term on the RHS describes rotation support, second term describes self-gravity, and
-the third term describes pressure support.
-The epicyclic frequency is defined as:
-\begin{equation}
-\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
-\label{eqn:kappa}
-\end{equation}
-% \kappa\propto\Omega
-One can then define the so-called Toomre-Q parameter/criterion for stability as
-\begin{equation}
-Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
-\label{eqn:Q}
-\end{equation}
-We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
-\begin{equation}
-\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
-\end{equation}
-Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
-and fragmentation can happen
-(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
-satellite galaxies and stellar feedback).
-That is, local fragmentation takes place when gravity overcomes pressure support
-from turbulence (thermal is small here) and shearing of differential rotation.
-
-In the limit of a thin rotating disk, rotation can help stabilizes
-self-gravitational contraction for wavelengths greater than the Toomre length:
-\begin{equation}
-\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
-\end{equation}
-yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
-which sets the ``upper limit'' to which MCs can form in a shearing disk.
-\DL{still yet to make the ``Q''-map}
-
-We overplot the MCs on the Toomre-Q map.
+%
+%\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
+%The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
+%and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
+%For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
+%of finite thickness $h$
+%is described by:
+%\begin{equation}
+%\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
+%\label{eqn:3Ddisp}
+%\end{equation}
+%where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
+%The first term on the RHS describes rotation support, second term describes self-gravity, and
+%the third term describes pressure support.
+%The epicyclic frequency is defined as:
+%\begin{equation}
+%\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
+%\label{eqn:kappa}
+%\end{equation}
+%% \kappa\propto\Omega
+%One can then define the so-called Toomre-Q parameter/criterion for stability as
+%\begin{equation}
+%Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
+%\label{eqn:Q}
+%\end{equation}
+%We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
+%\begin{equation}
+%\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
+%\end{equation}
+%Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
+%and fragmentation can happen
+%(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
+%satellite galaxies and stellar feedback).
+%That is, local fragmentation takes place when gravity overcomes pressure support
+%from turbulence (thermal is small here) and shearing of differential rotation.
+%
+%In the limit of a thin rotating disk, rotation can help stabilizes
+%self-gravitational contraction for wavelengths greater than the Toomre length:
+%\begin{equation}
+%\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
+%\end{equation}
+%yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
+%which sets the ``upper limit'' to which MCs can form in a shearing disk.
+%\DL{still yet to make the ``Q''-map}
+%
+%We overplot the MCs on the Toomre-Q map.
 

### 2018-10-25 WRITEUP/ms.tex
organization, shorten abstract

@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of Molecular Cloud Complexes in $z$\ssim6 Prototypical Galaxy
+\shorttitle{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
 }
@@
 \title{
-Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization
+Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
 }
@@
 \author{Andrea Ferrara\altaffilmark{4, 5}}
-\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7
-%mm, 8   [I only use the Drexel affiliation when working with folks
-%from there...]
-}}
+\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}
 
@@
 \altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
-%mm \altaffiltext{8}{Department of Physics, Disque Hall, Drexel University, Philadelphia, PA 19104, USA}
 
 \begin{abstract}
-We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
-at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
-We use a clump-finding algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
-to identify MCs and their sub-structures.
-We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
-for each MC and 
-compare them with those observed in the Milky Way disk, the Galactic center,
+We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in a prototypical galaxy (\flower)
+and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
+We use a clump-finding algorithm and H$_2$ density to identify MCs and their sub-structures.
+We compare the mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$)
+of each MC with those observed in the Milky Way, the Galactic center,
 and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
@@
 those observed in starburst galaxies.
-The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
+The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun.
+The $\sim$200\,pc-scale MCs found with a low density threshold
 correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
-The more massive and bigger MCs in \flower compared to the Milky Way 
+The velocity dispersion and gas surface density are found to be systematically higher than nearby galaxies
+regardless of the $n_{\rm cut}$ adopted, with $\sigma\gtrsim$\,100\,\kms.
+This likely results from the strong supernova and stellar feedback \flower experienced over multiple episodes of
+bursty \SF and constant cosmic gas inflows.
+Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
 likely result from the higher gas mass fraction, surface density, and velocity dispersion,
-which set the scale for fragmentation.
-The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted,
-with $\sigma\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
-the molecular substructures.
-The high velocity dispersions likely result from 
-the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
-Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
-This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
+which together sets the scale for fragmentation.
+Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters,
+ consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
 supported by turbulence and rotation on large scale.
@@
 due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
-MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
-as gas is being accreted from the intergalactic medium.
-We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
-Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
-mass distribution, which steepens with $n_{\rm cut}$. 
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
@@
 galaxy.
+{\bf AF: need aim and objectives of the study}
 
@@
 notwithstanding the limited numerical resolution of our simulation.
-That said, the Jeans mass $M_J$\eq$\sigma^4/(G^2\Sigma)$ yields $\sim$\,8\E{8}\,\Msun 
-for a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of 
-$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$, which are typical of the MCs of \flower.
-This Jeans mass is in agreement with the mass range found (see \Fig{dist}).
+That said, based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
+a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of
+$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$
+yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
+The enhanced MCs size-scale compared to local GMCs
+is therefore likely a manifestation of gravitational instabilities (resulting from the higher $f_{\rm gas}), which drives
+supersonic turbulence in the ISM.
 

### 2018-10-25 toomre.py
init Q_gas

@@ -1,0 +1,169 @@
+'''
+
+Toomre for gas component and stars and the effective combo of both
+
+'''
+
+import yt
+import numpy as np
+import cPickle as pickle
+import pymses
+from plot_modules.plot_cloud_prop import setup_plot
+setup_plot()
+from io_modules.manipulate_fetch_gal_fields import import_fetch_gal, prepare_unigrid, get_units
+
+# load camera stuff
+folder = 'precomputed_data/'
+f_camera = folder + 'camera_settings.log'
+
+with open(f_camera, 'rb') as f:
+    cameraDat = pickle.load(f)
+
+# prepare input data, if not already passed as arguments
+isnap = 28
+read_proper_unit = True
+
+if read_proper_unit:
+    import pymses
+    ro = pymses.RamsesOutput("output", isnap)
+    factor_vel = get_units(ro=ro)['vel'][0]
+    factor_rho = get_units(ro=ro)['rho'][0]
+    factor_R = get_units(ro=ro)['dx'][0] * 1.e-3
+    region_size = cameraDat[str(isnap)]['size']
+    region_size_kpc = region_size * factor_R
+else:
+    region_size_kpc = None
+
+data = import_fetch_gal(isnap=isnap)
+print data.keys()
+ds, dd = prepare_unigrid(data=data,
+                         add_unit=True,
+                         regionsize_kpc=region_size_kpc,
+                         debug=False)
+# ds: yt StreamDataset
+# dd: TYRegion
+print dd['density'].shape
+print dd['velx'].shape
+
+# def _vel(field, data):
+#     vel = np.c_[data['velx'], data['vely'], data['velz']]  # km/s
+#     return vel
+
+# ds.add_field(("velocity"), function=_vel)
+# # _dd = ds.all_data()
+# # print _dd['velocity']     # km/s
+
+# project velocity by mass-weighting, project surface density
+# axis : corresponding to the axis to slice along
+
+axes = {'0': 'x', '1': 'y', '2': 'z'}
+vel = {}
+projected_totalGasSurfaceDensity = {}
+coords = {}
+center_plane = {}
+
+xxx = dd["x"].reshape((224, 224, 224))
+yyy = dd["y"].reshape((224, 224, 224))
+zzz = dd["z"].reshape((224, 224, 224))
[…]

### 2018-10-25 call_resample_fields.py
resample star particle velocity

@@ -79,7 +79,7 @@ for ssnum in snapshotToLoad:
     if os.path.exists(outname):
         os.system('rm ' + outname)
 
-    camera = {'center': center,  
+    camera = {'center': center,
               'region_size': originalSize}
 
     loc_vec = ds['loc_vector']
@@ -87,13 +87,13 @@ for ssnum in snapshotToLoad:
     epoch_vec = ds['epoch']
     id_vec = ds['id']
     mass_vec = ds['mass']
+    vel_vec = ds['vel']
 
     import pymses
     ro = pymses.RamsesOutput("output", ssnum)
 
-    # resample star particle mass and compute mass-weighted avg epoch correspondingly                       
-    resample_star_mass_age(loc_vec, level_vec, epoch_vec, mass_vec, outname, camera, \
-                           old_dt_myr=100., young_dt_myr=10., ro_in=ro, Nrefined=N, debug=False)
+    # resample star particle mass and compute mass-weighted avg epoch correspondingly
+    resample_star_mass_age(loc_vec, level_vec, epoch_vec, mass_vec, vel_vec, outname, camera, old_dt_myr=100., young_dt_myr=10., ro_in=ro, Nrefined=N, debug=False)
 
     # ------ sanity check -- still in code units..
     f = h5py.File(outname, "r")
@@ -113,4 +113,4 @@ for ssnum in snapshotToLoad:
     assert mass.shape == H2density.shape
     assert mass.shape[0] == H2density.shape[0] == N
 
-    
+

### 2018-10-25 gridding_modules/locate_parts.py

@@ -12,8 +12,9 @@ import sys
 sys.path.append('../')
 
 
-def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector, \
-                           outname, camera, old_dt_myr=100., young_dt_myr=10., ro_in=None, Nrefined=None, debug=True):
+def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector,                       vel_vec, outname, camera, old_dt_myr=100.,
+                           young_dt_myr=10., ro_in=None, Nrefined=None,
+                           debug=True):
 
     """
 
@@ -47,7 +48,7 @@ def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector, \
         default: 10 Myr
 
     Nrefined: int
-       1D size of the resampled unigrid of the AMR stuff 
+       1D size of the resampled unigrid of the AMR stuff
 
     ro_in: pymses.RamsesOutput object
 
@@ -81,14 +82,14 @@ def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector, \
     bound_right  = center + originalSize/2.
 
     if Nrefined is None:
-        dx_vector = np.array(1/(np.e * levels_vec))        
+        dx_vector = np.array(1/(np.e * levels_vec))
         levels_uni  = np.unique(levels_vec)
 
         highestRes = 2.**(-levels_uni.max())
         N = int(originalSize / highestRes)
     else:
         N = int(Nrefined)
-    
+
     mass_cube = np.zeros((N, N, N))
     epoch_cube = np.zeros((N, N, N))
 
@@ -118,9 +119,9 @@ def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector, \
     #xx = np.array(xx, dtype=int)
 
     epoch_vec_universeAge = calculate_age_stars(ro_in=ro_in, dset_in={'epoch': epoch_vector})
-    mass_cube, epoch_universeAgeMyr_cube, young_cube, old_cube = grid_particle_mass(N, young_dt_myr, old_dt_myr, xx, mass_vector, epoch_vec_universeAge)
+    mass_cube, epoch_universeAgeMyr_cube, young_cube, old_cube, velx, vely, velz = grid_particle_mass(N, young_dt_myr, old_dt_myr, xx, mass_vector, epoch_vec_universeAge, vel_vec)
 
[…]

### 2018-10-25 call_resample_fields.py
save resampled vel of star particules for all snapshots

@@ -9,7 +9,6 @@ import os
 import numpy as np
 from gridding_modules.resample_fields import resam_each_field
 from gridding_modules.locate_parts import resample_star_mass_age
-import pickle
 import h5py
 import matplotlib.pyplot as plt
 
@@ -70,7 +69,6 @@ for ssnum in snapshotToLoad:
     plt.tight_layout()
     plt.savefig(plotdir + str(ssnum) + "_h2densityHist.png")
 
-
     # --- star particles ----
     # saved in call_fetch_gal_fields.py
     ds = np.load('snapshot' + str(ssnum) + '_center_stars.npz')
@@ -93,11 +91,20 @@ for ssnum in snapshotToLoad:
     ro = pymses.RamsesOutput("output", ssnum)
 
     # resample star particle mass and compute mass-weighted avg epoch correspondingly
+    N = 224
     resample_star_mass_age(loc_vec, level_vec, epoch_vec, mass_vec, vel_vec, outname, camera, old_dt_myr=100., young_dt_myr=10., ro_in=ro, Nrefined=N, debug=False)
 
     # ------ sanity check -- still in code units..
     f = h5py.File(outname, "r")
     mass = f['mass'].value
+
+    from io_modules.manipulate_fetch_gal_fields import get_units
+    ro = pymses.RamsesOutput("output", ssnum)
+    factor_vel = get_units(ro=ro)['vel'][0]
+    velx = f['velx'].value * factor_vel
+    vely = f['vely'].value * factor_vel
+    velz = f['velz'].value * factor_vel
+
     plt.figure()
     plt.imshow(np.log10(mass[:, :, :].sum(axis=0)))
     plt.tight_layout()
@@ -107,7 +114,6 @@ for ssnum in snapshotToLoad:
     plt.hist(np.log10(mass[mass > 1.e-23].flatten()), bins=100)
     plt.tight_layout()
     plt.savefig(plotdir + str(ssnum) + "_massCollapsedHist.png")
-
 
     # final sanity check of AMR and stellar field shapes
     assert mass.shape == H2density.shape

### 2018-10-25 call_resample_fields.py
doc

@@ -1,6 +1,6 @@
 '''
 
-Last mod: 24 July 2018
+Last mod: 25 Oct 2018
 
 
 '''
@@ -91,7 +91,6 @@ for ssnum in snapshotToLoad:
     ro = pymses.RamsesOutput("output", ssnum)
 
     # resample star particle mass and compute mass-weighted avg epoch correspondingly
-    N = 224
     resample_star_mass_age(loc_vec, level_vec, epoch_vec, mass_vec, vel_vec, outname, camera, old_dt_myr=100., young_dt_myr=10., ro_in=ro, Nrefined=N, debug=False)
 
     # ------ sanity check -- still in code units..

### 2018-10-25 io_modules/manipulate_fetch_gal_fields.py
pep8 and modified import_fetch_stars to read in particule velocity fields

@@ -7,11 +7,12 @@ last mod: 16 July 2018
 import numpy as np
 import pymses
 
+
 def get_dx(ssnum):
     # hard-code to get dx for now...
     # saved in fetch_gal_fields.py
     ro = pymses.RamsesOutput("output", ssnum)
-    ds = np.load('snapshot'+ str(ssnum) +'_center_fields0123456-15.npz')
+    ds = np.load('snapshot' + str(ssnum) + '_center_fields0123456-15.npz')
     dx_vector = ds['dx_vector']
 
     originalLevels = np.log2(1. / np.unique(dx_vector))
@@ -19,6 +20,7 @@ def get_dx(ssnum):
     # after finely sample unigrid
     dx_pc = highestRes * get_units(ro=ro)['dx'][0]
     return dx_pc
+
 
 def get_units(ro=None):
     from pymses.utils import constants as C
@@ -38,7 +40,8 @@ def get_units(ro=None):
 
     return dict_unit
 
-def import_fetch_gal(isnap=28, folder_ramsesdata='output', tag_h5file="_center_fields0123456-15_resampled.h5", verbose=True, convert = True):
+
+def import_fetch_gal(isnap=28, folder_ramsesdata='output', tag_h5file="_center_fields0123456-15_resampled.h5", verbose=True, convert=True):
 
     import pymses
     from pymses.utils import constants as C
@@ -66,26 +69,27 @@ def import_fetch_gal(isnap=28, folder_ramsesdata='output', tag_h5file="_center_f
     ro = pymses.RamsesOutput(folder_ramsesdata, isnap)
 
     if convert:
-      factor_density, unit_dens = get_units(ro=ro)['rho']      # 1/cm^3 (not H/cm^3)
-      density *= factor_density
-      if(verbose):
-          print 'max density'
-          print density.max(), unit_dens
+        factor_density, unit_dens = get_units(
+            ro=ro)['rho']      # 1/cm^3 (not H/cm^3)
+        density *= factor_density
+        if(verbose):
+            print 'max density'
+            print density.max(), unit_dens
 
-      factor_vel, unit_vel = get_units(ro=ro)['vel']
-      velx *= factor_vel
-      vely *= factor_vel
-      velz *= factor_vel
-      if(verbose):
-          print 'max vel'
-          print velx.max(), vely.max(), velz.max(), unit_vel
+        factor_vel, unit_vel = get_units(ro=ro)['vel']
+        velx *= factor_vel
[…]

### 2018-10-25 io_modules/manipulate_fetch_gal_fields.py
particles fields into yt dataframes

@@ -270,6 +270,40 @@ def prepare_unigrid(data, regionsize_kpc=7., verbose=False, add_unit=False, debu
     return ds, dd
 
 
+def prepare_star_unigrid(data, regionsize_kpc=7., verbose=False, add_unit=False, debug=False):
+
+    import yt
+    # prepare unigrid for stars
+    bbox_lim = regionsize_kpc / 2.
+    bbox = np.array([[-bbox_lim, bbox_lim],
+                     [-bbox_lim, bbox_lim],
+                     [-bbox_lim, bbox_lim]])
+
+    shape_data = data['velx'].shape
+
+    if add_unit:
+        data = dict(mass=(data['mass'], "Msun"),
+                    age=(data['epochMyr'], "Myr"),
+                    velx=(data['velx'], "km/s"),
+                    vely=(data['vely'], "km/s"),
+                    velz=(data['velz'], "km/s")
+                    )
+
+        ds = yt.load_uniform_grid(
+            data, shape_data, length_unit='kpc', bbox=bbox)
+    else:
+
+        ds = yt.load_uniform_grid(data, shape_data)
+
+    dd = ds.all_data()
+
+    if verbose:
+        print dd['velx'].max(), dd['velx'].min()
+        print dd['mass'].max(), dd['mass'].min()
+        print dd['epoch'].max(), dd['epoch'].min()
+    return ds, dd
+
+
 def check_hist_h2(data, th_list, ss=None, outdir='./'):
     """
 

### 2018-10-25 gridding_modules/locate_parts.py
clean

@@ -66,8 +66,6 @@ def resample_star_mass_age(loc_vector, levels_vec, epoch_vector, mass_vector,   
     from io_modules.pymses_helper import calculate_age_stars
     from pymses.utils import constants as C
 
-    outfieldnames = ['mass', 'epoch']
-
     # get the subregion
     center       = np.array(camera['center'])
     originalSize = np.array(camera['region_size'])

### 2019-03-01 WRITEUP/ms.tex
shorten abs, shuttle context according to AF's oct suggestion, edits on instability sec

@@
 \input{preamble}
-\slugcomment{Paper draft for the project developed at the Kavli Summer Program in Astrophysics 2018.
-To be Submitted.}
+\slugcomment{To be Submitted.}
 
@@
 \begin{abstract}
-We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in a prototypical galaxy (\flower)
+We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
 and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
-We use a clump-finding algorithm and H$_2$ density to identify MCs and their sub-structures.
-We compare the mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$)
-of each MC with those observed in the Milky Way, the Galactic center,
-and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
-The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to
-those observed in starburst galaxies.
-The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun.
-The $\sim$200\,pc-scale MCs found with a low density threshold
-correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
-The velocity dispersion and gas surface density are found to be systematically higher than nearby galaxies
-regardless of the $n_{\rm cut}$ adopted, with $\sigma\gtrsim$\,100\,\kms.
+We identify MCs using H$_2$ density, 
+and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
+with those observed in nearby and \z$\sim$\,2 galaxies.
+The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
+systematically higher than those observed in nearby galaxies but comparable to 
+starburst galaxies, with $\sigma\gtrsim$\,100\,\kms.
 This likely results from the strong supernova and stellar feedback \flower experienced over multiple episodes of
-bursty \SF and constant cosmic gas inflows.
+bursty \SF and cosmic gas inflows.
 Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
-likely result from the higher gas mass fraction, surface density, and velocity dispersion,
-which together sets the scale for fragmentation.
-Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters,
- consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
-supported by turbulence and rotation on large scale.
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback
-due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
+manifest from the higher gas mass fraction, surface density, and velocity dispersion.
+% , which together sets the scale for fragmentation.
+Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters,
+consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
+% , which are supported by turbulence and rotation on large scale.
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result from the weaker stellar feedback
+due to the less frequent \SF compared to \flower.
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
 Next Generation Very Large Array (ngVLA)
-will provide useful observational data to test our findings and the validity of our simulation to shed
+will furnish useful data to test our findings and simulation to shed
 light on \SF since the cosmic dark ages.
@@
 
-The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
-constraining the ISM conditions of galaxies and
-provide highly complementary information tracing the different phases of the ISM (ionized,
+The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are the key diagnostics for
+constraining the ISM conditions of a galaxy by
+providing highly complementary information that trace different phases of the ISM (ionized,
 atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
@@
 galaxies, using tracers such as
-dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
-Leung et al. 2018, submitted).
+dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
 These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
@@
 ionizing photons that reionized the Universe.
-
 While ALMA has enabled the detections of
@@
 state-of-the-art cosmological zoom-in hydrodynamic simulation
-\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), to examine
-the dynamical properties of the molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$)
-galaxy.
-{\bf AF: need aim and objectives of the study}
+\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), with a goal to examine
+and predict the dynamical properties of the star-forming molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$)
+galaxy. % to understand the physics behind \SF in the first galaxies.
 
 This paper is structured as follows.
-% \AP{TBM}
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
 and describe the method used to identify its molecular gas complexes.
-In \Sec{results}, we present scaling relations based on
-the MC identified and compare them with observations of molecular clouds
-and structures seen in nearby and \z$>$\,0 galaxies.
-% We present Toomre stability analysis in \Sec{Q}.
-We discuss the results % , robustness of our analysis, caveats,
-and implications of our findings in \Sec{diss},
+In \Sec{eqn}, we present the formalism within which we interpret the results.
+In \Sec{results}, we present scaling relations for the MCs identified. 
+% Toomre stability analysis in \Sec{Q}.
+We then interpret the results   % , robustness of our analysis, caveats,
+and discuss the implications of our findings in \Sec{diss},
 and present our conclusions in \Sec{conclusion}.
@@
 % ------------------
-\section{Method: Simulation and ``Clump''-finding} \label{sec:sim}
+\section{Simulation and Method} \label{sec:sim}
 
@@
 
-\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
+\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and
 adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
@@
 as a function of time.
-% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
-% {\DL or maybe in the discussion section?}
 This is advantageous especially at early cosmic epochs,
@@
 
-We show the \SF history of \flower in \Fig{SFH}, where
-the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
+We show the \SF history of \flower in \Fig{SFH},
+where the SFR is calculated based on existing young stellar population, which is
+defined to have an age of $t_{\rm age}<$\,10\,Myr.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
 The SFR plotted in Figure 2 of \citet{Pallottini17b}
@@
 as it evolves from an actively accreting phase to
-a starburst phase after a major merger, and then back to a relatively quiescent phase
-over the few hundred Myr simulated in our simulation.
-The SFR of \flower is calculated based on existing young stellar population, which is
-defined to have an age of $t_{\rm age}<$\,10\,Myr.
-
-Given the stochasticity in the \SF history of \flower,
-we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
-as examples in \Sec{singless} to illustrate the salient points of the discussion presented in this paper,
-since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
-most extreme variations in the cloud dynamics) --- one of which \flower is
-actively accreting materials from its surrounding
-and another of which \flower is undergoing
-a starburst phase after a major merger (see \Fig{SFH}).
+a starburst phase after a major merger, and then back to a relatively quiescent phase,
+over the few hundred Myr simulated in the simulation.
+
+Given the stochasticity in the \SF history of \flower (see \Fig{SFH}),
+we show the scaling relations found for two snapshots, corresponding to two of its most extreme evolutionary stages,
+in \Sec{singless} to illustrate the salient points of the discussion presented in this paper.
+The two phases (when \flower is accreting materials from its surrounding 
+and when \flower is undergoing a major starburst phase) are expected to bracket the most extreme variations in the cloud dynamics.
 
@@
  \centering
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_0.53}.pdf}
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
   \\ [-2.9em]
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_6.81}.pdf}
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
   \\ [-2.9em]
-  \includegraphics[scale=0.65]{\figpath/{dual_16_ncut_18.96}.pdf}
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
 \caption{
@@
 $n_{\rm cut}$ adopted and find no qualitative differences
-affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
+affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).}
 to the same snapshot
@@
 
-\section{Results: Cloud Scaling Relations}     \label{sec:results}
-
-%\AP{I see 2 main possible approaches to the presentation of the results
-%%
-%(a) focus on a single snapshot, analyze the cloud scaling relation by varying the cuts and then by varying the snapshot; after that one can discuss the stability/toomre analysis of the clumps (help in discussing the origin) and the CMF.
-%%
-%(b) discuss each scaling relation one at a time; probabily an introductionary subsection is needed to explain that different cuts yields no qualitative differences.
-%%
-%Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
-%%
-%I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g.
-the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
-%}
-%\DL{agreed, but will move things around later, after the report and after most of the content is ready.}
-
-Molecular clouds are the natal place for \SF, and thus,
-their structure and dynamics hold important clues to understanding
-the mechanisms and physics of formation and evolution of molecular structures and \SF.
+\section{Basic Physics} \label{sec:eqn}
+\subsection{Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
+% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
+Maybe we can put it as an appendix and keep only eq.
+10 in the main text (a put it at when analysing the relevant plot)?
+}
+
+% Relating Larson's law to stability and pressure (perhaps move this to other section?).
+A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
+a medium of pressure $P$ is described using the virial theorem:
+\begin{equation}
+\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
+\end{equation}
+where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
+$T$ is the volume term of the total kinetic energy (including thermal and
+bulk motions), $T_s$ is the surface term due to external pressure,
+$W$ is the gravity term, and $B$ is the magnetic term.
+In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
+\begin{equation}
+\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
+\label{eqn:virial}
+\end{equation}
+where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
+term is the gravity term, and the third term is the external pressure term.
+For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
+the LHS and the last term on the RHS vanish. The equation becomes:
+\begin{equation}
+\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
+\label{eqn:alpha}
+\end{equation}
+where $\Gamma$ is set to 3/5 for a uniform sphere.
+We can define
+\begin{equation}
+V_0^2\equiv\frac{\sigma^2}{R},
+\end{equation}
+which is related to one of the Larson's relations (linewidth-size relation),
+which can be recast into the form of:
+\begin{equation}
+\sigma^2/R = \pi G \Sigma/5.
+\end{equation}
+For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
+Equation~\ref{eqn:virial} becomes:
+\begin{equation}
+P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
+\label{eqn:pext}
+\end{equation}
+which describes the external pressure needed to confine the gas inside a volume $V$.
+Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
+this equation using the following:
+\begin{equation}
+\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
+\label{eqn:v0}
+\end{equation}
+Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
+$\sigma^2/R\propto\Sigma$, whereas
+Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
+needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
+In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$
+is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
+varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
+$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+
+We use the virial parameter, which is defined using \Eq{alpha} and describes
+the balance between kinetic and gravitational potential energies,
+to quantify how stable an MC is.
+An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms
+and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that
+the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
+
+\subsection{Gravitational Instabilities}   \label{sec:Q}
+The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
+From virial theorem, the Jeans 
+instability sets the scales at which gravitational potential overcomes kinetic energy. Namely, gravitational instabilities 
+dominates at scales $L > L_J$, where $L_J$ is the Jeans length. 
+However, in a differentially rotating system, centrifugal force resulting from differential rotation can 
+inhibit collapse even on these scales. Thus, a disk is unstable in the regime of $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
+% \propto \Sigma/B^2
+by the surface density of the disk and the angular velocity of the rotation.
+
+In theoretical and observational works, gravitational instability has been widely discussed in the 
+context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre Q parameter 
+(or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
+% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
+%
+% from linear analysis
+For {\it axisymmetric} mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
+of finite thickness $h$ 
+is described by:
+\begin{equation}
+\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
+\label{eqn:3Ddisp}
+\end{equation}
+where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
+\begin{equation}
+\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
+\label{eqn:kappa}
+\end{equation}
+% \kappa\propto\Omega
+The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and
+the third term describes pressure support.
+One can then define the so-called Toomre-Q parameter as:
+\begin{equation}
+Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
+\label{eqn:Q}
+\end{equation}
+For a thin disk, where $kh\ll1$, Equation~\ref{eqn:3Ddisp} reduces to the thin disk approximation, which 
+becomes unstable % perturbation grows exponentially in time
+for some $k$ when $\omega^2 < 0$ (or equivalently, $Q < 1$; \citealt{Toomre64a}).
+Under this condition (i.e., when local gravitational instability 
+overcomes support from pressure and rotation), fragmentation {\it can} happen. 
+% but further evolution depends on their EOS.
+%(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
+%satellite galaxies and stellar feedback).
+Similarly, for a collisionless fluid, the Toomre Q parameter is defined by:
+\begin{equation}
+Q\equiv\frac{\sigma\kappa}{3.36 G \Sigma}
+\end{equation}
+\citep{Toomre64a}.
+
+To account for stabilizing effect of both gas and stars and the non-negligible disk thickness, 
+% since thickness of a disk weakens the gravitational forces within the disk plane and lower the values for $Q$
+% Romeo:  The effect of thickness is to increase the stability parameter of each 
+% component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
+we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} which is 
+expressed as follows:
+\begin{equation}
+Q^{-1}_{\rm eff} = \[ \left\{
+				\begin{array}{lccr}
+					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
+                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\
+				\end{array} 
+			    \right,
+			    \]
+\end{equation}
+where $w$ is defined as:
+\begin{equation}
+w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
+\end{equation}
+and $T$ is defined as:
+\begin{equation}
+T\approx
+0.8+0.7\left(\frac{\sigma_{z}}{\sigma_{R}}\right)\,.
+\end{equation}
+
+\subsection{Key Properties of Clouds}
+
+% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
+% the mechanisms and physics of formation and evolution of molecular structures and \SF.
+In next section, we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
+describe interactions between gravity and turbulence and is the first set of
+relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
+density-size, and mass-size relations) and for comparing properties of molecular structures
+in different galactic environments.
+% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
+
 Upon identifying the molecular structures, we extract properties such as
@@
 snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).
+The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, 
+consistent with those observed in \z$\sim$2 galaxies in
+rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
 
@@
 
-In the following subsections,
-we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
-describe interactions between gravity and turbulence and is the first set of
-relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
-density-size, and mass-size relations) and for comparing properties of molecular structures
-in different galactic environments.
-% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
-Observations of nearby gas-rich galaxies such as M64 and NGC\,253
-show higher velocity dispersions compared
-to the disk/mid-plane of the Milky Way which are, on the other hand,
-more consistent with those observed in the inner regions of
-Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
-% which is $\propto\rho\sigma^2$
-% M51: Colombo+14
-While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
-to the inner regions of Milky Way, they are found to be bigger in size (approximately
-an order of magnitude) and mass (approximately two orders of magnitude).
-These bigger clouds have been interpreted as a results of their higher gas mass fractions and
-surface densities and velocity dispersions, since
-fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$
-and Jeans mass $M_J\propto\sigma^4/\Sigma$
-for dispersion-supported structures.
-
-\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
-% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
-Maybe we can put it as an appendix and keep only eq.
-10 in the main text (a put it at when analysing the relevant plot)?
-}
-
-% Relating Larson's law to stability and pressure (perhaps move this to other section?).
-A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
-a medium of pressure $P$ is described using the virial theorem:
-\begin{equation}
-\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
-\end{equation}
-where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
-$T$ is the volume term of the total kinetic energy (including thermal and
-bulk motions), $T_s$ is the surface term due to external pressure,
-$W$ is the gravity term, and $B$ is the magnetic term.
-In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
-\begin{equation}
-\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
-\label{eqn:virial}
-\end{equation}
-where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
-term is the gravity term, and the third term is the external pressure term.
-For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
-the LHS and the last term on the RHS vanish. The equation becomes:
-\begin{equation}
-\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
-\label{eqn:alpha}
-\end{equation}
-where $\Gamma$ is set to 3/5 for a uniform sphere.
-We can define
-\begin{equation}
-V_0^2\equiv\frac{\sigma^2}{R},
-\end{equation}
-which is related to one of the Larson's relations (linewidth-size relation),
-which can be recast into the form of:
-\begin{equation}
-\sigma^2/R = \pi G \Sigma/5.
-\end{equation}
-For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
-Equation~\ref{eqn:virial} becomes
-\begin{equation}
-P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
-\label{eqn:pext}
-\end{equation}
-which describes the external pressure needed to confine the gas inside a volume $V$.
-Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
-this equation using the following:
-\begin{equation}
-\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
-\label{eqn:v0}
-\end{equation}
-Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
-$\sigma^2/R\propto\Sigma$, whereas
-Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
-needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and
-\Fig{alpha27}).
-In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
-is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
-varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
-$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
-
-We use the virial parameter, which is defined using \Eq{alpha} and describes
-the balance between kinetic and gravitational potential energies,
-to quantify how stable an MC is.
-An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms
-and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that
-the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
-
-\subsection{MC Properties}
-\subsubsection{Single Snapshots}  \label{sec:singless}
-
-In each snapshot (see \Fig{MC} for example),
-we identify a set of MCs with consistently high turbulences and surface densities
-regardless of the H$_2$ density cuts adopted.
-These are the MCs at the center of the main disk of \flower and
+\section{Results: MC Properties and Cloud Scaling Relations}    \label{sec:results}
+\subsection{Single Snapshots}  \label{sec:singless}
+
+For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}),
+we identify a set of MCs. 
+Scaling relations for the MCs identified in the accretion phase are shown in top panels 
+of \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}, and in the bottom panels for the starburst phase.
+Regardless of the H$_2$ density cuts adopted,
+the MCs are found to have consistently high turbulences and surface densities in both stages.
+These correspond to MCs at the center of the main disk of \flower and
 occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-Their velocity dispersions are comparable to those observed in the inner Milky way and
-nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}),
-along the locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities are expected since
-they are located in the nuclear regions of the
-galaxy, where the potential well is also deeper. The higher velocity dispersions
-in these MCs can also be understood as they have experienced more recent episodes
-of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
-In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding
-to the top panels of \Fig{SFH} and \Fig{larsons_single}), \flower has assembled
-a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
-is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
-
-As we increase the density threshold, some of the MC within the main disk break
+As we increase the density threshold, some of the MCs within the main disk break
 into multiple sub-MCs.
-As such, we effectively identify a population of denser molecular structures (\Fig{MC}).
-This population of sub-MCs has dynamics largely
-similar to those observed
-in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
-terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
-e.g., \citealt{Swinbank11a}),
-with sizes of the order of $R\simeq$\,100\,pc and velocity
-dispersions of $\sigma\simeq$\,20$-$80\,\kms.
-As shown in the top panel of \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
-are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-%We note that previous studies by
-%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
-%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
+As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
 
@@
 We also compare the MCs identified in our simulations to
-those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of
-\Fig{alpha16}). The V-shaped dashed lines in the figure show the loci along which the given external pressures are needed for
+those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see \Fig{alpha27}). 
+The V-shaped dashed lines in the figure show the loci along which the given external pressures are needed for
 MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
@@
 Heyer+09).
-
-The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
-the notion that collapsing structures result from local gravitational
-instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
-which are supported by turbulence and rotation.
-In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
-the MC itself is gravitationally unbound and is supported
-by turbulence (from the feedback of multiple episodes of \SF)
-and galactic rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
-% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
-
-The MCs in the satellite galaxies are found to have
-lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
-with $\alpha_{\rm vir}\approx$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
-stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
-\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
-In addition, the MCs in the satellite galaxies follow the locus of
-$\log{(P/\textrm{K cm}^{-3})}$\eq6 (see bottom panel of \Fig{alpha16}).
-Given the low virial parameter and the $\sigma^2/R - \Sigma$ relation found for these MCs in the satellite galaxies,
-these structures are likely collapsing structures.
-This paints a picture, in which \SF continues as gas from the satellite galaxies are being accreted onto the main galaxies during the EoR.
+The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}).
 
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
+\caption{
+Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel) 
+and the starburst phase (bottom panel) compared to the 
+Milky Way (other symbols).
+Literature data are compiled from \citealt{Kauffmann17b} and references therein.
+Star symbols are color-coded by $n_{\rm cut}$.
+Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
+\label{fig:alpha16}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
 \includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
 \caption{
-Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way
-(other symbols).
-Literature data are compiled from \citealt{Kauffmann17b} and references therein.
-Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
+$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
+in the accretion phase (top panel) and the starburst phase (bottom panel)
 compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
@@
 are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
-In both panels, the star symbols are color-coded by $n_{\rm cut}$.
-Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel
-and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
-\label{fig:alpha16}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
-\caption{
-Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
+Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
+Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
+correspond to MCs in the satellite galaxies.
 \label{fig:alpha27}}
-\end{figure*}
-
-% -------------- all snapshots -----------
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28_PVE.png}
-\caption{
-Same as \Fig{alpha16}, but for MCs identified across all snapshots.
-Star symbols are color-coded by increasing SFR.
-\label{fig:alpha16-28}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
-\caption{
-Comparison of the MCs of \flower identified across all snapshots over the course of 700\,Myr (star symbols)
-to those observed in nearby and the \z$\sim$2 star-forming galaxy
-in the context of the linewidth-size relation --- showing variations in their properties at
-the different evolutionary phases of \flower and with varying SFRs.
-\label{fig:larsons16-28}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16-28-PVE-highncut.png}
-\caption{
-Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
-(i.e., MCs here are identified with the highest $n_{\rm cut}$).
-\label{fig:alpha16-28-highncut}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
-\caption{
-Same as \Fig{larsons16-28}, but only the denser substructures of the main disk of \flower are included
-(i.e., MCs here are identified with the highest $n_{\rm cut}$).
-\label{fig:larsons16-28-highncut}}
 \end{figure*}
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower in its accretion phase (see \Sec{sfh})
+We show in \Fig{MR} the size-mass relation of the MCs of \flower % in its accretion phase 
 compared to
@@
 Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
-\citet{Kauffmann10c} interpret this empirical relation
-as the threshold for massive \SF.
-The implication of this result is that cluster-forming cloud fragments are
-found to be more massive than those that are devoid of clusters
-at a given radius.
-We also show the loci of constant surface densities in \Fig{MR}, parameterized through the visual extinction $A_V$.
-
-As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus
-with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}, which
-% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
-is below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
-This can be understood by acknowledging the fact that a H$_2$ molecular cloud
-does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
-and that our simulation does not have enough resolution to directly form CO\footnote{
-In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we
-model the internal structure of MC within each cell in our simulation.}.
-That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the
-fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are
-observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
-
-Similar MC properties in relation to those observed in the nearby Universe are found during the starburst phase of
-\flower (see e.g., bottom panel of \Fig{larsons_single} and \Fig{alpha27}).
-On average, we do not find any quantitative differences in the MC properties in the accretion versus starburst phase.
+In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
+As shown in \Fig{MR}, the MCs identified 
+% in the accretion phase of 
+in \flower lie above this relation, along the locus
+with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
+We discuss this result in the following section.
 
@@
 
-\subsubsection{Cumulative Mass Distribution}   \label{sec:cmf}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/CMF_.png}
+Maps of the Toomre Q parameter of the gas component are shown in \Fig{Q} for 
+different projection angles during the accretion phase of \flower (see \Fig{h2density} for examples of clumps identified).
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_0}
 \caption{
-CMF of MCs in \flower and best-fit power law.
-\label{fig:cmf}}
-\end{figure}
-
-The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, which is
-consistent with those observed in \z$\sim$2 galaxies in
-rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-Observational studies in the nearby Universe, where
-spatially resolution are better at revealing molecular (sub-)structures,
-often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
-While the CMF of the MCs for a given snapshot of our simulation is
-quite noisy, since we have only one (main) galaxy,
-we can improve the ``signal-to-noise ratio'' by including
-MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
-the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
-We show the resulting CMF in \Fig{cmf}.
-
-Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
-\begin{equation}
-n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
-\end{equation}
-where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
-We find that
-the slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for the lowest and the highest $n_{\rm cut}$ adopted.
-The uncertainties are the formal fitting uncertainties.
-Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
-is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
-$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
-This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.
-
-%
-%\section{Origin of the clumps: Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
-%The onset of gravitational instability is considered to be tightly connected to (the conditions for) \SF \citep[e.g.,][]{Kennicutt89a, Li05b, Li06a}
-%and is widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}.
-%For axisymmetric mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk
-%of finite thickness $h$
-%is described by:
-%\begin{equation}
-%\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
-%\label{eqn:3Ddisp}
-%\end{equation}
-%where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency.
-%The first term on the RHS describes rotation support, second term describes self-gravity, and
-%the third term describes pressure support.
-%The epicyclic frequency is defined as:
-%\begin{equation}
-%\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
-%\label{eqn:kappa}
-%\end{equation}
-%% \kappa\propto\Omega
-%One can then define the so-called Toomre-Q parameter/criterion for stability as
-%\begin{equation}
-%Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
-%\label{eqn:Q}
-%\end{equation}
-%We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of
-%\begin{equation}
-%\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
-%\end{equation}
-%Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
-%and fragmentation can happen
-%(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
-%satellite galaxies and stellar feedback).
-%That is, local fragmentation takes place when gravity overcomes pressure support
-%from turbulence (thermal is small here) and shearing of differential rotation.
-%
-%In the limit of a thin rotating disk, rotation can help stabilizes
-%self-gravitational contraction for wavelengths greater than the Toomre length:
-%\begin{equation}
-%\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
-%\end{equation}
-%yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
-%which sets the ``upper limit'' to which MCs can form in a shearing disk.
-%\DL{still yet to make the ``Q''-map}
-%
-%We overplot the MCs on the Toomre-Q map.
+Maps of the total gas surface density (top left), 
+velocity dispersion (top right),
+epicyclic frequency (bottom left), 
+and Toomre Q parameter (bottom right) in the $xy$-plane.
+Modest smoothing has been applied to the maps. A divergent colormap is used for the Toomre Q map to facilitate 
+identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+\label{fig:Q}}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_1}
+\caption{Continued. Maps showing the various quantities projected in the $xz$-plane.}
+\addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_2}
+\caption{Continued. Maps show the various quantities projected in the $yz$-plane.}
+\end{figure*}
 
@@
 
-\subsection{Variation in MC Properties Depending on the Choice of Density Cuts and
-Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
-% single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
-to test
-the robustness of our results against the choice of density threshold by adopting
-different sets of $n_{\rm cut}$ in identifying the MCs.
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
-dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the snapshots and
-find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
-MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
-cloud scaling relations).
-In addition, for the densest MC in the main disk of \flower, we find that while
-its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
-its velocity dispersion remain
-approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
-This lack of variation is reassuring, in the sense that at least on the scales studied here,
-the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
-Our results are therefore robust to the various density cuts of choice.
-
-% temporal evolution in Cloud Dynamics
-We show the properties of all MCs identified across all snapshots
-in \Fig{alpha16-28}, \Fig{larsons16-28}, \Fig{alpha16-28-highncut},
-and \Fig{larsons16-28-highncut}.
-We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
-% \DL{This suggests that, at least ...., the ... of the cloud dynamics in \flower... over the timescale..}
+\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
+The population of sub-MCs has dynamics largely
+similar to those observed
+in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
+terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
+e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity
+dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+% velocity dispersion, larsons
+Their velocity dispersions are also comparable those observed in the inner Milky way and
+nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies
+along the locus of $\sigma\propto R^{0.56}$.
+Such high velocity dispersions and surface densities are expected since
+they are located in the nuclear regions of the
+galaxy, where the potential well is also deeper. The higher velocity dispersions
+in these MCs can also be understood as they have experienced more recent episodes
+of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
+In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding to an early phase of accretion as
+shown in \Fig{SFH}a), \flower has assembled
+a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
+is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
+
+% alpha parameters
+As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
+is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
+For the MCs in the satellite galaxies, a lower virial parameter is found 
+compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
+stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
+\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+% pext
+As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
+The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ of the sub-MCs
+compared to their parent MCs are consistent with
+the notion that collapsing structures result from local gravitational
+instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
+which are supported by turbulence and rotation on large scales.
+%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
+%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
+%and galactic rotation on large scales. 
+%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
+%Observationally, virial parameters of clouds form in the galactic disk
+%are found to have $\alpha_{\rm vir}$\eq0.2$-$10 \citep{Dobbs08a, Tasker09a}.
+
+For MCs in the satellite galaxies, we find low virial parameters and pressures, suggesting 
+that these structures are likely collapsing structures. 
+Their virial parameters are comparable with those found in clouds that are formed in the galactic disks 
+($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+Thus, \SF continues as gas from the satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+% mass-size relation
+In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, 
+which is an empirical relation corresponding to the threshold for massive \SF, but lies
+%The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
+%found to be more massive than those that are devoid of clusters
+%at a given radius.
+below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
+This can be understood by acknowledging the fact that a H$_2$ molecular cloud
+does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
+and that our simulation does not have enough resolution to directly form CO\footnote{
+In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we
+model the internal structure of MC within each cell in our simulation.}.
+That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the
+fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are
+observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
+
+% different evolutionary stages
+In the scaling relations examined, we find similar MC properties 
+in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of
+\flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
+That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which
+are separated by $\seq$300\,Myr.
 
 \subsection{Origin of the MCs} \label{sec:origin} 
-The largest molecular structure identified is essentially the main disk of \flower which breaks down into smaller
-substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28} and \Fig{larsons16-28-highncut}). In any case,
+\DL{discuss stuff on Toomre Q maps with clumps identified.}
+
+The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
+substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). In any case,
 the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
@@
 
-The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the
-molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
+The high pressure observed in \flower is comparable to what has been observed in local ULIRGs; however, the
+molecular clouds in the latter are concentrated within their 
+central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
 \citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
@@
 
-\subsection{Virial Parameter, Collapse, and high SFR at high-\z}
-
-While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
+\subsection{Virial Parameter, Collapse, and high SFR at high-\z} \label{sec:diss2}
+
+It may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
 nature of the majority of the molecular gas in \flower and its SFR.
@@
 
-\subsection{MC Dynamics and CMF and IMF at EoR}
-
-% interpretation
-Velocity dispersion and surface density are tightly connected to pressure.
-That is, the pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and
-since $P\propto\Sigma^2$).
-In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of
-$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
-The higher $\Sigma_{\rm gas}$ in turn is related to more massive clouds being formed.
-In M64 and M51, there are a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun \citep{Rosolowsky05a, Koda09a, Colombo14a}.
-On the other hand, such massive molecular structures are unknown to Local Group galaxies
-\citep[e.g.,][]{Rice16a}, and are likely the sites
-from which massive star clusters or OB associations are to be formed.
-%
-The shallower slope found in the CMF for \flower compared to those observed in the nearby Universe (see \Sec{cmf}) may
-suggest that the MCs of \flower are more massive compared to those observed in the nearby Universe,
-notwithstanding the limited numerical resolution of our simulation.
-That said, based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
+\subsection{MC Dynamics Setting the Mass Scale at EoR} \label{sec:diss3}
+
+%% pressure
+%The pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and
+%since $P\propto\Sigma^2$).
+%In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of
+%$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
+%The higher $\Sigma_{\rm gas}$ is in turn relates to more massive clouds being formed.
+%In fact, a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun 
+%are found in nearby gas-rich galaxies such as M64 and M51 \citep{Rosolowsky05a, Koda09a, Colombo14a}.
+%%On the other hand, such massive molecular structures are unknown to Local Group galaxies
+%%\citep[e.g.,][]{Rice16a}, and are likely the sites
+%%from which massive star clusters or OB associations are to be formed.
+%{\bf So?}
+
+% mass scale
+Observations of nearby gas-rich galaxies such as M64 and NGC\,253
+show higher velocity dispersions compared
+to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of
+Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
+% which is $\propto\rho\sigma^2$
+% M51: Colombo+14
+However, clouds in nearby gas-rich galaxies are bigger in size (approximately
+an order of magnitude) and mass (approximately two orders of magnitude).
+These bigger clouds have been interpreted as a results of their 
+higher gas mass fractions and
+surface densities and velocity dispersions, since
+fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$
+and Jeans mass $M_J\propto\sigma^4/\Sigma$
+for dispersion-supported structures.
+
+Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
 a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of
@@
 The enhanced MCs size-scale compared to local GMCs
-is therefore likely a manifestation of gravitational instabilities (resulting from the higher $f_{\rm gas}), which drives
+is therefore likely a manifestation of gravitational instabilities (resulting from the higher $f_{\rm gas}$), which drives
 supersonic turbulence in the ISM.
 
-% CMF and IMF
-The CMF is related to the mass function of stars (IMF),
-since the former describes the mass distribution of
-the materials for \SF (see e.g., \citet{McKee07a} for a review).
-Observational studies of a diverse range of environments suggest that the IMF is invariant
-between star-forming regions, star clusters, and spiral galaxies
-(see a review by \citealt{Bastian10a}; see also \citealt{Bochanski10a, AlvesdeOliveira13a, Calamida15b}), but is subject
-to variation under extreme conditions (e.g., temperatures, densities, and radiation field intensities), such as
-in the Galactic center (e.g., \citealt{Lu13a, Conroy13a}).
-Speculatively, the different CMF slope found in \flower may suggest a different IMF compared to those observed in nearby galaxies.
-In particular, the steeper slope may indirectly translate into a top-heavy IMF (see \citealt{Alves07a, Anathpindika11a}), which is commonly assumed in most \highz studies to date\footnote{Since intuitively, we expect a higher Jeans mass at higher redshift, due to the lower metallicities and higher temperature
-expected in these first galaxies.}.
-
-% a bit on caveat
-One should, however, keep in mind that
-the slope of the CMF reported here is subject
-to the uncertainties in the analysis method and limitations in the numerical resolution of our simulation.
-That is, we are likely biased to finding more massive clouds due to resolution effects;
-it is possible that we may identify more less massive MCs if our simulation
-was done at a higher resolution.
-That said, one must acknowledge that such a zoom-in simulation
-is currently quite expensive to perform with
-existing computational power. %, given the complexity of the physics invoked as input.
-In any case, similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
+Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
 simulations done at higher resolution (e.g., \citealt{Behrendt16a}).
@@
 This is consistent with what has been found previously in higher resolution idealized simulation of isolated galaxies.
-That said, our cosmological zoom-in simulation here allows us to examine
-the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
+Our simulation here confirms these results at EoR and under
+the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
 
 We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
-The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
+The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the 
+density threshold $n_{\rm cut}$ adopted in identifying the structures.
 Our results are thus insensitive to the various density cuts of choice.
 %However, our results are dependent on the numerical resolution of the simulation.
-The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for
-the molecular substructures.
+The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the 
+density threshold and even for the molecular substructures.
 Such a high velocity dispersion likely results from
 the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
+
 Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter.
@@
 experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
-MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues
-as gas is being accreted from the IGM.
-
-We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined.
-Our results are independent of the volume density threshold adopted, except for the slope of the cumulative
-mass distribution, which steepens as we increase $n_{\rm cut}$.
+MCs in the satellites are therefore likely collapsing structures.
+
+We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, 
+at least in terms of the scaling relations examined.
+Our results are robust against the H$_2$ volume density threshold adopted (see Appendix \Sec{ncut}).
 
@@
 in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
-High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics and is subject to the input model/sub-grid models adopted,
-provide an avenue to examine and postulate/make testable predictions on the morphology and dynamics of
-the multi-phase ISM structures of the first galaxies and their satellite galaxies.
-High resolution imaging of the molecular gas content in the first galaxies with ALMA and the ngVLA, on the other hand,
-have the potential to provide useful observational data to test our findings and the validity of our simulation to shed
-light on \SF since the cosmic dark ages.
+Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
+statistics and is subject to the sub-grid models adopted, 
+serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
+the multi-phase ISM structures of the first galaxies.
+These predictions can in turn be
+tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA,
+enabling us to test our findings and refine future simulations to shed light on the physical processes behind 
+\SF since the cosmic dark ages.
 
@@
 
-% \DL{to update}
-%\appendix
-%\section{Schmidt-Kennicutt Relation}
-%As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
-%We show in \Fig{sk} the MCs of \flower identified in the accretion phase using different $n_{\rm cut}$
-%(see \Sec{sfh} for details) and those reported in nearby and \highz \obs \citep{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a}.
-%
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
-%\caption{
-%SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those
-%observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
-%Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and
-%\citealt{Pallottini17b}.
-%%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b}
-%%and references therein, and Sharon et al. in prep.
-%\label{fig:sk}}
-%\end{figure*}
-%
-
-%
-
-%
+\appendix
+\section{Variation in MC Properties Depending on the Choice of Density Cuts and
+Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
+% single Snapshot
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
+to test
+the robustness of our results against the choice of density threshold by adopting
+different sets of $n_{\rm cut}$ in identifying the MCs.
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
+dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the snapshots and
+find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
+MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+cloud scaling relations).
+In addition, for the densest MC in the main disk of \flower, we find that while
+its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
+the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+This lack of variation is reassuring, in the sense that at least on the scales studied here,
+the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+Our results are therefore robust to the various density cuts of choice.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCs identified across all snapshots
+in \Fig{larsons16-28} and \Fig{alpha16-28}.
+We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+
+% -------------- all snapshots -----------
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 100 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
+\caption{
+Comparison of MCs identified across all snapshots (over 700\,Myr; star symbols)
+to those observed in nearby and \z$\sim$2 star-forming galaxies
+in the context of the linewidth-size relation.
+% showing variations in their properties at
+% the different evolutionary phases of \flower and with varying SFRs.
+Bottom panel corresponds to including only the denser substructures/sub-MCs identified in \flower
+(i.e., MCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+By and large, we find no quantitative differences in the mass-size relation over the 700\,Myr traced in the simulation.
+\label{fig:larsons16-28}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\caption{
+Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCs identified across all snapshots 
+(i.e., with different SFR). Star symbols are color-coded by increasing SFR.
+Right panels correspond to including only the denser substructures/sub-MCs identified in \flower
+(i.e., MCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+We find no obvious differences in relation to those observed in nearby and \highz 
+galaxies in the context of these cloud scaling relations.
+\label{fig:alpha16-28}}
+\end{figure*}
+
 \end{document}

### 2019-03-04 toomre.py
convert code into an object

@@ -16,475 +16,667 @@ from scipy.ndimage.filters import gaussian_filter
 
 from matplotlib import cm
 cmap = cm.get_cmap('viridis')
+cmap_div = cm.get_cmap('RdBu')         # divergent cmap
 
 from pymses.utils import constants as C_py
 from yt import units as C_yt
 import astropy.constants as C_ap
 import astropy.units as U
-kg2Msun  = 1. / 1.989E30
-kg2g     = 1.E+03
-pc2cm    = 3.086e18
-J2erg    = 1.E+07
-k_B_erg  = C_ap.k_B.value * J2erg
-g2Msun   = 1 / 1.989e33
-cm2pc    = 1 / pc2cm
-
-
-# load camera stuff
-folder = 'precomputed_data/'
-f_camera = folder + 'camera_settings.log'
-
-with open(f_camera, 'rb') as f:
-    cameraDat = pickle.load(f)
-
-# prepare input data, if not already passed as arguments
-isnap = 16
-read_proper_unit = True
-
-
-wg_var = 'density'
-
-if read_proper_unit:
-    import pymses
-    ro = pymses.RamsesOutput("output", isnap)
-    factor_vel = get_units(ro=ro)['vel'][0]
-    factor_rho = get_units(ro=ro)['rho'][0]
-    factor_R = get_units(ro=ro)['dx'][0] * 1.e-3
-    region_size = cameraDat[str(isnap)]['size']
-    region_size_kpc = region_size * factor_R
-else:
-    region_size_kpc = None
-
-data = import_fetch_gal(isnap=isnap)
-print data.keys()
-ds, dd = prepare_unigrid(data=data,
-                         add_unit=True,
-                         regionsize_kpc=region_size_kpc,
-                         debug=False)
-# ds: yt StreamDataset
-# dd: TYRegion
-
-n_bins = int(np.ceil(len(dd['density'])**(1. / 3)))
-xxx = dd["x"].reshape((n_bins, n_bins, n_bins))
-yyy = dd["y"].reshape((n_bins, n_bins, n_bins))
-zzz = dd["z"].reshape((n_bins, n_bins, n_bins))
-center = dd.get_field_parameter('center')
-
-# project velocity by mass-weighting, project surface density
[…]

### 2019-03-05 WRITEUP/ms.tex
edit def of T; updated abstract

@@
 starburst galaxies, with $\sigma\gtrsim$\,100\,\kms.
-This likely results from the strong supernova and stellar feedback \flower experienced over multiple episodes of
-bursty \SF and cosmic gas inflows.
+% Toomre Q
+We compute the effective two-component Toomre Q parameter (gas and stars) to examine 
+regions that are unstable to local axisymmetric perturbations. 
+We further perform virial analysis, which is observable, to examine collapsing regions.
+Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its 
+substructures have lower virial parameters,
+consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
+% , which are supported by turbulence and rotation on large scale.
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, 
+which we interpret as result from the weaker stellar feedback
+due to the less frequent \SF compared to \flower.
 Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
@@
 % , which together sets the scale for fragmentation.
-Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters,
-consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
-% , which are supported by turbulence and rotation on large scale.
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result from the weaker stellar feedback
-due to the less frequent \SF compared to \flower.
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
 Next Generation Very Large Array (ngVLA)
-will furnish useful data to test our findings and simulation to shed
-light on \SF since the cosmic dark ages.
+will furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
 \end{abstract}
@@
 \end{equation}
-For a thin disk, where $kh\ll1$, Equation~\ref{eqn:3Ddisp} reduces to the thin disk approximation, which 
+For $kh\ll1$, Equation~\ref{eqn:3Ddisp} reduces to the thin disk approximation, which 
 becomes unstable % perturbation grows exponentially in time
@@
 % component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
-we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} which is 
-expressed as follows:
+we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a, Inoue16a}
+which is expressed as follows:
 \begin{equation}
@@
 \end{equation}
-and $T$ is defined as:
-\begin{equation}
-T\approx
-0.8+0.7\left(\frac{\sigma_{z}}{\sigma_{R}}\right)\,.
+and $T$ is approximated as:
+\begin{equation}
+T = \[ \left\{
+		\begin{array}{lccr}
+			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [0.75em]
+			{\dispalystyle 1 + 0.6 \left(\frac{\sigma_z}{\sigam_r}\right)}             & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
+\\
+		\end{array}
+		\right.
+		\]
 \end{equation}

### 2019-03-05 WRITEUP/ms.tex
refine abstract again

@@
 The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
-systematically higher than those observed in nearby galaxies but comparable to 
-starburst galaxies, with $\sigma\gtrsim$\,100\,\kms.
-% Toomre Q
+systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
 We compute the effective two-component Toomre Q parameter (gas and stars) to examine 
 regions that are unstable to local axisymmetric perturbations. 
-We further perform virial analysis, which is observable, to examine collapsing regions.
-Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its 
-substructures have lower virial parameters,
+We further perform virial analysis, which is accessible from observations, to examine regions likely to be undergo collapse.
+Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
+substructures have lower virial parameters, which is
 consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
 % , which are supported by turbulence and rotation on large scale.
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, 
-which we interpret as result from the weaker stellar feedback
-due to the less frequent \SF compared to \flower.
-Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
+On the other hand, we find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
+which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
+Our results suggest that the more massive and bigger MCs compared to the Milky Way
 manifest from the higher gas mass fraction, surface density, and velocity dispersion.
@@
 Next Generation Very Large Array (ngVLA)
-will furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
+can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
 \end{abstract}

### 2019-03-05 toomre.py
two comp, thickness effective Q

@@ -15,7 +15,7 @@ import matplotlib.pyplot as plt
 from scipy.ndimage.filters import gaussian_filter
 
 from matplotlib import cm
-cmap = cm.get_cmap('viridis')
+cmap = cm.get_cmap('viridis')          # 'magma'
 cmap_div = cm.get_cmap('RdBu')         # divergent cmap
 
 from pymses.utils import constants as C_py
@@ -670,6 +670,185 @@ class ToomreAnalyze(object):
     return self.Q
 
 
+
+class ToomreAnalyze_2comp(object):
+  """
+
+  Toomre for gas + star in thick disk
+
+  """
+  def __init__(self, Q_gas, Q_star):
+
+    """
+
+    Calculates the combined Toomre Q parameter
+
+    Take into account the finite thickness of the disk
+    and that the gas and stars independently contribute to the gravitational
+    potential.
+
+    See Romeo & Wiegert (2011) [2011MNRAS.416.1191R] for details
+    http://adsabs.harvard.edu/abs/2011MNRAS.416.1191R
+
+    Parameters
+    ----------
+    Q_gas and Q_star are objects
+
+
+    """
+
+    self.debug = Q_gas.debug or Q_star.debug
+    self.Q_star_val = Q_star.Q
+
+    self.Q_gas = Q_gas
+    self.Q_star = Q_star
+
+    assert self.Q_gas.plane == self.Q_star.plane
+    self.plane = self.Q_gas.plane
+
+    assert self.Q_gas.isnap == self.Q_star.isnap
+    self.isnap = self.Q_gas.isnap
+
+    self.interpolate_gas_onto_star_grid()
+
+
+  def interpolate_gas_onto_star_grid(self):
+    from scipy import interpolate
+
+    xx = np.linspace(self.Q_gas.coords[self.plane][0].value.min(), self.Q_gas.coords[self.plane][0].value.max(), len(self.Q_gas.coords[self.plane][0]))
+    yy = np.linspace(self.Q_gas.coords[self.plane][1].value.min(), self.Q_gas.coords[self.plane][1].value.max(), len(self.Q_gas.coords[self.plane][1]))
+
+    f = interpolate.interp2d(xx,
+                             yy,
+                             self.Q_gas.Q,
+                             kind='cubic')
+    Q_gas_resampled = f(xx, yy)
[…]

### 2019-03-05 WRITEUP/ms.tex
edited up to sec 5.2

@@
 systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
-We compute the effective two-component Toomre Q parameter (gas and stars) to examine 
+We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine 
 regions that are unstable to local axisymmetric perturbations. 
@@
     Star formation history of \flower (top right) and
-    projected stellar mass distribution of \flower during one of its accretion phases
-    at its early stage of evolution {\it (a)}; during one of its major starburst phases
-    after a major merger {\it (b)}; and in a relatively quiescent phase post-starburst {\it (c)}.
+    projected stellar mass distribution of \flower during 
+    {\it (a)} one of its accretion phases
+    at its early stage of evolution; 
+    {\it (b)} one of its major starburst phases
+    after a major merger; and
+    {\it (c)} a relatively quiescent phase post-starburst.
 % f_gas history?
@@
 
-We use the virial parameter, which is defined using \Eq{alpha} and describes
+We use the virial parameter, which is defined by \Eq{alpha} and describes
 the balance between kinetic and gravitational potential energies,
@@
 The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-From virial theorem, the Jeans 
+From virial theorem, Jeans 
 instability sets the scales at which gravitational potential overcomes kinetic energy. Namely, gravitational instabilities 
@@
 However, in a differentially rotating system, centrifugal force resulting from differential rotation can 
-inhibit collapse even on these scales. Thus, a disk is unstable in the regime of $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
+inhibit collapse even on these scales. Thus, a disk is thought to be 
+unstable on scales of $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
 % \propto \Sigma/B^2
@@
 In theoretical and observational works, gravitational instability has been widely discussed in the 
-context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre Q parameter 
+context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter 
 (or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
@@
 %satellite galaxies and stellar feedback).
-Similarly, for a collisionless fluid, the Toomre Q parameter is defined by:
+Similarly, for a collisionless fluid, the Toomre $Q$ parameter is defined by:
 \begin{equation}
@@
 % component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
-we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a, Inoue16a}
-which is expressed as follows:
+we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} and
+\citet{Inoue16a} which is expressed as follows:
 \begin{equation}
@@
 		\begin{array}{lccr}
-			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [0.75em]
-			{\dispalystyle 1 + 0.6 \left(\frac{\sigma_z}{\sigam_r}\right)}             & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
+			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
+			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r 
 \\
 		\end{array}
-		\right.
+	\right \rlap{.}
 	\]
 \end{equation}
+
+For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the importance of support against axisymmetric perturbations from galactic rotation and shear in the extracted velocity dispersions of the MCs in \Sec{origin}.
+\DL{so does the extracted velocity disp. has a contribution from shear or is it just pressure? I thought we have concluded 
+that it is just high pressure leading to the high velocity disp, but not because of diff. rotation. It's not clear to me how 
+the Toomre $Q$ map is helpful to inform us on how much of the extracted velo. disp. is coming from diff. rotation.}
 
@@
 % the mechanisms and physics of formation and evolution of molecular structures and \SF.
-In next section, we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which
-describe interactions between gravity and turbulence and is the first set of
-relations used for studying star-forming molecular structure formation based on observables (linewidth-size,
-density-size, and mass-size relations) and for comparing properties of molecular structures
-in different galactic environments.
+In next section, we examine and compare properties of the MCs with
+observations in the context of the Larson's relations \citep{Larson81a}. 
+Namely, the linewidth-size, density-size, and mass-size relations.
+Larson's relations are adopted for the discussion in this work as they 
+describe the interactions between gravity and turbulence, and is the first set of
+relations used for studying star-forming molecular structure formation based on observables
+which has been routinely used for comparing properties of molecular structures in different galactic environments.
 % Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
@@
 \end{equation}
-The local sound speed ($c_s$)
-of all identified molecular complexes are generally much smaller compared to the their
+The local sound speed of all identified molecular complexes are much smaller compared to the their
 turbulent velocities\footnote{We find comparable velocity dispersion between that derived from
@@
 
-Maps of the Toomre Q parameter of the gas component are shown in \Fig{Q} for 
-different projection angles during the accretion phase of \flower (see \Fig{h2density} for examples of clumps identified).
+Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified
+in this snapshot).
 
@@
 epicyclic frequency (bottom left), 
-and Toomre Q parameter (bottom right) in the $xy$-plane.
-Modest smoothing has been applied to the maps. A divergent colormap is used for the Toomre Q map to facilitate 
+and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
+Modest smoothing has been applied to the maps. A divergent colormap is used for the Toomre $Q$ map to facilitate 
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
@@
 ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-Thus, \SF continues as gas from the satellite galaxies is being accreted onto the main galaxies during the EoR.
+Thus, this would suggest 
+\SF continues as gas from the satellite galaxies is being accreted onto the main galaxies during the EoR.
 
@@
 \subsection{Origin of the MCs} \label{sec:origin} 
-\DL{discuss stuff on Toomre Q maps with clumps identified.}
+\DL{discuss stuff on Toomre $Q$ maps with clumps identified.}
 

### 2019-03-05 WRITEUP/ms.tex
minor text edit

@@
 regions that are unstable to local axisymmetric perturbations. 
-We further perform virial analysis, which is accessible from observations, to examine regions likely to be undergo collapse.
+We further perform virial analysis, which is accessible from observations, to examine regions likely 
+to undergo collapse.
 Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
@@
 dominates at scales $L > L_J$, where $L_J$ is the Jeans length. 
-However, in a differentially rotating system, centrifugal force resulting from differential rotation can 
-inhibit collapse even on these scales. Thus, a disk is thought to be 
-unstable on scales of $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
+However, centrifugal force resulting from differential rotation in disk galaxies can 
+inhibit collapse even on these scales. As a result, a disk is thought to be 
+unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
 % \propto \Sigma/B^2
@@
 %satellite galaxies and stellar feedback).
+% Note that fragmentation is expected to happen at critical scale length 
+% $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of 
+% GMCs. It should be clear that the instability sets the scales for fragmentation, but 
+% star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales.
+% The fragmented structures thus correspond to regions where $Q\lesssim1.
 Similarly, for a collisionless fluid, the Toomre $Q$ parameter is defined by:
@@
 
-For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the importance of support against axisymmetric perturbations from galactic rotation and shear in the extracted velocity dispersions of the MCs in \Sec{origin}.
-\DL{so does the extracted velocity disp. has a contribution from shear or is it just pressure? I thought we have concluded 
-that it is just high pressure leading to the high velocity disp, but not because of diff. rotation. It's not clear to me how 
-the Toomre $Q$ map is helpful to inform us on how much of the extracted velo. disp. is coming from diff. rotation.}
+For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the 
+importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
 
@@
 In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion ($\sigma$).}.
+as the velocity dispersion ($\sigma$). \label{ftn:veldisp}}.
 On average, the Mach number of the MCs corresponds to about $\mathcal{M}\approx50$.
@@
 Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified
-in this snapshot).
+in this snapshot). Fragmentation are expected in regions of low-$Q$. 
+Further interpretation and implication of this is discussed in \Sec{origin}.
 
@@
 and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
-Modest smoothing has been applied to the maps. A divergent colormap is used for the Toomre $Q$ map to facilitate 
+Modest smoothing has been applied to the maps. 
+A divergent colormap is used for the Toomre $Q$ map to facilitate 
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
@@
 % velocity dispersion, larsons
-Their velocity dispersions are also comparable those observed in the inner Milky way and
+Their velocity dispersions are also comparable to those observed in the inner Milky way and
 nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies
@@
 they are located in the nuclear regions of the
-galaxy, where the potential well is also deeper. The higher velocity dispersions
-in these MCs can also be understood as they have experienced more recent episodes
+galaxy, where the potential well is also deeper. The higher velocity dispersions (see also 
+footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp})
+of these MCs can also be understood as they have experienced more recent episodes
 of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).

### 2019-03-05 WRITEUP/ms.tex
moved around text in 5.2 and 5.1

@@
 Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified
-in this snapshot). Fragmentation are expected in regions of low-$Q$. 
+in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
 Further interpretation and implication of this is discussed in \Sec{origin}.
@@
 \subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
+
 The population of sub-MCs has dynamics largely
@@
 
-% alpha parameters
-As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
-is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-For the MCs in the satellite galaxies, a lower virial parameter is found 
-compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
-stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
-\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
-% pext
-As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
-The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ of the sub-MCs
-compared to their parent MCs are consistent with
-the notion that collapsing structures result from local gravitational
-instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
-which are supported by turbulence and rotation on large scales.
-%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
-%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
-%and galactic rotation on large scales. 
-%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
-%Observationally, virial parameters of clouds form in the galactic disk
-%are found to have $\alpha_{\rm vir}$\eq0.2$-$10 \citep{Dobbs08a, Tasker09a}.
-
-For MCs in the satellite galaxies, we find low virial parameters and pressures, suggesting 
-that these structures are likely collapsing structures. 
-Their virial parameters are comparable with those found in clouds that are formed in the galactic disks 
-($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-Thus, this would suggest 
-\SF continues as gas from the satellite galaxies is being accreted onto the main galaxies during the EoR.
+The high pressure observed in \flower is comparable to what has been 
+observed in local ultra-luminous IR galaxies (ULIRGs); however, the
+molecular clouds in the latter are concentrated within their 
+central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun
+\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
+found throughout the disk. This difference likely stems from the different physical mechanisms giving rise
+to the formation (and thus the nature) of these molecular structures.
+For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud
+collision after large amount of gas from the pair of progenitor galaxies
+are being funneled toward the central region \citep{Tan00a, Wu18a}.  % Tasker09a
+On the other hand, the highly turbulent structures of \flower likely result from 
+constant cold gas accretion onto the entire galaxy (without
+requiring gas to be funneled into the central region).
+This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed
+in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed 
+size scales could also result from resolution limit where the true physical scales of MCs in
+$z$\,\ssim2 galaxies could be smaller in reality.
+The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
+the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is 
+consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
 
@@
 That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which
-are separated by $\seq$300\,Myr.
+are separated by $\simeq$300\,Myr.
 
@@
 The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
-substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). In any case,
-the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
-those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
-
-The high pressure observed in \flower is comparable to what has been observed in local ULIRGs; however, the
-molecular clouds in the latter are concentrated within their 
-central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
-\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
-found throughout the disk. This difference likely stems from the different physical mechanisms giving rise
-to the formation (and thus the nature) of these molecular structures.
-For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud
-collision after the large amount of gas from the progenitor galaxy merger
-is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
-whereas in \flower, which is actively accreting gaseous materials
-from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without
-requiring gas to be funneled into the central region).
-This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed
-in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}).
-The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
-the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the
-high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
+substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). Overall,
+the MCs we identified are much bigger in size and mass than nearby GMCs, 
+but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
+
+Note that ....
 

### 2019-03-06 WRITEUP/ms.tex
updated Sec 5 altogether

@@
 
-Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Q_eff}, respectively (see \Fig{h2density} for examples of clumps identified
+Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Qeff}, respectively (see \Fig{h2density} for examples of clumps identified
 in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
@@
 
-\subsection{Origin of the MCs} \label{sec:origin} 
-\DL{discuss stuff on Toomre $Q$ maps with clumps identified.}
-
+\subsection{Origin and Physical Scales of the MCs} \label{sec:origin} 
 The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
@@
 but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
-
-Note that ....
-
-\subsection{Virial Parameter, Collapse, and high SFR at high-\z} \label{sec:diss2}
-
-It may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
-nature of the majority of the molecular gas in \flower and its SFR.
-That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
-This discrepancy can be explained in two ways.
-First, our results are limited by the resolution of the simulation, such that, in each MC, there
-likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
-as in the classical MC hierarchy.
-Second, due to
-turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
-large-scale gravitational potential and differential rotation.
-This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
-MCs \citep{Clark04a, Clark05a}.
-Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
-can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation.
-
-We note that in a recent study by \citet{Pettitt18a}, the authors report that the virial parameter could be a poor indicator
-for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation.
-In particular, these authors do not find any significant correlations between the virial parameter, cloud mass,
-and star formation efficiency ($M_*/M_{\rm cl}$).
-Identifying a new diagnostic tool
-% would be interesting for the future, but is outside the aim of the present work
-is beyond the scope of this paper. Here, we are more interested in
-comparing the clouds dynamics with observational studies, and thus,
-part of the discussion of this paper is based on virial analysis.
-
-\subsection{MC Dynamics Setting the Mass Scale at EoR} \label{sec:diss3}
-
-%% pressure
-%The pressure of an MC is expected to increase with its velocity dispersion and surface density (see e.g., \Eq{pext} and
-%since $P\propto\Sigma^2$).
-%In the central molecular zone of the Milky Way (CMZ), we have seen molecular clouds with high pressures of
-%$P/k_B > $10$^7$\,K\,cm$^{-3}$. Such high pressures are also seen in massive star-forming regions such as 30 Doradus.
-%The higher $\Sigma_{\rm gas}$ is in turn relates to more massive clouds being formed.
-%In fact, a few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun 
-%are found in nearby gas-rich galaxies such as M64 and M51 \citep{Rosolowsky05a, Koda09a, Colombo14a}.
-%%On the other hand, such massive molecular structures are unknown to Local Group galaxies
-%%\citep[e.g.,][]{Rice16a}, and are likely the sites
-%%from which massive star clusters or OB associations are to be formed.
-%{\bf So?}
 
@@
 yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
-The enhanced MCs size-scale compared to local GMCs
-is therefore likely a manifestation of gravitational instabilities (resulting from the higher $f_{\rm gas}$), which drives
-supersonic turbulence in the ISM.
-
 Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
@@
 since they adopt non-cosmological initial conditions.
-It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$\,30\,pc).
-Future higher resolution zoom-in simulations would certainly be useful to understand
-the evolving dynamical properties of the lower-mass molecular structures in
-galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
+That said, this is reassuring --- our results are not far off in spite of the resolution ($l\approx$\,30\,pc).
+
+%Note that regions of $Q\lesssim1$ is actually somewhat 
+%less than the number of MCs we have identified based on density threshold --- 
+%but this has something to do with the dependence on 
+%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at 
+%MCs identified at the highest $n_{\rm cut}$. \DL{do they overlap?}
+
+% alpha parameters
+As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
+is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
+For the MCs in the satellite galaxies, a lower virial parameter is found 
+compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
+stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
+\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+% pext
+As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
+The lower virial parameter and external pressure of the sub-MCs
+compared to their parent MCs are consistent with
+the notion that collapsing structures result from local gravitational
+instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
+which are supported by turbulence and rotation on large scales.
+%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
+%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
+%and galactic rotation on large scales. 
+%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
+
+For MCs in the satellite galaxies, we find low pressures and virial parameters 
+which are comparable to those found in clouds formed in the galactic disks 
+($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures,
+and thus, \SF is expected to continue 
+as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+The apparently large virial parameters seen in the MCs of \flower can be understood using the 
+Toomre $Q$ parameter (\Fig{Q} and \Fig{Qeff}). 
+We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
+instability against axisymmetric perturbations), but  
+further evolution/collapse depends on the dynamics or equation of state of the gas. 
+Such fragmentation is expected to take place at the
+critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
+Second, this fragmentation scale is greater than the typical size of GMCs. This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs
+correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales. 
+Thus, the high virial parameter found 
+for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure 
+and rotation) and surface density, indicate that most of them are not collapsing structures. 
+As such, some MCs lie in regions of $Q>1$. 
+Only in (the denser) regions with a low Toomre $Q$ parameter and 
+when energy can be dissipated on a timescale 
+that is shorter than the timescale over which it gains energy (e.g., heating) 
+correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
+This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$
+nature of most MCs of \flower and its relatively high SFR.
+That is, if most of the molecular gas in \flower are stable against collapse, 
+how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
+The discrepancy can be explained in two ways.
+First, our results are limited by the resolution of the simulation, such that, in each MC, there
+likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
+as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
+Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
+large-scale gravitational potential and differential rotation.
+This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
+MCs \citep{Clark04a, Clark05a}.
+Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
+can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation
+and collapse on smaller scales to trigger \SF.
 

### 2019-03-06 WRITEUP/ms.tex
refined Sec 6

@@
 \includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_1}
-\caption{Continued. Maps showing the various quantities projected in the $xz$-plane.}
+\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
 \addtocounter{figure}{-1}
@@
 \includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_2}
-\caption{Continued. Maps show the various quantities projected in the $yz$-plane.}
+\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
 \end{figure*}
@@
 which set the scale for fragmentation.
-This is consistent with what has been found previously in higher resolution idealized simulation of isolated galaxies.
+This physical scale is 
+consistent with what has been found in higher resolution idealized simulation of isolated galaxies.
 Our simulation here confirms these results at EoR and under
@@
 Our results are thus insensitive to the various density cuts of choice.
-%However, our results are dependent on the numerical resolution of the simulation.
 The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the 
@@
 result of the weaker stellar feedback as they have
-experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
+experienced less episodes of \SF compared to \flower 
+(also supported by the lower stellar-to-gas mass ratio of the latter).
 MCs in the satellites are therefore likely collapsing structures.
@@
 serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
-the multi-phase ISM structures of the first galaxies.
+the multi-phase ISM of the first galaxies.
+%Future higher resolution zoom-in simulations would certainly be useful to understand
+%the evolving dynamical properties of the lower-mass molecular structures in
+%galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
 These predictions can in turn be
-tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA,
+tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby 
 enabling us to test our findings and refine future simulations to shed light on the physical processes behind 
@@
 We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
-T.K.D.L. acknowledges support by the NSF through award SOSPA4-009
+TKDL acknowledges support by the NSF through award SOSPA4-009
 from the NRAO and support from the Simons Foundation.
-A.F. acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
+AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
 This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA)

### 2019-03-06 WRITEUP/ms.tex
refined abstract

@@
 Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
-substructures have lower virial parameters, which is
-consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
-% , which are supported by turbulence and rotation on large scale.
-On the other hand, we find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
+substructures have lower virial parameters and Toomre $Q$, which is
+consistent with the notion that collapsing structures occur within globally stable structures.
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
 which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.

### 2019-03-07 toomre.py
regularization implemented; Qgas is NaN everiwhere (problems in the regridding?)

@@ -907,27 +907,55 @@ class ToomreAnalyze_2comp(object):
     # radial velocity dispersion.
 
     """ see eq. 3 of Inoue+16"""
-    w = 2. * self.Q_star.sigma_r * self.Q_gas.sigma_r / (self.Q_star.sigma_r**2 + self.Q_gas.sigma_r**2)
-    #
-    if self.verbose:
-      print "weight Q: "
-      print '  max/ min',np.max(w),np.min(w) 
-      print '  mean/std',np.mean(w),np.std(w) 
+    # calculate weight
+    up      = 2. * self.Q_star.sigma_r * self.Q_gas.sigma_r
+    low     = (self.Q_star.sigma_r**2 + self.Q_gas.sigma_r**2)
+    w       = np.zeros_like(up)
+    mask    = low>0
+    w[mask] = up[mask]/low[mask]
 
+    # get thick Q parameters
     Q_thick_star = self.Q_star_val * self.T_s
     Q_thick_gas  = self.Q_gas_val * self.T_g
 
-    """ see eq. 3 of Inoue+16"""
-    # 2D array
-    res1 = w /Q_thick_star + 1./ Q_thick_gas
-    res2 = 1./Q_thick_star +  w/Q_thick_gas
-    #
-    Q_twoComp_inv = np.where(Q_thick_star >= Q_thick_gas, res1, res2)
-    #
-    self.Q_twoComp = 1. / Q_twoComp_inv
+    # regularize
+    Q_thick_star[np.isnan(Q_thick_star)] = 0
+    Q_thick_gas [np.isnan(Q_thick_gas )] = 0
 
     if self.verbose:
-      print (np.isnan(self.Q_twoComp) == True).any()
+      for arr,nome in zip([w,Q_thick_star, Q_thick_gas],['weight','Q_thick_star','Q_thick_gas']):
+        print nome
+        print '  max/ min',np.max(arr),np.min(arr) 
+        print '  mean/std',np.mean(arr),np.std(arr) 
+
+    # init
+    mask          =  np.logical_and(Q_thick_star> 0, Q_thick_gas > 0)
+    Q_twoComp_inv = - np.ones_like(Q_thick_gas)
+    self.Q_twoComp= np.zeros_like(Q_thick_gas)
+    res1,res2     = - np.ones_like(Q_thick_gas), - np.ones_like(Q_thick_gas)
+ 
+    # compute Q composite
+    """ see eq. 3 of Inoue+16"""
[…]

### 2019-03-07 toomre.py
Q_gas is zero before the interpolation

@@ -711,7 +711,7 @@ class ToomreAnalyze(object):
     ax.set_ylim(y1,y2)
 
     ax = plt.subplot(224)
-    map_Q = gaussian_filter(np.log10(self.Q), sigma=self.smooth_size)
+    map_Q = np.log10(gaussian_filter(self.Q, sigma=self.smooth_size))
     im = ax.imshow(map_Q[bottomBound: topBound, leftBound:rightBound],
                    origin='lower',
                    extent=(xruler[leftBound],
@@ -850,12 +850,23 @@ class ToomreAnalyze_2comp(object):
     xx = np.linspace(self.Q_gas.coords[self.plane][0].value.min(), self.Q_gas.coords[self.plane][0].value.max(), len(self.Q_gas.coords[self.plane][0]))
     yy = np.linspace(self.Q_gas.coords[self.plane][1].value.min(), self.Q_gas.coords[self.plane][1].value.max(), len(self.Q_gas.coords[self.plane][1]))
 
+    if self.verbose:
+      print 'reinterpolating'
+      print 'Q'
+      print '  ',np.max(self.Q_gas.Q),np.max(self.Q_gas.Q)
+      print '  ',np.mean(self.Q_gas.Q),np.std(self.Q_gas.Q)
+
     f = interpolate.interp2d(xx,
                              yy,
                              self.Q_gas.Q,
                              kind='cubic')
     Q_gas_resampled = f(xx, yy)
     assert self.Q_star_val.shape == Q_gas_resampled.shape
+
+    if self.verbose:
+      print 'Q resampled'
+      print '  ',np.max(self.Q_gas.Q),np.max(self.Q_gas.Q)
+      print '  ',np.mean(self.Q_gas.Q),np.std(self.Q_gas.Q)
 
     if self.debug:
       plt.figure()

### 2019-03-07 toomre.py
extra checks

@@ -841,6 +841,9 @@ class ToomreAnalyze_2comp(object):
 
     self.smooth_size = smooth_size
 
+
+    self.Q_gas.SD = self.Q_gas.projected_SurfaceDensity[self.Q_gas.plane]
+
     self.interpolate_gas_onto_star_grid()
 
 

### 2019-03-07 toomre.py
smooth Q_eff

@@ -932,6 +932,11 @@ class ToomreAnalyze_2comp(object):
     return self.Q_twoComp
 
 
+  def smooth_Q_eff(self):
+    self.smooth_size = self.Q_gas.smooth_size
+    self.Q_twoComp = gaussian_filter(np.log10(self.Q_twoComp), sigma=self.smooth_size)
+
+
   def plot_Q_eff(self):
     plt.figure()
     im = plt.imshow(np.log10(self.Q_twoComp),
@@ -1035,6 +1040,7 @@ class ToomreAnalyze_2comp(object):
     self.compute_T_g()
     self.compute_T_s()
     self.calc_Q_eff()
+    self.smooth_Q_eff()
 
     self.plot_Q_eff_zoom(central_kpc_one_side, annotate_clump, clump_list_filename)
 
@@ -1047,7 +1053,7 @@ if __name__ == '__main__':
     os.mkdir(base_out)
 
   plane     = '0'
-  isnap     = 17
+  isnap     = 28
   annotate  = False
 
   clump_cut   = 0.32

### 2019-03-07 toomre.py
smooth in linear

@@ -933,7 +933,7 @@ class ToomreAnalyze_2comp(object):
 
   def smooth_Q_eff(self):
     self.smooth_size = self.Q_gas.smooth_size
-    self.Q_twoComp = gaussian_filter(np.log10(self.Q_twoComp), sigma=self.smooth_size)
+    self.Q_twoComp = gaussian_filter(self.Q_twoComp, sigma=self.smooth_size)
 
 
   def plot_Q_eff(self):

### 2019-03-07 toomre.py
transposing the clump position seems to work

@@ -20,6 +20,11 @@ from matplotlib import cm
 cmap     = cm.get_cmap('viridis')      # 'magma'
 cmap_div = cm.get_cmap('RdBu')         # divergent cmap
 
+c_clump  = 'k'
+#c_clump  = 'darkturquoise'
+#c_clump  = 'antiquewhite'
+
+
 from pymses.utils import constants as C_py
 from yt import units as C_yt
 import astropy.constants as C_ap
@@ -726,11 +731,11 @@ class ToomreAnalyze(object):
       # pos2 = pos * self.factor_R
 
       if self.plane == '0':
-        plt.plot(cly, clz, 'x', markersize=15, color='darkturquoise')
+        plt.plot(clz, cly, 'x', markersize=15, color=c_clump)
       elif self.plane == '1':
-        plt.plot(clx, clz, 'x', markersize=15, color='antiquewhite')
+        plt.plot(clz, clx, 'x', markersize=15, color=c_clump )
       elif self.plane == '2':
-        plt.plot(clx, cly, 'x', markersize=15, color='antiquewhite')
+        plt.plot(cly, clx, 'x', markersize=15, color=c_clump )
 
     ax.set_xlim(x1,x2)
     ax.set_ylim(y1,y2)
@@ -990,11 +995,11 @@ class ToomreAnalyze_2comp(object):
       # pos2 = pos * self.factor_R
 
       if self.plane == '0':
-        plt.plot(cly, clz, 'x', markersize=15, color='darkturquoise')
+        plt.plot(clz, cly, 'x', markersize=15, color=c_clump)
       elif self.plane == '1':
-        plt.plot(clx, clz, 'x', markersize=15, color='antiquewhite')
+        plt.plot(clz, clx, 'x', markersize=15, color=c_clump )
       elif self.plane == '2':
-        plt.plot(clx, cly, 'x', markersize=15, color='antiquewhite')
+        plt.plot(cly, clx, 'x', markersize=15, color=c_clump )
 
     cbar = plt.colorbar(im, extend='both',    # arrows in both direction
                          ticks=[-1, 0, 1]
@@ -1046,8 +1051,8 @@ if __name__ == '__main__':
     os.mkdir(base_out)
 
   plane     = '0'
-  isnap     = 17
-  annotate  = False
+  isnap     = 28
+  annotate  = True
 
   clump_cut   = 0.32
   smooth_kpc  = 0.3

### 2019-03-07 WRITEUP/ms.tex

@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_0}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0}
 \caption{
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_1}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_1}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss_16_toomre_proj_2}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/}
+\caption{
+Effective two-component Toomre Q map in the $xy$-plane.
+Modest smoothing has been applied to the maps. 
+A divergent colormap is used for the Toomre $Q$ map to facilitate 
+identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+\label{fig:Qeff}}
+% \addtocounter{figure}{-1}
 \end{figure*}

### 2019-03-07 WRITEUP/ms.tex
Updates from Overleaf

@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
+\shorttitle{Dynamical Properties of MC in Galaxies at the EoR
 }
@@
 \begin{document}
-\title{
-Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization
-}
+\title{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization}
 
@@
 \begin{abstract}
-We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
-and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
-We identify MCs using H$_2$ density, 
-and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
-with those observed in nearby and \z$\sim$\,2 galaxies.
-The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
-systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
-We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine 
-regions that are unstable to local axisymmetric perturbations. 
+We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower) and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
+%
+We identify MCs using H$_2$ density, and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$) with those observed in nearby and \z$\sim$\,2 galaxies.
+%
+The MCs span a mass range of $10^{6.5-9}$\,\Msun.
+Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
+%
+We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine regions that are unstable to local axisymmetric perturbations. 
+%
 We further perform virial analysis, which is accessible from observations, to examine regions likely 
 to undergo collapse.
-Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
-substructures have lower virial parameters and Toomre $Q$, which is
-consistent with the notion that collapsing structures occur within globally stable structures.
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
-which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
-Our results suggest that the more massive and bigger MCs compared to the Milky Way
-manifest from the higher gas mass fraction, surface density, and velocity dispersion.
+Our analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters and Toomre $Q$, which is consistent with the notion that collapsing structures occur within globally stable structures.
+%
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
+Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the higher gas mass fraction, surface density, and velocity dispersion.
 % , which together sets the scale for fragmentation.
-High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
-Next Generation Very Large Array (ngVLA)
-can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
+High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
 \end{abstract}
@@
 %--------------------------------------------------------------------------
-\section{Introduction}    \label{sec:intro}
+
+\section{Introduction}\label{sec:intro}
 
@@
 \begin{equation}
-Q^{-1}_{\rm eff} = \[ \left\{
+Q^{-1}_{\rm eff} =  \left\{
 				\begin{array}{lccr}
@@
 				\end{array} 
-			    \right,
-			    \]
+			    \right.
 \end{equation}
@@
 \begin{equation}
-T = \[ \left\{
+T = \left\{
 		\begin{array}{lccr}
@@
 		\end{array}
-	\right \rlap{.}
-	\]
+	\right.
 \end{equation}

### 2019-03-07 WRITEUP/ms.tex

@@
 \newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
+
+% it can be instead included as
+% \graphicspath{{Fig/}}
+% so that plots are automatically searched for in the given path
+\def\figpath{./Fig}
 
@@
 
-% it can be instead included as
-% \graphicspath{{Fig/}}
-% so that plots are automatically searched for in the given path
-\def\figpath{./Fig}
-
 %--------------------------------------------------------------------------
@@
 
-\section{Introduction}\label{sec:intro}
-
-The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
-galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
-and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
-The general consensus is that the growth of \highz galaxies are triggered and supported by massive
-gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves
-are more gas-rich in their star-forming molecular
-gas contents compared to present-day galaxies.
+\section{Introduction}%\label{sec:intro}
+
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
+The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves are more gas-rich in their star-forming molecular gas contents compared to present-day galaxies.
 % while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0_zoom_1.5_kpc.png}
 \caption{
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_1}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/16_gas_toomre_proj_1_zoom_1.5_kpc.png}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2_zoom_1.5_kpc.png}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_toomreEff_proj_0_zoom_1.5_kpc.png}
 \caption{

### 2019-03-07 WRITEUP/ms.tex
remove again

--- 2019-03-07 WRITEUP/ms.tex
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_0_zoom_2.0_kpc}}
 \caption{
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_1}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_1_zoom_2.0_kpc.png}}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc.png}}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_star_toomre_proj_0_zoom_2.0_kpc.png}}
+\caption{
+Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
+\label{fig:Qstar}}
+% \addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_toomreEff_proj_0_zoom_2.0_kpc.png}}
 \caption{

### 2019-03-07 WRITEUP/ms.tex
add latest Q figures, fix figure path

--- 2019-03-07 WRITEUP/ms.tex
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
 \caption{
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+\DL{Ignore the crosses for now....}
 \label{fig:Q}}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_1}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/}
-\caption{
-Effective two-component Toomre Q map in the $xy$-plane.
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
+\caption{
+Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
+\label{fig:Qstar}}
+% \addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 20 0, clip, width=0.55\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc}.png}
+\includegraphics[trim=10 0 0 0, clip, width=0.4\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png}
+\caption{
+Effective two-component Toomre Q (left) and gas surface density (right) maps projected onto the $xy$-plane.
 Modest smoothing has been applied to the maps. 
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+\DL{Ignore the crosses for now....Please compare by eye for the time being.}
 \label{fig:Qeff}}
@@
 \end{figure*}
+\clearpage
 

### 2019-03-08 WRITEUP/ms.tex
edited Q figure caption and some text

--- 2019-03-07 WRITEUP/ms.tex
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
 \caption{
@@
 
-Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Qeff}, respectively (see \Fig{h2density} for examples of clumps identified
-in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified
+in this snapshot). Fragmentation are expected in regions of low Toomre $Q$ values.
 Further interpretation and implication of this is discussed in \Sec{origin}.
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0_zoom_1.5_kpc.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
 \caption{
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
+Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
 \label{fig:Q}}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/16_gas_toomre_proj_1_zoom_1.5_kpc.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2_zoom_1.5_kpc.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_toomreEff_proj_0_zoom_1.5_kpc.png}
-\caption{
-Effective two-component Toomre Q map in the $xy$-plane.
+\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
+\caption{
+Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
+\label{fig:Qstar}}
+% \addtocounter{figure}{-1}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
+\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
+\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
+\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
+\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
+\caption{
+Effective two-component Toomre $Q_{\rm eff}$ (top row) 
+and gas surface density (middle) maps projected onto the $xy$-plane.
+Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
+and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
+Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
+Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
 Modest smoothing has been applied to the maps. 
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
+are likely gravitationally unstable.
 \label{fig:Qeff}}
@@
 The apparently large virial parameters seen in the MCs of \flower can be understood using the 
-Toomre $Q$ parameter (\Fig{Q} and \Fig{Qeff}). 
+Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,r$-$\,\ref{fig:Qeff}). 
 We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
@@
 We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as
-result of the weaker stellar feedback as they have
-experienced less episodes of \SF compared to \flower 
-(also supported by the lower stellar-to-gas mass ratio of the latter).
+result of the weaker stellar feedback compared to \flower 
 MCs in the satellites are therefore likely collapsing structures.

### 2019-03-08 WRITEUP/ms.tex
polished

@@
 \begin{abstract}
-We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower) and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
+We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower) and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
 %
@@
 %
-We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine regions that are unstable to local axisymmetric perturbations. 
+We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine regions that are 
+gravitationally unstable.
 %
@@
 %
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
-Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the higher gas mass fraction, surface density, and velocity dispersion.
+We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
+compared to \flower. Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the 
+higher gas mass fraction, surface density, and velocity dispersion.
 % , which together sets the scale for fragmentation.
@@
 The apparently large virial parameters seen in the MCs of \flower can be understood using the 
-Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,r$-$\,\ref{fig:Qeff}). 
+Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,$-$\,\ref{fig:Qeff}). 
 We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
@@
 and rotation) and surface density, indicate that most of them are not collapsing structures. 
-As such, some MCs lie in regions of $Q>1$. 
+As such, some MCs are found to lie in regions of $Q>1$. 
+% some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
 Only in (the denser) regions with a low Toomre $Q$ parameter and 
@@
 MCs \citep{Clark04a, Clark05a}.
-Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
-can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation
+Additionally, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
+can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation
 and collapse on smaller scales to trigger \SF.
@@
 
-Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter.
-This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
+Virial analysis indicates that MC/arms of the main disk of \flower are unbound, but substructures have
+lower virial parameter. Some of these sub-MCs have Toomre $Q_{\rm eff}$ parameters consistent with being 
+gravitationally unstable. This is consistent with the notion that collapsing structures resulting from
+gravitational instability occur within globally stable structures, which are
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as
-result of the weaker stellar feedback compared to \flower 
+We also find $\alpha_{\rm vir}\approx$\,2 for MCs in the satellite galaxies, which we interpret as
+result of the weaker stellar feedback compared to \flower.
 MCs in the satellites are therefore likely collapsing structures.
 
-We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, 
-at least in terms of the scaling relations examined.
-Our results are robust against the H$_2$ volume density threshold adopted (see Appendix \Sec{ncut}).
+In terms of the scaling relations examined, we do not observe any significant
+temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation.
+Similarly, we do not find any significant dependence on the H$_2$ volume density threshold adopted
+in the scaling relations examined (see Appendix \Sec{ncut}). 
+Our results are thus robust against the density threshold adopted.
 
@@
 serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
-the multi-phase ISM of the first galaxies.
+the molecular ISM of the first galaxies.
 %Future higher resolution zoom-in simulations would certainly be useful to understand

### 2019-03-08 toomre.py
look pretty, add func to plot SD as single panel

@@ -12,6 +12,7 @@ from plot_modules.plot_cloud_prop import setup_plot
 setup_plot()
 from io_modules.manipulate_fetch_gal_fields import import_fetch_gal, prepare_unigrid, prepare_star_unigrid, get_units, import_fetch_stars
 import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
 from scipy.ndimage.filters import gaussian_filter
 
 import os,sys
@@ -19,11 +20,6 @@ import os,sys
 from matplotlib import cm
 cmap     = cm.get_cmap('viridis')      # 'magma'
 cmap_div = cm.get_cmap('RdBu')         # divergent cmap
-
-c_clump  = 'k'
-#c_clump  = 'darkturquoise'
-#c_clump  = 'antiquewhite'
-
 
 from pymses.utils import constants as C_py
 from yt import units as C_yt
@@ -52,6 +48,11 @@ class ToomreAnalyze(object):
     self.convertPart = convertPart
     self.plane = plane
     self.field_type = field_type
+    #
+    if self.field_type == 'gas':
+      self.c_clump  = 'orange'
+    elif self.field_type == 'star':
+      self.c_clump = 'green'
     #
     self.smooth_size = 0.                  # size for smoothing image in code units
     self.smooth_kpc  = smooth_size_kpc     # size for smoothing image in kpc
@@ -582,7 +583,7 @@ class ToomreAnalyze(object):
     return self.Q
 
 
-  def plot_range_set_by_camera(self):
+  def set_plot_range_set_by_camera(self):
     self._xmin = (self.coords_plane[0] - self.center_plane[self.plane][0]).min()
     self._xmax = (self.coords_plane[0] - self.center_plane[self.plane][0]).max()
     self._ymin = (self.coords_plane[1] - self.center_plane[self.plane][1]).min()
@@ -590,8 +591,6 @@ class ToomreAnalyze(object):
 
 
   def plot_Q(self):
-    # define plot boundary kpc
-
     plt.figure()
     plt.imshow(np.log10(self.Q), origin='lower',
                 extent=(self._xmin, self._xmax, self._ymin, self._ymax)
@@ -731,11 +730,14 @@ class ToomreAnalyze(object):
       # pos2 = pos * self.factor_R
 
       if self.plane == '0':
[…]

### 2019-03-08 WRITEUP/ms.tex
Updates from Overleaf

--- 2019-03-07 WRITEUP/ms.tex
@@
 \section{Introduction}%\label{sec:intro}
+
+\AP{i have to check abstract and Sections 3. 4. 5., in particular 5.2; check also what have been moved to the app}
 
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_0_zoom_2.0_kpc}}
 \caption{
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-\DL{Ignore the crosses for now....}
 \label{fig:Q}}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_1_zoom_2.0_kpc.png}}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc.png}}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_star_toomre_proj_0_zoom_2.0_kpc.png}}
 \caption{
@@
 \centering
-\includegraphics[trim=0 0 20 0, clip, width=0.55\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc}.png}
-\includegraphics[trim=10 0 0 0, clip, width=0.4\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png}
-\caption{
-Effective two-component Toomre Q (left) and gas surface density (right) maps projected onto the $xy$-plane.
+\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{{\figpath/ss16_toomreEff_proj_0_zoom_2.0_kpc.png}}
+\caption{
+Effective two-component Toomre Q map in the $xy$-plane.
 Modest smoothing has been applied to the maps. 
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-\DL{Ignore the crosses for now....Please compare by eye for the time being.}
 \label{fig:Qeff}}
@@
 \end{figure*}
-\clearpage
 

### 2019-03-08 toomre_star.py
deprecated

@@ -1,607 +1,0 @@
-'''
-
-Toomre for star component.
-
-'''
-
-import yt
-import numpy as np
-import cPickle as pickle
-import pymses
-from plot_modules.plot_cloud_prop import setup_plot
-setup_plot()
-from io_modules.manipulate_fetch_gal_fields import import_fetch_gal, prepare_unigrid, prepare_star_unigrid, get_units, import_fetch_stars
-import matplotlib.pyplot as plt
-from scipy.ndimage.filters import gaussian_filter
-from matplotlib import cm
-cmap      = cm.get_cmap('viridis')
-
-import astropy.constants as C
-pc2cm = 3.086e18
-cm2pc = 1/pc2cm
-kg2Msun = 1. / 1.989E30
-kg2g = 1.E+03
-pc2cm = 3.086e18
-J2erg   = 1.E+07
-k_B_erg = C.k_B.value * J2erg
-g2Msun = 1 / 1.989e33
-
-# load camera stuff
-folder = 'precomputed_data/'
-f_camera = folder + 'camera_settings.log'
-
-with open(f_camera, 'rb') as f:
-    cameraDat = pickle.load(f)
-
-# prepare input data, if not already passed as arguments
-isnap = 28
-read_proper_unit = True
-
-verbose     = True
-megaverbose = False
-
-wg_var = 'mass'
-
-if read_proper_unit:
-    import pymses
-    ro = pymses.RamsesOutput("output", isnap)
-    factor_vel = get_units(ro=ro)['vel'][0]
-    factor_rho = get_units(ro=ro)['rho'][0]
-    factor_R = get_units(ro=ro)['dx'][0] * 1.e-3
-    region_size = cameraDat[str(isnap)]['size']
-    region_size_kpc = region_size * factor_R
-else:
-    region_size_kpc = None
-
-# read in particles
-# read from resampled.h5
-starData = import_fetch_stars(
-                              isnap=isnap,
-                              verbose=verbose,
-                              convert=True,  clipping  = 1.0
-                             )
-
-if verbose:
-  print 'stellar keys:'
-  print '  ',starData.keys()
-
-ds, dd = prepare_star_unigrid(data=starData,
-                              add_unit=True,     # since convert=True
[…]

### 2019-03-11 toomre.py
color

@@ -50,9 +50,9 @@ class ToomreAnalyze(object):
     self.field_type = field_type
     #
     if self.field_type == 'gas':
-      self.c_clump  = 'orange'
+      self.c_clump  = 'darkgoldenrod'
     elif self.field_type == 'star':
-      self.c_clump = 'green'
+      self.c_clump = '#bcbd22'    # https://matplotlib.org/users/dflt_style_changes.html
     #
     self.smooth_size = 0.                  # size for smoothing image in code units
     self.smooth_kpc  = smooth_size_kpc     # size for smoothing image in kpc
@@ -78,7 +78,7 @@ class ToomreAnalyze(object):
     self.f_camera = self.cameraFolder + 'camera_settings.log'
 
     # project velocity by mass-weighting, project surface density
-    # axis : corresponding to the axis to slice along
+    # axis : corresponding to the axis to slice along'none'
 
     self.axes = {'0': 'x', '1': 'y', '2': 'z'}
     self.vel = {}
@@ -683,6 +683,26 @@ class ToomreAnalyze(object):
               cmap=cmap)
     cbar = plt.colorbar(im)
     cbar.set_label(r"$\log{\Sigma}$ [M$_{\odot}$~pc$^{-2}$]", fontsize=16)
+
+    if annotate_clump:
+      _, clx, cly, clz = np.loadtxt(clump_list_filename, unpack=True)
+      # pos2 = pos * self.factor_R
+
+      if self.plane == '0':
+        plt.plot(clz, cly, '*', markersize=15, markerfacecolor='none',
+                   markeredgecolor=self.c_clump, fillstyle='none',
+                   markeredgewidth=1.15,
+                  linewidth=1.8)
+      elif self.plane == '1':
+        plt.plot(clz, clx, '*', markersize=15, markerfacecolor='none',
+                   markeredgecolor=self.c_clump, fillstyle='none',
+                   markeredgewidth=1.15,
+                  linewidth=1.8)
+      elif self.plane == '2':
+        plt.plot(cly, clx, '*', markersize=15, markerfacecolor='none',
+                   markeredgecolor=self.c_clump, fillstyle='none',
+                   markeredgewidth=1.15,
+                  linewidth=1.8)
     ax.set_xlim(x1,x2)
     ax.set_ylim(y1,y2)
 
@@ -730,13 +750,19 @@ class ToomreAnalyze(object):
       # pos2 = pos * self.factor_R
 
[…]

### 2019-03-11 WRITEUP/ms.tex
minor text edit

--- 2019-03-08 WRITEUP/ms.tex
@@
 
+\AP{i have to check abstract and Sections 3. 4. 5., in particular 5.2; check also what have been moved to the app}
+
 The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified
-in this snapshot). Fragmentation are expected in regions of low Toomre $Q$ values.
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
+Before accounting for contribution of the stellar component to the gravitational potential, 
+most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).
+Fragmentation are expected in regions of low Toomre $Q_{\rm eff}$ values.
 Further interpretation and implication of this is discussed in \Sec{origin}.
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
-Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
+Markers in the surface density and Toomre $Q$ maps
+correspond to the mass-weighted positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
+Positions of sub-MCs identified using lower $n_{\rm cut}$ are not shown (but see top row of \Fig{Qeff} for an example). 
+Before accounting for contribution of the stellar component to the 
+gravitational potential, we find that most MCs lie in regions of 
+$\log{Q_{\rm gas}}\simeq$\,0. 
 \label{fig:Q}}
@@
 \includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
+\includegraphics[trim=10 0 0 10, clip, width=0.4\textwidth]{\figpath/{ss16_star_SD_proj_0_zoom_2.0_kpc}.png}  
 \includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
-\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
+\includegraphics[trim=30 25 30 20, clip, width=0.38\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png} 
 \includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
@@
 Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
-and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
-Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
-Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
+and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as star markers.
+Bottom row: Zoom-in view of the effective $Q_{\rm eff}$ (left) and gas surface density (right) maps.
+Markers in the bottom left Toomre $Q$ map correspond to positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
 Modest smoothing has been applied to the maps. 

### 2019-03-11 WRITEUP/ms.tex
minor text edit

@@
 Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
-Before accounting for contribution of the stellar component to the gravitational potential, 
+Before accounting for the thickness of the disk and the 
+contribution of the stellar component to the gravitational potential, 
 most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).

### 2019-03-11 toomre.py
smoothing value is correctly taken in kpc now

@@ -247,12 +247,16 @@ class ToomreAnalyze(object):
           self.center_plane[kk] = [self.center[1], self.center[2]]
 
   def set_smooth_size(self):
-    dx = self.coords_plane[0].max() - self.coords_plane[0].min()
-    dy = self.coords_plane[1].max() - self.coords_plane[1].min()
+
+    # get spacing in x and y direction in kpc
+    nx = np.shape(self.coords_plane[0])[0]
+    ny = np.shape(self.coords_plane[1])[1]
+    dx = (self.coords_plane[0].max() - self.coords_plane[0].min())/nx
+    dy = (self.coords_plane[1].max() - self.coords_plane[1].min())/ny
     dx = (dx.convert_to_units('kpc')).value
     dy = (dy.convert_to_units('kpc')).value
-
-    self.smooth_size = self.smooth_kpc/np.sqrt(dx * dy)
+    # set smoothing radius
+    self.smooth_size = 0.5*self.smooth_kpc/np.sqrt(dx * dy)
 
   def project_onto_plane(self):
 
@@ -1124,7 +1128,7 @@ if __name__ == '__main__':
   annotate  = True
 
   clump_cut   = 0.32
-  smooth_kpc  = 0.3
+  smooth_kpc  = 0.1
 
   min_mass  = 1.e+1 # used to clip 0 in the stellar mass field
   size_kpc  = 2.0

### 2019-03-11 WRITEUP/ms.tex

@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 10 10, clip, width=0.65\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
 \caption{
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 10 10, clip, width=0.65\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
 \caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 10 10, clip, width=0.65\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
 \caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
@@
 \centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
+\includegraphics[trim=0 20 10 10, clip, width=0.65\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
 \caption{
@@
 \includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
-\includegraphics[trim=10 0 0 10, clip, width=0.4\textwidth]{\figpath/{ss16_star_SD_proj_0_zoom_2.0_kpc}.png}  
-\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
+\includegraphics[trim=10 0 0 10, clip, width=0.365\textwidth]{\figpath/{ss16_star_SD_proj_0_zoom_2.0_kpc}.png}  
+\includegraphics[trim=10 0 0 10, clip, width=0.39\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
 \includegraphics[trim=30 25 30 20, clip, width=0.38\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png} 

### 2019-03-11 WRITEUP/ms.tex
manual obtained from overleaf

--- 2019-03-11 WRITEUP/ms.tex
@@
 \usepackage{amsmath}
+
+\usepackage{comment}
+
 \input{preamble}
@@
 
-\author{T. K. Daisy Leung\altaffilmark{1, 2}}
-\author{Andrea Pallottini\altaffilmark{3, 4}}
-\author{Andrea Ferrara\altaffilmark{4, 5}}
-\author{Mordecai-Mark Mac Low\altaffilmark{2, 6, 7}}
+\author{T. K. Daisy Leung\altaffilmark{1,2}}
+\author{Andrea Pallottini\altaffilmark{3,4}}
+\author{Andrea Ferrara\altaffilmark{4,5}}
+\author{Mordecai-Mark Mac Low\altaffilmark{2,6,7}}
 
@@
 
-\section{Introduction}%\label{sec:intro}
-
-\AP{i have to check abstract and Sections 3. 4. 5., in particular 5.2; check also what have been moved to the app}
+\section{Introduction}
+
+\AP{i have to check abstract and Section 5., in particular 5.2; check also what have been moved to the app}
+
+\AP{For some plots, still the old versions are the ones available.
+It might still be overleaf fault.
+An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g.
+selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}
 
@@
 The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves are more gas-rich in their star-forming molecular gas contents compared to present-day galaxies.
-% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
-% the gravitational potential is still increasing), but their gas reservoirs
-% are continuously being replenished.
+%
 These massive gas inflows in turn trigger gravitational instability and lead
@@
 
-This paper is structured as follows.
-In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
-and describe the method used to identify its molecular gas complexes.
+%This paper is structured as follows.
+In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower), and describe the method used to identify its molecular gas complexes.
 In \Sec{eqn}, we present the formalism within which we interpret the results.
 In \Sec{results}, we present scaling relations for the MCs identified.
-% Toomre stability analysis in \Sec{Q}.
-We then interpret the results   % , robustness of our analysis, caveats,
-and discuss the implications of our findings in \Sec{diss},
-and present our conclusions in \Sec{conclusion}.
-Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
-in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
-Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
-spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.
+We then interpret the results and discuss the implications of our findings in \Sec{diss}, and present our conclusions in \Sec{conclusion}.
+This paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}.
+In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
+In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results.
+In \Sec{results}, we present the results and the scaling relations for the MCs.
+We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
+%
 
 % ------------------
-\section{Simulation and Method} \label{sec:sim}
+\section{Numerical simulations} \label{sec:sim}
 
@@
 }}
+
 The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
-
-\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and
-adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
+%
+\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
+%
 In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
@@
 Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
+%
 We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
@@
 
-The simulation data contain information such as the density ($\rho$) and velocity ($v_x$, $v_y$, and $v_z$) fields, from which we calculate
-the physical properties of each MC, such as mass and velocity dispersion.
+The simulation data contain information such as the density ($\rho$) and velocity ($v_x$, $v_y$, and $v_z$) fields, from which we calculate the physical properties of each MC, such as mass and velocity dispersion.
 Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids for the analysis presented in this paper.
-The grid size is defined
-based on the highest resolution of the simulation data (i.e., the less refined regions are supersampled in the resulting uniform grids).
+The grid size is defined based on the highest resolution of the simulation data (i.e., the less refined regions are supersampled in the resulting uniform grids).
 
 \subsection{Star Formation History} \label{sec:sfh}
-One of the main advantages for studying the dynamical properties of molecular structures at
-$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
-as a function of time.
-This is advantageous especially at early cosmic epochs,
-when the densest structures are beginning to form;
-gas is constantly being accreted onto the central galaxy from the cosmic web and
-satellite galaxies, thereby leading to bursts of \SF.
-Meanwhile, tidal forces resulting from interactions with these surrounding
-galaxies can disrupt the main disk and arms, likely leading to different dynamical states
-for the molecular structures compared to more evolved galaxies found at
-a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
-ones). % mainly expecting differences in alpha_vir, sigma, M_cl.
+One of the main advantages for studying the dynamical properties of molecular structures at $z$\ssim6 in simulation is the fact that we can examine how their properties evolve as a function of time.
+%
+This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
+Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
+% mainly expecting differences in alpha_vir, sigma, M_cl.
 
@@
 \caption{
-    Star formation history of \flower (top right) and
-    projected stellar mass distribution of \flower during 
-    {\it (a)} one of its accretion phases
-    at its early stage of evolution; 
-    {\it (b)} one of its major starburst phases
-    after a major merger; and
-    {\it (c)} a relatively quiescent phase post-starburst.
-% f_gas history?
+    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.\AP{please rearrange the maps such that either i) they have an L shape ii) they are all bewlo the SFR; numbers on the axis are too small, and phase (a) is missing the colorbar; a single colorbar for the star maps might substitute the current 2 ones; please use magma colorbar for the maps (or in any case the colorbar that has been select for for $\Sigma$ trhought the paper)}
 \label{fig:SFH}}
@@
 
-We show the \SF history of \flower in \Fig{SFH},
-where the SFR is calculated based on existing young stellar population, which is
-defined to have an age of $t_{\rm age}<$\,10\,Myr.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
-The SFR plotted in Figure 2 of \citet{Pallottini17b}
-is a factor of two higher than shown here since they also include contributions from
-massive satellite galaxies within the surrounding $\approx$50\,kpc, which
-are accreted onto \flower at \z$\lesssim$\,2.}
-as it evolves from an actively accreting phase to
-a starburst phase after a major merger, and then back to a relatively quiescent phase,
-over the few hundred Myr simulated in the simulation.
-
-Given the stochasticity in the \SF history of \flower (see \Fig{SFH}),
-we show the scaling relations found for two snapshots, corresponding to two of its most extreme evolutionary stages,
-in \Sec{singless} to illustrate the salient points of the discussion presented in this paper.
-The two phases (when \flower is accreting materials from its surrounding 
-and when \flower is undergoing a major starburst phase) are expected to bracket the most extreme variations in the cloud dynamics.
-
-\subsection{Structure identification} \label{sec:method}
+We show the \SF history of \flower in \Fig{SFH}, where the SFR is calculated based on existing young stellar population, which is defined to have an age of $t_{\rm age}<$\,10\,Myr.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher than shown here since they also include contributions from massive satellite galaxies within the surrounding $\approx$15\,kpc ($\simeq$ to the virial radius).} as it evolves from an actively accreting phase to a starburst phase after a major merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.
+
+Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), in \Sec{singless} \AP{but we both give the analysis for 2 stages for maps and all the stages in the scaling relation, is it correct?
+if so, this point should be made clearer here (or in the next section)} our work is focused on the analysis of two of its most extreme evolutionary stages, to illustrate the salient points of the discussion presented in this paper.
+The two phases correspond to i) when \flower is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such pahses are expected to bracket the most extreme variations in the cloud dynamics.
+
+\section{Molecular Cloud Complexes}\label{sec:eqn}
+
+\subsection{Structure identification}\label{sec:method}
+
 To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
@@
 
-In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
-molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
-We note that this process is in essence similar to
-identifying molecular structures based on the noise levels of surface density maps
-observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
-as commonly adopted in observational studies (e.g., identifying
-``clumps'' based on/after applying $\sigma$-clipping,
-using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
-and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
-We note that, owing to the nature of \obs, such structures are identified
-in position-position-velocity (PPV) space, whereas in simulations, one has the
-full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
+In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
+We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying ``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+
+We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
 % Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
-Existing studies find a good correspondence in the dynamical properties extracted in
-PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a,
-Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
+Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
 % large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
@@
 \caption{
-Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the
-accretion phase shown in \Fig{SFH}.
+Volumetric H$_2$ density distribution of \flower taken from a single evolutionary stage, corresponding to the accretion phase shown in \Fig{SFH}.
 \label{fig:h2density}}
@@
 \caption{
-Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of
-$n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is only a subset of all the $n_{\rm cut}$ adopted (see text).
+Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text).
 Color shows the H$_2$ surface density, weighted by the column density.
-%   \AP{plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}\DL{I tried more on Sept 7th, errrr, now all the ticks and labels for both panels disappear...
-hmm..
-Not worth my time to fix this for the report.}
+\AP{I would use the label $n_{\rm H2}$ instead of $n({\rm H2})$; i would add the corresponding $n_{cut}= ...$ in withe the lower right corner of each right panel; in the caption I would add which stage is the figure extracted from; optionally, the 3 row might be substituted by a single row with cuts of different colors (if yt allows ...)}
 \label{fig:MC}}
@@
 
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower
-for a given snapshot which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{For reference,
-the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times
-the critical density of the Universe % presumably defined at the redshift of \flower here?
-is $r_{\rm 200}$\ssim15\,kpc.}.
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density
-where ``clumps/structures'' are
-found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
-We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of
-$\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of
-$n_{\rm cut}$ adopted and find no qualitative differences
-affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).}
-to the same snapshot
-used to plot \Fig{h2density}.
-
-For visualization, we overplot the molecular structures identified using
-a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps
-in \Fig{MC} as an example.
+In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{\AP{i would move this note to the (main text of the) section introducing althaea}For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}$\ssim15\,kpc.}.
+%
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
+We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to the same stage used to plot \Fig{h2density}.
+
+For visualization, we overplot the molecular structures identified using a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps in \Fig{MC} as an example.
 The plots shown in \Fig{MC} are weighted by the column density of the total gas content.
@@
 
-Since the molecular structures identified could
-easily appear as overlapping structures depending on the viewing angle, we
-also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more
-easily see that they are collections of disjoint structures.
-We repeat this identification process for 14 snapshots between
-redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
+Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more easily see that they are collections of disjoint structures.
+%
+We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
 
@@
 
-\section{Basic Physics} \label{sec:eqn}
-\subsection{Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
-% \AP{I fear that putting this subsection here breaks a bit the flow of the analysis of the results.
-Maybe we can put it as an appendix and keep only eq.
-10 in the main text (a put it at when analysing the relevant plot)?
-}
+%\subsection{Key Properties of Clouds}
+\subsection{Properties of the Clouds}
+
+% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
+% the mechanisms and physics of formation and evolution of molecular structures and \SF.
+Upon identifying the molecular structures, we extract properties such as mass (\AP{we should uniform the notation} $M_{\rm cl}$), effective size ($R$), \AP{introduced here but not used except for comparison with vallini (in the text); maybe we can remove it} Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
+
+The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$.
+The effective size is defined assuming spherical geometry, i.e.
+$R \equiv (3 V /4 \pi)^{1/3}$.
+%
+In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
+We therefore calculate the non-thermal component of the velocity dispersion (\AP{check the definitions, we are using multiple symbols to indicate the same things} $\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the sum is done for the cells composing each MC.
+\AP{I would first introduce the velocity dispersion and the separate them in thermal and non thermal component; also, even $c_s$ is density weighted average} The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
+\begin{equation}
+\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
+\end{equation}
+The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
+\AP{isn t this definition already given in the main text?} In the subsequent sections, we adopt the root mean square of the velocity field as the velocity dispersion ($\sigma$).
+\label{ftn:veldisp}}.
+On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
+This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
+
+We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
+\end{equation}
+where $M_*$ is the stellar mass withing the MC volume.
+%
+We note that the distributions vary for different evolutionary stage of \flower.
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{6.5}$\,\Msun for the densest MC.
+%
+We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the considered evolutionary stages for each of the given $n_{\rm cut}$ (see \Sec{method}).
+The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
+\caption{Distributions of mass, size, and gas mass fraction of MCs identified using the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
+%
+Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified at higher $n_{\rm cut}$.
+\AP{it is a bit difficult to read the xaxis label; an option (but i'm not sure if it will work) would be to have a 3x2 alignment, and keeping the same axis range for both cuts (for easier visual comparison)}
+\label{fig:dist}}
+\end{figure*}
+
+%\section{Basic physical properties}\label{sec:eqn}
+
+%\subsection{Virial Equilibrium and Larson's Relations}\label{sec:PVE}
+\subsection{Larson's Relations}\label{sec:PVE}
+
+In next sections, we examine and compare properties of the MCs with observations in the context of the Larson's relations \citep{Larson81a}.
+Namely, the linewidth-size, density-size, and mass-size relations.
+Larson's relations are adopted for the discussion in this work as they  describe the interactions between gravity and turbulence, and is the first set of relations used for studying star-forming molecular structure formation based on observables which has been routinely used for comparing properties of molecular structures in different galactic environments.
+% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
 
 % Relating Larson's law to stability and pressure (perhaps move this to other section?).
-A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
-a medium of pressure $P$ is described using the virial theorem:
-\begin{equation}
-\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
-\end{equation}
-where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
-$T$ is the volume term of the total kinetic energy (including thermal and
-bulk motions), $T_s$ is the surface term due to external pressure,
-$W$ is the gravity term, and $B$ is the magnetic term.
-In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
-\begin{equation}
-\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
+In general, the virial theorem for a distribution of gas can be written as
+\begin{equation}\label{eqn:virial_th_general}
+\frac{1}{2}\ddot I = 2(T - T_{\rm ext}) + W,
+\end{equation}
+where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia, $T$ is the internal energy of the gas, $T_s$ is external pressure support, and $W$ is the gravity energy.
+%
+Let us specialize to the case of a spherical self-gravitating molecular cloud of mass \AP{check the definitions} $M$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion.
+Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
+\begin{equation}
+\frac{1}{2}\ddot I = 3 M \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM^2}{R}\,,
 \label{eqn:virial}
 \end{equation}
-where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
-term is the gravity term, and the third term is the external pressure term.
-For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
-the LHS and the last term on the RHS vanish. The equation becomes:
-\begin{equation}
-\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
+where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the first term on the right hand side (RHS) is the pressure term from internal velocity dispersion, the second term the external pressure term, and the third term is is the gravity term.
+For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
+\begin{equation}
+\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM}\,,
 \label{eqn:alpha}
 \end{equation}
-where $\Gamma$ is set to 3/5 for a uniform sphere.
-We can define
-\begin{equation}
-V_0^2\equiv\frac{\sigma^2}{R},
-\end{equation}
-which is related to one of the Larson's relations (linewidth-size relation),
-which can be recast into the form of:
+where we have defined the virial parameter $\alpha_{\rm vir}$. It is convenient to introduce \AP{i do not fully follow the logic of the following passages}
+\begin{equation}
+V_0^2\equiv\frac{\sigma^2}{R},\,
+\end{equation}
+which is related to Larson's linewidth-size relation \citep{Larson81a}, which can be recast into the form of:
 \begin{equation}
@@
 which describes the external pressure needed to confine the gas inside a volume $V$.
-Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
-this equation using the following:
+\AP{please specify which eq.s you are referring to} Rearranging the equation and substituting for the surface density $\Sigma$\eq$M/\pi R^2$, we can express this equation using the following:
 \begin{equation}
@@
 \end{equation}
-Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
-$\sigma^2/R\propto\Sigma$, whereas
-Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
-needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
-In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$
-is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
-varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
-$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
-
-We use the virial parameter, which is defined by \Eq{alpha} and describes
-the balance between kinetic and gravitational potential energies,
-to quantify how stable an MC is.
-An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms
-and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that
-the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
-
-\subsection{Gravitational Instabilities}   \label{sec:Q}
+Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since $\sigma^2/R\propto\Sigma$, whereas Equation~\ref{eqn:v0} represents the locus along which external pressures $P_{\rm ext}$ are needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
+% (see\Fig{alpha27}).
+In other words, \AP{the following is a bit unclear} a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$; cf.
+expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+
+Summarizing, to quantify the stability of MC we use the virial parameter (\Eq{alpha}), which describes the balance between kinetic and gravitational potential energies.
+An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
+
+%\subsection{Gravitational Instabilities}\label{sec:Q}
+\subsection{Toomre stability}\label{sec:Q}
+
 The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-From virial theorem, Jeans 
-instability sets the scales at which gravitational potential overcomes kinetic energy. Namely, gravitational instabilities 
-dominates at scales $L > L_J$, where $L_J$ is the Jeans length. 
-However, centrifugal force resulting from differential rotation in disk galaxies can 
-inhibit collapse even on these scales. As a result, a disk is thought to be 
-unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set 
-% \propto \Sigma/B^2
-by the surface density of the disk and the angular velocity of the rotation.
-
-In theoretical and observational works, gravitational instability has been widely discussed in the 
-context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter 
-(or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
+\AP{i think we can partially cut the following} From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy.
+Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length.
+However, centrifugal force resulting from differential rotation in disk galaxies can inhibit collapse even on these scales.
+As a result, a disk is thought to be unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set by the surface density of the disk and the angular velocity of the rotation.
+
+In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e.
+close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
 % https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
@@
 % from linear analysis
-For {\it axisymmetric} mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk
-of finite thickness $h$ 
-is described by:
-\begin{equation}
-\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
+For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of \AP{does this hold for a thin disk?}finite thickness $h$ is described by \AP{do we have a classical reference to add here?}:
+\begin{equation}
+\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
 \label{eqn:3Ddisp}
@@
 \end{equation}
-% \kappa\propto\Omega
-The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and
-the third term describes pressure support.
-One can then define the so-called Toomre-Q parameter as:
-\begin{equation}
-Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
+The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support.
+Then the Toomre-Q parameter can be defined as \citep{Toomre64a}:
+\begin{equation}
+Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
 \label{eqn:Q}
 \end{equation}
-For $kh\ll1$, Equation~\ref{eqn:3Ddisp} reduces to the thin disk approximation, which 
-becomes unstable % perturbation grows exponentially in time
-for some $k$ when $\omega^2 < 0$ (or equivalently, $Q < 1$; \citealt{Toomre64a}).
-Under this condition (i.e., when local gravitational instability 
-overcomes support from pressure and rotation), fragmentation {\it can} happen. 
-% but further evolution depends on their EOS.
-%(e.g., instability impose by angular momentum from gas accretion from the cosmic web and
-%satellite galaxies and stellar feedback).
-% Note that fragmentation is expected to happen at critical scale length 
-% $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of 
-% GMCs. It should be clear that the instability sets the scales for fragmentation, but 
-% star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales.
-% The fragmented structures thus correspond to regions where $Q\lesssim1.
-Similarly, for a collisionless fluid, the Toomre $Q$ parameter is defined by:
-\begin{equation}
-Q\equiv\frac{\sigma\kappa}{3.36 G \Sigma}
-\end{equation}
-\citep{Toomre64a}.
-
-To account for stabilizing effect of both gas and stars and the non-negligible disk thickness, 
-% since thickness of a disk weakens the gravitational forces within the disk plane and lower the values for $Q$
-% Romeo:  The effect of thickness is to increase the stability parameter of each 
-% component by a factor T, which depends on the ratio of vertical to radial velocity dispersion, following eqn 8 of their paper.
-we consider the approximation for the effective two-component $Q_{\rm eff}$ parameter following \citet{Romeo11a} and
-\citet{Inoue16a} which is expressed as follows:
-\begin{equation}
-Q^{-1}_{\rm eff} =  \left\{
-				\begin{array}{lccr}
-					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
-                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\
-				\end{array} 
-			    \right.
-\end{equation}
-where $w$ is defined as:
-\begin{equation}
-w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
-\end{equation}
-and $T$ is approximated as:
-\begin{equation}
-T = \left\{
+In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < 1$ (or equivalently $\omega^2 < 0$).
+Physically, this situation happens when local gravitational instability
+overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
+% but further evolution depends on their EOS. (e.g., instability impose by angular momentum from gas accretion from the cosmic web and satellite galaxies and stellar feedback).
+% Note that fragmentation is expected to happen at critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of  GMCs.
+It should be clear that the instability sets the scales for fragmentation, but star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales.
+The fragmented structures thus correspond to regions where $Q\lesssim1.
+Similarly, for a collisionless fluid -- as an ensamble of stars -- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
+\begin{equation}
+Q_{\rm star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
+\end{equation}
+
+In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.][see also \citealt{Inoue16a}]{Romeo11a}.
+%
+The effect of disk thickness modify the $Q$ parameter for gas/star by accounting for the vertical velocity dispersion:
+\begin{equation}
+T_{x} = \left\{
 		\begin{array}{lccr}
@@
 \end{equation}
-
-For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the 
-importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
-
-\subsection{Key Properties of Clouds}
-
-% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
-% the mechanisms and physics of formation and evolution of molecular structures and \SF.
-In next section, we examine and compare properties of the MCs with
-observations in the context of the Larson's relations \citep{Larson81a}. 
-Namely, the linewidth-size, density-size, and mass-size relations.
-Larson's relations are adopted for the discussion in this work as they 
-describe the interactions between gravity and turbulence, and is the first set of
-relations used for studying star-forming molecular structure formation based on observables
-which has been routinely used for comparing properties of molecular structures in different galactic environments.
-% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
-
-Upon identifying the molecular structures, we extract properties such as
-mass ($M_{\rm cl}$),
-size ($R$),
-Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and
-gas surface density ($\Sigma_{\rm gas}$)
-to examine their dynamics.
-
-The mass of an MC is calculated from the uniformly-gridded 3D density field,
-integrating over all zones of the MC, multiplied by its volume.
-The size of an MC ($R$) is defined assuming spherical geometry (i.e.,
-the size is parameterized via the radius of a sphere, which has a volume corresponding to that of the identified MC).
-% {\AP The size is an effective radius, calculated from the total volume of the MC assuming spherical symmetry.}
-Since in \obs, dense gas contributes more to the observed linewidths than the more diffuse gas. We therefore calculate
-the non-thermal component of the velocity dispersion ($\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
-\begin{equation}
-\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
-\end{equation}
-which is summed over the cells composing each MC.
-The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
-\begin{equation}
-\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
-\end{equation}
-The local sound speed of all identified molecular complexes are much smaller compared to the their
-turbulent velocities\footnote{We find comparable velocity dispersion between that derived from
-taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that
-rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
-% We further quantify the contributions arising from galactic rotation and shear to the extracted velocity dispersions of the MCs in \Sec{Q}.
-In the subsequent sections, we adopt the root mean square of the velocity field
-as the velocity dispersion ($\sigma$). \label{ftn:veldisp}}.
-On average, the Mach number of the MCs corresponds to about $\mathcal{M}\approx50$.
-This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
-
-We show in \Fig{dist} the MC distributions in terms of their
-molecular gas masses, radii, and gas mass fractions, which we define as
-\begin{equation}
-f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
-\end{equation}
-where $M_*$ is the stellar mass.
-We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of
-the order of 10$^{6.5}$\,\Msun for the densest MC.
-% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
-We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
-snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).
-The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, 
-consistent with those observed in \z$\sim$2 galaxies in
-rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
-\caption{
-Distributions of mass, size, and gas mass fraction of MCs identified using
-the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
-Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified
-at higher $n_{\rm cut}$.
-\label{fig:dist}}
-\end{figure*}
-
-\section{Results: MC Properties and Cloud Scaling Relations}    \label{sec:results}
-\subsection{Single Snapshots}  \label{sec:singless}
-
-For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}),
-we identify a set of MCs. 
-Scaling relations for the MCs identified in the accretion phase are shown in top panels 
-of \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}, and in the bottom panels for the starburst phase.
-Regardless of the H$_2$ density cuts adopted,
-the MCs are found to have consistently high turbulences and surface densities in both stages.
-These correspond to MCs at the center of the main disk of \flower and
-occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-As we increase the density threshold, some of the MCs within the main disk break
-into multiple sub-MCs.
-As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
+and
+\begin{equation}
+Q^{\rm thick}_{x} = T_{x} Q\,,
+\end{equation}
+with $x$ indicating either gas or stars.
+%
+The combined effect of gas and stars can then be account by writing
+\begin{equation}\label{eqn:q_eff}
+%Q^{-1}_{\rm eff} =  \left\{
+%				\begin{array}{lccr}
+%					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
+%                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\
+%				\end{array} 
+%			    \right.
+Q^{-1}_{\rm eff} =  \left\{
+				\begin{array}{lccr}
+					     {\displaystyle\frac{w}{Q^{\rm thick}_{\rm star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\rm star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
+                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\rm star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\rm star} \leq Q^{\rm thick}_{\rm gas} \\
+				\end{array} 
+			    \right.
+\end{equation}
+where the relative weight $w$ is defined as:
+\begin{equation}
+w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
+\end{equation}
+\AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
+
+For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
+
+\section{Results: MC Properties and Cloud Scaling Relations}\label{sec:results}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_larsons.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_larsons.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_alphavir.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_alphavir.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16_PVE.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_PVE.png}
+\caption{
+\AP{different cuts, 2 selected evolutionary stages (left/right); I have not found a good clipping for the upper left panel} \AP{If you like the current arrangement please 1) increase a bit the size of the labels 2) put the legend only the right panels 3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage 4) I would use a perceptually increasing colorbar to indicate the different cuts 5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
+\label{fig:alpha16-28}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_larsons.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-larsons-highncut.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\caption{
+\AP{evolutionary stage (function of sfr), different cuts (left/right)}\AP{similarly to the previous figure for different cuts; we might visually distinguish the points different color codes for the SFR and $n_{cut}$}
+\label{fig:alpha16-28}}
+\end{figure*}
+
+\subsection{Single evolutionary stage}  \label{sec:singless}
+
+For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
+%
+Scaling relations for the MCs identified in the accretion phase are shown in top panels of \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}, and in the bottom panels for the starburst phase.
+%
+Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} high turbulences and surface densities in both stages.
+These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
+%
+As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
 
 % PVE
-We also compare the MCs identified in our simulations to
-those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see \Fig{alpha27}). 
-The V-shaped dashed lines in the figure show the loci along which the given external pressures are needed for
-MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
+We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see \Fig{alpha27}).
+The dashed lines in the figure show the loci along which the given external pressures are needed for MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
 Heyer+09).
-The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}).
-
+The MCs in the \AP{i do not find a clear introduction of satellite galaxies in the text} satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}) \AP{note that such numbers are consistet with the bulk of dense gas found in the simulation in the phase-space analysis in \citet{Pallottini17a}}.
+
+\subsection{Temporal evolution and cut dependence}\label{sec:ncut}
+% single Snapshot
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
+different sets of $n_{\rm cut}$ in identifying the MCs.
+%
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+cloud scaling relations).
+%
+In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%
+This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+Our results are therefore robust to the various density cuts of choice.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
+We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+
+\begin{comment}
 \begin{figure*}[htbp]
@@
 % Red lines show the relation obtained from \citet{}.
-Literature data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
+Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
 \label{fig:larsons_single}}
@@
 \end{figure*}
+\end{comment}
 
@@
 % column density) as fundamental properties of molecular cloud structure.
-Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales
-via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the law of constant column density,
-since cloud mass in \obs is sometimes derived by integrating
-over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).
+\AP{some of this symbols have been already introduced} Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
+This is also known as the law of constant column density, since cloud mass in \obs is sometimes derived by integrating over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).
 That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower % in its accretion phase 
-compared to
-observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF
-\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on
-Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
+We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
+%
 In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
-As shown in \Fig{MR}, the MCs identified 
-% in the accretion phase of 
-in \flower lie above this relation, along the locus
-with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
+As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
 We discuss this result in the following section.
@@
 \caption{
-Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols)
-compared to observational data of molecular clouds in the Milky Way associated with massive \SF
-(magenta circles, green stars, blue dots, and black triangles) and empirical relations
-established based on \obs of the Milky Way.
+Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
 Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
@@
 Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to
-lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
+The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to lines of constant surface density (i.e., Larson's third relation).
+This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
+\AP{same color code as in the panels with different ncut}
 \label{fig:MR}}
@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively. 
-Before accounting for contribution of the stellar component to the gravitational potential, 
-most MCs lie in regions of $\log{Q_{\rm gas}}\simeq$\,0 (see \Fig{Q}).
-Fragmentation are expected in regions of low Toomre $Q_{\rm eff}$ values.
-Further interpretation and implication of this is discussed in \Sec{origin}.
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified  in this evolutionary stage).
+Fragmentation are expected in regions of low Toomre $Q$ values.
+\AP{why then we do not postpone the figure presentation?} Further interpretation and implication of this is discussed in \Sec{origin}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0}.png}
+\caption{\AP{let me know which scheme you prefer (as per mail) or you would like a different plotting scheme; in any case, i guess we should go from $\log \sigma$ to $\sigma$; additionally we might want to use shared colorbars (e.g.
+$\Sigma_{gas}\,,\Sigma_{\star}-> \Sigma$) and write gas and stars as white text on the maps}
+%
+}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
+\caption{\AP{if we keep a 3x1 scheme we should probably use horizontal colorbars or a signle vertical one, with gas stars and combined written as an inset; probably the 50 pc smoothing radius is be too large, we might want to go to 30 or 20}
+%
+}
+\end{figure*}
+
+\begin{comment}
 
@@
 identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-Markers in the surface density and Toomre $Q$ maps
-correspond to the mass-weighted positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
-Positions of sub-MCs identified using lower $n_{\rm cut}$ are not shown (but see top row of \Fig{Qeff} for an example). 
-Before accounting for contribution of the stellar component to the 
-gravitational potential, we find that most MCs lie in regions of 
-$\log{Q_{\rm gas}}\simeq$\,0. 
+Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
+Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
 \label{fig:Q}}
@@
 \includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
-\includegraphics[trim=10 0 0 10, clip, width=0.4\textwidth]{\figpath/{ss16_star_SD_proj_0_zoom_2.0_kpc}.png}  
 \includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
-\includegraphics[trim=30 25 30 20, clip, width=0.38\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png} 
+\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
 \includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
@@
 Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
-and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as star markers.
-Bottom row: Zoom-in view of the effective $Q_{\rm eff}$ (left) and gas surface density (right) maps.
-Markers in the bottom left Toomre $Q$ map correspond to positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
+and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
+Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
+Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
 Modest smoothing has been applied to the maps. 
@@
 \end{figure*}
-\clearpage
+%\clearpage
+
+\end{comment}
 
@@
 %--------------------------------------------------------------------------
-\section{Discussions and Implications}     \label{sec:diss}
+\section{Discussions and Implications}\label{sec:diss}
 
@@
 
-The population of sub-MCs has dynamics largely
-similar to those observed
-in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
-terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
-e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity
-dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+The population of \AP{i would drop the sub- notation, and simply call everything MCs} sub-MCs has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+%
 % velocity dispersion, larsons
-Their velocity dispersions are also comparable to those observed in the inner Milky way and
-nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies
-along the locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities are expected since
-they are located in the nuclear regions of the
-galaxy, where the potential well is also deeper. The higher velocity dispersions (see also 
-footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp})
-of these MCs can also be understood as they have experienced more recent episodes
-of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
-In fact, by $z\simeq$\,7.2 (i.e., the snapshot corresponding to an early phase of accretion as
-shown in \Fig{SFH}a), \flower has assembled
-a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion
-is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
-
-The high pressure observed in \flower is comparable to what has been 
-observed in local ultra-luminous IR galaxies (ULIRGs); however, the
-molecular clouds in the latter are concentrated within their 
-central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun
-\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are
-found throughout the disk. This difference likely stems from the different physical mechanisms giving rise
-to the formation (and thus the nature) of these molecular structures.
-For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud
-collision after large amount of gas from the pair of progenitor galaxies
-are being funneled toward the central region \citep{Tan00a, Wu18a}.  % Tasker09a
-On the other hand, the highly turbulent structures of \flower likely result from 
-constant cold gas accretion onto the entire galaxy (without
-requiring gas to be funneled into the central region).
-This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed
-in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed 
-size scales could also result from resolution limit where the true physical scales of MCs in
-$z$\,\ssim2 galaxies could be smaller in reality.
+%
+Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
+Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep.
+The higher velocity dispersions (see also footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
+%
+In fact, by $z\simeq$\,7.2 (\AP{i would always refer to the evolutionary stage name, once in defined in Fig.
+1; we might want to use italic to underline it is a definition} i.e., the evolutionary stage corresponding to an early phase of accretion as shown in \Fig{SFH}a), \flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
+Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
+
+The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk.
+This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+%
+For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
+% Tasker09a
+On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} (without requiring gas to be funneled into the central region).
+This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
+%
 The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
@@
 % mass-size relation
-In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, 
-which is an empirical relation corresponding to the threshold for massive \SF, but lies
+In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, which is an empirical relation corresponding to the threshold for massive \SF, but lies
 %The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
@@
 below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
-This can be understood by acknowledging the fact that a H$_2$ molecular cloud
-does not necessary contain CO (e.g., as CO forms deeper in molecular clouds),
-and that our simulation does not have enough resolution to directly form CO\footnote{
-In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we
-model the internal structure of MC within each cell in our simulation.}.
-That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the
-fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are
-observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
+This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
+%
+That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO \AP{this AV is also consistent with the result reported in \citet{Behrens18a}}.
 
 % different evolutionary stages
-In the scaling relations examined, we find similar MC properties 
-in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of
-\flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
-That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which
-are separated by $\simeq$300\,Myr.
+In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
+That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
 
 \subsection{Origin and Physical Scales of the MCs} \label{sec:origin}
-The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller
-substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}). Overall,
-the MCs we identified are much bigger in size and mass than nearby GMCs, 
-but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
+
+The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}).
+Overall, the MCs we identified are much bigger in size and mass than nearby GMCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
 
 % mass scale
-Observations of nearby gas-rich galaxies such as M64 and NGC\,253
-show higher velocity dispersions compared
-to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of
-Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
+Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.
+% also higher $P_{\rm int}$,
 % which is $\propto\rho\sigma^2$
 % M51: Colombo+14
-However, clouds in nearby gas-rich galaxies are bigger in size (approximately
-an order of magnitude) and mass (approximately two orders of magnitude).
-These bigger clouds have been interpreted as a results of their 
-higher gas mass fractions and
-surface densities and velocity dispersions, since
-fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$
-and Jeans mass $M_J\propto\sigma^4/\Sigma$
-for dispersion-supported structures.
-
-Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass,
-a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of
-$\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$
-yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
-Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy
-simulations done at higher resolution (e.g., \citealt{Behrendt16a}).
-Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations
-since they adopt non-cosmological initial conditions.
-That said, this is reassuring --- our results are not far off in spite of the resolution ($l\approx$\,30\,pc).
+However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
+These bigger clouds have been interpreted as a results of their higher gas mass fractions and surface densities and velocity dispersions, since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.
+
+Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
+%
+Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (\AP{which was Behrendt16a resolution?
+I would report the value} e.g., \citealt{Behrendt16a}).
+Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
+That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l\approx$\,30\,pc).
 
@@
 % alpha parameters
-As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which 
-is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-For the MCs in the satellite galaxies, a lower virial parameter is found 
-compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
-stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
-\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
+%
+For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+\AP{hum, I do not follow this point, but it might be due to satellite definition; to me satellite is a separate galaxy (which typically has a lower potential well, thus feedback should be more effective); if by satellite you mean merging satellite we should check its recent stellar activity; if it is negligible, that is why they have lower feedback and subsequently values of $\alpha_{vir}$} Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
 % pext
 As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
-The lower virial parameter and external pressure of the sub-MCs
-compared to their parent MCs are consistent with
-the notion that collapsing structures result from local gravitational
-instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
-which are supported by turbulence and rotation on large scales.
+The lower virial parameter and external pressure of the sub-MCs compared to their parent MCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
 %Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
@@
 
-For MCs in the satellite galaxies, we find low pressures and virial parameters 
-which are comparable to those found in clouds formed in the galactic disks 
-($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures,
-and thus, \SF is expected to continue 
-as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
-
-The apparently large virial parameters seen in the MCs of \flower can be understood using the 
-Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,$-$\,\ref{fig:Qeff}). 
-We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
-instability against axisymmetric perturbations), but  
-further evolution/collapse depends on the dynamics or equation of state of the gas. 
-Such fragmentation is expected to take place at the
-critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
-Second, this fragmentation scale is greater than the typical size of GMCs. This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs
-correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales. 
-Thus, the high virial parameter found 
-for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure 
-and rotation) and surface density, indicate that most of them are not collapsing structures. 
-As such, some MCs are found to lie in regions of $Q>1$. 
+For MCs in the satellite galaxies, we find low pressures and virial parameters  which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus,\AP{i suspect a low or null \SF in the satellites, i.e.
+some of them should have $f_gas = 1$, i.e.
+no stars} \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+The apparently large virial parameters seen in the MCs of \flower can be understood using the Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,$-$\,\ref{fig:Qeff}).
+We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
+%
+Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$ \AP{can we give a typical number, given the mean sigma and kappa inside clumps?}.
+Second, this fragmentation scale is greater than the typical size of GMCs.
+This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
+%
+Thus, the high virial parameter found for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
+As such, \AP{some or most?} some MCs are found to lie in regions of $Q>1$.
 % some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
-Only in (the denser) regions with a low Toomre $Q$ parameter and 
-when energy can be dissipated on a timescale 
-that is shorter than the timescale over which it gains energy (e.g., heating) 
-correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
-This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$
-nature of most MCs of \flower and its relatively high SFR.
-That is, if most of the molecular gas in \flower are stable against collapse, 
-how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
-The discrepancy can be explained in two ways.
-First, our results are limited by the resolution of the simulation, such that, in each MC, there
-likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
+Only in (the denser) regions with a low Toomre $Q$ parameter and when energy can be dissipated on a timescale that is shorter than the timescale over which it gains energy (e.g., heating) correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
+%
+This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$ nature of most MCs of \flower and its relatively \AP{however, the high sfr is in some of the clumps, which does not necessarily correspond to the location of current H2 rich clumps} high SFR.
+That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
+%
+\AP{however, such high-sfr is only seen in case (b), while high alpha vir are seen in all cases; i do not fully see the discrepancy} The discrepancy can be explained in two ways.
+First, our results are limited by the resolution of the simulation, such that, in each MC, there likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
 as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
-Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
-large-scale gravitational potential and differential rotation.
-This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
-MCs \citep{Clark04a, Clark05a}.
-Additionally, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
-can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation
-and collapse on smaller scales to trigger \SF.
+%
+Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by large-scale gravitational potential and differential rotation.
+This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound MCs \citep{Clark04a, Clark05a}.
+%
+Additionally, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
 
@@
 We decompose the molecular structures into non-overlapping tiles
-by identifying a set of different density contours at different snapshots.
+by identifying a set of different density contours at different evolutionary stages.
 Using volumetric H$_2$ is essentially similar to identifying molecular structures using
@@
 We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
-TKDL acknowledges support by the NSF through award SOSPA4-009
-from the NRAO and support from the Simons Foundation.
+%
+TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
+%
 AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
-This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA)
-held at the Center for
-Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli
-Foundation and the Simons Foundation.
-We thank the KSPA Scientific and Local Organizing Committees, and the program founder,
-Pascale Garaud, for supporting the genesis of this work.
-We also thank the Center for Cosmology and Particle Physics
-at the New York University
-for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
-This research has made use of NASA's Astrophysics Data System Bibliographic Services
-and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
+%
+This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018.
+The program was co-funded by the Kavli Foundation and the Simons Foundation.
+%
+We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
+%
+We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
+%
+This research has made use of NASA's Astrophysics Data System Bibliographic Services.
+%
+We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk2011a}.
+%
+%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
 
 \bibliographystyle{yahapj}
-\bibliography{master_cleanup}
-
+\bibliography{master_cleanup,codes}
+
+\begin{comment}
 \appendix
-\section{Variation in MC Properties Depending on the Choice of Density Cuts and
-Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
+\section{Variation in MC Properties Depending on the Choice of Density Cuts and Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
 % single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
-to test
-the robustness of our results against the choice of density threshold by adopting
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
 different sets of $n_{\rm cut}$ in identifying the MCs.
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
-dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the snapshots and
-find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
-MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
 cloud scaling relations).
-In addition, for the densest MC in the main disk of \flower, we find that while
-its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
-the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-This lack of variation is reassuring, in the sense that at least on the scales studied here,
-the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+%
+In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%
+This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
 Our results are therefore robust to the various density cuts of choice.
@@
 % temporal evolution in Cloud Dynamics
-We show the properties of all MCs identified across all snapshots
-in \Fig{larsons16-28} and \Fig{alpha16-28}.
+We show the properties of all MCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
 We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
@@
 \caption{
-Comparison of MCs identified across all snapshots (over 700\,Myr; star symbols)
+%Comparison of MCs identified across all evolutionary stages (over 700\,Myr; star symbols)
 to those observed in nearby and \z$\sim$2 star-forming galaxies
 in the context of the linewidth-size relation.
-% showing variations in their properties at
-% the different evolutionary phases of \flower and with varying SFRs.
-Bottom panel corresponds to including only the denser substructures/sub-MCs identified in \flower
+%Bottom panel corresponds to including only the denser substructures/sub-MCs identified in \flower
 (i.e., MCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
@@
 \caption{
-Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCs identified across all snapshots 
+Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCs identified across all evolutionary stages 
 (i.e., with different SFR). Star symbols are color-coded by increasing SFR.

### 2019-03-11 calc_sfr_fromParticles.py
cmap, fontsize

@@ -22,7 +22,8 @@ import numpy as np
 import os
 from pymses.analysis.visualization import *
 from plot_modules.plot_cloud_prop import setup_plot
-
+from matplotlib import cm
+cmap     = cm.get_cmap('magma')
 
 
 if __name__ == '__main__':
@@ -137,13 +138,15 @@ if __name__ == '__main__':
 
         size_region_kpc = camera_in['region_size'][0] * ro.info['unit_length'].express(C.kpc)
         bu = ax.imshow(np.log10(mapp),extent = [-size_region_kpc/2,size_region_kpc/2,-size_region_kpc/2,+size_region_kpc/2]
-                       ,vmin = z1, vmax = z2
+                       ,vmin = z1, vmax = z2,
+                       cmap=cmap
                       )
-        plt.ylabel("kpc")
-        plt.xlabel("kpc")
+        plt.ylabel("kpc", fontsize=18)
+        plt.xlabel("kpc", fontsize=18)
+        plt.tick_params(which='minor', length=4)
         #
         cbar = fig.colorbar(bu)
-        cbar.set_label(r"$\log \Sigma_{\star}$" + r"[M$_{\odot}\,{\rm pc}^{-2}]$")
+        cbar.set_label(r"$\log \Sigma_{\star}$" + r"[M$_{\odot}\,{\rm pc}^{-2}]$", fontsize=18)
         cbar.set_clim(z1,z2)
         plt.tight_layout()
         plt.savefig(stardir + "star_" + str(ssnum) + '.png')
@@ -214,8 +217,8 @@ if __name__ == '__main__':
               print '    ',name_out
             plt.figure()
             plt.plot(t_binned, y)
-            plt.ylabel("dM/dt [Msun/yr]")
-            plt.xlabel("Age of Galaxy [Myr]")
+            plt.ylabel("SFR " + r"[$M_{\odot}\,yr^{-1}$]", fontsize=18)
+            plt.xlabel("Age of Galaxy [Myr]", fontsize=18)
             plt.title(" SFR of Main Galaxy in snapshot " + str(ssnum) + " averaged over " + str(int(it)) + " Myr")
             plt.tight_layout()
             plt.savefig(out_name)

### 2019-03-11 plot_modules/plot_cloud_prop.py
fontsize stuff

@@ -16,21 +16,22 @@ def setup_plot():
     # print(matplotlib.matplotlib_fname())
 
     matplotlib.rcParams.update({'figure.figsize': (8, 5)    # inches
-                                , 'font.size': 12      # points
+                                , 'font.size': 16      # points
                                 , 'legend.fontsize': 10      # points
                                 , 'lines.linewidth': 2       # points
                                 , 'axes.linewidth': 1       # points
                                 , 'axes.prop_cycle': cycler('color', 'bgrcmyk')
                                 , 'text.usetex': True    # Use LaTeX to layout text
                                 , 'font.family': "serif"  # Use serifed fonts
-                                , 'xtick.major.size': 10     # length, points
+                                , 'xtick.major.size': 13     # length, points
                                 , 'xtick.major.width': 1     # points
-                                , 'xtick.minor.size': 6     # length, points
+                                , 'xtick.minor.size': 8     # length, points
                                 , 'xtick.minor.width': 1     # points
-                                , 'ytick.major.size': 10     # length, points
+                                , 'ytick.major.size': 13     # length, points
                                 , 'ytick.major.width': 1     # points
-                                , 'ytick.minor.size': 6     # length, points
-
+                                , 'ytick.minor.size': 8     # length, points
+                                , 'xtick.labelsize': 14
+                                , 'ytick.labelsize': 14
                                 , 'ytick.minor.width': 1     # points
                                 , 'font.serif': ("Times", "Palatino", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
                                 })

### 2019-03-11 plotSS.py
pdf instead of png

@@ -163,7 +163,7 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     fig.subplots_adjust(hspace=0.45)
     plt.tick_params(which='minor', length=4)
 
-    plt.savefig(plotdir + 'minmaxNcut_basicDistributions.png', \
+    plt.savefig(plotdir + 'minmaxNcut_basicDistributions.pdf', \
                 bbox_inches='tight')
     plt.close()
 
@@ -259,12 +259,12 @@ if __name__ == '__main__':
     #         count += 1
     # print count
 
-    # plotting_procedure(16, 28, pattern="0.32")
-    # plotting_procedure(16, 28, pattern="0.53")
-    # plotting_procedure(16, 28, pattern="0.88")
-    # plotting_procedure(16, 28, pattern="1.47")
-    # plotting_procedure(16, 28, pattern="2.45")
-    # plotting_procedure(16, 28, pattern="4.08")
-    # plotting_procedure(16, 28, pattern="6.81")
-    # plotting_procedure(16, 28, pattern="11.36")
-    # plotting_procedure(16, 28, pattern="18.96")
+    plotting_procedure(16, 28, pattern="0.32")
+    plotting_procedure(16, 28, pattern="0.53")
+    plotting_procedure(16, 28, pattern="0.88")
+    plotting_procedure(16, 28, pattern="1.47")
+    plotting_procedure(16, 28, pattern="2.45")
+    plotting_procedure(16, 28, pattern="4.08")
+    plotting_procedure(16, 28, pattern="6.81")
+    plotting_procedure(16, 28, pattern="11.36")
+    plotting_procedure(16, 28, pattern="18.96")

### 2019-03-12 WRITEUP/ms.tex

@@
 
+\DL{Maybe we will have to do it that way, and I will manually maintain my copy on the repo and on my macbook?}
+
 The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
@@
 %
-In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
 Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
@@
 It is therefore a prototypical galaxy at \z$\sim$\,6.
+For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}\simeq$\,15\,kpc.
 
@@
 \centering
-\includegraphics[trim=10 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
 \caption{
-    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.\AP{please rearrange the maps such that either i) they have an L shape ii) they are all bewlo the SFR; numbers on the axis are too small, and phase (a) is missing the colorbar; a single colorbar for the star maps might substitute the current 2 ones; please use magma colorbar for the maps (or in any case the colorbar that has been select for for $\Sigma$ trhought the paper)}
+    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
 \label{fig:SFH}}
@@
 
-Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), in \Sec{singless} \AP{but we both give the analysis for 2 stages for maps and all the stages in the scaling relation, is it correct?
-if so, this point should be made clearer here (or in the next section)} our work is focused on the analysis of two of its most extreme evolutionary stages, to illustrate the salient points of the discussion presented in this paper.
-The two phases correspond to i) when \flower is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such pahses are expected to bracket the most extreme variations in the cloud dynamics.
+Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), we focus this work on the analysis of two of its most extreme evolutionary 
+stages (see \Sec{singless}), to illustrate the salient points of discussion presented in this paper.
+The two phases correspond to i) when \flower 
+is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics. 
+For completeness, we also show the results (in terms of the scaling relations presented) for 
+the other evolutionary stages traced in the simulation.
+
+Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower,
+which is $\sim$\,1\,kpc in radius.
 
@@
 
-To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
+To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
 %
@@
 \caption{
-Examples showing the MCs identified in our simulation by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text).
+Examples showing the MCs identified in the accreting phase of \flower by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text).
 Color shows the H$_2$ surface density, weighted by the column density.
-\AP{I would use the label $n_{\rm H2}$ instead of $n({\rm H2})$; i would add the corresponding $n_{cut}= ...$ in withe the lower right corner of each right panel; in the caption I would add which stage is the figure extracted from; optionally, the 3 row might be substituted by a single row with cuts of different colors (if yt allows ...)}
 \label{fig:MC}}
@@
 
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center\footnote{\AP{i would move this note to the (main text of the) section introducing althaea}For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}$\ssim15\,kpc.}.
+In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center.
 %
@@
 % the mechanisms and physics of formation and evolution of molecular structures and \SF.
-Upon identifying the molecular structures, we extract properties such as mass (\AP{we should uniform the notation} $M_{\rm cl}$), effective size ($R$), \AP{introduced here but not used except for comparison with vallini (in the text); maybe we can remove it} Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
+Upon identifying the molecular structures, we extract properties such as the H$_2$ gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
 
@@
 %
-In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
-We therefore calculate the non-thermal component of the velocity dispersion (\AP{check the definitions, we are using multiple symbols to indicate the same things} $\sigma_{\rm NT}$) of each MC as a density-weighted quantity:
+The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
+\begin{equation}
+\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
+\label{eqn:veldisp}
+\end{equation}
+% 
+In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate 
+each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is 
+calculated as follows:
 \begin{equation}
@@
 where the sum is done for the cells composing each MC.
-\AP{I would first introduce the velocity dispersion and the separate them in thermal and non thermal component; also, even $c_s$ is density weighted average} The total velocity dispersion includes contributions from the thermal sound speed ($c_s$):
-\begin{equation}
-\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
-\end{equation}
-The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.
-\AP{isn t this definition already given in the main text?} In the subsequent sections, we adopt the root mean square of the velocity field as the velocity dispersion ($\sigma$).
-\label{ftn:veldisp}}.
+The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.}.
 On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
@@
 \begin{equation}
-f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
+f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_*\right)},
 \end{equation}
-where $M_*$ is the stellar mass withing the MC volume.
+where $M_*$ is the stellar mass within the MC volume.
 %
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
-\caption{Distributions of mass, size, and gas mass fraction of MCs identified using the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
-%
-Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified at higher $n_{\rm cut}$.
-\AP{it is a bit difficult to read the xaxis label; an option (but i'm not sure if it will work) would be to have a 3x2 alignment, and keeping the same axis range for both cuts (for easier visual comparison)}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
+Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}
@@
 %
-Let us specialize to the case of a spherical self-gravitating molecular cloud of mass \AP{check the definitions} $M$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion.
+Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion.
 Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
 \begin{equation}
-\frac{1}{2}\ddot I = 3 M \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM^2}{R}\,,
+\frac{1}{2}\ddot I = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
 \label{eqn:virial}
@@
 \begin{equation}
-\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM}\,,
+\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM_{\rm cl}/R} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
 \label{eqn:alpha}
 \end{equation}
-where we have defined the virial parameter $\alpha_{\rm vir}$. It is convenient to introduce \AP{i do not fully follow the logic of the following passages}
+where we have defined the virial parameter $\alpha_{\rm vir}$.
+
+\AP{i do not fully follow the logic of the following passages}
+\DL{need some work to clarify this para}
+Motivated by the Larson's relations, we express the observable quantities in the following forms:
 \begin{equation}
@@
 \begin{equation}
-P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
+P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \frac{\Gamma G M_{\rm cl}^2}{4\pi R^4},
 \label{eqn:pext}
@@
 Summarizing, to quantify the stability of MC we use the virial parameter (\Eq{alpha}), which describes the balance between kinetic and gravitational potential energies.
-An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
+An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure in \obs \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
+To facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to 
+the stellar component.
 
@@
 The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-\AP{i think we can partially cut the following} From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy.
+\AP{i think we can partially cut the following} \DL{probably, but I am just being explicit here to help remind myself what am I trying to say.}
+From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy.
 Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length.
@@
 % from linear analysis
-For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of \AP{does this hold for a thin disk?}finite thickness $h$ is described by \AP{do we have a classical reference to add here?}:
+For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of 
+finite thickness $h$ is described by 
 \begin{equation}
@@
 \begin{equation}
-\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
+\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,,
 \label{eqn:kappa}
 \end{equation}
+\citep{Romeo92a}.
 The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support.
@@
 \AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
+\DL{this is small $w$. Whether or not we need the Larson's relation stuff, I think those eqns there help understand the motivation 
+behind relating aa with bb and bb and cc, etc, in the Larson's relations?}
 
@@
 \caption{
-\AP{different cuts, 2 selected evolutionary stages (left/right); I have not found a good clipping for the upper left panel} \AP{If you like the current arrangement please 1) increase a bit the size of the labels 2) put the legend only the right panels 3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage 4) I would use a perceptually increasing colorbar to indicate the different cuts 5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
+Linewidth-size relation (top), 
+{\bf .... (middle), and blah blah (bottom)}
+for MCs (star symbols) 
+identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
+Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
+\AP{ have not found a good clipping for the upper left panel} 
+\AP{please 1) increase a bit the size of the labels 2) put the legend only the right panels 
+3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage 
+4) I would use a perceptually increasing colorbar to indicate the different cuts 
+5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
 \label{fig:alpha16-28}}
@@
 %
-Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} high turbulences and surface densities in both stages.
+Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} \DL{?}
+high turbulences and surface densities in both stages.
 These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
@@
 Heyer+09).
-The MCs in the \AP{i do not find a clear introduction of satellite galaxies in the text} satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}) \AP{note that such numbers are consistet with the bulk of dense gas found in the simulation in the phase-space analysis in \citet{Pallottini17a}}.
+The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}), which 
+is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.
 
@@
 % column density) as fundamental properties of molecular cloud structure.
-\AP{some of this symbols have been already introduced} Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
-This is also known as the law of constant column density, since cloud mass in \obs is sometimes derived by integrating over the mass surface density ($\Sigma$), which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).
+Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
+This is also known as the law of constant column density, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).
 That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified  in this evolutionary stage).
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see also \Fig{h2density} for an example of MCs identified in this evolutionary stage of \flower
+for different $n_{\rm cut}$).
 Fragmentation are expected in regions of low Toomre $Q$ values.
-\AP{why then we do not postpone the figure presentation?} Further interpretation and implication of this is discussed in \Sec{origin}.
+\AP{why then we do not postpone the figure presentation?} \DL{I am not sure if I should first show all the plots in Sec 4 and the discuss in details in Sec 5 or what.
+I guess we could just show
+in Sec 5.}
+Further interpretation and implication of this is discussed in \Sec{origin}.
 
@@
 \includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
-\caption{\AP{if we keep a 3x1 scheme we should probably use horizontal colorbars or a signle vertical one, with gas stars and combined written as an inset; probably the 50 pc smoothing radius is be too large, we might want to go to 30 or 20}
+\caption{\AP{we should probably use horizontal colorbars or a signle vertical one, with gas stars and combined written as an inset; probably the 50 pc smoothing radius is be too large, we might want to go to 30 or 20}
 %
@@
 
-The population of \AP{i would drop the sub- notation, and simply call everything MCs} sub-MCs has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+The MCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
 %
@@
 %
-That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO \AP{this AV is also consistent with the result reported in \citet{Behrens18a}}.
+That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
 
@@
 Thus, the high virial parameter found for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
-As such, \AP{some or most?} some MCs are found to lie in regions of $Q>1$.
+As such, \AP{some or most?}
+\DL{I think we can keep "some"?}
+some MCs are found to lie in regions of $Q>1$. 
 % some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
@@
 This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$ nature of most MCs of \flower and its relatively \AP{however, the high sfr is in some of the clumps, which does not necessarily correspond to the location of current H2 rich clumps} high SFR.
-That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
+That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
 %
-\AP{however, such high-sfr is only seen in case (b), while high alpha vir are seen in all cases; i do not fully see the discrepancy} The discrepancy can be explained in two ways.
+\AP{however, such high-sfr is only seen in case (b), while high alpha vir are seen in all cases; i do not fully see the discrepancy} 
+\DL{maybe it's just we should also account for stellar mass in alpha vir, but leave it out when we compare that with observations?}
+The discrepancy can be explained in two ways.
 First, our results are limited by the resolution of the simulation, such that, in each MC, there likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),

### 2019-03-12 toomre.py
share cbar, inset anootation

@@ -1086,7 +1086,7 @@ class ToomreAnalyze_2comp(object):
     topBound = np.argmin(abs(yruler - central_kpc_one_side))
     bottomBound = np.argmin(abs(yruler + central_kpc_one_side))
 
-    return bottomBound, topBound, leftBound,rightBound,xruler,yruler 
+    return bottomBound, topBound, leftBound,rightBound,xruler,yruler
 
   def plot_Q_eff_zoom(self, central_kpc_one_side=None, annotate_clump=False, clump_list_filename=None):
 
@@ -1159,10 +1159,10 @@ class ToomreAnalyze_2comp(object):
     tmp = gaussian_filter(self.Q_star.veldisp_vertical_plane.convert_to_units('km/s').value,self.smooth_size)
     self.Q_star.veldisp_vertical_plane = YTArray(tmp, 'km/s')
 
-  def wrapper_plot(self,ax= None
+  def wrapper_plot(self, fig=None, ax=None
                   ,mappa= None, label= '', tipo= ''
                   ,bottomBound=0, topBound=-1, leftBound=0,rightBound=-1
-                  ,xruler= None,yruler= None 
+                  ,xruler= None,yruler= None, showcbar=True
                   ):
 
 
@@ -1182,14 +1182,28 @@ class ToomreAnalyze_2comp(object):
               extent=(xruler[leftBound],xruler[rightBound],yruler[bottomBound],yruler[topBound]),
               cmap=cmap_plt, vmin= vmin_plt,vmax=vmax_plt)
     if tipo == 'Q':
-      cbar = plt.colorbar(im, extend='both',    # arrows in both direction
-                         ticks=[-1, 0, 1]
-                        )
-      cbar.ax.set_yticklabels([r'$<-1$', r'$0$', r'$>1$'])
-
-    else:
+      if showcbar:
+        # cbar = plt.colorbar(im, extend='both',    # arrows in both direction
+        #                    ticks=[-1, 0, 1],
+        #                    orientation='horizontal',
+        #                    location='top'
+        #                   )
+        ax_cbar = fig.add_axes([0.15, 0.95, 0.8, 0.03])
+        cbar = plt.colorbar(im, extend='both',    # arrows in both direction
+                           ticks=[-1, 0, 1],
+                           orientation='horizontal',
[…]

### 2019-03-12 WRITEUP/ms.tex
updated fig and text correspondingly

@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see also \Fig{h2density} for an example of MCs identified in this evolutionary stage of \flower
-for different $n_{\rm cut}$).
-Fragmentation are expected in regions of low Toomre $Q$ values.
-\AP{why then we do not postpone the figure presentation?} \DL{I am not sure if I should first show all the plots in Sec 4 and the discuss in details in Sec 5 or what.
-I guess we could just show
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Q} 
+(see also \Fig{h2density} for an example of MCs identified in this evolutionary stage of \flower
+for different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
+ \AP{why then we do not postpone the figure presentation?} \DL{I am not sure if I should first show all the plots in Sec 4 and the discuss in details in Sec 5 or what. I guess we could just show
 in Sec 5.}
+We discuss the importance of accounting for stellar contributions and the effect of the thickness of the disk to the total stability criterion. 
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in 
+governing the stability of the MCs against $m$\eq0 perturbations.
+This can be understood since stars in \flower dominates in mass in the central part of the galaxy, 
+so their gravitational potential provides a non-negligible contribution to the stability. 
+Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
+scale height ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc$\simeq$\,0.15) and since \flower is more of a warped disk.
+That is, some MCs are located in regions of $Q_{\rm gas}$\ssim1, but 
+when including the effects of stars and thickness of the disk (via $\sigma_z$),
+they are consistent with $Q_{\rm gas} > 1$.
 Further interpretation and implication of this is discussed in \Sec{origin}.
@@
 \includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0}.png}
-\caption{\AP{let me know which scheme you prefer (as per mail) or you would like a different plotting scheme; in any case, i guess we should go from $\log \sigma$ to $\sigma$; additionally we might want to use shared colorbars (e.g.
+\caption{\AP{guess we should go from $\log \sigma$ to $\sigma$; additionally we might want to use shared colorbars (e.g.
 $\Sigma_{gas}\,,\Sigma_{\star}-> \Sigma$) and write gas and stars as white text on the maps}
@@
 \includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
-\caption{\AP{we should probably use horizontal colorbars or a signle vertical one, with gas stars and combined written as an inset; probably the 50 pc smoothing radius is be too large, we might want to go to 30 or 20}
-%
-}
+\caption{
+Toomre $Q$ maps derived from the gas (left) and stellar (middle) components, respectively. 
+A map of the effective two-component Toomre $Q_{\rm eff}$ parameter is shown in the right panel. 
+All maps are projected onto the $xy$-plane.
+Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
+% Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
+A smoothing length of 30\,pc has been applied to the maps.
+A divergent colormap is used for the Toomre $Q$ map to facilitate 
+identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ 
+are likely gravitationally unstable.
+\label{fig:Qeff}}
 \end{figure*}

### 2019-03-12 WRITEUP/ms.tex
add zoom in plot

@@
 \centering
-\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
-\caption{
-Toomre $Q$ maps derived from the gas (left) and stellar (middle) components, respectively. 
-A map of the effective two-component Toomre $Q_{\rm eff}$ parameter is shown in the right panel. 
+\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
+\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.png}
+\caption{
+Toomre $Q$ maps derived from the 
+central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
+Gas-only $Q$ are shown in the left panels and stellar-only $Q$ are shown in the middle panels.
+Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels. 
 All maps are projected onto the $xy$-plane.
 Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
-% Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
 A smoothing length of 30\,pc has been applied to the maps.
 A divergent colormap is used for the Toomre $Q$ map to facilitate 
-identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+identification of regions above and below $\log{Q}$\eq0.
 Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ 

### 2019-03-12 toomre.py
shared cbar for Sigma and sigma 2by2 plot

@@ -1199,11 +1199,30 @@ class ToomreAnalyze_2comp(object):
         cbar.set_label(r'$\log{Q}$', fontsize=13, labelpad=5)
       else:
         cbar = None
-    elif showcbar:
-      cbar = plt.colorbar(im)
-
-    if tipo != 'Q' and showcbar:
-      cbar.set_label(label, fontsize=16)
+    elif tipo == "Sigma":
+      if showcbar:
+        ax_cbar = fig.add_axes([0.15, 0.935, 0.8, 0.01])
+        cbar = plt.colorbar(im,
+                            orientation='horizontal',
+                            cax=ax_cbar, ticklocation='top'
+                            )
+        cbar.ax.tick_params(length=6)
+        label = r'$\log{\Sigma}$ [M$_{\odot}$~pc$^{-2}$]'
+        cbar.set_label(label, fontsize=16)
+      else:
+        cbar = None
+    elif tipo == "sigma":
+      if showcbar:
+        ax_cbar = fig.add_axes([0.15, 0.492, 0.8, 0.01])
+        cbar = plt.colorbar(im,
+                            orientation='horizontal',
+                            cax=ax_cbar, ticklocation='top'
+                            )
+        cbar.ax.tick_params(length=6)
+        label = r'$\sigma$ [km\,s$^{-1}$]'
+        cbar.set_label(label, fontsize=16)
+      else:
+        cbar = None
 
     return ax,cbar
 
@@ -1241,22 +1260,30 @@ class ToomreAnalyze_2comp(object):
 
     if type_plots in ['2by2','3by2']:
 
-      fig = plt.figure(figsize=(9, 8))
-      fig.subplots_adjust(left=0.10, right=0.90, hspace=0.3, wspace=0.25)
+      fig = plt.figure(figsize=(9, 10))
+      plt.subplots_adjust(left=0.10, right=0.90, wspace=0.2, hspace=0.05)
 
       list_maps    = [
                       np.log10(self.Q_gas.SD / self.Q_gas.cm2pc**2 * self.Q_gas.g2Msun)
                      ,np.log10(self.Q_star.SD / self.Q_star.cm2pc**2 * self.Q_star.g2Msun)
-                     ,np.log10(self.Q_gas.sigma_r)
-                     ,np.log10(self.Q_star.sigma_r)
+#                      ,np.log10(self.Q_gas.sigma_r)
+#                      ,np.log10(self.Q_star.sigma_r)
[…]

### 2019-03-12 WRITEUP/ms.tex
clarify sec 3.3

@@
 \begin{abstract}
-We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower) and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
+We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower) 
+at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
 %
@@
 %
-The MCs span a mass range of $10^{6.5-9}$\,\Msun.
+The MCs span a mass range of $10^{6.5-9}$\,\Msun and a size range of $R\lesssim200$\,pc.
 Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
 %
-We compute the effective two-component Toomre $Q$ parameter (gas and stars) to examine regions that are 
+We compute the effective two-component Toomre $Q_{\rm eff}$ parameter (gas and stars) to examine regions that are 
 gravitationally unstable.
 %
-We further perform virial analysis, which is accessible from observations, to examine regions likely 
-to undergo collapse.
-Our analysis indicates that the MCs in the main disk of \flower are unbound, but its substructures have lower virial parameters and Toomre $Q$, which is consistent with the notion that collapsing structures occur within globally stable structures.
+We further perform virial analysis, which is accessible to observations, to examine regions that are likely 
+to undergo collapse. Our analysis indicates that MCs in the main disk of \flower are unbound, but its 
+substructures have lower virial parameters and Toomre $Q_{\rm eff}$, which is consistent 
+with the notion that collapsing structures occur within globally stable structures.
 %
@@
 \caption{
-    Star formation history of \flower (top right) and projected stellar mass distribution of \flower during {\it (a)} one of its accretion phases at its early stage of evolution; {\it (b)} one of its major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
+    Star formation history of \flower (top) and projected stellar mass distribution (bottom) of \flower during {\it (a)} 
+    one of its accretion phases at its early stage of evolution; {\it (b)} 
+    one of its major starburst phases after a merger event; and {\it (c)} 
+    a relatively quiescent phase post-starburst.
 \label{fig:SFH}}
@@
 
-In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
-We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying ``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower 
+at different evolutionary stages (between redshifts of $z$\eq6.0\,$-$\,7.2). We 
+note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying ``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
 
@@
 \caption{
-Examples showing the MCs identified in the accreting phase of \flower by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see text).
+Examples showing the MCs identified in the accreting phase of \flower by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see \Sec{method}).
 Color shows the H$_2$ surface density, weighted by the column density.
@@
 We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
-We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to the same stage used to plot \Fig{h2density}.
-
-For visualization, we overplot the molecular structures identified using a subset of the $n_{\rm cut}$ (0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps in \Fig{MC} as an example.
+We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to each snapshot.
+
+For visualization purposes, we overplot the molecular structures identified using a subset of the volumetric H2 density cuts
+($n_{\rm cut}$\eq0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example (see \Fig{MC}). 
 The plots shown in \Fig{MC} are weighted by the column density of the total gas content.
@@
 %
-We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the considered evolutionary stages for each of the given $n_{\rm cut}$ (see \Sec{method}).
+We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work,
+for each of the given $n_{\rm cut}$ (see \Sec{method}).
 The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
@@
 \end{equation}
-where we have defined the virial parameter $\alpha_{\rm vir}$.
-
-\AP{i do not fully follow the logic of the following passages}
-\DL{need some work to clarify this para}
-Motivated by the Larson's relations, we express the observable quantities in the following forms:
-\begin{equation}
-V_0^2\equiv\frac{\sigma^2}{R},\,
-\end{equation}
-which is related to Larson's linewidth-size relation \citep{Larson81a}, which can be recast into the form of:
-\begin{equation}
-\sigma^2/R = \pi G \Sigma/5.
-\end{equation}
-For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
+which is also the defined as the virial parameter $\alpha_{\rm vir}$.
+
+Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, 
+we recast Equation~\ref{eqn:alpha} into the form of:
+\begin{equation}
+\sigma^2/R = \pi G \Sigma/5\,, 
+\label{eqn:SVE}
+\end{equation}
+for gas in virial equilibrium (i.e., by setting $\alpha_{\rm vir}$\eq1).
+On the other hand, for pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
 Equation~\ref{eqn:virial} becomes:
@@
 \end{equation}
-which describes the external pressure needed to confine the gas inside a volume $V$.
-\AP{please specify which eq.s you are referring to} Rearranging the equation and substituting for the surface density $\Sigma$\eq$M/\pi R^2$, we can express this equation using the following:
-\begin{equation}
-\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
+which describes how much external pressure is needed to confine the gas inside a given volume. 
+Substituting surface density $\Sigma$\eq$M/\pi R^2$ into Equation~\ref{eqn:pext}, we can express it with the following:
+\begin{equation}
+\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right)\,,
 \label{eqn:v0}
 \end{equation}
-Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since $\sigma^2/R\propto\Sigma$, whereas Equation~\ref{eqn:v0} represents the locus along which external pressures $P_{\rm ext}$ are needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities.
-% (see\Fig{alpha27}).
-In other words, \AP{the following is a bit unclear} a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$; cf.
+keeping $\sigma^2/R$ on the LHS.
+
+Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping 
+between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, 
+since $\sigma^2/R\propto\Sigma$. Equation~\ref{eqn:v0} 
+then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have 
+linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
+In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with 
+external pressure $P_{\rm ext}$ (and therefore $\sigma^2/R$ is not constant 
+with $\Sigma$ but varies depending on $P_{\rm ext}$; cf. 
 expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
 
-Summarizing, to quantify the stability of MC we use the virial parameter (\Eq{alpha}), which describes the balance between kinetic and gravitational potential energies.
-An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms and is often used to assess the boundedness of a given structure in \obs \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
+Summarizing, we use the virial parameter (\Eq{alpha}) to quantify the stability of an MC. 
+An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between gravitational and kinetic energies, and is
+ often used to assess the boundedness of a given structure in \obs \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
 To facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to 
@@
 \begin{equation}
-Q_{\rm star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
+Q_{\star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
 \end{equation}
@@
 %				\begin{array}{lccr}
-%					     {\displaystyle\frac{w}{T_{\rm star} Q_{\rm star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
-%                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\rm star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\rm star} \leq T_{\rm gas} Q_{\rm gas} \\
+%					     {\displaystyle\frac{w}{T_{\rm star} Q_{\star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
+%                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \leq T_{\rm gas} Q_{\rm gas} \\
 %				\end{array} 
@@
 \begin{equation}
-w\equiv\frac{2 \sigma_{\rm star} \sigma_{\rm gas}}{\sigma_{\rm star}^2 + \sigma_{\rm gas}^2},
+w\equiv\frac{2 \sigma_{\star} \sigma_{\rm gas}}{\sigma_{\star}^2 + \sigma_{\rm gas}^2},
 \end{equation}
@@
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
-scale height ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc$\simeq$\,0.15) and since \flower is more of a warped disk.
+scale height ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
 That is, some MCs are located in regions of $Q_{\rm gas}$\ssim1, but 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0}.png}
-\caption{\AP{guess we should go from $\log \sigma$ to $\sigma$; additionally we might want to use shared colorbars (e.g.
-$\Sigma_{gas}\,,\Sigma_{\star}-> \Sigma$) and write gas and stars as white text on the maps}
-%
-}
+\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
+\caption{
+Surface density maps of the gas (top left) and stellar (top right) components of \flower and 
+their radial velocity dispersion maps projected onto the $xy$-plane.
+%
+\label{fig:sigma}}
 \end{figure*}
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0}.png}
-\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
+\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
 \caption{
@@
 central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
-Gas-only $Q$ are shown in the left panels and stellar-only $Q$ are shown in the middle panels.
+Gas-only $Q_{\rm gas}$ are shown in the left panels and stellar-only $Q_\star$ are shown in the middle panels.
 Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels. 
@@
 A smoothing length of 30\,pc has been applied to the maps.
-A divergent colormap is used for the Toomre $Q$ map to facilitate 
+A divergent colormap is used for the Toomre $Q$ maps to facilitate 
 identification of regions above and below $\log{Q}$\eq0.
@@
 %
-Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (\AP{which was Behrendt16a resolution?
-I would report the value} e.g., \citealt{Behrendt16a}).
+Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum 
+resolution of 3\,kpc in the 48\,kpc box studied by \citealt{Behrendt16a}). 
 Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
@@
 For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
-\AP{hum, I do not follow this point, but it might be due to satellite definition; to me satellite is a separate galaxy (which typically has a lower potential well, thus feedback should be more effective); if by satellite you mean merging satellite we should check its recent stellar activity; if it is negligible, that is why they have lower feedback and subsequently values of $\alpha_{vir}$} Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
 % pext
@@
 %
-Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$ \AP{can we give a typical number, given the mean sigma and kappa inside clumps?}.
+Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
 Second, this fragmentation scale is greater than the typical size of GMCs.

### 2019-03-13 WRITEUP/ms.tex
moved Sec on Q to discussion.

@@
 
-\subsection{Structure identification}\label{sec:method}
+\subsection{Structure Identification}\label{sec:method}
 
@@
 where the sum is done for the cells composing each MC.
-The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.}.
-On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
-This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
+The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.\label{ftn:veldisp}}.
+On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
 
@@
 %\subsection{Gravitational Instabilities}\label{sec:Q}
-\subsection{Toomre stability}\label{sec:Q}
+\subsection{Toomre Stability}\label{sec:Q}
 
@@
 
-For the purpose of this work, we present Toomre $Q$ map in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
+For the purpose of this work, we present Toomre $Q$ maps in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
 
@@
 5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
-\label{fig:alpha16-28}}
+\label{fig:larsons_single}}
 \end{figure*}
@@
 
-\subsection{Single evolutionary stage}  \label{sec:singless}
+\subsection{Single Evolutionary Stage}  \label{sec:singless}
 
@@
 %
-Scaling relations for the MCs identified in the accretion phase are shown in top panels of \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}, and in the bottom panels for the starburst phase.
+Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right 
+panels for the starburst phase.
 %
@@
 % PVE
-We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see \Fig{alpha27}).
-The dashed lines in the figure show the loci along which the given external pressures are needed for MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).
+We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}).
+Dashed lines in the figure show the loci along which the given external pressures are
+needed for MCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
 Heyer+09).
-The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6 (see \Fig{alpha27}), which 
+The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6, which 
 is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.
-
-\subsection{Temporal evolution and cut dependence}\label{sec:ncut}
-% single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
-different sets of $n_{\rm cut}$ in identifying the MCs.
-%
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
-cloud scaling relations).
-%
-In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%
-This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
-Our results are therefore robust to the various density cuts of choice.
-
-% temporal evolution in Cloud Dynamics
-We show the properties of all MCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
-We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
-
-\begin{comment}
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
-\caption{
-Larson's (linewidth-size) relation of \flower in
-accretion phase (top) and
-starburst phase (bottom) compared to
-those observed in nearby and the \z$\sim$2 star-forming galaxy.
-% Red lines show the relation obtained from \citet{}.
-Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
-\label{fig:larsons_single}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
-\caption{
-Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel) 
-and the starburst phase (bottom panel) compared to the 
-Milky Way (other symbols).
-Literature data are compiled from \citealt{Kauffmann17b} and references therein.
-Star symbols are color-coded by $n_{\rm cut}$.
-Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
-\label{fig:alpha16}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
-\caption{
-$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
-in the accretion phase (top panel) and the starburst phase (bottom panel)
-compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
-The V-shaped dashed lines show the loci along which the given external pressures
-are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
-Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
-Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
-correspond to MCs in the satellite galaxies.
-\label{fig:alpha27}}
-\end{figure*}
-\end{comment}
 
@@
 As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
-We discuss this result in the following section.
+We discuss this result in the Discussion section.
 
@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Q} 
-(see also \Fig{h2density} for an example of MCs identified in this evolutionary stage of \flower
-for different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
- \AP{why then we do not postpone the figure presentation?} \DL{I am not sure if I should first show all the plots in Sec 4 and the discuss in details in Sec 5 or what. I guess we could just show
-in Sec 5.}
-We discuss the importance of accounting for stellar contributions and the effect of the thickness of the disk to the total stability criterion. 
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in 
+\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
+% single Snapshot
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
+different sets of $n_{\rm cut}$ in identifying the MCs.
+%
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+cloud scaling relations).
+%
+In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%
+This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+Our results are therefore robust to the various density cuts of choice.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCs identified across all evolutionary stages in \Fig{alpha16-28}. We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+
+%
+%\begin{comment}
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
+%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
+%\caption{
+%Larson's (linewidth-size) relation of \flower in
+%accretion phase (top) and
+%starburst phase (bottom) compared to
+%those observed in nearby and the \z$\sim$2 star-forming galaxy.
+%% Red lines show the relation obtained from \citet{}.
+%Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
+%\label{fig:larsons_single}}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
+%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
+%\caption{
+%Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel) 
+%and the starburst phase (bottom panel) compared to the 
+%Milky Way (other symbols).
+%Literature data are compiled from \citealt{Kauffmann17b} and references therein.
+%Star symbols are color-coded by $n_{\rm cut}$.
+%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
+%\label{fig:alpha16}}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
+%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
+%\caption{
+%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
+%in the accretion phase (top panel) and the starburst phase (bottom panel)
+%compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
+%The V-shaped dashed lines show the loci along which the given external pressures
+%are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
+%Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
+%Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
+%correspond to MCs in the satellite galaxies.
+%\label{fig:alpha27}}
+%\end{figure*}
+%\end{comment}
+
+%
+%\begin{comment}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
+%\caption{
+%Maps of the total gas surface density (top left), 
+%velocity dispersion (top right),
+%epicyclic frequency (bottom left), 
+%and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
+%Modest smoothing has been applied to the maps. 
+%A divergent colormap is used for the Toomre $Q$ map to facilitate 
+%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+%Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
+%Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
+%\label{fig:Q}}
+%\addtocounter{figure}{-1}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
+%\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
+%\addtocounter{figure}{-1}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
+%\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
+%\caption{
+%Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
+%\label{fig:Qstar}}
+%% \addtocounter{figure}{-1}
+%\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
+%\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
+%\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
+%\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
+%\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
+%\caption{
+%Effective two-component Toomre $Q_{\rm eff}$ (top row) 
+%and gas surface density (middle) maps projected onto the $xy$-plane.
+%Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
+%and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
+%Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
+%Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
+%Modest smoothing has been applied to the maps. 
+%A divergent colormap is used for the Toomre $Q$ map to facilitate 
+%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
+%Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
+%are likely gravitationally unstable.
+%\label{fig:Qeff}}
+%% \addtocounter{figure}{-1}
+%\end{figure*}
+%%\clearpage
+%
+%\end{comment}
+
+%--------------------------------------------------------------------------
+%                                Discussion
+%--------------------------------------------------------------------------
+\section{Discussions and Implications}\label{sec:diss}
+
+\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
+
+The MCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+%
+% velocity dispersion, larsons
+%
+Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
+Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep.
+The higher velocity dispersions
+(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
+%
+In fact, by $z\simeq$\,7.2 (\AP{i would always refer to the evolutionary stage name, once in defined in Fig.
+1; we might want to use italic to underline it is a definition} i.e., accretion phase; see \Fig{SFH}a), \flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
+Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
+
+The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk.
+This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+%
+For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
+% Tasker09a
+On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} (without requiring gas to be funneled into the central region).
+This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
+%
+The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
+the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is 
+consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
+
+% mass-size relation
+In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, which is an empirical relation corresponding to the threshold for massive \SF, but lies
+%The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
+%found to be more massive than those that are devoid of clusters
+%at a given radius.
+below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
+This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
+%
+That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
+
+% different evolutionary stages
+In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}).
+That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
+
+\subsection{Origin and Physical Scales of MCs} \label{sec:origin}
+
+The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{alpha16-28}).
+Overall, the MCs we identified are much bigger in size and mass than nearby GMCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
+
+% mass scale
+Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.
+% also higher $P_{\rm int}$,
+% which is $\propto\rho\sigma^2$
+% M51: Colombo+14
+However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude). 
+These bigger clouds have been interpreted as a result of their higher gas mass fractions, surface densities, and velocity dispersions, 
+since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and 
+Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.
+
+Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a 
+velocity dispersion of $\sigma\approx50$\,\kms and a 
+gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yields 
+$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
+%
+Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum 
+resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). 
+Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
+That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\approx$\,30\,pc).
+
+%Note that regions of $Q\lesssim1$ is actually somewhat 
+%less than the number of MCs we have identified based on density threshold --- 
+%but this has something to do with the dependence on 
+%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at 
+%MCs identified at the highest $n_{\rm cut}$.
+
+% alpha parameters
+As shown in \Fig{larsons_single}, 
+the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
+%
+For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+
+% pext
+As shown in \Fig{larsons_single}, 
+MCs in the main disk of \flower have higher pressure than the sub-MCs.
+The lower virial parameter and external pressure of the sub-MCs compared to their parent MCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
+%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
+%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
+%and galactic rotation on large scales. 
+%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
+
+For MCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus,\AP{i suspect a low or null \SF in the satellites, i.e.
+some of them should have $f_gas = 1$, i.e.
+no stars} \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+ \DL{should probably move to somwehere later in this sec}
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} 
+(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
+using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the 
+stellar component play an important role in 
 governing the stability of the MCs against $m$\eq0 perturbations.
-This can be understood since stars in \flower dominates in mass in the central part of the galaxy, 
+This can be understood since stars in \flower dominates the central part of the galaxy in mass, 
 so their gravitational potential provides a non-negligible contribution to the stability. 
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a 
-scale height ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
-That is, some MCs are located in regions of $Q_{\rm gas}$\ssim1, but 
-when including the effects of stars and thickness of the disk (via $\sigma_z$),
-they are consistent with $Q_{\rm gas} > 1$.
-Further interpretation and implication of this is discussed in \Sec{origin}.
+scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
+That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, which would suggest that they are gravitationally unstable;
+however, when including the stabilizing effects due to its stellar potential and the 
+thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
+This highlights the importance of accounting for stellar contribution and disk thickness when examining the stability of 
+molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts 
+that are preferentially being imaged at high resolution with ALMA. One should be caution when interpreting results
+based on gas-only Toomre $Q$ analysis.
 
@@
 
-\begin{comment}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
-\caption{
-Maps of the total gas surface density (top left), 
-velocity dispersion (top right),
-epicyclic frequency (bottom left), 
-and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
-Modest smoothing has been applied to the maps. 
-A divergent colormap is used for the Toomre $Q$ map to facilitate 
-identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
-Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
-\label{fig:Q}}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
-\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
-\addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
-\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
-\caption{
-Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
-\label{fig:Qstar}}
-% \addtocounter{figure}{-1}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
-\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
-\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
-\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
-\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
-\caption{
-Effective two-component Toomre $Q_{\rm eff}$ (top row) 
-and gas surface density (middle) maps projected onto the $xy$-plane.
-Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
-and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
-Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
-Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
-Modest smoothing has been applied to the maps. 
-A divergent colormap is used for the Toomre $Q$ map to facilitate 
-identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
-are likely gravitationally unstable.
-\label{fig:Qeff}}
-% \addtocounter{figure}{-1}
-\end{figure*}
-%\clearpage
-
-\end{comment}
-
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
-\section{Discussions and Implications}\label{sec:diss}
-
-\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
-
-The MCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
-%
-% velocity dispersion, larsons
-%
-Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep.
-The higher velocity dispersions (see also footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
-%
-In fact, by $z\simeq$\,7.2 (\AP{i would always refer to the evolutionary stage name, once in defined in Fig.
-1; we might want to use italic to underline it is a definition} i.e., the evolutionary stage corresponding to an early phase of accretion as shown in \Fig{SFH}a), \flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
-Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
-
-The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
-%
-For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
-% Tasker09a
-On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} (without requiring gas to be funneled into the central region).
-This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
-%
-The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
-the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is 
-consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
-
-% mass-size relation
-In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, which is an empirical relation corresponding to the threshold for massive \SF, but lies
-%The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
-%found to be more massive than those that are devoid of clusters
-%at a given radius.
-below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
-This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
-%
-That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
-
-% different evolutionary stages
-In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}, \Fig{alpha16}, and \Fig{alpha27}).
-That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
-
-\subsection{Origin and Physical Scales of the MCs} \label{sec:origin}
-
-The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{larsons16-28}).
-Overall, the MCs we identified are much bigger in size and mass than nearby GMCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
-
-% mass scale
-Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.
-% also higher $P_{\rm int}$,
-% which is $\propto\rho\sigma^2$
-% M51: Colombo+14
-However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
-These bigger clouds have been interpreted as a results of their higher gas mass fractions and surface densities and velocity dispersions, since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.
-
-Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a velocity dispersion of $\sigma\approx50$\,\kms and a gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yield $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
-%
-Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum 
-resolution of 3\,kpc in the 48\,kpc box studied by \citealt{Behrendt16a}). 
-Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
-That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l\approx$\,30\,pc).
-
-%Note that regions of $Q\lesssim1$ is actually somewhat 
-%less than the number of MCs we have identified based on density threshold --- 
-%but this has something to do with the dependence on 
-%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at 
-%MCs identified at the highest $n_{\rm cut}$. \DL{do they overlap?}
-
-% alpha parameters
-As shown in \Fig{alpha16}, the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-%
-For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
-% pext
-As shown in \Fig{alpha27}, MCs in the main disk of \flower have higher pressure than the sub-MCs.
-The lower virial parameter and external pressure of the sub-MCs compared to their parent MCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
-%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
-%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
-%and galactic rotation on large scales. 
-%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
-
-For MCs in the satellite galaxies, we find low pressures and virial parameters  which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus,\AP{i suspect a low or null \SF in the satellites, i.e.
-some of them should have $f_gas = 1$, i.e.
-no stars} \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
-
-The apparently large virial parameters seen in the MCs of \flower can be understood using the Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,$-$\,\ref{fig:Qeff}).
+The apparently large virial parameters seen in the MCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}).
 We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
@@
 \DL{I think we can keep "some"?}
-some MCs are found to lie in regions of $Q>1$. 
+some MCs are found to lie in regions of $Q_{\rm eff}>1$. 
 % some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
-Only in (the denser) regions with a low Toomre $Q$ parameter and when energy can be dissipated on a timescale that is shorter than the timescale over which it gains energy (e.g., heating) correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
-%
-This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$ nature of most MCs of \flower and its relatively \AP{however, the high sfr is in some of the clumps, which does not necessarily correspond to the location of current H2 rich clumps} high SFR.
-That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
+Only in (the denser) regions with a low Toomre $Q_{\rm eff}$ parameter and when energy can be dissipated on a timescale that is shorter than the timescale over which it gains energy (e.g., heating) correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
+%
+This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$ nature of most MCs of \flower and its relatively \AP{however, the high sfr is in some of the clumps, which does not necessarily correspond to the location of current H2 rich clumps}
+\DL{don't understand this comment} 
+high SFR. That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
 %
@@
 %
-We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk2011a}.
+We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
 %

### 2019-03-14 WRITEUP/ms.tex
fleshed out a bit more

@@
 %
-We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
-compared to \flower. Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the 
+Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
 higher gas mass fraction, surface density, and velocity dispersion.
@@
 It might still be overleaf fault.
-An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g.
-selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}
+An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g., selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}
 
@@
 The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support.
-Then the Toomre-Q parameter can be defined as \citep{Toomre64a}:
+The Toomre-Q parameter can be defined as \citep{Toomre64a}:
 \begin{equation}
@@
 \end{equation}
-In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < 1$ (or equivalently $\omega^2 < 0$).
-Physically, this situation happens when local gravitational instability
+In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that 
+$Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability
 overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
-% but further evolution depends on their EOS. (e.g., instability impose by angular momentum from gas accretion from the cosmic web and satellite galaxies and stellar feedback).
-% Note that fragmentation is expected to happen at critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$, which is greater than the typical size of  GMCs.
-It should be clear that the instability sets the scales for fragmentation, but star-forming GMCs are the collapsing, denser, and cooler molecular structures on even smaller scales.
-The fragmented structures thus correspond to regions where $Q\lesssim1.
-Similarly, for a collisionless fluid -- as an ensamble of stars -- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
+Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
 \begin{equation}
@@
 
-In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.][see also \citealt{Inoue16a}]{Romeo11a}.
+In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
 %
@@
 with $x$ indicating either gas or stars.
-%
-The combined effect of gas and stars can then be account by writing
+% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction.
+As such, it is easier to be stable against gravitaional instability.
+Thus, the criterion for instability $Q$ is reduced.
+%
+The combined effect of gas and stars can then be accounted for by writing
 \begin{equation}\label{eqn:q_eff}
-%Q^{-1}_{\rm eff} =  \left\{
-%				\begin{array}{lccr}
-%					     {\displaystyle\frac{w}{T_{\rm star} Q_{\star}} + \frac{1}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \geq T_{\rm gas} Q_{\rm gas} \\ [0.75em]
-%                                               {\displaystyle\frac{1}{T_{\rm star} Q_{\star}} + \frac{w}{T_{\rm gas} Q_{\rm gas}}}      & & & \mbox{if\ }T_{\rm star} Q_{\star} \leq T_{\rm gas} Q_{\rm gas} \\
-%				\end{array} 
-%			    \right.
 Q^{-1}_{\rm eff} =  \left\{
@@
 \end{equation}
+Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making 
+a system easier to obtain stability, and thus, lowering the criterion of the critical Toomre 
+$Q_{\rm crit}$ from $\simeq$\,1 to 
+0.67 \citep{Goldreich65a}. On the other hand, including the contribution of the stellar 
+component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$.
+unless it is dynamically hot to ``compensate''.  
+As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
 \AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
@@
 behind relating aa with bb and bb and cc, etc, in the Larson's relations?}
-
-For the purpose of this work, we present Toomre $Q$ maps in \Sec{results} and discuss the importance of support from galactic rotation and shear against axisymmetric perturbations in \Sec{origin}.
 
@@
 \caption{
-\AP{evolutionary stage (function of sfr), different cuts (left/right)}\AP{similarly to the previous figure for different cuts; we might visually distinguish the points different color codes for the SFR and $n_{cut}$}
+Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary 
+stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
+Left panels show MCs identified using a low $n_{\rm cut}$ \DL{check how low?} 
+and right panels show MCs identified using a high $n_{\rm cut}$ \DL{check how high?}.
 \label{fig:alpha16-28}}
@@
 % Tasker09a
-On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} (without requiring gas to be funneled into the central region).
+On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} \DL{doesn't it take a long time for gas to lose angular
+momentum to fall onto the central region of a galaxy? Given turbulent it is across the entire galaxy \Fig{sigma}, 
+isn't more conceivable that cold gas accretion is the dominant reason to the turbulent structures in \flower?} 
+(without requiring gas to be funneled into the central region).
 This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
@@
 using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the 
-stellar component play an important role in 
+Close resemblance of the $Q_{\star}$ and $Q_{\rm eff}$ maps (especially in the central region of \flower)
+indicates that contributions from the stellar component play an important role in
 governing the stability of the MCs against $m$\eq0 perturbations.
 This can be understood since stars in \flower dominates the central part of the galaxy in mass,
-so their gravitational potential provides a non-negligible contribution to the stability. 
+so their gravitational potential provides a non-negligible contribution to the instability.
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a
-scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk.
-That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, which would suggest that they are gravitationally unstable;
-however, when including the stabilizing effects due to its stellar potential and the 
+scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk. That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, 
+which would suggest that they are gravitationally unstable;
+however, when including the effects due to its stellar potential and the
 thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
-This highlights the importance of accounting for stellar contribution and disk thickness when examining the stability of 
+This highlights the importance of accounting for stellar contribution and disk thickness 
+when examining the stability of
 molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts
-that are preferentially being imaged at high resolution with ALMA. One should be caution when interpreting results
-based on gas-only Toomre $Q$ analysis.
+that are preferentially being imaged at high resolution with ALMA. 
+One should be caution when interpreting results based on gas-only Toomre $Q$ analysis.
+In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
+both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
+Notably, these are the more gas-rich regions (see \Fig{sigma}).
 
@@
 are likely gravitationally unstable.
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
+indicates that stellar component plays an important role in governing the stability of the MCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}

### 2019-03-14 brute.py
uncomment again

@@ -191,59 +191,59 @@ for snapshotnum in range(istart, iend):
         np.savetxt(outname, X, fmt='%d %.5f %.5f %.5f', header=head)
         np.savetxt(outname.replace('_clumppos_','_wgclumppos_'), Y, fmt='%d %.5f %.5f %.5f', header=head2)
 
-        # for ileaf in id_sorted:
-        #     _fc = np.mean(leaf_clumps[ileaf].data.fcoords[:], axis=0)
-        #     prj.annotate_marker(_fc,
-        #                         coord_system='data',
-        #                         plot_args={'color': 'red', 's': 500})
-        #     prj.annotate_text(_fc,
-        #                       ileaf,
-        #                       coord_system='data',
-        #                       text_args={'color': 'black', 'size': 32},
-        #                       inset_box_args={'boxstyle': 'square',
-        #                                       'facecolor': 'white',
-        #                                       'linewidth': 2.0,
-        #                                       'edgecolor': 'white',
-        #                                       'alpha': 0.})
+        for ileaf in id_sorted:
+            _fc = np.mean(leaf_clumps[ileaf].data.fcoords[:], axis=0)
+            prj.annotate_marker(_fc,
+                                coord_system='data',
+                                plot_args={'color': 'red', 's': 500})
+            prj.annotate_text(_fc,
+                              ileaf,
+                              coord_system='data',
+                              text_args={'color': 'black', 'size': 32},
+                              inset_box_args={'boxstyle': 'square',
+                                              'facecolor': 'white',
+                                              'linewidth': 2.0,
+                                              'edgecolor': 'white',
+                                              'alpha': 0.})
 
-        # print 'ncut = ', incut
-        # print '  N clumps', len(leaf_clumps)
-        # for i in xrange(len(leaf_clumps)):
-        #     print '    id     ', i
-        #     print '    len    ', len(leaf_clumps[i]["h2density"])
-        #     print '    max f*d', np.max(leaf_clumps[i]["h2density"])
-        #     print '    min f*d', np.min(leaf_clumps[i]["h2density"])
+        print 'ncut = ', incut
+        print '  N clumps', len(leaf_clumps)
+        for i in xrange(len(leaf_clumps)):
+            print '    id     ', i
+            print '    len    ', len(leaf_clumps[i]["h2density"])
+            print '    max f*d', np.max(leaf_clumps[i]["h2density"])
[…]

### 2019-03-14 plot_modules/plot_cloud_prop.py
3x2 shared cbar cloud prop plot for paper

@@ -5,7 +5,7 @@ import os
 here    = os.path.dirname(os.path.abspath(__file__))
 litpath = here[:here.rfind('/')]+'/literature/'
 
-def setup_cmap(cm='gist_rainbow'):
+def setup_cmap(cm='Blues'):
     import matplotlib.pyplot as plt
     return plt.set_cmap(cm)
 
@@ -35,8 +35,8 @@ def setup_plot():
                                 , 'ytick.minor.width': 1     # points
                                 , 'font.serif': ("Times", "Palatino", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
                                 })
-    setup_cmap()
-    return None
+    cm = setup_cmap()
+    return cm
 
 
 
@@ -142,7 +142,7 @@ def unpack_xy(ss):
 
 
 def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
-               leglabel='', tag='', cm='gist_rainbow',
+               leglabel='', tag='',
                to_plot=None, save=True, outdir='./',
                sfrlabel=False):
     """
@@ -175,8 +175,8 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
     fig = plt.figure()
     ax = fig.add_subplot(111)
 
+    cm = plt.get_cmap()
     NUM_COLORS = len(to_plot)
-    cm = plt.get_cmap()  # "plasma_r")
 
     legend_h = []
 
@@ -749,7 +749,7 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
 
 
 def plot_stuff_3dim(xstr, ystr, zstr, ls='', markersize=7, marker='*',
-                    leglabel='', tag='', cm='gist_rainbow',
+                    leglabel='', tag='',
                     to_plot=None, save=True, outdir='./', sfrlabel=False):
     from matplotlib.ticker import NullFormatter
 
@@ -763,7 +763,7 @@ def plot_stuff_3dim(xstr, ystr, zstr, ls='', markersize=7, marker='*',
     ax = fig.add_subplot(111)
 
     NUM_COLORS = len(to_plot)
-    cm = plt.get_cmap(cm)  # "plasma_r")
[…]

### 2019-03-14 plotsingleSS.py
call

@@ -83,8 +83,8 @@ def plotting_procedure(snapshot_num):
 # ---
 if __name__ == '__main__':
 
-    for isnap in range(16, 29):
-        plotting_procedure(isnap)
+    # for isnap in range(16, 29):
+    #     plotting_procedure(isnap)
 
     # min MC mass for highest n_cut (for paper)
     # for isnap in [16, 27]:
@@ -93,3 +93,26 @@ if __name__ == '__main__':
     # # plot Larson and local points only (for talk introduction slide)
     # _, to_plot, _ = load_pickleTOplot(16)
     # plot_stuff("size pc", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir='./')
+
+
+    # for paper, 3x2 panel for just ss16 and ss27
+    plt.close('all')
+
+    from plot_modules.plot_cloud_prop import setup_plot
+    cm = setup_plot()
+
+    from plot_modules.plot_cloud_prop import plot_stuff, plot_stuff_3by2
+    from plotsingleSS import load_pickleTOplot
+    ss1, to_plot1, leafdir_out1 = load_pickleTOplot(16)
+    ss2, to_plot2, leafdir_out2 = load_pickleTOplot(27)
+
+    fig, ax = plot_stuff_3by2(to_plot1, to_plot2, ls='',
+                              markersize=10,
+                              marker='*',
+                              tag='',
+#                              cmap=cm,
+                              sfrlabel=False,
+                              cbarLabelSize=16,
+                              outdir='./',
+                              legendFontSize=13,
+                              saveFig=False)

### 2019-03-14 plotsingleSS.py
filename

@@ -109,7 +109,7 @@ if __name__ == '__main__':
     fig, ax = plot_stuff_3by2(to_plot1, to_plot2, ls='',
                               markersize=10,
                               marker='*',
-                              tag='',
+                              tag='ss16-ss27',
 #                              cmap=cm,
                               sfrlabel=False,
                               cbarLabelSize=16,

### 2019-03-14 plotSS.py
3by2 plot for allss

@@ -185,7 +185,7 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
 if __name__ == '__main__':
 
     # for paper
-    plot_dis_allSS()
+    # plot_dis_allSS()
 
     # # of MCs w/ mass > 1e8 Msun (for paper)
     # _to, _ = load_pickleTOplot(16, 28, fname="0.32_10_fields.p")
@@ -259,12 +259,37 @@ if __name__ == '__main__':
     #         count += 1
     # print count
 
-    plotting_procedure(16, 28, pattern="0.32")
-    plotting_procedure(16, 28, pattern="0.53")
-    plotting_procedure(16, 28, pattern="0.88")
-    plotting_procedure(16, 28, pattern="1.47")
-    plotting_procedure(16, 28, pattern="2.45")
-    plotting_procedure(16, 28, pattern="4.08")
-    plotting_procedure(16, 28, pattern="6.81")
-    plotting_procedure(16, 28, pattern="11.36")
-    plotting_procedure(16, 28, pattern="18.96")
+    # plotting_procedure(16, 28, pattern="0.32")
+    # plotting_procedure(16, 28, pattern="0.53")
+    # plotting_procedure(16, 28, pattern="0.88")
+    # plotting_procedure(16, 28, pattern="1.47")
+    # plotting_procedure(16, 28, pattern="2.45")
+    # plotting_procedure(16, 28, pattern="4.08")
+    # plotting_procedure(16, 28, pattern="6.81")
+    # plotting_procedure(16, 28, pattern="11.36")
+    # plotting_procedure(16, 28, pattern="18.96")
+
+
+    # for paper, 3x2 panel for just
+    plt.close('all')
+
+    from plot_modules.plot_cloud_prop import setup_plot, plot_stuff, plot_stuff_3by2
+    cm = setup_plot()
+
+    fname1 = '0.53_10_fields.p'
+    fname2 = '18.96_10_fields.p'
+    _, to_plot1, leafdir_out1 = load_pickleTOplot(16, 28, fname1)
+    _, to_plot2, leafdir_out2 = load_pickleTOplot(16, 28, fname2)
+
+    bubu = [fname1[:fname1.find('_')], fname2[:fname2.find('_')]]
+
+    fig, ax = plot_stuff_3by2(to_plot1, to_plot2, ls='',
+                              markersize=10,
+                              marker='*',
+                              tag='allss',
+#                              cmap=cm,
+                              sfrlabel=bubu,
[…]

### 2019-03-14 plot_modules/plot_cloud_prop.py

@@ -865,7 +865,7 @@ def set_minorticks(fig, ax):
     return fig, ax
 
 
-def plot_size_veldisp(fig, ax, to_plot, sfrlabel, ls='',
+def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
                       markersize=10, marker='*',
                       showylabel=True,
                       showLegend=False, legendFontSize=None):
@@ -948,22 +948,10 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, ls='',
         # ks = numerical value of ncut or sfr
         _x = to_plot[ks]["size pc"]
         _y = to_plot[ks]["sigma kms"]
-        if sfrlabel:
-            h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
-                         marker=marker,
-                         label="SFR: " + "{0:d}".format(int(sfr[ks])),
-                         markeredgecolor='gray',
-                         markeredgewidth=0.5)
-#            legend_h.append(h)
-        else:
-            h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
-                         marker=marker,
-                         markeredgecolor='gray',
-                         markeredgewidth=0.5)
-
-#            legend_h.append(h)
-
-
+        h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
+                     marker=marker,
+                     markeredgecolor='gray',
+                     markeredgewidth=0.5)
     # Shrink current axis by 10%
     box = ax.get_position()
     ax.set_position([box.x0, box.y0, box.width, box.height * 0.9])
@@ -978,7 +966,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, ls='',
 
     ax.set_xscale("log")
     ax.set_xlabel("Cloud Size [pc]")
-    ax.set_xlim(1.0, 2.e3)
+    ax.set_xlim(2, 2.e3)
 
     ax.set_yscale("log")
     ax.set_ylabel(r"$\sigma$ [km s$^{-1}$]")
@@ -991,7 +979,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, ls='',
     return fig, ax
 
 
-def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, ls='',
+def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
[…]

### 2019-03-14 plotSS.py
uncomment stuff that shouldn't be commented

@@ -259,15 +259,15 @@ if __name__ == '__main__':
     #         count += 1
     # print count
 
-    # plotting_procedure(16, 28, pattern="0.32")
-    # plotting_procedure(16, 28, pattern="0.53")
-    # plotting_procedure(16, 28, pattern="0.88")
-    # plotting_procedure(16, 28, pattern="1.47")
-    # plotting_procedure(16, 28, pattern="2.45")
-    # plotting_procedure(16, 28, pattern="4.08")
-    # plotting_procedure(16, 28, pattern="6.81")
-    # plotting_procedure(16, 28, pattern="11.36")
-    # plotting_procedure(16, 28, pattern="18.96")
+    plotting_procedure(16, 28, pattern="0.32")
+    plotting_procedure(16, 28, pattern="0.53")
+    plotting_procedure(16, 28, pattern="0.88")
+    plotting_procedure(16, 28, pattern="1.47")
+    plotting_procedure(16, 28, pattern="2.45")
+    plotting_procedure(16, 28, pattern="4.08")
+    plotting_procedure(16, 28, pattern="6.81")
+    plotting_procedure(16, 28, pattern="11.36")
+    plotting_procedure(16, 28, pattern="18.96")
 
 
     # for paper, 3x2 panel for just

### 2019-03-14 plot_modules/plot_cloud_prop.py
MR relation cbar representation

@@ -593,10 +593,10 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
 
             h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
                          marker=marker,
-                         label="SFR: " + "{0:d}".format(int(sfr[ks])),
+#                         label="SFR: " + "{0:d}".format(int(sfr[ks])),
                          markeredgecolor='gray',
                          markeredgewidth=0.5)
-            legend_h.append(h)
+#            legend_h.append(h)
 
         else:
             if xstr == "gas sd per ff" and ystr == "sfr sd":
@@ -604,11 +604,12 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
                 _y = np.log10(_y)
 
             h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
-                         marker=marker, label=leglabel + ks,
+                         marker=marker,
+#                         label=leglabel + ks,
                          markeredgecolor='gray',
                          markeredgewidth=0.5)
 
-            legend_h.append(h)
+#            legend_h.append(h)
 
     # name_out = ystr.replace(' ', '-') + '_' + \
     #     xstr.replace(' ', '-')

### 2019-03-14 plotsingleSS.py

@@ -83,8 +83,11 @@ def plotting_procedure(snapshot_num):
 # ---
 if __name__ == '__main__':
 
-    # for isnap in range(16, 29):
-    #     plotting_procedure(isnap)
+    from plot_modules.plot_cloud_prop import setup_plot
+    cm = setup_plot()
+
+    for isnap in range(16, 29):
+        plotting_procedure(isnap)
 
     # min MC mass for highest n_cut (for paper)
     # for isnap in [16, 27]:
@@ -97,9 +100,6 @@ if __name__ == '__main__':
 
     # for paper, 3x2 panel for just ss16 and ss27
     plt.close('all')
-
-    from plot_modules.plot_cloud_prop import setup_plot
-    cm = setup_plot()
 
     from plot_modules.plot_cloud_prop import plot_stuff, plot_stuff_3by2
     from plotsingleSS import load_pickleTOplot

### 2019-03-14 WRITEUP/ms.tex
corresponding changes to ms

@@
 \centering
-\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_larsons.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_larsons.png}
-\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16_alphavir.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_alphavir.png}
-\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16_PVE.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss27_PVE.png}
+\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
 \caption{
@@
 identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
-Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
-\AP{ have not found a good clipping for the upper left panel}
-\AP{please 1) increase a bit the size of the labels 2) put the legend only the right panels
-3) add a text label to the upper left corner, to ditinguish between accreting and starburst stage
-4) I would use a perceptually increasing colorbar to indicate the different cuts
-5) legend for the cuts can be substituted by a colorbar axis to be shown as an inset in 1 of the panels or as a separate figure below the panels}
+Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). \DL{some missing character after downloading 
+to local.. only the case if we saved them as .pdf.. interestingly but not the case if I save as .png}
 \label{fig:larsons_single}}
@@
 \centering
-\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_larsons.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-larsons-highncut.png}
-\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
-\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\includegraphics[trim=20 20 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_allss.png}
 \caption{
@@
 stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
-Left panels show MCs identified using a low $n_{\rm cut}$ \DL{check how low?} 
-and right panels show MCs identified using a high $n_{\rm cut}$ \DL{check how high?}.
+Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc
+and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
 \label{fig:alpha16-28}}

### 2019-03-15 WRITEUP/ms.tex
merged w/ pallo comments

@@
 \section{Introduction}
-
-\AP{i have to check abstract and Section 5., in particular 5.2; check also what have been moved to the app}
 
@@
 Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars to account for energy dissipations.
 To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell during a supernova explosion.
@@
 We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
-We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut}).} to each snapshot.
+We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work (see \Sec{ncut}).} to each snapshot.
 
@@
 \begin{equation}\label{eqn:virial_th_general}
-\frac{1}{2}\ddot I = 2(T - T_{\rm ext}) + W,
-\end{equation}
-where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia, $T$ is the internal energy of the gas, $T_s$ is external pressure support, and $W$ is the gravity energy.
+\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
+\end{equation}
+where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, 
+$\mathcal{T}$ is the internal energy of the gas, 
+$\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
 %
@@
 \begin{equation}
-\frac{1}{2}\ddot I = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
+\frac{1}{2}{\mathcal{I}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
 \label{eqn:virial}
@@
 The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}. 
-\AP{i think we can partially cut the following} \DL{probably, but I am just being explicit here to help remind myself what am I trying to say.}
 From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy.
@@
 
-In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre stability criterion \citep{Toomre64a, Goldreich65b}, or the Toomre $Q$ parameter (\AP{i would put this parenthesis as a note later on, i.e.
-close to \Eq{q_eff}} or the proxy, circular velocity to dispersion ratio; $v_{\rm circ}/\sigma$; e.g., \citealt{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}).
+In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
+$v_{\rm circ}/\sigma$, i.e., the circular velocity to dispersion ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
 % https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
@@
 The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support.
-The Toomre-Q parameter can be defined as \citep{Toomre64a}:
-\begin{equation}
-Q_{\rm gas}\equiv\frac{\sigma\kappa}{\pi G \Sigma}\,.
+The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
+\begin{equation}
+Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
 \label{eqn:Q}
@@
 \begin{equation}
-Q_{\star} \equiv\frac{\sigma\kappa}{3.36 G \Sigma}\,.
+Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
 \end{equation}
@@
 				\begin{array}{lccr}
-					     {\displaystyle\frac{w}{Q^{\rm thick}_{\rm star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\rm star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
-                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\rm star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\rm star} \leq Q^{\rm thick}_{\rm gas} \\
+					     {\displaystyle\frac{w}{Q^{\rm thick}_{\star}} + \frac{1}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ }  Q^{\rm thick}_{\star} \geq Q^{\rm thick}_{\rm gas} \\ [0.75em]
+                                               {\displaystyle\frac{1}{Q^{\rm thick}_{\star}} + \frac{w}{Q^{\rm thick}_{\rm gas}}}      & & & \mbox{if\ } Q^{\rm thick}_{\star} \leq Q^{\rm thick}_{\rm gas} \\
 				\end{array}
@@
 As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
-\AP{symbol already used for internal enrgy in \Eq{virial_th_general}; do we already need the virial theorem derivation?}
-\DL{this is small $w$. Whether or not we need the Larson's relation stuff, I think those eqns there help understand the motivation
-behind relating aa with bb and bb and cc, etc, in the Larson's relations?}
 
@@
 identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
-Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). \DL{some missing character after downloading 
-to local.. only the case if we saved them as .pdf.. interestingly but not the case if I save as .png}
+Star symbols are color-coded by the density thresholds ($n_{\rm cut}$). 
 \label{fig:larsons_single}}
@@
 %
-Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently \AP{which is already said in the last part of previous Sec.; I would put here that part} \DL{?}
+Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently 
 high turbulences and surface densities in both stages.
 These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-%
 As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
@@
 This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
-\AP{same color code as in the panels with different ncut}
+The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}.
 \label{fig:MR}}
@@
 %
-In fact, by $z\simeq$\,7.2 (\AP{i would always refer to the evolutionary stage name, once in defined in Fig.
-1; we might want to use italic to underline it is a definition} i.e., accretion phase; see \Fig{SFH}a), \flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
-Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies ($\sigma\approx$10\,\kms).
+In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
+\flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
+Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellites ($\sigma\approx$10\,\kms).
 
@@
 % Tasker09a
-On the other hand, the highly turbulent structures of \flower likely result from constant cold gas accretion onto the entire galaxy \AP{i do not fully grasp the following point} \DL{doesn't it take a long time for gas to lose angular
-momentum to fall onto the central region of a galaxy? Given turbulent it is across the entire galaxy \Fig{sigma}, 
-isn't more conceivable that cold gas accretion is the dominant reason to the turbulent structures in \flower?} 
-(without requiring gas to be funneled into the central region).
-This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
+On the other hand, the highly turbulent structures of \flower likely result from 
+extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
+The presence of such extra-planar flows may also be the 
+dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
 %
@@
 For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
 
@@
 For MCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus,\AP{i suspect a low or null \SF in the satellites, i.e.
-some of them should have $f_gas = 1$, i.e.
-no stars} \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
-
- \DL{should probably move to somwehere later in this sec}
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
-(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
-using different $n_{\rm cut}$). Fragmentation are expected in regions of low Toomre $Q$ values.
-Close resemblance of the $Q_{\star}$ and $Q_{\rm eff}$ maps (especially in the central region of \flower)
-indicates that contributions from the stellar component play an important role in
-governing the stability of the MCs against $m$\eq0 perturbations.
-This can be understood since stars in \flower dominates the central part of the galaxy in mass,
-so their gravitational potential provides a non-negligible contribution to the instability.
-Similarly, contribution from the thickness of the disk is important in \flower since its disk is not thin (with a
-scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15) and since \flower is more of a warped disk. That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, 
-which would suggest that they are gravitationally unstable;
-however, when including the effects due to its stellar potential and the
-thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
-This highlights the importance of accounting for stellar contribution and disk thickness 
-when examining the stability of
-molecular gas structures, especially in the relatively evolved and enriched systems at high redshifts
-that are preferentially being imaged at high resolution with ALMA. 
-One should be caution when interpreting results based on gas-only Toomre $Q$ analysis.
-In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
-both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
-Notably, these are the more gas-rich regions (see \Fig{sigma}).
+This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+\subsection{Stability of MCs}
 
@@
 
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
+(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
+using different $n_{\rm cut}$).
+
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCs against $m$\eq0 perturbations.
+This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the stability.
+
+Similarly, contribution from the thickness of the disk is important in \flower since its disk warped and cannot be considered thin, i.e., 
+it has a scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
+
+That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, 
+which would suggest that they are gravitationally unstable;
+however, when including the stabilizing effects due to its stellar potential and the
+thickness of its disk (via $\sigma_z$), some of these MCs are consistent with $Q_{\rm eff} > 1$.
+This highlights the importance of accounting for stellar contribution and disk thickness 
+when examining the stability of molecular gas structures.
+This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
+that are preferentially being imaged at high resolution with ALMA.
+% One should be caution when interpreting results based on gas-only Toomre $Q$ analysis.
+In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
+both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
+Notably, these are the more gas-rich regions (see \Fig{sigma}).
+
 The apparently large virial parameters seen in the MCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}).
@@
 Thus, the high virial parameter found for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
-As such, \AP{some or most?}
-\DL{I think we can keep "some"?}
+As such,
 some MCs are found to lie in regions of $Q_{\rm eff}>1$.
 % some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
-Only in (the denser) regions with a low Toomre $Q_{\rm eff}$ parameter and when energy can be dissipated on a timescale that is shorter than the timescale over which it gains energy (e.g., heating) correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
-%
-This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$ nature of most MCs of \flower and its relatively \AP{however, the high sfr is in some of the clumps, which does not necessarily correspond to the location of current H2 rich clumps}
-\DL{don't understand this comment}
-high SFR. That is, if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
-%
-\AP{however, such high-sfr is only seen in case (b), while high alpha vir are seen in all cases; i do not fully see the discrepancy}
-\DL{maybe it's just we should also account for stellar mass in alpha vir, but leave it out when we compare that with observations?}
-The discrepancy can be explained in two ways.
-First, our results are limited by the resolution of the simulation, such that, in each MC, there likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
-as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
+Only in (the denser) regions with a low Toomre $Q_{\rm eff}$ parameter and when the cooling time is lower then the dynamical time star formation can proceed in {\it clumps} and {\it cores} with low virial parameters.
+
+Note that even in stages when \flower~is star forming we find that most of its MCs have high $\alpha_{\rm vir}$.
+This seem to be self-contradictory: if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
+Such tension in the interpretation is understood as follows.
+%
+First, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
+This re-iterates the statement about low $Q$ above.
 %
 Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by large-scale gravitational potential and differential rotation.
-This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound MCs \citep{Clark04a, Clark05a}.
-%
-Additionally, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+This in turn enables sub-regions of the MCs to collapse and potentially form OB associations out of these unbound MCs \citep{Clark04a, Clark05a}.
+%
+Further, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+Finally, the SFR is very bursty and high SFR stages are transient.
 
@@
 
-We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy
+We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy, \flower,
 at the EoR using state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
 which includes a chemical network to determine the formation of molecular
-hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
+hydrogen, heating and cooling of the ISM by metals, and detailed stellar feedback.
 We use a clump-finding algorithm and a set of H$_2$ volumetric densities
-to identify MCs and their sub-structures in the main galaxy of the
-simulated 20\,Mpc~$h$\pmOne box --- \flower\ --- and in its satellites.
+to identify MCs and their sub-structures in \flower and its satellites.
 We decompose the molecular structures into non-overlapping tiles
 by identifying a set of different density contours at different evolutionary stages.
-Using volumetric H$_2$ is essentially similar to identifying molecular structures using
-different contour levels/surfaces on surface brightness maps/cubes of molecular line tracers (e.g., CO, CS, NH$_3$),
+Such identification method is similar to MC identification based on 
+contour levels/surfaces of surface brightness maps/cubes of molecular line tracers (e.g., CO, CS, NH$_3$),
 since the line luminosity scales with the molecular gas density (modulo optical depth effects).
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and
-compare them with those observed in the Milky Way disk, the Galactic center,
-and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
-We also examine their properties at the different evolutionary stages of \flower and compare
-them with observations.
+
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and we perform a Toomre-$Q$ stability analysis.
+The properties of the MCs in \flower are compared with observed MCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
+This is done for different evolutionary stages of \flower.
 
@@
 those observed in $z$\ssim2 starburst galaxies.
-The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold
+The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun, depending on the chosen H$_{2}$ cut. 
+The $\sim$200\,pc-scale MCs found with a low density threshold
 correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
@@
 density threshold $n_{\rm cut}$ adopted in identifying the structures.
-Our results are thus insensitive to the various density cuts of choice.
-The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the
-density threshold and even for the molecular substructures.
-Such a high velocity dispersion likely results from
-the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
+ The found scaling relations are insensitive to the various density cuts. 
+ The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the density threshold and 
+ even for the molecular substructures. 
+ Such a high velocity dispersion likely results from the strong supernova and stellar feedback \flower experienced 
+ over the multiple episodes of bursty \SF.
 
@@
 We also find $\alpha_{\rm vir}\approx$\,2 for MCs in the satellite galaxies, which we interpret as
-result of the weaker stellar feedback compared to \flower.
-MCs in the satellites are therefore likely collapsing structures.
-
+result of the weaker/delayed stellar feedback compared to \flower. 
+In particular, some of the MCs in the satellites are collapsing structures that have not yet formed stars, as confirmed by their
+higher gas-to-stellar fractions.
 In terms of the scaling relations examined, we do not observe any significant
 temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation.
-Similarly, we do not find any significant dependence on the H$_2$ volume density threshold adopted
-in the scaling relations examined (see Appendix \Sec{ncut}).
-Our results are thus robust against the density threshold adopted.
 

### 2019-03-15 WRITEUP/ms.tex
fig 5 caption

@@
 Linewidth-size relation (top),
-{\bf .... (middle), and blah blah (bottom)}
+$\alpha_{\rm vir}$-mass relation 
+(middle), and 
+$\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom)
 for MCs (star symbols)

### 2019-03-18 WRITEUP/ms.tex
AP AF word edits

@@
 \newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
+\definecolor{afcolor}{HTML}{b3443c}
+\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
 
@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of MC in Galaxies at the EoR
-}
+\shorttitle{Dynamical Properties of MC in Galaxies at the EoR}
 \shortauthors{Leung et al.}
@@
 \altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
-\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (IPMU), The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa 277-8583, Japan}
+\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), University of Tokyo, Kashiwa 277-8583, Japan}
 \altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
@@
 \begin{abstract}
-We study the dynamical properties of molecular cloud complexes (MC) in a prototypical galaxy (\flower)
-at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
-%
-We identify MCs using H$_2$ density, and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$) with those observed in nearby and \z$\sim$\,2 galaxies.
-%
-The MCs span a mass range of $10^{6.5-9}$\,\Msun and a size range of $R\lesssim200$\,pc.
-Their velocity dispersions and gas surface densities are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
-%
-We compute the effective two-component Toomre $Q_{\rm eff}$ parameter (gas and stars) to examine regions that are
-gravitationally unstable.
-%
-We further perform virial analysis, which is accessible to observations, to examine regions that are likely
-to undergo collapse. Our analysis indicates that MCs in the main disk of \flower are unbound, but its
-substructures have lower virial parameters and Toomre $Q_{\rm eff}$, which is consistent
-with the notion that collapsing structures occur within globally stable structures.
-%
-Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
-higher gas mass fraction, surface density, and velocity dispersion.
+We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``\flower") at redshift $z\approx 6$ using cosmological zoom-in simulations.
+%
+We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
+%
+In \flower, MCs masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
+Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
+%
+We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter (gas+stars), and using a more observationally accessible $\alpha_{\rm vir}$ analysis.
+We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of collapse.
+%
+%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
+%higher gas mass fraction, surface density, and velocity dispersion.
 % , which together sets the scale for fragmentation.
+\AF{Abstract is a bit thin. Revise at the end}
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
@@
 \section{Introduction}
-
-\AP{For some plots, still the old versions are the ones available.
-It might still be overleaf fault.
-An option would be to have a clean new overleaf document; pros: probably the compilation will be faster and the service less buggy (e.g., selecting every time the main manuscript file, files are actually uploaded, etc) and thus more convenient to use; cons: it will not be syncronized with the repo}
-
-\DL{Maybe we will have to do it that way, and I will manually maintain my copy on the repo and on my macbook?}
-
-The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes) and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
-The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves are more gas-rich in their star-forming molecular gas contents compared to present-day galaxies.
-%
-These massive gas inflows in turn trigger gravitational instability and lead
-to the formation of gas structures that are typically more massive and denser than those
-observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
-and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
-Some theoretical works argue that the
-migration of such giant massive clumps are responsible for contributing to the
-buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
-
-Given that \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these relatively more extreme conditions, thereby driving the evolution and assembly
-of galaxies
-since the cosmic dark ages.
-Current consensus is that at higher redshifts, galaxies have higher
-star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and
-smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to those found in the local Universe.
-The former are thus expected to have more \ion{H}{2} regions, ionized gas, and more intense radiation stellar feedbacks.
-Since their metallicity and dust content are also expected to be lower as they are assembling,
-this affects the shielding of UV photons, heating and cooling mechanisms in these early systems. Such differences in turn
-affect the regulation of thermal and chemical structures of their ISM.
-Their multi-phase ISM and the dynamics of the star-forming molecular cloud complexes (MC)
-are therefore expected to differ from nearby galaxies.
-Even in the local Universe, where the most detailed \obs can be attained, variations in cloud properties have been
-observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-It is thus intuitive and reasonable to pose the question: what are the dynamical states of the MCs of the first galaxies and
-how do they differ from the local Universe, and are they analogous to any seen in the local \galpop?
-%
-
-The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are the key diagnostics for
-constraining the ISM conditions of a galaxy by
-providing highly complementary information that trace different phases of the ISM (ionized,
-atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
-Global measurements of these diagnostics in \highz galaxies
-have informed us on their galaxy-wide properties (e.g.,
-gas masses, gas temperature, and radiation field intensity).
-However, spatially resolving their ISM is necessary to understand their roles in galaxy evolution and
-the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
-To date, spatially resolved ISM properties of \highz galaxies
-have only been examine observationally in a handful of (strongly-lensed)
-galaxies, using tracers such as
-dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
-These studies find that galaxies at $z$\ssim2 galaxies, close to the peak of cosmic \SF, are more
-molecular gas-rich, turbulent, and clumpy than nearby galaxies.
-That said, it remains unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 ---
-the epoch of reionization  ---
-which is responsible for producing the
-ionizing photons that reionized the Universe.
-While ALMA has enabled the detections of
-ISM diagnostic lines e.g., the \cii158\,$\micron$ and CO line emission in
-normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Odorico18a, Carniani18b},
-we are still far from mapping their molecular ISM due to the cosmological dimming.
-As such, we have undertaken a study, exploiting
-state-of-the-art cosmological zoom-in hydrodynamic simulation
-\ncode{Serra} (Greenhouse in Italian; \citealt{Pallottini17a, Pallottini17b}), with a goal to examine
-and predict the dynamical properties of the star-forming molecular cloud complexes in a \z$\sim$6 prototypical (i.e., $L^*$)
-galaxy. % to understand the physics behind \SF in the first galaxies.
-
-%This paper is structured as follows.
-In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower), and describe the method used to identify its molecular gas complexes.
-In \Sec{eqn}, we present the formalism within which we interpret the results.
-In \Sec{results}, we present scaling relations for the MCs identified.
-We then interpret the results and discuss the implications of our findings in \Sec{diss}, and present our conclusions in \Sec{conclusion}.
-This paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}.
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes).
+Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
+The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times.
+Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.
+
+Such massive gas inflows trigger gravitational instabilities which lead to the formation of molecular complexes that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+%
+Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
+
+Given that \highz galaxies statistically represent  the early evolutionary stages of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceeds under more extreme conditions.
+Current consensus is that early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population.
+%
+As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF).
+Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons - responsible for the photoheating of the gas - is strongly reduced.
+Such differences in turn affect the regulation of the multi-phase ISM thermal and chemical state.
+
+Even in the local Universe, where detailed \obs can be attained, variations in cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
+It is thus intuitive and reasonable to pose the question: {\it what are the physical properties of MCs in early galaxies, and how do they differ from those found in local \galpop?}
+%
+
+FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO and [\ci]~lines are key diagnostics for constraining the ISM conditions of galaxies.
+They also provide highly complementary information on different ISM phases (ionized, atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
+%
+Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity).
+However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
+%
+To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of (strongly-lensed) galaxies at intermediate-$z$, using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
+These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2), are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+
+Earlier epochs still represent an essentially uncharted territory for ISM investigations.
+At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
+%
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Smit18a,Jones17a}.
+
+To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming molecular cloud complexes in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
+
+The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}.
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
@@
 % ------------------
-\section{Numerical simulations} \label{sec:sim}
-
-\subsection{\ncode{Serra} Simulation\footnote{Serra means greenhouse in Italian which is motivated by the
-fact that our simulation includes a chemical network to calculate the abundance of H$_2$, which in turn
-dictates the formation of CO.
-}}
-
-The simulation used in this work is described by \citealt{Pallottini17a, Pallottini17b} and is briefly summarized here.
-%
-\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
+\section{Numerical simulations}\label{sec:sim}
+The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
+%
+\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
 %
 In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
-Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
-Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
-%
-We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).
+The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
+Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
+
+We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
+Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}).
 
@@
 Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars to account for energy dissipations.
-To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell during a supernova explosion.
-The energy dissipated is then injected into the ISM in the form of kinetic and thermal energies.
-Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).
-
-Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
-Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG), hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
-At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-It is therefore a prototypical galaxy at \z$\sim$\,6.
-For reference, the half mass radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius at which the mean enclosed density is 200 times the critical density of the Universe is $r_{\rm 200}\simeq$\,15\,kpc.
-
-The simulation data contain information such as the density ($\rho$) and velocity ($v_x$, $v_y$, and $v_z$) fields, from which we calculate the physical properties of each MC, such as mass and velocity dispersion.
-Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids for the analysis presented in this paper.
-The grid size is defined based on the highest resolution of the simulation data (i.e., the less refined regions are supersampled in the resulting uniform grids).
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars.
+Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
+The remaining energy is injected into the ISM in kinetic and thermal energy forms.
+Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
+
+The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following.
+\flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
+Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 
 \subsection{Star Formation History} \label{sec:sfh}
-One of the main advantages for studying the dynamical properties of molecular structures at $z$\ssim6 in simulation is the fact that we can examine how their properties evolve as a function of time.
-%
-This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
+
+\begin{figure*}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\caption{
+    Star formation history of \flower (top) and projected stellar mass distribution (bottom) during {\it (a)} an accretion phases at its early stage of evolution; {\it (b)} a major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
+\label{fig:SFH}}
+\end{figure*}
+
+One of the main advantages for studying the dynamical properties of simulated galaies is the fact that we can examine how their properties evolve with time.
+%
+%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
 Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
@@
 
-\begin{figure*}[!htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
-\caption{
-    Star formation history of \flower (top) and projected stellar mass distribution (bottom) of \flower during {\it (a)}
-    one of its accretion phases at its early stage of evolution; {\it (b)}
-    one of its major starburst phases after a merger event; and {\it (c)}
-    a relatively quiescent phase post-starburst.
-\label{fig:SFH}}
-\end{figure*}
-
-We show the \SF history of \flower in \Fig{SFH}, where the SFR is calculated based on existing young stellar population, which is defined to have an age of $t_{\rm age}<$\,10\,Myr.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher than shown here since they also include contributions from massive satellite galaxies within the surrounding $\approx$15\,kpc ($\simeq$ to the virial radius).} as it evolves from an actively accreting phase to a starburst phase after a major merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.
-
-Given the stochasticity in the \SF history of \flower (see \Fig{SFH}), we focus this work on the analysis of two of its most extreme evolutionary
-stages (see \Sec{singless}), to illustrate the salient points of discussion presented in this paper.
-The two phases correspond to i) when \flower
-is accreting materials from its surrounding  and ii) when \flower is undergoing a major starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics.
-For completeness, we also show the results (in terms of the scaling relations presented) for
-the other evolutionary stages traced in the simulation.
-
-Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower,
-which is $\sim$\,1\,kpc in radius.
+The \SF history of \flower is shown in \Fig{SFH}.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{Note that here the SFR is calculated based on the stallar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contributions from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.
+
+Given the stochasticity in the \SF history of \flower, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}).
+The two phases correspond to (a) when \flower is accreting materials from its surrounding  and (b) when \flower is undergoing a starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics.
+For completeness, for the other evolutionary stages traced in the simulation we only show the results in terms of the found scaling relations (see \Fig{alpha16-28}).
+
+\AP{i think we need a different name for these objects}
+Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower, which is $\sim$\,1\,kpc in radius.
 
@@
 
-To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
-%
-The latest version of the default \ncode{yt} clump finder decomposes the zones in the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree).
+To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
+%
+The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree).
 It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
 In the customized version used for this study, we modify the function to enhance the stability of the code.
-% (which essentially means we fixed the bugs in order for it to actually work).
-
-In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower
-at different evolutionary stages (between redshifts of $z$\eq6.0\,$-$\,7.2). We
-note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying ``clumps'' based on/after applying $\sigma$-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
-
+%
+Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids.
+The grid size is defined based on the highest resolution of the simulation data, i.e., the less refined regions are supersampled in the resulting uniform grids.
+
+In the clump-finding process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z$\eq6.0\,$-$\,7.2).
+%
+We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+%
 We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
@@
 \includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
-\caption{
-Volumetric H$_2$ density distribution of \flower taken from a single evolutionary stage, corresponding to the accretion phase shown in \Fig{SFH}.
+\caption{H$_2$ number density distribution of \flower taken from the accretion phase shown in \Fig{SFH}.
 \label{fig:h2density}}
@@
 \caption{
-Examples showing the MCs identified in the accreting phase of \flower by applying volumetric H$_2$ density cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see \Sec{method}).
-Color shows the H$_2$ surface density, weighted by the column density.
+Examples of MCs identified by the clump-finder.
+\flower is shown in its in the accreting phase: white contours indicate the identified clumps and the color-bar shows the mean H$_2$ number density, weighted by gas mass.
+Different rows shows the clump-finder results obtained by applying different H$_2$ number density.
+Left and right panels show the galaxy from different inclinations
+%cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see \Sec{method})
 \label{fig:MC}}
@@
 
-In \Fig{h2density}, we show an example of the volumetric H$_2$ density ($n_{\rm H2}$) distribution of \flower~for a given evolutionary stage which includes contributions within $R\sim$\,3.5\,kpc from the galaxy center.
-%
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on the Euler characteristic, i.e., the fourth Minkowsky functional (see \citealt{Pallottini17b}).
+In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by inlcuding the contribution from the gas within 3.5 kpc from the galaxy center.
+%
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger then zero.
+Such functional is a measure of the Euler characteristic, being positive (negative) implies that the field is made of isolated (connected) components.
+See Fig.
+6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
 We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work (see \Sec{ncut}).} to each snapshot.
 
-For visualization purposes, we overplot the molecular structures identified using a subset of the volumetric H2 density cuts
-($n_{\rm cut}$\eq0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps as an example (see \Fig{MC}).
-The plots shown in \Fig{MC} are weighted by the column density of the total gas content.
+To have a visual overwview of the clump finding results, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps.
 % equation below for bookkeeping:
@@
 % to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
-
 Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more easily see that they are collections of disjoint structures.
@@
 
-Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we impose an addition constraint such that an identified structure only survives if it spans at least 10 cells in PPP space.
-We caution that one caveats of such constraint is that we can only examine the parameter space of ``cloud'' scaling relations at ``cloud'' size $R\gtrsim100$\,pc.
-
-%\subsection{Key Properties of Clouds}
+Note that we impose the additional constraint that an identified structure must be composed of at least 10 cells.
+We caution that an important caveat of such constraint is that we can only examine the parameter space of ``cloud'' of typical size $R\gtrsim 60$\,pc, because of the resolution limit in the simulation.
+
 \subsection{Properties of the Clouds}
@@
 We note that the distributions vary for different evolutionary stage of \flower.
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{6.5}$\,\Msun for the densest MC.
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
 %
@@
 for each of the given $n_{\rm cut}$ (see \Sec{method}).
-The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
+The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
 
@@
 
-\section{Results: MC Properties and Cloud Scaling Relations}\label{sec:results}
+\section{Results}\label{sec:results}
 
@@
 those observed in $z$\ssim2 starburst galaxies.
-The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun, depending on the chosen H$_{2}$ cut. 
+The mass scale of the MCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
 The $\sim$200\,pc-scale MCs found with a low density threshold

### 2019-03-18 WRITEUP/ms.tex
minor note and text edit

@@
 \begin{abstract}
-We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``\flower") at redshift $z\approx 6$ using cosmological zoom-in simulations.
+We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``Alth{\ae}a'') at redshift $z\approx 6$ using cosmological zoom-in simulations.
 %
@@
 \section{Introduction}
+\DL{please igonre Fig 7 for now. Labels/markers in the AlphaVir plots in Fig 5,6 will be updated based on Jens Kauffman's comments} 
 The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes).
@@
 We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}).
+Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}.
 
@@
 % 
-Regardless of the H$_2$ density cuts adopted, the MCs are found to have consistently 
-high turbulences and surface densities in both stages.
-These correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
+Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure)
+compared to the accretion phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
+%
+Regardless of the H$_2$ density cuts adopted, MCs in both phases are found to have consistently 
+high turbulences and surface densities. They correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
 As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).

### 2019-03-18 io_modules/manipulate_fetch_gal_fields.py
histogram limit

@@ -342,7 +342,7 @@ def check_hist_h2(data, th_list, ss=None, outdir='./'):
 
     plt.close('all')
     plt.figure()
-    plt.hist(aa, bins=100)
+    plt.hist(aa[aa>-7], bins=100)
     for ele in th_list:
         x = np.log10(ele)
         # plt.plot([x, x], [1, 1.e+7], ls='--', color='k')

### 2019-03-18 plot_modules/plot_cloud_prop.py
A_v Lombardi from A_k, attempt to fix figsize issue and white space in larsons plot

@@ -402,7 +402,9 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
         k10_Msun = 870. * (r_pc)**1.33
 
         # corresponds to A_v = 4 mag
-        mag4_Msun = 265. * (r_pc)**2.
+        A_0_k = 1.0
+        A_V_from_A_K = 1/0.112
+        mag4_Msun = A_0_k * A_V_from_A_K * 265. * (r_pc)**2.
 
         # 10^n mag
         mag10_Msun = 662. * 10**1.0 * (r_pc)**2
@@ -964,7 +966,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     ax.set_yscale("log")
     ax.set_ylabel(r"$\sigma$ [km s$^{-1}$]")
-    ax.set_ylim(0.5, 1.e5)   # 2.e2
+    ax.set_ylim([0.5, 2.e2])
 
     ax.tick_params(axis='both', which='both')   # direction='in'
 
@@ -1313,9 +1315,10 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
     else:
         sfr_val = sorted([ii for ii in sfr.itervalues()])
 
-    fig, axes = plt.subplots(nrows=3, ncols=2, sharex=False, sharey=True,
-                             figsize=(40,40))
-    fig.subplots_adjust(right=0.875, left=0.1, top=0.9,
+    fig, axes = plt.subplots(nrows=3, ncols=2, sharex=False,
+                             sharey=False,   # do NOT set to TRUE
+                             figsize=(15,10))
+    fig.subplots_adjust(right=0.87, left=0.1, top=0.9,
                         bottom=0.1, hspace=0.25,
                         wspace=0.1)
     if sfrlabel:
@@ -1398,8 +1401,10 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
     _cmap = mpl.cm.ScalarMappable(norm=norm, cmap=cm)
     _cmap.set_array([])
 
+    # cax = fig.add_axes([0.88, 0.1, 0.1, 0.8])
     cbar = fig.colorbar(_cmap, ticks=c, fraction=0.04, # aspect=10,
                         ax=axes.ravel().tolist())
+                        # ax=cax)
     cbar.ax.tick_params(length=6)
     if sfrlabel:
[…]

### 2019-03-18 WRITEUP/ms.tex

@@
 The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}.
+We start by providing some physical background in \Sec{Back}.
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
@@
 %
+\section{Physical Background}\label{sec:Back}
+We begin by introducing some basic material concerning known physical relations and stability analysis of MCs that will become useful in the following.
+\subsection{Larson relations}\label{sec:PVE}
+\citep{Larson81a} discussed a number of relations among Galactic MC properties, namely the linewidth-size, density-size, and mass-size relations.
+Larson relations are routinely used for comparing properties of molecular structures in different galactic environments.
+They also represent a useful framework to analyze our results as they arise from the interplay between gravity and turbulence encoded in the virial theorem.
 
-% ------------------
-\section{Numerical simulations}\label{sec:sim}
-The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
-%
-\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
-%
-In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
-The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
-Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
-
-We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}.
-
-% radiative feedback --> NT pressure
-Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars.
-Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
-The remaining energy is injected into the ISM in kinetic and thermal energy forms.
-Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
-
-The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following.
-\flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
-
-\subsection{Star Formation History} \label{sec:sfh}
-
-\begin{figure*}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
-\caption{
-    Star formation history of \flower (top) and projected stellar mass distribution (bottom) during {\it (a)} an accretion phases at its early stage of evolution; {\it (b)} a major starburst phases after a merger event; and {\it (c)} a relatively quiescent phase post-starburst.
-\label{fig:SFH}}
-\end{figure*}
-
-One of the main advantages for studying the dynamical properties of simulated galaies is the fact that we can examine how their properties evolve with time.
-%
-%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
-Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
-% mainly expecting differences in alpha_vir, sigma, M_cl.
-
-The \SF history of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{Note that here the SFR is calculated based on the stallar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
-The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contributions from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the few hundred Myr simulated in the simulation.
-
-Given the stochasticity in the \SF history of \flower, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}).
-The two phases correspond to (a) when \flower is accreting materials from its surrounding  and (b) when \flower is undergoing a starburst phase; such phases are expected to bracket the most extreme variations in the cloud dynamics.
-For completeness, for the other evolutionary stages traced in the simulation we only show the results in terms of the found scaling relations (see \Fig{alpha16-28}).
-
-\AP{i think we need a different name for these objects}
-Throughout this paper, we call ``satellite galaxies'' as dense gas regions outside the main disk of \flower, which is $\sim$\,1\,kpc in radius.
-
-\section{Molecular Cloud Complexes}\label{sec:eqn}
-
-\subsection{Structure Identification}\label{sec:method}
-
-To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
-%
-The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a k-dimensional tree (k-d tree).
-It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
-In the customized version used for this study, we modify the function to enhance the stability of the code.
-%
-Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids.
-The grid size is defined based on the highest resolution of the simulation data, i.e., the less refined regions are supersampled in the resulting uniform grids.
-
-In the clump-finding process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z$\eq6.0\,$-$\,7.2).
-%
-We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
-%
-We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
-% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
-Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
-% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
-1 of Beaumount13a).
-(may be worth putting more thoughts on this after the report is due).
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
-\caption{H$_2$ number density distribution of \flower taken from the accretion phase shown in \Fig{SFH}.
-\label{fig:h2density}}
-\end{figure}
-
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
-  \\ [-2.9em]
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
-  \\ [-2.9em]
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
-\caption{
-Examples of MCs identified by the clump-finder.
-\flower is shown in its in the accreting phase: white contours indicate the identified clumps and the color-bar shows the mean H$_2$ number density, weighted by gas mass.
-Different rows shows the clump-finder results obtained by applying different H$_2$ number density.
-Left and right panels show the galaxy from different inclinations
-%cuts of $n_{\rm cut}$\eq[0.53, 6.81,19.00]\,cm$^{-3}$, which is a subset of all the $n_{\rm cut}$ adopted (see \Sec{method})
-\label{fig:MC}}
-% \addtocounter{figure}{-1}
-\end{figure*}
-
-In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by inlcuding the contribution from the gas within 3.5 kpc from the galaxy center.
-%
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of density where ``clumps/structures'' are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger then zero.
-Such functional is a measure of the Euler characteristic, being positive (negative) implies that the field is made of isolated (connected) components.
-See Fig.
-6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
-We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of $\log{(n_{\rm cut}/{\rm cm^{-3})}}\in[-0.5, 1.5]$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]\footnote{We also vary the range of $n_{\rm cut}$ adopted and find no qualitative differences affecting the results and conclusions of this work (see \Sec{ncut}).} to each snapshot.
-
-To have a visual overwview of the clump finding results, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 6.81, and 19.00\,\cc) on the H$_2$ density maps.
-% equation below for bookkeeping:
-% ${\rm pixel_i}$\eq$\frac{\sum_i~\rho_{\rm H2, i}~w_i~\Delta z_i}{\sum_i~w_i~\Delta z_i}$,
-% where $\rho_{\rm H2, i}$ is the H$_2$ density of pixel $i$, $w_i$ is the weighted quantity in pixel $i$ which we adopt
-% to be the total gas density, and $\Delta z_i$ is the path length of pixel $i$ along the line-of-sight over which the quantities are integrated along.
-Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) --- so that one can more easily see that they are collections of disjoint structures.
-%
-We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
-
-Note that we impose the additional constraint that an identified structure must be composed of at least 10 cells.
-We caution that an important caveat of such constraint is that we can only examine the parameter space of ``cloud'' of typical size $R\gtrsim 60$\,pc, because of the resolution limit in the simulation.
-
-\subsection{Properties of the Clouds}
-
-% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
-% the mechanisms and physics of formation and evolution of molecular structures and \SF.
-Upon identifying the molecular structures, we extract properties such as the H$_2$ gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
-
-The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$.
-The effective size is defined assuming spherical geometry, i.e.
-$R \equiv (3 V /4 \pi)^{1/3}$.
-%
-The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
-\begin{equation}
-\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
-\label{eqn:veldisp}
-\end{equation}
-%
-In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate
-each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is
-calculated as follows:
-\begin{equation}
-\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
-\end{equation}
-where the sum is done for the cells composing each MC.
-The local sound speed of all identified molecular complexes are much smaller compared to the their turbulent velocities\footnote{We find comparable velocity dispersion between that derived from taking the root mean square versus that derived from thermal and non-thermal pressure terms, indicating that rotation velocity is unlikely to be the dominant source of velocity dispersion reported here.\label{ftn:veldisp}}.
-On average, the Mach number of the MCs corresponds to about $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
-
-We show in \Fig{dist} the MC distributions in terms of their molecular gas masses, radii, and gas mass fractions, which we define as
-\begin{equation}
-f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_*\right)},
-\end{equation}
-where $M_*$ is the stellar mass within the MC volume.
-%
-We note that the distributions vary for different evolutionary stage of \flower.
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
-%
-We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work,
-for each of the given $n_{\rm cut}$ (see \Sec{method}).
-The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame {\it UV and optical light} \citep{Elmegreen07a, Elmegreen09a}.
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
-Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
-\label{fig:dist}}
-\end{figure*}
-
-%\section{Basic physical properties}\label{sec:eqn}
-
-%\subsection{Virial Equilibrium and Larson's Relations}\label{sec:PVE}
-\subsection{Larson's Relations}\label{sec:PVE}
-
-In next sections, we examine and compare properties of the MCs with observations in the context of the Larson's relations \citep{Larson81a}.
-Namely, the linewidth-size, density-size, and mass-size relations.
-Larson's relations are adopted for the discussion in this work as they  describe the interactions between gravity and turbulence, and is the first set of relations used for studying star-forming molecular structure formation based on observables which has been routinely used for comparing properties of molecular structures in different galactic environments.
-% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
-
-% Relating Larson's law to stability and pressure (perhaps move this to other section?).
-In general, the virial theorem for a distribution of gas can be written as
+In general, the virial theorem for a gas distribution of gas can be written as
 \begin{equation}\label{eqn:virial_th_general}
@@
 \end{equation}
-where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, 
-$\mathcal{T}$ is the internal energy of the gas, 
-$\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
+where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
 %
-Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and velocity dispersion $\sigma$, accounting for both thermal and turbulent velocity dispersion.
-Neglecting magnetic field and calling $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
+Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and r.m.s.
+velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
+Neglecting magnetic field and defining $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
 \begin{equation}
-\frac{1}{2}{\mathcal{I}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R - \frac{\Gamma GM_{\rm cl}^2}{R}\,,
+\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm cl}^2}{R}\,,
 \label{eqn:virial}
 \end{equation}
-where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the first term on the right hand side (RHS) is the pressure term from internal velocity dispersion, the second term the external pressure term, and the third term is is the gravity term.
+where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the r.h.s. represent the kinetic, external, and gravity pressure terms. 
+%
 For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
 \begin{equation}
-\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma GM_{\rm cl}/R} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
+\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma (GM_{\rm cl}/R)} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
 \label{eqn:alpha}
 \end{equation}
-which is also the defined as the virial parameter $\alpha_{\rm vir}$.
+which defined as the virial parameter $\alpha_{\rm vir}$.
 
-Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a},
-we recast Equation~\ref{eqn:alpha} into the form of:
+Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we recast Equation~\ref{eqn:alpha} into 
 \begin{equation}
@@
 \end{equation}
-for gas in virial equilibrium (i.e., by setting $\alpha_{\rm vir}$\eq1).
-On the other hand, for pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
-Equation~\ref{eqn:virial} becomes:
+for gas in virial equilibrium, i.e., by setting $\alpha_{\rm vir}$\eq1; the surface density $\Sigma$\eq$M/\pi R^2$.
+On the other hand, for pressure-bounded virial equilibrium (PVE; i.e.
+equilibrium state with external pressure), Equation~\ref{eqn:virial} becomes:
 \begin{equation}
-P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \frac{\Gamma G M_{\rm cl}^2}{4\pi R^4},
+P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \Gamma\frac{G M_{\rm cl}^2}{4\pi R^4}\,,
 \label{eqn:pext}
 \end{equation}
-which describes how much external pressure is needed to confine the gas inside a given volume.
-Substituting surface density $\Sigma$\eq$M/\pi R^2$ into Equation~\ref{eqn:pext}, we can express it with the following:
+which quantifies the external pressure needed to confine the gas inside a given volume. Substituting again $\Sigma$  into Equation~\ref{eqn:pext}, we find 
 \begin{equation}
@@
 
-Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping
-between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud,
-since $\sigma^2/R\propto\Sigma$. Equation~\ref{eqn:v0}
-then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have
-linewidths $\sigma$ for a given set of surface densities. % (see\Fig{alpha27}).
-In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with
-external pressure $P_{\rm ext}$ (and therefore $\sigma^2/R$ is not constant
-with $\Sigma$ but varies depending on $P_{\rm ext}$; cf.
+Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma^2/R\propto\Sigma$.
+Equation~\ref{eqn:v0} then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have linewidths $\sigma$ for a given set of surface densities.
+In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with external pressure $P_{\rm ext}$; therefore $\sigma^2/R$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$ (cf.
 expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
 
-Summarizing, we use the virial parameter (\Eq{alpha}) to quantify the stability of an MC.
-An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between gravitational and kinetic energies, and is
- often used to assess the boundedness of a given structure in \obs \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.
-To facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to
-the stellar component.
+Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MC.
+Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
+%
+Such criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}; in the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.
 
 %\subsection{Gravitational Instabilities}\label{sec:Q}
-\subsection{Toomre Stability}\label{sec:Q}
+\subsection{Toomre stability analysis}\label{sec:Q}
 
@@
 
-In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
-$v_{\rm circ}/\sigma$, i.e., the circular velocity to dispersion ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
+In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to dispersion ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
 % https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
@@
 % from linear analysis
-For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of
-finite thickness $h$ is described by
+For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of finite thickness $h$ is described by
 \begin{equation}
@@
 \begin{equation}
-\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,,
+\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,.
 \label{eqn:kappa}
@@
 \end{equation}
-In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that 
-$Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this situation happens when local gravitational instability
+In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
+Physically, this situation occurs when local gravitational instability
 overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
@@
 
-In our stability analysis, we account for a non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
+In our stability analysis, we account for the non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
 %
@@
 \end{equation}
-Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making 
-a system easier to obtain stability, and thus, lowering the criterion of the critical Toomre 
-$Q_{\rm crit}$ from $\simeq$\,1 to 
-0.67 \citep{Goldreich65a}. On the other hand, including the contribution of the stellar 
-component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$.
-unless it is dynamically hot to ``compensate''.  
-As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
+Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making it easier for a system to obtain stability, and thus lowering the criterion of the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to
+0.67 \citep{Goldreich65a}.
+%
+On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$, unless it is dynamically hot to ``compensate''.
+As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.
+% 0.67 * 2
+
+% ------------------
+\section{Numerical simulations}\label{sec:sim}
+The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
+%
+\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
+%
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
+The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
+Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
+
+We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
+Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}.
+
+% radiative feedback --> NT pressure
+Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars.
+Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
+The remaining energy is injected into the ISM in kinetic and thermal energy forms.
+Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
+
+The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following.
+\flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
+Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+
+\subsection{Star Formation History} \label{sec:sfh}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\caption{
+    {\it Top panel}: Star formation history of \flower.
+{\it Bottom}: projected stellar mass distribution during {\it (a)} an early accretion phase;  {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
+\label{fig:SFH}}
+\end{figure*}
+
+One of the main advantages for studying the dynamical properties of simulated galaies is the fact that we can examine how their properties evolve with time.
+%
+%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
+Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
+% mainly expecting differences in alpha_vir, sigma, M_cl.
+
+The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
+
+Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}).
+The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}).
+We are interesting in determining whether MC properties are sensitive to these different dynamical conditions.
+For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).
+
+Throughout this paper, we dub as ``satellite galaxies'' the dense gas regions outside the main disk of \flower.
+The distinction between clumps and satellites is admittedly somewhat ambiguous, and we consider it only as a working one.
+\AF{To be discussed at the end}
+
+\section{Molecular Cloud Complexes}\label{sec:eqn}
+
+\subsection{Identification}\label{sec:method}
+
+To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
+%
+The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a $k$-dimensional tree ($k$-D tree).
+It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
+In the customized version used for this study, we modify the function to enhance the stability of the code.
+%
+Due to the nature of our AMR simulation, we regrid the simulation data into uniform grids.
+The grid size is defined based on the highest resolution of the simulation data, i.e., the less refined regions are supersampled in the resulting uniform grids.
+
+In the clump-finding process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z$\eq6.0\,$-$\,7.2).
+%
+We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+%
+We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
+% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
+Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
+% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
+1 of Beaumount13a).
+(may be worth putting more thoughts on this after the report is due).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
+\caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
+\label{fig:h2density}}
+\end{figure}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
+  \\ [-2.9em]
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
+  \\ [-2.9em]
+  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
+\caption{
+Examples of MCs (white contours) identified by the clump-finder in  \flower during its  accreting phase.
+The color-bar shows the mean H$_2$ number density, weighted by gas mass.
+Different rows shows the clump-finder results obtained by applying different H$_2$ number density cuts density cuts $(n_{\rm cut})$ as shown by the label.
+Left and right panels show the galaxy from different viewing angles.
+\label{fig:MC}}
+\end{figure*}
+
+In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by including the contribution from the gas within 3.5 kpc from the galaxy center.
+%
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger than zero.
+This implies that the field is made of isolated components.
+See Fig.
+6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
+We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.
+
+To visually appreciate  the clump finding procedure, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
+Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) so that one can more easily see that they are collections of disjoint structures.
+%
+We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
+
+Note that we impose the additional constraint that an identified structure must be composed of at least 10 cells.
+We caution that an important caveat of such constraint is that we can only examine the parameter space of ``cloud'' of typical size $R\gtrsim 60$\,pc, because of the resolution limit in the simulation.
+
+\subsection{Properties of the Clouds}
+
+% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
+% the mechanisms and physics of formation and evolution of molecular structures and \SF.
+Upon identifying the molecular structures, we extract properties such as the gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), r.m.s.
+velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
+
+The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$.
+The effective size is defined assuming spherical geometry, i.e.
+$R \equiv (3 V /4 \pi)^{1/3}$.
+%
+The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
+\begin{equation}
+\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
+\label{eqn:veldisp}
+\end{equation}
+%
+In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
+We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity.
+For instance, the non-thermal velocity dispersion is calculated as follows:
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the sum is done for the cells composing each MC.
+%
+The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}.
+On average, the Mach number of the MCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
+This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
+
+We show in \Fig{dist} the MC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
+\end{equation}
+where $M_\star$ is the stellar mass within the MC volume.
+%
+We note that the distributions vary for different evolutionary stages of \flower.
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
+%
+We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value.
+\AF{This is true only for low $n_{cut}$?
+Why in Fig.
+do you show the valu 18.96 instead?} \DL{MCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$.
+The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+\AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCs?}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
+Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
+\label{fig:dist}}
+\end{figure*}
 
@@
 \caption{
-Linewidth-size relation (top),
-$\alpha_{\rm vir}$-mass relation 
-(middle), and 
-$\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom)
-for MCs (star symbols)
-identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
 Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
+Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein.
+\DL{for some reason, I can't change the yaxis-limit first the top plots..}
 \label{fig:larsons_single}}
@@
 \includegraphics[trim=20 20 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_allss.png}
-\caption{
-Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary 
-stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. 
-Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc
-and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
+\caption{Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages.
+Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
 \label{fig:alpha16-28}}
@@
 For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
+Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right panels for the starburst phase.
 % 
-Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right
-panels for the starburst phase.
+Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accretion phase.
+\DL{Is this significant enough to say something physical?
+If so, not immediately clear to me what cause the differences.}
 %
-Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure)
-compared to the accretion phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
-%
-Regardless of the H$_2$ density cuts adopted, MCs in both phases are found to have consistently 
-high turbulences and surface densities. They correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs. As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
+Regardless of the H$_2$ density cuts adopted, MCs in both phases are found to have consistently high turbulence and surface densities.
+They correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
+As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs.
+As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
 
@@
 We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}).
-Dashed lines in the figure show the loci along which the given external pressures are
-needed for MCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+Dashed lines in the figure show the loci along which the given external pressures are needed for MCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
@@
 % column density) as fundamental properties of molecular cloud structure.
-Larson's third relation describes fundamental properties of molecular clouds, relating their structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
-This is also known as the law of constant column density, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_{\rm H2}$) obtainable from extinction maps ($A_V$).
-That is, $N_{\rm H2}\propto A_V$, $\Sigma\propto N_{\rm H2}$, and $M$\eq$\int \Sigma~dA$.
-Therefore, cloud mass is related to $N_{\rm H2}$ and $A_V$.
+Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
+This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
+By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with MW-like dust can be written as
+\begin{equation}
+A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+\end{equation}
+then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $l$
+\begin{equation}\label{eqn:constantcolumndensity}
+M_{\rm cl} = \frac{4\pi}{3} \mu m_p n l^3 = 154 \,A_v \left(\frac{l}{\rm pc}\right)^2 \Msun \,,
+\end{equation}
+where we have taken $\mu = 2.5$ as the mean molecular weight.
 
@@
 In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
-As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus with a visual extinction of $A_V$\eq4\,mag \citep{Lombardi10a}.
-We discuss this result in the Discussion section.
+As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
+%
+% use bla
+
+%
+The values of $A_V$ inferred from http://adsab%s.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+5 therein]{Behrens18a}
 
@@
 The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}.
+\AP{please implement the following} The reference lines with different $A_V$ are computed from \Eq{constantcolumndensity}.
+\DL{Ignore the blue dotted line for now.}
 \label{fig:MR}}
@@
 % single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
-different sets of $n_{\rm cut}$ in identifying the MCs.
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCs.
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
 %
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
-cloud scaling relations).
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
 %
@@
 %
-This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+This lack of variation is reassuring, i.e.
+the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$ on the scales studied in the present work.
 Our results are therefore robust to the various density cuts of choice.
@@
 In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
-\flower has assembled a stellar mass of $M_*$\eq7.5\E{9}\,\Msun.
+\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
 Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellites ($\sigma\approx$10\,\kms).
@@
 
-We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data.
+We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
 %

### 2019-03-18 WRITEUP/ms.tex
Updates from Overleaf

@@
 \centering
-\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
 \caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
@@
 \end{equation}
-then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $l$
+then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $R$
 \begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm cl} = \frac{4\pi}{3} \mu m_p n l^3 = 154 \,A_v \left(\frac{l}{\rm pc}\right)^2 \Msun \,,
+M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154 \,A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
 \end{equation}
@@
 %
-% use bla
-
-%
-The values of $A_V$ inferred from http://adsab%s.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
 5 therein]{Behrens18a}
@@
 % mass-size relation
-In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, which is an empirical relation corresponding to the threshold for massive \SF, but lies
-%The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
-%found to be more massive than those that are devoid of clusters
-%at a given radius.
-below the locus of $A_V$\eq100\,mag followed by Milky Way clouds.
+MCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}.
 This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
@@
 
+The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
+an ``internal'' mass-size relation where $M\propto r^{1.33}$.
+If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
+regions of high-mass \SF. That is, the MCs identified have mass-size relations suggesting they are capable of high-mass \SF.
+
 % different evolutionary stages
@@
 That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
+\DL{some MCs in SB phase have
+lower $\alpha_{\rm vir}$ and pressure, but 
+is there any significance in that?}
 

### 2019-03-18 WRITEUP/ms.tex
edits on MR relation

@@
 \centering
-\includegraphics[trim=30 30 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
 \caption{
@@
 Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
-Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein.
-\DL{for some reason, I can't change the yaxis-limit first the top plots..}
+Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein (see Fig 4 of \citealt{Kauffmann17b}).
 \label{fig:larsons_single}}
@@
 Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
-Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
+Red line shows the
+mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}.
 Star symbols are color-coded by increasing $n_{\rm cut}$.

### 2019-03-18 plot_modules/plot_cloud_prop.py
cbar

@@ -1317,7 +1317,7 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
 
     fig, axes = plt.subplots(nrows=3, ncols=2, sharex=False,
                              sharey=False,   # do NOT set to TRUE
-                             figsize=(15,15))
+                             figsize=(15,17))
     fig.subplots_adjust(right=0.8, left=0.1, top=0.85,
                         bottom=0.1, hspace=0.25,
                         wspace=0.1)
@@ -1404,10 +1404,10 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
     _cmap = mpl.cm.ScalarMappable(norm=norm, cmap=cm)
     _cmap.set_array([])
 
-    cax = fig.add_axes([0.85, 0.1, 0.1, 0.8])
+    cax = fig.add_axes([0.85, 0.1, 0.03, 0.8])
     cbar = fig.colorbar(_cmap, ticks=c, # fraction=0.04, # aspect=10,
-                        # ax=axes.ravel().tolist())
-                        ax=cax)
+                        # ax=axes.ravel().tolist(),
+                        cax=cax)
     cbar.ax.tick_params(length=6)
     if sfrlabel:
         label = r'SFR [M$_{\odot}$~yr$^{-1}$]'

### 2019-03-18 plotSS.py
import maplotlib

@@ -7,15 +7,10 @@ last mod: 18 Aug 2018
 
 '''
 
-import os
-from plot_modules.plot_cloud_prop import setup_plot
-setup_plot()
-import matplotlib.pyplot as plt
-
-
 def load_pickleTOplot(minss, maxss, fname):
     from plot_modules.plot_cloud_prop import unpack_xy
     from io_modules.leaf_pickle import load_in_pickle_SS
+    import os
 
     here = os.path.dirname(os.path.abspath(__file__))
     pickle_base_fold = here + '/test_brute/'
@@ -79,6 +74,7 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     from plot_modules.plot_cloud_prop import get_masses_all_clouds, get_sizes_all_clouds, get_fgas_all_clouds
     from matplotlib.ticker import AutoMinorLocator, MultipleLocator
     import matplotlib.ticker as ticker
+    import matplotlib.pyplot as plt
 
     ss11, to_plot11, _ = load_pickleTOplot(minss, maxss, \
                                            fname=pattern1 + '_10_fields.p')
@@ -184,6 +180,13 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
 
 if __name__ == '__main__':
 
+    import matplotlib
+    matplotlib.use('agg')
+
+    import matplotlib.pyplot as plt
+    from plot_modules.plot_cloud_prop import setup_plot
+    cm = setup_plot()
+
     # for paper
     # plot_dis_allSS()
 
@@ -269,12 +272,10 @@ if __name__ == '__main__':
     plotting_procedure(16, 28, pattern="11.36")
     plotting_procedure(16, 28, pattern="18.96")
 
-
     # for paper, 3x2 panel for just
     plt.close('all')
 
     from plot_modules.plot_cloud_prop import setup_plot, plot_stuff, plot_stuff_3by2
-    cm = setup_plot()
 
     fname1 = '0.53_10_fields.p'
     fname2 = '18.96_10_fields.p'
@@ -292,4 +293,4 @@ if __name__ == '__main__':
                               cbarLabelSize=16,
                               outdir='./',
                               legendFontSize=13,
-                              saveFig=False)
+                              saveFig=True)

### 2019-03-18 plot_modules/plot_cloud_prop.py
def of Av in MR relation

@@ -401,14 +401,9 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
         # threshold for high-mass stars from Kauffmann & Pillai10
         k10_Msun = 870. * (r_pc)**1.33
 
-        # corresponds to A_v = 4 mag
-        A_0_k = 1.0
-        A_V_from_A_K = 1/0.112
-        mag4_Msun = A_0_k * A_V_from_A_K * 265. * (r_pc)**2.
-
-        # 10^n mag
-        mag10_Msun = 662. * 10**1.0 * (r_pc)**2
-        mag102_Msun = 662. * 10**2.0 * (r_pc)**2
+        mag4_Msun = 154 * 4.0 * (r_pc)**2
+        mag10_Msun = 154 * 10**1.0 * (r_pc)**2
+        mag102_Msun = 154 * 10**2.0 * (r_pc)**2
 
         h, = ax.plot(r_pc, k10_Msun, linestyle='-.', color='r',
                 linewidth=2,

### 2019-03-18 WRITEUP/ms.tex
Updates from Overleaf
caption for MR relation

@@
 \section{Introduction}
-\DL{please igonre Fig 7 for now. Labels/markers in the AlphaVir plots in Fig 5,6 will be updated based on Jens Kauffman's comments} 
 The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes).
@@
 \centering
-\includegraphics[trim=20 20 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_allss.png}
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
 \caption{Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages.
@@
 Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to lines of constant surface density (i.e., Larson's third relation).
-This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
+Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
+constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
 The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
-\AP{please implement the following} The reference lines with different $A_V$ are computed from \Eq{constantcolumndensity}.
-\DL{Ignore the blue dotted line for now.}
 \label{fig:MR}}

### 2019-03-18 WRITEUP/ms.tex
edited caption MR relation

@@
 In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
-The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
+The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
 Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
@@
 This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
-By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with MW-like dust can be written as
+By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
 \begin{equation}
@@
 \end{equation}
-then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $R$
+then, assuming spherical symmetry, the mass of an MC can be expressed as a function of $A_v$ and its size $R$
 \begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154 \,A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
 \end{equation}
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
+We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(R/{\rm pc}\right)^{1.33}$.
 %
@@
 The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
+Extrapolating the masses and sizes of MCs of \flower along the \citet{Kauffmann10b} 
+relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCs are capable of high-mass \SF.
 \label{fig:MR}}
@@
 The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
-an ``internal'' mass-size relation where $M\propto r^{1.33}$.
+an ``internal'' mass-size relation where $M\propto R^{1.33}$.
 If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in

### 2019-03-20 WRITEUP/ms.tex
AF changes

@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some basic material concerning known physical relations and stability analysis of MCs that will become useful in the following.
-\subsection{Larson relations}\label{sec:PVE}
+We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCs, and the gravitational instability of galactic disks, which might be driving MC formation.
+Such notions will be used in the subsequent analysis of our simulations.
+\subsection{Larson relations and virial parameter}\label{sec:PVE}
 \citep{Larson81a} discussed a number of relations among Galactic MC properties, namely the linewidth-size, density-size, and mass-size relations.
@@
 where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the r.h.s. represent the kinetic, external, and gravity pressure terms.
-%
-For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), \Eq{virial} becomes:
+
+Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e. ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
+$\Sigma$\eq$M/\pi R^2$, and rewrite previous equation as 
 \begin{equation}
-\alpha_{\rm vir} \equiv \frac{3\sigma^2}{\Gamma (GM_{\rm cl}/R)} = \frac{5\sigma^2R}{GM_{\rm cl}}\,,
+\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \frac{3}{5} \pi G \Sigma \right)\,,
+\label{eqn:v0}
+\end{equation}
+which further reduces to 
+\begin{equation}
+\frac{\sigma^2}{R} = \frac{\pi}{5} G \Sigma\,,
+\label{eqn:SVE}
+\end{equation}
+if the external pressure $P_{\rm ext}=0$. For this case (often referred to as simple virial equilibrium) from the balance between kinetic and gravity terms we can define the virial parameter as 
+\begin{equation}
+\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma^2}{\pi G \Sigma R}\,,
 \label{eqn:alpha}
 \end{equation}
-which defined as the virial parameter $\alpha_{\rm vir}$.
 
-Motivated by the Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we recast Equation~\ref{eqn:alpha} into 
-\begin{equation}
-\sigma^2/R = \pi G \Sigma/5\,,
-\label{eqn:SVE}
-\end{equation}
-for gas in virial equilibrium, i.e., by setting $\alpha_{\rm vir}$\eq1; the surface density $\Sigma$\eq$M/\pi R^2$.
-On the other hand, for pressure-bounded virial equilibrium (PVE; i.e.
-equilibrium state with external pressure), Equation~\ref{eqn:virial} becomes:
-\begin{equation}
-P_{\rm ext} = \frac{3\sigma^2M_{\rm cl}}{4\pi R^3} - \Gamma\frac{G M_{\rm cl}^2}{4\pi R^4}\,,
-\label{eqn:pext}
-\end{equation}
-which quantifies the external pressure needed to confine the gas inside a given volume. Substituting again $\Sigma$  into Equation~\ref{eqn:pext}, we find 
-\begin{equation}
-\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right)\,,
-\label{eqn:v0}
-\end{equation}
-keeping $\sigma^2/R$ on the LHS.
-
-Based on Equations~\ref{eqn:SVE} and \ref{eqn:pext}, a one-to-one mapping between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma^2/R\propto\Sigma$.
-Equation~\ref{eqn:v0} then yields the loci along which external pressures $P_{\rm ext}$ are needed in order for some given MCs to have linewidths $\sigma$ for a given set of surface densities.
-In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\mapsto\Sigma$ is in equilibrium with external pressure $P_{\rm ext}$; therefore $\sigma^2/R$ is not constant with $\Sigma$ but varies depending on $P_{\rm ext}$ (cf.
-expectation for SVE, where $\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma^2/R\propto\Sigma$.
+Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
 
@@
 %
-Such criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}; in the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.
+Such criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
 
@@
 Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length.
-However, centrifugal force resulting from differential rotation in disk galaxies can inhibit collapse even on these scales.
+However, centrifugal forces resulting from differential rotation in disk galaxies can stabilize perturbations even on these scales.
 As a result, a disk is thought to be unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set by the surface density of the disk and the angular velocity of the rotation.
 
-In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to dispersion ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
+In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to the disk r.m.s.
+velocity dispersion \AF{This is not exactly the same $\sigma$ as before} ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
 % https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
@@
 % from linear analysis
-For {\it axisymmetric} mode, the dispersion relation for the growth of density perturbation in a rotating turbulent disk of finite thickness $h$ is described by
+For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
 \begin{equation}
@@
 \citep{Romeo92a}.
-The first term on the RHS of Equation~\ref{eqn:3Ddisp} describes rotation support, whereas the second term describes self-gravity, and the third term describes internal pressure support.
+\AF{$R$ is not the same as the MC radius in the proev. Section}
+In Equation~\ref{eqn:3Ddisp} the terms on the r.h.s.
+are related to rotation, self-gravity and internal pressure, respectively.
 The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
@@
 \end{equation}
-In the thin disk approximation ($kh\ll1$), the solution of \Eq{3Ddisp} is unstable for scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
-Physically, this situation occurs when local gravitational instability
+In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
+Physically, this implies that the local gravitational field
 overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
@@
 
-\subsection{Properties of the Clouds}
+\subsection{Molecular Cloud Properties}
 

### 2019-03-25 WRITEUP/ms.tex
AF comments

@@
 \subsection{Single Evolutionary Stage}  \label{sec:singless}
+\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
+We first focus on the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), and identify a set of MCs in each of them.
+Scaling relations for the MCs are shown in \Fig{larsons_single} for the accretion (left panels) and starburst phase (right), respectively.
+Let us start from analyzing the accretion phase.
 
-For each of the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), we identify a set of MCs.
-Scaling relations for the MCs identified in the accretion phase are shown in left panels of \Fig{larsons_single} and in the right panels for the starburst phase.
-% 
+MCs in \flower\ are characterized by large velocity dispersions ($\sigma \approx 100 {\rm km s}^{-1}$) and sizes ($R\approx 100$ pc).
+These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs.
+here and in caption; in addition it would good to give the properties of this galaxy}.
+Sizes are somewhat dependent on the choice of $n_{\rm cut}$.
+As such density threshold is increased, some of the MCs within the main disk break into multiple sub-MCs.
+In this case, we effectively identify a population of denser molecular structures (see \Fig{MC}).
+Instead, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+
+%Now discuss sigma - R relation; poor statistcis. But how many MCs do we have?
+
+% Starburst 
 Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accretion phase.
@@
 If so, not immediately clear to me what cause the differences.}
-%
-Regardless of the H$_2$ density cuts adopted, MCs in both phases are found to have consistently high turbulence and surface densities.
-They correspond to MCs at the center of the main disk of \flower and occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
-As we increase the density threshold, some of the MCs within the main disk break into multiple sub-MCs.
-As such, we effectively identify a population of denser molecular structures (see \Fig{MC}).
-
 % PVE
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(R/{\rm pc}\right)^{1.33}$.
+We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
 %
@@
 Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCs against $m$\eq0 perturbations.
-This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the stability.
+This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
 
@@
 
-That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, 
-which would suggest that they are gravitationally unstable;
-however, when including the stabilizing effects due to its stellar potential and the
+That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
+Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
 thickness of its disk (via $\sigma_z$), some of these MCs are consistent with  $Q_{\rm eff} > 1$. 
-This highlights the importance of accounting for stellar contribution and disk thickness 
+This demonstrates the importance of accounting for stellar contribution and disk thickness 
 when examining the stability of molecular gas structures.
@@
 that are preferentially being imaged at high resolution with ALMA.
-% One should be caution when interpreting results based on gas-only Toomre $Q$ analysis.
 In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
@@
 Further, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
-Finally, the SFR is very bursty and high SFR stages are transient.
+These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
+Finally, the SFR of \flower is very bursty and high SFR stages are only transient.
+% the giant MCs found are likely due to non-axisymmetric mode.
 
@@
 %--------------------------------------------------------------------------
-\section{Summary and Conclusions}      \label{sec:conclusion}
+\section{Summary}      \label{sec:conclusion}
 

### 2019-03-27 WRITEUP/ms.tex
edits to abstract and first part of intro.  Changed MC to MCC throughout.

@@
 \newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
+\definecolor{mmcolor}{HTML}{006600}
+\newcommand{\MM}[1]{({\bf \color{mmcolor} MM: #1})}
 
@@
 \author{Andrea Ferrara\altaffilmark{4,5}}
-\author{Mordecai-Mark Mac Low\altaffilmark{2,6,7}}
+\author{Mordecai-Mark Mac Low\altaffilmark{2,6}}
 
@@
 \altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), University of Tokyo, Kashiwa 277-8583, Japan}
-\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
-\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
+%mm \altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
+\altaffiltext{6}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}
 
 \begin{abstract}
-We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``Alth{\ae}a'') at redshift $z\approx 6$ using cosmological zoom-in simulations.
+%mm rearranged sentence
+We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
+prototypical galaxy (``\flower'') at redshift $z\approx 6$.
 %
@@
 %
-In \flower, MCs masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
+In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
 Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
 %
-We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter (gas+stars), and using a more observationally accessible $\alpha_{\rm vir}$ analysis.
-We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of collapse.
+We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
+%mm (gas+stars), 
+    taking into account both gas and stars, 
+and by using a more observationally accessible $\alpha_{\rm vir}$ analysis.
+We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
+%mm
+    instability to gravitational 
+collapse.
 %
@@
 \AF{Abstract is a bit thin. Revise at the end}
-High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
+High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
+%mm scrutinizing 
+data to test our findings and shed light on \SF since the cosmic dark ages.
 \end{abstract}
@@
 \section{Introduction}
-The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes).
-Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
-The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times.
-Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.
-
-Such massive gas inflows trigger gravitational instabilities which lead to the formation of molecular complexes that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
-%
-Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
-
-Given that \highz galaxies statistically represent  the early evolutionary stages of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceeds under more extreme conditions.
-Current consensus is that early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population.
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) 
+%mm to fuel \SF (and feed their  [using "to" implies purpose]
+     either directly from the cosmic web, or through mergers with other galaxies.  This gas fuels \SF and feeds central
+supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium 
+%mm with 
+   by expelling some
+part of this material. 
+%mm [now redundant with first sentence] The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic times.
+Back then,
+    Early
+galaxies 
+%mm themselves 
+are more gas-rich and their molecular fraction possibly higher 
+%mm compared to
+   than
+present-day galaxies.
+
+Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
+%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
+   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
+that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+%
+Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
+
+%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
+Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population. 
 %
 As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF).
-Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons - responsible for the photoheating of the gas - is strongly reduced.
-Such differences in turn affect the regulation of the multi-phase ISM thermal and chemical state.
-
-Even in the local Universe, where detailed \obs can be attained, variations in cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-It is thus intuitive and reasonable to pose the question: {\it what are the physical properties of MCs in early galaxies, and how do they differ from those found in local \galpop?}
+Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced.
+Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM).
+Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
+%
+Even in the local Universe, where detailed \obs can be made, variations in 
+%mm cloud
+     MCC  \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
+properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of MCCs in early galaxies, and how do they differ from those found in local \galpop?}
 %
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Smit18a,Jones17a}.
-
-To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming molecular cloud complexes in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Jones17a,Smit18a}.
+
+%mm To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts, 
+    To understand the physical properties of MCCs in early galaxies,
+we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming %mm molecular cloud complexes
+    MCCs
+in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
 
@@
 In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results.
-In \Sec{results}, we present the results and the scaling relations for the MCs.
+In \Sec{results}, we present the results and the scaling relations for the MCCs.
 We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCs, and the gravitational instability of galactic disks, which might be driving MC formation.
+We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation.
 Such notions will be used in the subsequent analysis of our simulations.
 \subsection{Larson relations and virial parameter}\label{sec:PVE}
-\citep{Larson81a} discussed a number of relations among Galactic MC properties, namely the linewidth-size, density-size, and mass-size relations.
+\citep{Larson81a} discussed a number of relations among Galactic MCC properties, namely the linewidth-size, density-size, and mass-size relations.
 Larson relations are routinely used for comparing properties of molecular structures in different galactic environments.
@@
 
-Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MC.
+Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MCC.
 Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
@@
 \citep{Romeo92a}.
-\AF{$R$ is not the same as the MC radius in the proev. Section}
+\AF{$R$ is not the same as the MCC radius in the proev. Section}
 In Equation~\ref{eqn:3Ddisp} the terms on the r.h.s.
@@
 The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}).
-We are interesting in determining whether MC properties are sensitive to these different dynamical conditions.
+We are interesting in determining whether MCC properties are sensitive to these different dynamical conditions.
 For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).
@@
 \caption{
-Examples of MCs (white contours) identified by the clump-finder in  \flower during its  accreting phase.
+Examples of MCCs (white contours) identified by the clump-finder in  \flower during its  accreting phase.
 The color-bar shows the mean H$_2$ number density, weighted by gas mass.
@@
 Left and right panels show the galaxy from different viewing angles.
-\label{fig:MC}}
+\label{fig:MCC}}
 \end{figure*}
@@
 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
-We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.
-
-To visually appreciate  the clump finding procedure, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
-Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) so that one can more easily see that they are collections of disjoint structures.
+We identify MCCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.
+
+To visually appreciate  the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
+Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
 %
@@
 
-The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$.
+The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$.
 The effective size is defined assuming spherical geometry, i.e.
@@
 %
-The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
+The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
 \begin{equation}
@@
 %
-In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
+In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
 We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity.
@@
 \end{equation}
-where the sum is done for the cells composing each MC.
+where the sum is done for the cells composing each MCC.
 %
 The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}.
-On average, the Mach number of the MCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
+On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
 
-We show in \Fig{dist} the MC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
 \begin{equation}
@@
 \end{equation}
-where $M_\star$ is the stellar mass within the MC volume.
+where $M_\star$ is the stellar mass within the MCC volume.
 %
 We note that the distributions vary for different evolutionary stages of \flower.
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
-%
-We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value.
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
+%
+We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value.
 \AF{This is true only for low $n_{cut}$?
 Why in Fig.
-do you show the valu 18.96 instead?} \DL{MCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$.
-The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-\AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCs?}
+do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$.
+The mass of the MCCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+\AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}
 
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
-Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
+Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}
@@
 \caption{
-Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
 Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
@@
 \includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages.
-Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
+\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages.
+Left panels show MCCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs identified using a high $n_{\rm cut}$\eq19\,\cc.
 \label{fig:alpha16-28}}
@@
 \AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
-We first focus on the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), and identify a set of MCs in each of them.
-Scaling relations for the MCs are shown in \Fig{larsons_single} for the accretion (left panels) and starburst phase (right), respectively.
+We first focus on the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), and identify a set of MCCs in each of them.
+Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accretion (left panels) and starburst phase (right), respectively.
 Let us start from analyzing the accretion phase.
 
-MCs in \flower\ are characterized by large velocity dispersions ($\sigma \approx 100 {\rm km s}^{-1}$) and sizes ($R\approx 100$ pc).
+MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \approx 100 {\rm km s}^{-1}$) and sizes ($R\approx 100$ pc).
 These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs.
@@
 Sizes are somewhat dependent on the choice of $n_{\rm cut}$.
-As such density threshold is increased, some of the MCs within the main disk break into multiple sub-MCs.
-In this case, we effectively identify a population of denser molecular structures (see \Fig{MC}).
+As such density threshold is increased, some of the MCCs within the main disk break into multiple sub-MCCs.
+In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}).
 Instead, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
 
-%Now discuss sigma - R relation; poor statistcis. But how many MCs do we have?
+%Now discuss sigma - R relation; poor statistcis. But how many MCCs do we have?
 
 % Starburst 
-Some MCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accretion phase.
+Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accretion phase.
 \DL{Is this significant enough to say something physical?
@@
 % PVE
-We also compare the MCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}).
-Dashed lines in the figure show the loci along which the given external pressures are needed for MCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
+We also compare the MCCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}).
+Dashed lines in the figure show the loci along which the given external pressures are needed for MCCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
 Heyer+09).
-The MCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6, which
+The MCCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6, which
 is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.
@@
 % column density) as fundamental properties of molecular cloud structure.
-Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
+Larson's third relation relates MCCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
 This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
@@
 \end{equation}
-then, assuming spherical symmetry, the mass of an MC can be expressed as a function of $A_v$ and its size $R$
+then, assuming spherical symmetry, the mass of an MCC can be expressed as a function of $A_v$ and its size $R$
 \begin{equation}\label{eqn:constantcolumndensity}
@@
 
-We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
 %
 In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
-As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
+As shown in \Fig{MR}, the MCCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
 %
@@
 \caption{
-Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+Size-mass relation of MCCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
 Red line shows the
@@
 The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
-Extrapolating the masses and sizes of MCs of \flower along the \citet{Kauffmann10b} 
-relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCs are capable of high-mass \SF.
+Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
+relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
 \label{fig:MR}}
@@
 % single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCs.
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs.
 That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
 %
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
-%
-In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
+%
+In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
 %
 This lack of variation is reassuring, i.e.
-the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$ on the scales studied in the present work.
+the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$ on the scales studied in the present work.
 Our results are therefore robust to the various density cuts of choice.
@@
 % temporal evolution in Cloud Dynamics
-We show the properties of all MCs identified across all evolutionary stages in \Fig{alpha16-28}. We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
+We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
 
@@
 %Star symbols are color-coded by $n_{\rm cut}$.
-%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCs in the satellite galaxies.
+%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCCs in the satellite galaxies.
 %\label{fig:alpha16}}
@@
 %\caption{
-%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols)
+%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCCs identified in our simulation (star symbols)
 %in the accretion phase (top panel) and the starburst phase (bottom panel)
@@
 %The V-shaped dashed lines show the loci along which the given external pressures
-%are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
+%are needed for MCCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
 %Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
 %Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
-%correspond to MCs in the satellite galaxies.
+%correspond to MCCs in the satellite galaxies.
 %\label{fig:alpha27}}
@@
 %identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-%Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
-%Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example).
+%Crosses correspond to positions of MCCs identified using the lowest $n_{\rm cut}$. % using 0.32
+%Positions of sub-MCCs are not shown (but see top row of \Fig{Qeff} for an example).
 %\label{fig:Q}}
@@
 %and gas surface density (middle) maps projected onto the $xy$-plane.
-%Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
+%Positions of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
 %and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
 %Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
-%Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
+%Cross markers indicate positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
 %Modest smoothing has been applied to the maps.
@@
 %identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-%Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$
+%Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$
 %are likely gravitationally unstable.
@@
 
-The MCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+The MCCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
 %
@@
 The higher velocity dispersions
-(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCs also have higher stellar-to-gas mass ratios of $\sim$60).
+(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCCs also have higher stellar-to-gas mass ratios of $\sim$60).
 %
@@
 \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCs in its satellites ($\sigma\approx$10\,\kms).
+Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\approx$10\,\kms).
 
 The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCs of \flower are found throughout the disk.
+In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
 This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
@@
 The presence of such extra-planar flows may also be the 
-dominant mode for forming the highly supersonic massive MCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCs in $z$\,\ssim2 galaxies could be smaller in reality.
+dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCCs in $z$\,\ssim2 galaxies could be smaller in reality.
 %
 The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
-the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is
-consistent with the high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.
+the MCCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is
+consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
 
 % mass-size relation
-MCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}.
-This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
-%
-That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.
+MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}.
+This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
+%
+That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MCC, and indeed, have sufficient column density to form CO.
 
@@
 an ``internal'' mass-size relation where $M\propto R^{1.33}$.
-If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
-regions of high-mass \SF. That is, the MCs identified have mass-size relations suggesting they are capable of high-mass \SF.
+If this holds for MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
+regions of high-mass \SF. That is, the MCCs identified have mass-size relations suggesting they are capable of high-mass \SF.
 
 % different evolutionary stages
-In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}).
-That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
-\DL{some MCs in SB phase have
+In the scaling relations examined, we find similar MCC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}).
+That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
+\DL{some MCCs in SB phase have
 lower $\alpha_{\rm vir}$ and pressure, but 
@@
 
-\subsection{Origin and Physical Scales of MCs} \label{sec:origin}
+\subsection{Origin and Physical Scales of MCCs} \label{sec:origin}
 
 The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{alpha16-28}).
-Overall, the MCs we identified are much bigger in size and mass than nearby GMCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
+Overall, the MCCs we identified are much bigger in size and mass than nearby GMCCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
 
@@
 gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yields
-$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCs identified (see \Fig{dist}).
+$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
 %
@@
 %Note that regions of $Q\lesssim1$ is actually somewhat
-%less than the number of MCs we have identified based on density threshold ---
+%less than the number of MCCs we have identified based on density threshold ---
 %but this has something to do with the dependence on
-%$n_{\rm cut}$. The number of MCs and regions of low $Q$ are comparable if we only look at
-%MCs identified at the highest $n_{\rm cut}$.
+%$n_{\rm cut}$. The number of MCCs and regions of low $Q$ are comparable if we only look at
+%MCCs identified at the highest $n_{\rm cut}$.
 
@@
 As shown in \Fig{larsons_single},
-the virial parameter of the sub-MCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-%
-For the MCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+the virial parameter of the sub-MCCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
+%
+For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
 Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
@@
 As shown in \Fig{larsons_single},
-MCs in the main disk of \flower have higher pressure than the sub-MCs.
-The lower virial parameter and external pressure of the sub-MCs compared to their parent MCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
-%Based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower,
-%the MC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
+MCCs in the main disk of \flower have higher pressure than the sub-MCCs.
+The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
+%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
+%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
 %and galactic rotation on large scales.
-%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.
-
-For MCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-This suggests that MCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
-
-\subsection{Stability of MCs}
+%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.
+
+For MCCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+This suggests that MCCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
+
+\subsection{Stability of MCCs}
 
@@
 All maps are projected onto the $xy$-plane.
-Positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
+Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
 A smoothing length of 30\,pc has been applied to the maps.
@@
 identification of regions above and below $\log{Q}$\eq0.
-Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
+Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
 are likely gravitationally unstable.
 Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
-indicates that stellar component plays an important role in governing the stability of the MCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
+indicates that stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}
@@
 Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
-(see also \Fig{h2density} for example of MCs identified in this evolutionary stage of \flower
+(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower
 using different $n_{\rm cut}$).
 
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCs against $m$\eq0 perturbations.
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against $m$\eq0 perturbations.
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
@@
 
-That is, some MCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
+That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
 Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
-thickness of its disk (via $\sigma_z$), some of these MCs are consistent with  $Q_{\rm eff} > 1$. 
+thickness of its disk (via $\sigma_z$), some of these MCCs are consistent with  $Q_{\rm eff} > 1$. 
 This demonstrates the importance of accounting for stellar contribution and disk thickness 
@@
 
-The apparently large virial parameters seen in the MCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}).
+The apparently large virial parameters seen in the MCCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}).
 We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
@@
 Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
-Second, this fragmentation scale is greater than the typical size of GMCs.
-This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
-%
-Thus, the high virial parameter found for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
+Second, this fragmentation scale is greater than the typical size of GMCCs.
+This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
+%
+Thus, the high virial parameter found for most MCCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
 As such,
-some MCs are found to lie in regions of $Q_{\rm eff}>1$.
-% some MCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
+some MCCs are found to lie in regions of $Q_{\rm eff}>1$.
+% some MCCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
 Only in (the denser) regions with a low Toomre $Q_{\rm eff}$ parameter and when the cooling time is lower then the dynamical time star formation can proceed in {\it clumps} and {\it cores} with low virial parameters.
 
-Note that even in stages when \flower~is star forming we find that most of its MCs have high $\alpha_{\rm vir}$.
+Note that even in stages when \flower~is star forming we find that most of its MCCs have high $\alpha_{\rm vir}$.
 This seem to be self-contradictory: if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
@@
 Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by large-scale gravitational potential and differential rotation.
-This in turn enables sub-regions of the MCs to collapse and potentially form OB associations out of these unbound MCs \citep{Clark04a, Clark05a}.
+This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
 %
@@
 Finally, the SFR of \flower is very bursty and high SFR stages are only transient.
-% the giant MCs found are likely due to non-axisymmetric mode.
+% the giant MCCs found are likely due to non-axisymmetric mode.
 
@@
 We use a clump-finding algorithm and a set of H$_2$ volumetric densities
-to identify MCs and their sub-structures in \flower and its satellites.
+to identify MCCs and their sub-structures in \flower and its satellites.
 We decompose the molecular structures into non-overlapping tiles
 by identifying a set of different density contours at different evolutionary stages.
-Such identification method is similar to MC identification based on 
+Such identification method is similar to MCC identification based on 
 contour levels/surfaces of surface brightness maps/cubes of molecular line tracers (e.g., CO, CS, NH$_3$),
@@
 
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC and we perform a Toomre-$Q$ stability analysis.
-The properties of the MCs in \flower are compared with observed MCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MCC and we perform a Toomre-$Q$ stability analysis.
+The properties of the MCCs in \flower are compared with observed MCCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
 This is done for different evolutionary stages of \flower.
 
-We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
+We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
 those observed in $z$\ssim2 starburst galaxies.
-The mass scale of the MCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
-The $\sim$200\,pc-scale MCs found with a low density threshold
-correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds.
-The more massive and bigger MCs in \flower compared to the Milky Way
+The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
+The $\sim$200\,pc-scale MCCs found with a low density threshold
+correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
+The more massive and bigger MCCs in \flower compared to the Milky Way
 likely result from the higher gas mass fraction, surface density, and velocity dispersion,
@@
 
-We compare the dynamics of MCs in \flower to \obs in the context of the Larson's relation.
-The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the
+We compare the dynamics of MCCs in \flower to \obs in the context of the Larson's relation.
+The MCCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the
 density threshold $n_{\rm cut}$ adopted in identifying the structures.
@@
 
-Virial analysis indicates that MC/arms of the main disk of \flower are unbound, but substructures have
-lower virial parameter. Some of these sub-MCs have Toomre $Q_{\rm eff}$ parameters consistent with being
+Virial analysis indicates that MCC/arms of the main disk of \flower are unbound, but substructures have
+lower virial parameter. Some of these sub-MCCs have Toomre $Q_{\rm eff}$ parameters consistent with being
 gravitationally unstable. This is consistent with the notion that collapsing structures resulting from
@@
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\approx$\,2 for MCs in the satellite galaxies, which we interpret as
+We also find $\alpha_{\rm vir}\approx$\,2 for MCCs in the satellite galaxies, which we interpret as
 result of the weaker/delayed stellar feedback compared to \flower. 
-In particular, some of the MCs in the satellites are collapsing structures that have not yet formed stars, as confirmed by their
+In particular, some of the MCCs in the satellites are collapsing structures that have not yet formed stars, as confirmed by their
 higher gas-to-stellar fractions.
 In terms of the scaling relations examined, we do not observe any significant
-temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation.
+temporal variations in the MCC dynamics over the course of 700\,Myr traced in our simulation.
 
@@
 \appendix
-\section{Variation in MC Properties Depending on the Choice of Density Cuts and Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
+\section{Variation in MCC Properties Depending on the Choice of Density Cuts and Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
 % single Snapshot
 We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
-different sets of $n_{\rm cut}$ in identifying the MCs.
+different sets of $n_{\rm cut}$ in identifying the MCCs.
 That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
 cloud scaling relations).
 %
-In addition, for the densest MC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%
-This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%
+This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$.
 Our results are therefore robust to the various density cuts of choice.
@@
 % temporal evolution in Cloud Dynamics
-We show the properties of all MCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
+We show the properties of all MCCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
 We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
@@
 \caption{
-%Comparison of MCs identified across all evolutionary stages (over 700\,Myr; star symbols)
+%Comparison of MCCs identified across all evolutionary stages (over 700\,Myr; star symbols)
 to those observed in nearby and \z$\sim$2 star-forming galaxies
 in the context of the linewidth-size relation.
-%Bottom panel corresponds to including only the denser substructures/sub-MCs identified in \flower
-(i.e., MCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+%Bottom panel corresponds to including only the denser substructures/sub-MCCs identified in \flower
+(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
 By and large, we find no quantitative differences in the mass-size relation over the 700\,Myr traced in the simulation.
@@
 \caption{
-Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCs identified across all evolutionary stages
+Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCCs identified across all evolutionary stages
 (i.e., with different SFR). Star symbols are color-coded by increasing SFR.
-Right panels correspond to including only the denser substructures/sub-MCs identified in \flower
-(i.e., MCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+Right panels correspond to including only the denser substructures/sub-MCCs identified in \flower
+(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
 We find no obvious differences in relation to those observed in nearby and \highz

### 2019-03-27 WRITEUP/ms.tex
final edits to intro
edits to 2.1 Virial parameter

@@
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
-In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results.
+In \Sec{eqn}, we describe the method used to identify
+%mm molecular gas complexes 
+    MCCs,
+and present the formalism within which we interpret the results.
 In \Sec{results}, we present the results and the scaling relations for the MCCs.
@@
 \subsection{Larson relations and virial parameter}\label{sec:PVE}
-\citep{Larson81a} discussed a number of relations among Galactic MCC properties, namely the linewidth-size, density-size, and mass-size relations.
+\citet{Larson81a} discussed a number of relations among Galactic 
+%mm MCC 
+     molecular cloud 
+properties, namely the linewidth-size, density-size, and mass-size relations.
 Larson relations are routinely used for comparing properties of molecular structures in different galactic environments.
-They also represent a useful framework to analyze our results as they arise from the interplay between gravity and turbulence encoded in the virial theorem.
-
-In general, the virial theorem for a gas distribution of gas can be written as
+They also represent a useful framework to analyze our results as they
+%mm
+     have been argued to 
+arise from the interplay between gravity and turbulence encoded in the virial theorem
+%mm 
+    (however, note the alternative interpretation involving gravitational collapse by 
+    \citealt{Ballesteros-Paredes11}).
+
+%mm In general, the virial theorem for a gas distribution of gas can be written as
+     The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee1992}
 \begin{equation}\label{eqn:virial_th_general}
@@
 %
-Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and r.m.s.
-velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
-Neglecting magnetic field and defining $P_{\rm ext}$ the external pressure, \Eq{virial_th_general} can be written as
+Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
+%mm Neglecting magnetic field and 
+Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
 \begin{equation}
@@
 \end{equation}
-where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the r.h.s. represent the kinetic, external, and gravity pressure terms.
-
-Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e. ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
-$\Sigma$\eq$M/\pi R^2$, and rewrite previous equation as 
+where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the
+%mm  kinetic, external, and gravity pressure terms. 
+    kinetic energy, external pressure, and gravitational potential energy terms.
+
+Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e.\ ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
+$\Sigma$\eq$M/\pi R^2$, and rewrite the previous equation as 
 \begin{equation}
@@
 
-Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MCC.
+Summarizing, the virial parameter can be used to quantify the stability/boundedness of 
+%mm an MCC. 
+    a molecular cloud.
 Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
 %
-Such criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
+Such a criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
 

### 2019-03-27 WRITEUP/ms.tex
rearranged Toomre discussion fairly extensively, added reference to Rafikov 2001

@@
 
-The onset of gravitational instability is considered to be tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-From virial theorem, Jeans instability sets the scales at which gravitational potential overcomes the internal energy.
-Namely, gravitational instabilities dominates at scales $L > L_J$, where $L_J$ is the Jeans length.
-However, centrifugal forces resulting from differential rotation in disk galaxies can stabilize perturbations even on these scales.
-As a result, a disk is thought to be unstable on scales between $L_J < L < L_{\rm rot}$, where $L_{\rm rot}$ is set by the surface density of the disk and the angular velocity of the rotation.
-
-In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to the disk r.m.s.
-velocity dispersion \AF{This is not exactly the same $\sigma$ as before} ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
-% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
-%
-% from linear analysis
+The onset of gravitational instability is 
+%mm considered to be 
+tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}. 
+%mm [rearranged to put derivation before result]
 For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
 \begin{equation}
-\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
+\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma_{\rm disk}^2 k^2\,,
 \label{eqn:3Ddisp}
@@
 \begin{equation}
-\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,.
+\kappa^2\equiv\frac{2\Omega}{\altomega}\frac{d}{d\altomega}\left(\altomega^2\Omega\right)\,.
 \label{eqn:kappa}
@@
 \citep{Romeo92a}.
-\AF{$R$ is not the same as the MCC radius in the proev. Section}
-In Equation~\ref{eqn:3Ddisp} the terms on the r.h.s.
-are related to rotation, self-gravity and internal pressure, respectively.
-The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
+\AF{$R$ is not the same as the MCC radius in the prev.\ Section} \MM{replaced $R$ with $\altomega$, and $\sigma$ with $\sigma_{\rm disk}$.}
+In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively. 
+%mm
+    Heuristically, the instability can be understood by considering the scale
+ at which gravitational potential overcomes the internal energy. Gravity dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, 
+%mm centrifugal forces resulting from
+   shearing by 
+differential rotation in disk galaxies can stabilize perturbations 
+%mm even on these scales. 
+    that might otherwise collapse for $L > L_{\rm rot}$, where $L_{\rm rot}$ is set by $\kappa$.
+%mm As a result, a disk is thought to be unstable on
+    As a result, disks are unstable to gravitational collapse on 
+scales between $L_J < L < L_{\rm rot}$.
+
+From the dispersion relation, a parameter $Q$ can be derived such that $Q < 1$ when instability occurs, that reproduces this inequality to order unity.
+For a collisionless fluid---such as an ensemble of stars--- this parameter is \citep{Toomre64a}
+\begin{equation}
+Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
+\end{equation}
+The equivalent parameter for a collisional gas was derived by
+%mm [corrected from Toomre64a to Goldreich65a (not Goldreich65b, which is about spiral arm formation)]
+    \citep{Goldreich65a}:
 \begin{equation}
@@
 In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). 
-Physically, this implies that the local gravitational field
-overcomes support from pressure and rotation, allowing fragmentation and collapse to happen.
-Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
-\begin{equation}
-Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
-\end{equation}
-
-In our stability analysis, we account for the non-negligible disk thickness and for the combined effect of gas and stars; this is done adopting the approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
-%
-The effect of disk thickness modify the $Q$ parameter for gas/star by accounting for the vertical velocity dispersion:
+%mm  In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
+     A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion
+$v_{\rm circ}/\sigma_{\rm disk}$
+%mm , i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} \MM{see above} ratio 
+\citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
+% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
+%
+% from linear analysis
+
+In our stability analysis, we account for the combined effect of gas and stars 
+%mm 
+     \citep[derived exactly by][]{Rafikov01}, 
+and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
+%
+The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion:
 \begin{equation}
@@
 \end{equation}
-Conceptually, the thickness of a disk reduces the gravity in the vertical direction, thereby making it easier for a system to obtain stability, and thus lowering the criterion of the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to
+Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
+%mm obtain
+    maintain 
+stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
 0.67 \citep{Goldreich65a}.
 %
-On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus, increasing the criterion of the Toomre $Q_{\rm crit}$, unless it is dynamically hot to ``compensate''.
-As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.
-% 0.67 * 2
+On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus, increases
+%mm  the criterion of the Toomre
+$Q_{\rm crit}$
+%mm, unless it is dynamically hot to ``compensate''. 
+As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
 

### 2019-03-27 WRITEUP/ms.tex
definition for altomega added, kohandel bibentry cleaned
revisions to 3.0

@@
 %
-On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus, increases
+On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
 %mm  the criterion of the Toomre
-$Q_{\rm crit}$
+$Q_{\rm crit}$, 
 %mm, unless it is dynamically hot to ``compensate''. 
+   moreso if the stars have low velocity dispersion.
 As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
@@
 %
-\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
-%
-In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
-The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level.
-Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
-
-We include a chemical network including ${\rm e}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
-Of particular importance here is that abundances are calculated using a on-the-fly non-equilibrium formation of molecular hydrogen scheme following \citet{Pallottini17b}.
+\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
+%
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, 
+%mm resolving down to a physical scale of 
+     with the finest refined cell sizes 
+$l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution
+%mm
+    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
+    local density, which would have to be specified here.}
+ of $m_b\simeq$\,10$^4$\,\Msun at the finest level. 
+%mm Such a physical scales are comparable to those of
+     Cell sizes are comparable to the sizes of
+local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
+%mm 
+     \MM{Nota Bene!} although the resolved scale of 5--10 cells is rather larger.
+
+%mm We
+    The models 
+include a chemical network 
+%mm including ${\rm e}^{-}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ 
+   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$
+\citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme 
+%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
+    described by \citet{Pallottini17a}.
 
 % radiative feedback --> NT pressure
-Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SN) and OB/AGB stars.
+Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe)
+%mm and OB/AGB stars. 
+   as well as OB and asymptotic giant branch stars.
 Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
@@
 Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
-
-The simulation zooms on a galaxy named \flower whose properties are given in \citet{Pallottini17b} and are briefly summarized in the following.
-\flower is a Lyman-break galaxy (LBG), that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc; \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+%mm
+   \MM{confirm:} Photoionization and stellar wind feedback is neglected.
+
+The simulation zooms in on a galaxy named
+%mm 
+   after the flower 
+\flower whose properties are given in 
+%mm \citet{Pallottini17b} 
+      \citet{Pallottini17a} 
+and are briefly summarized in the following. \flower is a Lyman-break galaxy 
+%mm (LBG), [unused acronym]
+that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+\flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
+\MM{What is its gas fraction?
+I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 

### 2019-03-27 WRITEUP/ms.tex
revisions and comments on Sect 3 Numerical Methods

@@
 \IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
+
+%\def\altomega{r_{\rm disk}}
+\def\altomega{\varpi}
 
@@
 %mm (LBG), [unused acronym]
-that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
-\flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-\MM{What is its gas fraction?
-I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
+  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
+accretes mass from the IGM mainly via three filaments of length
+$\simeq$\,100\,kpc. \flower has a stellar mass of
+$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
+$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
+  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,
+%mm [not according to Figure 1] 100
+     50--70
+\,\Msun\,yr\pmOne. \MM{What is its gas fraction?  I ask because its
+  molecular gas mass is minuscule, particularly for such a high SFR:
+  this is a depletion time of only 0.7--1 Myr, while modern galaxies
+  usually have depletion times more like 0.5--2~{\em Gyr!}} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 
@@
 The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
-The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
 The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
 
-Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}).
-The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}).
-We are interesting in determining whether MCC properties are sensitive to these different dynamical conditions.
-For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).
-
-Throughout this paper, we dub as ``satellite galaxies'' the dense gas regions outside the main disk of \flower.
-The distinction between clumps and satellites is admittedly somewhat ambiguous, and we consider it only as a working one.
+Given \flower's SF stochastic nature, in this work we mostly focus on
+the analysis of two of its most extreme evolutionary stages (see
+\Sec{singless}). The two phases correspond to (a) intense accretion
+(b) starburst (\Fig{SFH}). We are interesting in determining whether
+MCC properties are sensitive to these different dynamical
+conditions. For completeness, for the other evolutionary stages traced
+in the simulation we only show scaling relations (see 
+%mm [Figures must be numbered and placed in order cited.  Better to
+%cite to the section and leave the figure in its proper place.] \Fig{alpha16-28}).
+     Sect.~\ref{sec:ncut}).
+
+Throughout this paper, we 
+%mm dub as ``satellite galaxies'' the dense gas regions outside the
+%main disk of \flower. 
+     describe  the dense gas regions outside the main disk of \flower
+     as satellite galaxies.
+The distinction between clumps and satellites is admittedly somewhat
+ambiguous, though, and we consider it only as a working one.
 \AF{To be discussed at the end}

### 2019-03-27 WRITEUP/ms.tex
updated Sec 3

--- 2019-03-27 WRITEUP/ms.tex
@@
 We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
-prototypical galaxy (``\flower'') at redshift $z\approx 6$.
+prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
 %
@@
    cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
-that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
 %
@@
 %
-In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, 
-%mm resolving down to a physical scale of 
-     with the finest refined cell sizes 
-$l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
+The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size.
+The simulation zoom-in on a target halo of mass $\sim 10^11 \Msun$.
+The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter (equivalent baryonic) mass resolution is $\simeq 6\times 10^4 \Msun$ ($1.2 \times 10^4 \Msun$).
+Such region is spatially refined with a quasi-Lagrangian mass threshold-based criterion, i.e.
+a cell is refined if its total (DM+baryonic) mass exceed the the mass resolution by a factor 8.
+The final finest refined cell in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$).
 %mm
     \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
-    local density, which would have to be specified here.}
- of $m_b\simeq$\,10$^4$\,\Msun at the finest level. 
-%mm Such a physical scales are comparable to those of
-     Cell sizes are comparable to the sizes of
-local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
+    local density, which would have to be specified here.} \AP{the setting description has been extended}
+     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
 %mm 
-     \MM{Nota Bene!} although the resolved scale of 5--10 cells is rather larger.
-
+     \MM{Nota Bene!} \AP{This note is discussed in details in the following section.
+In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
 %mm We
-    The models 
-include a chemical network 
+    The models include a chemical network 
 %mm including ${\rm e}^{-}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ 
-   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$
-\citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme 
+   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}.
+Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme
 %mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
@@
 %mm and OB/AGB stars. 
-   as well as OB and asymptotic giant branch stars.
+   as well as winds from OB and asymptotic giant branch stars.
 Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
@@
 %mm
-   \MM{confirm:} Photoionization and stellar wind feedback is neglected.
+   \MM{confirm:} Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}. \AP{modified accordingly}
 
@@
 \MM{What is its gas fraction?
-I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very flickering and depends on which radius we are considering, as the galaxy is actively accreating material and merging; depletion time are low, see the ssfr note added considering that $ssfr \propto t_{depletion}^{-1}$} The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq 4 -- 40 \rm Gry ^{-1}$, compatible with sSFR vs $M_{\star}$ relation observed at high-redshift \citep{Jiang2016}, that is higher with respect to normal local galaxies.
+Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 
@@
 The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
-The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\simeq$15\,kpc).} of \flower is shown in \Fig{SFH}.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\simeq 700$ Myr.
 
@@
 The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}.
-On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$.
+On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$.
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
@@
 do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$.
-The mass of the MCCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+The mass of the MCCs identified ranges between $M_{\rm cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
 \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}
@@
 
-MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \approx 100 {\rm km s}^{-1}$) and sizes ($R\approx 100$ pc).
+MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$ pc).
 These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs.
@@
 %Star symbols are color-coded by $n_{\rm cut}$.
-%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCCs in the satellite galaxies.
+%Star symbols lying close to $\alpha_{\rm vir}\simeq2$ correspond to MCCs in the satellite galaxies.
 %\label{fig:alpha16}}
@@
 \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\approx$10\,\kms).
+Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).
 
@@
 Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
-velocity dispersion of $\sigma\approx50$\,\kms and a
-gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yields
+velocity dispersion of $\sigma\simeq50$\,\kms and a
+gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
 $M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
@@
 Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
-That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\approx$\,30\,pc).
+That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
 
@@
 %
-For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
+For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
 Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
@@
 
-We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
+We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\simeq$\,200\,\kms) comparable to
 those observed in $z$\ssim2 starburst galaxies.
@@
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\approx$\,2 for MCCs in the satellite galaxies, which we interpret as
+We also find $\alpha_{\rm vir}\simeq$\,2 for MCCs in the satellite galaxies, which we interpret as
 result of the weaker/delayed stellar feedback compared to \flower. 

### 2019-03-27 WRITEUP/ms.tex

@@
 The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
-The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\simeq$15\,kpc).} of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\simeq 700$ Myr.
-
-Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}).
-The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}).
-We are interesting in determining whether MCC properties are sensitive to these different dynamical conditions.
-For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).
-
-Throughout this paper, we dub as ``satellite galaxies'' the dense gas regions outside the main disk of \flower.
-The distinction between clumps and satellites is admittedly somewhat ambiguous, and we consider it only as a working one.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
+The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
+
+Given \flower's SF stochastic nature, in this work we mostly focus on
+the analysis of two of its most extreme evolutionary stages (see
+\Sec{singless}). The two phases correspond to (a) intense accretion
+(b) starburst (\Fig{SFH}). We are interesting in determining whether
+MCC properties are sensitive to these different dynamical
+conditions. For completeness, for the other evolutionary stages traced
+in the simulation we only show scaling relations (see 
+%mm [Figures must be numbered and placed in order cited.  Better to
+%cite to the section and leave the figure in its proper place.] \Fig{alpha16-28}).
+     Sect.~\ref{sec:ncut}).
+
+Throughout this paper, we 
+%mm dub as ``satellite galaxies'' the dense gas regions outside the
+%main disk of \flower. 
+     describe  the dense gas regions outside the main disk of \flower
+     as satellite galaxies.
+The distinction between clumps and satellites is admittedly somewhat
+ambiguous, though, and we consider it only as a working one.
+
 \AF{To be discussed at the end}

### 2019-03-27 WRITEUP/ms.tex
revisions in response to Andrea's edits of Sect 3.

@@
 %
-In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
-The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size.
-The simulation zoom-in on a target halo of mass $\sim 10^11 \Msun$.
-The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter (equivalent baryonic) mass resolution is $\simeq 6\times 10^4 \Msun$ ($1.2 \times 10^4 \Msun$).
-Such region is spatially refined with a quasi-Lagrangian mass threshold-based criterion, i.e.
-a cell is refined if its total (DM+baryonic) mass exceed the the mass resolution by a factor 8.
-The final finest refined cell in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$).
+In particular, it uses a modified version of \ncode{ramses}
+\citep{Teyssier02a} as the AMR backend. The simulation used here
+covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
+zooms in on a target halo of mass $\sim 10^11 \Msun$. The Lagrangian
+region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
+%mm (equivalent baryonic) 
+mass resolution of $\simeq 6\times 10^4 \Msun$, 
+%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
+%I have it right]  Such
+     equivalent at initial density to a baryonic mass resolution of $1.2
+     \times 10^4 \Msun$.  This 
+region is spatially refined with a quasi-Lagrangian criterion based on
+a mass threshold, so that a cell is refined if its total dark matter
+plus baryonic mass exceeds the mass resolution by a factor of
+eight. The final finest refined cell in the zoom in region has size
+$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
 %mm
-    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
-    local density, which would have to be specified here.} \AP{the setting description has been extended}
+%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
+%    local density, which would have to be specified here.} \AP{the setting description has been extended}
      Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
 %mm 
-     \MM{Nota Bene!} \AP{This note is discussed in details in the following section.
+%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section.
 In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
-%mm We
 The models include a chemical network 
-%mm including ${\rm e}^{-}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ 
-   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}.
-Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme
+following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
+H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
+that abundances are calculated using an on-the-fly non-equilibrium
+formation of molecular hydrogen scheme  
 %mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
@@
 %mm
-   \MM{confirm:} Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}. \AP{modified accordingly}
+%   \MM{confirm:} 
+Photoionization from local sources is neglected in this simulation
+\citep[see][for its effect]{pallottini:2019,decataldo:2019}. 
+%mm \AP{modified accordingly}
 
@@
 %mm (LBG), [unused acronym]
-that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
-\flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne.
-\MM{What is its gas fraction?
-I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very flickering and depends on which radius we are considering, as the galaxy is actively accreating material and merging; depletion time are low, see the ssfr note added considering that $ssfr \propto t_{depletion}^{-1}$} The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq 4 -- 40 \rm Gry ^{-1}$, compatible with sSFR vs $M_{\star}$ relation observed at high-redshift \citep{Jiang2016}, that is higher with respect to normal local galaxies.
-Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
+  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
+accretes mass from the IGM mainly via three filaments of length
+$\simeq$\,100\,kpc. \flower has a stellar mass of
+$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
+$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
+  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of
+%mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
+   30--80 \Msun\,yr\pmOne. 
+%mm \MM{What is its gas fraction?  I ask because its molecular gas
+%mass is minuscule, particularly for such a high SFR: this is a
+%depletion time of only 0.5 Myr, while modern galaxies usually have
+%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
+%flickering and depends on which radius we are considering, as the
+%galaxy is actively accreating material and merging; depletion time
+%are low, see the ssfr note added considering that $ssfr \propto
+%t_{depletion}^{-1}$} 
+The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
+\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
+relation observed at high redshift \citep{Jiang2016}, which is higher
+than normal local galaxies. The effective stellar radius of \flower
+is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
+  200}\simeq$\,15\,kpc.
 
@@
 \caption{
-    {\it Top panel}: Star formation history of \flower.
+    {\it Top}: Star formation history of \flower.
 {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accretion phase;  {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
@@
 
-One of the main advantages for studying the dynamical properties of simulated galaies is the fact that we can examine how their properties evolve with time.
+One of the main advantages for studying the dynamical properties of simulated galaies is that we can examine how their properties evolve with time.
 %
@@
 % mainly expecting differences in alpha_vir, sigma, M_cl.
-
-The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass.
-The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
+%mm [delete para break]
+The \SF history\footnote{Note that here the SFR is calculated based on
+  the stellar mass formed in the last 10 Myr within 3.5 kpc from the
+  galaxy center of mass. The SFR plotted in Figure 2 of
+  \citet{Pallottini17b} is a factor of two higher since there the SFR
+  accounts for the contribution from massive satellite galaxies within
+  the virial radius ($\approx$15\,kpc).} of \flower is shown in
+\Fig{SFH}.
+The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
 

### 2019-03-27 WRITEUP/ms.tex
revisions to 4.1

@@
 
-To identify the molecular complexes, we use a customized version of the ``clump-finding'' algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a}, but this function has been modified since then.
-%
-The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a $k$-dimensional tree ($k$-D tree).
-It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
-In the customized version used for this study, we modify the function to enhance the stability of the code.
+To identify the molecular complexes, we use a customized version of
+the clump-finding algorithm available in the \ncode{python} package
+\ncode{yt} \citep{Turk11a}, which was initially described in
+\citet{Smith09a}, 
+%mm but this function has been modified since then.
+     and modified since.
+The latest version of the default \ncode{yt} clump finder decomposes
+the zones of the simulation into non-overlapping tiles, which are
+stored in a 
+%mm $k$-dimensional tree ($k$-D tree). [unused acronym]
+     three-dimensional tree that can be processed using $k$-dimensional tree algorithms.
+     \MM{Too persnickety?} 
+It then identifies the contours of a variable field (here, the density
+field) within a tile and connects them across the tiles. In the
+customized version used for this study, we
+%mm modify the function to enhance 
+     enhanced
+the stability of the code.
 %
@@
 
-In the clump-finding process, we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z$\eq6.0\,$-$\,7.2).
-%
-We note that this process is in essence similar to identifying molecular structures based on the noise levels of surface density maps observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN, as commonly adopted in observational studies (e.g., identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
-%
-We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
+In the clump-finding process, we employ a set of different density
+thresholds defined based on the molecular hydrogen density of \flower
+at different evolutionary stages ($z=6.0$--7.2).
+%
+We note that this process is 
+%mm in essence similar
+    the three-dimensional analog
+to identifying molecular structures based on the noise levels 
+%mm of surface density maps
+     in position-position-velocity maps that
+observers obtain with telescopes, using molecular line tracers such as
+CO, CS, and HCN.
+%mm , as commonly adopted in observational studies (e.g., 
+     This is commonly done by 
+identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+%
+%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
 % Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
-Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see also \citealt{Shetty10a} for a discussion on caveats and limitations).
+Existing studies find a good correspondence in the dynamical
+properties extracted in PPV- versus PPP-space 
+%mm
+   for well-isolated structures 
+(\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see
+%mm
+    \citealt{Ballesteros-Paredes02a} and 
+\citealt{Shetty10a} for a discussion on caveats and limitations).
 % large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
-\caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
+\caption{Probability distribution function of the H$_2$ number density
+  in \flower during the accreting phase shown in \Fig{SFH}{\em
+    (b)}. \MM{PDFs should be normalized to unity by dividing by the
+    area under the curve (total number of samples).  A label on the
+    y-axis would also be useful, and perhaps minor ticks on the x-axis.}
 \label{fig:h2density}}
@@
 \caption{
-Examples of MCCs (white contours) identified by the clump-finder in  \flower during its  accreting phase.
-The color-bar shows the mean H$_2$ number density, weighted by gas mass.
-Different rows shows the clump-finder results obtained by applying different H$_2$ number density cuts density cuts $(n_{\rm cut})$ as shown by the label.
+Examples of MCCs (white contours) identified by the clump finder in
+\flower during its  accreting phase. The color bar shows the mean
+H$_2$ number density, weighted by gas mass.
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label.
 Left and right panels show the galaxy from different viewing angles.
@@
 
-In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by including the contribution from the gas within 3.5 kpc from the galaxy center.
-%
-We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger than zero.
-This implies that the field is made of isolated components.
-See Fig.
-6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
-We identify MCCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.
-
-To visually appreciate  the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
+In \Fig{h2density}, we show the probability distribution of H$_2$
+number density $n_{\rm H2}$ for \flower~ during its accreting phase,
+including the contribution from the gas within 3.5 kpc from the
+galaxy center. 
+%
+We note that the distribution is almost flat for $n_{\rm
+  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
+are found based on morphological analysis\footnote{For $n_{\rm
+    H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$
+  density field is significantly larger than zero. This implies that
+  the field is made of isolated components. See Fig. 6 in
+  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
+applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
+    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
+5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
+%mm [I moved the next sentence into the main text from the footnote.]
+We also tested variations in
+  $n_{\rm cut}$ range and found no qualitative differences (see
+  \Sec{ncut}).
+%mm
+\MM{I am confused how H$_2$ can survive at such low number
+  densities.  Is there some sort of hidden clumping factor at work
+  here? Or is this due to the neglect of local photodissociating
+  radiation? Either way, the point should be mentioned in section 3, I
+guess.}
+
+To visually
+%mm appreciate
+    display 
+the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
 Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
@@
 
-Note that we impose the additional constraint that an identified structure must be composed of at least 10 cells.
-We caution that an important caveat of such constraint is that we can only examine the parameter space of ``cloud'' of typical size $R\gtrsim 60$\,pc, because of the resolution limit in the simulation.
-
-\subsection{Molecular Cloud Properties}
+Note that we impose the additional constraint that an identified
+structure must be composed of at least 10 cells. We caution that an
+important caveat of such a constraint is that we can only examine the
+parameter space of cloud complexes of 
+%mm typical size
+   radius 
+$R\gtrsim 60$\,pc, because of the resolution limit of the simulation.
+
+\subsection{Molecular Cloud 
+%mm
+    Complex
+Properties}
 

### 2019-03-27 WRITEUP/ms.tex
revisions and comments to 4.2

@@
 parameter space of cloud complexes of 
-%mm typical size
-   radius 
-$R\gtrsim 60$\,pc, because of the resolution limit of the simulation.
+%mm typical size $R\gtrsim 60$\,pc [revised assuming spherical MCCs
+%per Sect 4.2]
+   radius $R\gtrsim 40$\,pc,
+because of the resolution limit of the simulation.
 
@@
 % the mechanisms and physics of formation and evolution of molecular structures and \SF.
-Upon identifying the molecular structures, we extract properties such as the gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), r.m.s.
-velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.
+Upon identifying the molecular structures, we extract properties such
+as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
+$\mathcal{M}$, r.m.s. velocity dispersion $\sigma$
+, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.
 
@@
 %
-The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
+The velocity dispersion of MCCs is calculated from non-thermal
+velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
 \begin{equation}
@@
 %
-In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas.
-We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity.
-For instance, the non-thermal velocity dispersion is calculated as follows:
+In \obs of MCCs, the linewidth contribution of dense gas 
+exceeds that from the diffuse gas. We therefore calculate each term on
+the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
 \begin{equation}
@@
 %
-The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}.
+The local sound speed of all identified molecular complexes is much
+smaller than their turbulent velocities\footnote{Velocity dispersions
+  calculated from velocity field are comparable to those calculated
+  from the pressure field 
+%mm
+    \MM{The turbulent pressure field has not been
+    mentioned in section 3, so you'll need to add a sentence there
+    mentioning its presence and behavior to mention it here}, 
+indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}.
 On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$.
@@
 %
-We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value.
-\AF{This is true only for low $n_{cut}$?
-Why in Fig.
-do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$.
-The mass of the MCCs identified ranges between $M_{\rm cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-\AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}
+We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
+all the evolutionary stages considered in this work, for each  $n_{\rm
+  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
+  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
+  is the case for each ncut.} \MM{I am afraid I am also confused by
+  this, for two reasons.  First, if I understand the Figure, the
+  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
+  back in section 3, the H$_2$ mass of \flower was given as 5\E7
+  \Msun, precluding the existence of even a single 10$^8$ \Msun
+  cloud.} Such massive clouds correspond to the molecular disk of the
+galaxy, which is identified as a single component for low $n_{\rm
+  cut}$. The mass of the MCCs identified ranges between $M_{\rm
+  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
+\z$\sim$2 galaxies in rest-frame UV and optical light
+\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
+  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
+  high-density plot, it looks like you have quite a number of
+  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}
 
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
-Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCCs are identified at higher $n_{\rm cut}$.
+\caption{Distributions of mass (left), size (middle), and gas mass
+  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
+  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
+%mm
+      over all times analyzed here.
+Note that the scalesshown on the $y$-axes are different between the top
+and bottom panels, as fewer MCCs are identified at higher $n_{\rm
+  cut}$. \MM{Put labels on the y-axis (maybe just $N$ or some such). Tick marks should point inwards
+  rather than outwards.  I'd suggest putting the $n_{\rm cut}$ labels
+  on the left panels following the style of the previous figure (and
+  drop the brackets around the unit there). The $R$ axis could
+  reasonably be pulled in to 250 pc, providing a bit more dynamic
+  range at the low end.}
 \label{fig:dist}}

### 2019-03-28 WRITEUP/ms.tex
first comments on sec 5.  More to come

@@
 \caption{
-    {\it Top}: Star formation history of \flower.
-{\it Bottom}: projected stellar mass distribution during {\it (a)} an early accretion phase;  {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
+    {\it Top}: Star formation history of \flower. {\it Bottom}:
+    projected stellar mass distribution during {\it (a)} an early
+    accreting phase;  {\it (b)} a major starburst following a merger
+    event; and {\it (c)} a relatively quiescent post-starburst
+    phase. \MM{The figure says ``Accreting'', so I have edited
+      elsewhere to match.  You could also remove the quote marks from Quiescent.}
 \label{fig:SFH}}
@@
 \caption{
-Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting phase (left) and starburst phase (right).
-Star symbols are color-coded by the density thresholds ($n_{\rm cut}$).
-Data points in the $\alpha_{\rm vir}$-mass figure are taken from \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein (see Fig 4 of \citealt{Kauffmann17b}).
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
+(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
+MCCs (star symbols) identified in the two most extreme evolutionary
+stages of \flower\ ---accreting phase (left) and starburst phase
+(right). Star symbols are color-coded by the density thresholds
+$n_{\rm cut}$.  \MM{Give the color coding somewhere.} 
+Data points in the $\alpha_{\rm vir}$-mass figure are taken from
+\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
+(see Fig 4 of \citealt{Kauffmann17b}).   \MM{For consistency with
+  Figure 1, label as ``Accreting'' rather than ``Accretion'' phase. I
+  am inclined to leave the pressure confinement curves off of the
+  final plot.}
 \label{fig:larsons_single}}
@@
 \AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
-We first focus on the two most extreme evolutionary stages of \flower\ --- accretion and starburst phase (see \Sec{sfh}), and identify a set of MCCs in each of them.
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accretion (left panels) and starburst phase (right), respectively.
+We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), and identify a set of MCCs in each of them.
+Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively.
 Let us start from analyzing the accretion phase.
@@
 Heyer+09).
-The MCCs in the satellite galaxies are found to follow the locus of $\log{(P/\textrm{K cm}^{-3})}$\eq6, which
+The MCCs in the satellite galaxies are found to follow the locus of
+$\log{(P/\textrm{K cm}^{-3})}$\eq6, \MM{This is not shown in the
+  figure.  If you want to claim it, it needs to be shown somewhere.} which
 is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.
@@
 % column density) as fundamental properties of molecular cloud structure.
-Larson's third relation relates MCCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}.
-This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
+Larson's third relation relates MCCs structures on small and large
+scales via two physical properties: mass and size \citep{Larson81a,
+  McKee07a}. This is also known as the constant column density
+relation,
+\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+  point on that relationship, at the constant $\Sigma$ value.  This
+  suggests that the mass-size relation is just an artifact of the
+  narrow range of column densities observed with $^{12}CO$, as
+  suggested among others by \citet{Ballesteros11}.}
+ since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
 By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
@@
 \caption{
-Size-mass relation of MCCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+Size-mass relation of MCCs identified in the accreting phase \MM{In
+  Figure  of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
 Red line shows the

### 2019-03-29 WRITEUP/ms.tex
missing bracket
minor comments

@@
 guess.}
+\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
+ what one expects for purely H2 regions.}
 
@@
   \Msun, precluding the existence of even a single 10$^8$ \Msun
-  cloud.} Such massive clouds correspond to the molecular disk of the
+  cloud.} 
+\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
+like total gas mass. AP will add disclaimer in Section 3. Will double check 
+Mcl for all ncut and address AF's comment.}
+  Such massive clouds correspond to the molecular disk of the
 galaxy, which is identified as a single component for low $n_{\rm
@@
 \label{fig:MR}}
+}
 \end{figure*}

### 2019-03-29 WRITEUP/ms.tex
comments on the summary.  Will now try to go back and comment secs 5-7

--- 2019-03-28 WRITEUP/ms.tex
@@
 %
-In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$.
-As shown in \Fig{MR}, the MCCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
+In the same plot, we also show loci of constant surface densities,
+which are parameterized through the visual extinction $A_V$. \MM{Why
+  do you go through $A_v$ rather than just using surface densities
+  directly?} As shown
+in \Fig{MR}, the MCCs identified in \flower lie above this relation,
+along the locus of $A_v \simeq 8.9$ clouds observed by
+\citet{Lombardi10a} in the MW. \MM{Does the variation in surface
+  density seen in Figure 6 correspond to the variation in $A_V$ seen
+  here?}
 %
@@
 \caption{
-Size-mass relation of MCCs identified in the accreting phase \MM{In
-  Figure  of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
 Red line shows the
-mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}.
-Star symbols are color-coded by increasing $n_{\rm cut}$.
-Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
+mass-size relation found for regions in the Milky Way with massive \SF
+reported by \citet{Kauffmann10b}. Star symbols are color-coded by
+increasing $n_{\rm cut}$. \MM{which direction? White high or blue
+  high?} Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
 Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
 constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
-The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
+%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
+%same as \Fig{larsons_single}.  
 Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
@@
 
-The largest molecular structure identified is essentially the main disk of \flower and breaks down into smaller substructures that are denser as we increase $n_{\rm cut}$ (see e.g., \Fig{alpha16-28}).
-Overall, the MCCs we identified are much bigger in size and mass than nearby GMCCs, but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
+The largest molecular structure identified is essentially the main
+disk of \flower and breaks down into smaller substructures that are
+denser as we increase $n_{\rm cut}$ (see e.g.,
+\Fig{alpha16-28}). Overall, the MCCs we identified are much bigger in
+size and mass than nearby giant molecular clouds (GMCs), but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
 
@@
 Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
-Second, this fragmentation scale is greater than the typical size of GMCCs.
-This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
+Second, this fragmentation scale is greater than the typical size of GMCs.
+This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
 %
@@
 
+\MM{Each item in the summary needs to refer to definite results and
+  analysis in the previous paper.  I have noted the items that don't
+  seem to me to have that necessary support.}
 We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy, \flower,
-at the EoR using state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
+at the EoR using the state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
 which includes a chemical network to determine the formation of molecular
-hydrogen, heating and cooling of the ISM by metals, and detailed stellar feedback.
+hydrogen, heating and cooling of the ISM by
+%mm metals
+    UV radiation and metal lines, 
+and detailed stellar feedback.
 We use a clump-finding algorithm and a set of H$_2$ volumetric densities
 to identify MCCs and their sub-structures in \flower and its satellites.
-We decompose the molecular structures into non-overlapping tiles
-by identifying a set of different density contours at different evolutionary stages.
-Such identification method is similar to MCC identification based on 
-contour levels/surfaces of surface brightness maps/cubes of molecular line tracers (e.g., CO, CS, NH$_3$),
+We decompose the molecular structures into non-overlapping 
+%mm tiles
+     objects
+by identifying a set of 
+%mm different density contours at different 
+     density contours with varying cutoff densities at multiple
+evolutionary stages.
+Such an identification method is 
+%mm similar 
+     the three-dimensional analog
+to MCC identification based on 
+%mm contour levels/surfaces of surface brightness maps/cubes 
+    intensity levels in surface brightness maps or
+    position-position-velocity cubes
+of molecular line tracers (e.g., CO, CS, NH$_3$),
 since the line luminosity scales with the molecular gas density (modulo optical depth effects).
 
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MCC and we perform a Toomre-$Q$ stability analysis.
+We extract properties such as mass, size, Mach number, velocity
+dispersion, gas surface density, and virial parameter for each MCC and
+we perform a Toomre-$Q$ stability analysis
+%mm
+    on the galaxy. 
 The properties of the MCCs in \flower are compared with observed MCCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
@@
 
-We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\simeq$\,200\,\kms) comparable to
+We find that the MCCs of \flower 
+%mm are highly supersonic, with high 
+   have highly supersonic
+velocity dispersions ($\sigma\simeq$\,200\,\kms) comparable to
 those observed in $z$\ssim2 starburst galaxies.
-The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
+The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun,
+depending on the chosen H$_{2}$ density cut. 
 The $\sim$200\,pc-scale MCCs found with a low density threshold
-correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
+correspond to the arms of the disk of \flower. These break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
 The more massive and bigger MCCs in \flower compared to the Milky Way
 likely result from the higher gas mass fraction, surface density, and velocity dispersion,
-which set the scale for fragmentation.
+which set the scale for fragmentation. \MM{This could be quantified in
+  the discussion by calculating the Jeans scale for the disk conditions.}
 This physical scale is
-consistent with what has been found in higher resolution idealized simulation of isolated galaxies.
+consistent with what has been found in higher resolution idealized
+simulation of isolated galaxies. \MM{Perhaps this could be shown more explicitly?}
 Our simulation here confirms these results at EoR and under
@@
 
-We compare the dynamics of MCCs in \flower to \obs in the context of the Larson's relation.
-The MCCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the
+We compare the dynamics of MCCs in \flower to \obs in the context of
+the Larson's relation. \MM{Which one?}
+The MCCs of \flower are found to have higher $\sigma$ and $\Sigma$
+\MM{compared to Milky Way clouds?}
+systematically regardless of the 
 density threshold $n_{\rm cut}$ adopted in identifying the structures.
- The found scaling relations are insensitive to the various density cuts. 
+The scaling relations found are insensitive to the various density
+cuts.  \MM{This point needs to be made more clearly, probably by
+  defining the colors that correspond to the density cuts in the figures.}
  The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the density threshold and 
- even for the molecular substructures. 
+ even for the molecular substructures.  \MM{You never clearly identify
+   what you mean by ``molecular substructures.''  Do you just mean
+   objects found with high $n_{\rm cut}$?}
  Such a high velocity dispersion likely results from the strong supernova and stellar feedback \flower experienced 
- over the multiple episodes of bursty \SF.
+ over the multiple episodes of bursty \SF.   \MM{Or is it from the
+   deep potential?  Feedback-driven turbulence famously decays quickly.}
 
 Virial analysis indicates that MCC/arms of the main disk of \flower are unbound, but substructures have
-lower virial parameter. Some of these sub-MCCs have Toomre $Q_{\rm eff}$ parameters consistent with being
-gravitationally unstable. This is consistent with the notion that collapsing structures resulting from
+lower virial parameter.
+\MM{where is this explicitly discussed?}
+ Some of these sub-MCCs have Toomre $Q_{\rm eff}$ parameters consistent with being
+gravitationally unstable.  \MM{I don't see this looking at Figure 9.
+  Rather the opposite if anything.} This is consistent with the notion that collapsing structures resulting from
 gravitational instability occur within globally stable structures, which are
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\simeq$\,2 for MCCs in the satellite galaxies, which we interpret as
+We also find $\alpha_{\rm vir}\simeq$\,2 for MCCs in the satellite
+galaxies, \MM{I didn't see any explicit discussion of the MCCs in
+  satellite galaxies.} which we interpret as
 result of the weaker/delayed stellar feedback compared to \flower. 
 In particular, some of the MCCs in the satellites are collapsing structures that have not yet formed stars, as confirmed by their
-higher gas-to-stellar fractions.
+higher gas-to-stellar fractions. \MM{Also not shown so far as I can see.}
 In terms of the scaling relations examined, we do not observe any significant
-temporal variations in the MCC dynamics over the course of 700\,Myr traced in our simulation.
+temporal variations in the MCC dynamics over the course of 700\,Myr
+traced in our simulation.
 
@@
 Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics and is subject to the sub-grid models adopted,
-serve as an useful avenue/tool for examining and making predictions on the morphology and dynamics of
+statistics, and subject to the sub-grid models adopted,
+serve as a useful tool for examining and making predictions on the
+morphology and dynamics of 
 the molecular ISM of the first galaxies.
@@
 %
-AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
+AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
+H2020/740120.
+%mm
+    M-MML acknowledges partial support by the NSF through award
+    AST18-15461, and hospitality from the Insitute for Theoretical
+    Astrophysics at the University of Heidleberg.
 %

### 2019-03-29 WRITEUP/ms.tex
about to run out of battery. first comments on 6.  (I meant 5-6 in last commit msg).

@@
 
-The MCCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+The MCCs of \flower have dynamics largely similar to those observed in
+$z$\ssim2 spatially resolved studies of gas-rich star-forming
+galaxies, in terms of their velocity dispersions, sizes, and gas
+surface densities (\Fig{larsons_single}; see e.g.,
+\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
+and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
+\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
+  high compared to the data sets provided, particularly for their
+  relatively low surface densities (Figs.\ 5, 6).}
 %
@@
 The higher velocity dispersions
-(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCCs also have higher stellar-to-gas mass ratios of $\sim$60).
+(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
+these MCCs can also be understood as they have experienced more recent
+episodes of \SF as \flower is assembling its stellar mass (these MCCs
+also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
+  an enormous stellar to gas mass ratio, suggesting the clouds are
+  completely controlled by the gravitational potential of the stars.
+  A normal molecular cloud would have a ratio of < 0.1!  The
+  implications of this for the apparent virial parameters and velocity
+dispersions need to be considered much more carefully than they have been.}
 %

### 2019-03-30 WRITEUP/ms.tex
finished sec 6 comments.  This completes my comments and revisions for the moment.

@@
   highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
-  back in section 3, the H$_2$ mass of \flower was given as 5\E7
+  back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
   \Msun, precluding the existence of even a single 10$^8$ \Msun
@@
   completely controlled by the gravitational potential of the stars.
-  A normal molecular cloud would have a ratio of < 0.1!  The
+h  A normal molecular cloud would have a ratio of < 0.1!  The
   implications of this for the apparent virial parameters and velocity
@@
 In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
-\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).
-
-The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+\flower has assembled a stellar mass of
+$M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is
+due in part to the stronger stellar feedback \MM{Again, not clear that
+  this is feedback and not potential driven. Can you demonstrate one
+  or the other explicitly?} compared to e.g., MCCs in
+its satellites ($\sigma\simeq$10\,\kms) \MM{This needs to be shown in
+  a Figure, not just asserted}.
+
+The high pressure observed in \flower \MM{Where are pressures shown?
+  You can't just draw them from the virial vs.\ surface density plot
+  because that assumes equilibrium gas clouds, which these are clearly
+  not, given their huge stellar contents.} is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
 %
-For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
+For instance, in local ULIRGs, 
+%mm they are likely form 
+  MCCs are likely formed
+by shock compression and cloud-cloud collisions 
+%mm after large amounts of gas from the pair of progenitor galaxies
+%are funneled toward the central region 
+    that funnel large amounts of gas from the progenitor galaxies
+    towards the central region
+\citep{Tan00a, Wu18a}.
 % Tasker09a
@@
 extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
-The presence of such extra-planar flows may also be the 
-dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCCs in $z$\,\ssim2 galaxies could be smaller in reality.
-%
-The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
-the MCCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is
+The presence of such extra-planar flows may \MM{Do we have any
+  evidence for or against this speculation?} also be the 
+dominant mode for forming the highly supersonic massive MCCs observed
+in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
+\citealt{Swinbank11a}) --- but the observed size scales could also
+result from the resolution limit, while the true physical scales of
+MCCs in $z$\,\ssim2 galaxies could be smaller.
+%mm in reality.
+%
+The constant inter-cloud collisions as gas is being accreted onto the
+main galaxy \MM{This is a highly dissipative process.  Hennebelle \&
+  Klessen found it could only be important in rather small galaxies.
+  Does \flower qualify?} would also render
+the MCCs 
+%mm to be 
+gravitationally unbound (see e.g., \citealt{Dobbs11a}), \MM{Dobbs
+  started with a low-density disk, and got low-density clouds. I don't
+  think that's what you have here.  Do you have any evidence for
+  inter-cloud collisions being important?} which is
 consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
@@
 % mass-size relation
-MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}.
-This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
-%
-That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MCC, and indeed, have sufficient column density to form CO.
+The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
+by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
+can be understood by acknowledging the fact that a H$_2$ molecular
+cloud does not necessary contain CO (e.g., as CO forms deeper in
+molecular clouds), and that our simulation does not have enough
+resolution to directly form CO\footnote{In fact, to form CO and make
+  predictions for CO line emission in the work presented by
+  \citet{Vallini18a}, we model the internal structure of MCC within
+  each cell in our simulation.}.  
+\MM{But column densities have nothing to do with CO, and you are
+  deriving $A_V$ from column densities.  Forming CO doesn't increase
+  column densities; it is just a tracer of dense gas.  Atomic line
+  cooling will be just as efficient as CO in actually cooling the gas
+  down to tens of Kelvin (see Clark \& Glover some years ago).}
+%
+That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag 
+%mm likely manifests from the fact 
+    demonstrates
+that the MCCs in our simulation have lower column densities than the
+star-forming cores observed in the Milky Way, which are
+observationally well-resolved within an MCC, and indeed, have
+sufficient column density to form CO.  \MM{I suppose the question is
+  if we observed the Milky Way at equivalent resolution, would we see
+  such low column densities on average?  This is more or less the game
+that Diderijk Kruijssen has been playing.}
 
@@
 an ``internal'' mass-size relation where $M\propto R^{1.33}$.
-If this holds for MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
-regions of high-mass \SF. That is, the MCCs identified have mass-size relations suggesting they are capable of high-mass \SF.
+If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
+regions of high-mass \SF. That is, the MCCs identified have mass-size
+relations suggesting they are capable of high-mass \SF. \MM{I don't
+  yet understand how this squares with their very high virial
+  parameters and large stellar contents.}
 
 % different evolutionary stages
-In the scaling relations examined, we find similar MCC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}).
-That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
+In the scaling relations examined, we find similar MCC properties in
+relation to those observed in the nearby Universe between the
+accretion phase and the starburst phase of \flower (see
+\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
+  trying to say.  These MCCs don't look similar to nearby objects to
+  me...
+but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
 \DL{some MCCs in SB phase have
 lower $\alpha_{\rm vir}$ and pressure, but 
-is there any significance in that?}
+is there any significance in that?} \MM{I'd say there is great
+significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
+stars, exactly what would be expected during a starburst.}
 
@@
 The largest molecular structure identified is essentially the main
-disk of \flower and breaks down into smaller substructures that are
+disk of \flower \MM{Is this consistent with your assertion of no shear
+  in a footnote above?} and breaks down into smaller substructures that are
 denser as we increase $n_{\rm cut}$ (see e.g.,
@@
 % mass scale
-Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.
-% also higher $P_{\rm int}$,
+Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show
+higher velocity dispersions compared to the disk
+%mm/mid-plane 
+of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
 % which is $\propto\rho\sigma^2$
@@
 However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
-These bigger clouds have been interpreted as a result of their higher gas mass fractions, surface densities, and velocity dispersions,
-since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and
+These bigger clouds have been interpreted as 
+%mm a result of their higher gas mass fractions, [I had trouble
+%interpreting this sentence. Do you agree with the revision?]
+    forming because of the higher gas fractions in these galaxies,
+    which lead to higher
+surface densities, and 
+%mm velocity dispersions
+   ultimately velocity dispersions as collapse occurs.
+Fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and
 Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.
@@
 gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
-$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
-%
-Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
+$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass
+range found in the MCCs identified (see \Fig{dist}).  \MM{I really
+  don't see this: \Fig{dist} has no clouds that massive, and in
+  the higher density case doesn't even get within an order of
+  magnitude of this value.  In both cases, the mode is closer to 5\E{6} \Msun.}
+%
+Similarly massive \MM{8\E{8} \Msun?} molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
 resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 As shown in \Fig{larsons_single},
-the virial parameter of the sub-MCCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
-%
-For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).
+the virial parameter of the sub-MCCs \MM{How can we distinguish
+  sub-MCCs from MCCs in this figure?} is $\alpha_{\rm vir}\gtrsim10$,
+which is considerably lower than their ``parent'' MCCs found in the
+main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).  \MM{However,
+  both are extremely high.}
+%
+For the MCCs in the satellite galaxies, \MM{How can we distinguish
+  these, in turn?} a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
+Differences in their $\alpha_{\rm vir}$ most likely result from the
+weaker stellar feedback in the satellites \MM{Or lower stellar content
+and thus weaker potentials?} as they have experienced fewer episodes
+of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
+$\sim$0.1) \MM{This is what I would expect for molecular gas.  Should
+  you explicitly show stellar-to-gas mass ratios in a figure?}.
 
@@
 As shown in \Fig{larsons_single},
-MCCs in the main disk of \flower have higher pressure than the sub-MCCs.
-The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
+MCCs in the main disk of \flower have higher pressure than the
+sub-MCCs. \MM{Pressures are not shown in this figure, as noted
+  above. If you want to demonstrate pressure, you need to actually
+  examine the gas pressure field.} The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
 %Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
@@
 
-For MCCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
+For MCCs in the satellite galaxies, we find even lower pressures and
+virial parameters, \MM{This needs to be shown explicitly in a figure,
+  as I think I already mentioned above.} which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
 This suggests that MCCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
@@
 central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
-Gas-only $Q_{\rm gas}$ are shown in the left panels and stellar-only $Q_\star$ are shown in the middle panels.
+Gas-only $Q_{\rm gas}$ is shown in the left panels and stellar-only $Q_\star$ is shown in the middle panels.
 Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
@@
 identification of regions above and below $\log{Q}$\eq0.
-Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
+Some MCCs \MM{But these are the exception.} lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
 are likely gravitationally unstable.
 Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
-indicates that stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
+indicates that the stellar component plays an important role in
+governing the stability of the MCCs against $m=0$  perturbations,
+\MM{Well, there are definitely regions dominated by gas.}  highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}
@@
 Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
-thickness of its disk (via $\sigma_z$), some of these MCCs are consistent with  $Q_{\rm eff} > 1$. 
+thickness of its disk (via $\sigma_z$), some of these MCCs are
+consistent with  $Q_{\rm eff} > 1$. 
+\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
+  should probably show it's value explicitly, or else remove that
+  section of the explanation [you don't want to leave the ``rifle on
+  the wall''.]}.
 This demonstrates the importance of accounting for stellar contribution and disk thickness 
@@
 %
-Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by large-scale gravitational potential and differential rotation.
-This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
-%
-Further, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+Second, due to turbulence dissipation on small-scales, such
+(sub-)structures are no longer supported by large-scale gravitational
+potential and differential rotation.  \MM{Not sure how potential can
+  support, and in that footnote above you asserted that shear was
+  unimportant, contradicting this claim.} This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
+%
+Further, mechanisms causing non-axisymmetric perturbations (e.g.,
+arms) to the gravitational potential \MM{Gravitational instability is
+  that mechanism (see e.g.\ Wada et al.'s classic review of the
+  subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
 These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.

### 2019-03-31 io_modules/manipulate_fetch_gal_fields.py
considered mm's suggestions to h2 number density Fig

@@ -342,12 +342,18 @@ def check_hist_h2(data, th_list, ss=None, outdir='./'):
 
     plt.close('all')
     plt.figure()
-    plt.hist(aa[aa>-7], bins=100)
+    toplot = aa[aa>-7]
+    plt.hist(toplot, bins=100) # , normed=True)
+
     for ele in th_list:
+        # plot the ncut positions.
         x = np.log10(ele)
         # plt.plot([x, x], [1, 1.e+7], ls='--', color='k')
+
     plt.yscale('log')
+    # plt.ylabel('Counts')
     plt.xlabel(r"$\log~n_{{\rm H}_2}$ [cm$^{-3}$]")
+    plt.minorticks_on()
     plt.tight_layout()
     if ss is None:
         plt.savefig(outdir + 'hist_test.png')

### 2019-03-31 WRITEUP/ms.tex
extra bracket removed
minor edits

@@
 %mm rearranged sentence
-We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
+We study the properties of molecular cloud complexes (MCCs) in a cosmological zoom-in simulation of a
 prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
 %
-We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
-%
-In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
+We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
+%
+In \flower, MCC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
 Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
 %
-We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
+We identify gravitationally unstable MCCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
 %mm (gas+stars), 
@@
 and by using a more observationally accessible $\alpha_{\rm vir}$ analysis.
-We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
+We find that MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
 %mm
@@
 %mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
-   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
+   cloud complexes (MCCs) 
 that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
@@
 In \Sec{eqn}, we describe the method used to identify
-%mm molecular gas complexes 
 MCCs,
@@
     (however, note the alternative interpretation involving gravitational collapse by 
-    \citealt{Ballesteros-Paredes11}).
-
-%mm In general, the virial theorem for a gas distribution of gas can be written as
-     The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee1992}
+    \citealt{Ballesteros-Paredes11a}).
+
+The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
 \begin{equation}\label{eqn:virial_th_general}
@@
 
-Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e.\ ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
+Motivated by Larson's linewidth-size relation \citep{Larson81a} and the work by \citet{Heyer09a}, we assume equilibrium (i.e.,\ ${\ddot{\mathcal{I}}}=0$), define the cloud surface density as
 $\Sigma$\eq$M/\pi R^2$, and rewrite the previous equation as 
@@
 Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
-%mm obtain
 maintain 
@@
 On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
-%mm  the criterion of the Toomre
-$Q_{\rm crit}$, 
-%mm, unless it is dynamically hot to ``compensate''. 
-   moreso if the stars have low velocity dispersion.
+$Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
 As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
@@
 covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
-zooms in on a target halo of mass $\sim 10^11 \Msun$. The Lagrangian
+zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian
 region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
@@
     event; and {\it (c)} a relatively quiescent post-starburst
-    phase. \MM{The figure says ``Accreting'', so I have edited
-      elsewhere to match.  You could also remove the quote marks from Quiescent.}
+    phase. 
 \label{fig:SFH}}
@@
 
-In the clump-finding process, we employ a set of different density
+In the clump-finding process (in position-position-position space; PPP), we employ a set of different density
 thresholds defined based on the molecular hydrogen density of \flower
@@
 We note that this process is 
-%mm in essence similar
 the three-dimensional analog
 to identifying molecular structures based on the noise levels 
-%mm of surface density maps
-     in position-position-velocity maps that
+     in position-position-velocity (PPV) maps that
 observers obtain with telescopes, using molecular line tracers such as
@@
 %We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
-% Many concerning the correspondence between  ... , dating back to the work by \citep{Adler92a}.
 Existing studies find a good correspondence in the dynamical
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
-\caption{Probability distribution function of the H$_2$ number density
-  in \flower during the accreting phase shown in \Fig{SFH}{\em
-    (b)}. \MM{PDFs should be normalized to unity by dividing by the
-    area under the curve (total number of samples).  A label on the
-    y-axis would also be useful, and perhaps minor ticks on the x-axis.}
+\caption{Number distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
+    (b)}. 
 \label{fig:h2density}}
@@
 are found based on morphological analysis\footnote{For $n_{\rm
-    H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$
+    H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$
   density field is significantly larger than zero. This implies that
@@
 Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively.
-Let us start from analyzing the accretion phase.
+Let us start from analyzing the accreting phase.
 
@@
 % Starburst 
-Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accretion phase.
+Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accreting phase.
 \DL{Is this significant enough to say something physical?
@@
 \label{fig:MR}}
-}
+%mm}
 \end{figure*}
@@
 %
-In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
+In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
 \flower has assembled a stellar mass of
@@
 relation to those observed in the nearby Universe between the
-accretion phase and the starburst phase of \flower (see
+accreting phase and the starburst phase of \flower (see
 \Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is

### 2019-04-01 plotSS.py
fix bug in counting MCCs w/ Mcl > 1.e8 Msun

@@ -84,8 +84,8 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     # fig = plt.figure(figsize=(13, 6))
     # ax = fig.subplots(2, 3)
 
-    fig, ax = plt.subplots(nrows=2, ncols=3, figsize=(13, 3.5))
-    fig.subplots_adjust(left=0.12, wspace=0.15, bottom=0.1, top=0.95, hspace=0.0)
+    fig, ax = plt.subplots(nrows=2, ncols=3, figsize=(14, 3.5))
+    fig.subplots_adjust(left=0.12, wspace=0.18, bottom=0.1, top=0.95, hspace=0.0)
 
     # # separate allmasses into two color scheme
     # med11 = allmass11.median()
@@ -119,12 +119,12 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     # size
     allsizes11 = get_sizes_all_clouds(ss11)
     ax[0, 1].hist(allsizes11)
-    ax[0, 1].set_xlim([45, 300])
+    ax[0, 1].set_xlim([45, 260])
     ax[0, 1].set_xticklabels([])
     ax[0, 1].set_title(r'R [pc]')
     allsizes12 = get_sizes_all_clouds(ss12)
     ax[1, 1].hist(allsizes12)
-    ax[1, 1].set_xlim([45, 300])
+    ax[1, 1].set_xlim([45, 260])
 #    fig.text(0.5, 0.33, r'R [pc]', ha='center', fontsize=20)
 
     minorLocator = AutoMinorLocator(5)
@@ -191,76 +191,86 @@ if __name__ == '__main__':
     # plot_dis_allSS()
 
     # # of MCs w/ mass > 1e8 Msun (for paper)
-    # _to, _ = load_pickleTOplot(16, 28, fname="0.32_10_fields.p")
+    # _, _to, _ = load_pickleTOplot(16, 28, fname="0.32_10_fields.p")
     # count = 0
     # for i in _to.iterkeys():
-    #     if _to[i]['cloud mass'] > 1.e8:
-    #         count += 1
+    #     for ii in range(len(_to[i]['cloud mass'])):
+    #         if _to[i]['cloud mass'][ii] > 1.e8:
+    #             count += 1
     # print count
     # import pdb; pdb.set_trace()
 
[…]

### 2019-04-01 WRITEUP/ms.tex
addressed AF's comments on Mcl > 1.e8 Msun

@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
-\caption{Number distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
+\caption{Distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
     (b)}. 
@@
 
-To visually
-%mm appreciate
-    display 
+To visually display 
 the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
@@
 parameter space of cloud complexes of 
-%mm typical size $R\gtrsim 60$\,pc [revised assuming spherical MCCs
-%per Sect 4.2]
 radius $R\gtrsim 40$\,pc,
@@
 
-\subsection{Molecular Cloud 
-%mm
-    Complex
-Properties}
+\subsection{Molecular Cloud Complex Properties}
 
@@
 
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
+a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
+we therefore consider MCCs identified with the second highest density threshold  ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
 We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
@@
 We note that the distributions vary for different evolutionary stages of \flower. 
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
-%
-We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
-all the evolutionary stages considered in this work, for each  $n_{\rm
-  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
-  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
-  is the case for each ncut.} \MM{I am afraid I am also confused by
-  this, for two reasons.  First, if I understand the Figure, the
-  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
+%
+\MM{The highest $n_{\rm cut}$ shows no such large MCCs ($>$10$^8$\,\Msun) at any time.  Second,
   back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
@@
 \DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
-like total gas mass. AP will add disclaimer in Section 3. Will double check 
-Mcl for all ncut and address AF's comment.}
+like total gas mass. AP will add disclaimer in Section 3.}
   Such massive clouds correspond to the molecular disk of the
@@
 and bottom panels, as fewer MCCs are identified at higher $n_{\rm
-  cut}$. \MM{Put labels on the y-axis (maybe just $N$ or some such). Tick marks should point inwards
-  rather than outwards.  I'd suggest putting the $n_{\rm cut}$ labels
-  on the left panels following the style of the previous figure (and
-  drop the brackets around the unit there). The $R$ axis could
-  reasonably be pulled in to 250 pc, providing a bit more dynamic
-  range at the low end.}
+  cut}$. 
 \label{fig:dist}}

### 2019-04-02 brute.py
python

@@ -1,3 +1,5 @@
+#!/mnt/home/daisyleung/Downloads/yt-conda/bin/python
+
 """
 
 Get to the buttom of the buggy yt clump finder...
@@ -26,6 +28,9 @@ last mod: 23 July 2018
 
 
 """
+
+import sys
+assert 'yt' in sys.path[1]     # instead of using the anaconda version
 
 import yt
 import os
@@ -56,7 +61,7 @@ largeNum = 1.e+42   # to plot only one contour in a hacky way
 
 
 istart = 16
-iend = 17
+iend = 29
 
 
 isnap = str(istart)

### 2019-04-02 plotSS.py
minor

@@ -99,10 +99,12 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     ax[0, 0].hist(np.log10(allmass11))
 #     ax[0, 0].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1)
     ax[0, 0].set_title(r'$\log M_{\rm cl}$ [M$_{\odot}]$')
+    ax[0, 0].set_ylabel(r'$N$')
     ax[0, 0].set_xlim([5.7, 8.5])
     ax[0, 0].set_xticklabels([])
     allmass12 = get_masses_all_clouds(ss12)
     ax[1, 0].hist(np.log10(allmass12))
+    ax[0, 0].set_ylabel(r'$N$')
     ax[1, 0].set_xlim([5.7, 8.5])
 #     ax[0, 1].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2)
 #    fig.text(0.51, 0.62, r'$\log $ M$_{\rm cl}$ [M$_{\odot}]$', ha='center', fontsize=20)

### 2019-04-02 plotsingleSS.py

@@ -78,13 +78,13 @@ def plotting_procedure(snapshot_num):
 if __name__ == '__main__':
 
     import matplotlib
-    matplotlib.use('agg')
+    # matplotlib.use('agg')
 
     from plot_modules.plot_cloud_prop import setup_plot
     cm = setup_plot()
 
-    for isnap in range(16, 29):
-        plotting_procedure(isnap)
+    # for isnap in range(16, 17):
+    #     plotting_procedure(isnap)
 
     # min MC mass for highest n_cut (for paper)
     # for isnap in [16, 27]:
@@ -113,4 +113,4 @@ if __name__ == '__main__':
                               cbarLabelSize=16,
                               outdir='./',
                               legendFontSize=13,
-                              saveFig=True)
+                              saveFig=False)

### 2019-04-02 clump_modules/clump_wrapper.py
fix major bug that stored stellar velx, y, z as gas; calc alpha_vir_total and plot

@@ -193,9 +193,9 @@ def get_phyprop_of_leaf(subleaf, density, H2density, Pressure, P_nt, metallicity
                     'Pressure': None,
                     'P_nt': None,
                     'metallicity': None,
-                    'velx': None,
-                    'vely': None,
-                    'velz': None}
+                    'velx_gas': None,
+                    'vely_gas': None,
+                    'velz_gas': None}
 
     if starPartDict is not None:
         for kkk in starPartDict.iterkeys():
@@ -208,13 +208,19 @@ def get_phyprop_of_leaf(subleaf, density, H2density, Pressure, P_nt, metallicity
 
     # print(subleaf.quantities.total_mass())
     # print(subleaf.quantities.center_of_mass())
-    
+
     for fff in _leaf_fields.iterkeys():
         if not fff in starPartDict.iterkeys():
-            _leaf_fields[fff] = eval(fff)[ii, jj, kk]
+            if fff == 'velx_gas':
+                _leaf_fields[fff]  = eval('velx')[ii, jj, kk]
+            elif fff == 'vely_gas':
+                _leaf_fields[fff]  = eval('vely')[ii, jj, kk]
+            elif fff == 'velz_gas':
+                _leaf_fields[fff]  = eval('velz')[ii, jj, kk]
+            else:
+                _leaf_fields[fff] = eval(fff)[ii, jj, kk]
         else:
             _leaf_fields[fff] = starPartDict[fff][ii, jj, kk]
-        
     #_h2_subleaf = subleaf.data['h2density']
     #h2_subleaf = _leaf_fields['H2density']
     #assert round(_h2_subleaf[0]) == round(h2_subleaf[0])

### 2019-04-02 clump_modules/leafprop.py

@@ -53,9 +53,9 @@ class Cloud(object):
         self.Pressure = leaf_0_dict['Pressure']    # K cm-3
         self.P_nt = leaf_0_dict['P_nt']            # K cm-3
         self.metallicity = leaf_0_dict['metallicity']   # old solar units
-        self.velx = leaf_0_dict['velx']            # km/s
-        self.vely = leaf_0_dict['vely']
-        self.velz = leaf_0_dict['velz']
+        self.velx = leaf_0_dict['velx_gas']            # km/s
+        self.vely = leaf_0_dict['vely_gas']
+        self.velz = leaf_0_dict['velz_gas']
         # plt.hist(self.velx)
         # plt.show()
         # import pdb; pdb.set_trace()
@@ -64,7 +64,10 @@ class Cloud(object):
         self.epoch = leaf_0_dict['epochMyr']       # Myr (age of universe when SF)
         self.mstar_young = leaf_0_dict['young10']       # Myr (age of universe when SF)
         self.mstar_old = leaf_0_dict['old100']       # Myr (age of universe when SF)
-        
+        self.velx_star = leaf_0_dict['velx']
+        self.vely_star = leaf_0_dict['vely']
+        self.velz_star = leaf_0_dict['velz']
+
         self.vol_pc3()
         self.vol_cc()
         self.mass_Msun()
@@ -90,24 +93,52 @@ class Cloud(object):
         self.mass_star_Msun()
         self.young_SFR()
         self.old_SFR()
+        self.alphaVir_total()
 
 
-    # --- star particles --- 
+    def alphaVir_total(self):
+        """
+
+        Cloud's alpha virial, Bertoldi & McKee 1992.
+
+                   5 * sigma ^ 2 * R
+          alpha =  ------------------
+                        G * M
+
+        """
+
+        # mass-weighted stellar velo disp
+        _velx_star = (self.velx_star - np.mean(self.velx_star)) * self.km2cm
+        _vely_star = (self.vely_star - np.mean(self.vely_star)) * self.km2cm
+        _velz_star = (self.velz_star - np.mean(self.velz_star)) * self.km2cm
+
+        self.sigmaSq_star = 1. / 3 * \
+            (self.mstar * ((_velx_star)**2 + (_vely_star) **
+                             2 + (_velz_star)**2)).sum() / self.mstar.sum()
+
[…]

### 2019-04-02 plot_modules/plot_cloud_prop.py

@@ -84,6 +84,7 @@ def unpack_xy(ss):
         _SFR_young = []
         _SFR_old = []
         _alpha = []
+        _alpha_tot = []   # include stellar
         _mSD = []
         _sizepc = []
         _R2pc2 = []
@@ -108,6 +109,7 @@ def unpack_xy(ss):
             _SFR_young.append(ss[ks][kkk].young_SFR_MsunPyr)
             _SFR_old.append(ss[ks][kkk].old_SFR_MsunPyr)
             _alpha.append(ss[ks][kkk].alpha)
+            _alpha_tot.append(ss[ks][kkk].alpha_total)
             _mSD.append(ss[ks][kkk].massSD)
             _sizepc.append(ss[ks][kkk].R_pc * 2.0)
             _R2pc2.append((ss[ks][kkk].R_pc * 2.0) ** 2.0)
@@ -131,6 +133,7 @@ def unpack_xy(ss):
         to_plot[ks]['jeans mass'] = _Mj
         to_plot[ks]['mass over jeans mass'] = _MMj
         to_plot[ks]['alpha vir'] = _alpha
+        to_plot[ks]['alpha vir total'] = _alpha_tot
         to_plot[ks]['gas sd'] = _mSD
         to_plot[ks]['sfr sd'] = _SFRSD
         to_plot[ks]['size pc'] = _sizepc
@@ -1142,9 +1145,15 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
         # ks = numerical value of ncut or sfr
         _x = to_plot[ks]["cloud mass"]
         _y = to_plot[ks]["alpha vir"]
+        _y2 = to_plot[ks]["alpha vir total"]
         h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
                      marker=marker,
                      markeredgecolor='gray',
+                     markeredgewidth=0.5)
+        # alpha_virial total
+        ax.plot(_x, _y2, ls=ls, markersize=markersize,
+                     marker='o',
+                     markeredgecolor='black',
                      markeredgewidth=0.5)
 
     # shrink
@@ -1312,17 +1321,12 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
 
     fig, axes = plt.subplots(nrows=3, ncols=2, sharex=False,
                              sharey=False,   # do NOT set to TRUE
-                             figsize=(15,17))
[…]

### 2019-04-02 WRITEUP/ms.tex

@@
 (right). Star symbols are color-coded by the density thresholds
-$n_{\rm cut}$.  \MM{Give the color coding somewhere.} 
+$n_{\rm cut}$, as illustrated by the colorbar.
 Data points in the $\alpha_{\rm vir}$-mass figure are taken from
@@
 reported by \citet{Kauffmann10b}. Star symbols are color-coded by
-increasing $n_{\rm cut}$. \MM{which direction? White high or blue
-  high?} Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
+increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
+Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
 Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
@@
   section of the explanation [you don't want to leave the ``rifle on
-  the wall''.]}.
+  the wall''.]}. \DL{ this is based on Eqn 12.}
 This demonstrates the importance of accounting for stellar contribution and disk thickness 

### 2019-04-02 plot_modules/plot_cloud_prop.py
subplot_adjust

@@ -977,7 +977,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
         if not legendFontSize:
             legendFontSize = 10
         ax.legend(loc="upper center", ncol=4, fontsize=legendFontSize,
-                  bbox_to_anchor=(1.1, 1.28), markerscale=3)
+                  bbox_to_anchor=(1.1, 1.2), markerscale=3)    # 1.28
         # ax.legend(handles=legend_h, loc="upper center", ncol=2,
         #           fontsize=legendFontSize,
         #           bbox_to_anchor=(0.5, 0.9))
@@ -1158,12 +1158,12 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     # shrink
     box = ax.get_position()
-    ax.set_position([box.x0, box.y0, box.width, box.height * 0.87])
+    ax.set_position([box.x0, box.y0, box.width, box.height * 0.85])    # 0.82
     if showLegend:
         if not legendFontSize:
             legendFontSize = 10
         ax.legend(loc="upper center", ncol=5, fontsize=legendFontSize,
-                  bbox_to_anchor=(1.05, 1.1),
+                  bbox_to_anchor=(1.08, 1.12),   # 1.17
                       markerscale=3)
         # ax.legend(handles=legend_h, loc="upper center", ncol=2,
         #           fontsize=legendFontSize,
@@ -1175,7 +1175,7 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     ax.set_yscale("log")
     ax.set_ylabel(r"$\alpha_{\rm vir}$")
-    ax.set_ylim(0.02, 2.e2)
+    ax.set_ylim(0.02, 3.e2)
 
     ax.tick_params(axis='both', which='both')   # direction='in'
     fig, ax = set_minorticks(fig, ax)
@@ -1319,9 +1319,15 @@ def plot_stuff_3by2(to_plotLeft, to_plotRight,
     else:
         sfr_val = sorted([ii for ii in sfr.itervalues()])
 
-    fig, axes = plt.subplots(nrows=3, ncols=2, sharex=False,
-                             sharey=False,   # do NOT set to TRUE
-                             figsize=(15,10))
+    if saveFig:
+        figsize= (22, 20)
+        dpi = 120
+    else:
+        figsize = (150/10., 300/10.)
[…]

### 2019-04-02 plotsingleSS.py
fontsize

@@ -83,16 +83,16 @@ if __name__ == '__main__':
     from plot_modules.plot_cloud_prop import setup_plot
     cm = setup_plot()
 
-    # for isnap in range(16, 17):
+    # for isnap in range(16, 29):
     #     plotting_procedure(isnap)
 
-    # min MC mass for highest n_cut (for paper)
-    # for isnap in [16, 27]:
-    #     _, _, _ = load_pickleTOplot(isnap, pattern='*18.96*10*p')
+    min MC mass for highest n_cut (for paper)
+    for isnap in [16, 27]:
+        _, _, _ = load_pickleTOplot(isnap, pattern='*18.96*10*p')
 
-    # # plot Larson and local points only (for talk introduction slide)
-    # _, to_plot, _ = load_pickleTOplot(16)
-    # plot_stuff("size pc", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir='./')
+    # plot Larson and local points only (for talk introduction slide)
+    _, to_plot, _ = load_pickleTOplot(16)
+    plot_stuff("size pc", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir='./')
 
 
     # for paper, 3x2 panel for just ss16 and ss27
@@ -110,7 +110,7 @@ if __name__ == '__main__':
                               tag='ss16-ss27',
 #                              cmap=cm,
                               sfrlabel=False,
-                              cbarLabelSize=16,
+                              cbarLabelSize=20,
                               outdir='./',
-                              legendFontSize=13,
-                              saveFig=False)
+                              legendFontSize=16,
+                              saveFig=True)

### 2019-04-02 WRITEUP/ms.tex
update includ. stellar

@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_ss16-27.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss27.pdf}
 \caption{
@@
 \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
-(see Fig 4 of \citealt{Kauffmann17b}).   \MM{For consistency with
-  Figure 1, label as ``Accreting'' rather than ``Accretion'' phase. I
+(see Fig 4 of \citealt{Kauffmann17b}).   \MM{I
   am inclined to leave the pressure confinement curves off of the

### 2019-04-02 plotSS.py
minor plot setting

@@ -302,7 +302,7 @@ if __name__ == '__main__':
                               tag='allss',
 #                              cmap=cm,
                               sfrlabel=bubu,
-                              cbarLabelSize=16,
+                              cbarLabelSize=20,
                               outdir='./',
-                              legendFontSize=13,
+                              legendFontSize=16,
                               saveFig=True)

### 2019-04-02 plot_modules/plot_cloud_prop.py

@@ -964,7 +964,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     ax.set_yscale("log")
     ax.set_ylabel(r"$\sigma$ [km s$^{-1}$]")
-    ax.set_ylim([0.5, 2.e2])
+    ax.set_ylim([0.5, 3.e2])
 
     ax.tick_params(axis='both', which='both')   # direction='in'
 

### 2019-04-02 plotsingleSS.py

@@ -86,13 +86,13 @@ if __name__ == '__main__':
     # for isnap in range(16, 29):
     #     plotting_procedure(isnap)
 
-    min MC mass for highest n_cut (for paper)
-    for isnap in [16, 27]:
-        _, _, _ = load_pickleTOplot(isnap, pattern='*18.96*10*p')
+    # # min MC mass for highest n_cut (for paper)
+    # for isnap in [16, 27]:
+    #     _, _, _ = load_pickleTOplot(isnap, pattern='*18.96*10*p')
 
-    # plot Larson and local points only (for talk introduction slide)
-    _, to_plot, _ = load_pickleTOplot(16)
-    plot_stuff("size pc", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir='./')
+    # # plot Larson and local points only (for talk introduction slide)
+    # _, to_plot, _ = load_pickleTOplot(16)
+    # plot_stuff("size pc", "sigma kms", leglabel="ncut: ", to_plot=to_plot, outdir='./')
 
 
     # for paper, 3x2 panel for just ss16 and ss27

### 2019-04-03 WRITEUP/ms.tex

@@
      MCC  \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
+     \DL{This is just a statement to say there are variations among local GMCs.
+Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs.
+}
 properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
@@
 %
-Such a criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
+Such a criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.\DL{perhaps to be removed...}} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
 
@@
 \citep{Romeo92a}.
-\AF{$R$ is not the same as the MCC radius in the prev.\ Section} \MM{replaced $R$ with $\altomega$, and $\sigma$ with $\sigma_{\rm disk}$.}
 In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively. 
@@
      three-dimensional tree that can be processed using $k$-dimensional tree algorithms.
-     \MM{Too persnickety?} 
 It then identifies the contours of a variable field (here, the density
@@
 
-In \Fig{h2density}, we show the probability distribution of H$_2$
+In \Fig{h2density}, we show the distribution of H$_2$
 number density $n_{\rm H2}$ for \flower~ during its accreting phase,
@@
 \DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
- what one expects for purely H2 regions.}
+ what one expects for purely H2 regions. No clumping factor.}
 
@@
 %
-\MM{The highest $n_{\rm cut}$ shows no such large MCCs ($>$10$^8$\,\Msun) at any time.  Second,
-  back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
-  \Msun, precluding the existence of even a single 10$^8$ \Msun
-  cloud.} 
-\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
-like total gas mass. AP will add disclaimer in Section 3.}
-  Such massive clouds correspond to the molecular disk of the
+The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
+clouds identified at low density cut (see top left panel of \Fig{dist})  
+correspond to the molecular disk of the
 galaxy, which is identified as a single component for low $n_{\rm

### 2019-04-03 plotsingleSS.py
plot Mach from velo vs. pressure; SB is ss22 not ss27

@@ -45,6 +45,8 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff('alpha vir', 'sigmaSq over size', leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("alpha vir", "SFR young", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("cloud mass", "mass over jeans mass",
                leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("cloud mass", "jeans mass", leglabel="ncut: ",
@@ -53,7 +55,11 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("Mach", "Mach pressure", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("Mach", "SFR young", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("Mach", "SFR old", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("stellar to gas mass", "sigma kms", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
@@ -61,8 +67,15 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("size pc", "cloud mass", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("size pc", "cloud mass", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("cloud mass", "Mach", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("cloud mass", "Mach pressure", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
     plot_stuff_3dim("tff Myr", "size pc", "cloud mass",
[…]

### 2019-04-03 WRITEUP/ms.tex

@@
 %
-\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
+\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
 %
@@
 The \SF history\footnote{Note that here the SFR is calculated based on
-  the stellar mass formed in the last 10 Myr within 3.5 kpc from the
+  the stellar mass formed in the last 4 Myr within 3.5 kpc from the
   galaxy center of mass. The SFR plotted in Figure 2 of
@@
 \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
-  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
-  high-density plot, it looks like you have quite a number of
-  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}
+  $f_{gas}$ here..Also, what is the total number of MCCs?}
 
@@
 In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}).
-Instead, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+On the other hand, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
 
@@
 % Starburst 
-Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ (closer to loci with lower external pressure) compared to the accreting phase.
+Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ compared to the accreting phase.
 \DL{Is this significant enough to say something physical?
@@
 cuts.  \MM{This point needs to be made more clearly, probably by
-  defining the colors that correspond to the density cuts in the figures.}
+  defining the colors that correspond to the density cuts in the figures.} \DL{They are color-coded by ncut in Fig 5 and 7.}
  The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the density threshold and 
@@
 Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics, and subject to the sub-grid models adopted,
+statistics and are subject to the sub-grid models adopted,
 serve as a useful tool for examining and making predictions on the

### 2019-04-03 plot_modules/plot_cloud_prop.py
mach from pressure, pdf to png to fix missing greek

@@ -24,7 +24,7 @@ def setup_plot():
                                 , 'lines.linewidth': 2       # points
                                 , 'axes.linewidth': 1       # points
                                 , 'axes.prop_cycle': cycler('color', 'bgrcmyk')
-                                , 'text.usetex': True    # Use LaTeX to layout text
+                                , 'text.usetex': True
                                 , 'font.family': "serif"  # Use serifed fonts
                                 , 'xtick.major.size': 13     # length, points
                                 , 'xtick.major.width': 1     # points
@@ -36,7 +36,7 @@ def setup_plot():
                                 , 'xtick.labelsize': 14
                                 , 'ytick.labelsize': 14
                                 , 'ytick.minor.width': 1     # points
-                                , 'font.serif': ("Times", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
+                                , 'font.serif': ("times", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
                                 })
     cm = setup_cmap()
     return cm
@@ -79,6 +79,7 @@ def unpack_xy(ss):
         _MMj = []
         _m = []
         _mach = []
+        _mach_pressure = []
         _mstar = []
         _mstar2mgas = []
         _SFR_young = []
@@ -103,6 +104,7 @@ def unpack_xy(ss):
             MMj = ss[ks][kkk].mass_Msun / ss[ks][kkk].M_jeans
             _MMj.append(MMj)
             _mach.append(ss[ks][kkk].Mach)
+            _mach_pressure.append(np.mean(ss[ks][kkk].Mach_vec))
             _m.append(ss[ks][kkk].mass_Msun)
             _mstar.append(ss[ks][kkk].mstar_Msun_tot)
             _mstar2mgas.append(ss[ks][kkk].s2gR)
@@ -126,6 +128,7 @@ def unpack_xy(ss):
         to_plot[ks] = {}
         to_plot[ks]['cloud mass'] = _m
[…]

### 2019-04-04 plotSS.py
plot Mach diagnostics

@@ -34,30 +34,45 @@ def plotting_procedure(minss, maxss, pattern):
     fname = pattern + '_10_fields.p'
     ss, to_plot, leafdir_out = load_pickleTOplot(minss, maxss, fname)
 
+    plot_stuff("alpha vir", "SFR young", leglabel="sfr: ",
+               to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("cloud mass", "mass over jeans mass", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("cloud mass", "jeans mass",  leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("cloud mass", "alpha vir", leglabel="ncut: ",
+    plot_stuff("cloud mass", "alpha vir", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
+    plot_stuff("size pc", "sigma kms", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("Mach", "SFR young", leglabel="ncut: ",
+    plot_stuff("Mach", "Mach pressure", leglabel="sfr: ",
+                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
+    plot_stuff("Mach", "SFR young", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("stellar to gas mass", "sigma kms", leglabel="ncut: ",
+    plot_stuff("Mach", "SFR old", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-#     plot_stuff("gas sd", "sfr sd", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("gas sd", "sigma kms", leglabel="ncut: ",
+    plot_stuff("stellar to gas mass", "sigma kms", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",
[…]

### 2019-04-04 plotSS.py
equalize binsize

@@ -110,15 +110,16 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     fig.text(0.05, 0.95, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1, rotation=90)
     fig.text(0.05, 0.43, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2, rotation=90)
 
-    allmass11 = get_masses_all_clouds(ss11)
-    ax[0, 0].hist(np.log10(allmass11))
+    binwidth = 0.1
+    allmass11 = np.log10(get_masses_all_clouds(ss11))
+    ax[0, 0].hist(allmass11, bins=np.arange(min(allmass11), max(allmass11) +binwidth, binwidth))
 #     ax[0, 0].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1)
     ax[0, 0].set_title(r'$\log M_{\rm cl}$ [M$_{\odot}]$')
     ax[0, 0].set_ylabel(r'$N$')
     ax[0, 0].set_xlim([5.7, 8.5])
     ax[0, 0].set_xticklabels([])
-    allmass12 = get_masses_all_clouds(ss12)
-    ax[1, 0].hist(np.log10(allmass12))
+    allmass12 = np.log10(get_masses_all_clouds(ss12))
+    ax[1, 0].hist(allmass12, bins=np.arange(min(allmass12), max(allmass12) +binwidth, binwidth))
     ax[0, 0].set_ylabel(r'$N$')
     ax[1, 0].set_xlim([5.7, 8.5])
 #     ax[0, 1].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2)
@@ -134,40 +135,46 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     ax[0, 1].minorticks_on()
 
     # size
+    binwidth = 10
     allsizes11 = get_sizes_all_clouds(ss11)
-    ax[0, 1].hist(allsizes11)
-    ax[0, 1].set_xlim([45, 260])
+    ax[0, 1].hist(allsizes11, bins=np.arange(min(allsizes11), max(allsizes11) +binwidth, binwidth))
+    ax[0, 1].set_xlim([0, 260])
     ax[0, 1].set_xticklabels([])
     ax[0, 1].set_title(r'R [pc]')
[…]

### 2019-04-04 plotSS.py
added ylabel N

@@ -120,7 +120,7 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     ax[0, 0].set_xticklabels([])
     allmass12 = np.log10(get_masses_all_clouds(ss12))
     ax[1, 0].hist(allmass12, bins=np.arange(min(allmass12), max(allmass12) +binwidth, binwidth))
-    ax[0, 0].set_ylabel(r'$N$')
+    ax[1, 0].set_ylabel(r'$N$')
     ax[1, 0].set_xlim([5.7, 8.5])
 #     ax[0, 1].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2)
 #    fig.text(0.51, 0.62, r'$\log $ M$_{\rm cl}$ [M$_{\odot}]$', ha='center', fontsize=20)

### 2019-04-09 plot_modules/plot_cloud_prop.py
plot 1x2 side-by-side alpha-vir-M_cl

@@ -427,7 +427,7 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
                 label=r'Heyer \& Brunt 2004 $\sigma \propto R^{0.56}$')
         legend_h.append(h)
 
-        # Bolatto+08: sigma = 0.44 * R^0.6 km/s
+        # Bolatto+08: sigma = 0.44 * R^0.6 km/s; eqn 9
         yB08 = 0.44 * x**0.60
         h, = ax.plot(x, yB08, linestyle=':', color='b', linewidth=1.5,
                 label=r'Bolatto+08 $\sigma \propto R^{0.60}$')
@@ -1269,6 +1269,111 @@ def plot_sigmaSqOR_SD(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     ax.tick_params(axis='both', which='both')   # direction='in'
     fig, ax = set_minorticks(fig, ax)
+
+    return fig, ax
+
+
+def plot_alpha_vir_2ss(to_plot1, to_plot2,
+                       ls='', markersize=10, marker='*',
+                       tag='',
+                       t1='Pre-starburst Phase',
+                       t2='Starburst Phase',
+                       cbarLabelSize=16,
+                       outdir='./',
+                       legendFontSize=16,
+                       saveFig=False):
+
+    """
+    Plot alpha_vir for two snapshot side by side
+
+    created so I can plot it for Pre-SB phase and SB phase.
+
+    """
+    import matplotlib as mpl
+    from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+    sfr = None
+    sfrlabel = None
+
+    plt.close('all')
+    cm = plt.get_cmap()
+    NUM_COLORS = max(len(to_plot1), len(to_plot2))
+
+    # get ncut calues
+    ncut = []
+    if len(to_plot1) > len(to_plot2):
+        _to_plot = to_plot1
+    else:
+        _to_plot = to_plot2
+    for kkk in _to_plot.iterkeys():
+        ncut.append(float(kkk))
+    ncut = sorted(ncut)
+
+    # if saveFig:
+    #     figsize= (22, 20)
+    #     dpi = 120
+    # else:
+    #     figsize = (150/10., 300/10.)
+    #     dpi = 100           # otherwise mpl won't let me have a figure bigger than my screen size
+
+
+    fig = plt.figure(figsize=(19, 6))
+    ax = plt.subplot(121)
[…]

### 2019-04-09 plotsingleSS.py

@@ -40,50 +40,56 @@ def plotting_procedure(snapshot_num):
 
     ss, to_plot, leafdir_out = load_pickleTOplot(snapshot_num)
 
-    plot_stuff("gas sd per ff", "sfr sd", leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)    # SK
-    plot_stuff('gas sd cgs', 'sigmaSq over size', leglabel="ncut: ",
+    plot_stuff("stellar to gas mass", "cloud mass", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff('alpha vir', 'sigmaSq over size', leglabel="ncut: ",
+    plot_stuff("stellar to gas mass", "alpha vir", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("alpha vir", "SFR young", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("cloud mass", "mass over jeans mass",
-               leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("cloud mass", "jeans mass", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("cloud mass", "alpha vir", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("Mach", "Mach pressure", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("Mach", "SFR young", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("Mach", "SFR old", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("stellar to gas mass", "sigma kms", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("gas sd", "sigma kms", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
[…]

### 2019-04-09 WRITEUP/ms.tex
Updates from Overleaf

@@
 %
-Such a criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.\DL{perhaps to be removed...}} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
+Such a criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
+
+In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
+\begin{equation}
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
+					       {M_{\rm cl} + M_{\star} }\,.
+\label{eqn:alpha_tot}
+\end{equation}
 
@@
 indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. 
-On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$.
+On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
+but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
@@
   cut}$. The mass of the MCCs identified ranges between $M_{\rm
-  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
+  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
 \z$\sim$2 galaxies in rest-frame UV and optical light
-\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
-  $f_{gas}$ here..Also, what is the total number of MCCs?}
+\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges ($M_{\star}/M_{\rm cl}$) between $<$\,0.1 to 70 over all the
+MCCs identified across all evolutionary stages of \flower.
 
@@
   (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
-%mm
  over all times analyzed here.
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss27.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
 \caption{
@@
 MCCs (star symbols) identified in the two most extreme evolutionary
-stages of \flower\ ---accreting phase (left) and starburst phase
+stages of \flower\ --- accreting phase (left) and starburst phase
 (right). Star symbols are color-coded by the density thresholds
 $n_{\rm cut}$, as illustrated by the colorbar.
+Blue circular symbols shown in the $\alpha_{\rm vir}$-mass plot shows the total virial parameters, including
+the stellar contribution (see Equation~\ref{eqn:alpha_tot}).
+Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a, 
+% black dot = extragalactic GMCs in quiescent environments
+Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are 
+from \citet{Larson81a, Heyer04a, Bolatto08a}.
 Data points in the $\alpha_{\rm vir}$-mass figure are taken from
 \citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
-(see Fig 4 of \citealt{Kauffmann17b}).   \MM{I
-  am inclined to leave the pressure confinement curves off of the
-  final plot.}
+(see Fig 4 of \citealt{Kauffmann17b}).   
+The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
+gas in equilibrium, see Equation~\ref{eqn:v0}.
 \label{fig:larsons_single}}
@@
 \includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages.
-Left panels show MCCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs identified using a high $n_{\rm cut}$\eq19\,\cc.
+\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
+Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
+identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
 \label{fig:alpha16-28}}
@@
 \AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
-We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), and identify a set of MCCs in each of them.
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right), respectively.
-Let us start from analyzing the accreting phase.
-
-MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$ pc).
-These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs.
-here and in caption; in addition it would good to give the properties of this galaxy}.
-Sizes are somewhat dependent on the choice of $n_{\rm cut}$.
-As such density threshold is increased, some of the MCCs within the main disk break into multiple sub-MCCs.
-In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}).
-On the other hand, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), 
+and identify a set of MCCs in each of them. \DL{note that delay in cloud properties and SFR.}
+Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+
+Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
+and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
+such as the nearby gas-rich galaxy M64 and 
+% Kennicutt, 1996IAUS..171...11K
+% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
+% with the inner gas disk the remnant of the
+% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
+the z\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
+\citep{Rosolowsky05a, Swinbank11a}.
+Since the sizes are somewhat dependent on the choice of $n_{\rm cut}$, as such, 
+some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
+In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
+On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
 
@@
 % Starburst 
-Some MCCs in the starburst phase have lower velocity dispersion, $\alpha_{\rm vir}$, and $\sigma^2/R$ compared to the accreting phase.
-\DL{Is this significant enough to say something physical?
-If so, not immediately clear to me what cause the differences.}
+In the starburst phase, some MCCs have lower velocity dispersion, virial parameter, 
+and $\sigma^2/R$ compared to the accreting phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
 % PVE
@@
   think that's what you have here.  Do you have any evidence for
-  inter-cloud collisions being important?} which is
-consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
+  inter-cloud collisions being important?}
+\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
+which is consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
 
@@
   down to tens of Kelvin (see Clark \& Glover some years ago).}
+\DL{It doesn't increase the column density, but these obs. results are based on CO, which traces deeper 
+regions than we could here because MCCs are not entirely molecular, this may become clearer after 
+expanding what $n_{\rm cut}$ means in Sec 3. {\bf AP?}}
 %
@@
 that Diderijk Kruijssen has been playing.}
+\DL{Don't think this is a resolution effect, but our MCC is not entirely H2 {\bf AP?}}
 
@@
 % different evolutionary stages
-In the scaling relations examined, we find similar MCC properties in
-relation to those observed in the nearby Universe between the
-accreting phase and the starburst phase of \flower (see
-\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
-  trying to say.  These MCCs don't look similar to nearby objects to
-  me...
-but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.
+In the scaling relations examined, we do not find any quantitative major differences
+in the MCC properties with respect to those observed in the nearby Universe 
+between the accreting phase and the starburst phase of \flower (see
+\Fig{larsons_single}), which are separated by $\simeq$300\,Myr. 
+However, between the two phases, {\bf blah...}
 \DL{some MCCs in SB phase have
@@
 of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
-$\sim$0.1) \MM{This is what I would expect for molecular gas.  Should
-  you explicitly show stellar-to-gas mass ratios in a figure?}.
-
-% pext
-As shown in \Fig{larsons_single},
+$\sim$0.1) \MM{Should you explicitly show stellar-to-gas mass ratios in a figure?}.
+
+% Pressure
 MCCs in the main disk of \flower have higher pressure than the
-sub-MCCs. \MM{Pressures are not shown in this figure, as noted
-  above. If you want to demonstrate pressure, you need to actually
-  examine the gas pressure field.} The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
+sub-MCCs. \MM{examine the gas pressure field.} The lower virial parameter and 
+pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
 %Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
@@
 Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
-thickness of its disk (via $\sigma_z$), some of these MCCs are
+thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are
 consistent with  $Q_{\rm eff} > 1$. 
-\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
-  should probably show it's value explicitly, or else remove that
-  section of the explanation [you don't want to leave the ``rifle on
-  the wall''.]}. \DL{ this is based on Eqn 12.}
 This demonstrates the importance of accounting for stellar contribution and disk thickness 

### 2019-04-10 plotSS.py
plot stellar-gas mass ratio

@@ -34,6 +34,11 @@ def plotting_procedure(minss, maxss, pattern):
     fname = pattern + '_10_fields.p'
     ss, to_plot, leafdir_out = load_pickleTOplot(minss, maxss, fname)
 
+    plot_stuff("stellar to gas mass", "cloud mass", leglabel="sfr: ",
+               to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
+    plot_stuff("stellar to gas mass", "alpha vir", leglabel="sfr: ",
+               to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
+
     plot_stuff("alpha vir", "SFR young", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("cloud mass", "mass over jeans mass", leglabel="sfr: ",
@@ -74,12 +79,12 @@ def plotting_procedure(minss, maxss, pattern):
                     leglabel="sfr: ", to_plot=to_plot,
                     outdir=leafdir_out, sfrlabel=True)
 
-    from plot_modules.plot_cloud_prop import get_masses_all_clouds, massFuncUnbinnedCDF, massFuncPDF, massFuncDifferential, CMF
-    allmass = get_masses_all_clouds(ss)
-    massFuncUnbinnedCDF(allmass, outdir=leafdir_out)
-    massFuncPDF(allmass, outdir=leafdir_out)
-    massFuncDifferential(allmass, outdir=leafdir_out)
-    CMF(allmass, outdir=leafdir_out)
+    # from plot_modules.plot_cloud_prop import get_masses_all_clouds, massFuncUnbinnedCDF, massFuncPDF, massFuncDifferential, CMF
+    # allmass = get_masses_all_clouds(ss)
+    # massFuncUnbinnedCDF(allmass, outdir=leafdir_out)
+    # massFuncPDF(allmass, outdir=leafdir_out)
+    # massFuncDifferential(allmass, outdir=leafdir_out)
+    # CMF(allmass, outdir=leafdir_out)
 
 
 def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
@@ -213,7 +218,6 @@ if __name__ == '__main__':
 
     # for paper
     plot_dis_allSS()
-    import sys; sys.exit()
 
     # # of MCs w/ mass > 1e8 Msun (for paper)
     # _, _to, _ = load_pickleTOplot(16, 28, fname="0.32_10_fields.p")

### 2019-04-10 WRITEUP/ms.tex
address comments up to Sec 6

@@
 %
-Even in the local Universe, where detailed \obs can be made, variations in 
-%mm cloud
-     MCC  \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
-     \DL{This is just a statement to say there are variations among local GMCs.
+Even in the local Universe, where detailed \obs can be made, variations in molecular cloud 
+%       \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
+%     \DL{This is just a statement to say there are variations among local GMCs.
 Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs.
@@
 properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of MCCs in early galaxies, and how do they differ from those found in local \galpop?}
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
+molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
 %
@@
 \alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
-					       {M_{\rm cl} + M_{\star} }\,.
+					       {M_{\rm cl} + M_{\star} }\,,
 \label{eqn:alpha_tot}
 \end{equation}
+where $M_\star$ is the stellar mass within the MCC volume.
 
@@
 Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
-%mm
-%   \MM{confirm:} 
+\DL{AP: please elaborate non-thermal pressure here..}
 Photoionization from local sources is neglected in this simulation
@@
 %mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
-   30--80 \Msun\,yr\pmOne. 
+   30\,--\,80\,\Msun\,yr\pmOne. 
 %mm \MM{What is its gas fraction?  I ask because its molecular gas
@@
 
-Given \flower's SF stochastic nature, in this work we mostly focus on
-the analysis of two of its most extreme evolutionary stages (see
-\Sec{singless}). The two phases correspond to (a) intense accretion
-(b) starburst (\Fig{SFH}). We are interesting in determining whether
+Given the stochastic nature of \flower in its star formation history, we mostly focus on
+two of its most extreme evolutionary stages in this work (see \Sec{singless}).
+The two phases correspond to (a) an intensely accreting phase and
+(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
 MCC properties are sensitive to these different dynamical
-conditions. For completeness, for the other evolutionary stages traced
-in the simulation we only show scaling relations (see 
-%mm [Figures must be numbered and placed in order cited.  Better to
-%cite to the section and leave the figure in its proper place.] \Fig{alpha16-28}).
-     Sect.~\ref{sec:ncut}).
+conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced
+in the simulation (see \Sec{ncut}).
 
@@
 
-\subsection{Molecular Cloud Complex Properties}
+\subsection{Molecular Cloud Complex Properties} \label{sec:distribution}
 
@@
 where the sum is done for the cells composing each MCC.
-%
+
 The local sound speed of all identified molecular complexes is much
@@
   from the pressure field 
-%mm
     \MM{The turbulent pressure field has not been
@@
     mentioning its presence and behavior to mention it here}, 
-indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. 
+    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
+indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
+at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
 On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
@@
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
+We also compute the Mach number from turbulent and thermal pressure to determine the importance of 
+differential rotation in the derived velocity dispersion: 
+\begin{equation}
+\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}\,,
+\end{equation}
+where $P_{\rm NT}$ is non-thermal pressure and $P$ is thermal pressure.
 
@@
 \begin{equation}
-f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
-\end{equation}
-where $M_\star$ is the stellar mass within the MCC volume.
+f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)}.
+\end{equation}
 %
@@
 galaxy, which is identified as a single component for low $n_{\rm
-  cut}$. The mass of the MCCs identified ranges between $M_{\rm
+  cut}$. Overall, the mass of all MCCs identified ranges between $M_{\rm
   cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
 \z$\sim$2 galaxies in rest-frame UV and optical light
-\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges ($M_{\star}/M_{\rm cl}$) between $<$\,0.1 to 70 over all the
-MCCs identified across all evolutionary stages of \flower.
+\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
+MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
+The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) as they correspond to a large part of \flower, and thus, 
+include a large number of stellar mass already ensembled in \flower. 
+\label{fig:stellarRatio16}}
+\end{figure}
 
@@
 \centering
+\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
+\caption{$\alpha_{\rm vir}$-mass relation for pre-starburst (left) and starburst phase. 
+Definition of the symbol shown are the same as in \Fig{larsons_single}.
+Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
+\label{fig:alpha21-22}}
+\end{figure*}
+
+\begin{figure*}
+\centering
 \includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
@@
 \subsection{Single Evolutionary Stage}  \label{sec:singless}
-\AF{Description of the results is very chaotic. You mix evol. phases, properties, ncut, that is physical and numerical issues. Please reorder and make it more logical.}
-We first focus on the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}), 
-and identify a set of MCCs in each of them. \DL{note that delay in cloud properties and SFR.}
+
+We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
+and identify a set of MCCs in each of them. 
 Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
@@
 % original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
-the z\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
-\citep{Rosolowsky05a, Swinbank11a}.
-Since the sizes are somewhat dependent on the choice of $n_{\rm cut}$, as such, 
-some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
-In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
-On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
-
-%Now discuss sigma - R relation; poor statistcis. But how many MCCs do we have?
-
-% Starburst 
-In the starburst phase, some MCCs have lower velocity dispersion, virial parameter, 
-and $\sigma^2/R$ compared to the accreting phase. \DL{Is this significant enough to say something physical? If so, not immediately clear to me what cause the differences.}
+the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
+\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.
+
+% middle
+While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
+mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
+for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
+MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
+\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
+the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
+
 % PVE
-We also compare the MCCs identified in our simulations to those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panels of \Fig{larsons_single}).
-Dashed lines in the figure show the loci along which the given external pressures are needed for MCCs to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
+In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
+Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
+linewidths for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
 Heyer+09).
-The MCCs in the satellite galaxies are found to follow the locus of
-$\log{(P/\textrm{K cm}^{-3})}$\eq6, \MM{This is not shown in the
-  figure.  If you want to claim it, it needs to be shown somewhere.} which
-is consistent with that found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a}.
 
@@
 % column density) as fundamental properties of molecular cloud structure.
-Larson's third relation relates MCCs structures on small and large
+Larson's third relation relates MCC structures on small and large
 scales via two physical properties: mass and size \citep{Larson81a,
@@
   suggested among others by \citet{Ballesteros11}.}
- since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$).
+since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
+which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
+% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
 By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
 \begin{equation}
-A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-\end{equation}
-then, assuming spherical symmetry, the mass of an MCC can be expressed as a function of $A_v$ and its size $R$
+A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+\end{equation}
+Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
 \begin{equation}\label{eqn:constantcolumndensity}
@@
 \end{equation}
-where we have taken $\mu = 2.5$ as the mean molecular weight.
-
-We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-%
-In the same plot, we also show loci of constant surface densities,
-which are parameterized through the visual extinction $A_V$. \MM{Why
-  do you go through $A_v$ rather than just using surface densities
-  directly?} As shown
-in \Fig{MR}, the MCCs identified in \flower lie above this relation,
-along the locus of $A_v \simeq 8.9$ clouds observed by
-\citet{Lombardi10a} in the MW. \MM{Does the variation in surface
-  density seen in Figure 6 correspond to the variation in $A_V$ seen
+where we adopt $\mu = 2.5$ as the mean molecular weight.
+
+We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
+Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+MCCs of \flower spans a 
+ lie along the locus of $A_V \simeq 8.9$ clouds observed by
+\citet{Lombardi10a} in the MW. 
+\MM{Does the variation in surface
+  density seen in Figure 7 correspond to the variation in $A_V$ seen
   here?}
@@
 
+% Starburst 
+In the starburst phase, MCCs have velocity dispersion, sizes,
+and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
+a wider range in $\sigma^2/R$ and gas surface density. 
+Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
+As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
+of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range. which is as expected.
+% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
+% i.e., we haven’t reached those scales where true collapse is happening. 
+% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
+
 \subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
-% single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs.
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-%
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
-%
-In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%
-This lack of variation is reassuring, i.e.
-the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$ on the scales studied in the present work.
-Our results are therefore robust to the various density cuts of choice.
+
+We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the 
+choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, 
+the results presented in \Sec{singless} dependent on the choice of density thresholds.
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
+and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
+For instance, the cluster of points found at the lowest density threshold, 
+occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
+are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
+typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.} ). 
+These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
+In this way, we identify a population of denser molecular structures (see \Fig{MCC}). 
+On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+%% 
+%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
+%%
+%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%%
+This lack of variation is reassuring, i.e., our inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
+nearby and \z$\sim$2 galaxies in the context of linewidth-size relations are not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
+
+%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold 
+%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
+%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size  
+%at increasing $n_{\rm cut}$.
 
@@
 
-%
-%\begin{comment}
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
-%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
-%\caption{
-%Larson's (linewidth-size) relation of \flower in
-%accretion phase (top) and
-%starburst phase (bottom) compared to
-%those observed in nearby and the \z$\sim$2 star-forming galaxy.
-%% Red lines show the relation obtained from \citet{}.
-%Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
-%\label{fig:larsons_single}}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
-%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
-%\caption{
-%Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel)
-%and the starburst phase (bottom panel) compared to the
-%Milky Way (other symbols).
-%Literature data are compiled from \citealt{Kauffmann17b} and references therein.
-%Star symbols are color-coded by $n_{\rm cut}$.
-%Star symbols lying close to $\alpha_{\rm vir}\simeq2$ correspond to MCCs in the satellite galaxies.
-%\label{fig:alpha16}}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
-%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
-%\caption{
-%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCCs identified in our simulation (star symbols)
-%in the accretion phase (top panel) and the starburst phase (bottom panel)
-%compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
-%The V-shaped dashed lines show the loci along which the given external pressures
-%are needed for MCCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
-%Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
-%Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
-%correspond to MCCs in the satellite galaxies.
-%\label{fig:alpha27}}
-%\end{figure*}
-%\end{comment}
-
-%
-%\begin{comment}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
-%\caption{
-%Maps of the total gas surface density (top left),
-%velocity dispersion (top right),
-%epicyclic frequency (bottom left),
-%and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
-%Modest smoothing has been applied to the maps.
-%A divergent colormap is used for the Toomre $Q$ map to facilitate
-%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-%Crosses correspond to positions of MCCs identified using the lowest $n_{\rm cut}$. % using 0.32
-%Positions of sub-MCCs are not shown (but see top row of \Fig{Qeff} for an example).
-%\label{fig:Q}}
-%\addtocounter{figure}{-1}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
-%\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
-%\addtocounter{figure}{-1}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
-%\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
-%\caption{
-%Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
-%\label{fig:Qstar}}
-%% \addtocounter{figure}{-1}
-%\end{figure*}
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
-%\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
-%\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
-%\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
-%\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
-%\caption{
-%Effective two-component Toomre $Q_{\rm eff}$ (top row)
-%and gas surface density (middle) maps projected onto the $xy$-plane.
-%Positions of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
-%and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
-%Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
-%Cross markers indicate positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
-%Modest smoothing has been applied to the maps.
-%A divergent colormap is used for the Toomre $Q$ map to facilitate
-%identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
-%Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$
-%are likely gravitationally unstable.
-%\label{fig:Qeff}}
-%% \addtocounter{figure}{-1}
-%\end{figure*}
-%%\clearpage
-%
-%\end{comment}
+% Also mentioned in \Sec{sfh}, we will frame the remainder of this work focusing on the properties of MCCs identified in the two most extreme 
+% evolutionary stages of \flower.
 
@@
 
+\DL{
+1) Note becasuse some MCCs have high stellar-to-gas mass ratios, we plot both gas-only virial parameter 
+and the total virial parameter (eqn xx) on the alphavir-mass plots in \Fig{}. The former is used in \obs since 
+the quantities are measured using gas tracers. On the other hand, because our MCs are identified with gas density and 
+some have high stellar-to-gas mass ratio, influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
+% 
+2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
+can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
+% 
+3) add alphavir versus stellar-to-gas mass ratio, 
+which shows in the pre-SB phase, we see overall lower alphavir. 
+We interpret the alphavir versus stellar-to-gas mass ratio plot as 
+1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
+The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
+directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
+This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
+}
+
 \subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
 
+Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
+linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
+mostly the main disk of \flower.......{\DL blah}.
 The MCCs of \flower have dynamics largely similar to those observed in
@@
 in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
-\citealt{Swinbank11a}) --- but the observed size scales could also
-result from the resolution limit, while the true physical scales of
-MCCs in $z$\,\ssim2 galaxies could be smaller.
-%mm in reality.
-%
+\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
+high due to the resolution limit.
 The constant inter-cloud collisions as gas is being accreted onto the
-main galaxy \MM{This is a highly dissipative process.  Hennebelle \&
-  Klessen found it could only be important in rather small galaxies.
-  Does \flower qualify?} would also render
-the MCCs 
-%mm to be 
-gravitationally unbound (see e.g., \citealt{Dobbs11a}), \MM{Dobbs
-  started with a low-density disk, and got low-density clouds. I don't
-  think that's what you have here.  Do you have any evidence for
-  inter-cloud collisions being important?}
-\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
-which is consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
+main galaxy 
+%\MM{This is a highly dissipative process.  Hennebelle \&
+%  Klessen found it could only be important in rather small galaxies.
+%  Does \flower qualify?} 
+would also render the MCCs gravitationally unbound (see e.g., \citealt{Dobbs11a}), 
+%\MM{Dobbs
+%  started with a low-density disk, and got low-density clouds. I don't
+%  think that's what you have here.  Do you have any evidence for
+%  inter-cloud collisions being important?}
+%\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
+which would be consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
 

### 2019-04-10 plot_modules/plot_cloud_prop.py
plot side by side ss21 and ss22 alpha_vir-stellar-to-gas ratio

@@ -153,6 +153,7 @@ def unpack_xy(ss):
 def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
                leglabel='', tag='',
                to_plot=None, save=True, outdir='./',
+               showLegend=True,
                sfrlabel=False):
     """
 
@@ -711,7 +712,7 @@ def plot_stuff(xstr, ystr, ls='', markersize=10, marker='*',
 #       ax.set_xlim(-2.2, 5)
         ax.minorticks_on()
 
-    if leglabel is not '':
+    if leglabel is not '' and showLegend:
         if xstr == "size pc" and ystr == "sigma kms":
                 # Shrink current axis by 20%
             box = ax.get_position()
@@ -986,147 +987,148 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
 
 def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
-                       markersize=10, marker='*',
+                       markersize=10, marker='*', xaxis='mass',
                        showLegend=False, legendFontSize=None):
 
-    # Kauffmann+17 Figure 4
-    # read data from old Kauffmann paper
-    CloudData = pd.read_table(litpath + './Kauffmann17/filter_alpha_vp-paper.dat',
-                              header=0,
-                              delim_whitespace=True)
+    if xaxis == 'mass':
+        # Kauffmann+17 Figure 4
+        # read data from old Kauffmann paper
+        CloudData = pd.read_table(litpath + './Kauffmann17/filter_alpha_vp-paper.dat',
+                                  header=0,
+                                  delim_whitespace=True)
 
-    # CMZ data: GCMS dendrograms
-    DataTable = pd.DataFrame()
-    LinewidthSizeFiles = glob.glob(
-        litpath + './Kauffmann17/Clumps_*.pickle')
-    for File in LinewidthSizeFiles:
-        DataTable = DataTable.append(pd.read_pickle(File))
+        # CMZ data: GCMS dendrograms
+        DataTable = pd.DataFrame()
+        LinewidthSizeFiles = glob.glob(
+            litpath + './Kauffmann17/Clumps_*.pickle')
[…]

### 2019-04-10 plotsingleSS.py

@@ -44,52 +44,53 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("stellar to gas mass", "alpha vir", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("stellar to gas mass", "Mach pressure", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("gas sd per ff", "sfr sd", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)    # SK
+    plot_stuff('gas sd cgs', 'sigmaSq over size', leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff('alpha vir', 'sigmaSq over size', leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("alpha vir", "SFR young", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("cloud mass", "mass over jeans mass",
+               leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("cloud mass", "jeans mass", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("cloud mass", "alpha vir", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("Mach", "Mach pressure", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("Mach", "SFR young", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("Mach", "SFR old", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("stellar to gas mass", "sigma kms", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("gas sd", "sigma kms", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
+    plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out)
[…]

### 2019-04-10 plot_modules/plot_cloud_prop.py
plot 4x1 mach - stellar-to-gas ratio

@@ -856,9 +856,6 @@ def load_Heiderman10():
     return Heinerman_mass, Heinerman_SigmaGas, Heinerman_SFR, Heinerman_SigmaSFR
 
 
-
-
-
 def set_minorticks(fig, ax):
     from matplotlib.ticker import AutoMinorLocator, MultipleLocator
 
@@ -1181,6 +1178,7 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
         ax.set_xlim(0.02, 1.0e8)    # to accomodate Kauffmann+17 data
     elif xaxis == 'massRatio':
         ax.set_xlabel(r"$M_\star / M_{\rm cl}$")
+        ax.set_xlim(0.07, 2e2)
 
     ax.set_yscale("log")
     ax.set_ylabel(r"$\alpha_{\rm vir}$")
@@ -1278,6 +1276,181 @@ def plot_sigmaSqOR_SD(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
 
     ax.tick_params(axis='both', which='both')   # direction='in'
     fig, ax = set_minorticks(fig, ax)
+
+    return fig, ax
+
+
+def plot_Mach_massRatio(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
+                       markersize=10, marker='*'):
+
+    psuedo_keys = []
+    if not sfrlabel:
+        for kkk in to_plot.iterkeys():
+            psuedo_keys.append(float(kkk))
+        psuedo_keys = sorted(psuedo_keys)
+        psuedo_keys = map(str, psuedo_keys)
+    else:
+        sfr_ = []
+        for kkk in to_plot.iterkeys():
+            sfr_.append(sfr[kkk])
+            psuedo_keys.append(kkk)
+        _idx = np.argsort(sfr_)
+        psuedo_keys = [psuedo_keys[i] for i in _idx]
+    for ks in psuedo_keys:
+        # ks = numerical value of ncut or sfr
+        _x = to_plot[ks]['stellar to gas mass']
+        _y = to_plot[ks]["Mach pressure"]
+        h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
+                     marker=marker,
+                     markeredgecolor='gray',
+                     markeredgewidth=0.5)
+
+    ax.set_xscale("log")
+    ax.set_xlabel(r"$M_\star/M_{\rm cl}$")
[…]

### 2019-04-10 plotsingleSS.py

@@ -120,7 +120,7 @@ if __name__ == '__main__':
     plt.close('all')
 
     from plotsingleSS import load_pickleTOplot
-    from plot_modules.plot_cloud_prop import plot_alpha_vir_2ss
+    # from plot_modules.plot_cloud_prop import plot_alpha_vir_2ss, plot_Mach_massRatio_4ss
     ss1, to_plot1, leafdir_out1 = load_pickleTOplot(21)
     ss2, to_plot2, leafdir_out2 = load_pickleTOplot(22)
     fig, ax = plot_alpha_vir_2ss(to_plot1, to_plot2, ls='',
@@ -148,6 +148,23 @@ if __name__ == '__main__':
                               showcbar=False,
                               legendFontSize=16,
                               saveFig=True)
+
+    # Mach - stellar-to-gas mass ratio
+    ss1, to_plot1, leafdir_out1 = load_pickleTOplot(21)
+    ss2, to_plot2, leafdir_out2 = load_pickleTOplot(22)   # SB
+    ss3, to_plot3, leafdir_out3 = load_pickleTOplot(23)
+    ss4, to_plot4, leafdir_out4 = load_pickleTOplot(27)
+    fig, ax = plot_Mach_massRatio_4ss(to_plot1, to_plot2, to_plot3, to_plot4,
+                                      ls='', markersize=10, marker='*',
+                                      tag='',
+                                      t1='Pre-starburst Phase',
+                                      t2='Starburst Phase',
+                                      t3='Post-starburst Phase',
+                                      t4='Quiescent Phase',
+                                      cbarLabelSize=20,
+                                      outdir='./',
+                                      legendFontSize=16,
+                                      saveFig=True)
 
     # for paper, 3x2 panel for just ss16 and ss22!!!!
     from plot_modules.plot_cloud_prop import plot_stuff_3by2

### 2019-04-10 plot_modules/plot_cloud_prop.py
cleanup

@@ -1045,52 +1045,11 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
                  markerfacecolor=(1, 0.7, 0.7),
                  zorder=10, label='')
 
-        # ax.plot(DataTable[DataTable['Target'] == 'SgrD']['mass'],
-        #          DataTable[DataTable['Target'] == 'SgrD']['alpha'],
-        #          '+',
-        #          markersize=13.,
-        #          markeredgecolor='blue', markeredgewidth=6.,
-        #          markerfacecolor=(1, 0.7, 0.7),
-        #          zorder=10, label='')
-
-        # ax.plot(DataTable[DataTable['Target'] == 'SgrD']['mass'],
-        #          DataTable[DataTable['Target'] == 'SgrD']['alpha'],
-        #          '+',
-        #          markersize=13.,
-        #          markeredgecolor='white', markeredgewidth=2.,
-        #          markerfacecolor=(1, 0.7, 0.7),
-        #          zorder=10, label='Sgr D outside CMZ')
-
         ax.annotate(s='"clumps"',
                     xy=[5.0E3, 0.7],
                     color='blue',
                     ha='left',
                     fontsize=15)
-
-        # # estimate for dense cores
-        # ax.fill_between([1.0E2, 1.0E3],
-        #                 1.2 * 0.6**2. * 0.1 /
-        #                 (np.array([1.0E2, 1.0E3]) / 1.0E3),
-        #                 1.2 * 2.2**2. * 0.1 /
-        #                 (np.array([1.0E2, 1.0E3]) / 1.0E3),
-        #                 facecolor='blue', edgecolor='none', alpha=0.3,
-        #                 zorder=3)
-        # plt.plot([1.0E2, 1.0E3],
-        #          1.2 * 0.6**2. * 0.1 / (np.array([1.0E2, 1.0E3]) / 1.0E3),
-        #          color='blue',
-        #          linewidth=3.)
-        # annotate(s=r'$\sigma_{\mathdefault{v}} = \mathdefault{0.6 \, km \, s^{-1}}$',
-        #          xy=[300., 1. / 1.5 * 1.2 * 0.6**2. * 0.1 / (300. / 1.0E3)],
-        #          color='blue',
-        #          ha='right')
-        # plt.plot([1.0E2, 1.0E3],
[…]

### 2019-04-10 WRITEUP/ms.tex

@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
-\caption{$\alpha_{\rm vir}$-mass relation for pre-starburst (left) and starburst phase. 
-Definition of the symbol shown are the same as in \Fig{larsons_single}.
-Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
-\label{fig:alpha21-22}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
-Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
-identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-\label{fig:alpha16-28}}
-\end{figure*}
-
-\subsection{Single Evolutionary Stage}  \label{sec:singless}
-
-We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
-and identify a set of MCCs in each of them. 
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
-
-Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
-and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
-such as the nearby gas-rich galaxy M64 and 
-% Kennicutt, 1996IAUS..171...11K
-% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
-% with the inner gas disk the remnant of the
-% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
-the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
-\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.
-
-% middle
-While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
-mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
-for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
-MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
-\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
-This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
-the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
-
-% PVE
-Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
-In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
-Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
-linewidths for a given set of surface densities (see \Sec{PVE}).
-% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
-Heyer+09).
-
-% cloud structures at large and small scale
-% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
-% column density) as fundamental properties of molecular cloud structure.
-Larson's third relation relates MCC structures on small and large
-scales via two physical properties: mass and size \citep{Larson81a,
-  McKee07a}. This is also known as the constant column density
-relation,
-\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
-  $\Sigma$.  Effectively, Larson's mass-size relation is a single
-  point on that relationship, at the constant $\Sigma$ value.  This
-  suggests that the mass-size relation is just an artifact of the
-  narrow range of column densities observed with $^{12}CO$, as
-  suggested among others by \citet{Ballesteros11}.}
-since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
-which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
-% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
-By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
-\begin{equation}
-A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-\end{equation}
-Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
-\begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
-\end{equation}
-where we adopt $\mu = 2.5$ as the mean molecular weight.
-
-We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
-Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-MCCs of \flower spans a 
- lie along the locus of $A_V \simeq 8.9$ clouds observed by
-\citet{Lombardi10a} in the MW. 
-\MM{Does the variation in surface
-  density seen in Figure 7 correspond to the variation in $A_V$ seen
-  here?}
-%
-%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
-5 therein]{Behrens18a}
-
 \begin{figure*}[htbp]
@@
 
+\begin{figure*}
+% \centering
+\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
+% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
+\caption{
+% Top: 
+Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
+% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
+Definition of the symbol shown are the same as in \Fig{larsons_single}.
+Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
+Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
+\label{fig:alpha21-22}}
+\end{figure*}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
+\caption{
+Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
+% ss20,21,22,27
+The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
+light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
+\label{fig:Mach_stellarRatio}}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
+\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
+Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
+identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
+\label{fig:alpha16-28}}
+\end{figure*}
+
+\subsection{Single Evolutionary Stage}  \label{sec:singless}
+
+We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
+and identify a set of MCCs in each of them. 
+Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+
+Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
+and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
+such as the nearby gas-rich galaxy M64 and 
+% Kennicutt, 1996IAUS..171...11K
+% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
+% with the inner gas disk the remnant of the
+% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
+the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
+\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.
+
+% middle
+While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
+mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
+for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
+MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
+\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
+the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
+
+% PVE
+Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
+In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
+Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
+linewidths for a given set of surface densities (see \Sec{PVE}).
+% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
+Heyer+09).
+
+% cloud structures at large and small scale
+% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
+% column density) as fundamental properties of molecular cloud structure.
+Larson's third relation relates MCC structures on small and large
+scales via two physical properties: mass and size \citep{Larson81a,
+  McKee07a}. This is also known as the constant column density
+relation,
+\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+  point on that relationship, at the constant $\Sigma$ value.  This
+  suggests that the mass-size relation is just an artifact of the
+  narrow range of column densities observed with $^{12}CO$, as
+  suggested among others by \citet{Ballesteros11}.}
+since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
+which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
+% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
+By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
+\begin{equation}
+A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+\end{equation}
+Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
+\begin{equation}\label{eqn:constantcolumndensity}
+M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+\end{equation}
+where we adopt $\mu = 2.5$ as the mean molecular weight.
+
+We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
+Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+MCCs of \flower spans a 
+ lie along the locus of $A_V \simeq 8.9$ clouds observed by
+\citet{Lombardi10a} in the MW. 
+\MM{Does the variation in surface
+  density seen in Figure 7 correspond to the variation in $A_V$ seen
+  here?}
+%
+%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+5 therein]{Behrens18a}
+
 % Starburst 
@@
 As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
-of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range. which is as expected.
+of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
+%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
+%These trends are as expected in the MCC properties prior to and during a starburst. 
 % None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
@@
 % This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
+As \SF proceed, stellar feedback inject kinetic energy in the form of turbulence. As shown in 
+\Fig{Mach_stellarRatio}, the Mach number of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
+(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
+increases from the pre-starburst phase through the post-starburst phase.
 
@@
 \DL{
-1) Note becasuse some MCCs have high stellar-to-gas mass ratios, we plot both gas-only virial parameter 
-and the total virial parameter (eqn xx) on the alphavir-mass plots in \Fig{}. The former is used in \obs since 
-the quantities are measured using gas tracers. On the other hand, because our MCs are identified with gas density and 
-some have high stellar-to-gas mass ratio, influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
+1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
+influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
 % 
@@
 can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
-% 
-3) add alphavir versus stellar-to-gas mass ratio, 
-which shows in the pre-SB phase, we see overall lower alphavir. 
-We interpret the alphavir versus stellar-to-gas mass ratio plot as 
+and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
+% 
+3) overall lower alphavir in the pre-SB phase in \Fig{alpha21-22}. 
 1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
@@
 linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
-mostly the main disk of \flower.......{\DL blah}.
-The MCCs of \flower have dynamics largely similar to those observed in
+the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
 $z$\ssim2 spatially resolved studies of gas-rich star-forming
@@
 and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
-\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
-  high compared to the data sets provided, particularly for their
-  relatively low surface densities (Figs.\ 5, 6).}
-%
-% velocity dispersion, larsons
-%
 Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
@@
 these MCCs can also be understood as they have experienced more recent
-episodes of \SF as \flower is assembling its stellar mass (these MCCs
-also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
-  an enormous stellar to gas mass ratio, suggesting the clouds are
-  completely controlled by the gravitational potential of the stars.
-h  A normal molecular cloud would have a ratio of < 0.1!  The
-  implications of this for the apparent virial parameters and velocity
-dispersions need to be considered much more carefully than they have been.}
+episodes of \SF as \flower is assembling its stellar mass --- these MCCs have higher stellar-to-gas mass ratios of $M_\star/M_{\rm gas}\simeq0.1 - 1$ (\Fig{stellarRatio16}) and high turbulent pressure as shown by the high $\mathcal{M}$ in \Fig{Mach_stellarRatio}.
 %
@@
   this is feedback and not potential driven. Can you demonstrate one
-  or the other explicitly?} compared to e.g., MCCs in
-its satellites ($\sigma\simeq$10\,\kms) \MM{This needs to be shown in
-  a Figure, not just asserted}.
+  or the other explicitly?}
 

### 2019-04-10 WRITEUP/ms.tex
minor edits to 6.1

@@
 \mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}\,,
+\label{eqn:MPress}
 \end{equation}
@@
 % This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
-As \SF proceed, stellar feedback inject kinetic energy in the form of turbulence. As shown in 
-\Fig{Mach_stellarRatio}, the Mach number of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
+As shown in \Fig{Mach_stellarRatio}, the Mach number (see Equation~\ref{eqn:MPress}) 
+of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
 (i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
 increases from the pre-starburst phase through the post-starburst phase. 
+This results as stellar feedback injects kinetic energy into the surrounding ISM in the form of turbulence as \SF proceed.
+In the quiescent phase, high Mach number are seen in mostly MCCs identified with the lowest density threshold. These 
+correspond to satellites MCCs in the outskirts of \flower.
 
@@
 \flower has assembled a stellar mass of
-$M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is
-due in part to the stronger stellar feedback \MM{Again, not clear that
-  this is feedback and not potential driven. Can you demonstrate one
-  or the other explicitly?}
-
-The high pressure observed in \flower \MM{Where are pressures shown?
-  You can't just draw them from the virial vs.\ surface density plot
-  because that assumes equilibrium gas clouds, which these are clearly
-  not, given their huge stellar contents.} is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+$M_\star$\eq7.5\E{9}\,\Msun.
+
+The high pressure observed in \flower (see \Fig{Mach_stellarRatio}, see also \citealt{Pallottini17a})
+is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
   in a footnote above?} and breaks down into smaller substructures that are
-denser as we increase $n_{\rm cut}$ (see e.g.,
-\Fig{alpha16-28}). Overall, the MCCs we identified are much bigger in
+denser as we increase $n_{\rm cut}$ (see \Sec{ncut}). Overall, the MCCs we identified are much bigger in
 size and mass than nearby giant molecular clouds (GMCs), but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
@@
 their radial velocity dispersion maps projected onto the $xy$-plane.
-%
+Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols. 
 \label{fig:sigma}}
@@
 Second, due to turbulence dissipation on small-scales, such
-(sub-)structures are no longer supported by large-scale gravitational
-potential and differential rotation.  \MM{Not sure how potential can
-  support, and in that footnote above you asserted that shear was
+(sub-)structures are no longer supported by differential rotation.  \MM{footnote above, you asserted that shear was
   unimportant, contradicting this claim.} This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
@@
 hydrogen, heating and cooling of the ISM by
-%mm metals
     UV radiation and metal lines, 
@@
 We decompose the molecular structures into non-overlapping 
-%mm tiles
      objects
 by identifying a set of 
-%mm different density contours at different 
      density contours with varying cutoff densities at multiple
@@
 Such an identification method is 
-%mm similar 
      the three-dimensional analog
 to MCC identification based on 
-%mm contour levels/surfaces of surface brightness maps/cubes 
     intensity levels in surface brightness maps or
@@
 dispersion, gas surface density, and virial parameter for each MCC and
-we perform a Toomre-$Q$ stability analysis
-%mm
-    on the galaxy. 
+we perform a Toomre-$Q$ stability analysis on the galaxy. 
 The properties of the MCCs in \flower are compared with observed MCCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
@@
 We find that the MCCs of \flower 
-%mm are highly supersonic, with high 
 have highly supersonic

### 2019-04-10 WRITEUP/ms.tex
added comment on extraplanr flows

@@
 The presence of such extra-planar flows may \MM{Do we have any
-  evidence for or against this speculation?} also be the 
+  evidence for or against this speculation? Clarify citations and
+  mergers vs accretion...} also be the 
 dominant mode for forming the highly supersonic massive MCCs observed

### 2019-04-10 WRITEUP/ms.tex
alpha_vir for 8 ss, double check ss order

--- 2019-04-10 WRITEUP/ms.tex
@@
 
-\begin{figure*}
-% \centering
-\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
-% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
-\caption{
-% Top: 
-Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
-% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
-Definition of the symbol shown are the same as in \Fig{larsons_single}.
-Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
-Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
-% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
-\label{fig:alpha21-22}}
+%\begin{figure*}
+%% \centering
+%\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
+%% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
+%\caption{
+%% Top: 
+%Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
+%% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
+%Definition of the symbol shown are the same as in \Fig{larsons_single}.
+%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
+%Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+%% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
+%\label{fig:alpha21-22}}
+%\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
+\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
+Evolutionary stages are shown chronologically from top left to bottom left, followed by top right to bottom right.
+Definition of symbols shown are the same as in \Fig{larsons_single}.
+Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
+Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
+MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+The virial parameter vary over the $\sim$300\,Myr shown here, as \flower\ evolves.
+The variation is clearly seen between the pre-starburst through post-starburst phase. 
+\label{fig:alphaEvol}}
 \end{figure*}
+{\bf CHECK if I am plotting the righ alphaVIR snapshots../.}
 
@@
 Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
-As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
+As shown in \Fig{alphaEvol}, the total virial parameter (blue dots in the figure) 
 of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
@@
 % 
-3) overall lower alphavir in the pre-SB phase in \Fig{alpha21-22}. 
+3) overall lower alphavir in the pre-SB phase in \Fig{alphaEvol}. 
 1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  

### 2019-04-10 WRITEUP/ms.tex
add fig to show a disky phase of althaea

@@
 
+% This is the messy stage 
 \begin{figure*}[htbp]
@@
 Examples of MCCs (white contours) identified by the clump finder in
-\flower during its  accreting phase. The color bar shows the mean
+\flower during its accreting phase, where \flower is dispersion-dominated.
+Colorbar on the right shows the mean
 H$_2$ number density, weighted by gas mass.
@@
 \label{fig:MCC}}
+\end{figure*}
+
+% Add a figure that shows \flower in "disky" stage. We are interested in exploring whether the MCC properties are dependent on the disk properties. 
+% In other words, if the nature of the MCCs we are identifying are large chucks of arms/disk in \flower, then its dynamics that we are deriving will be dominated by 
+% large-scale shear.
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_0.53}.pdf}
+  \\ [-2.7em]
+  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_6.81}.pdf}
+  \\ [-2.7em]
+  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_18.96}.pdf}
+\caption{
+Same as \Fig{MCC}, except we show the quiescent phase of \flower, which is supported by rotation. 
+\label{fig:MCC28}}
 \end{figure*}
@@
     cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
-5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
-%mm [I moved the next sentence into the main text from the footnote.]
+6.81, 11.36, 18.96, 31.62]$ to each snapshot. 
 We also tested variations in

### 2019-04-10 plotsingleSS.py
fixed subplot order

@@ -158,8 +158,8 @@ if __name__ == '__main__':
     ss6, to_plot6, leafdir_out6 = load_pickleTOplot(21)  # Pre-SB
     ss7, to_plot7, leafdir_out7 = load_pickleTOplot(22)  # SB
     ss8, to_plot8, leafdir_out8 = load_pickleTOplot(23)
-    fig, ax = plot_alpha_vir_8ss(to_plot1, to_plot5, to_plot2, to_plot4,
-                                     to_plot3, to_plot6, to_plot4, to_plot8,
+    fig, ax = plot_alpha_vir_8ss(to_plot1, to_plot5, to_plot2, to_plot6,
+                                     to_plot3, to_plot7, to_plot4, to_plot8,
                                      ls='',
                                      markersize=10,
                                      marker='*',

### 2019-04-10 plot_modules/plot_cloud_prop.py
panels annotation

@@ -1465,6 +1465,11 @@ def plot_alpha_vir_8ss(to_plot1, to_plot2, to_plot3, to_plot4,
             horizontalalignment='center',
             fontsize=16,
             transform=ax.transAxes)
+    plt.text(0.07, 0.08,
+            "(a)",
+            horizontalalignment='center',
+            fontsize=16,
+            transform=ax.transAxes)
 
     ax = plt.subplot(422)
     ax.set_prop_cycle('color', [cm(1. * i / NUM_COLORS)
@@ -1476,6 +1481,11 @@ def plot_alpha_vir_8ss(to_plot1, to_plot2, to_plot3, to_plot4,
     ax.set_xlabel('')
     ax.set_yticklabels([])
     ax.set_xticklabels([])
+    plt.text(0.07, 0.08,
+            "(e)",
+            horizontalalignment='center',
+            fontsize=16,
+            transform=ax.transAxes)
 
     ax = plt.subplot(423)
     ax.set_prop_cycle('color', [cm(1. * i / NUM_COLORS)
@@ -1486,6 +1496,12 @@ def plot_alpha_vir_8ss(to_plot1, to_plot2, to_plot3, to_plot4,
     ax.set_ylabel('')
     ax.set_xlabel('')
     ax.set_xticklabels([])
+    plt.text(0.07, 0.08,
+            "(b)",
+            horizontalalignment='center',
+            fontsize=16,
+            transform=ax.transAxes)
+
 
     ax = plt.subplot(424)
     ax.set_prop_cycle('color', [cm(1. * i / NUM_COLORS)
@@ -1502,6 +1518,12 @@ def plot_alpha_vir_8ss(to_plot1, to_plot2, to_plot3, to_plot4,
     ax.set_xlabel('')
     ax.set_yticklabels([])
     ax.set_xticklabels([])
+    plt.text(0.07, 0.08,
+            "(f)",
+            horizontalalignment='center',
+            fontsize=16,
+            transform=ax.transAxes)
+
 
     ax = plt.subplot(425)
     ax.set_prop_cycle('color', [cm(1. * i / NUM_COLORS)
@@ -1512,6 +1534,11 @@ def plot_alpha_vir_8ss(to_plot1, to_plot2, to_plot3, to_plot4,
     ax.set_ylabel('')
     ax.set_xlabel('')
     ax.set_xticklabels([])
+    plt.text(0.07, 0.08,
+            "(c)",
+            horizontalalignment='center',
[…]

### 2019-04-15 WRITEUP/ms.tex
ss number and galaxy age

@@
 %mm [corrected from Toomre64a to Goldreich65a (not Goldreich65b, which is about spiral arm formation)]
-    \citep{Goldreich65a}:
+    \citep{Goldreich65a}
 \begin{equation}
@@
 %
-The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion:
+The effect of disk thickness modifies the $Q$ parameter for gas and stars by accounting for the vertical velocity dispersion
 \begin{equation}
@@
 \end{equation}
-where the relative weight $w$ is defined as:
+where the relative weight $w$ is defined as
 \begin{equation}
@@
 \citep[see][for its effect]{pallottini:2019,decataldo:2019}.
-%mm \AP{modified accordingly}
-
-The simulation zooms in on a galaxy named
-%mm 
-   after the flower 
+
+The simulation zooms in on a galaxy named after the flower 
 \flower whose properties are given in 
@@
 and are briefly summarized in the following. \flower is a Lyman-break galaxy 
-%mm (LBG), [unused acronym]
 that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
@@
 $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
-  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of
-%mm $\simeq$\,100\,\Msun\,yr\pmOne. [for consistency with the next subsection] 
-   30\,--\,80\,\Msun\,yr\pmOne. 
+  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne. 
 %mm \MM{What is its gas fraction?  I ask because its molecular gas
@@
 
-One of the main advantages for studying the dynamical properties of simulated galaies is that we can examine how their properties evolve with time.
+One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which
+is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
 %
@@
 two of its most extreme evolutionary stages in this work (see \Sec{singless}).
-The two phases correspond to (a) an intensely accreting phase and
+These phases correspond to (a) an intensely accreting phase and
 (b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
 MCC properties are sensitive to these different dynamical
-conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages traced
-in the simulation (see \Sec{ncut}).
-
-Throughout this paper, we 
-%mm dub as ``satellite galaxies'' the dense gas regions outside the
-%main disk of \flower. 
-     describe  the dense gas regions outside the main disk of \flower
-     as satellite galaxies.
+conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages 
+traced in the simulation (see \Sec{ncut}). 
+In \Sec{rot}, we examine the importance of rotation support in the MCC dynamics and
+discuss the implication of this finding in \Sec{rotDiss}.
+
+Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies.
 The distinction between clumps and satellites is admittedly somewhat
@@
 %
-We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.
+We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq15\,Myr.
 
@@
 $R \equiv (3 V /4 \pi)^{1/3}$.
-%
-The velocity dispersion of MCCs is calculated from non-thermal
-velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
-\begin{equation}
-\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
+The full velocity dispersion of MCCs is calculated from 
+the bulk velocity field $\sigma_{\rm bulk}$, non-thermal velocity dispersion $\sigma_{\rm NT}$, and thermal sound speed $c_s$, following
+\begin{equation}
+\sigma^2 = \sigma_{\rm NT}^2 + \sigma_{\rm bulk}^2 + c_s^2.
 \label{eqn:veldisp}
@@
 exceeds that from the diffuse gas. We therefore calculate each term on
-the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
-\begin{equation}
-\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
+For instance, the bulk is calculated as follows
+\begin{equation}
+\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
 \end{equation}
 where the sum is done for the cells composing each MCC.
+Similarly, the non-thermal velocity dispersion is calculated as follows
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,
+\end{equation}
+and the thermal sound speed is calculated through
+\begin{equation}
+%        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
+\end{equation}
+where $P_{\rm NT, i}$ and $P_i$ are the non-thermal and thermal pressures of cell $i$ in units of [K\,\cc], respectively, $k_B$ is the Boltzmann constant, and 
+$M_p$ is the mass of a proton.
 
@@
 This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
-We also compute the Mach number from turbulent and thermal pressure to determine the importance of 
-differential rotation in the derived velocity dispersion: 
-\begin{equation}
-\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}\,,
+We also compute the Mach number from turbulent and thermal pressures following
+\begin{equation}
+\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}.
 \label{eqn:MPress}
 \end{equation}
-where $P_{\rm NT}$ is non-thermal pressure and $P$ is thermal pressure.
+% to track its variation over the evolutionary stages of \flower.
 
@@
 
-%\begin{figure*}
-%% \centering
-%\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
-%% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
-%\caption{
-%% Top: 
-%Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
-%% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
-%Definition of the symbol shown are the same as in \Fig{larsons_single}.
-%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
-%Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
-%% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
-%\label{fig:alpha21-22}}
-%\end{figure*}
-
 \begin{figure*}[htbp]
@@
 \caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
-Evolutionary stages are shown chronologically from top left to bottom left, followed by top right to bottom right.
-Definition of symbols shown are the same as in \Fig{larsons_single}.
+Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
+Definition of symbols are same as in \Fig{larsons_single}.
 Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
+The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
+the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through 
+post-starburst phase.
+The variation is clearly seen between the pre-starburst through post-starburst phase. 
 Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
 MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
-The virial parameter vary over the $\sim$300\,Myr shown here, as \flower\ evolves.
-The variation is clearly seen between the pre-starburst through post-starburst phase. 
 \label{fig:alphaEvol}}
 \end{figure*}
-{\bf CHECK if I am plotting the righ alphaVIR snapshots../.}
 
@@
 light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
+\DL{replace w/ non-thermal velocity versus bulk velocity plot to investigate importance of differential rotation in the derived velocity dispersion.}
 \label{fig:Mach_stellarRatio}}
@@
 Larson's third relation relates MCC structures on small and large
-scales via two physical properties: mass and size \citep{Larson81a,
-  McKee07a}. This is also known as the constant column density
-relation,
+scales via mass and size \citep{Larson81a,
+  McKee07a}. Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
+which is related to the column density ($N_H$) that is obtainable from extinction maps ($A_V$), the mass-size relation is 
+also known as the constant column density relation. 
 \MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
@@
   suggested among others by \citet{Ballesteros11}.}
-since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
-which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). 
-% Motivated by \obs, we overplot lines of constants $A_V$ in the mass-size relation shown in \Fig{MR}.
+  \DL{will discuss implication in \Sec{MR}.}
 By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
@@
 % 
-2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
-can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
-and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
+2) Comment somewhere that feedback plays in important role in the virial parameter, as 
+can be seen in the strong variation in alphavir across the different evolutionary stages of \flower \Fig{alphaEvol}.
 % 
@@
 This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
+4) 
 }
@@
 
-% mass-size relation
+% different evolutionary stages
+In the scaling relations examined, we do not find any quantitative major differences
+in the MCC properties with respect to those observed in the nearby Universe 
+between the accreting phase and the starburst phase of \flower in terms of the Larson's relation (see
+\Fig{larsons_single}), which are separated by $\simeq$300\,Myr. 
+However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ and pressure compared to the starburst phase. 
+Similarly, we see that MCCs .... in the post-starburst phase. 
+This is expected for \SF.
+
+\subsection{Interpretation of Mass-Size Relation} \label{sec:MR}
+\DL{To be rewritten later.}
 The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
@@
   parameters and large stellar contents.}
-
-% different evolutionary stages
-In the scaling relations examined, we do not find any quantitative major differences
-in the MCC properties with respect to those observed in the nearby Universe 
-between the accreting phase and the starburst phase of \flower (see
-\Fig{larsons_single}), which are separated by $\simeq$300\,Myr. 
-However, between the two phases, {\bf blah...}
-\DL{some MCCs in SB phase have
-lower $\alpha_{\rm vir}$ and pressure, but 
-is there any significance in that?} \MM{I'd say there is great
-significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
-stars, exactly what would be expected during a starburst.}
 
@@
 
+\subsection{Importance of Rotation in Molecular Structures Observed To-date} \label{sec:rotDiss}
+read paper on angular momentum of clouds in \citep{Jappsen04a}.
+
+How important is rotation energy in supporting the MCCs we see in \flower, versus pressure supported? Do we see differences 
+in the dynamical properties of MCCs ($\sigma_{\rm pressure, NT}$ vs. $\sigma_v$) between ss16 and ss28?
+
+Concerning the role of rotation from large-scale motion in contributing to the observed linewidths of molecular gas structures identified in spatially resolved \obs of \highz galaxies.
+poses a challenge to the interpretation of existing \obs of spatially resolved molecular gas structures detected in \highz galaxies to-date.
+
 %--------------------------------------------------------------------------
@@
 \section{Summary}      \label{sec:conclusion}
+
+\DL{Note to self: New observations that are now routinely obtained with ALMA provides 
+sensitive and high fidelity images revealing the morphology of gas and dust in \highz galaxies, and possibly on sub-kpc scales. However, 
+as shown here, prototypical galaxies at such high redshift with properties similar to \flower\ will have molecular gas structures
+on sub-kpc scales, but they are not the truly star-forming clumps. As illustrated by studies in local galaxies, \SF proceed on smaller scales than 
+what existing \obs are reaching. While the properties of galaxies at EoR differ from nearby galaxies, we argue that 
+the physics behind \SF is the same, and so regions of where \SF truly takes places/unstable to collapse is on even smaller scales. 
+This results means that caution should be taken when interpreting observational data, albeit the impressive resolution and sensitivity that are unprecedented. 
+Careful consideration of large-scale motions is required when interpreting the observed data in order to understand the origin of star formation activity 
+in galaxies at EoR. 
+}
 

### 2019-04-23 plot_modules/plot_cloud_prop.py
update to make relevant plots for pp

@@ -84,7 +84,7 @@ def unpack_xy(ss):
         _SFR_young = []
         _SFR_old = []
         #
-        _alpha_tot = []
+        _alpha = []
         #
         _mSD = []
         _sizepc = []
@@ -122,8 +122,7 @@ def unpack_xy(ss):
             _sigma_NT.append(ss[ks][kkk].mean_sigma_NT_mass_avg/1.e5)
             _sigma_bulk.append(ss[ks][kkk].v_disp)
             _sigmakms.append(np.sqrt(ss[ks][kkk].sigma_gas_tot))
-            print(_sigma_NT, _sigma_bulk, _sigmakms) # check units
-            _alpha_tot.append(ss[ks][kkk].alpha_vir_summed)
+            _alpha.append(ss[ks][kkk].alpha_vir_summed)
 
             _tffMyr.append(ss[ks][kkk].tff_Myr)
             _rho.append(ss[ks][kkk].avg_density)    # 1/cc
@@ -131,7 +130,7 @@ def unpack_xy(ss):
 
             _mSD_cgs.append(ss[ks][kkk].massSD *
                             ss[ks][kkk].Msun2g / (ss[ks][kkk].pc2cm)**2)
-            _sigma2oR.append(ss[ks][kkk].sigmaSq / (1.e5)**2 /
+            _sigma2oR.append(ss[ks][kkk].sigma_gas_tot /
                              (ss[ks][kkk].R_pc * 2.0))
             _mSD_per_ff.append(ss[ks][kkk].massSD / (ss[ks][kkk].R_pc)**2 / ss[ks][kkk].tff_Myr)
 
@@ -622,6 +621,9 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10, marker='
         ax.set_xlabel("Cloud Size [pc]")
         ax.set_xlim(1.0, 2.e3)
 
+        if 'density' in ystr:
+            ax.set_xlim(50, 700)
+
     if xstr == 'R2 pc2':
         ax.set_xscale("log")
         ax.set_xlim(10.0, 1.e8)
@@ -664,6 +666,10 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10, marker='
         ax.set_yscale("log")
         ax.set_ylabel(r"$\sigma_{\rm NT}$ [km s$^{-1}$]")
         ax.set_ylim(0.1, 7e2)
+
[…]

### 2019-04-23 plotsingleSS.py

@@ -5,6 +5,15 @@ plot physical properties of clouds.
 Single snapshot, different ncuts (from brute.py)
 
 
+main plots:
+- alpha-vir_cloud-mass.png
+- sigma-kms_size-pc.png
+- sigma-kms_stellar-to-gas-mass.png
+- Mach_cloud-mass.png
+- weighted-density_size-pc.png
+- sigma-kms-bulk_sigma-kms-NT.png
+
+
 last mod: August 18 2018
 
 '''
@@ -44,7 +53,7 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("stellar to gas mass", "alpha vir", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("stellar to gas mass", "Mach pressure", leglabel="ncut: ",
+    plot_stuff("stellar to gas mass", "Mach", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("gas sd per ff", "sfr sd", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)    # SK
@@ -60,9 +69,11 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("cloud mass", "alpha vir", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
+    # alpha_vir w/ different definition of sigma in it
+    plot_stuff("cloud mass", "alpha vir", compareAlphaVir=True,
+               leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
-    plot_stuff("Mach", "Mach pressure", leglabel="ncut: ",
+    plot_stuff("size pc", "sigma kms", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("Mach", "SFR young", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
@@ -78,19 +89,20 @@ def plotting_procedure(snapshot_num):
                to_plot=to_plot, outdir=leafdir_out)
     plot_stuff("cloud mass", "Mach", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out)
[…]

### 2019-04-23 plot_modules/plot_cloud_prop.py
remove debugger

@@ -963,8 +963,6 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
         print psuedo_keys
         _idx = np.argsort(sfr_)
         psuedo_keys = [psuedo_keys[i] for i in _idx]
-        print psuedo_keys
-        import pdb; pdb.set_trace()
     for ks in psuedo_keys:
         # ks = numerical value of ncut or sfr
         _x = to_plot[ks]["size pc"]
@@ -1117,8 +1115,6 @@ def plot_alphavir_Mass(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
             psuedo_keys.append(kkk)
         _idx = np.argsort(sfr_)
         psuedo_keys = [psuedo_keys[i] for i in _idx]
-        print(psuedo_keys)
-        import pdb; pdb.set_trace()
     for ks in psuedo_keys:
         # ks = numerical value of ncut or sfr
         if xaxis == 'mass':

### 2019-04-23 io_modules/leaf_pickle.py
updated mass-weighted quantities

@@ -43,6 +43,7 @@ def load_in_pickled_leaf_singleSS(directory, snapshot_num, pattern="*_10*.p"):
             Cloud_dict[kkk] = Cloud(get_dx(snapshot_num), leaf_fields[kkk],
                                     int(kkk))
             print Cloud_dict[kkk]
+            # import pdb; pdb.set_trace()      # pause after printing prop of each MC
         ss[ncut_str] = Cloud_dict
 
     return ss

### 2019-04-23 plotSS.py

@@ -49,8 +49,6 @@ def plotting_procedure(minss, maxss, pattern):
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("size pc", "sigma kms", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("Mach", "Mach pressure", leglabel="sfr: ",
-                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("Mach", "SFR young", leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("Mach", "SFR old", leglabel="sfr: ",
@@ -66,7 +64,9 @@ def plotting_procedure(minss, maxss, pattern):
                 to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff("cloud mass", "Mach", leglabel="sfr: ",
                 to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff("cloud mass", "Mach pressure", leglabel="sfr: ",
+    plot_stuff("size pc", "weighted density", leglabel="sfr: ",
+               to_plot=to_plot, outdir=leafdir_out,  sfrlabel=True)
+    plot_stuff('sigma kms NT', 'sigma kms bulk', leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
 
     plot_stuff_3dim("tff Myr", "size pc", "cloud mass", leglabel="sfr: ",
@@ -75,9 +75,7 @@ def plotting_procedure(minss, maxss, pattern):
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
     plot_stuff('alpha vir', 'sigmaSq over size', leglabel="sfr: ",
                to_plot=to_plot, outdir=leafdir_out, sfrlabel=True)
-    plot_stuff_3dim("Mach" ,"Mach pressure", "cloud mass",
-                    leglabel="sfr: ", to_plot=to_plot,
-                    outdir=leafdir_out, sfrlabel=True)
+
 
     # from plot_modules.plot_cloud_prop import get_masses_all_clouds, massFuncUnbinnedCDF, massFuncPDF, massFuncDifferential, CMF
     # allmass = get_masses_all_clouds(ss)
[…]

### 2019-04-23 WRITEUP/ms.tex
updated fig

@@
 % ------------------
-\section{Numerical simulations}\label{sec:sim}
+\section{Numerical Simulations}\label{sec:sim}
 The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
@@
 at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
-On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$, 
-but this depends on the evolutionary stage of \flower.  % see e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
-This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
-We also compute the Mach number from turbulent and thermal pressures following
+We compute the Mach number from turbulent and thermal pressures following
 \begin{equation}
@@
 \end{equation}
-% to track its variation over the evolutionary stages of \flower.
+On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$,
+% allss: 0.32 
+% In [13]: print(get_Mach_all_clouds(ss11))
+%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
+%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
+%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
+%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
+%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
+%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
+%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
+%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
+%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
+%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
+%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
+%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
+%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
+% allss: 18.96
+%In [15]: print(get_Mach_all_clouds(ss12))
+%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
+%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
+%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
+%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
+%  5.05517168  6.93886988  5.4830306 ]
+but this depends on the evolutionary stage of \flower.  % see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
+% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
 
@@
 $n_{\rm cut}$, as illustrated by the colorbar.
-Blue circular symbols shown in the $\alpha_{\rm vir}$-mass plot shows the total virial parameters, including
-the stellar contribution (see Equation~\ref{eqn:alpha_tot}).
 Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a, 
@@
 While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
-mainly composed of molecular gas only, we also calculate the total virial parameter ($\alpha_{\rm vir, tot}$; Equation~\ref{eqn:alpha_tot}) 
-for MCCs of \flower, given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}). 
+mainly composed of molecular gas only, we calculate the virial parameter including the influence from the stellar component 
+for MCCs of \flower (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
+some of them (see \Fig{stellarRatio16}). 
 MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
@@
 
+\subsection{Importance of Bulk Motions in Measured Velocity Dispersion}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
+\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting phase (top) and 
+quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the 
+quiescent phase, which displays a disk-like morphology (\Fig{MCC28}). 
+Most MCCs in the accreting phase have velocity dispersions from turbulent motions higher than those from bulk motions. 
+The opposite trend is true in the quiescent phase.
+\label{fig:vv}}
+\end{figure}
+
+We compare the velocity dispersion from bulk motions versus turbulent motions in \Fig{vv}, for the accreting phase
+and the quiescent phase. The accreting phase has a disturbed morphology while the quiescent phase 
+displays a disk-like morphology (see \Fig{MCC} and \Fig{MCC28}). 
+Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions. The opposite is true for the 
+quiescent phase. Second, the two velocity dispersions are of the same order of magnitude. 
+This indicates that the .... have an important contribution from large-scale rotation.
+\DL{ rewrite: This also poses challenge to measurements and interpretation of .... from existing observations of 
+molecular ``clouds'' observed with 
+ALMA and VLA. 
+n, and so comparison of their dynamics with local clouds via e.g., Larsons relations is not straightforward, and thus, the interpretation of such. 
+Meaning a lot of the sigma people infer at the sub-pc scale have a non-negligible contribution from rotation (cf.
+solely random motion), so it's not immediately fair for observations to say that higher redshift molecular gas are more turbulent based on solely measured velocity dispersion.
+}
+
 \subsection{Interpretation of Mass-Size Relation} \label{sec:MR}

### 2019-04-25 WRITEUP/ms.tex
up to sec 6

@@
 traced in the simulation (see \Sec{ncut}). 
-In \Sec{rot}, we examine the importance of rotation support in the MCC dynamics and
-discuss the implication of this finding in \Sec{rotDiss}.
+In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties 
+in the disturbed phase of \flower and in the disk-like ordered phase.
 
@@
 Examples of MCCs (white contours) identified by the clump finder in
-\flower during its accreting phase, where \flower is dispersion-dominated.
+\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated.
 Colorbar on the right shows the mean
@@
 To visually display 
-the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
+the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
 Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
@@
 as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
-$\mathcal{M}$, r.m.s. velocity dispersion $\sigma$
+$\mathcal{M}$, velocity dispersion $\sigma$
 , and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.
@@
 the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
-For instance, the bulk is calculated as follows
+For instance, the bulk velocity dispersion is calculated as follows
 \begin{equation}
@@
 \begin{equation}
-\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,
+\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,
 \end{equation}
@@
 %        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
-c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / <\rho_i> \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
 \end{equation}
@@
 %
-The massive ($M_{\rm cl}>$10$^8$\,\Msun) 
-clouds identified at low density cut (see top left panel of \Fig{dist})  
-correspond to the molecular disk of the
+The most massive ($M_{\rm cl}>$10$^8$\,\Msun) 
+cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist})  
+corresponds to the molecular disk of the
 galaxy, which is identified as a single component for low $n_{\rm
@@
 MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}). 
+The main disk occupying the top right corner of \Fig{stellarRatio16} has a stellar-to-gas mass ratio of $\simeq$\,50--100.
 
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
-\caption{
-Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
-% ss20,21,22,27
-The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
-light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
-\DL{replace w/ non-thermal velocity versus bulk velocity plot to investigate importance of differential rotation in the derived velocity dispersion.}
-\label{fig:Mach_stellarRatio}}
-\end{figure}
-
 \begin{figure*}
@@
 
-We present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}), 
-and identify a set of MCCs in each of them. 
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
 
 Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
-and sizes ($R\simeq 100$\,pc). These values are consistent with those found in starburst galaxies, 
+and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, 
 such as the nearby gas-rich galaxy M64 and 
@@
 the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
-\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs \citep{Heyer04a, Bolatto08a}.
+\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
 
 % middle
-While the virial parameter is typically defined as Equation~\ref{eqn:alpha} in observational studies, as they probes structures that are 
-mainly composed of molecular gas only, we calculate the virial parameter including the influence from the stellar component 
-for MCCs of \flower (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are 
+composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component 
+(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
 some of them (see \Fig{stellarRatio16}). 
 MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
-\Fig{MCC} and \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
+\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
 This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
@@
 % PVE
-Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panel of \Fig{larsons_single}.
+Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
-Dashed lines in the figure show the loci along which the corresponding external pressures are needed for MCCs in equilibrium to have certain 
-linewidths for a given set of surface densities (see \Sec{PVE}).
+Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium 
+to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
@@
 
-% cloud structures at large and small scale
-% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
-% column density) as fundamental properties of molecular cloud structure.
-Larson's third relation relates MCC structures on small and large
-scales via mass and size \citep{Larson81a,
-  McKee07a}. Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
-which is related to the column density ($N_H$) that is obtainable from extinction maps ($A_V$), the mass-size relation is 
-also known as the constant column density relation. 
-\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
-  $\Sigma$.  Effectively, Larson's mass-size relation is a single
-  point on that relationship, at the constant $\Sigma$ value.  This
-  suggests that the mass-size relation is just an artifact of the
-  narrow range of column densities observed with $^{12}CO$, as
-  suggested among others by \citet{Ballesteros11}.}
-  \DL{will discuss implication in \Sec{MR}.}
+Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
+\citep{Larson81a, McKee07a}.
+Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
+which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$), 
+the mass-size relation is also known as the constant column density relation and has been 
+proposed as a fundamental property of molecular clouds on different physical scales.
+
 By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
@@
 Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-MCCs of \flower spans a 
- lie along the locus of $A_V \simeq 8.9$ clouds observed by
+As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
 \citet{Lombardi10a} in the MW. 
-\MM{Does the variation in surface
-  density seen in Figure 7 correspond to the variation in $A_V$ seen
-  here?}
-%
-%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+%
+%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
+%the $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
 5 therein]{Behrens18a}
@@
 % Starburst 
-In the starburst phase, MCCs have velocity dispersion, sizes,
-and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
-a wider range in $\sigma^2/R$ and gas surface density. 
-Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
-As shown in \Fig{alphaEvol}, the total virial parameter (blue dots in the figure) 
-of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
-%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
-%These trends are as expected in the MCC properties prior to and during a starburst. 
-% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
-% i.e., we haven’t reached those scales where true collapse is happening. 
-% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
-As shown in \Fig{Mach_stellarRatio}, the Mach number (see Equation~\ref{eqn:MPress}) 
-of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
-(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
-increases from the pre-starburst phase through the post-starburst phase. 
-This results as stellar feedback injects kinetic energy into the surrounding ISM in the form of turbulence as \SF proceed.
-In the quiescent phase, high Mach number are seen in mostly MCCs identified with the lowest density threshold. These 
-correspond to satellites MCCs in the outskirts of \flower.
+Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes 
+as those in the accreting phase; however, the MCCs in the starburst phase span 
+a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
+Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
+(\Fig{alphaEvol}).
+Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand, 
+the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase. 
+This is consistent with our physical intuition of gas instability leading to \SF.
 
@@
 the results presented in \Sec{singless} dependent on the choice of density thresholds.
+
 The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
@@
 that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
-typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.} ). 
+typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}). 
 These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
@@
 We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
-We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
-
-% Also mentioned in \Sec{sfh}, we will frame the remainder of this work focusing on the properties of MCCs identified in the two most extreme 
-% evolutionary stages of \flower.
+We find no quantitative differences over the 700\,Myr traced in our simulation, except 
+for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
 
@@
 Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep.
-The higher velocity dispersions
-(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
-these MCCs can also be understood as they have experienced more recent
-episodes of \SF as \flower is assembling its stellar mass --- these MCCs have higher stellar-to-gas mass ratios of $M_\star/M_{\rm gas}\simeq0.1 - 1$ (\Fig{stellarRatio16}) and high turbulent pressure as shown by the high $\mathcal{M}$ in \Fig{Mach_stellarRatio}.
-%
+Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also the deepest,
+and also resulting from the injection of kinetic energy from recent
+\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
@@
 
-The high pressure observed in \flower (see \Fig{Mach_stellarRatio}, see also \citealt{Pallottini17a})
+The high pressure observed in \flower (see \citealt{Pallottini17a})
 is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
@@
 
-\subsection{Stability of MCCs}
+\subsection{Stability of MCCs} \label{sec:Qeff}
 

### 2019-04-25 WRITEUP/ms.tex
up to 6.3

@@
 identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
+The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher 
+density thresholds (top right panel).
 \label{fig:alpha16-28}}
@@
 
-\DL{
-1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
-influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
-% 
-2) Comment somewhere that feedback plays in important role in the virial parameter, as 
-can be seen in the strong variation in alphavir across the different evolutionary stages of \flower \Fig{alphaEvol}.
-% 
-3) overall lower alphavir in the pre-SB phase in \Fig{alphaEvol}. 
-1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
-The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
-directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
-This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
-4) 
-}
-
-\subsection{Placing Results in the Context of Existing Observations} \label{sec:diss1}
-
+\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}
+
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm cl}$, 
+$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
 Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
@@
 and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
-Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also the deepest,
-and also resulting from the injection of kinetic energy from recent
-\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs).
+Their velocity dispersions are also comparable to those observed in the inner 
+Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the 
+locus of $\sigma\propto R^{0.56}$. 
+Such high velocity dispersions and surface densities can be explained partly because 
+these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest, 
+and also from the injection of kinetic energy from recent
+\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
@@
 $M_\star$\eq7.5\E{9}\,\Msun. 
+Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that 
+the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in 
+its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in 
+interpreting observational results is further discussed in the next subsection (\Sec{rot}).
 
@@
 %
-For instance, in local ULIRGs, 
-%mm they are likely form 
-  MCCs are likely formed
+For instance, in local ULIRGs, MCCs are likely formed
 by shock compression and cloud-cloud collisions 
-%mm after large amounts of gas from the pair of progenitor galaxies
-%are funneled toward the central region 
  that funnel large amounts of gas from the progenitor galaxies
@@
 high due to the resolution limit.
-The constant inter-cloud collisions as gas is being accreted onto the
-main galaxy 
-%\MM{This is a highly dissipative process.  Hennebelle \&
-%  Klessen found it could only be important in rather small galaxies.
-%  Does \flower qualify?} 
-would also render the MCCs gravitationally unbound (see e.g., \citealt{Dobbs11a}), 
-%\MM{Dobbs
-%  started with a low-density disk, and got low-density clouds. I don't
-%  think that's what you have here.  Do you have any evidence for
-%  inter-cloud collisions being important?}
-%\DL{think okay to state as speculation since we are not drawing conclusions based on this?} 
-which would be consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.
 
 % different evolutionary stages
-In the scaling relations examined, we do not find any quantitative major differences
+In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences
 in the MCC properties with respect to those observed in the nearby Universe 
-between the accreting phase and the starburst phase of \flower in terms of the Larson's relation (see
+between the accreting and starburst phase of \flower (see
 \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
-However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ and pressure compared to the starburst phase. 
-Similarly, we see that MCCs .... in the post-starburst phase. 
-This is expected for \SF.
-
-\subsection{Importance of Bulk Motions in Measured Velocity Dispersion}
+However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+Similarly, the virial parameter is higher in the post-starburst phase compared to both the pre-\SB and \SB phases. 
+This is expected for \SF to proceed.
+
+\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}
 
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting phase (top) and 
+\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and 
 quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the 
 quiescent phase, which displays a disk-like morphology (\Fig{MCC28}). 
-Most MCCs in the accreting phase have velocity dispersions from turbulent motions higher than those from bulk motions. 
-The opposite trend is true in the quiescent phase.
+The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but 
+the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion. 
+This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales as here
+should not be taken as a direct evidence that these gas structures at high redshifts are intrinsically more turbulent than those in the local ISM.
+% either higher resolution, or properly accounting for large scale motions. 
 \label{fig:vv}}
@@
 
-We compare the velocity dispersion from bulk motions versus turbulent motions in \Fig{vv}, for the accreting phase
-and the quiescent phase. The accreting phase has a disturbed morphology while the quiescent phase 
-displays a disk-like morphology (see \Fig{MCC} and \Fig{MCC28}). 
-Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions. The opposite is true for the 
-quiescent phase. Second, the two velocity dispersions are of the same order of magnitude. 
-This indicates that the .... have an important contribution from large-scale rotation.
-\DL{ rewrite: This also poses challenge to measurements and interpretation of .... from existing observations of 
-molecular ``clouds'' observed with 
-ALMA and VLA. 
-n, and so comparison of their dynamics with local clouds via e.g., Larsons relations is not straightforward, and thus, the interpretation of such. 
-Meaning a lot of the sigma people infer at the sub-pc scale have a non-negligible contribution from rotation (cf.
-solely random motion), so it's not immediately fair for observations to say that higher redshift molecular gas are more turbulent based on solely measured velocity dispersion.
-}
-
-\subsection{Interpretation of Mass-Size Relation} \label{sec:MR}
+We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting 
+and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase 
+but a disk-like morphology in the quiescent phase 
+(see \Fig{MCC} and \Fig{MCC28}). 
+Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
+whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude. 
+{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here 
+have an important contribution from large-scale rotation.} Hence, velocity dispersions measured on these scales should {\em not} be taken as 
+a direct evidence of \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
+and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
+
+\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
 \DL{To be rewritten later.}
@@
 by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
-can be understood by acknowledging the fact that a H$_2$ molecular
-cloud does not necessary contain CO (e.g., as CO forms deeper in
-molecular clouds), and that our simulation does not have enough
-resolution to directly form CO\footnote{In fact, to form CO and make
+can be understood by acknowledging the fact that a given MCC does not necessary contain CO (as CO forms deeper in
+molecular clouds and our simulation does not have enough
+resolution to directly form CO)\footnote{In fact, to form CO and make
   predictions for CO line emission in the work presented by
@@
   each cell in our simulation.}.  
-\MM{But column densities have nothing to do with CO, and you are
-  deriving $A_V$ from column densities.  Forming CO doesn't increase
-  column densities; it is just a tracer of dense gas.  Atomic line
-  cooling will be just as efficient as CO in actually cooling the gas
-  down to tens of Kelvin (see Clark \& Glover some years ago).}
-\DL{It doesn't increase the column density, but these obs. results are based on CO, which traces deeper 
-regions than we could here because MCCs are not entirely molecular, this may become clearer after 
-expanding what $n_{\rm cut}$ means in Sec 3. {\bf AP?}}
-%
-That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag 
-%mm likely manifests from the fact 
-    demonstrates
+That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
 that the MCCs in our simulation have lower column densities than the
@@
 observationally well-resolved within an MCC, and indeed, have
-sufficient column density to form CO.  \MM{I suppose the question is
-  if we observed the Milky Way at equivalent resolution, would we see
-  such low column densities on average?  This is more or less the game
-that Diderijk Kruijssen has been playing.}
-\DL{Don't think this is a resolution effect, but our MCC is not entirely H2 {\bf AP?}}
+sufficient column density to form CO.
 

### 2019-04-25 WRITEUP/ms.tex
up to sec 7

@@
 \z$\sim$2 galaxies in rest-frame UV and optical light
-\citep{Elmegreen07a, Elmegreen09a}. The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
+\citep{Elmegreen07a, Elmegreen09a}. 
+The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
 MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}). 
@@
 In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
-On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun) have been 
+reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
+resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+However, the IGM and merger and accretion histories are not properly modeled in such simulations since 
+they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
+reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+The gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
 %% 
@@
 %%
-This lack of variation is reassuring, i.e., our inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
-nearby and \z$\sim$2 galaxies in the context of linewidth-size relations are not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
+This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
+nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
 
@@
 the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion. 
-This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales as here
-should not be taken as a direct evidence that these gas structures at high redshifts are intrinsically more turbulent than those in the local ISM.
+This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales 
+should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
 % either higher resolution, or properly accounting for large scale motions. 
 \label{fig:vv}}
+\vspace{0.5em}
 \end{figure}
@@
 {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here 
-have an important contribution from large-scale rotation.} Hence, velocity dispersions measured on these scales should {\em not} be taken as 
-a direct evidence of \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
+have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures 
+on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
 and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
@@
 by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
-can be understood by acknowledging the fact that a given MCC does not necessary contain CO (as CO forms deeper in
-molecular clouds and our simulation does not have enough
-resolution to directly form CO)\footnote{In fact, to form CO and make
+can be understood by acknowledging the fact that a given MCC in \flower 
+does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and 
+our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
 predictions for CO line emission in the work presented by 
-  \citet{Vallini18a}, we model the internal structure of MCC within
-  each cell in our simulation.}.  
+\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
 That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
@@
 
+In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases. 
+This makes sense from simply the fact that smaller MCCs have smaller masses. 
+However, what does it mean for them to lie on the same locus?
+% is it what Jen's proposed? Or is it's just a result of $\rho\propto M R^{-3}$ (and $\rho$ is independent of R) 
+% and observational bias (selection effect due to projection in 2D, so $\rho \propto N_H R^{-1}$, where $N_H$ is a 
+% constant due to gas tracer) (i.e., middle and bottom panels of Fig 9 in BM02)?
+
 The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
-an ``internal'' mass-size relation where $M\propto R^{1.33}$.
-If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
-regions of high-mass \SF. That is, the MCCs identified have mass-size
-relations suggesting they are capable of high-mass \SF. \MM{I don't
-  yet understand how this squares with their very high virial
-  parameters and large stellar contents.}
-
-\subsection{Origin and Physical Scales of MCCs} \label{sec:origin}
-
-The largest molecular structure identified is essentially the main
-disk of \flower \MM{Is this consistent with your assertion of no shear
-  in a footnote above?} and breaks down into smaller substructures that are
-denser as we increase $n_{\rm cut}$ (see \Sec{ncut}). Overall, the MCCs we identified are much bigger in
-size and mass than nearby giant molecular clouds (GMCs), but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.
-
-% mass scale
-Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show
-higher velocity dispersions compared to the disk
-%mm/mid-plane 
-of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
-% which is $\propto\rho\sigma^2$
-% M51: Colombo+14
-However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
-These bigger clouds have been interpreted as 
-%mm a result of their higher gas mass fractions, [I had trouble
-%interpreting this sentence. Do you agree with the revision?]
-    forming because of the higher gas fractions in these galaxies,
-    which lead to higher
-surface densities, and 
-%mm velocity dispersions
-   ultimately velocity dispersions as collapse occurs.
-Fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and
-Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.
-
-Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
-velocity dispersion of $\sigma\simeq50$\,\kms and a
-gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
-$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass
-range found in the MCCs identified (see \Fig{dist}).  \MM{I really
-  don't see this: \Fig{dist} has no clouds that massive, and in
-  the higher density case doesn't even get within an order of
-  magnitude of this value.  In both cases, the mode is closer to 5\E{6} \Msun.}
-%
-Similarly massive \MM{8\E{8} \Msun?} molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
-resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
-That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-
-%Note that regions of $Q\lesssim1$ is actually somewhat
-%less than the number of MCCs we have identified based on density threshold ---
-%but this has something to do with the dependence on
-%$n_{\rm cut}$. The number of MCCs and regions of low $Q$ are comparable if we only look at
-%MCCs identified at the highest $n_{\rm cut}$.
-
-% alpha parameters
-As shown in \Fig{larsons_single},
-the virial parameter of the sub-MCCs \MM{How can we distinguish
-  sub-MCCs from MCCs in this figure?} is $\alpha_{\rm vir}\gtrsim10$,
-which is considerably lower than their ``parent'' MCCs found in the
-main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).  \MM{However,
-  both are extremely high.}
-%
-For the MCCs in the satellite galaxies, \MM{How can we distinguish
-  these, in turn?} a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
-Differences in their $\alpha_{\rm vir}$ most likely result from the
-weaker stellar feedback in the satellites \MM{Or lower stellar content
-and thus weaker potentials?} as they have experienced fewer episodes
-of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
-$\sim$0.1) \MM{Should you explicitly show stellar-to-gas mass ratios in a figure?}.
-
-% Pressure
-MCCs in the main disk of \flower have higher pressure than the
-sub-MCCs. \MM{examine the gas pressure field.} The lower virial parameter and 
-pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
-%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
-%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
-%and galactic rotation on large scales.
-%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.
-
-For MCCs in the satellite galaxies, we find even lower pressures and
-virial parameters, \MM{This needs to be shown explicitly in a figure,
-  as I think I already mentioned above.} which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
-This suggests that MCCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.
-
-\subsection{Stability of MCCs} \label{sec:Qeff}
+an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
+If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond 
+to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
+If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
+one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as 
+regions of massive \SF. 
+%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+%  point on that relationship, at the constant $\Sigma$ value.  }
+However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
+with a certain tracer (e.g., \citealt{Ballesteros11}). 
+That is, it is solely a result of $\rho\propto M R^{-3}$. 
+For instance, \citet{Ballesteros02a} show that the density 
+of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of 
+two-dimensional space, as is done in \obs. 
+When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given 
+line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant. 
+They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$ 
+observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in 
+observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+% since $M$ would then scale as $R^{3}$.
+% naturally display a linear relationship in $\log M - \log R$ plot.
+
+% the widespread in density for a given R. 
+We show the density-size relation ($\rho - R$) relation of MCCs of \flower in \Fig{rho}.
+The interpretation of this figure is not that MCCs with small $R$ are found at high $n_{\rm cut}$ and large $R$ at low $n_{\rm cut}$, nor is that
+the density of MCCs is independent of $R$. Rather, it is as we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and 
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+\DL{This is puzzling to me why we are seeing some really steep relationship between $\rho$ and $R$, almost $\rho \propto R^{-6}$ 
+even though we are identifying the structures in 3D just like what BM02 did.}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16} 
+\caption{Density and size of MCCs in the accreting phase of \flower.
+At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and 
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+\label{fig:rho}}
+\vspace{0.5em}
+\end{figure}
+
+\subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}
 
@@
 \caption{
-Surface density maps of the gas (top left) and stellar (top right) components of \flower and
-their radial velocity dispersion maps projected onto the $xy$-plane.
-Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols. 
+Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and
+their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
+Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols
+as an illustrative example.
 \label{fig:sigma}}
@@
 identification of regions above and below $\log{Q}$\eq0.
-Some MCCs \MM{But these are the exception.} lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
+Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
 are likely gravitationally unstable.
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} of \flower 
 indicates that the stellar component plays an important role in
 governing the stability of the MCCs against $m=0$  perturbations,
-\MM{Well, there are definitely regions dominated by gas.}  highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
+highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}
@@
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-
-Similarly, contribution from the thickness of the disk is important in \flower since its disk warped and cannot be considered thin, i.e., 
-it has a scale height to radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
-
-That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
+Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and 
+has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
+
+That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that 
+they correspond to regions of high surface densities that are gravitationally unstable. 
 Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
@@
 when examining the stability of molecular gas structures.
-This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
+This consideration is especially relevant for the relatively evolved and enriched systems at high redshift,
 that are preferentially being imaged at high resolution with ALMA.
@@
 The apparently large virial parameters seen in the MCCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}). 
-We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
+We first note that fragmentation {\it can} happen in regions of low $Q$ 
+(if we only consider instability against axisymmetric perturbations), 
+but further evolution/collapse depends on the dynamics or equation of state of the gas.
 %
@@
 Second, this fragmentation scale is greater than the typical size of GMCs. 
-This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales.
-%
-Thus, the high virial parameter found for most MCCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure and rotation) and surface density, indicate that most of them are not collapsing structures.
-As such,
-some MCCs are found to lie in regions of $Q_{\rm eff}>1$.
-% some MCCs at Q < 1, some are marginally stable against m=0 mode perturb, some are Q>1.
-Only in (the denser) regions with a low Toomre $Q_{\rm eff}$ parameter and when the cooling time is lower then the dynamical time star formation can proceed in {\it clumps} and {\it cores} with low virial parameters.
-
-Note that even in stages when \flower~is star forming we find that most of its MCCs have high $\alpha_{\rm vir}$.
-This seem to be self-contradictory: if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
+% 
+This could be interpreted as a result of instability setting the scales for fragmentation, 
+{\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
+%
+Thus, the high virial parameter found for most MCCs in \flower 
+indicates that some of them are not collapsing structures (but the virial parameter varies depending on the evolutionary stage 
+of \flower). Hence, some MCCs are found to lie in regions of $Q_{\rm eff}>1$.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
+and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
+where energy quickly dissipates. % with low virial parameters.
+
+If most of the MCCs in \flower are stable against collapse, 
+how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? 
 Such tension in the interpretation is understood as follows.
@@
 Second, due to turbulence dissipation on small-scales, such
-(sub-)structures are no longer supported by differential rotation.  \MM{footnote above, you asserted that shear was
-  unimportant, contradicting this claim.} This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
-%
-Further, mechanisms causing non-axisymmetric perturbations (e.g.,
-arms) to the gravitational potential \MM{Gravitational instability is
-  that mechanism (see e.g.\ Wada et al.'s classic review of the
-  subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+(sub-)structures are no longer supported by differential rotation. 
+This in turn enables sub-regions of the MCCs to collapse and potentially form 
+OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
+% Mechanisms causing non-axisymmetric perturbations (e.g.,
+% arms) to the gravitational potential \MM{Gravitational instability is
+%   that mechanism (see e.g.\ Wada et al.'s classic review of the
+%   subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} 
+% can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
 These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
-Finally, the SFR of \flower is very bursty and high SFR stages are only transient.
-% the giant MCCs found are likely due to non-axisymmetric mode.
-
-\subsection{Importance of Rotation in Molecular Structures Observed To-date} \label{sec:rotDiss}
-read paper on angular momentum of clouds in \citep{Jappsen04a}.
-
-How important is rotation energy in supporting the MCCs we see in \flower, versus pressure supported? Do we see differences 
-in the dynamical properties of MCCs ($\sigma_{\rm pressure, NT}$ vs. $\sigma_v$) between ss16 and ss28?
-
-Concerning the role of rotation from large-scale motion in contributing to the observed linewidths of molecular gas structures identified in spatially resolved \obs of \highz galaxies.
-poses a challenge to the interpretation of existing \obs of spatially resolved molecular gas structures detected in \highz galaxies to-date.
+Further, the SFR of \flower is very bursty and high SFR stages are only transient.
 

### 2019-04-26 WRITEUP/ms.tex
revised sec 7

@@
 \subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
-\DL{To be rewritten later.}
 The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
@@
 
-The apparently large virial parameters seen in the MCCs of \flower can be understood using the Toomre $Q$ parameter (see \Fig{Qeff}). 
-We first note that fragmentation {\it can} happen in regions of low $Q$ 
+The large virial parameters seen in some MCCs of \flower can be understood 
+by first noting that fragmentation {\em can} happen in regions of low $Q$ 
 (if we only consider instability against axisymmetric perturbations), 
@@
 %
-Thus, the high virial parameter found for most MCCs in \flower 
-indicates that some of them are not collapsing structures (but the virial parameter varies depending on the evolutionary stage 
-of \flower). Hence, some MCCs are found to lie in regions of $Q_{\rm eff}>1$.
+Thus, the high virial parameter found for some MCCs in \flower 
+indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage 
+of \flower) and are found in regions of $Q_{\rm eff}>1$.
 On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
@@
 %--------------------------------------------------------------------------
-\section{Summary}      \label{sec:conclusion}
-
-\DL{Note to self: New observations that are now routinely obtained with ALMA provides 
-sensitive and high fidelity images revealing the morphology of gas and dust in \highz galaxies, and possibly on sub-kpc scales. However, 
-as shown here, prototypical galaxies at such high redshift with properties similar to \flower\ will have molecular gas structures
-on sub-kpc scales, but they are not the truly star-forming clumps. As illustrated by studies in local galaxies, \SF proceed on smaller scales than 
-what existing \obs are reaching. While the properties of galaxies at EoR differ from nearby galaxies, we argue that 
-the physics behind \SF is the same, and so regions of where \SF truly takes places/unstable to collapse is on even smaller scales. 
-This results means that caution should be taken when interpreting observational data, albeit the impressive resolution and sensitivity that are unprecedented. 
-Careful consideration of large-scale motions is required when interpreting the observed data in order to understand the origin of star formation activity 
-in galaxies at EoR. 
-}
-
-\MM{Each item in the summary needs to refer to definite results and
-  analysis in the previous paper.  I have noted the items that don't
-  seem to me to have that necessary support.}
-We study the dynamical properties of molecular clouds complexes and their temporal evolution in a \z$\sim$\,6 prototypical galaxy, \flower,
-at the EoR using the state-of-the-art cosmological zoom-in simulation (\ncode{Serra}),
-which includes a chemical network to determine the formation of molecular
-hydrogen, heating and cooling of the ISM by
-    UV radiation and metal lines, 
-and detailed stellar feedback.
-We use a clump-finding algorithm and a set of H$_2$ volumetric densities
-to identify MCCs and their sub-structures in \flower and its satellites.
-We decompose the molecular structures into non-overlapping 
-     objects
-by identifying a set of 
-     density contours with varying cutoff densities at multiple
-evolutionary stages.
-Such an identification method is 
-     the three-dimensional analog
-to MCC identification based on 
-    intensity levels in surface brightness maps or
-    position-position-velocity cubes
-of molecular line tracers (e.g., CO, CS, NH$_3$),
-since the line luminosity scales with the molecular gas density (modulo optical depth effects).
-
+\section{Summary and Conclusions}      \label{sec:conclusion}
+
+Properties of the star-forming ISM of galaxies near the Epoch of Reionization are now within reach with ALMA. 
+While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology 
+on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution
+and sensitivity are needed. As such, observational studies on such scales are still missing in the literature. 
+In this work, we aim to understand the origin and dynamical properties of molecular clouds complexes 
+in prototypical galaxies at the EoR in numerical simulations 
+to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
+
+We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower,
+and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}),
+which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by
+UV radiation and metal lines, and detailed stellar feedback.
+Properties of \flower are briefly summarized in \Sec{sim}.
+We use a three-dimensional clump-finding algorithm to identify MCCs and their sub-structures. 
+We decompose the molecular structures into non-overlapping objects by identifying a set of 
+density contours with varying cutoff densities at multiple evolutionary stages. 
+Most notably, the accreting phase, starburst phase, and quiescent phase. 
 We extract properties such as mass, size, Mach number, velocity
-dispersion, gas surface density, and virial parameter for each MCC and
-we perform a Toomre-$Q$ stability analysis on the galaxy. 
-The properties of the MCCs in \flower are compared with observed MCCs in the Milky Way disk, the Galactic center, and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
-This is done for different evolutionary stages of \flower.
-
-We find that the MCCs of \flower 
-have highly supersonic
-velocity dispersions ($\sigma\simeq$\,200\,\kms) comparable to
-those observed in $z$\ssim2 starburst galaxies.
-The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun,
-depending on the chosen H$_{2}$ density cut. 
+dispersion, gas surface density, and virial parameter ($M_{\rm cl}, R, \mathcal{M}, 
+\sigma, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
+and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
 The $\sim$200\,pc-scale MCCs found with a low density threshold
-correspond to the arms of the disk of \flower. These break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
-The more massive and bigger MCCs in \flower compared to the Milky Way
-likely result from the higher gas mass fraction, surface density, and velocity dispersion,
-which set the scale for fragmentation. \MM{This could be quantified in
-  the discussion by calculating the Jeans scale for the disk conditions.}
-This physical scale is
-consistent with what has been found in higher resolution idealized
-simulation of isolated galaxies. \MM{Perhaps this could be shown more explicitly?}
-Our simulation here confirms these results at EoR and under
-the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
-
-We compare the dynamics of MCCs in \flower to \obs in the context of
-the Larson's relation. \MM{Which one?}
-The MCCs of \flower are found to have higher $\sigma$ and $\Sigma$
-\MM{compared to Milky Way clouds?}
-systematically regardless of the 
-density threshold $n_{\rm cut}$ adopted in identifying the structures.
-The scaling relations found are insensitive to the various density
-cuts.  \MM{This point needs to be made more clearly, probably by
-  defining the colors that correspond to the density cuts in the figures.} \DL{They are color-coded by ncut in Fig 5 and 7.}
- The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the density threshold and 
- even for the molecular substructures.  \MM{You never clearly identify
-   what you mean by ``molecular substructures.''  Do you just mean
-   objects found with high $n_{\rm cut}$?}
- Such a high velocity dispersion likely results from the strong supernova and stellar feedback \flower experienced 
- over the multiple episodes of bursty \SF.   \MM{Or is it from the
-   deep potential?  Feedback-driven turbulence famously decays quickly.}
-
-Virial analysis indicates that MCC/arms of the main disk of \flower are unbound, but substructures have
-lower virial parameter.
-\MM{where is this explicitly discussed?}
- Some of these sub-MCCs have Toomre $Q_{\rm eff}$ parameters consistent with being
-gravitationally unstable.  \MM{I don't see this looking at Figure 9.
-  Rather the opposite if anything.} This is consistent with the notion that collapsing structures resulting from
+correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
+Overall, the mass of MCCs ranges between $10^{5.5-8.5}$\,\Msun, depending on the chosen density threshold.
+This mass range is comparable to those observed in \z\ssim2 galaxies in rest-frame UV and optical wavelengths.
+Similarly massive molecular structures (few times 10$^7$\,\Msun) have been 
+reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 
+48\,kpc box studied by \citealt{Behrendt16a}). 
+However, the IGM and merger and accretion histories are not properly modeled in such simulations. 
+That said, the similar mass range found in MCCs of \flower\ is
+reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
+On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the adopted density threshold.
+
+We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
+observed in the Milky Way disk, the Galactic center, and 
+gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations. 
+This comparison is done for different evolutionary stages of \flower.
+
+MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than 
+Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted. 
+These MCCs are, in fact, highly supersonic (with high Mach numbers).
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma\simeq200$\,\kms); however, 
+comparing the velocity dispersions of MCCs from bulk motions versus turbulence 
+indicates that large-scale rotation is an important contributor, even in the 
+accreting phase of \flower, which displays a highly disturbed morphology. 
+This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date. 
+In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc) 
+should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM, 
+unless contributions from bulk motions are properly accounted for.
+%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution 
+%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used 
+%for structures in the literature) are more turbulent based on solely measured velocity dispersion.
+
+We do not observe any significant temporal variations in the MCC dynamics over the course of 700\,Myr
+traced in our simulation, except in the virial parameter, which is the lowest in the pre-starburst phase. 
+The virial parameter increases after a starburst as gas is self-regulated by feedback.
+
+% Toomre:
+Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps 
+indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against
+axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also 
+non-negligible. Our Toomre-Q analysis thus illustrates the importance of accounting for stellar contribution 
+and disk thickness when examining the stability of 
+molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
+
+We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of 
+molecule gas structures. The high virial parameter found for some MCCs in \flower 
+indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
+and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
+where energy quickly dissipates. % with low virial parameters.
+This is consistent with the notion that collapsing structures resulting from
 gravitational instability occur within globally stable structures, which are
 supported by turbulence and rotation on large scale.
-We also find $\alpha_{\rm vir}\simeq$\,2 for MCCs in the satellite
-galaxies, \MM{I didn't see any explicit discussion of the MCCs in
-  satellite galaxies.} which we interpret as
-result of the weaker/delayed stellar feedback compared to \flower. 
-In particular, some of the MCCs in the satellites are collapsing structures that have not yet formed stars, as confirmed by their
-higher gas-to-stellar fractions. \MM{Also not shown so far as I can see.}
-In terms of the scaling relations examined, we do not observe any significant
-temporal variations in the MCC dynamics over the course of 700\,Myr
-traced in our simulation.
-
+%% 
+%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
+%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales. 
+%Low-$Q$ sets the regions that fragments 
+%and within those regions where alphavir is low enough is where structures to further collapse to form stars. 
+This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
+and thus, \SF in the first galaxies.
+
+% end
 Determining the multi-phase ISM properties of early galaxies
@@
 for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
-Observations leveraging the combination of spatial-spectral imaging of
-multi-band continuum and spectral line emission are crucial for better understanding
-the role of \highz galaxy populations
-in the context of galaxy evolution and the ISM physics behind their intense star formation in the early Universe.
-Cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics and are subject to the sub-grid models adopted,
-serve as a useful tool for examining and making predictions on the
-morphology and dynamics of 
-the molecular ISM of the first galaxies.
-%Future higher resolution zoom-in simulations would certainly be useful to understand
-%the evolving dynamical properties of the lower-mass molecular structures in
-%galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
+While observations leveraging the combination of spatial-spectral imaging of
+multi-band continuum and spectral line emission are crucial, 
+we shown in this work that prototypical galaxies at the EoR with properties similar to \flower
+are expected to have molecular gas structures on sub-kpc scales; however, these are not 
+the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from 
+large-scale motions even in the dispersion dominated stage. 
+This results means that caution should be taken when interpreting observational data, albeit the impressive resolution and sensitivity that are unprecedented. 
+Careful consideration of large-scale motions is required when interpreting the observed data in order to understand the origin of star formation activity 
+in galaxies at EoR. 
+It is thus currently unclear whether \highz molecular gas structures are intrinsically more turbulent than those in the local ISM. 
+This will become clearer in the next few years as deep and high resolution imaging of molecular gas at \highz are obtained with ALMA and NOEMA.
+
+On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
+statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining 
+and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
 These predictions can in turn be 

### 2019-04-26 WRITEUP/ms.tex
polish sec 7

@@
 where energy quickly dissipates. % with low virial parameters.
-This is consistent with the notion that collapsing structures resulting from
-gravitational instability occur within globally stable structures, which are
+This is consistent with the notion that collapsing structures result from
+gravitational instability occuring within globally stable structures, which are
 supported by turbulence and rotation on large scale.
@@
 multi-band continuum and spectral line emission are crucial, 
-we shown in this work that prototypical galaxies at the EoR with properties similar to \flower
+we show in this work that prototypical galaxies at the EoR with properties similar to \flower
 are expected to have molecular gas structures on sub-kpc scales; however, these are not 
 the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from 
-large-scale motions even in the dispersion dominated stage. 
-This results means that caution should be taken when interpreting observational data, albeit the impressive resolution and sensitivity that are unprecedented. 
-Careful consideration of large-scale motions is required when interpreting the observed data in order to understand the origin of star formation activity 
-in galaxies at EoR. 
-It is thus currently unclear whether \highz molecular gas structures are intrinsically more turbulent than those in the local ISM. 
-This will become clearer in the next few years as deep and high resolution imaging of molecular gas at \highz are obtained with ALMA and NOEMA.
-
+large-scale motions even in a highly disturbed stage.
+This means that caution should be taken when interpreting observational data, 
+albeit the impressive resolution and sensitivity that are unprecedented. 
+%Careful consideration of large-scale motions is required 
+%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR. 
+It is thus currently unclear whether \highz molecular gas structures are truly intrinsically more turbulent than those in the local ISM. 
+This will become clearer in the next few years as deeper and higher resolution imaging of 
+molecular gas at \highz are observed with ALMA and NOrthern Extended Millimeter Array (NOEMA). 
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
@@
 and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
-These predictions can in turn be 
-tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
-enabling us to test our findings and refine future simulations to shed light on the physical processes behind
-\SF since the cosmic dark ages.
+%These predictions can in turn be 
+%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
+%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
+%\SF since the cosmic dark ages.
 

### 2019-04-29 WRITEUP/ms.tex
non-thermal energy model specified

@@
 \begin{equation}
-\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma^2}{\pi G \Sigma R}\,,
+\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma_{\rm gas}^2}{\pi G \Sigma R}\,,
 \label{eqn:alpha}
@@
 
-Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma^2/R\propto\Sigma$.
+Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$.
 Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
@@
 \begin{equation}
-\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma^2 + M_{\star} \sigma_\star^2}
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
 					       {M_{\rm cl} + M_{\star} }\,,
@@
 \end{equation}
+
+\AP{shouldn t it be something like}
+\begin{equation}
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm cl} + M_{\star})} \frac{M_{\rm cl} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
+					       {M_{\rm cl} + M_{\star} }\,,
+\label{eqn:alpha_tot}
+\end{equation}
+\AP{? Additionally, I am still unsure if the stellar dispersion should give a contribution to the alpha parameter.}
+
 where $M_\star$ is the stellar mass within the MCC volume.
@@
 In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively.
-%mm
-    Heuristically, the instability can be understood by considering the scale
- at which gravitational potential overcomes the internal energy. Gravity dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, 
-%mm centrifugal forces resulting from
-   shearing by 
-differential rotation in disk galaxies can stabilize perturbations 
-%mm even on these scales. 
-    that might otherwise collapse for $L > L_{\rm rot}$, where $L_{\rm rot}$ is set by $\kappa$.
-%mm As a result, a disk is thought to be unstable on
-    As a result, disks are unstable to gravitational collapse on 
-scales between $L_J < L < L_{\rm rot}$.
+Heuristically, the instability can be understood by considering the scale at which gravitational potential overcomes the internal energy.
+Gravity dominates at scales $L > L_J$, where $L_J$ is the Jeans length.
+However, differential rotation in disk galaxies can stabilize perturbations that might otherwise collapse for $L > L_{\rm rot}$, where $L_{\rm rot}$ is set by $\kappa$.
+As a result, disks are unstable to gravitational collapse on scales between $L_J < L < L_{\rm rot}$.
 
@@
 \end{equation}
-The equivalent parameter for a collisional gas was derived by
-%mm [corrected from Toomre64a to Goldreich65a (not Goldreich65b, which is about spiral arm formation)]
-    \citep{Goldreich65a}
+The equivalent parameter for a collisional gas was derived by \citet{Goldreich65a}
 \begin{equation}
@@
 In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
-%mm  In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy
-     A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion
-$v_{\rm circ}/\sigma_{\rm disk}$
-%mm , i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} \MM{see above} ratio 
-\citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
+A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
 % https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
 %
-% from linear analysis
 
@@
 %
-In particular, it uses a modified version of \ncode{ramses}
-\citep{Teyssier02a} as the AMR backend. The simulation used here
-covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation
-zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. The Lagrangian
-region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter
-%mm (equivalent baryonic) 
-mass resolution of $\simeq 6\times 10^4 \Msun$, 
-%mm ($1.2 \times 10^4 \Msun$) [expanded out the meaning, but check if
-%I have it right]  Such
-     equivalent at initial density to a baryonic mass resolution of $1.2
-     \times 10^4 \Msun$.  This 
-region is spatially refined with a quasi-Lagrangian criterion based on
-a mass threshold, so that a cell is refined if its total dark matter
-plus baryonic mass exceeds the mass resolution by a factor of
-eight. The final finest refined cell in the zoom in region has size
-$l_{\rm cell}\simeq$\,30\,pc (at $z = 6$). 
-%mm
-%    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
-%    local density, which would have to be specified here.} \AP{the setting description has been extended}
-     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
-%mm 
-%     \MM{Nota Bene!} \AP{This note is discussed in details in the following section.
-In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
-The models include a chemical network 
-following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and
-H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is
-that abundances are calculated using an on-the-fly non-equilibrium
-formation of molecular hydrogen scheme  
-%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
-    described by \citet{Pallottini17a}.
-
-% radiative feedback --> NT pressure
+In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend.
+The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size.
+The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$.
+The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
+This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceedes the mass resolution by a factor of eight.
+The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e.
+sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
+The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}.
+Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
+
 Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe)
-%mm and OB/AGB stars. 
-   as well as winds from OB and asymptotic giant branch stars.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
 Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
@@
 Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
-\DL{AP: please elaborate non-thermal pressure here..}
-Photoionization from local sources is neglected in this simulation
-\citep[see][for its effect]{pallottini:2019,decataldo:2019}.
-
-The simulation zooms in on a galaxy named after the flower 
-\flower whose properties are given in 
-%mm \citet{Pallottini17b} 
-      \citet{Pallottini17a} 
-and are briefly summarized in the following. \flower is a Lyman-break galaxy 
-that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm
-  DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and
-accretes mass from the IGM mainly via three filaments of length
-$\simeq$\,100\,kpc. \flower has a stellar mass of
-$M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of
-$Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm
-  H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne. 
-%mm \MM{What is its gas fraction?  I ask because its molecular gas
-%mass is minuscule, particularly for such a high SFR: this is a
-%depletion time of only 0.5 Myr, while modern galaxies usually have
-%depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very
-%flickering and depends on which radius we are considering, as the
-%galaxy is actively accreating material and merging; depletion time
-%are low, see the ssfr note added considering that $ssfr \propto
-%t_{depletion}^{-1}$} 
-The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star}
-\simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$
-relation observed at high redshift \citep{Jiang2016}, which is higher
-than normal local galaxies. The effective stellar radius of \flower
-is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm
-  200}\simeq$\,15\,kpc.
+Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}.
+
+Note that in the simulation the gas acquire energy from feedback processes in both thermal and non-thermal form \citep{agertz:2013}, with the latter being a term that mimics unresolved turbulence; the non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{maclow1999turb}; see \citet{Pallottini17b} for further details.
+
+The simulation zooms in on a galaxy named after the flower \flower whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following.
+\flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+\flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
+%
+The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang2016}, which is higher than normal local galaxies.
+The effective stellar radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 

### 2019-04-29 WRITEUP/ms.tex

@@
    cloud complexes (MCCs) 
-that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
 %
@@
 %
-Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm cl}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
+Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
 %mm Neglecting magnetic field and 
@@
 \begin{equation}
-\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm cl} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm cl}^2}{R}\,,
+\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm gas} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm gas}^2}{R}\,,
 \label{eqn:virial}
@@
 \begin{equation}
-\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm cl}} = \frac{5\sigma_{\rm gas}^2}{\pi G \Sigma R}\,,
+\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm gas}} = \frac{5\sigma_{\rm gas}^2}{\pi G \Sigma R}\,,
 \label{eqn:alpha}
@@
 \begin{equation}
-\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm cl} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
-					       {M_{\rm cl} + M_{\star} }\,,
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
+					       {M_{\rm gas} + M_{\star} }\,,
 \label{eqn:alpha_tot}
@@
 \begin{equation}
-\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm cl} + M_{\star})} \frac{M_{\rm cl} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
-					       {M_{\rm cl} + M_{\star} }\,,
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
+					       {M_{\rm gas} + M_{\star} }\,,
 \label{eqn:alpha_tot}
 \end{equation}
-\AP{? Additionally, I am still unsure if the stellar dispersion should give a contribution to the alpha parameter.}
+\AP{? Additionally, I am still unsure if the stellar dispersion should give a contribution to the alpha parameter, naively I would write it as}
+\begin{equation}
+\alpha_{\rm vir, tot} \equiv \frac{5 R \sigma_{\rm gas}^2}{G (M_{\rm gas} + M_{\star})}
+\label{eqn:alpha_tot}
+\end{equation}
 
@@
 
-The onset of gravitational instability is 
-%mm considered to be 
-tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}. 
-%mm [rearranged to put derivation before result]
-For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
+The onset of gravitational instability is tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
+For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by \AP{there might be too many $\sigma$}
 \begin{equation}
@@
 
-In our stability analysis, we account for the combined effect of gas and stars 
-%mm 
-     \citep[derived exactly by][]{Rafikov01}, 
-and for the non-negligible disk thickness. This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
+In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01}, and for the non-negligible disk thickness.
+This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
 %
@@
 \end{equation}
-Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to
-maintain 
-stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 
-0.67 \citep{Goldreich65a}.
+Conceptually, the finite disk thickness reduces the gravity in the vertical direction, thereby making it easier for a system to maintain stability, and thus lowering the critical Toomre $Q_{\rm crit}$ from $\simeq$\,1 to 0.67 \citep{Goldreich65a}.
 %
@@
 \section{Numerical Simulations}\label{sec:sim}
-The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
+The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are briefly summarized here.
 %
@@
 The remaining energy is injected into the ISM in kinetic and thermal energy forms.
-Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).
+Radiation pressure on dust and gas is also included.
 Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}.
-
-Note that in the simulation the gas acquire energy from feedback processes in both thermal and non-thermal form \citep{agertz:2013}, with the latter being a term that mimics unresolved turbulence; the non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{maclow1999turb}; see \citet{Pallottini17b} for further details.
+%
+Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{agertz:2013}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{maclow1999turb}.
+See \citet{Pallottini17b} for further details.
 
@@
 %mm [delete para break]
-The \SF history\footnote{Note that here the SFR is calculated based on
-  the stellar mass formed in the last 4 Myr within 3.5 kpc from the
-  galaxy center of mass. The SFR plotted in Figure 2 of
-  \citet{Pallottini17b} is a factor of two higher since there the SFR
-  accounts for the contribution from massive satellite galaxies within
-  the virial radius ($\approx$15\,kpc).} of \flower is shown in
-\Fig{SFH}.
+The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 4 Myr within 3.5 kpc from the galaxy center of mass.
+The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
 The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
 
-Given the stochastic nature of \flower in its star formation history, we mostly focus on
-two of its most extreme evolutionary stages in this work (see \Sec{singless}).
-These phases correspond to (a) an intensely accreting phase and
-(b) a starburst phase (\Fig{SFH}). We are interested in determining whether 
-MCC properties are sensitive to these different dynamical
-conditions. For completeness, we also show the scaling relations examined for the other evolutionary stages 
-traced in the simulation (see \Sec{ncut}). 
+Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
+%
+These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}).
+We are interested in determining whether MCC properties are sensitive to these different dynamical conditions.
+For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
+
 In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties 
@@
 Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies.
-The distinction between clumps and satellites is admittedly somewhat
-ambiguous, though, and we consider it only as a working one.
+The distinction between clumps and satellites is admittedly somewhat ambiguous, though, and we consider it only as a working one.
 
@@
 
-To identify the molecular complexes, we use a customized version of
-the clump-finding algorithm available in the \ncode{python} package
-\ncode{yt} \citep{Turk11a}, which was initially described in
-\citet{Smith09a}, 
-%mm but this function has been modified since then.
-     and modified since.
-The latest version of the default \ncode{yt} clump finder decomposes
-the zones of the simulation into non-overlapping tiles, which are
-stored in a 
-%mm $k$-dimensional tree ($k$-D tree). [unused acronym]
-     three-dimensional tree that can be processed using $k$-dimensional tree algorithms.
-It then identifies the contours of a variable field (here, the density
-field) within a tile and connects them across the tiles. In the
-customized version used for this study, we
-%mm modify the function to enhance 
-     enhanced
-the stability of the code.
+To identify the molecular complexes, we use a customized version of the clump-finding algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk11a}, which was initially described in \citet{Smith09a} and modified since.
+%
+The latest version of the default \ncode{yt} clump finder decomposes the zones of the simulation into non-overlapping tiles, which are stored in a three-dimensional tree that can be processed using $k$-dimensional tree algorithms.
+It then identifies the contours of a variable field (here, the density field) within a tile and connects them across the tiles.
+In the customized version used for this study, we enhanced the stability of the code.
 %
@@
 
-In the clump-finding process (in position-position-position space; PPP), we employ a set of different density
-thresholds defined based on the molecular hydrogen density of \flower
-at different evolutionary stages ($z=6.0$--7.2).
-%
-We note that this process is 
-the three-dimensional analog
-to identifying molecular structures based on the noise levels 
-     in position-position-velocity (PPV) maps that
-observers obtain with telescopes, using molecular line tracers such as
-CO, CS, and HCN.
-%mm , as commonly adopted in observational studies (e.g., 
+In the clump-finding process (in position-position-position space; PPP), we employ a set of different density thresholds defined based on the molecular hydrogen density of \flower at different evolutionary stages ($z=6.0$--7.2).
+%
+We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN.
 This is commonly done by
@@
 %We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
-Existing studies find a good correspondence in the dynamical
-properties extracted in PPV- versus PPP-space 
-%mm
-   for well-isolated structures 
-(\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see
-%mm
-    \citealt{Ballesteros-Paredes02a} and 
-\citealt{Shetty10a} for a discussion on caveats and limitations).
+Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
 % large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
@@
 
-In \Fig{h2density}, we show the distribution of H$_2$
-number density $n_{\rm H2}$ for \flower~ during its accreting phase,
-including the contribution from the gas within 3.5 kpc from the
-galaxy center. 
-%
-We note that the distribution is almost flat for $n_{\rm
-  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
-are found based on morphological analysis\footnote{For $n_{\rm
-    H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$
-  density field is significantly larger than zero. This implies that
-  the field is made of isolated components. See Fig. 6 in
-  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
-applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
-    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
-6.81, 11.36, 18.96, 31.62]$ to each snapshot. 
-We also tested variations in
-  $n_{\rm cut}$ range and found no qualitative differences (see
-  \Sec{ncut}).
-%mm
-\MM{I am confused how H$_2$ can survive at such low number
-  densities.  Is there some sort of hidden clumping factor at work
-  here? Or is this due to the neglect of local photodissociating
-  radiation? Either way, the point should be mentioned in section 3, I
-guess.}
-\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
- what one expects for purely H2 regions. No clumping factor.}
-
-To visually display 
-the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
-Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
+In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower~ during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
+%
+We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$ density field is significantly larger than zero.
+This implies that the field is made of isolated components.
+See Fig.
+6 in \citet{Pallottini17b}.} \citep{Pallottini17b}.
+%
+In each evolutionary stage, we identify MCCs by applying density cuts to the H$_2$ density distriution, i.e.
+$n_{\rm H2}\geq n_{\rm cut}$.
+We select 10 equally-spaced cuts in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
+We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
+Note that with these choice we are including in the MCC also material that is not fully molecular ($n = 0.5 n_{\rm H2}$).
+
+To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
+Since the molecular structures are identified in the 3D H2 density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
 %
@@
 
-Note that we impose the additional constraint that an identified
-structure must be composed of at least 10 cells. We caution that an
-important caveat of such a constraint is that we can only examine the
-parameter space of cloud complexes of 
-radius $R\gtrsim 40$\,pc,
-because of the resolution limit of the simulation.
+We impose the additional constraint that an identified structure must be composed of at least 10 cells.
+We caution that an important caveat of such a constraint is that we can only examine the parameter space of cloud complexes of radius $R\gtrsim 40$\,pc, because of the resolution limit of the simulation.
 
@@
 
-% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
-% the mechanisms and physics of formation and evolution of molecular structures and \SF.
-Upon identifying the molecular structures, we extract properties such
-as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
-$\mathcal{M}$, velocity dispersion $\sigma$
-, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.
+Upon identifying the molecular structures, we extract properties such as the gas mass $M_{\rm gas}$, effective size $R$, Mach number
+$\mathcal{M}$, velocity dispersion $\sigma_{\rm gas}$, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.
 
@@
 $R \equiv (3 V /4 \pi)^{1/3}$.
-The full velocity dispersion of MCCs is calculated from 
-the bulk velocity field $\sigma_{\rm bulk}$, non-thermal velocity dispersion $\sigma_{\rm NT}$, and thermal sound speed $c_s$, following
-\begin{equation}
-\sigma^2 = \sigma_{\rm NT}^2 + \sigma_{\rm bulk}^2 + c_s^2.
+%
+The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
+\begin{equation}
+\sigma{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
 \label{eqn:veldisp}
@@
 %
-In \obs of MCCs, the linewidth contribution of dense gas 
-exceeds that from the diffuse gas. We therefore calculate each term on
-the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. 
-For instance, the bulk velocity dispersion is calculated as follows
+In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
+We therefore calculate each term on the right-hand side of Equation~\ref{eqn:veldisp} as a mass-weighted quantity.
+%
+The bulk velocity dispersion is then
 \begin{equation}
@@
 \end{equation}
-where the sum is done for the cells composing each MCC.
-Similarly, the non-thermal velocity dispersion is calculated as follows
-\begin{equation}
-\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,
-\end{equation}
-and the thermal sound speed is calculated through
-\begin{equation}
-%        x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.avg_density
-c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~k_B / M_p / {\bar \rho_i} \right)^2}{\sum_i \rho_i}\,,   % so that cs^2 has dimension of [erg/g]
-\end{equation}
-where $P_{\rm NT, i}$ and $P_i$ are the non-thermal and thermal pressures of cell $i$ in units of [K\,\cc], respectively, $k_B$ is the Boltzmann constant, and 
-$M_p$ is the mass of a proton.
-
-The local sound speed of all identified molecular complexes is much
-smaller than their turbulent velocities\footnote{Velocity dispersions
-  calculated from velocity field are comparable to those calculated
-  from the pressure field 
-    \MM{The turbulent pressure field has not been
-    mentioned in section 3, so you'll need to add a sentence there
-    mentioning its presence and behavior to mention it here}, 
-    \DL{AP: also mention turbulent pressure found for the bulk of dense gas in the simulation in the phase-space analysis presented in \citet{Pallottini17a} here?}
-indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially 
-at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}. 
-We compute the Mach number from turbulent and thermal pressures following
-\begin{equation}
-\mathcal{M} \equiv \sqrt{\frac{P_{\rm NT} + P}{ P }}.
+where the sum is done for the cells composing each MCC\footnote{Since we are calculating quantities on unigridded data, mass-weighted averages can be written as density weighted averages}.
+%
+The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
+\begin{equation}
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the pressure is in units of [K\,\cc], $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
+Similarly, the contribution from the non-thermal energy is calculated from the non-thermal pressure ($P_{\rm NT}$) as follows
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,.
+\end{equation}
+%
+Finally, the Mach number can expressed as follows
+\begin{equation}
+\mathcal{M} \equiv \frac{\sum_{i} \rho_i \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}}}{\sum_{i} \rho_i}.
 \label{eqn:MPress}
 \end{equation}
-On average, the Mach number of the MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$,
+\AP{in the following two paragraphs we are mixing results and expectations. The might be moved to th result section}
+As the non-thermal pressure contribution dominates the thermal one for dense gas \citet{Pallottini17b}, the local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, i.e.
+$c_s^2 \ll \sigma_{\rm NT}^2$.
+In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds $\mathcal{M} \sim 10$ for \flower.
+%
+Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to showw the point?}, but this depends on the evolutionary stage of \flower.
+%
+%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.
+
 % allss: 0.32 
@@
 %  5.05517168  6.93886988  5.4830306 ]
-but this depends on the evolutionary stage of \flower.  % see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
+% see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
 % This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
 
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to 
-a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, 
-we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following. 
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following.
 We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
 \begin{equation}
-f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)}.
+f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
 \end{equation}
@@
 %
-The most massive ($M_{\rm cl}>$10$^8$\,\Msun) 
-cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist})  
-corresponds to the molecular disk of the
-galaxy, which is identified as a single component for low $n_{\rm
-  cut}$. Overall, the mass of all MCCs identified ranges between $M_{\rm
-  cl}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in
-\z$\sim$2 galaxies in rest-frame UV and optical light
-\citep{Elmegreen07a, Elmegreen09a}. 
-The stellar-to-gas mass ratio ranges between $M_{\star}/M_{\rm cl} \simeq$\,0.1\,--\,100 over all the
-MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}). 
+The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
+%
+Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
 The main disk occupying the top right corner of \Fig{stellarRatio16} has a stellar-to-gas mass ratio of $\simeq$\,50--100.
@@
 The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) as they correspond to a large part of \flower, and thus, 
-include a large number of stellar mass already ensembled in \flower. 
+include a large number of stellar mass already ensembled in \flower \AP{please change $M_{cl}$ to $M_{\rm gas}$ in the figure}. 
 \label{fig:stellarRatio16}}
@@
 \begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
 \end{equation}
@@
 %The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
-%the $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
 5 therein]{Behrens18a}
@@
 
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm cl}$, 
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$, 
 $\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
@@
 We extract properties such as mass, size, Mach number, velocity
-dispersion, gas surface density, and virial parameter ($M_{\rm cl}, R, \mathcal{M}, 
+dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, 
 \sigma, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.

### 2019-04-29 WRITEUP/ms.tex
Updates from Overleaf
uniforming notation; per fig. comments added

@@
 \begin{equation}
-\sigma{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
+\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
 \label{eqn:veldisp}
@@
 In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
-We therefore calculate each term on the right-hand side of Equation~\ref{eqn:veldisp} as a mass-weighted quantity.
-%
-The bulk velocity dispersion is then
-\begin{equation}
-\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
-\end{equation}
-where the sum is done for the cells composing each MCC\footnote{Since we are calculating quantities on unigridded data, mass-weighted averages can be written as density weighted averages}.
+Therefore, when calculating global quantities for MCS, we always perform a mass-weighting.
+Since we operate on data on a unigrid, this is equivalent to density averaged quantities.
+In general, for the quantity $x$ in a MCC we write
+\begin{equation}\label{eqn:defineaverage}
+\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
+\end{equation}
+where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
+%
+The bulk velocity dispersion is
+\begin{equation}
+\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
+\end{equation}
 %
@@
 \begin{equation}
-c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
+c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
 \end{equation}
@@
 \begin{equation}
-\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,.
-\end{equation}
-%
-Finally, the Mach number can expressed as follows
-\begin{equation}
-\mathcal{M} \equiv \frac{\sum_{i} \rho_i \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}}}{\sum_{i} \rho_i}.
+\sigma_{\rm NT}^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n} \right)^2 \right\rangle\,.
+\end{equation}
+%
+It is also convenient to write the Mach number
+\begin{equation}
+\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
 \label{eqn:MPress}
@@
 The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
-The main disk occupying the top right corner of \Fig{stellarRatio16} has a stellar-to-gas mass ratio of $\simeq$\,50--100.
+The main disk occupying the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
 
@@
 \caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
-The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) as they correspond to a large part of \flower, and thus, 
+The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
 include a large number of stellar mass already ensembled in \flower \AP{please change $M_{cl}$ to $M_{\rm gas}$ in the figure}. 
@@
 The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
-gas in equilibrium, see Equation~\ref{eqn:v0}.
+gas in equilibrium, see Equation~\ref{eqn:v0}. \AP{$\sigma$ should be $\sigma_{\rm gas}$}
 \label{fig:larsons_single}}
@@
 Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
-relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
+relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF \AP{please change y label to $M_{\rm gas}$; note that in Fig.
+\ref{fig:dist} R instead of cloud size is used; we have to pick one}.
 \label{fig:MR}}
@@
 Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
-MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{please change x label to $M_{\rm gas}$; note that this plot seems a bit redundant}
 \label{fig:alphaEvol}}
@@
 The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher 
-density thresholds (top right panel).
+density thresholds (top right panel). \AP{please change x labels of the middle panels to $M_{\rm gas}$; $\sigma$ should be $\sigma_{\rm gas}$}
 \label{fig:alpha16-28}}
@@
 some of them (see \Fig{stellarRatio16}). 
-MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
+MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
 \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
@@
 %
-For instance, in local ULIRGs, MCCs are likely formed
-by shock compression and cloud-cloud collisions 
- that funnel large amounts of gas from the progenitor galaxies
- towards the central region
-\citep{Tan00a, Wu18a}.
+For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
 % Tasker09a
-On the other hand, the highly turbulent structures of \flower likely result from 
-extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
-The presence of such extra-planar flows may \MM{Do we have any
-  evidence for or against this speculation? Clarify citations and
-  mergers vs accretion...} also be the 
-dominant mode for forming the highly supersonic massive MCCs observed
-in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
-\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
-high due to the resolution limit.
+On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and to higher velocity the accretion/SN-driven outflows \citep{gallerani:2018}.
+The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.
 
@@
 should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
+\AP{to guide the eye, I would draw the $x=y$ line in both panels}
 % either higher resolution, or properly accounting for large scale motions. 
@@
 At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and 
-form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. \AP{$\rho \rightarrow n$; this should stay close to Fig. \ref{fig:MR}}
 \label{fig:rho}}

### 2019-05-10 WRITEUP/ms.tex
minor edits on plane

--- 2019-04-29 WRITEUP/ms.tex
@@
 \end{equation}
-\AP{? Additionally, I am still unsure if the stellar dispersion should give a contribution to the alpha parameter, naively I would write it as}
 \begin{equation}
@@
 The onset of gravitational instability is tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by \AP{there might be too many $\sigma$}
+For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
 \begin{equation}
@@
 To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
-Since the molecular structures are identified in the 3D H2 density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
+Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
 %
@@
 \begin{equation}
-c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
-\end{equation}
-where the pressure is in units of [K\,\cc], $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
-Similarly, the contribution from the non-thermal energy is calculated from the non-thermal pressure ($P_{\rm NT}$) as follows
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_{{\rm TH}, i}~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
+Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
 \begin{equation}
@@
 %
-Finally, the Mach number can expressed as follows
+Finally, the Mach number is related to the pressure terms as follows
 \begin{equation}
@@
 \end{equation}
-\AP{in the following two paragraphs we are mixing results and expectations. The might be moved to th result section}
-As the non-thermal pressure contribution dominates the thermal one for dense gas \citet{Pallottini17b}, the local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, i.e.
-$c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds $\mathcal{M} \sim 10$ for \flower.
-%
-Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to showw the point?}, but this depends on the evolutionary stage of \flower.
+
+\section{Results}\label{sec:results}
+
+\subsection{Distributions of MCC Basic Properties}
+
+The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, 
+as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
+ In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
+%
+Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to show the point?}\DL{This is currently shown in \Fig{vv}}, but this depends on the evolutionary stage of \flower.
 %
@@
 
-\section{Results}\label{sec:results}
-
 \begin{figure*}
@@
 reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-The gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
 %% 

### 2019-05-10 WRITEUP/ms.tex

--- 2019-04-29 WRITEUP/ms.tex
@@
 \begin{equation}
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_{{\rm TH}, i}~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
 c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
 \end{equation}
-where the pressure is in units of [K\,\cc], $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
-Similarly, the contribution from the non-thermal energy is calculated from the non-thermal pressure ($P_{\rm NT}$) as follows
+where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
+Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
 \begin{equation}
@@
 %
-It is also convenient to write the Mach number
+Finally, the Mach number is related to the pressure terms as follows
 \begin{equation}
@@
 \end{equation}
-\AP{in the following two paragraphs we are mixing results and expectations. The might be moved to th result section}
-As the non-thermal pressure contribution dominates the thermal one for dense gas \citet{Pallottini17b}, the local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, i.e.
-$c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds $\mathcal{M} \sim 10$ for \flower.
-%
-Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to showw the point?}, but this depends on the evolutionary stage of \flower.
+
+\section{Results}\label{sec:results}
+
+\subsection{Distributions of MCC Basic Properties}
+
+The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
+as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
+ In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
+%
+Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to show the point?}\DL{This is currently shown in \Fig{vv}}, but this depends on the evolutionary stage of \flower.
 %
@@
 reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-The gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
+The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
 %%

### 2019-05-10 WRITEUP/ms.tex
merge
typos
up to sec 5

@@
 \begin{equation}
-\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm gas} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm gas}^2}{R}\,,
+\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
 \label{eqn:virial}
@@
 \begin{equation}
-\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
-					       {M_{\rm gas} + M_{\star} }\,,
-\label{eqn:alpha_tot}
-\end{equation}
-
-\AP{shouldn t it be something like}
-\begin{equation}
 \alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
@@
 \end{equation}
-\begin{equation}
-\alpha_{\rm vir, tot} \equiv \frac{5 R \sigma_{\rm gas}^2}{G (M_{\rm gas} + M_{\star})}
-\label{eqn:alpha_tot}
-\end{equation}
-
 where $M_\star$ is the stellar mass within the MCC volume.
+\DL{Should we leave out $\sigma_{\star}$ since stellar motions shouldn't affect the gas?}
 
@@
 
-In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower~ during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
+In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
 %
@@
 %
-In each evolutionary stage, we identify MCCs by applying density cuts to the H$_2$ density distriution, i.e.
-$n_{\rm H2}\geq n_{\rm cut}$.
-We select 10 equally-spaced cuts in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
-We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
-Note that with these choice we are including in the MCC also material that is not fully molecular ($n = 0.5 n_{\rm H2}$).
+In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs 
+are selected at $n_{\rm cut} \leq n_{\rm H2}$.
+We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
+% We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}). 
+Note that with these choice we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
 
@@
 \begin{equation}
-c_s^2 = \frac{\sum_{i} \rho_i \left(P_{{\rm TH}, i}~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
 c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,

### 2019-05-10 plot_modules/plot_cloud_prop.py
Mcl to Mgas, cloud size to R

@@ -19,7 +19,7 @@ def setup_plot():
     # print(matplotlib.matplotlib_fname())
 
     matplotlib.rcParams.update({'figure.figsize': (8, 5)    # inches
-                                , 'font.size': 16      # points
+                                , 'font.size': 18      # points
                                 , 'legend.fontsize': 10      # points
                                 , 'lines.linewidth': 2       # points
                                 , 'axes.linewidth': 1       # points
@@ -33,8 +33,8 @@ def setup_plot():
                                 , 'ytick.major.size': 13     # length, points
                                 , 'ytick.major.width': 1     # points
                                 , 'ytick.minor.size': 8     # length, points
-                                , 'xtick.labelsize': 14
-                                , 'ytick.labelsize': 14
+                                , 'xtick.labelsize': 16
+                                , 'ytick.labelsize': 16
                                 , 'ytick.minor.width': 1     # points
                                 , 'font.serif': ("times", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
                                 })
@@ -162,9 +162,11 @@ def unpack_xy(ss):
     return to_plot
 
 
-def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10, marker='*',
+def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
+               marker='*',
                leglabel='', tag='',
                to_plot=None, save=True, outdir='./',
+               legendFontSize=10,
                showLegend=True,
                sfrlabel=False):
     """
@@ -181,9 +183,12 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10, marker='
[…]

### 2019-05-10 plotsingleSS.py

@@ -44,58 +44,58 @@ def load_pickleTOplot(snapshot_num, pattern=None):
     return ss, to_plot, leafdir_out
 
 
-def plotting_procedure(snapshot_num):
+def plotting_procedure(snapshot_num, legendFontSize=13):
     from plot_modules.plot_cloud_prop import plot_stuff, plot_stuff_3dim
 
     ss, to_plot, leafdir_out = load_pickleTOplot(snapshot_num)
 
     plot_stuff("stellar to gas mass", "cloud mass", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("stellar to gas mass", "alpha vir", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("stellar to gas mass", "Mach", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("gas sd per ff", "sfr sd", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)    # SK
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff('gas sd cgs', 'sigmaSq over size', leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff('alpha vir', 'sigmaSq over size', leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("alpha vir", "SFR young", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("cloud mass", "mass over jeans mass",
-               leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out)
[…]

### 2019-05-10 plot_modules/plot_cloud_prop.py
hide legend for sigma-sigma plot

@@ -577,7 +577,9 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
                          label="SFR: " + "{0:d}".format(int(sfr[ks])),
                          markeredgecolor='gray',
                          markeredgewidth=0.5)
-            legend_h.append(h)
+            # uncomment below to get ncut in legend
+            # for paper, we commented this out since we show it as colorbar in other figures.
+            # legend_h.append(h)
 
         else:
             if xstr == "gas sd per ff" and ystr == "sfr sd":
@@ -590,6 +592,8 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
                          markeredgecolor='gray',
                          markeredgewidth=0.5)
 
+            # uncomment below to get ncut in legend
+            # for paper, we commented this out since we show it as colorbar in other figures.
             # legend_h.append(h)
 
 
@@ -669,7 +673,7 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
 
         if xstr == "sigma kms NT":
             # 1-1 line
-            xx = np.arange(np.min((_x, _y)), np.max((_x, _y)))
+            xx = np.arange(1., 500.)
             h, = ax.plot(xx, xx, ls='--',
                          label='', lw=2, color='k')
 

### 2019-05-10 plotsingleSS.py

@@ -86,23 +86,23 @@ def plotting_procedure(snapshot_num, legendFontSize=13):
     plot_stuff("R2 pc2", "cloud mass", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("size pc", "cloud mass", leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out, legendFontSize=12)
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=10)
     plot_stuff("cloud mass", "Mach", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("size pc", "weighted density",  leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff('sigma kms NT', 'sigma kms bulk', leglabel="ncut: ",
-               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
+               to_plot=to_plot, outdir=leafdir_out, showLegend=False)
 
     plot_stuff_3dim("tff Myr", "size pc", "cloud mass",
                     leglabel="ncut: ", to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
 
-    # from plot_modules.plot_cloud_prop import get_masses_all_clouds, massFuncUnbinnedCDF, massFuncPDF, massFuncDifferential
-    # allmass = get_masses_all_clouds(ss)
-    # tag = 'ss' + str(snapshot_num) + 'diffncuts'
-    # massFuncUnbinnedCDF(allmass, outdir=leafdir_out, tag=tag)
-    # massFuncPDF(allmass, outdir=leafdir_out, tag=tag)
-    # massFuncDifferential(allmass, outdir=leafdir_out, tag=tag)
+    from plot_modules.plot_cloud_prop import get_masses_all_clouds, massFuncUnbinnedCDF, massFuncPDF, massFuncDifferential
+    allmass = get_masses_all_clouds(ss)
+    tag = 'ss' + str(snapshot_num) + 'diffncuts'
+    massFuncUnbinnedCDF(allmass, outdir=leafdir_out, tag=tag)
+    massFuncPDF(allmass, outdir=leafdir_out, tag=tag)
+    massFuncDifferential(allmass, outdir=leafdir_out, tag=tag)
 
 
 

### 2019-05-10 WRITEUP/ms.tex
consistent notation in figures

@@
 \begin{equation}
-c_s^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right)^2 \right\rangle\,,
+c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
 \end{equation}
@@
 \begin{equation}
-\sigma_{\rm NT}^2 = \left\langle \left( \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n} \right)^2 \right\rangle\,.
+\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
 \end{equation}
@@
 \subsection{Distributions of MCC Basic Properties}
+
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following.
+We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
+\end{equation}
+%
+We note that the distributions vary for different evolutionary stages of \flower.
+%
+The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
+%
+Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
+The main disk occupying the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
+The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
+include a large number of stellar mass already ensembled in \flower 
+\label{fig:stellarRatio16}}
+\end{figure}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
+\caption{Distributions of mass (left), size (middle), and gas mass
+  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
+  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
+ over all times analyzed here.
+Note that the scales shown on the $y$-axes are different between the top
+and bottom panels, as fewer MCCs are identified at higher $n_{\rm
+  cut}$.
+\label{fig:dist}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
+\caption{
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
+(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
+MCCs (star symbols) identified in the two most extreme evolutionary
+stages of \flower\ --- accreting phase (left) and starburst phase
+(right). Star symbols are color-coded by the density thresholds
+$n_{\rm cut}$, as illustrated by the colorbar.
+Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
+% black dot = extragalactic GMCs in quiescent environments
+Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
+from \citet{Larson81a, Heyer04a, Bolatto08a}.
+Data points in the $\alpha_{\rm vir}$-mass figure are taken from
+\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
+(see Fig 4 of \citealt{Kauffmann17b}).
+The gray dotted lines shown in the bottom panels correspond to the various external pressures for
+gas in equilibrium, see Equation~\ref{eqn:v0}.
+\label{fig:larsons_single}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
+\caption{
+Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+Star symbols are color-coded by
+increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
+Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
+Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
+Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
+constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
+%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
+%same as \Fig{larsons_single}.
+%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
+%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
+For interpretation of this figure, see discussion in \Sec{MR}.
+\label{fig:MR}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
+\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
+Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
+Definition of symbols are same as in \Fig{larsons_single}.
+Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
+The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
+the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
+post-starburst phase.
+The variation is clearly seen between the pre-starburst through post-starburst phase.
+Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
+MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+\label{fig:alphaEvol}}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
+\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
+Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
+identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
+The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
+density thresholds (top right panel).
+\label{fig:alpha16-28}}
+\end{figure*}
+
+\subsection{Single Evolutionary Stage}  \label{sec:singless}
+
+We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+
+Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$)
+and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies,
+such as the nearby gas-rich galaxy M64 and
+% Kennicutt, 1996IAUS..171...11K
+% Spiral gal, appears to have accreted a gas-rich companion in the recent past,
+% with the inner gas disk the remnant of the
+% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995).
+the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
+\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
+
+% middle
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are
+composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component
+(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of
+some of them (see \Fig{stellarRatio16}).
+MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of
+\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
+the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
+
+% PVE
+Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
+In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
+Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium
+to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
+Heyer+09).
+
+Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
+\citep{Larson81a, McKee07a}.
+Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
+which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
+the mass-size relation is also known as the constant column density relation and has been
+proposed as a fundamental property of molecular clouds on different physical scales.
+
+By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
+\begin{equation}
+A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+\end{equation}
+Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
+\begin{equation}\label{eqn:constantcolumndensity}
+M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+\end{equation}
+where we adopt $\mu = 2.5$ as the mean molecular weight.
+
+We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
+Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
+\citet{Lombardi10a} in the MW.
+Further discussions on the interpretation of this is provided in \Sec{MR}.
+%
+%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
+%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+5 therein]{Behrens18a}
+
+% Starburst
+Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes
+as those in the accreting phase; however, the MCCs in the starburst phase span
+a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
+Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
+(\Fig{alphaEvol}).
+Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
+the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
+This is consistent with our physical intuition of gas instability leading to \SF.
+
+\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
+
+We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the
+choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus,
+the results presented in \Sec{singless} dependent on the choice of density thresholds.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
+and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
+For instance, the cluster of points found at the lowest density threshold,
+occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
+are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
+typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
+These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel.
+In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
+
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been
+reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
+resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+However, the IGM and merger and accretion histories are not properly modeled in such simulations since
+they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
+reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
+%%
+%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
+%%
+%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%%
+This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
+nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
+
+%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold
+%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
+%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size
+%at increasing $n_{\rm cut}$.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
+We find no quantitative differences over the 700\,Myr traced in our simulation, except
+for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
+
+%--------------------------------------------------------------------------
+%                                Discussion
+%--------------------------------------------------------------------------
+\section{Discussions and Implications}\label{sec:diss}
+
+\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}
+
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$,
+$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
+Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
+linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to
+the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
+$z$\ssim2 spatially resolved studies of gas-rich star-forming
+galaxies, in terms of their velocity dispersions, sizes, and gas
+surface densities (\Fig{larsons_single}; see e.g.,
+\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
+and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+Their velocity dispersions are also comparable to those observed in the inner
+Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
+locus of $\sigma\propto R^{0.56}$.
+Such high velocity dispersions and surface densities can be explained partly because
+these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest,
+and also from the injection of kinetic energy from recent
+\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2,
+\flower has assembled a stellar mass of
+$M_\star$\eq7.5\E{9}\,\Msun.
+Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that
+the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in
+its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in
+interpreting observational results is further discussed in the next subsection (\Sec{rot}).
+
+The high pressure observed in \flower (see \citealt{Pallottini17a})
+is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
+This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+%
+For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
+% Tasker09a
+On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and higher velocity accretion/SN-driven outflows \citep{gallerani:2018}.
+The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.
+
+% different evolutionary stages
+In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences
+in the MCC properties with respect to those observed in the nearby Universe
+between the accreting and starburst phase of \flower (see
+\Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase.
+Similarly, the virial parameter is higher in the post-starburst phase compared to both the pre-\SB and \SB phases.
+This is expected for \SF to proceed.
+
+\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
+\caption{Gas velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
+quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
+quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
+the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
+This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
+should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM. 
+% either higher resolution, or properly accounting for large scale motions.
+\label{fig:vv}}
+\vspace{0.5em}
+\end{figure}
 
@@
  % 
-Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to show the point?}\DL{This is currently shown in \Fig{vv}}, but this depends on the evolutionary stage of \flower.
+ Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, 
+as the two are connected via the Euler equation, but this depends on the evolutionary stage of \flower (\Fig{vv}).
 %
@@
 
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following.
-We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
-\begin{equation}
-f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
-\end{equation}
-%
-We note that the distributions vary for different evolutionary stages of \flower.
-%
-The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
-%
-Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
-The main disk occupying the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
-The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
-include a large number of stellar mass already ensembled in \flower \AP{please change $M_{cl}$ to $M_{\rm gas}$ in the figure}.
-\label{fig:stellarRatio16}}
-\end{figure}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass
-  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
-  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
- over all times analyzed here.
-Note that the scalesshown on the $y$-axes are different between the top
-and bottom panels, as fewer MCCs are identified at higher $n_{\rm
-  cut}$.
-\label{fig:dist}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
-\caption{
-Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
-(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
-MCCs (star symbols) identified in the two most extreme evolutionary
-stages of \flower\ --- accreting phase (left) and starburst phase
-(right). Star symbols are color-coded by the density thresholds
-$n_{\rm cut}$, as illustrated by the colorbar.
-Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
-% black dot = extragalactic GMCs in quiescent environments
-Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
-from \citet{Larson81a, Heyer04a, Bolatto08a}.
-Data points in the $\alpha_{\rm vir}$-mass figure are taken from
-\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
-(see Fig 4 of \citealt{Kauffmann17b}).
-The gray dotted lines shown in the bottom panels correspond to the various external pressures for
-gas in equilibrium, see Equation~\ref{eqn:v0}. \AP{$\sigma$ should be $\sigma_{\rm gas}$}
-\label{fig:larsons_single}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
-\caption{
-Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
-Red line shows the
-mass-size relation found for regions in the Milky Way with massive \SF
-reported by \citet{Kauffmann10b}. Star symbols are color-coded by
-increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
-Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
-constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
-%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
-%same as \Fig{larsons_single}.
-Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
-relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF \AP{please change y label to $M_{\rm gas}$; note that in Fig.
-\ref{fig:dist} R instead of cloud size is used; we have to pick one}.
-\label{fig:MR}}
-%mm}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
-\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
-Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
-Definition of symbols are same as in \Fig{larsons_single}.
-Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
-The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
-the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
-post-starburst phase.
-The variation is clearly seen between the pre-starburst through post-starburst phase.
-Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
-MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{please change x label to $M_{\rm gas}$; note that this plot seems a bit redundant}
-\label{fig:alphaEvol}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
-Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
-identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
-density thresholds (top right panel). \AP{please change x labels of the middle panels to $M_{\rm gas}$; $\sigma$ should be $\sigma_{\rm gas}$}
-\label{fig:alpha16-28}}
-\end{figure*}
-
-\subsection{Single Evolutionary Stage}  \label{sec:singless}
-
-We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
-Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
-
-Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$)
-and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies,
-such as the nearby gas-rich galaxy M64 and
-% Kennicutt, 1996IAUS..171...11K
-% Spiral gal, appears to have accreted a gas-rich companion in the recent past,
-% with the inner gas disk the remnant of the
-% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995).
-the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
-\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
-
-% middle
-While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are
-composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component
-(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of
-some of them (see \Fig{stellarRatio16}).
-MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of
-\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
-This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
-the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
-
-% PVE
-Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
-In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
-Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium
-to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
-Heyer+09).
-
-Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
-\citep{Larson81a, McKee07a}.
-Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
-which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
-the mass-size relation is also known as the constant column density relation and has been
-proposed as a fundamental property of molecular clouds on different physical scales.
-
-By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
-\begin{equation}
-A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-\end{equation}
-Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
-\begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
-\end{equation}
-where we adopt $\mu = 2.5$ as the mean molecular weight.
-
-We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
-Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
-\citet{Lombardi10a} in the MW.
-%
-%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
-%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
-5 therein]{Behrens18a}
-
-% Starburst
-Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes
-as those in the accreting phase; however, the MCCs in the starburst phase span
-a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
-Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
-(\Fig{alphaEvol}).
-Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
-the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
-This is consistent with our physical intuition of gas instability leading to \SF.
-
-\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
-
-We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the
-choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus,
-the results presented in \Sec{singless} dependent on the choice of density thresholds.
-
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
-and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
-For instance, the cluster of points found at the lowest density threshold,
-occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
-are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
-that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
-typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
-These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel.
-In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
-
-We note that similarly massive molecular structures (few times 10$^7$\,\Msun) have been
-reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
-resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-However, the IGM and merger and accretion histories are not properly modeled in such simulations since
-they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
-reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
-%%
-%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
-%%
-%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%%
-This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
-nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
-
-%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold
-%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
-%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size
-%at increasing $n_{\rm cut}$.
-
-% temporal evolution in Cloud Dynamics
-We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
-We find no quantitative differences over the 700\,Myr traced in our simulation, except
-for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
-
-%--------------------------------------------------------------------------
-%                                Discussion
-%--------------------------------------------------------------------------
-\section{Discussions and Implications}\label{sec:diss}
-
-\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}
-
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$,
-$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
-Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
-linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to
-the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
-$z$\ssim2 spatially resolved studies of gas-rich star-forming
-galaxies, in terms of their velocity dispersions, sizes, and gas
-surface densities (\Fig{larsons_single}; see e.g.,
-\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
-and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
-Their velocity dispersions are also comparable to those observed in the inner
-Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
-locus of $\sigma\propto R^{0.56}$.
-Such high velocity dispersions and surface densities can be explained partly because
-these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest,
-and also from the injection of kinetic energy from recent
-\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
-In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2,
-\flower has assembled a stellar mass of
-$M_\star$\eq7.5\E{9}\,\Msun.
-Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that
-the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in
-its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in
-interpreting observational results is further discussed in the next subsection (\Sec{rot}).
-
-The high pressure observed in \flower (see \citealt{Pallottini17a})
-is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
-%
-For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
-% Tasker09a
-On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and to higher velocity the accretion/SN-driven outflows \citep{gallerani:2018}.
-The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.
-
-% different evolutionary stages
-In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences
-in the MCC properties with respect to those observed in the nearby Universe
-between the accreting and starburst phase of \flower (see
-\Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
-However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase.
-Similarly, the virial parameter is higher in the post-starburst phase compared to both the pre-\SB and \SB phases.
-This is expected for \SF to proceed.
-
-\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}
-
-\begin{figure}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
-quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
-quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
-The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
-the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
-This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
-should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
-\AP{to guide the eye, I would draw the $x=y$ line in both panels}
-% either higher resolution, or properly accounting for large scale motions.
-\label{fig:vv}}
-\vspace{0.5em}
-\end{figure}
-
 We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting
@@
 whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
+
+We note that \citet{Behrendt16a} similarly concluded that large scale bulk motion may mimic turbulent velocity dispersion 
+due to beam smearing even though the self-rotation of each individual sub-MCCs is washed out.
+
 {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
@@
 At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and
-form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. \AP{$\rho \rightarrow n$; this should stay close to Fig. \ref{fig:MR}}
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
+See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
+\AP{$\rho \rightarrow n$}
 \label{fig:rho}}
@@
 %-------------------------------------
-\acknowledgements
-
+% \acknowledgements
+
+\section*{Acknowledgements}
 We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.

### 2019-05-11 plot_modules/plot_cloud_prop.py
loci of rho and R

@@ -588,7 +588,7 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
 
             h, = ax.plot(_x, _y, ls=ls, markersize=markersize,
                          marker=marker,
-                         label=leglabel + ks,
+                         # label=leglabel + ks,         # don't show n cut in legend
                          markeredgecolor='gray',
                          markeredgewidth=0.5)
 
@@ -631,7 +631,39 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
         ax.set_xlim(1.0, 2.e3)
 
         if 'density' in ystr:
-            ax.set_xlim(50, 700)
+            ax.set_xlim(10., 700)
+            xx = np.arange(10., 500.)
+
+            from scipy.optimize import curve_fit as fit
+            logy = lambda x, a, b: a * np.log10(x) + b
+
+            # get normalization offset constant
+            xx = np.array([154.03388287747785,171.55142581874753,184.84825987587666])
+            yy = np.array([523.4370542322141, 499.14952519314403, 467.58350935283244])
+            popt, pcov = fit(logy, xx, np.log10(yy), p0=(-0.1, 10))
+
+            # sanity check
+            # ax.plot(xx, 10**logy(xx, *popt), 'r-', label='fit: a=%5.2f, b=%5.2f' %tuple(popt))
+
+            # plot loci of that
+            xx = np.arange(10.0, 700.)
+            # ax.plot(xx, 10**logy(xx, *popt), 'k--', label=r'$n \propto R^{{:.2f}}$'.format(popt[0]), linewidth=0.5)
+            # for i in np.linspace(3.5, 4.5, 5):
+            #     ax.plot(xx, 10**logy(xx, popt[0], i), 'k--', linewidth=0.5)
+
+            # ranges of index (-0.5 to -1.7) for different power law index in MR relation (M propto 1.3 to 2.5)
+            for i, ee in enumerate(np.linspace(2.5, 4.5, 10)):
+                if i == 0:
+                    ax.plot(xx, 10**logy(xx, -0.5, ee), 'k--', label=r"$n \propto R^{-1/2}$ (If Larson's: $M\propto R^{5/2}$)", linewidth=0.5)
+                else:
+                    ax.plot(xx, 10**logy(xx, -0.5, ee), 'k--', linewidth=0.5)
+
[…]

### 2019-05-11 WRITEUP/ms.tex
revisde

@@
 %mm rearranged sentence
-We study the properties of molecular cloud complexes (MCCs) in a cosmological zoom-in simulation of a
-prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
-%
-We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
-%
-In \flower, MCC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
+We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
+$z\simeq 6$ prototypical galaxy (``\flower'').
+%
+We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter 
+to \obs.
+%
+In \flower, MCC masses are in the range of $10^{5.5-8.5}$\,\Msun, with sizes $R\lesssim200$\,pc. 
+% 
+We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
+the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis. 
+MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
+instability to % gravitational 
+collapse.
+%
 Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
 % 
-We identify gravitationally unstable MCCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter
-%mm (gas+stars),
-    taking into account both gas and stars,
-and by using a more observationally accessible $\alpha_{\rm vir}$ analysis.
-We find that MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
-%mm
-    instability to gravitational
-collapse.
-%
-%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
-%higher gas mass fraction, surface density, and velocity dispersion.
-% , which together sets the scale for fragmentation.
-\AF{Abstract is a bit thin. Revise at the end}
-High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish
-%mm scrutinizing
-data to test our findings and shed light on \SF since the cosmic dark ages.
+We show that large-scale rotation is an important contributor to the velocity dispersion of MCCs, even in the highly disturbed phase of \flower, posing 
+a challenge to the interpretation of molecular gas dynamics in \highz galaxies in the literature.
+% Thus, velocity dispersions measured on similar scales (even down to 40\,pc) should not be taken as a direct 
+% evidence that \highz molecular gas are intrinsically more turbulent than the local ISM, 
+% unless contributions from bulk motions are properly accounted for.
+% 
+%Close resemblance of $Q_{\rm eff}$ and $Q_{\star}$ maps illustrates the importance of accounting for stellar contribution and disk thickness when 
+%examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift 
+%that are preferentially being observed now.
+% 
+High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
+$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
 \end{abstract}
@@
 Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
-\citet{Lombardi10a} in the MW.
 Further discussions on the interpretation of this is provided in \Sec{MR}.
@@
 
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$,
-$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$,
+$\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at.
 Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
@@
 \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
-and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
+and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
 Their velocity dispersions are also comparable to those observed in the inner
 Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
-locus of $\sigma\propto R^{0.56}$.
+locus of $\sigma_{\rm gas}\propto R^{0.56}$.
 Such high velocity dispersions and surface densities can be explained partly because
@@
  In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
- % 
- Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, 
-as the two are connected via the Euler equation, but this depends on the evolutionary stage of \flower (\Fig{vv}).
-%
-%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.
-
 % allss: 0.32
@@
 
-We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting
+We show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting
 and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
@@
 Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
-whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.
-
-We note that \citet{Behrendt16a} similarly concluded that large scale bulk motion may mimic turbulent velocity dispersion 
-due to beam smearing even though the self-rotation of each individual sub-MCCs is washed out.
-
+whereas the opposite is true in the quiescent phase. 
+In addition, the two velocity dispersion terms are of the same order of magnitude. % as the two are connected via the Euler equation
 {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
@@
 and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
+\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: 
+large-scale bulk motions may mimic turbulent velocity dispersion due to  
+beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam.
 
@@
 However, what does it mean for them to lie on the same locus?
-% is it what Jen's proposed? Or is it's just a result of $\rho\propto M R^{-3}$ (and $\rho$ is independent of R)
-% and observational bias (selection effect due to projection in 2D, so $\rho \propto N_H R^{-1}$, where $N_H$ is a
-% constant due to gas tracer) (i.e., middle and bottom panels of Fig 9 in BM02)?
 
@@
 an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
-If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
-to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
-If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
-one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
-regions of massive \SF.
+%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
+%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
+%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
+%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
+%regions of massive \SF.
 %\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
@@
 of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-two-dimensional space, as is done in \obs.
+two-dimensional space; the latter is done in \obs.
 When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
@@
 % the widespread in density for a given R.
-We show the density-size relation ($\rho - R$) relation of MCCs of \flower in \Fig{rho}.
-The interpretation of this figure is not that MCCs with small $R$ are found at high $n_{\rm cut}$ and large $R$ at low $n_{\rm cut}$, nor is that
-the density of MCCs is independent of $R$. Rather, it is as we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
+We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
+As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
 form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
-\DL{This is puzzling to me why we are seeing some really steep relationship between $\rho$ and $R$, almost $\rho \propto R^{-6}$
-even though we are identifying the structures in 3D just like what BM02 did.}
+Following \citet{Ballesteros02a}'s argument, we expect the density 
+of MCCs to be independent of the cloud size (since they are identified in 3D-space).
+On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
+we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
+As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
 
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
-\caption{Density and size of MCCs in the accreting phase of \flower.
-At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and
+\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
+At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
 form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
 See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
-\AP{$\rho \rightarrow n$}
-\label{fig:rho}}
+For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
+\label{fig:n}}
 \vspace{0.5em}
@@
 Properties of \flower are briefly summarized in \Sec{sim}.
-We use a three-dimensional clump-finding algorithm to identify MCCs and their sub-structures.
+We use a three-dimensional clump-finding algorithm to identify MCCs.
 We decompose the molecular structures into non-overlapping objects by identifying a set of
-density contours with varying cutoff densities at multiple evolutionary stages.
+density contours with varying densities at multiple evolutionary stages.
 Most notably, the accreting phase, starburst phase, and quiescent phase.
@@
 dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M},
-\sigma, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
+\sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
 
@@
 reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
-On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the adopted density threshold.
+On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.
 
@@
 These MCCs are, in fact, highly supersonic (with high Mach numbers).
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma\simeq200$\,\kms); however,
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms); however,
 comparing the velocity dispersions of MCCs from bulk motions versus turbulence
@@
 %when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR.
-It is thus currently unclear whether \highz molecular gas structures are truly intrinsically more turbulent than those in the local ISM.
-This will become clearer in the next few years as deeper and higher resolution imaging of
-molecular gas at \highz are observed with ALMA and NOrthern Extended Millimeter Array (NOEMA).
+Thus, with the resolution provided by existing data, it remains unclear whether \highz molecular gas structures 
+are truly intrinsically more turbulent than those in the local ISM.
+This picture will become clearer as deeper and higher resolution imaging of
+molecular gas at \highz are obtained with ALMA and NOrthern Extended Millimeter Array (NOEMA) in the next few years, and 
+potentially with the Next Generation VLA (ngVLA) in the 2030s.
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy

### 2019-05-11 WRITEUP/ms.tex
commented MR relation; cleanup

@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
-\caption{
-Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
-Star symbols are color-coded by
-increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
-Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
-Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
-constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
-%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
-%same as \Fig{larsons_single}.
-%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
-%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
-For interpretation of this figure, see discussion in \Sec{MR}.
-\label{fig:MR}}
-\end{figure*}
+%
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
+%\caption{
+%Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+%Star symbols are color-coded by
+%increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
+%Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}. 
+%Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
+%Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
+%constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
+%%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
+%%same as \Fig{larsons_single}.
+%%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
+%%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
+%For interpretation of this figure, see discussion in \Sec{MR}.
+%\label{fig:MR}}
+%\end{figure*}
 
@@
 % PVE
-Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
+Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
@@
 
-Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
-\citep{Larson81a, McKee07a}.
-Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
-which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
-the mass-size relation is also known as the constant column density relation and has been
-proposed as a fundamental property of molecular clouds on different physical scales.
-
-By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
-\begin{equation}
-A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-\end{equation}
-Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
-\begin{equation}\label{eqn:constantcolumndensity}
-M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
-\end{equation}
-where we adopt $\mu = 2.5$ as the mean molecular weight.
-
-We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
-Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-Further discussions on the interpretation of this is provided in \Sec{MR}.
-%
-%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
-%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
+%\citep{Larson81a, McKee07a}.
+%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
+%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
+%the mass-size relation is also known as the constant column density relation and has been
+%proposed as a fundamental property of molecular clouds on different physical scales.
+%
+%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
+%\begin{equation}
+%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+%\end{equation}
+%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
+%\begin{equation}\label{eqn:constantcolumndensity}
+%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+%\end{equation}
+%where we adopt $\mu = 2.5$ as the mean molecular weight.
+%
+%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
+%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+%Further discussions on the interpretation of this is provided in \Sec{MR}.
+%%
+%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
+%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
 5 therein]{Behrens18a}
@@
 
-\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
-The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
-by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
-can be understood by acknowledging the fact that a given MCC in \flower
-does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
-our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
-predictions for CO line emission in the work presented by
-\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
-That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
-that the MCCs in our simulation have lower column densities than the
-star-forming cores observed in the Milky Way, which are
-observationally well-resolved within an MCC, and indeed, have
-sufficient column density to form CO.
-
-In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
-This makes sense from simply the fact that smaller MCCs have smaller masses.
-However, what does it mean for them to lie on the same locus?
-
-The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
-an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
-%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
-%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
-%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
-%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
-%regions of massive \SF.
-%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
-%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
-%  point on that relationship, at the constant $\Sigma$ value.  }
-However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
-with a certain tracer (e.g., \citealt{Ballesteros11}).
-That is, it is solely a result of $\rho\propto M R^{-3}$.
-For instance, \citet{Ballesteros02a} show that the density
-of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-two-dimensional space; the latter is done in \obs.
-When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
-line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
-They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
-observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
-observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
-% since $M$ would then scale as $R^{3}$.
-% naturally display a linear relationship in $\log M - \log R$ plot.
-
-% the widespread in density for a given R.
-We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
-As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
-form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
-Following \citet{Ballesteros02a}'s argument, we expect the density 
-of MCCs to be independent of the cloud size (since they are identified in 3D-space).
-On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
-we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
-As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
-
-\begin{figure}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
-\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
-At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
-form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
-See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
-For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
-\label{fig:n}}
-\vspace{0.5em}
-\end{figure}
+%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
+%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
+%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
+%can be understood by acknowledging the fact that a given MCC in \flower
+%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
+%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
+%predictions for CO line emission in the work presented by
+%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
+%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
+%that the MCCs in our simulation have lower column densities than the
+%star-forming cores observed in the Milky Way, which are
+%observationally well-resolved within an MCC, and indeed, have
+%sufficient column density to form CO.
+%
+%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
+%This makes sense from simply the fact that smaller MCCs have smaller masses.
+%However, what does it mean for them to lie on the same locus?
+%
+%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
+%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
+%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
+%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
+%%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
+%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
+%%regions of massive \SF.
+%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+%%  point on that relationship, at the constant $\Sigma$ value.  }
+%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
+%with a certain tracer (e.g., \citealt{Ballesteros11}).
+%That is, it is solely a result of $\rho\propto M R^{-3}$.
+%For instance, \citet{Ballesteros02a} show that the density
+%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
+%two-dimensional space; the latter is done in \obs.
+%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
+%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
+%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
+%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
+%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+%% since $M$ would then scale as $R^{3}$.
+%% naturally display a linear relationship in $\log M - \log R$ plot.
+%
+%% the widespread in density for a given R.
+%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
+%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
+%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
+%Following \citet{Ballesteros02a}'s argument, we expect the density 
+%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
+%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
+%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
+%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
+%
+%\begin{figure}
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
+%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
+%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
+%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
+%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
+%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
+%\label{fig:n}}
+%\vspace{0.5em}
+%\end{figure}
 

### 2019-05-15 WRITEUP/ms.tex
few modification to Sec. 5

@@
 
-The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following.
-We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
 \begin{equation}
@@
 %
-We note that the distributions vary for different evolutionary stages of \flower.
-%
-The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
+We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
 %
 Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
-The main disk occupying the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
+The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
+%
+The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
+This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages.
+Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\label{fig:dist}}
+\end{figure*}
 
@@
 \end{figure}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass
-  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
-  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
- over all times analyzed here.
-Note that the scales shown on the $y$-axes are different between the top
-and bottom panels, as fewer MCCs are identified at higher $n_{\rm
-  cut}$.
-\label{fig:dist}}
-\end{figure*}
 
@@
 Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
-MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant} 
 \label{fig:alphaEvol}}
@@
 
-We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+We can now focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
 Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
 
-Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$)
-and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies,
-such as the nearby gas-rich galaxy M64 and
-% Kennicutt, 1996IAUS..171...11K
-% Spiral gal, appears to have accreted a gas-rich companion in the recent past,
-% with the inner gas disk the remnant of the
-% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995).
-the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
-\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
+During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
 
 % middle
-While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are
-composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component
-(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of
-some of them (see \Fig{stellarRatio16}).
-MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of
-\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
-This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
-the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
+%
+MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
 
@@
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
-Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium
-to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
 % (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
@@
 % Starburst
-Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes
-as those in the accreting phase; however, the MCCs in the starburst phase span
-a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
+In the starburst phase, MCC have similar velocity dispersion and sizes as those in the accreting phase; however, the MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters, i.e.
+they more susceptible to collapse.
 Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
-(\Fig{alphaEvol}).
-Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
+%
+\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
 the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
@@
 
-\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
+\subsection{Adopted Density Threshold Dependence and Temporal Evolution}\label{sec:ncut}
 
 We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the
-choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus,
-the results presented in \Sec{singless} dependent on the choice of density thresholds.
-
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
-and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
-For instance, the cluster of points found at the lowest density threshold,
-occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
-are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs.
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
+%
+The cluster of points found at the lowest density threshold, occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
 that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
 typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
-These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel.
-In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
-
-We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been
-reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
-resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-However, the IGM and merger and accretion histories are not properly modeled in such simulations since
-they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
-reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+%
+These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
+
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+%
+However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
+That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+%
 The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
@@
 % temporal evolution in Cloud Dynamics
+\AP{the following is cutting the discussion a bit too abruptly; additionally, it might seem contradicting with the fact that we find differences when analysing extreme stages}
 We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
-We find no quantitative differences over the 700\,Myr traced in our simulation, except
-for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
+We find no quantitative differences over the 700\,Myr traced in our simulation, except for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
 

### 2019-05-17 WRITEUP/ms.tex
minor edits

@@
 % temporal evolution in Cloud Dynamics
-\AP{the following is cutting the discussion a bit too abruptly; additionally, it might seem contradicting with the fact that we find differences when analysing extreme stages}
 We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
-We find no quantitative differences over the 700\,Myr traced in our simulation, except for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
+One of the most pronounce differences in the dynamics of MCCs traced over the 700\,Myr shown in this work 
+is seen in the virial parameter --- the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
 
@@
 
-We do not observe any significant temporal variations in the MCC dynamics over the course of 700\,Myr
-traced in our simulation, except in the virial parameter, which is the lowest in the pre-starburst phase.
-The virial parameter increases after a starburst as gas is self-regulated by feedback.
-
 % Toomre:
@@
 This is consistent with the notion that collapsing structures result from
-gravitational instability occuring within globally stable structures, which are
+gravitational instability occurring within globally stable structures, which are
 supported by turbulence and rotation on large scale.
@@
 and thus, \SF in the first galaxies.
+
+We examine temporal variations in the MCC dynamics over the course of 700\,Myr
+traced in our simulation. One of the most prominent differences is the virial parameter, which is the lowest in the pre-starburst phase
+but increases after a starburst as gas is self-regulated by feedback.
 

### 2019-05-17 WRITEUP/ms.tex
section 6 commented

@@
 
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$,
-$\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at.
-Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
-linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to
-the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
-$z$\ssim2 spatially resolved studies of gas-rich star-forming
-galaxies, in terms of their velocity dispersions, sizes, and gas
-surface densities (\Fig{larsons_single}; see e.g.,
-\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
-and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
-Their velocity dispersions are also comparable to those observed in the inner
-Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
-locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersions and surface densities can be explained partly because
-these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest,
-and also from the injection of kinetic energy from recent
-\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
-In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2,
-\flower has assembled a stellar mass of
-$M_\star$\eq7.5\E{9}\,\Msun.
-Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that
-the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in
-its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in
-interpreting observational results is further discussed in the next subsection (\Sec{rot}).
-
-The high pressure observed in \flower (see \citealt{Pallottini17a})
-is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
+%
+We exclude for the moment the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
+
+The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
+%
+Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+Such high velocity dispersions and surface densities can be explained partly because these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest, and also from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
+%
+\AP{I do not fully understand the following} Furthermore, the comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in its later stage of evolution as \flower is settling into a rotating disk galaxy.
+The implication of this in interpreting observational results is further discussed in the next subsection (\Sec{rot}).
+
+The high pressure observed in \flower (see \citealt{Pallottini17a}) is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
 %
-For instance, in local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
-% Tasker09a
+In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
 On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and higher velocity accretion/SN-driven outflows \citep{gallerani:2018}.
@@
 % different evolutionary stages
-In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences
-in the MCC properties with respect to those observed in the nearby Universe
-between the accreting and starburst phase of \flower (see
-\Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences in the MCC properties with respect to those observed in the nearby Universe between the accreting and starburst phase of \flower (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
 However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase.
@@
 The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
-as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
+as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e.
+$c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
-% allss: 0.32
-% In [13]: print(get_Mach_all_clouds(ss11))
-%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
-%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
-%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
-%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
-%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
-%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
-%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
-%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
-%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
-%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
-%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
-%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
-%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
-% allss: 18.96
-%In [15]: print(get_Mach_all_clouds(ss12))
-%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
-%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
-%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
-%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
-%  5.05517168  6.93886988  5.4830306 ]
-% see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
-% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
-
-We show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting
-and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
-but a disk-like morphology in the quiescent phase
-(see \Fig{MCC} and \Fig{MCC28}).
-Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
-whereas the opposite is true in the quiescent phase. 
-In addition, the two velocity dispersion terms are of the same order of magnitude. % as the two are connected via the Euler equation
-{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
-have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures
-on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
-and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
-\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: 
-large-scale bulk motions may mimic turbulent velocity dispersion due to  
-beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam.
-
+%
+This can be further analyzed as follows.
+In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase.
+Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
+%
+Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase.
+In addition, the two velocity dispersion terms are of the same order of magnitude.
+% as the two are connected via the Euler equation
+\AP{I still do not get the point; bulk motion is a dispersion, i.e.
+should not receive contribution from the rotation of the system; a possibility might be to calulate the specific angular momentum ($\vec{x}\wedge\vec{v}$ averaged using \Eq{defineaverage}) of the system and compare it to the one for gas in circular motion} {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}
+%
+Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
+\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam \AP{they argue that self-rotation is not important, but i do not see how we match the result with our analysis}.
+
+\AP{I would not remove the mass-size relation discussion (commented now in the text)}
 %\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
@@
 highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
+\AP{maybe it is better to put a single set of maps, with FOV from -1.5 to 1.5 kpc}
 \label{fig:Qeff}}
@@
 
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
-(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower
-using different $n_{\rm cut}$).
-
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against $m$\eq0 perturbations.
+\AP{Q was introduced at page 3, but then not used. I think some intro sentence should be added here}
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
+
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against \AP{should we introduce this classification of the perturbations in the \Sec{Q}} $m$\eq0 perturbations.
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and
-has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
-
-That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that
-they correspond to regions of high surface densities that are gravitationally unstable.
-Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
-thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are
-consistent with $Q_{\rm eff} > 1$.
-This demonstrates the importance of accounting for stellar contribution and disk thickness
-when examining the stability of molecular gas structures.
-This consideration is especially relevant for the relatively evolved and enriched systems at high redshift,
-that are preferentially being imaged at high resolution with ALMA.
-In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with
-both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$.
+Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
+
+That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
+Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
+%
+This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures.
+This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA.
+In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$.
 Notably, these are the more gas-rich regions (see \Fig{sigma}).
 
-The large virial parameters seen in some MCCs of \flower can be understood
-by first noting that fragmentation {\em can} happen in regions of low $Q$
-(if we only consider instability against axisymmetric perturbations),
-but further evolution/collapse depends on the dynamics or equation of state of the gas.
-%
-Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
-Second, this fragmentation scale is greater than the typical size of GMCs.
-%
-This could be interpreted as a result of instability setting the scales for fragmentation,
-{\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
-%
-Thus, the high virial parameter found for some MCCs in \flower
-indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage
-of \flower) and are found in regions of $Q_{\rm eff}>1$.
-On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
-and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
-where energy quickly dissipates. % with low virial parameters.
-
-If most of the MCCs in \flower are stable against collapse,
-how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
+The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
+%
+Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
+%
+This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
+%
+Thus, \AP{from the sentence, it is unclear if the Q analysis is consistent or is in an independent indication with respect to the virial parameter analysis} the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage of \flower) and are found in regions of $Q_{\rm eff}>1$.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
+
+If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
 Such tension in the interpretation is understood as follows.
 %
-First, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
-This re-iterates the statement about low $Q$ above.
-%
-Second, due to turbulence dissipation on small-scales, such
-(sub-)structures are no longer supported by differential rotation.
-This in turn enables sub-regions of the MCCs to collapse and potentially form
-OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
-% Mechanisms causing non-axisymmetric perturbations (e.g.,
-% arms) to the gravitational potential \MM{Gravitational instability is
-%   that mechanism (see e.g.\ Wada et al.'s classic review of the
-%   subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.}
-% can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+First, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by differential rotation.
+This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
+% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
 These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
 Further, the SFR of \flower is very bursty and high SFR stages are only transient.
+%
+Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
+This re-iterates the statement about low $Q$ above.
 

### 2019-05-29 WRITEUP/ms.tex
minor edits

@@
 
+% TO edit:
+% alpha lesssim 2 MCCs are bounded. For reference, GMCs in MW and nearby galaxies: 0.1 - 10 \citep{Solomon87a, Bolatto08a, Heyer09a, Roman-Duval10a, Wong11a}
+
 \author{T. K. Daisy Leung\altaffilmark{1,2}}
@@
 \begin{abstract}
-%mm rearranged sentence
 We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
@@
 %
-We show that large-scale rotation is an important contributor to the velocity dispersion of MCCs, even in the highly disturbed phase of \flower, posing 
-a challenge to the interpretation of molecular gas dynamics in \highz galaxies in the literature.
-% Thus, velocity dispersions measured on similar scales (even down to 40\,pc) should not be taken as a direct 
-% evidence that \highz molecular gas are intrinsically more turbulent than the local ISM, 
-% unless contributions from bulk motions are properly accounted for.
-% 
-%Close resemblance of $Q_{\rm eff}$ and $Q_{\star}$ maps illustrates the importance of accounting for stellar contribution and disk thickness when 
-%examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift 
-%that are preferentially being observed now.
-% 
+We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs, even in the highly disturbed phase of \flower.
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
@@
 %mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
-Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population.
+Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population \citep[see also a review by][]{Stark16a}.
 %
@@
 where $M_\star$ is the stellar mass within the MCC volume.
-\DL{Should we leave out $\sigma_{\star}$ since stellar motions shouldn't affect the gas?}
 
@@
 \sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
+% First term: large scale motion
+% second and last terms: small scale
 \label{eqn:veldisp}
@@
 Therefore, when calculating global quantities for MCS, we always perform a mass-weighting.
-Since we operate on data on a unigrid, this is equivalent to density averaged quantities.
+Since we operate on data on a uni-grid, this is equivalent to density averaged quantities.
 In general, for the quantity $x$ in a MCC we write
@@
 \end{equation}
-where the sum is done for the cells indexed by $i$ composing the MCC. We can use the defintion \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
+where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
 %
@@
 The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
+% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
 %
@@
 The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
-include a large number of stellar mass already ensembled in \flower 
+include a large number of stellar mass that is already ensembled in \flower
 \label{fig:stellarRatio16}}
@@
 % as the two are connected via the Euler equation
-\AP{I still do not get the point; bulk motion is a dispersion, i.e.
-should not receive contribution from the rotation of the system; a possibility might be to calulate the specific angular momentum ($\vec{x}\wedge\vec{v}$ averaged using \Eq{defineaverage}) of the system and compare it to the one for gas in circular motion} {\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}
+\DL{interpretation To be revised ...}
+{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}....
 %
 Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
-\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam \AP{they argue that self-rotation is not important, but i do not see how we match the result with our analysis}.
-
-\AP{I would not remove the mass-size relation discussion (commented now in the text)}
+\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing.
+
 %\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
@@
 
-\AP{Q was introduced at page 3, but then not used. I think some intro sentence should be added here}
-Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
-
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against \AP{should we introduce this classification of the perturbations in the \Sec{Q}} $m$\eq0 perturbations.
+We define Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ in \Sec{Q}.
+Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff}
+(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
+
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations.
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
@@
 That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
-Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
+Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
 %
@@
 %
-Thus, \AP{from the sentence, it is unclear if the Q analysis is consistent or is in an independent indication with respect to the virial parameter analysis} the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage of \flower) and are found in regions of $Q_{\rm eff}>1$.
+Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
 On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
@@
 These MCCs are, in fact, highly supersonic (with high Mach numbers).
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms); however,
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms);
+\DL{TBD} however,
 comparing the velocity dispersions of MCCs from bulk motions versus turbulence
@@
 %
-TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
+TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
 %
@@
 H2020/740120.
-%mm
+% mm
 M-MML acknowledges partial support by the NSF through award

### 2019-05-29 WRITEUP/ms.tex
updated ref

@@
     a molecular cloud.
-Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
+Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{Bertoldi92b}.
 %
@@
 
-In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01}, and for the non-negligible disk thickness.
+In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01a}, and for the non-negligible disk thickness.
 This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
@@
 Radiation pressure on dust and gas is also included.
-Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}.
-%
-Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{agertz:2013}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{maclow1999turb}.
+Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{Pallottini19a, Decataldo19a}.
+%
+Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{Agertz13a}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{Maclow99a}.
 See \citet{Pallottini17b} for further details.
@@
 %
-The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang2016}, which is higher than normal local galaxies.
+The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}, which is higher than normal local galaxies.
 The effective stellar radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
@@
 In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
-On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{kohandel:2019} and higher velocity accretion/SN-driven outflows \citep{gallerani:2018}.
+On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}.
 The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.

### 2019-05-30 WRITEUP/ms.tex
moved comparison of velo disp to Sec 5.1

@@
 The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
-This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceedes the mass resolution by a factor of eight.
+This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceeds the mass resolution by a factor of eight.
 The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e.
@@
 
-\subsection{Distributions of MCC Basic Properties}
-
-We start by considering the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
-\begin{equation}
-f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
-\end{equation}
-%
-We show in \Fig{dist} the results for the distributions considering all the evolutionary stages and dividing the sample in a low ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
-%
-Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
-The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower.
-% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
-%
-The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
-This main disk component occupy the top right corner of \Fig{stellarRatio16} has a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio of $\simeq$\,50--100.
-
+\subsection{Distributions of MCC Basic Properties and Outlier}
 \begin{figure*}[htbp]
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages.
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
+$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
 Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
@@
 
+We start by considering the MCC distributions in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
+\end{equation}
+%
+We show in \Fig{dist} the distributions considering all the evolutionary stages of \flower and dividing the sample in a low 
+($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
+%
+Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
+whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
+
+% address the biggest MCC = molecular disk of \flower
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
-The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} as they correspond to a large part of \flower, and thus,
-include a large number of stellar mass that is already ensembled in \flower
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
+The most massive MCC identified at low $n_{\rm cut}$ shows 
+a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
+and corresponds to the molecular disk of \flower (see also \Fig{vv}). Thus,
+it includes a large number of stellar mass that is already assembled in \flower. Such structure is excluded 
+in the discussion of MCC dynamics in the remainder of this paper.
 \label{fig:stellarRatio16}}
 \end{figure}
+
+The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
+which is identified as a single component at low $n_{\rm cut}$.
+This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?}
+stellar-to-gas mass ratio of $\simeq$\,50--100. 
+Such structure has velocity dispersion dominated by bulk motions, as shown in \Fig{vv}, where we compare 
+the velocity dispersions of MCCs  
+resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
+for the accreting and quiescent phases of \flower.
+The accreting phase (\Fig{MCC}) of \flower displays a disturbed morphology compared to the
+quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+Excluding the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower 
+are dominated by turbulent motions. 
+On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
+in the quiescent disk-like phase.
+
+The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper.
+Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
+% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
+\caption{Gas velocity dispersions from bulk motions and turbulent motions for MCCs identified in accreting (top) and
+quiescent phase (bottom) of \flower across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}).
+The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
+quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. 
+On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
+in the quiescent disk-like phase.
+\label{fig:vv}}
+\vspace{0.5em}
+\end{figure}
+
+The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
+as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e.
+$c_s^2 \ll \sigma_{\rm NT}^2$.
+In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
+%%
+%This can be further analyzed as follows.
+In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase.
+Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
+%%
+%Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase.
+In addition, the two velocity dispersion terms are of the same order of magnitude.
+%% as the two are connected via the Euler equation
+
+\subsection{Single Evolutionary Stage}  \label{sec:singless}
 
@@
 (see Fig 4 of \citealt{Kauffmann17b}).
-The gray dotted lines shown in the bottom panels correspond to the various external pressures for
-gas in equilibrium, see Equation~\ref{eqn:v0}.
+The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
+the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
 \label{fig:larsons_single}}
@@
 
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
-\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
-Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
-Definition of symbols are same as in \Fig{larsons_single}.
-Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
-The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
-the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
-post-starburst phase.
-The variation is clearly seen between the pre-starburst through post-starburst phase.
-Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
-MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
-\label{fig:alphaEvol}}
-\end{figure*}
+%\begin{figure*}[htbp]
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
+%\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
+%Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
+%Definition of symbols are same as in \Fig{larsons_single}.
+%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
+%The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
+%the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
+%post-starburst phase.
+%The variation is clearly seen between the pre-starburst through post-starburst phase.
+%Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
+%MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
+%\label{fig:alphaEvol}}
+%\end{figure*}
 
@@
 
-\subsection{Single Evolutionary Stage}  \label{sec:singless}
-
-We can now focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
-Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+Here, we focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
 
@@
 MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
-This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
 
@@
 Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
-Heyer+09).
+At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
+Such variations in $\sigma^2/R$ is observed in GMCs of the Milky Way \citep{Heyer09a}.
+
+If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
+% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$.
+The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
+molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
+is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
+column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
+%For instance, \citet{Ballesteros02a} show that the density
+%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
+%two-dimensional space; the latter is done in \obs.
+%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
+%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
+%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
+%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
+%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).
 
@@
 % Starburst
-In the starburst phase, MCC have similar velocity dispersion and sizes as those in the accreting phase; however, the MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters, i.e.
-they more susceptible to collapse.
-Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
-%
-\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
-the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
-This is consistent with our physical intuition of gas instability leading to \SF.
+In the starburst phase, MCCs have similar velocity dispersion and sizes as those in the accreting phase; however, 
+MCCs in the starburst phase span a wider range in gas surface density 
+(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
+for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
+That is, more MCCs in the starburst phase of \flower are more susceptible to collapse.
+%
+% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
+%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
+%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
+%This is consistent with our physical intuition of gas instability leading to \SF.
 
@@
 
-We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the
-choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs.
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
-%
-The cluster of points found at the lowest density threshold, occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
-that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
-typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
-%
-These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
+We investigate possible variations in the dynamics of the molecular structures of \flower 
+by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
+to test the robustness of our results against the choice of density threshold. 
+That is, how sensitive are the structure properties, and thus, the 
+results presented in \Sec{singless} dependent on the choice of density thresholds.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$. 
+As mentioned in \Sec{}, the most massive cloud identified at low H$_2$ gas density threshold corresponds to the molecular 
+disk of \flower, and is broken down into multiple smaller MCCs at higher 
+$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
+ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
+%
+%For instance, the cluster of points found at the lowest density threshold, 
+%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
+%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
+%MCCs identified at lower density in the outskirts of \flower
+%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
+%%
+%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.
 
@@
 This is expected for \SF to proceed.
-
-\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}
-
-\begin{figure}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Gas velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and
-quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the
-quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
-The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but
-the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion.
-This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales
-should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
-% either higher resolution, or properly accounting for large scale motions.
-\label{fig:vv}}
-\vspace{0.5em}
-\end{figure}
-
-The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
-as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e.
-$c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
-%
-This can be further analyzed as follows.
-In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase.
-Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
-%
-Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase.
-In addition, the two velocity dispersion terms are of the same order of magnitude.
-% as the two are connected via the Euler equation
-\DL{interpretation To be revised ...}
-{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here have an important contribution from large-scale rotation.}....
-%
-Hence, the linewidths observed in \highz molecular gas structures on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM, and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
-\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: large-scale bulk motions may mimic turbulent velocity dispersion due to beam smearing.
 

### 2019-05-30 WRITEUP/ms.tex
done w/ sec 5

@@
 
-\subsection{Distributions of MCC Basic Properties and Outlier}
+\subsection{Distributions of MCC Basic Properties and Outlier} \label{sec:dist}
 \begin{figure*}[htbp]
@@
 
-The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper.
+The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper
+since its dynamics is dominated by large-scale shear.
 Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
-% GMCs in nearby galaxies: 10^5 < M < 1e7 Msun \citep{Rosolowsky03a, Freeman17a}
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
+have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
+That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
 
@@
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
-%%
-%This can be further analyzed as follows.
-In \Fig{vv} we show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting and quiescent phase.
-Recall that \flower displays a disturbed morphology in the accreting phase but a disk-like morphology in the quiescent phase (see \Fig{MCC} and \Fig{MCC28}).
-%%
-%Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions, whereas the opposite is true in the quiescent phase.
-In addition, the two velocity dispersion terms are of the same order of magnitude.
-%% as the two are connected via the Euler equation
 
@@
 for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
-That is, more MCCs in the starburst phase of \flower are more susceptible to collapse.
+That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
 %
@@
 
-\subsection{Adopted Density Threshold Dependence and Temporal Evolution}\label{sec:ncut}
+\subsection{Adopted Density Threshold Dependence}\label{sec:ncut}
 
@@
 
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$. 
-As mentioned in \Sec{}, the most massive cloud identified at low H$_2$ gas density threshold corresponds to the molecular 
-disk of \flower, and is broken down into multiple smaller MCCs at higher 
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
+As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
+corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
 $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
  since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
+Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
+(see top panels of \Fig{larsons_single}). 
+At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,100\,pc.
 %
@@
 
-We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-%
-However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
-That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-%
-The gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the actual value of $n_{\rm cut}$.
-%%
-%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
+%
+The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
 %%
@@
 %%
-This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in
-nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
-
-%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold
-%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
-%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size
-%at increasing $n_{\rm cut}$.
-
-% temporal evolution in Cloud Dynamics
-We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}.
-One of the most pronounce differences in the dynamics of MCCs traced over the 700\,Myr shown in this work
-is seen in the virial parameter --- the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
+This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
+nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
 

### 2019-05-30 WRITEUP/ms.tex
polished intro

@@
 %
-In \flower, MCC masses are in the range of $10^{5.5-8.5}$\,\Msun, with sizes $R\lesssim200$\,pc.
+In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc.
 %
@@
 %
-We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs, even in the highly disturbed phase of \flower.
+We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs.
 High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
@@
 \section{Introduction}
-The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM)
-%mm to fuel \SF (and feed their  [using "to" implies purpose]
-     either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central
-supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium
-%mm with
-   by expelling some
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies.
+This gas fuels \SF and feeds central
+supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
 part of this material.
-%mm [now redundant with first sentence] The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic times.
-Back then,
-    Early
-galaxies
-%mm themselves
-are more gas-rich and their molecular fraction possibly higher
-%mm compared to
-   than
-present-day galaxies.
-
-Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular
-%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?]
-   cloud complexes (MCCs)
+Existing studies indicated that early galaxies are more gas-rich with molecular fractions higher than
+those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
+Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs)
 that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
-%
 Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
@@
 %
-As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF).
+As a consequence, we expect them to be significantly more ionized, and have intense and hard interstellar radiation fields (ISRF).
 Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced.
@@
 properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question:
+{\it what are the physical properties of
 molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
@@
 Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity).
-However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
-%
-To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of (strongly-lensed) galaxies at intermediate-$z$, using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
-These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2), are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne;
+see e.g., the review by \citealt{CW13}).
+%
+To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of 
+galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
+Hodge16a, Leung19a}). These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
 
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Jones17a,Smit18a}.
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a,Smit18a}.
 
@@
 %
+
 \section{Physical Background}\label{sec:Back}
@@
 Such notions will be used in the subsequent analysis of our simulations.
+
 \subsection{Larson relations and virial parameter}\label{sec:PVE}
 \citet{Larson81a} discussed a number of relations among Galactic
-%mm MCC
 molecular cloud
@@
 They also represent a useful framework to analyze our results as they
-%mm
-     have been argued to
-arise from the interplay between gravity and turbulence encoded in the virial theorem
-%mm
-    (however, note the alternative interpretation involving gravitational collapse by
-    \citealt{Ballesteros-Paredes11a}).
+have been argued to arise from the interplay between gravity and turbulence encoded in the virial theorem
+(note, however, the alternative interpretation involving gravitational collapse by
+e.g., \citealt{Ballesteros-Paredes11a}).
 
@@
 \end{equation}
-where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the
-%mm  kinetic, external, and gravity pressure terms.
-    kinetic energy, external pressure, and gravitational potential energy terms.
+where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.
 
@@
 %--------------------------------------------------------------------------
-\section{Discussions and Implications}\label{sec:diss}
+\section{Discussions}\label{sec:diss}
 
@@
 In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-%
-We exclude for the moment the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
-
+%%
+%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
 The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
@@
 Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersions and surface densities can be explained partly because these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest, and also from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+Such high velocity dispersion is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%
-\AP{I do not fully understand the following} Furthermore, the comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in its later stage of evolution as \flower is settling into a rotating disk galaxy.
-The implication of this in interpreting observational results is further discussed in the next subsection (\Sec{rot}).
 
@@
 In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences in the MCC properties with respect to those observed in the nearby Universe between the accreting and starburst phase of \flower (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
-However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase.
-Similarly, the virial parameter is higher in the post-starburst phase compared to both the pre-\SB and \SB phases.
+However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
 This is expected for \SF to proceed.
@@
 %
-First, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by differential rotation.
+First, due to energy dissipation on small-scales, such (sub-)structures are no longer supported by turbulence. 
 This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
@@
 The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
-and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
+and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$.
 The $\sim$200\,pc-scale MCCs found with a low density threshold
 correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
-Overall, the mass of MCCs ranges between $10^{5.5-8.5}$\,\Msun, depending on the chosen density threshold.
-This mass range is comparable to those observed in \z\ssim2 galaxies in rest-frame UV and optical wavelengths.
-Similarly massive molecular structures (few times 10$^7$\,\Msun) have been
+Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun and are supported by 
+non-thermal pressure. Similarly massive molecular structures (few times 10$^7$\,\Msun) have been
 reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the
-48\,kpc box studied by \citealt{Behrendt16a}).
-However, the IGM and merger and accretion histories are not properly modeled in such simulations.
+48\,kpc box studied by \citealt{Behrendt16a}); 
+owever, the IGM and merger and accretion histories are not properly modeled in such simulations.
 That said, the similar mass range found in MCCs of \flower\ is
@@
 We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
-observed in the Milky Way disk, the Galactic center, and
-gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations.
-This comparison is done for different evolutionary stages of \flower.
+%observed in the Milky Way disk, the Galactic center, and
+%gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations.
+%This comparison is done for different evolutionary stages of \flower.
 
@@
 accreting phase of \flower, which displays a highly disturbed morphology.
-This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date.
-In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc)
-should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
-unless contributions from bulk motions are properly accounted for.
-%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution
-%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used
-%for structures in the literature) are more turbulent based on solely measured velocity dispersion.
+....
 
@@
 We examine temporal variations in the MCC dynamics over the course of 700\,Myr
-traced in our simulation. One of the most prominent differences is the virial parameter, which is the lowest in the pre-starburst phase
-but increases after a starburst as gas is self-regulated by feedback.
+traced in our simulation. One of the most prominent differences is the virial parameter, more MCCs have lower virial parameters
+in the starburst phase compared to the accreting phase of \flower.
 
@@
 
-\begin{comment}
-\appendix
-\section{Variation in MCC Properties Depending on the Choice of Density Cuts and Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
-% single Snapshot
-We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
-different sets of $n_{\rm cut}$ in identifying the MCCs.
-That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
-We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
-cloud scaling relations).
-%
-In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%
-This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$.
-Our results are therefore robust to the various density cuts of choice.
-
-% temporal evolution in Cloud Dynamics
-We show the properties of all MCCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
-We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
-
-% -------------- all snapshots -----------
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=0 100 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
-\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
-\caption{
-%Comparison of MCCs identified across all evolutionary stages (over 700\,Myr; star symbols)
-to those observed in nearby and \z$\sim$2 star-forming galaxies
-in the context of the linewidth-size relation.
-%Bottom panel corresponds to including only the denser substructures/sub-MCCs identified in \flower
-(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
-By and large, we find no quantitative differences in the mass-size relation over the 700\,Myr traced in the simulation.
-\label{fig:larsons16-28}}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\centering
-\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
-\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
-\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
-\caption{
-Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCCs identified across all evolutionary stages
-(i.e., with different SFR). Star symbols are color-coded by increasing SFR.
-Right panels correspond to including only the denser substructures/sub-MCCs identified in \flower
-(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
-We find no obvious differences in relation to those observed in nearby and \highz
-galaxies in the context of these cloud scaling relations.
-\label{fig:alpha16-28}}
-\end{figure*}
-\end{comment}
-
 \end{document}

### 2019-05-30 plotSS.py
get pressure of MCCs

@@ -210,12 +210,25 @@ if __name__ == '__main__':
     import matplotlib
     matplotlib.use('agg')
 
+    import numpy as np
+
     import matplotlib.pyplot as plt
-    from plot_modules.plot_cloud_prop import setup_plot
+    from plot_modules.plot_cloud_prop import setup_plot, get_P_NT_all_clouds
     cm = setup_plot()
 
     # # for paper
-    # plot_dis_allSS()
+    # minss=16
+    # maxss=28
+    # pattern1='0.32'
+    # pattern2='18.96'
+    # plotdir='./test_brute/leaf_fields_ss16-28/'
+    # plot_dis_allSS(minss, maxss, pattern1, pattern2, plotdir)
+    # ss11, to_plot11, _ = load_pickleTOplot(minss, maxss, \
+    #                                        fname=pattern1 + '_10_fields.p')
+    # ss12, to_plot12, _ = load_pickleTOplot(minss, maxss, \
+    #                                        fname=pattern2 + '_10_fields.p')
+    # print(get_P_NT_all_clouds(ss11).min(), get_P_NT_all_clouds(ss11).max(), np.median(get_P_NT_all_clouds(ss11)))
+    # print(get_P_NT_all_clouds(ss12).min(), get_P_NT_all_clouds(ss12).max(), np.median(get_P_NT_all_clouds(ss12)))
 
     # # of MCs w/ mass > 1e8 Msun (for paper)
     # _, _to, _ = load_pickleTOplot(16, 28, fname="0.32_10_fields.p")

### 2019-05-30 plot_modules/plot_cloud_prop.py

@@ -101,6 +101,8 @@ def unpack_xy(ss):
         _sigma2oR = []
         _mSD_per_ff = []   # Msun/pc^2/Myr
 
+        _P_NT = []
+
         for kkk in ss[ks].iterkeys():
             # print ss[ks][kkk]
             _Mj.append(ss[ks][kkk].M_jeans)
@@ -133,6 +135,7 @@ def unpack_xy(ss):
             _sigma2oR.append(ss[ks][kkk].sigma_gas_tot /
                              (ss[ks][kkk].R_pc * 2.0))
             _mSD_per_ff.append(ss[ks][kkk].massSD / (ss[ks][kkk].R_pc)**2 / ss[ks][kkk].tff_Myr)
+            _P_NT = [].append(ss[ks][kkk].P_nt)
 
         to_plot[ks] = {}
         to_plot[ks]['cloud mass'] = _m
@@ -1460,7 +1463,7 @@ def plot_Mach_massRatio_4ss(to_plot1, to_plot2, to_plot3, to_plot4,
                             # ax=axes.ravel().tolist(),
                             cax=cax)
         cbar.ax.tick_params(length=6, labelsize=legendFontSize)
-        label = r'$n_{\rm cut}$'
+        label = r'$n_{\rm cut}$ [cm$^{-3}$] $\equiv$ Density cut in $n_{\rm H2}$ '
         cbar.set_label(label, fontsize=cbarLabelSize)
 
     if saveFig:
@@ -2096,6 +2099,14 @@ def get_Mach_all_clouds(ss):
         for snapleafs in ss[snap].iterkeys():
             allMach.append(np.mean(ss[snap][snapleafs].Mach_vec))
     return np.array(allMach)
+
+def get_P_NT_all_clouds(ss):
+    allP_NT = []
+    for snap in ss.iterkeys():
+        for snapleafs in ss[snap].iterkeys():
+            allP_NT.append(np.mean(ss[snap][snapleafs].P_nt))
+    return np.array(allP_NT)
+
 
 
 def massFuncUnbinnedCDF(allmasses, save=True, outdir='./', tag=''):

### 2019-05-30 WRITEUP/ms.tex

@@
 %
-In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc.
+In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc, comparable to nearby spirals and starburst galaxies.
 %
@@
 \end{equation}
-In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
+In the thin disk approximation ($kh\ll1$), instability occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$ in \Eq{3Ddisp}).
 A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
@@
 %
-The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}, which is higher than normal local galaxies.
-The effective stellar radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}.
+The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 
@@
 
-\begin{figure*}
+\begin{figure*}[hptb]
 \centering
@@
 %
-%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
+%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and \section{•}
+atellite galaxies, thereby leading to bursts of \SF.
 Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
@@
 The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
+The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$\,Myr.
 
@@
 For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
-
-In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties
-in the disturbed phase of \flower and in the disk-like ordered phase.
-
-Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies.
-The distinction between clumps and satellites is admittedly somewhat ambiguous, though, and we consider it only as a working one.
-
-\AF{To be discussed at the end}
+In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
+by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
 
@@
 This is commonly done by
-identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
+identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMyer13a}).
 %
@@
 stellar-to-gas mass ratio of $\simeq$\,50--100. 
-Such structure has velocity dispersion dominated by bulk motions, as shown in \Fig{vv}, where we compare 
-the velocity dispersions of MCCs  
-resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
-for the accreting and quiescent phases of \flower.
-The accreting phase (\Fig{MCC}) of \flower displays a disturbed morphology compared to the
-quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
-Excluding the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower 
-are dominated by turbulent motions. 
+The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
+the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
+in the accreting and quiescent phases of \flower.
+The accreting phase of \flower displays a disturbed morphology (\Fig{MCC}) while the 
+quiescent phase displays a disk-like morphology (\Fig{MCC28}).
+Excluding the structure corresponding to the molecular disk, the 
+velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
 On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Gas velocity dispersions from bulk motions and turbulent motions for MCCs identified in accreting (top) and
-quiescent phase (bottom) of \flower across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}).
+\caption{Gas velocity dispersions resulting from bulk versus turbulent motions 
+for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and
+quiescent phase (bottom) of \flower.
 The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
@@
 
-The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
-as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e.
-$c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
+The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
+as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$.
+In particular, the average Mach number for MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
 
@@
 identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher
-density thresholds (top right panel).
+The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
+disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
 \label{fig:alpha16-28}}
@@
 % 
-MCCs with the highest \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower.
-This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio 
+($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}).
+A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
+On the other hand, the
+remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way
+but the former is more massive.
 
 % PVE
-Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
+Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the accreting phase of \flower in the bottom left panels of \Fig{larsons_single}.
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
@@
 At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
-Such variations in $\sigma^2/R$ is observed in GMCs of the Milky Way \citep{Heyer09a}.
-
-If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
-% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+Such variation in $\sigma^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.
+
+If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
 one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
@@
 % Starburst
-In the starburst phase, MCCs have similar velocity dispersion and sizes as those in the accreting phase; however, 
+In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
 MCCs in the starburst phase span a wider range in gas surface density 
@@
 That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
+The gas surface density of MCCs in both accreting and starburst phases is higher than the Milky Way at 8\,kpc, but comparable to 
+those observed in starburst galaxies and the nearby ULIRGs \citep{Boulares90a, Scoville91a, Weiss01a, Leroy15a}.
+% M82: 0.1 g cm^-2
+% Arp 220: 7-20 g cm^-2
 %
@@
 %
-Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+Such high velocity dispersion of MCCs in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
 
-The high pressure observed in \flower (see \citealt{Pallottini17a}) is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
+% The pressure of MCCs identified at the lowest $n_{\rm cut}$ ranges between $\log\left(P/K$\,\cc$\right)\in[6, 8.7]$, with a median of 7.4.
+The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
+Such high pressure is comparable to those observed in local ultra-luminous IR galaxies (ULIRGs; 
+e.g., \citealt{}); however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
 On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}.
-The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also be biased high due to the resolution limit.
+The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2.
+For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and
+molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based 
+on spatially resolved CO line \obs.
 
@@
 Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun and are supported by 
-non-thermal pressure. Similarly massive molecular structures (few times 10$^7$\,\Msun) have been
-reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the
-48\,kpc box studied by \citealt{Behrendt16a}); 
-owever, the IGM and merger and accretion histories are not properly modeled in such simulations.
+non-thermal pressure. Similarly massive molecular structures 
+have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{DonovanMeyer13a, Colombo14a, Leroy15a},
+and reported in idealized closed-box isolated galaxy simulations done at higher resolution 
+(e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}); 
+however, the IGM and merger and accretion histories are not properly modeled in such simulations.
 That said, the similar mass range found in MCCs of \flower\ is

### 2019-05-30 WRITEUP/ms.tex
checked sec 6.2

@@
 That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
-The gas surface density of MCCs in both accreting and starburst phases is higher than the Milky Way at 8\,kpc, but comparable to 
-those observed in starburst galaxies and the nearby ULIRGs \citep{Boulares90a, Scoville91a, Weiss01a, Leroy15a}.
+The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
+of the Milky Way and the LMC, but comparable to those observed in starburst galaxies and the nearby 
+ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
+% LMC: 0.01 g cm^-2
 % M82: 0.1 g cm^-2
@@
 The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
-Such high pressure is comparable to those observed in local ultra-luminous IR galaxies (ULIRGs; 
-e.g., \citealt{}); however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
+Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
 %
-First, due to energy dissipation on small-scales, such (sub-)structures are no longer supported by turbulence. 
+First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. 
 This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.

### 2019-05-30 WRITEUP/ms.tex
done with sec 6.2 and 7

@@
 nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
+
+At the highest density cut, only the densest gas structures are identified. This automatically excludes the molecular disk and arms 
+of \flower. The virial parameter of these MCCs indicates that most of them are unstable against collapse 
+(see middle right panel of \Fig{alpha16-28}).
 
@@
 on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution
-and sensitivity are needed. As such, observational studies on such scales are still missing in the literature.
-In this work, we aim to understand the origin and dynamical properties of molecular clouds complexes
-in prototypical galaxies at the EoR in numerical simulations
+and sensitivity are needed. As such, observational studies of MCCs on such scales are still missing in the literature.
+In this work, we aim to understand the origin and dynamical properties of MCCs in prototypical galaxies at the EoR 
+in numerical simulations
 to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
@@
 correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
-Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun and are supported by 
-non-thermal pressure. Similarly massive molecular structures 
-have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{DonovanMeyer13a, Colombo14a, Leroy15a},
+Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun. 
+Similarly massive molecular structures 
+have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, 
+DonovanMeyer13a, Colombo14a, Leroy15a},
 and reported in idealized closed-box isolated galaxy simulations done at higher resolution 
@@
 
-We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
+% We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
 %observed in the Milky Way disk, the Galactic center, and
@@
 
+The variation in $\sigma^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third law''  
+is an artifact arising from observational bias artifact of the limited range of 
+column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
+This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.
+
 MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
 Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
-These MCCs are, in fact, highly supersonic (with high Mach numbers).
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms);
-\DL{TBD} however,
-comparing the velocity dispersions of MCCs from bulk motions versus turbulence
-indicates that large-scale rotation is an important contributor, even in the
-accreting phase of \flower, which displays a highly disturbed morphology.
-....
+These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms).
+A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that most MCCs, excluding the arms and the disk of \flower, are supported by turbulence motions.
 
@@
 Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps
-indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against
+indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against
 axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also
-non-negligible. Our Toomre-Q analysis thus illustrates the importance of accounting for stellar contribution
+non-negligible. This illustrates the importance of accounting for stellar contribution
 and disk thickness when examining the stability of
@@
 
-We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of
-molecule gas structures. The high virial parameter found for some MCCs in \flower
-indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
-On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
-and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
-where energy quickly dissipates. % with low virial parameters.
-This is consistent with the notion that collapsing structures result from
+We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
+% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
+On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
+Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower 
+density thresholds. 
+% Such MCCs are thus susceptible to collapse. 
+% The high virial parameter found for some MCCs are found in regions of $Q_{\rm eff}>1$.
+% On the other hand, 
+Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
+Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
+where energy quickly dissipates. This is consistent with the notion that collapsing structures result from
 gravitational instability occurring within globally stable structures, which are
@@
 %%
-%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
-%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales.
 %Low-$Q$ sets the regions that fragments 
-%and within those regions where alphavir is low enough is where structures to further collapse to form stars.
-This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
+% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
+%
+%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with 
+% higher gas mass surface densities and velocity dispersions. 
+This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to 
+examine the truly star-forming structures (cores),
 and thus, \SF in the first galaxies.
-
-We examine temporal variations in the MCC dynamics over the course of 700\,Myr
-traced in our simulation. One of the most prominent differences is the virial parameter, more MCCs have lower virial parameters
-in the starburst phase compared to the accreting phase of \flower.
-
-% end
-Determining the multi-phase ISM properties of early galaxies
-is a critical piece to understanding the evolution and
-assembly history of galaxies, since they set the pace
-for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
-While observations leveraging the combination of spatial-spectral imaging of
-multi-band continuum and spectral line emission are crucial,
-we show in this work that prototypical galaxies at the EoR with properties similar to \flower
-are expected to have molecular gas structures on sub-kpc scales; however, these are not
-the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from
-large-scale motions even in a highly disturbed stage.
-This means that caution should be taken when interpreting observational data,
-albeit the impressive resolution and sensitivity that are unprecedented.
-%Careful consideration of large-scale motions is required
-%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR.
-Thus, with the resolution provided by existing data, it remains unclear whether \highz molecular gas structures
-are truly intrinsically more turbulent than those in the local ISM.
-This picture will become clearer as deeper and higher resolution imaging of
-molecular gas at \highz are obtained with ALMA and NOrthern Extended Millimeter Array (NOEMA) in the next few years, and
-potentially with the Next Generation VLA (ngVLA) in the 2030s.
+%
+%% end
+%Determining the multi-phase ISM properties of early galaxies
+%is a critical piece to understanding the evolution and
+%assembly history of galaxies, since they set the pace
+%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
+%While observations leveraging the combination of spatial-spectral imaging of
+%multi-band continuum and spectral line emission are crucial,
+%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
+%% are expected to have molecular gas structures on sub-kpc scales. 
+% Higher resolution imaging of molecular gas 
+Such resolution is within reach with ALMA. % 0.01" at the high freq bands
+The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc 
+via \aco line emission. % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy

### 2019-05-31 WRITEUP/ms.tex
revised abstract

@@
 \begin{abstract}
-We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
-$z\simeq 6$ prototypical galaxy (``\flower'').
-%
-We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter
-to \obs.
-%
-In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc, comparable to nearby spirals and starburst galaxies.
-%
-We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
+We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization using cosmological zoom-in simulation.
+We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
+using an H$_2$ density-based clump finder. 
+We compare their mass, size, velocity dispersion, gas surface density, and virial parameter to \obs and perform Toomre-Q stability 
+analysis to understand the origin and dynamical properties of MCC.
+%
+In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\simeq45-100$\,pc, 
+which are comparable to nearby spirals and starburst galaxies. 
+MCCs are highly supersonic and supported by non-thermal turbulence, with velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
+and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way).
+That said, their velocity dispersion and gas surface density are comparable to nearby and $z$\ssim2 gas-rich starburst galaxies.
+%
+We identify gravitationally unstable MCCs via Toomre $Q_{\rm eff}$ analysis and
 the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
-MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
-instability to % gravitational
-collapse.
-%
-Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
-%
-We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs.
-High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
-$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
+MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have low $\alpha_{\rm vir}$ 
+and $Q_{\rm eff}$ values, indicative of instability to collapse. 
+Star formation is expected to take place within the clumps and cores on smaller scales, where non-thermal energy 
+quickly dissipates and the gas structures are no longer supported by turbulence.
+%
+As such, spatial resolution of $\lesssim$40\,pc 
+is necessary to shed light on the star-forming gas dynamics since the cosmic dark ages which is 
+within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
 \end{abstract}
@@
 {\it what are the physical properties of
-molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
+molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop? }
 %
@@
 \begin{equation}
-\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \frac{3}{5} \pi G \Sigma \right)\,,
+\frac{\sigma_{\rm gas}^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \frac{3}{5} \pi G \Sigma \right)\,,
 \label{eqn:v0}
@@
 \begin{equation}
-\frac{\sigma^2}{R} = \frac{\pi}{5} G \Sigma\,,
+\frac{\sigma_{\rm gas}^2}{R} = \frac{\pi}{5} G \Sigma\,,
 \label{eqn:SVE}
@@
 \begin{equation}
-\alpha_{\rm vir} \equiv  \frac{5\sigma^2R}{GM_{\rm gas}} = \frac{5\sigma_{\rm gas}^2}{\pi G \Sigma R}\,,
+\alpha_{\rm vir} \equiv  \frac{5\sigma_{\rm gas}^2R}{GM_{\rm gas}} = \frac{5\sigma_{\rm gas}^2}{\pi G \Sigma R}\,,
 \label{eqn:alpha}
@@
 This is commonly done by
-identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMyer13a}).
+identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a}).
 %
@@
 Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
-(middle), and $\sigma^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
+(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
 MCCs (star symbols) identified in the two most extreme evolutionary
@@
 Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
-Such variation in $\sigma^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.
+At a given gas surface density, MCCs display a range of $\sigma_{\rm gas}^2/R$. 
+Such variation in $\sigma_{\rm gas}^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.
 
@@
 one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
-The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
+The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
 molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
@@
 The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
-%%
-%In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
-%%
 This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
@@
 
-The variation in $\sigma^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third law''  
+The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third law''  
 is an artifact arising from observational bias artifact of the limited range of 
@@
 These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms).
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies.
 A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that most MCCs, excluding the arms and the disk of \flower, are supported by turbulence motions.

### 2019-05-31 WRITEUP/ms.tex

@@
 have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
+However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations.
 That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
@@
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio 
-($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}).
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}).
 A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
-On the other hand, the
-remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way
-but the former is more massive.
+On the other hand, the  remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
 
@@
 
-If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
 (i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
@@
 
-% The pressure of MCCs identified at the lowest $n_{\rm cut}$ ranges between $\log\left(P/K$\,\cc$\right)\in[6, 8.7]$, with a median of 7.4.
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
+The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B \,{\rm K}\,{\rm cm}^{-3})\in[7, 9]$, with a median of 7.6.
 Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
@@
 %%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
-%%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
+%%If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds,
 %%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
@@
 Properties of the star-forming ISM of galaxies near the Epoch of Reionization are now within reach with ALMA.
-While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology
-on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution
-and sensitivity are needed. As such, observational studies of MCCs on such scales are still missing in the literature.
-In this work, we aim to understand the origin and dynamical properties of MCCs in prototypical galaxies at the EoR 
-in numerical simulations
-to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
-
-We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower,
-and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}),
-which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by
-UV radiation and metal lines, and detailed stellar feedback.
-Properties of \flower are briefly summarized in \Sec{sim}.
+While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution and sensitivity are needed.
+As such, observational studies of MCCs on such scales are still missing in the literature.
+%
+In this work, we aim to understand the origin and dynamical properties of MCCs in prototypical galaxies at the EoR in numerical simulations to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
+
+We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower, and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}), which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by UV radiation and metal lines, and detailed stellar feedback.
+%
 We use a three-dimensional clump-finding algorithm to identify MCCs.
-We decompose the molecular structures into non-overlapping objects by identifying a set of
-density contours with varying densities at multiple evolutionary stages.
+We decompose the molecular structures into non-overlapping objects by identifying a set of H$_2$ density contours with varying densities ($n_{\rm cut}$) at multiple evolutionary stages.
 Most notably, the accreting phase, starburst phase, and quiescent phase.
-We extract properties such as mass, size, Mach number, velocity
-dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M},
-\sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
-
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
-and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$.
-The $\sim$200\,pc-scale MCCs found with a low density threshold
-correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, \sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$.
+The $\sim$200\,pc-scale MCCs found with a low density threshold correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
+%
 Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun.
-Similarly massive molecular structures 
-have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, 
-DonovanMeyer13a, Colombo14a, Leroy15a},
-and reported in idealized closed-box isolated galaxy simulations done at higher resolution 
-(e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}); 
-however, the IGM and merger and accretion histories are not properly modeled in such simulations.
-That said, the similar mass range found in MCCs of \flower\ is
-reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
+Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
 On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.
@@
 
-The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third law''  
-is an artifact arising from observational bias artifact of the limited range of 
-column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
+The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
 This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.
 
-MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
-Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
+MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
 These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
@@
 % Toomre:
-Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps
-indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against
-axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also
-non-negligible. This illustrates the importance of accounting for stellar contribution
-and disk thickness when examining the stability of
-molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
-
+Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower.
+Similarly, stabilizing effect due to the thickness of its disk is also non-negligible.
+This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
+
+% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
 We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
-% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
 On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
@@
 Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
-Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
-where energy quickly dissipates. This is consistent with the notion that collapsing structures result from
-gravitational instability occurring within globally stable structures, which are
-supported by turbulence and rotation on large scale.
+Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
+This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
 %%
@@
 % higher gas mass surface densities and velocity dispersions. 
-This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to 
-examine the truly star-forming structures (cores),
-and thus, \SF in the first galaxies.
+This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
 %
@@
 Such resolution is within reach with ALMA. % 0.01" at the high freq bands
-The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc 
-via \aco line emission. % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
-On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
-statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining
-and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
+The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission. % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
+On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
 %These predictions can in turn be

### 2019-05-31 WRITEUP/ms.tex
Updates from Overleaf

--- 2019-05-30 WRITEUP/ms.tex
@@
 
-% TO edit:
-% alpha lesssim 2 MCCs are bounded. For reference, GMCs in MW and nearby galaxies: 0.1 - 10 \citep{Solomon87a, Bolatto08a, Heyer09a, Roman-Duval10a, Wong11a}
-
 \author{T. K. Daisy Leung\altaffilmark{1,2}}
@@
 \begin{abstract}
-We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
-$z\simeq 6$ prototypical galaxy (``\flower'').
-%
-We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter
-to \obs.
-%
-In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\lesssim100$\,pc, comparable to nearby spirals and starburst galaxies.
-%
-We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
-the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
-MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
-instability to % gravitational
+%mm rearranged sentence
+We study the properties of molecular cloud complexes (MCCs) in a cosmological zoom-in simulation of a
+prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
+%
+We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
+%
+In \flower, MCC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc.
+Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
+%
+We identify gravitationally unstable MCCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
+%mm (gas+stars), 
+    taking into account both gas and stars, 
+and by using a more observationally accessible $\alpha_{\rm vir}$ analysis.
+We find that MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
+%mm
+    instability to gravitational 
 collapse.
 %
-Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
-%
-We show that large-scale rotation is an important contributor to the velocity dispersion of some MCCs.
-High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
-$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
+%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
+%higher gas mass fraction, surface density, and velocity dispersion.
+% , which together sets the scale for fragmentation.
+\AF{Abstract is a bit thin. Revise at the end}
+High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
+%mm scrutinizing 
+data to test our findings and shed light on \SF since the cosmic dark ages.
 \end{abstract}
@@
 \section{Introduction}
-The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies.
-This gas fuels \SF and feeds central
-supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
+The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) 
+%mm to fuel \SF (and feed their  [using "to" implies purpose]
+     either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central
+supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium 
+%mm with 
+   by expelling some
 part of this material. 
-Existing studies indicated that early galaxies are more gas-rich with molecular fractions higher than
-those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
-Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs)
+%mm [now redundant with first sentence] The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic times.
+Back then,
+    Early
+galaxies 
+%mm themselves 
+are more gas-rich and their molecular fraction possibly higher 
+%mm compared to
+   than
+present-day galaxies.
+
+Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
+%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
+   cloud complexes (MCCs) 
 that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+%
 Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
@@
 %mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
-Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population \citep[see also a review by][]{Stark16a}.
-%
-As a consequence, we expect them to be significantly more ionized, and have intense and hard interstellar radiation fields (ISRF).
+Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population. 
+%
+As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF).
 Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced.
@@
 properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question:
-{\it what are the physical properties of
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
 molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
@@
 Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity).
-However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne;
-see e.g., the review by \citealt{CW13}).
-%
-To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of 
-galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
-Hodge16a, Leung19a}). These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
+%
+To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of (strongly-lensed) galaxies at intermediate-$z$, using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
+These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2), are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
 
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a,Smit18a}.
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Jones17a,Smit18a}.
 
@@
 %
-
 \section{Physical Background}\label{sec:Back}
@@
 Such notions will be used in the subsequent analysis of our simulations.
-
 \subsection{Larson relations and virial parameter}\label{sec:PVE}
 \citet{Larson81a} discussed a number of relations among Galactic 
+%mm MCC 
      molecular cloud 
@@
 They also represent a useful framework to analyze our results as they
-have been argued to arise from the interplay between gravity and turbulence encoded in the virial theorem
-(note, however, the alternative interpretation involving gravitational collapse by
-e.g., \citealt{Ballesteros-Paredes11a}).
+%mm
+     have been argued to 
+arise from the interplay between gravity and turbulence encoded in the virial theorem
+%mm 
+    (however, note the alternative interpretation involving gravitational collapse by 
+    \citealt{Ballesteros-Paredes11a}).
 
@@
 \begin{equation}
-\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
+\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M_{\rm gas} \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM_{\rm gas}^2}{R}\,,
 \label{eqn:virial}
 \end{equation}
-where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.
+where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the
+%mm  kinetic, external, and gravity pressure terms. 
+    kinetic energy, external pressure, and gravitational potential energy terms.
 
@@
     a molecular cloud.
-Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{Bertoldi92b}.
+Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
 %
@@
 In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
+\begin{equation}
+\alpha_{\rm vir, tot} \equiv \frac{5 R}{G} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
+					       {M_{\rm gas} + M_{\star} }\,,
+\label{eqn:alpha_tot}
+\end{equation}
+
+\AP{shouldn t it be something like}
 \begin{equation}
@@
 \end{equation}
+\AP{? Additionally, I am still unsure if the stellar dispersion should give a contribution to the alpha parameter, naively I would write it as}
+\begin{equation}
+\alpha_{\rm vir, tot} \equiv \frac{5 R \sigma_{\rm gas}^2}{G (M_{\rm gas} + M_{\star})}
+\label{eqn:alpha_tot}
+\end{equation}
+
 where $M_\star$ is the stellar mass within the MCC volume.
@@
 The onset of gravitational instability is tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
-For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
+For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by \AP{there might be too many $\sigma$}
 \begin{equation}
@@
 \end{equation}
-In the thin disk approximation ($kh\ll1$), instability occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$ in \Eq{3Ddisp}).
+In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$).
 A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
@@
 
-In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01a}, and for the non-negligible disk thickness.
+In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01}, and for the non-negligible disk thickness.
 This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
@@
 The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
-This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceeds the mass resolution by a factor of eight.
+This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceedes the mass resolution by a factor of eight.
 The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e.
@@
 Radiation pressure on dust and gas is also included.
-Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{Pallottini19a, Decataldo19a}.
-%
-Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{Agertz13a}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{Maclow99a}.
+Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}.
+%
+Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{agertz:2013}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{maclow1999turb}.
 See \citet{Pallottini17b} for further details.
@@
 %
-The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}.
-The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang2016}, which is higher than normal local galaxies.
+The effective stellar radius of \flower is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
 
@@
 
-\begin{figure*}[hptb]
+\begin{figure*}
 \centering
@@
 %
-%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and \section{•}
-atellite galaxies, thereby leading to bursts of \SF.
+%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
 Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
@@
 The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR accounts for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}.
-The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$\,Myr.
+The SFR of \flower varies between $\sim$30--80 \Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.
 
@@
 For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
-In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
-by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
+
+In \Sec{rot}, we investigate the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties 
+in the disturbed phase of \flower and in the disk-like ordered phase.
+
+Throughout this paper, we describe the dense gas regions outside the main disk of \flower as satellite galaxies.
+The distinction between clumps and satellites is admittedly somewhat ambiguous, though, and we consider it only as a working one.
+
+\AF{To be discussed at the end}
 
@@
 This is commonly done by
-identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMyer13a}).
+identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a}).
 %
@@
 
-In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
+In \Fig{h2density}, we show the distribution of H$_2$ number density $n_{\rm H2}$ for \flower~ during its accreting phase, including the contribution from the gas within 3.5 kpc from the galaxy center.
 %
@@
 %
-In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs
-are selected at $n_{\rm cut} \leq n_{\rm H2}$.
-We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
-% We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
-Note that with these choice we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
+In each evolutionary stage, we identify MCCs by applying density cuts to the H$_2$ density distriution, i.e.
+$n_{\rm H2}\geq n_{\rm cut}$.
+We select 10 equally-spaced cuts in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
+We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
+Note that with these choice we are including in the MCC also material that is not fully molecular ($n = 0.5 n_{\rm H2}$).
 
 To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
-Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
+Since the molecular structures are identified in the 3D H2 density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
 %
@@
 \sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
-% First term: large scale motion
-% second and last terms: small scale
 \label{eqn:veldisp}
@@
 In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
-Therefore, when calculating global quantities for MCS, we always perform a mass-weighting.
-Since we operate on data on a uni-grid, this is equivalent to density averaged quantities.
-In general, for the quantity $x$ in a MCC we write
-\begin{equation}\label{eqn:defineaverage}
-\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
-\end{equation}
-where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
-%
-The bulk velocity dispersion is
-\begin{equation}
-\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
-\end{equation}
+We therefore calculate each term on the right-hand side of Equation~\ref{eqn:veldisp} as a mass-weighted quantity.
+%
+The bulk velocity dispersion is then
+\begin{equation}
+\sigma_{\rm bulk}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the sum is done for the cells composing each MCC\footnote{Since we are calculating quantities on unigridded data, mass-weighted averages can be written as density weighted averages}.
 %
@@
 \begin{equation}
-c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
-\end{equation}
-where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
-Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
-\begin{equation}
-\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
-\end{equation}
-%
-Finally, the Mach number is related to the pressure terms as follows
-\begin{equation}
-\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
+c_s^2 = \frac{\sum_{i} \rho_i \left(P_i~{\rm k_B} / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,,
+\end{equation}
+where the pressure is in units of [K\,\cc], $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton.
+Similarly, the contribution from the non-thermal energy is calculated from the non-thermal pressure ($P_{\rm NT}$) as follows
+\begin{equation}
+\sigma_{\rm NT}^2 = \frac{\sum_{i} \rho_i \left(P_{\rm NT, i}~k_B / m_p / \rho_i \right)^2}{\sum_i \rho_i}\,.
+\end{equation}
+%
+Finally, the Mach number can expressed as follows
+\begin{equation}
+\mathcal{M} \equiv \frac{\sum_{i} \rho_i \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}}}{\sum_{i} \rho_i}.
 \label{eqn:MPress}
 \end{equation}
-
-\section{Results}\label{sec:results}
-
-\subsection{Distributions of MCC Basic Properties and Outlier} \label{sec:dist}
+\AP{in the following two paragraphs we are mixing results and expectations. The might be moved to th result section}
+As the non-thermal pressure contribution dominates the thermal one for dense gas \citet{Pallottini17b}, the local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities, i.e.
+$c_s^2 \ll \sigma_{\rm NT}^2$.
+In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds $\mathcal{M} \sim 10$ for \flower.
+%
+Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to $\sigma_{\rm NT}$, as the two are connected via the Euler equation \AP{do we want to add a plot here to showw the point?}, but this depends on the evolutionary stage of \flower.
+%
+%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.
+
+% allss: 0.32 
+% In [13]: print(get_Mach_all_clouds(ss11))
+%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
+%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
+%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
+%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
+%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
+%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
+%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
+%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
+%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
+%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
+%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
+%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
+%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
+% allss: 18.96
+%In [15]: print(get_Mach_all_clouds(ss12))
+%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
+%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
+%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
+%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
+%  5.05517168  6.93886988  5.4830306 ]
+% see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
+% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.
+
+The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold,  we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc) in the following.
+We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+\begin{equation}
+f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
+\end{equation}
+%
+We note that the distributions vary for different evolutionary stages of \flower.
+%
+The most massive ($M_{\rm gas}>$10$^8$\,\Msun) cloud identified at each density threshold (see top right corner of \Fig{stellarRatio16} and top left panel of \Fig{dist}) corresponds to the molecular disk of the galaxy, which is identified as a single component for low $n_{\rm cut}$.
+%
+Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, which is comparable to those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
+The gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,100 over all the MCCs identified across all evolutionary stages of \flower (see e.g., \Fig{stellarRatio16}).
+The main disk occupying the top right corner of \Fig{stellarRatio16} has a stellar-to-gas mass ratio of $\simeq$\,50--100.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower.
+The most massive MCCs have the highest stellar-to-gas mass ratio ($\gtrsim$\,1) as they correspond to a large part of \flower, and thus, 
+include a large number of stellar mass already ensembled in \flower \AP{please change $M_{cl}$ to $M_{\rm gas}$ in the figure}. 
+\label{fig:stellarRatio16}}
+\end{figure}
+
 \begin{figure*}[htbp]
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
-$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\caption{Distributions of mass (left), size (middle), and gas mass
+  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
+  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
+ over all times analyzed here.
+Note that the scalesshown on the $y$-axes are different between the top
+and bottom panels, as fewer MCCs are identified at higher $n_{\rm
+  cut}$. 
 \label{fig:dist}}
@@
 
-We start by considering the MCC distributions in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
-\begin{equation}
-f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
-\end{equation}
-%
-We show in \Fig{dist} the distributions considering all the evolutionary stages of \flower and dividing the sample in a low 
-($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
-%
-Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
-whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
-
-% address the biggest MCC = molecular disk of \flower
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
-The most massive MCC identified at low $n_{\rm cut}$ shows 
-a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
-and corresponds to the molecular disk of \flower (see also \Fig{vv}). Thus,
-it includes a large number of stellar mass that is already assembled in \flower. Such structure is excluded 
-in the discussion of MCC dynamics in the remainder of this paper.
-\label{fig:stellarRatio16}}
-\end{figure}
-
-The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
-which is identified as a single component at low $n_{\rm cut}$.
-This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?}
-stellar-to-gas mass ratio of $\simeq$\,50--100. 
-The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
-the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
-in the accreting and quiescent phases of \flower.
-The accreting phase of \flower displays a disturbed morphology (\Fig{MCC}) while the 
-quiescent phase displays a disk-like morphology (\Fig{MCC28}).
-Excluding the structure corresponding to the molecular disk, the 
-velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
-in the quiescent disk-like phase.
-
-The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper
-since its dynamics is dominated by large-scale shear.
-Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
-We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
-have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-However, the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions.
-That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
-
-\begin{figure}
-\centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Gas velocity dispersions resulting from bulk versus turbulent motions 
-for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and
-quiescent phase (bottom) of \flower.
-The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
-quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
-Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase. 
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
-in the quiescent disk-like phase.
-\label{fig:vv}}
-\vspace{0.5em}
-\end{figure}
-
-The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
-as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the average Mach number for MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
-
-\subsection{Single Evolutionary Stage}  \label{sec:singless}
+\section{Results}\label{sec:results}
 
@@
 (see Fig 4 of \citealt{Kauffmann17b}).   
-The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
-the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
+The gray dotted lines shown in the bottom panels correspond to the various external pressures for 
+gas in equilibrium, see Equation~\ref{eqn:v0}.
 \label{fig:larsons_single}}
@@
 
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
-%\caption{
-%Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
-%Star symbols are color-coded by
-%increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
-%Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}.
-%Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-%Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
-%constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
-%%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
-%%same as \Fig{larsons_single}.
-%%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
-%%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
-%For interpretation of this figure, see discussion in \Sec{MR}.
-%\label{fig:MR}}
-%\end{figure*}
-
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
-%\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
-%Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
-%Definition of symbols are same as in \Fig{larsons_single}.
-%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
-%The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
-%the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
-%post-starburst phase.
-%The variation is clearly seen between the pre-starburst through post-starburst phase.
-%Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
-%MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
-%\label{fig:alphaEvol}}
-%\end{figure*}
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
+\caption{
+Size-mass relation of MCCs identified in the accreting phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
+Red line shows the
+mass-size relation found for regions in the Milky Way with massive \SF
+reported by \citet{Kauffmann10b}. Star symbols are color-coded by
+increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
+Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
+Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
+constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
+%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
+%same as \Fig{larsons_single}.  
+Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
+relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
+\label{fig:MR}}
+%mm}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
+\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
+Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
+Definition of symbols are same as in \Fig{larsons_single}.
+Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
+The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
+the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through 
+post-starburst phase.
+The variation is clearly seen between the pre-starburst through post-starburst phase. 
+Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
+MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+\label{fig:alphaEvol}}
+\end{figure*}
 
@@
 identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
-disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
+The biggest MCCs identified at lowest density threshold, occupying the top right corner of the top left panel), are broken into smaller MCCs at higher 
+density thresholds (top right panel).
 \label{fig:alpha16-28}}
@@
 
-Here, we focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
-
-During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
-These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
+\subsection{Single Evolutionary Stage}  \label{sec:singless}
+
+We first present results on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+Scaling relations for the MCCs identified are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+
+Focusing on the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) 
+and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, 
+such as the nearby gas-rich galaxy M64 and 
+% Kennicutt, 1996IAUS..171...11K
+% Spiral gal, appears to have accreted a gas-rich companion in the recent past, 
+% with the inner gas disk the remnant of the
+% original disk (Braun et al. 1992; Rubin 1994; Rix et al. 1995). 
+the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 % SFR: 400, fgas ~ 0.6.
+\citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
 
 % middle
-While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
-% 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio 
-($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}).
-A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
-On the other hand, the
-remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way
-but the former is more massive.
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are 
+composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component 
+(i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of 
+some of them (see \Fig{stellarRatio16}). 
+MCCs with the highest stellar-to-gas mass ratio ($\gtrsim$\,1) correspond to the central main disk of \flower (see top panels of 
+\Fig{MCC} and \Fig{MCC28}, see also \Sec{distribution}), which includes a large fraction of stellar mass that are already assembled in \flower. 
+This explains the low total virial parameter seen in the most massive MCCs of \flower in this phase, as shown in
+the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influence the overall stability of such MCCs.
 
 % PVE
-Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the accreting phase of \flower in the bottom left panels of \Fig{larsons_single}.
+Motivated by observational studies, we also plot the $\sigma^2/R$ ratio and gas surface density of MCCs in the bottom left panels of \Fig{larsons_single}.
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
-Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-At a given gas surface density, MCCs display a range of $\sigma^2/R$. 
-Such variation in $\sigma^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.
-
-If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
-(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
-one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
-The variation in $\sigma^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
-molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
-is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
-column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
-%For instance, \citet{Ballesteros02a} show that the density
-%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-%two-dimensional space; the latter is done in \obs.
-%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
-%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
-%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
-%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
-%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
-%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).
-
-%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
-%\citep{Larson81a, McKee07a}.
-%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
-%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
-%the mass-size relation is also known as the constant column density relation and has been
-%proposed as a fundamental property of molecular clouds on different physical scales.
-%
-%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
-%\begin{equation}
-%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-%\end{equation}
-%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
-%\begin{equation}\label{eqn:constantcolumndensity}
-%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
-%\end{equation}
-%where we adopt $\mu = 2.5$ as the mean molecular weight.
-%
-%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
-%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-%Further discussions on the interpretation of this is provided in \Sec{MR}.
+Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium 
+to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
+% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf.
+Heyer+09).
+
+Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
+\citep{Larson81a, McKee07a}.
+Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density, 
+which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$), 
+the mass-size relation is also known as the constant column density relation and has been 
+proposed as a fundamental property of molecular clouds on different physical scales.
+
+By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
+\begin{equation}
+A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+\end{equation}
+Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
+\begin{equation}\label{eqn:constantcolumndensity}
+M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+\end{equation}
+where we adopt $\mu = 2.5$ as the mean molecular weight.
+
+We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the 
+Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
+\citet{Lombardi10a} in the MW. 
+%
+%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
+%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+5 therein]{Behrens18a}
+
+% Starburst 
+Focusing on MCCs in the starburst phase, they have similar velocity dispersion and sizes 
+as those in the accreting phase; however, the MCCs in the starburst phase span 
+a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters (thus, more susceptible to collapse).
+Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase
+(\Fig{alphaEvol}).
+Most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand, 
+the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase. 
+This is consistent with our physical intuition of gas instability leading to \SF.
+
+\subsection{Temporal Evolution and Adopted Density Threshold Dependence}\label{sec:ncut}
+
+We investigate possible variations in the dynamics of the molecular structures of \flower to test the robustness of our results against the 
+choice of density threshold by adopting different sets of $n_{\rm cut}$ in identifying the MCCs. That is, how sensitive are the structure properties, and thus, 
+the results presented in \Sec{singless} dependent on the choice of density thresholds.
+
+The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
+and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
+For instance, the cluster of points found at the lowest density threshold, 
+occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
+are broken down into sub-MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+that while the biggest MCCs are broken into sub-MCCs at higher $n_{\rm cut}$, MCCs identified at lower density in the outskirts of \flower
+typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}). 
+These sub-MCCs are smaller in size, and thus, are shifted leftward in the top right panel. 
+In this way, we identify a population of denser molecular structures (see \Fig{MCC}).
+
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun) have been 
+reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
+resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+However, the IGM and merger and accretion histories are not properly modeled in such simulations since 
+they adopt non-cosmological initial conditions. That said, the similar mass range found in MCCs of \flower\ is
+reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+The gas velocity dispersion $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.
 %% 
-%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
-%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
-5 therein]{Behrens18a}
-
-% Starburst
-In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
-MCCs in the starburst phase span a wider range in gas surface density 
-(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
-for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
-That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
-The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
-of the Milky Way and the LMC, but comparable to those observed in starburst galaxies and the nearby 
-ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
-% LMC: 0.01 g cm^-2
-% M82: 0.1 g cm^-2
-% Arp 220: 7-20 g cm^-2
-%
-% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
-%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
-%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
-%This is consistent with our physical intuition of gas instability leading to \SF.
-
-\subsection{Adopted Density Threshold Dependence}\label{sec:ncut}
-
-We investigate possible variations in the dynamics of the molecular structures of \flower 
-by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
-to test the robustness of our results against the choice of density threshold. 
-That is, how sensitive are the structure properties, and thus, the 
-results presented in \Sec{singless} dependent on the choice of density thresholds.
-
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
-As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
-corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
-$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
- since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
-Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
-(see top panels of \Fig{larsons_single}). 
-At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,100\,pc.
-%
-%For instance, the cluster of points found at the lowest density threshold, 
-%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
-%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
-%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
-%MCCs identified at lower density in the outskirts of \flower
-%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
-%%
-%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.
-
-%
-The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
+%We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results, i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of cloud scaling relations.
 %%
@@
 %%
-This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
-nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
-
-At the highest density cut, only the densest gas structures are identified. This automatically excludes the molecular disk and arms 
-of \flower. The virial parameter of these MCCs indicates that most of them are unstable against collapse 
-(see middle right panel of \Fig{alpha16-28}).
+This lack of variation is reassuring. Our inference on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in 
+nearby and \z$\sim$2 galaxies in the context of linewidth-size relation is thus not artifacts or biased by our choice of $n_{\rm cut}$ in this work.
+
+%Comparing the left and right panels, the mass range of MCCs identified at the highest density threshold 
+%is narrower by about an order of magnitude compared to those identified at the lowest density threshold.
+%MCCs identified in the lowest $n_{\rm cut} also have a wider gas surface density. These are a direct manifestation of the decrease in MCC size  
+%at increasing $n_{\rm cut}$.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCCs identified across all evolutionary stages in \Fig{alpha16-28}. 
+We find no quantitative differences over the 700\,Myr traced in our simulation, except 
+for the virial parameter, where the most relevant phases are shown in \Fig{alphaEvol} (see \Sec{singless}).
 
@@
 %--------------------------------------------------------------------------
-\section{Discussions}\label{sec:diss}
+\section{Discussions and Implications}\label{sec:diss}
 
@@
 
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-%%
-%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
-The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
-%
-Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion of MCCs in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
-In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-
-% The pressure of MCCs identified at the lowest $n_{\rm cut}$ ranges between $\log\left(P/K$\,\cc$\right)\in[6, 8.7]$, with a median of 7.4.
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B)\in[7, 9]$\,K\,\cc, with a median of 7.6\,K\,\cc.
-Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
+In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$, 
+$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
+Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
+linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
+the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
+$z$\ssim2 spatially resolved studies of gas-rich star-forming
+galaxies, in terms of their velocity dispersions, sizes, and gas
+surface densities (\Fig{larsons_single}; see e.g.,
+\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
+and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
+Their velocity dispersions are also comparable to those observed in the inner 
+Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the 
+locus of $\sigma\propto R^{0.56}$. 
+Such high velocity dispersions and surface densities can be explained partly because 
+these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest, 
+and also from the injection of kinetic energy from recent
+\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
+\flower has assembled a stellar mass of
+$M_\star$\eq7.5\E{9}\,\Msun. 
+Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that 
+the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in 
+its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in 
+interpreting observational results is further discussed in the next subsection (\Sec{rot}).
+
+The high pressure observed in \flower (see \citealt{Pallottini17a})
+is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
@@
 %
-In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
-On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}.
-The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2.
-For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and
-molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based 
-on spatially resolved CO line \obs.
+For instance, in local ULIRGs, MCCs are likely formed
+by shock compression and cloud-cloud collisions 
+ that funnel large amounts of gas from the progenitor galaxies
+ towards the central region
+\citep{Tan00a, Wu18a}.
+% Tasker09a
+On the other hand, the highly turbulent structures of \flower likely result from 
+extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
+The presence of such extra-planar flows may \MM{Do we have any
+  evidence for or against this speculation? Clarify citations and
+  mergers vs accretion...} also be the 
+dominant mode for forming the highly supersonic massive MCCs observed
+in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
+\citealt{Swinbank11a}) --- but the observed size scales could also be biased 
+high due to the resolution limit.
 
 % different evolutionary stages
-In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences in the MCC properties with respect to those observed in the nearby Universe between the accreting and starburst phase of \flower (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
-However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
+In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences
+in the MCC properties with respect to those observed in the nearby Universe 
+between the accreting and starburst phase of \flower (see
+\Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+However, MCCs in the pre-\SB phase have lower $\alpha_{\rm vir}$ compared to the starburst phase. 
+Similarly, the virial parameter is higher in the post-starburst phase compared to both the pre-\SB and \SB phases. 
 This is expected for \SF to proceed.
 
-%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
-%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
-%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
-%can be understood by acknowledging the fact that a given MCC in \flower
-%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
-%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
-%predictions for CO line emission in the work presented by
-%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
-%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
-%that the MCCs in our simulation have lower column densities than the
-%star-forming cores observed in the Milky Way, which are
-%observationally well-resolved within an MCC, and indeed, have
-%sufficient column density to form CO.
-%
-%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
-%This makes sense from simply the fact that smaller MCCs have smaller masses.
-%However, what does it mean for them to lie on the same locus?
-%
-%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
-%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
-%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
-%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
-%%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
-%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
-%%regions of massive \SF.
-%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
-%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
-%%  point on that relationship, at the constant $\Sigma$ value.  }
-%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
-%with a certain tracer (e.g., \citealt{Ballesteros11}).
-%That is, it is solely a result of $\rho\propto M R^{-3}$.
-%For instance, \citet{Ballesteros02a} show that the density
-%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-%two-dimensional space; the latter is done in \obs.
-%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
-%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
-%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
-%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
-%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
-%% since $M$ would then scale as $R^{3}$.
-%% naturally display a linear relationship in $\log M - \log R$ plot.
-%
-%% the widespread in density for a given R.
-%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
-%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
-%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
-%Following \citet{Ballesteros02a}'s argument, we expect the density
-%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
-%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
-%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$.
-%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
-%
-%\begin{figure}
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
-%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
-%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
-%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
-%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower.
-%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
-%\label{fig:n}}
-%\vspace{0.5em}
-%\end{figure}
+\subsection{Importance of Bulk Motions in Measured Velocity Dispersion} \label{sec:rot}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
+\caption{Velocity dispersions from bulk motions and turbulent motions of \flower in accreting (top) and 
+quiescent phase (bottom). The accreting phase (\Fig{MCC}) displays a more disturbed morphology compared to the 
+quiescent phase, which displays a disk-like morphology (\Fig{MCC28}). 
+The velocity dispersion from turbulent motions is higher than that from bulk motions for most MCCs in the accreting phase, but 
+the opposite is true in the quiescent phase. Thus, large-scale motion plays an important role in contributing to the total velocity dispersion. 
+This implies that the velocity dispersion measured in molecular gas structures from \obs on similar physical scales 
+should not be taken as direct evidence that these structures at high redshifts are intrinsically more turbulent than those in the local ISM.
+% either higher resolution, or properly accounting for large scale motions. 
+\label{fig:vv}}
+\vspace{0.5em}
+\end{figure}
+
+We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting 
+and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase 
+but a disk-like morphology in the quiescent phase 
+(see \Fig{MCC} and \Fig{MCC28}). 
+Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
+whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude. 
+{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here 
+have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures 
+on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
+and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
+
+\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
+The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
+by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
+can be understood by acknowledging the fact that a given MCC in \flower 
+does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and 
+our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
+predictions for CO line emission in the work presented by 
+\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
+That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
+that the MCCs in our simulation have lower column densities than the
+star-forming cores observed in the Milky Way, which are
+observationally well-resolved within an MCC, and indeed, have
+sufficient column density to form CO.
+
+In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases. 
+This makes sense from simply the fact that smaller MCCs have smaller masses. 
+However, what does it mean for them to lie on the same locus?
+% is it what Jen's proposed? Or is it's just a result of $\rho\propto M R^{-3}$ (and $\rho$ is independent of R) 
+% and observational bias (selection effect due to projection in 2D, so $\rho \propto N_H R^{-1}$, where $N_H$ is a 
+% constant due to gas tracer) (i.e., middle and bottom panels of Fig 9 in BM02)?
+
+The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
+an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
+If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond 
+to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
+If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds, 
+one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as 
+regions of massive \SF. 
+%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+%  point on that relationship, at the constant $\Sigma$ value.  }
+However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
+with a certain tracer (e.g., \citealt{Ballesteros11}). 
+That is, it is solely a result of $\rho\propto M R^{-3}$. 
+For instance, \citet{Ballesteros02a} show that the density 
+of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of 
+two-dimensional space, as is done in \obs. 
+When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given 
+line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant. 
+They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$ 
+observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in 
+observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+% since $M$ would then scale as $R^{3}$.
+% naturally display a linear relationship in $\log M - \log R$ plot.
+
+% the widespread in density for a given R. 
+We show the density-size relation ($\rho - R$) relation of MCCs of \flower in \Fig{rho}.
+The interpretation of this figure is not that MCCs with small $R$ are found at high $n_{\rm cut}$ and large $R$ at low $n_{\rm cut}$, nor is that
+the density of MCCs is independent of $R$. Rather, it is as we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and 
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+\DL{This is puzzling to me why we are seeing some really steep relationship between $\rho$ and $R$, almost $\rho \propto R^{-6}$ 
+even though we are identifying the structures in 3D just like what BM02 did.}
+
+\begin{figure}
+\centering
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16} 
+\caption{Density and size of MCCs in the accreting phase of \flower.
+At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and 
+form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+\label{fig:rho}}
+\vspace{0.5em}
+\end{figure}
 
@@
 highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
-\AP{maybe it is better to put a single set of maps, with FOV from -1.5 to 1.5 kpc}
 \label{fig:Qeff}}
@@
 
-We define Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ in \Sec{Q}.
-Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff}
-(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
-
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations.
+Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in \Fig{Qeff}
+(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower
+using different $n_{\rm cut}$).
+
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against $m$\eq0 perturbations.
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
-
-That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
-Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
-%
-This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures.
-This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA.
-In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$.
+Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and 
+has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
+
+That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that 
+they correspond to regions of high surface densities that are gravitationally unstable. 
+Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
+thickness of its disk (via $\sigma_z$, see Equation~\ref{eqn:q_eff}), some of these MCCs are
+consistent with $Q_{\rm eff} > 1$. 
+This demonstrates the importance of accounting for stellar contribution and disk thickness 
+when examining the stability of molecular gas structures.
+This consideration is especially relevant for the relatively evolved and enriched systems at high redshift,
+that are preferentially being imaged at high resolution with ALMA.
+In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
+both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
 Notably, these are the more gas-rich regions (see \Fig{sigma}).
 
-The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
-%
-Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
-%
-This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
-%
-Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
-On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
-
-If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
+The large virial parameters seen in some MCCs of \flower can be understood 
+by first noting that fragmentation {\em can} happen in regions of low $Q$ 
+(if we only consider instability against axisymmetric perturbations), 
+but further evolution/collapse depends on the dynamics or equation of state of the gas.
+%
+Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. 
+Second, this fragmentation scale is greater than the typical size of GMCs. 
+% 
+This could be interpreted as a result of instability setting the scales for fragmentation, 
+{\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
+%
+Thus, the high virial parameter found for some MCCs in \flower 
+indicates that they are not the collapsing structures (but the virial parameter varies depending on the evolutionary stage 
+of \flower) and are found in regions of $Q_{\rm eff}>1$.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
+and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
+where energy quickly dissipates. % with low virial parameters.
+
+If most of the MCCs in \flower are stable against collapse, 
+how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? 
 Such tension in the interpretation is understood as follows.
 %
-First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. 
-This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
-% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
+First, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
+This re-iterates the statement about low $Q$ above.
+%
+Second, due to turbulence dissipation on small-scales, such
+(sub-)structures are no longer supported by differential rotation. 
+This in turn enables sub-regions of the MCCs to collapse and potentially form 
+OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
+% Mechanisms causing non-axisymmetric perturbations (e.g.,
+% arms) to the gravitational potential \MM{Gravitational instability is
+%   that mechanism (see e.g.\ Wada et al.'s classic review of the
+%   subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} 
+% can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
 These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
 Further, the SFR of \flower is very bursty and high SFR stages are only transient.
-%
-Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
-This re-iterates the statement about low $Q$ above.
 
@@
 on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution
-and sensitivity are needed. As such, observational studies of MCCs on such scales are still missing in the literature.
-In this work, we aim to understand the origin and dynamical properties of MCCs in prototypical galaxies at the EoR 
-in numerical simulations
+and sensitivity are needed. As such, observational studies on such scales are still missing in the literature. 
+In this work, we aim to understand the origin and dynamical properties of molecular clouds complexes 
+in prototypical galaxies at the EoR in numerical simulations 
 to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
@@
 Properties of \flower are briefly summarized in \Sec{sim}.
-We use a three-dimensional clump-finding algorithm to identify MCCs.
+We use a three-dimensional clump-finding algorithm to identify MCCs and their sub-structures. 
 We decompose the molecular structures into non-overlapping objects by identifying a set of 
-density contours with varying densities at multiple evolutionary stages.
+density contours with varying cutoff densities at multiple evolutionary stages. 
 Most notably, the accreting phase, starburst phase, and quiescent phase. 
@@
 dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, 
-\sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
+\sigma, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
 
 The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, 
-and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$.
+and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$. 
 The $\sim$200\,pc-scale MCCs found with a low density threshold
 correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
-Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun. 
-Similarly massive molecular structures 
-have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, 
-DonovanMeyer13a, Colombo14a, Leroy15a},
-and reported in idealized closed-box isolated galaxy simulations done at higher resolution 
-(e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}); 
-however, the IGM and merger and accretion histories are not properly modeled in such simulations.
+Overall, the mass of MCCs ranges between $10^{5.5-8.5}$\,\Msun, depending on the chosen density threshold.
+This mass range is comparable to those observed in \z\ssim2 galaxies in rest-frame UV and optical wavelengths.
+Similarly massive molecular structures (few times 10$^7$\,\Msun) have been 
+reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 
+48\,kpc box studied by \citealt{Behrendt16a}). 
+However, the IGM and merger and accretion histories are not properly modeled in such simulations. 
 That said, the similar mass range found in MCCs of \flower\ is
 reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
-On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.
-
-% We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
-%observed in the Milky Way disk, the Galactic center, and
-%gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations.
-%This comparison is done for different evolutionary stages of \flower.
-
-The variation in $\sigma^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third law''  
-is an artifact arising from observational bias artifact of the limited range of 
-column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
-This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.
+On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the adopted density threshold.
+
+We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
+observed in the Milky Way disk, the Galactic center, and 
+gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations. 
+This comparison is done for different evolutionary stages of \flower.
 
@@
 Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted. 
-These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms).
-A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that most MCCs, excluding the arms and the disk of \flower, are supported by turbulence motions.
+These MCCs are, in fact, highly supersonic (with high Mach numbers).
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma\simeq200$\,\kms); however, 
+comparing the velocity dispersions of MCCs from bulk motions versus turbulence 
+indicates that large-scale rotation is an important contributor, even in the 
+accreting phase of \flower, which displays a highly disturbed morphology. 
+This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date. 
+In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc) 
+should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM, 
+unless contributions from bulk motions are properly accounted for.
+%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution 
+%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used 
+%for structures in the literature) are more turbulent based on solely measured velocity dispersion.
+
+We do not observe any significant temporal variations in the MCC dynamics over the course of 700\,Myr
+traced in our simulation, except in the virial parameter, which is the lowest in the pre-starburst phase. 
+The virial parameter increases after a starburst as gas is self-regulated by feedback.
 
@@
 Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps 
-indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against
+indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against
 axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also 
-non-negligible. This illustrates the importance of accounting for stellar contribution
+non-negligible. Our Toomre-Q analysis thus illustrates the importance of accounting for stellar contribution 
 and disk thickness when examining the stability of 
@@
 
-We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
-% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
-On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
-Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower 
-density thresholds. 
-% Such MCCs are thus susceptible to collapse. 
-% The high virial parameter found for some MCCs are found in regions of $Q_{\rm eff}>1$.
-% On the other hand, 
-Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
-Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales,
-where energy quickly dissipates. This is consistent with the notion that collapsing structures result from
-gravitational instability occurring within globally stable structures, which are
+We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of 
+molecule gas structures. The high virial parameter found for some MCCs in \flower 
+indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
+and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
+where energy quickly dissipates. % with low virial parameters.
+This is consistent with the notion that collapsing structures result from
+gravitational instability occuring within globally stable structures, which are
 supported by turbulence and rotation on large scale.
 %% 
+%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
+%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales. 
 %Low-$Q$ sets the regions that fragments 
-% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
-%
-%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with 
-% higher gas mass surface densities and velocity dispersions. 
-This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to 
-examine the truly star-forming structures (cores),
+%and within those regions where alphavir is low enough is where structures to further collapse to form stars. 
+This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
 and thus, \SF in the first galaxies.
-%
-%% end
-%Determining the multi-phase ISM properties of early galaxies
-%is a critical piece to understanding the evolution and
-%assembly history of galaxies, since they set the pace
-%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
-%While observations leveraging the combination of spatial-spectral imaging of
-%multi-band continuum and spectral line emission are crucial,
-%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
-%% are expected to have molecular gas structures on sub-kpc scales. 
-% Higher resolution imaging of molecular gas 
-Such resolution is within reach with ALMA. % 0.01" at the high freq bands
-The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc 
-via \aco line emission. % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
+
+% end
+Determining the multi-phase ISM properties of early galaxies
+is a critical piece to understanding the evolution and
+assembly history of galaxies, since they set the pace
+for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
+While observations leveraging the combination of spatial-spectral imaging of
+multi-band continuum and spectral line emission are crucial, 
+we show in this work that prototypical galaxies at the EoR with properties similar to \flower
+are expected to have molecular gas structures on sub-kpc scales; however, these are not 
+the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from 
+large-scale motions even in a highly disturbed stage.
+This means that caution should be taken when interpreting observational data, 
+albeit the impressive resolution and sensitivity that are unprecedented. 
+%Careful consideration of large-scale motions is required 
+%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR. 
+It is thus currently unclear whether \highz molecular gas structures are truly intrinsically more turbulent than those in the local ISM. 
+This will become clearer in the next few years as deeper and higher resolution imaging of 
+molecular gas at \highz are observed with ALMA and NOrthern Extended Millimeter Array (NOEMA). 
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
@@
 %-------------------------------------
-% \acknowledgements
-
-\section*{Acknowledgements}
+\acknowledgements
+
 We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
 %
-TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
+TKDL acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
 %
@@
 H2020/740120.
-% mm
+%mm
     M-MML acknowledges partial support by the NSF through award
@@
 
+\begin{comment}
+\appendix
+\section{Variation in MCC Properties Depending on the Choice of Density Cuts and Temporal Evolution in Cloud Dynamics}    \label{sec:ncut}
+% single Snapshot
+We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites to test the robustness of our results against the choice of density threshold by adopting
+different sets of $n_{\rm cut}$ in identifying the MCCs.
+That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless} dependent on the choice of density thresholds.
+We vary the choice of H$_2$ density for each of the evolutionary stages and find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
+cloud scaling relations).
+%
+In addition, for the densest MCC in the main disk of \flower, we find that while its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, the velocity dispersion remain approximately $\sigma\simeq$\,200\,\kms (see also \Fig{larsons_single}).
+%
+This lack of variation is reassuring, in the sense that at least on the scales studied here, the dynamics of the MCCs are not artifacts or biased by our choice of $n_{\rm cut}$.
+Our results are therefore robust to the various density cuts of choice.
+
+% temporal evolution in Cloud Dynamics
+We show the properties of all MCCs identified across all evolutionary stages in \Fig{larsons16-28} and \Fig{alpha16-28}.
+We find no quantitative differences in the cloud properties over the 700\,Myr traced in our simulation.
+
+% -------------- all snapshots -----------
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=0 100 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
+\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
+\caption{
+%Comparison of MCCs identified across all evolutionary stages (over 700\,Myr; star symbols)
+to those observed in nearby and \z$\sim$2 star-forming galaxies
+in the context of the linewidth-size relation.
+%Bottom panel corresponds to including only the denser substructures/sub-MCCs identified in \flower
+(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+By and large, we find no quantitative differences in the mass-size relation over the 700\,Myr traced in the simulation.
+\label{fig:larsons16-28}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+\centering
+\includegraphics[trim=5 5 8 8, clip, width=0.515\textwidth]{\figpath/ss16-28_alphavir.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
+\includegraphics[trim=5 5 8 8, clip, width=0.512\textwidth]{\figpath/ss16-28_PVE.png}
+\includegraphics[trim=50 5 5 6, clip, width=0.472\textwidth]{\figpath/ss16-28-PVE-highncut.png}
+\caption{
+Same as \Fig{alpha16} (top panels) and \Fig{alpha27} (bottom panels), but for MCCs identified across all evolutionary stages
+(i.e., with different SFR). Star symbols are color-coded by increasing SFR.
+Right panels correspond to including only the denser substructures/sub-MCCs identified in \flower
+(i.e., MCCs here are identified with the highest $n_{\rm cut}$, see \Sec{method}).
+We find no obvious differences in relation to those observed in nearby and \highz
+galaxies in the context of these cloud scaling relations.
+\label{fig:alpha16-28}}
+\end{figure*}
+\end{comment}
+
 \end{document}

### 2019-06-15 WRITEUP/ms.tex
minor comments added; i would substitute figure 3 and 4 with 5 (it is packed version)

--- 2019-05-31 WRITEUP/ms.tex
@@
 \caption{Distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
-    (b)}.
+    (b)} \AP{what is the normalization/axis here? I would plot the distribution such that the integral on the function is 1}.
 \label{fig:h2density}}
@@
 Left and right panels show the galaxy from different viewing angles.
-\label{fig:MCC}}
+\label{fig:MCC}\AP{see \Fig{MMCidentification} for an alternative version}}
 \end{figure*}
@@
 \caption{
-Same as \Fig{MCC}, except we show the quiescent phase of \flower, which is supported by rotation.
-\label{fig:MCC28}}
+Same as \Fig{MCC} for the quiescent phase of \flower, when the galaxy is supported by rotation.
+\label{fig:MCC28} \AP{see \Fig{MMCidentification} for an alternative version}}
+\end{figure*}
+
+\begin{figure*}[htbp]
+ \centering
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}
+
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}
+
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
+\caption{\AP{proposed alternative to substitute \Fig{MCC} and \Fig{MCC28}; if adopted, label with the phase should be included in the first row}
+\label{fig:MMCidentification}
+}
 \end{figure*}
@@
 $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\AP{I would normalize the distributions such that their sum is 100\% (bin width already accounted for), so that the comparison is more direct; on a side, could we use a different shade of blue?
+(see also \Fig{h2density})} Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}
@@
 \caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
-The most massive MCC identified at low $n_{\rm cut}$ shows 
-a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} 
-and corresponds to the molecular disk of \flower (see also \Fig{vv}). Thus,
-it includes a large number of stellar mass that is already assembled in \flower. Such structure is excluded 
-in the discussion of MCC dynamics in the remainder of this paper.
+The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} and corresponds to the molecular disk of \flower (see also \Fig{vv}).
+%
+Thus, it encloses a large of stellar mass that is already assembled in \flower.
+The disk structure is excluded in the discussion of MCC dynamics in the remainder of this paper.
+\AP{minor mod: legend with horizontal alignment, text with arrows pointing to the disk and proper MMC clouds of points}
 \label{fig:stellarRatio16}}
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Gas velocity dispersions resulting from bulk versus turbulent motions 
-for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and
-quiescent phase (bottom) of \flower.
-The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the
-quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and quiescent phase (bottom) of \flower.
+%
+The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+%
 Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
-in the quiescent disk-like phase.
+On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
 \label{fig:vv}}
@@
 The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2.
-For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and
-molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based 
-on spatially resolved CO line \obs.
+For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.
 
@@
 \caption{
-Toomre $Q$ maps derived from the
-central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
-Gas-only $Q_{\rm gas}$ is shown in the left panels and stellar-only $Q_\star$ is shown in the middle panels.
+Toomre $Q$ maps derived from the central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
+The contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown separately in the left and middle panels, respectively.
 Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
-All maps are projected onto the $xy$-plane.
+%
+All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
+%
 Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
-A smoothing length of 30\,pc has been applied to the maps.
-A divergent colormap is used for the Toomre $Q$ maps to facilitate
-identification of regions above and below $\log{Q}$\eq0.
-Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
-are likely gravitationally unstable.
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} of \flower
-indicates that the stellar component plays an important role in
-governing the stability of the MCCs against $m=0$  perturbations,
-highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
+%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
+Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
+%
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} of \flower indicates that the stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
 \AP{maybe it is better to put a single set of maps, with FOV from -1.5 to 1.5 kpc}
@@
 We define Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ in \Sec{Q}.
-Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff}
-(see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
+Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
 
@@
 Properties of the star-forming ISM of galaxies near the Epoch of Reionization are now within reach with ALMA.
-While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology on sub-kpc scales and even smaller, such \obs remain time-consuming; logistically, data from multiple cycles pushing to increasing resolution and sensitivity are needed.
+While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology on sub-kpc scales and even smaller, such \obs remain challenging; logistically, data from multiple cycles pushing to increasing resolution and sensitivity are needed.
 As such, observational studies of MCCs on such scales are still missing in the literature.
@@
 
-We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower, and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}), which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by UV radiation and metal lines, and detailed stellar feedback.
+We study the dynamics of MCCs and their temporal evolution in \flower, a \z$\sim$\,6 prototypical galaxy obtained from the state-of-the-art cosmological zoom-in simulations \ncode{Serra}, which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by UV radiation and metal lines, and detailed stellar feedback.
 %
 We use a three-dimensional clump-finding algorithm to identify MCCs.
-We decompose the molecular structures into non-overlapping objects by identifying a set of H$_2$ density contours with varying densities ($n_{\rm cut}$) at multiple evolutionary stages.
-Most notably, the accreting phase, starburst phase, and quiescent phase.
+We decompose the molecular structures into non-overlapping objects by using a set of H$_2$ density contours ($n_{\rm cut}$) at multiple evolutionary stages, in particular focusing on the accreting phase, starburst phase, and quiescent phase.
 We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, \sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
@@
 
+\AP{the following should be removed if the corresponding point in the main text is commented out (as it has been now)}
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
@@
 
+% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
+We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
+On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
+Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
+% Such MCCs are thus susceptible to collapse. 
+% The high virial parameter found for some MCCs are found in regions of $Q_{\rm eff}>1$.
+% On the other hand, 
+Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
 % Toomre:
@@
 This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
-
-% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
-We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
-On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
-Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower
-density thresholds. 
-% Such MCCs are thus susceptible to collapse. 
-% The high virial parameter found for some MCCs are found in regions of $Q_{\rm eff}>1$.
-% On the other hand, 
-Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
+%
 Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
@@
 % Higher resolution imaging of molecular gas 
-Such resolution is within reach with ALMA. % 0.01" at the high freq bands
-The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission. % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
+Such resolution is within reach with ALMA, for which 0.01" resolution images are available for the high freq bands.
+The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission.
+% 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

### 2019-06-15 WRITEUP/ms.tex
minor edits

@@
 
-% This is the messy stage
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
-  \\ [-2.9em]
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
-  \\ [-2.9em]
-  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
-\caption{
-Examples of MCCs (white contours) identified by the clump finder in
-\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated.
-Colorbar on the right shows the mean
-H$_2$ number density, weighted by gas mass.
-Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label.
-Left and right panels show the galaxy from different viewing angles.
-\label{fig:MCC}\AP{see \Fig{MMCidentification} for an alternative version}}
-\end{figure*}
-
-% Add a figure that shows \flower in "disky" stage. We are interested in exploring whether the MCC properties are dependent on the disk properties.
-% In other words, if the nature of the MCCs we are identifying are large chucks of arms/disk in \flower, then its dynamics that we are deriving will be dominated by
-% large-scale shear.
-\begin{figure*}[htbp]
- \centering
-  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_0.53}.pdf}
-  \\ [-2.7em]
-  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_6.81}.pdf}
-  \\ [-2.7em]
-  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_18.96}.pdf}
-\caption{
-Same as \Fig{MCC} for the quiescent phase of \flower, when the galaxy is supported by rotation.
-\label{fig:MCC28} \AP{see \Fig{MMCidentification} for an alternative version}}
-\end{figure*}
-
 \begin{figure*}[htbp]
@@
   \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
-\caption{\AP{proposed alternative to substitute \Fig{MCC} and \Fig{MCC28}; if adopted, label with the phase should be included in the first row}
-\label{fig:MMCidentification}
+\caption{
+Examples of MCCs (white contours) identified by the clump finder in
+\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
+its quiescent phase, which is rotation-dominated (right two columns).
+Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
+in the quiescent phase.
+Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
+\AP{label with the phase should be included in the first row}
+\label{fig:MCC}
 }
@@
 To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
-Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections (right panels of \Fig{MCC}) so that the identification can be more easily appreciated.
+Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections so that the identification can be more easily appreciated.
 %
@@
 in the accreting and quiescent phases of \flower.
-The accreting phase of \flower displays a disturbed morphology (\Fig{MCC}) while the 
-quiescent phase displays a disk-like morphology (\Fig{MCC28}).
+The accreting phase of \flower displays a disturbed morphology, whereas the 
+quiescent phase displays a disk-like morphology (\Fig{MCC}).
 Excluding the structure corresponding to the molecular disk, the 
@@
 %
-The accreting phase (\Fig{MCC}) of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC28}).
+The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC}).
 %
@@
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Fig{MCC28}, and \Sec{distribution}).
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
 A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
@@
 
-\AP{the following should be removed if the corresponding point in the main text is commented out (as it has been now)}
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.

### 2019-06-23 WRITEUP/ms.tex
combined figures and bigger fonts

@@
  \centering
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}
-
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}
-
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_0.53}.pdf} \hspace{-1.2em}
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_0.53}.pdf}
+
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_6.81}.pdf} \hspace{-1.2em}
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_6.81}.pdf}
+
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_18.96}.pdf} \hspace{-1.2em}
+  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_18.96}.pdf}
 \caption{

### 2019-06-23 WRITEUP/ms.tex
accted for AP comment

--- 2019-06-15 WRITEUP/ms.tex
@@
  \centering
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}
-
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}
-
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
-  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
+  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
 \caption{
 Examples of MCCs (white contours) identified by the clump finder in
-\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
-its quiescent phase, which is rotation-dominated (right two columns).
-Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
-in the quiescent phase.
+\flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
+its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
+Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
 Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
-Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
-\AP{label with the phase should be included in the first row}
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as annotated by the label in the bottom left corners. 
 \label{fig:MCC}

### 2019-06-24 plotSS.py
matching color blue across plots, normalized distributions

@@ -102,28 +102,30 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     # fig = plt.figure(figsize=(13, 6))
     # ax = fig.subplots(2, 3)
 
-    fig, ax = plt.subplots(nrows=2, ncols=3, figsize=(14, 3.5))
-    fig.subplots_adjust(left=0.12, wspace=0.18, bottom=0.1, top=0.95, hspace=0.0)
+    fig, ax = plt.subplots(nrows=2, ncols=3, figsize=(16, 5))
+    fig.subplots_adjust(left=0.12, wspace=0.18, bottom=0.1, top=0.95, hspace=0.2)
 
     # # separate allmasses into two color scheme
     # med11 = allmass11.median()
     # mask11_low = allmass11 <= med1
     # mask11_high = allmass11 >= med1
 
-    fig.text(0.05, 0.95, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1, rotation=90)
-    fig.text(0.05, 0.43, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2, rotation=90)
+    fig.text(0.05, 0.95, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1, rotation=90, fontsize=20)
+    fig.text(0.05, 0.43, r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern2, rotation=90, fontsize=20)
 
     binwidth = 0.1
     allmass11 = np.log10(get_masses_all_clouds(ss11))
-    ax[0, 0].hist(allmass11, bins=np.arange(min(allmass11), max(allmass11) +binwidth, binwidth))
+    weights = np.ones_like(allmass11)/float(len(allmass11))
+    ax[0, 0].hist(allmass11, bins=np.arange(min(allmass11), max(allmass11) +binwidth, binwidth), weights=weights)
 #     ax[0, 0].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1)
-    ax[0, 0].set_title(r'$\log M_{\rm cl}$ [M$_{\odot}]$')
-    ax[0, 0].set_ylabel(r'$N$')
+    ax[0, 0].set_title(r'$\log M_{\rm cl}$ [M$_{\odot}]$', fontsize=20)
+    ax[0, 0].set_ylabel(r'$N$', fontsize=20)
     ax[0, 0].set_xlim([5.7, 8.5])
[…]

### 2019-06-24 plot_modules/plot_cloud_prop.py

@@ -23,7 +23,7 @@ def setup_plot():
                                 , 'legend.fontsize': 10      # points
                                 , 'lines.linewidth': 2       # points
                                 , 'axes.linewidth': 1       # points
-                                , 'axes.prop_cycle': cycler('color', 'bgrcmyk')
+                                # , 'axes.prop_cycle': cycler('color', 'bgrcmyk')
                                 , 'text.usetex': True
                                 , 'font.family': "serif"  # Use serifed fonts
                                 , 'xtick.major.size': 13     # length, points

### 2019-06-24 WRITEUP/ms.tex
updated fig caption

@@
 the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
-MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have low $\alpha_{\rm vir}$ 
-and $Q_{\rm eff}$ values, indicative of instability to collapse. 
-Star formation is expected to take place within the clumps and cores on smaller scales, where non-thermal energy 
-quickly dissipates and the gas structures are no longer supported by turbulence.
-%
-As such, spatial resolution of $\lesssim$40\,pc 
-is necessary to shed light on the star-forming gas dynamics since the cosmic dark ages which is 
+MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have lower $\alpha_{\rm vir}$ 
+and $Q_{\rm eff}$ values, % indicative of instability to collapse. 
+where star formation is expected to take place within the clumps and cores on even smaller scales, as non-thermal energy 
+quickly dissipates. % and the gas structures are no longer supported by turbulence.
+%
+As such, detailed studies on the star-forming gas dynamics at EoR requires a spatial resolution of $\lesssim$40\,pc, which is 
 within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
@@
 {\it what are the physical properties of
-molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop? }
+molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
 %
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a,Smit18a}.
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
 
@@
 and present the formalism within which we interpret the results.
-In \Sec{results}, we present the results and the scaling relations for the MCCs.
+In \Sec{results}, we present the results and characteristic properties of the MCCs.
 We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation.
+We begin by introducing some basic equations concerning the empirical relations commonly mentioned in observational studies of molecular clouds in the literature and the gravitational instability of galactic disks, which might be driving MCC formation.
 Such notions will be used in the subsequent analysis of our simulations.
 
-\subsection{Larson relations and virial parameter}\label{sec:PVE}
+\subsection{Larson's Relations and Virial Parameter}\label{sec:PVE}
 \citet{Larson81a} discussed a number of relations among Galactic
@@
 We are interested in determining whether MCC properties are sensitive to these different dynamical conditions.
-For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
+For completeness, we also show relationships of MCC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).
 In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
-\caption{Distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
-    (b)} \AP{what is the normalization/axis here? I would plot the distribution such that the integral on the function is 1}.
+\caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
+    (a)}.
 \label{fig:h2density}}
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
+\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
 $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-\AP{I would normalize the distributions such that their sum is 100\% (bin width already accounted for), so that the comparison is more direct; on a side, could we use a different shade of blue?
-(see also \Fig{h2density})} Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}

### 2019-06-24 WRITEUP/ms.tex
replace Mstar/Mgas with fgas

@@
 \centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.png}
 \caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
-The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} and corresponds to the molecular disk of \flower (see also \Fig{vv}).
+The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) and corresponds to the molecular disk of \flower (see also \Fig{vv}).
 %

### 2019-06-24 WRITEUP/ms.tex
annotation

@@
 \centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.png}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
-The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) and corresponds to the molecular disk of \flower (see also \Fig{vv}).
-%
-Thus, it encloses a large of stellar mass that is already assembled in \flower.
-The disk structure is excluded in the discussion of MCC dynamics in the remainder of this paper.
-\AP{minor mod: legend with horizontal alignment, text with arrows pointing to the disk and proper MMC clouds of points}
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
+identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
+%
+Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
+in the discussion of MCC dynamics in the remainder of this paper. 
 \label{fig:stellarRatio16}}

### 2019-06-25 WRITEUP/ms.tex
updated Fig 6

@@
 \flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
-its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
+its late quiescent phase (right two columns), where \flower shows a rotating disk configuration.
 Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
@@
 The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
-which is identified as a single component at low $n_{\rm cut}$.
-This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?}
-stellar-to-gas mass ratio of $\simeq$\,50--100. 
+which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
+low gas mass fraction of $\simeq$\,0.
 The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
-\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and quiescent phase (bottom) of \flower.
-%
-The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC}).
-%
-Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
+\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures 
+identified across all $n_{\rm cut}$, as shown using the same color-coding as \Fig{stellarRatio16}.
+%
+Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
+The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
+%
+The dashed black lines show a one-to-one mapping between the axes to facilitate comparison. 
+%
+Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase. On the other hand, 
+$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
 \label{fig:vv}}
@@
 % Higher resolution imaging of molecular gas 
-Such resolution is within reach with ALMA, for which 0.01" resolution images are available for the high freq bands.
+Such resolution is within reach with ALMA, for which 0\farcs01 resolution images are available for the high frequency bands.
 The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission.

### 2019-06-25 plot_modules/plot_cloud_prop.py
add also alpha_vir based on gas-only to similar OOM

@@ -81,10 +81,12 @@ def unpack_xy(ss):
         _mach = []
         _mstar = []
         _mstar2mgas = []
+        _fgas = []
         _SFR_young = []
         _SFR_old = []
         #
         _alpha = []
+        _alpha_gasOnly = []
         #
         _mSD = []
         _sizepc = []
@@ -111,6 +113,7 @@ def unpack_xy(ss):
             _mach.append(np.mean(ss[ks][kkk].Mach_vec))
             _m.append(ss[ks][kkk].mass_Msun)
             _mstar.append(ss[ks][kkk].mstar_Msun_tot)
+            _fgas.append(ss[ks][kkk].mass_Msun/(ss[ks][kkk].mass_Msun + ss[ks][kkk].mstar_Msun_tot))
             _mstar2mgas.append(ss[ks][kkk].s2gR)
             _SFR_young.append(ss[ks][kkk].young_SFR_MsunPyr)
             _SFR_old.append(ss[ks][kkk].old_SFR_MsunPyr)
@@ -125,7 +128,7 @@ def unpack_xy(ss):
             _sigma_bulk.append(ss[ks][kkk].v_disp)
             _sigmakms.append(np.sqrt(ss[ks][kkk].sigma_gas_tot))
             _alpha.append(ss[ks][kkk].alpha_vir_summed)
-
+            _alpha_gasOnly.append(ss[ks][kkk].alpha_vir_summed_gasonly)
             _tffMyr.append(ss[ks][kkk].tff_Myr)
             _rho.append(ss[ks][kkk].avg_density)    # 1/cc
             _rho_mass_wei.append(ss[ks][kkk].mean_density_mass_avg)    # 1/cc
@@ -141,12 +144,14 @@ def unpack_xy(ss):
         to_plot[ks]['cloud mass'] = _m
         to_plot[ks]['Mach'] = _mach
         to_plot[ks]['cloud stellar mass'] = _mstar
+        to_plot[ks]['fgas'] = _fgas
         to_plot[ks]['stellar to gas mass'] = _mstar2mgas
         to_plot[ks]['SFR young'] = _SFR_young
         to_plot[ks]['SFR old'] = _SFR_old
         to_plot[ks]['jeans mass'] = _Mj
         to_plot[ks]['mass over jeans mass'] = _MMj
         to_plot[ks]['alpha vir'] = _alpha
+        to_plot[ks]['alpha vir gas'] = _alpha_gasOnly
[…]

### 2019-06-25 clump_modules/leafprop.py
forgot to commit - also compute gas-only alpha vir fto show comparison

@@ -86,6 +86,7 @@ class Cloud(object):
         self.mean_bulk_veldisp_mass_avg()
         self.mean_star_veldisp_mass_avg()
         self.alpha_vir()
+        self.alpha_vir_gas()
 
         self.young_SFR()
         self.old_SFR()
@@ -178,6 +179,31 @@ class Cloud(object):
       mass = self.mstar_Msun_tot + self.mass_Msun
 
       self.alpha_vir_summed = 5.0 * sigma_2_tot * conv * self.R_pc/mass
+
+
+    def alpha_vir_gas(self, include_bulk=True):
+
+      x = (self.Pressure * self.k_B_erg / C.m_p.cgs.value) / self.density
+      self.cs_avg = np.sqrt(np.sum(self.density * x)/np.sum(self.density))
+
+      v_NT = self.mean_sigma_NT_mass_avg/1.e+5
+      v_cs = self.cs_avg/1.e5
+
+      if include_bulk:
+        v_disp = 0.0
+        for i,x in enumerate(['x','y','z']):
+          v_disp = v_disp + (self.mean_veldisp_mass_avg[i]/1.e+5)**2
+        v_disp = (1.0/3.0)*np.sqrt(v_disp)
+
+        self.sigma_gas_tot = v_NT**2 + v_cs**2 + v_disp**2
+      else:
+        self.sigma_gas_tot = v_NT**2 + v_cs**2
+
+      from astropy import units,constants
+      conv = (units.km/units.s)**2 * constants.pc /( constants.G * constants.M_sun)
+      conv = conv.to(1).value
+
+      self.alpha_vir_summed_gasonly = 5.0 * self.sigma_gas_tot * conv * self.R_pc/self.mass_Msun
 
 
     # --- star particles ---

### 2019-06-25 plot_modules/plot_cloud_prop.py
3by2 fig bigger fonts; also plot gas-only alphaVir

@@ -170,7 +170,7 @@ def unpack_xy(ss):
     return to_plot
 
 
-def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
+def plot_stuff(xstr, ystr, ls='', markersize=10,
                marker='*',
                leglabel='', tag='',
                to_plot=None, save=True, outdir='./',
@@ -186,9 +186,6 @@ def plot_stuff(xstr, ystr, compareAlphaVir=False, ls='', markersize=10,
 
     ystr: str
         something like 'cloud mass', 'alpha vir'
-
-    compareAlphaVir: bool
-        if True, plot different alpha_vir w/ different definition of sigma in it as different symbols.
 
     leglabel: str
         something like "ncut: ", or "snapshot: " for legend
@@ -951,7 +948,9 @@ def set_minorticks(fig, ax):
 def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
                       markersize=10, marker='*',
                       showylabel=True,
-                      showLegend=False, legendFontSize=None):
+                      showLegend=False, legendFontSize=None,
+                      labelsize=18,
+                      ticklabsize=18):
 
     legend_h = []
 
@@ -1009,7 +1008,7 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
                    color='b', marker='o', s=7)
     legend_h.append(h)
 
-    h = ax.scatter(xegc, yegc, label="Bolatto+08: Extra-Galactic GMCs",
+    h = ax.scatter(xegc, yegc, label="Extra-Galactic GMCs",
                    color='k', marker='.', s=10)
     legend_h.append(h)
 
@@ -1039,14 +1038,14 @@ def plot_size_veldisp(fig, ax, to_plot, sfrlabel, sfr=None, ls='',
                      markeredgewidth=0.5)
 
     ax.set_xscale("log")
-    ax.set_xlabel("R [pc]")
+    ax.set_xlabel("R [pc]", fontsize=labelsize)
     ax.set_xlim(2, 2.e3)
 
     ax.set_yscale("log")
-    ax.set_ylabel(r"$\sigma_{\rm gas}$ [km s$^{-1}$]")
+    ax.set_ylabel(r"$\sigma_{\rm gas}$ [km s$^{-1}$]", fontsize=labelsize)
     ax.set_ylim([0.5, 3.e2])
 
[…]

### 2019-06-25 WRITEUP/ms.tex
3by2 fig bigger fonts; also plot gas-only alphaVir

@@
 \flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
-its late quiescent phase (right two columns), where \flower shows a rotating disk configuration.
+its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
 Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
@@
 %
-Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase. On the other hand, 
+Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas 
 $\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
@@
 (right). Star symbols are color-coded by the density thresholds
-$n_{\rm cut}$, as illustrated by the colorbar.
+$n_{\rm cut}$, as illustrated by the colorbar on the right.
+We also plot gas-only $\alpha_{\rm vir}$ (orange star symbols), which is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs,
+since they are gas-dominated (see \Fig{stellarRatio16}).
 Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
@@
 
-%
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
-%\caption{
-%Size-mass relation of MCCs in the accreting phase of \flower (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way.
-%Star symbols are color-coded by
-%increasing $n_{\rm cut}$, same as the colorbar shown in \Fig{larsons_single}.
-%Red line shows the mass-size relation found for regions in the Milky Way with massive \SF \citep{Kauffmann10b}.
-%Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
-%Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), corresponding to lines of
-%constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see \Sec{singless} and e.g., \citealt{Lombardi10a}).
-%%mm [redundant] The star symbols are color-coded by $n_{\rm cut}$,
-%%same as \Fig{larsons_single}.
-%%Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b}
-%%relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
-%For interpretation of this figure, see discussion in \Sec{MR}.
-%\label{fig:MR}}
-%\end{figure*}
-
-%\begin{figure*}[htbp]
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
-%\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
-%Evolutionary stages are shown chronologically from panels {\it (a)} through {\it (f)}.
-%Definition of symbols are same as in \Fig{larsons_single}.
-%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
-%The virial parameter vary over the $\sim$300\,Myr shown here as \flower\ evolves. Most notably, the biggest MCCs transition from
-%the unstable region as \flower\ accretes materials to being stable (e.g., panel {\it (c)}), a similar pattern is seen in the pre-starburst through
-%post-starburst phase.
-%The variation is clearly seen between the pre-starburst through post-starburst phase.
-%Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}),
-%MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. \AP{I still think that this figure might be a bit redundant}
-%\label{fig:alphaEvol}}
-%\end{figure*}
-
 \begin{figure*}
@@
 
-Here, we focus on the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
-Scaling relations for the MCCs are shown in \Fig{larsons_single} for the accreting (left panels) and starburst phase (right panels), respectively.
+Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). 
+These properties are plotted in \Fig{larsons_single} together with observational results of nearby and $z$\,$\simeq$2 molecular structures for comparison.
 

### 2019-06-25 WRITEUP/ms.tex
fig caption

@@
 MCCs (star symbols) identified in the two most extreme evolutionary
-stages of \flower\ --- accreting phase (left) and starburst phase
-(right). Star symbols are color-coded by the density thresholds
-$n_{\rm cut}$, as illustrated by the colorbar on the right.
-We also plot gas-only $\alpha_{\rm vir}$ (orange star symbols), which is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs,
+stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
+$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
+Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
 since they are gas-dominated (see \Fig{stellarRatio16}). 
-Literature data in the linewidth-size plots are from \citet{Heyer04a, Rosolowsky05a, Bolatto08a,
-% black dot = extragalactic GMCs in quiescent environments
-Leroy15a}, and \citet{Swinbank11a}, and the empirical scaling relations are
-from \citet{Larson81a, Heyer04a, Bolatto08a}.
-Data points in the $\alpha_{\rm vir}$-mass figure are taken from
-\citet{Kauffmann17a} and \citet{Kauffmann17b} and references therein
-(see Fig 4 of \citealt{Kauffmann17b}).
+Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
 The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
 the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
+Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
+Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
+MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
+and \citet{Kauffmann17b}.
 \label{fig:larsons_single}}

### 2019-06-25 WRITEUP/ms.tex

--- 2019-06-25 WRITEUP/ms.tex
@@
 the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
-MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have lower $\alpha_{\rm vir}$ 
-and $Q_{\rm eff}$ values, % indicative of instability to collapse. 
-where star formation is expected to take place within the clumps and cores on even smaller scales, as non-thermal energy 
-quickly dissipates. % and the gas structures are no longer supported by turbulence.
-%
-As such, detailed studies on the star-forming gas dynamics at EoR requires a spatial resolution of $\lesssim$40\,pc, which is 
+MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have low $\alpha_{\rm vir}$ 
+and $Q_{\rm eff}$ values, indicative of instability to collapse. 
+Star formation is expected to take place within the clumps and cores on smaller scales, where non-thermal energy 
+quickly dissipates and the gas structures are no longer supported by turbulence.
+%
+As such, spatial resolution of $\lesssim$40\,pc 
+is necessary to shed light on the star-forming gas dynamics since the cosmic dark ages which is 
 within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a,Smit18a}.
 
@@
 and present the formalism within which we interpret the results.
-In \Sec{results}, we present the results and characteristic properties of the MCCs.
+In \Sec{results}, we present the results and the scaling relations for the MCCs.
 We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some basic equations concerning the empirical relations commonly mentioned in observational studies of molecular clouds in the literature and the gravitational instability of galactic disks, which might be driving MCC formation.
+We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation.
 Such notions will be used in the subsequent analysis of our simulations.
 
-\subsection{Larson's Relations and Virial Parameter}\label{sec:PVE}
+\subsection{Larson relations and virial parameter}\label{sec:PVE}
 \citet{Larson81a} discussed a number of relations among Galactic
@@
 We are interested in determining whether MCC properties are sensitive to these different dynamical conditions.
-For completeness, we also show relationships of MCC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).
+For completeness, we also show the scaling relations examined for the other evolutionary stages traced in the simulation (see \Sec{ncut}).
 In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
@@
 \includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
-\caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
-    (a)}.
+\caption{Distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
+    (b)} \AP{what is the normalization/axis here? I would plot the distribution such that the integral on the function is 1}.
 \label{fig:h2density}}
@@
  \centering
-  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}
+
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}
+
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
+  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
 \caption{
 Examples of MCCs (white contours) identified by the clump finder in
-\flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
-its late quiescent phase (right two columns), where \flower shows a rotating disk configuration.
-Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
+\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
+its quiescent phase, which is rotation-dominated (right two columns).
+Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
+in the quiescent phase.
 Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
-Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as annotated by the label in the bottom left corners. 
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
+\AP{label with the phase should be included in the first row}
 \label{fig:MCC}
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
+\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
 $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\AP{I would normalize the distributions such that their sum is 100\% (bin width already accounted for), so that the comparison is more direct; on a side, could we use a different shade of blue?
+(see also \Fig{h2density})} Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
-identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
-%
-Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
-in the discussion of MCC dynamics in the remainder of this paper. 
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_stellar-to-gas-mass_ss16.png}
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
+The most massive MCC identified at low $n_{\rm cut}$ shows a high stellar-to-gas mass ratio ($\gtrsim$\,1) \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?} and corresponds to the molecular disk of \flower (see also \Fig{vv}).
+%
+Thus, it encloses a large of stellar mass that is already assembled in \flower.
+The disk structure is excluded in the discussion of MCC dynamics in the remainder of this paper.
+\AP{minor mod: legend with horizontal alignment, text with arrows pointing to the disk and proper MMC clouds of points}
 \label{fig:stellarRatio16}}
@@
 The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
-which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
-low gas mass fraction of $\simeq$\,0.
+which is identified as a single component at low $n_{\rm cut}$.
+This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a \AP{do we really need both $f_{\rm gas}$ and $M_\star/M_{\rm gas}$?}
+stellar-to-gas mass ratio of $\simeq$\,50--100. 
 The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
-\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures 
-identified across all $n_{\rm cut}$, as shown using the same color-coding as \Fig{stellarRatio16}.
-%
-Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
-The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
-%
-The dashed black lines show a one-to-one mapping between the axes to facilitate comparison. 
-%
-Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase. On the other hand, 
-$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-sigma-kms-bulk_sigma-kms-NT} \\
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss28-sigma-kms-bulk_sigma-kms-NT}
+\caption{Gas velocity dispersions resulting from bulk versus turbulent motions for MCCs identified across all $n_{\rm cut}$ (same color-coding as \Fig{stellarRatio16}) in the accreting (top) and quiescent phase (bottom) of \flower.
+%
+The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (\Fig{MCC}).
+%
+Velocity dispersion from turbulent motions dominates over bulk motions for most MCCs in the accreting phase.
+On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
 \label{fig:vv}}
@@
 
+\AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}
+
 %--------------------------------------------------------------------------
@@
 % Higher resolution imaging of molecular gas 
-Such resolution is within reach with ALMA, for which 0\farcs01 resolution images are available for the high frequency bands.
+Such resolution is within reach with ALMA, for which 0.01" resolution images are available for the high freq bands.
 The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission.

### 2019-06-25 WRITEUP/ms.tex
edit of sec 5.2

--- 2019-06-25 WRITEUP/ms.tex
@@
 
-The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
 which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
-low gas mass fraction of $\simeq$\,0.
+low gas mass fraction of $f_{\rm gas}\simeq$\,0.
 The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
@@
 
-The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper
-since its dynamics is dominated by large-scale shear.
+The most massive MCC is excluded in the discussion of MCC dynamics in \Sec{diss} of this paper,
+since its dynamics is dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}) 
+as would be done so for an observational study. % where we would plot everything we identify and try to interpret their nature.
+
 Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
@@
 as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the average Mach number for MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
+In particular, the average Mach number for MCCs identified at the highest density threshold is $\bar{\mathcal{M}}\,\simeq6$.
+This is consistent with the analysis done in \citet{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
 
@@
 % middle
-While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
-A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs.
-On the other hand, the  remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
+disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
+explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
+influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
+virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
 

### 2019-06-25 plot_modules/plot_cloud_prop.py
R

@@ -36,7 +36,7 @@ def setup_plot():
                                 , 'xtick.labelsize': 16
                                 , 'ytick.labelsize': 16
                                 , 'ytick.minor.width': 1     # points
-                                , 'font.serif': ("times", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
+                                , 'font.serif': ("Times", "Computer Modern Roman", "New Century Schoolbook", "Bookman"), 'font.sans-serif': ("Helvetica", "Avant Garde", "Computer Modern Sans serif"), 'font.monospace': ("Courier", "Computer Modern Typewriter"), 'font.cursive': "Zapf Chancery"
                                 })
     cm = setup_cmap()
     return cm
@@ -119,8 +119,8 @@ def unpack_xy(ss):
             _SFR_old.append(ss[ks][kkk].old_SFR_MsunPyr)
             #
             _mSD.append(ss[ks][kkk].massSD)
-            _sizepc.append(ss[ks][kkk].R_pc * 2.0)
-            _R2pc2.append((ss[ks][kkk].R_pc * 2.0) ** 2.0)
+            _sizepc.append(ss[ks][kkk].R_pc * 1.0)
+            _R2pc2.append((ss[ks][kkk].R_pc * 1.0) ** 2.0)
             _SFRSD.append((ss[ks][kkk].SFR) / 1.0e6 /
                           (np.pi * ss[ks][kkk].R_pc * pc2kpc)**2)
 
@@ -136,7 +136,7 @@ def unpack_xy(ss):
             _mSD_cgs.append(ss[ks][kkk].massSD *
                             ss[ks][kkk].Msun2g / (ss[ks][kkk].pc2cm)**2)
             _sigma2oR.append(ss[ks][kkk].sigma_gas_tot /
-                             (ss[ks][kkk].R_pc * 2.0))
+                             (ss[ks][kkk].R_pc * 1.0))
             _mSD_per_ff.append(ss[ks][kkk].massSD / (ss[ks][kkk].R_pc)**2 / ss[ks][kkk].tff_Myr)
             _P_NT = [].append(ss[ks][kkk].P_nt)
 

### 2019-06-25 plotSS.py
fontsie, labelsize

@@ -345,7 +345,11 @@ if __name__ == '__main__':
                               tag='allss',
 #                              cmap=cm,
                               sfrlabel=bubu,
-                              cbarLabelSize=20,
+                              cbarLabelSize=25,
                               outdir='./',
-                              legendFontSize=16,
+                              legendFontSize=20,
+                              axwidth=1.5,
+                              tickwidth=2,
+                              labelsize=25,
+                              ticklabsize=20,
                               saveFig=True)

### 2019-06-25 plotsingleSS.py

@@ -49,6 +49,10 @@ def plotting_procedure(snapshot_num, legendFontSize=13):
 
     ss, to_plot, leafdir_out = load_pickleTOplot(snapshot_num)
 
+    plot_stuff("fgas", "cloud mass", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
+    plot_stuff("fgas", "alpha vir", leglabel="ncut: ",
+               to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("stellar to gas mass", "cloud mass", leglabel="ncut: ",
                to_plot=to_plot, outdir=leafdir_out, legendFontSize=legendFontSize)
     plot_stuff("stellar to gas mass", "alpha vir", leglabel="ncut: ",
@@ -194,7 +198,11 @@ if __name__ == '__main__':
                               tag='ss16-ss22',
 #                              cmap=cm,
                               sfrlabel=False,
-                              cbarLabelSize=23,
+                              cbarLabelSize=25,
                               outdir='./',
-                              legendFontSize=18,
+                              legendFontSize=20,
+                              axwidth=1.5,
+                              tickwidth=2,
+                              labelsize=25,
+                              ticklabsize=20,
                               saveFig=True)

### 2019-06-25 WRITEUP/ms.tex
minor wording

@@
 \includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing MCCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar).
-Left panels show MCCs identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and right panels show MCCs
-identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
+\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right).
+Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
 The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
 disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
+Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
+The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
 \label{fig:alpha16-28}}
@@
 is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
-column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
+column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
 %For instance, \citet{Ballesteros02a} show that the density
@@
 MCCs in the starburst phase span a wider range in gas surface density 
-(bottom panels of \Fig{larsons_single}) and have lower virial parameters, even
-for MCCs with masses $<$\,10$^7$\,\Msun (i.e., excluding the molecular disk of \flower identified).
-That is, more MCCs in the starburst phase of \flower are more susceptible to collapse, as expected.
+(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
+That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
 The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
-of the Milky Way and the LMC, but comparable to those observed in starburst galaxies and the nearby 
+of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
 ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
@@
 Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
-(see top panels of \Fig{larsons_single}). 
-At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,100\,pc.
+(see top panels of \Fig{alpha16-28}). 
+At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
 %
@@
 
-At the highest density cut, only the densest gas structures are identified. This automatically excludes the molecular disk and arms 
-of \flower. The virial parameter of these MCCs indicates that most of them are unstable against collapse 
-(see middle right panel of \Fig{alpha16-28}).
+At the highest density cut, only the densest gas structures are identified.
+The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more 
+unstable against collapse (see middle right panel of \Fig{alpha16-28}).
 
@@
 %We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
-The MCCs of \flower have dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
+The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
+spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
+However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
+are limited by the spatial resolution. 
 %
-Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion of MCCs in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+Such high velocity dispersion
+in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
@@
 % different evolutionary stages
-In terms of the Larson's linewidth-size relation, we do not find any major quantitative differences in the MCC properties with respect to those observed in the nearby Universe between the accreting and starburst phase of \flower (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase 
+with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
 However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
@@
 This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
+In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$
+of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
-
+% 
 That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
@@
 
-The large virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution/collapse depends on the dynamics or equation of state of the gas.
+The large ($>$\,2) virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
 %
@@
 Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
-On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
+On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
 
@@
 %
-First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence.
-This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
+First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. This in turn would enable
+sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
 % Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
@@
 This re-iterates the statement about low $Q$ above.
+
+% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}
 
@@
 
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$, and thus, some of the MCCs within the main disk break into multiple MCCs at higher $n_{\rm cut}$.
+The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, after excluding the 
+most massive molecular structure identified (which correspond to the main disk of \flower). 
+The main disk is break into multiple MCCs at higher $n_{\rm cut}$.
 The $\sim$200\,pc-scale MCCs found with a low density threshold correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.

### 2019-06-25 WRITEUP/ms.tex
minor wording

@@
 most massive molecular structure identified (which correspond to the main disk of \flower). 
-The main disk is break into multiple MCCs at higher $n_{\rm cut}$.
-The $\sim$200\,pc-scale MCCs found with a low density threshold correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
-%
-Excluding the biggest MCC, the typical mass of MCCs is $10^{6.5}$\,\Msun.
+The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 
+and breaks down into smaller MCCs at higher density thresholds, with a typical size of $R\simeq\,50$\,pc.
+%
+The typical mass of MCCs is $10^{6.5}$\,\Msun.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
 That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
-On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.
+On the other hand, the gas velocity dispersion
+of $\sigma_{\rm gas}\simeq$\,20-10\,\kms is rather insensitive to the adopted density threshold.
+
+Velocity dispersion and gas surface density of MCCs of \flower are systematically higher than Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
+These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
+Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies.
+A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that MCCs
+are supported by turbulence motions.
 
@@
 
-MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
-These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
-Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies.
-A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that most MCCs, excluding the arms and the disk of \flower, are supported by turbulence motions.
-
 % where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
@@
 Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
-% Such MCCs are thus susceptible to collapse. 
-% The high virial parameter found for some MCCs are found in regions of $Q_{\rm eff}>1$.
-% On the other hand, 
-Such MCCs identified in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
+Such MCCs identified in the denser regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
+
 % Toomre:
@@
 % Higher resolution imaging of molecular gas 
-Such resolution is within reach with ALMA, for which 0\farcs01 resolution images are available for the high frequency bands.
-The Next Generation VLA (ngVLA) in the 2030s will enable deeper imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission.
+Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
+The Next Generation VLA (ngVLA) in the 2030s could in principle enable imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission. 
 % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6

### 2019-06-25 toomre.py
1.2 FoV

@@ -1292,8 +1292,8 @@ class ToomreAnalyze_2comp(object):
         list_labels  = list_labels+ [r'$\log Q_{\rm gas}$','$\log Q_{\star}$']
     elif type_plots == '3by1':
 
-      fig = plt.figure(figsize=(9, 3))
-      fig.subplots_adjust(left=0.10, right=0.90, wspace=0.00)
+      fig = plt.figure(figsize=(8, 3))
+      fig.subplots_adjust(left=0.10, right=0.90, wspace=0.00, hspace=-0.1)
 
       list_plt_ids = [131,132,133]
       list_types   = ['Q','Q','Q']
@@ -1424,7 +1424,7 @@ if __name__ == '__main__':
                            clump_list_filename=testfile
                            )
 
-  for type_plots in ['2by2', '3by1']:    #  '3by2',
+  for type_plots in ['2by2', '3by1']:   #  '3by2',
     Q_tot_obj.plots_combined(
                             central_kpc_one_side = size_kpc
                             ,annotate_clump=annotate
@@ -1437,7 +1437,12 @@ if __name__ == '__main__':
                             ,clump_list_filename=testfile
                             ,type_plots= type_plots
                            )
-
+    Q_tot_obj.plots_combined(
+                            central_kpc_one_side=1.2
+                            ,annotate_clump=annotate
+                            ,clump_list_filename=testfile
+                            ,type_plots= type_plots
+                           )
   #Q_tot_obj.plot_Q_eff_zoom(central_kpc_one_side=size_kcp,
   #                          annotate_clump=annotate,
   #                          clump_list_filename=testfile)

### 2019-06-25 WRITEUP/ms.tex

@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
-\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
 \caption{
-Toomre $Q$ maps derived from the central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
-The contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown separately in the left and middle panels, respectively.
-Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
+Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower.
+Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively.
+The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
 %
@@
 %
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} of \flower indicates that the stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
-\AP{maybe it is better to put a single set of maps, with FOV from -1.5 to 1.5 kpc}
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} 
+reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations 
+in relatively evolved and enriched systems at high redshifts. 
 \label{fig:Qeff}}

### 2019-06-27 WRITEUP/ms.tex
few details about some figures; comparison with grisdale added

@@
 Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+Similar conclusions are also reached from the analysis of clouds forming in Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.
 
-Summarizing, the virial parameter can be used to quantify the stability/boundedness of
-%mm an MCC.
-    a molecular cloud.
+Summarizing, the virial parameter can be used to quantify the stability/boundedness of a molecular cloud.
 Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{Bertoldi92b}.
-%
 Such a criterion is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.
@@
 \caption{
-Examples of MCCs (white contours) identified by the clump finder in
-\flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
-its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
+Examples of MCCs identified in \flower by our clump finder.
+%
+The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
+%
+Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
+%
 Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
-Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
-Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as annotated by the label in the bottom left corners. 
+%
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel. \AP{please change $\rm Kpc$ to $\rm kpc$}
 \label{fig:MCC}
@@
 Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
 \label{fig:dist}}
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
-which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
-low gas mass fraction of $f_{\rm gas}\simeq$\,0.
-The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
-the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
-in the accreting and quiescent phases of \flower.
-The accreting phase of \flower displays a disturbed morphology, whereas the 
-quiescent phase displays a disk-like morphology (\Fig{MCC}).
-Excluding the structure corresponding to the molecular disk, the 
-velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
-in the quiescent disk-like phase.
-
-The most massive MCC is excluded in the discussion of MCC dynamics in \Sec{diss} of this paper,
-since its dynamics is dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}) 
-as would be done so for an observational study. % where we would plot everything we identify and try to interpret their nature.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
+This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
+The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
+%
+Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
+On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
+%
+For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.
 
 Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
-We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
-have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations.
+We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
+However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations, e.g.
+see \citet{grisdale:2017,grisdale:2019} for the importance of feedback in shaping the properties of clouds forming in local simulated galaxies.
 That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
@@
 Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
-since they are gas-dominated (see \Fig{stellarRatio16}). 
+since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
 Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
@@
 % different evolutionary stages
-We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase 
-with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
 However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.

### 2019-07-03 WRITEUP/ms.tex
added a not quite gratuitous reference to Garland et al 2015

@@
 % --------------------------------------------
-
+%mm2 edits of 3 Jul 19 marked like this M-MML
 % AP: I have some compatibility issues with the new style (i.e. \section does not work)
@@
 part of this material.
-Existing studies indicated that early galaxies are more gas-rich with molecular fractions higher than
+Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than
 those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
@@
 galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
-Hodge16a, Leung19a}). These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent, and clumpy than nearby galaxies.
+Hodge16a, Leung19a}). These studies find that galaxies close to the
+peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent,
+and clumpy than nearby galaxies,
+% mm2
+    although luminous compact blue galaxies may represent local
+    analogs of these gas-rich, clumpy systems \citep{Garland15}.
 

### 2019-07-04 WRITEUP/ms.tex
added quick summary of theoretical work by Behrendt et al on clump structure.
added some discussion of virial relation and Martin & Kennicutt 2001 cite to Toomre

@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line
+emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6
+over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the
+first spatially resolved observations are just starting to become
+available \citep[e.g., ][]{Jones17a}.
+% mm2
+    On the theoretical side, a schematic investigation by
+    \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist
+    of many smaller clumps formed by gravitational instability, a hierarchical
+    structure that persists in an idealized disk model by \citet{Behrendt19}.
 
@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some basic equations concerning the empirical relations commonly mentioned in observational studies of molecular clouds in the literature and the gravitational instability of galactic disks, which might be driving MCC formation.
-Such notions will be used in the subsequent analysis of our simulations.
+%mm2 [revised paragraph]
+We begin by introducing some empirical relations commonly mentioned in
+observational studies of molecular clouds in the literature, as well
+as describing the gravitational instability of galactic disks, which
+might be driving MCC formation. These concepts will be used in the subsequent analysis of our simulations.
 
@@
 They also represent a useful framework to analyze our results as they
-have been argued to arise from the interplay between gravity and turbulence encoded in the virial theorem
+have been argued to arise from the interplay between gravity and
+% mm2 turbulence encoded in the
+    velocity dispersion given by
+virial theorem
 (note, however, the alternative interpretation involving gravitational collapse by
@@
 \end{equation}
-where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
+where $\ddot{\mathcal{I}}$ is the second time derivative of the
+Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
+the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and
+$\mathcal{W}$ is the gravitational energy.
 %
@@
 
-Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$.
-Deviations from this relation are usually attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
-Similar conclusions are also reached from the analysis of clouds forming in Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.
+Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between
+$\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a
+virialized cloud, since $\sigma_{\rm
+  gas}^2/R\propto\Sigma$.
+% mm2
+    \citep{Heyer09a} pointed out that the original size-linewidth
+    relation implies constant surface density in this interpretation.
+    The limited dynamic range in column density of CO observations
+    appears to account for this \citep[see also][]{Ballesteros-Paredes11a}.
+Deviations from this relation are
+% mm2 usually
+        often
+attributed to a significant contribution from external pressure as per
+Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a,
+  Hughes13b, Meidt13a}). Similar conclusions are also reached from the
+analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.
 
@@
 
-In cases where stellar component plays an important role in the dynamics, the virial parameter becomes
+In cases where a stellar component plays an important role in the
+dynamics, the virial parameter becomes
+%mm2 [citation or derivation needed?]   ***********
 \begin{equation}
@@
 
-The onset of gravitational instability is tightly connected to \SF \citep[e.g.,][]{Kennicutt89a, Wang94a, Li05b, Li06a}.
+The onset of gravitational instability is tightly connected to \SF
+%mm2 [added Martin & Kennicutt 2001]
+\citep[e.g.,][]{Kennicutt89a, Martin01, Wang94a, Li05b, Li06a}.
 For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by

### 2019-07-04 WRITEUP/ms.tex
section 3 revisions, including recovering a missing sentence fragment...

@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of MC in Galaxies at the EoR}
+\shorttitle{Dynamical Properties of
+  % mm2 MC
+              MCCs
+  in Galaxies at the EoR}
 \shortauthors{Leung et al.}
@@
 \section{Numerical Simulations}\label{sec:sim}
-The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are briefly summarized here.
+The simulations used in this work are described by \citet{Pallottini17a, Pallottini17b} and are briefly summarized here.
 %
@@
 The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
-This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryionic) mass exceeds the mass resolution by a factor of eight.
+This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight.
 The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e.
@@
 
-Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
-Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
-The remaining energy is injected into the ISM in kinetic and thermal energy forms.
-Radiation pressure on dust and gas is also included.
-Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{Pallottini19a, Decataldo19a}.
-%
-Via feedback processes the gas can acquire energy both thermal and non-thermal form \citep{Agertz13a}; the latter is a term that mimics unresolved turbulence: such non-thermal energy is not affected by cooling but rather is dissipated on the eddy turn-over time scale \citep{Maclow99a}.
-See \citet{Pallottini17b} for further details.
-
-The simulation zooms in on a galaxy named after the flower \flower whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following.
+Star formation is modeled using an H$_2$-based prescription of the
+Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar
+tracks from \ncode{starburst99} and include stellar feedback from
+supernovae (SNe) as well as winds from OB and asymptotic giant branch
+stars. Coupling to the gas is implemented via a sub-grid model for
+blastwaves, which accounts for radiative energy losses inside the
+cell. The remaining energy is injected into the ISM in
+%mm2 kinetic and thermal energy forms. Via feedback processes the gas
+%can acquire energy in
+both thermal and non-thermal form \citep{Agertz13a}; the latter is
+a term that mimics unresolved turbulence. The non-thermal energy is
+not affected by radiative cooling but rather is dissipated on the eddy
+turn-over time scale \citep{Maclow99a}. See \citet{Pallottini17b} for
+further details.
+%mm2 [moved down to unify discussion of non-thermal energy]
+Radiation pressure on dust and gas is also included. Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{Pallottini19a, Decataldo19a}.
+
+The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following.
 \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
@@
 is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
-%
-%This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and \section{•}
-atellite galaxies, thereby leading to bursts of \SF.
+%mm2 [the first three lines of the following sentence were commented
+%out, but not the last line.  Since it makes sense, and the following sentence starts with
+%Meanwhile, I have recovered the entire sentence.] 
+This is advantageous especially at early cosmic epochs, when the
+densest structures are beginning to form; gas is constantly being
+accreted onto the central galaxy from the cosmic web and 
+%mm2  \section{•} atellite
+             satellite
+galaxies, thereby leading to bursts of \SF.
 Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
@@
 
+% mm2 [move this sentence up to give sections in order]
+In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
+by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
+%
 Given the stochastic nature of \flower in its star formation history, we mostly focus on few of its most extreme evolutionary stages in this work (see \Sec{singless}).
@@
 For completeness, we also show relationships of MCC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).
-In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
-by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
 

### 2019-07-04 WRITEUP/ms.tex
minor fixes to sect 4

@@
 This is commonly done by
-identifying clumps based on/after applying S/N-clipping, using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a}).
+identifying clumps based on/after applying S/N-clipping, using tools
+such as the \ncode{aips} tasks \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; (e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a})).
 %
@@
 % We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
-Note that with these choice we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
+Note that with these choices we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
 

### 2019-07-04 WRITEUP/ms.tex

@@
 
-\subsection{Distributions of MCC Basic Properties and Outlier} \label{sec:dist}
+\subsection{Distributions of MCC Basic Properties
+  % mm2 and Outlier
+} \label{sec:dist}
 \begin{figure*}[htbp]
@@
 \caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
-$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc
+(bottom panels) over all the considered evolutionary stages of \flower
+traced in the simulation. Note that the scales shown on the $y$-axes
+are different between the top and bottom panels, as fewer MCCs are
+identified at higher $n_{\rm cut}$.
+%mm2: [still needs to be done]
 \AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
@@
 
-We start by considering the MCC distributions in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
+%mm2 We start by considering the MCC distributions in terms of their
+     We start by considering the distributions of MCC
+molecular gas mass, radius, and gas mass fraction, which we define as
 \begin{equation}
@@
 %
-We show in \Fig{dist} the distributions considering all the evolutionary stages of \flower and dividing the sample in a low 
-($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm cut}$\eq18.96\,\cc, lower panels) density cuts\footnote{The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, we therefore consider MCCs identified with the second highest density threshold ($n_{\rm cut}$\eq18.96\,\cc).}.
-%
-Overall, the mass of all MCCs identified ranges between $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
+We show in \Fig{dist} the distributions
+%mm2 considering all the evolutionary stages of \flower and dividing the sample in
+%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
+%cut}$\eq18.96\,\cc, lower panels) density cuts 
+      from the combination of the three considered evolution stages.
+      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
+      (top panels) and a high cut \footnote{The highest density
+        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
+        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
+        densest structure. However, not all evolutionary stages
+        considered have at least one MCC at this highest density
+        threshold, so we consider MCCs identified with the second
+        highest density threshold instead.}.
+ of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
+%
+Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
 whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
@@
 % address the biggest MCC = molecular disk of \flower
+%mm2 [This figure would be better with a color bar rather than the
+%prominent stars at the bottom...]
 \begin{figure}
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
-This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
+to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
+identified as a single component at low $n_{\rm cut}$. This main disk
+component
+% mm2 occupy the top right   [left not right!]
+          occupies the top left
+corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
 The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.

### 2019-07-04 WRITEUP/ms.tex
some comment cleanup

@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of
-  % mm2 MC
-              MCCs
-  in Galaxies at the EoR}
+\shorttitle{Dynamical Properties of MCCs in Galaxies at the EoR}
 \shortauthors{Leung et al.}
@@
 The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies.
-This gas fuels \SF and feeds central
-supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
+This gas fuels \SF and feeds central supermassive black holes.
+Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
 part of this material.
-Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than
-those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. 
-Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs)
-that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+%
+Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}.
+Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs) that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
 Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
 
-%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
 Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population \citep[see also a review by][]{Stark16a}.
@@
 %
-Even in the local Universe, where detailed \obs can be made, variations in molecular cloud
-%       \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
-%     \DL{This is just a statement to say there are variations among local GMCs.
-Together with the different galaxy properties found for early galaxies, it is interesting to study properties of molecular structures at earlier epochs.
-}
-properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question:
-{\it what are the physical properties of
-molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
+Even in the local Universe, where detailed \obs can be made, variations in molecular cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
 %
@@
 Global measurements of these diagnostics in \highz galaxies have provided preliminary information on their global properties (e.g., gas masses, gas temperature, and radiation field intensity).
-However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne;
-see e.g., the review by \citealt{CW13}).
-%
-To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of 
-galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, 
-Hodge16a, Leung19a}). These studies find that galaxies close to the
-peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent,
-and clumpy than nearby galaxies,
-% mm2
-    although luminous compact blue galaxies may represent local
-    analogs of these gas-rich, clumpy systems \citep{Garland15}.
+However, spatially resolving their ISM is necessary to fully understand many aspects of galaxy evolution and the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne; see e.g., the review by \citealt{CW13}).
+%
+To date, spatially resolved ISM properties of \highz galaxies have only been mapped in a handful of galaxies at high redshift using tracers such as dust continuum, CO, and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a, Leung19a}).
+These studies find that galaxies close to the peak of cosmic \SF ($z$\ssim2) are more molecular gas-rich, turbulent, and clumpy than nearby galaxies, although luminous compact blue galaxies may represent local analogs of these gas-rich, clumpy systems \citep{Garland15}.
 
@@
 %
-While ALMA has enabled the detection of \cii158\,$\micron$ and CO line
-emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6
-over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the
-first spatially resolved observations are just starting to become
-available \citep[e.g., ][]{Jones17a}.
-% mm2
-    On the theoretical side, a schematic investigation by
-    \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist
-    of many smaller clumps formed by gravitational instability, a hierarchical
-    structure that persists in an idealized disk model by \citet{Behrendt19}.
-
-%mm To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts,
-To understand the physical properties of MCCs in early galaxies,
-we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming %mm molecular cloud complexes
-MCCs
-in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
+While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep[e.g., ][]{Jones17a}.
+%
+On the theoretical side, a schematic investigation by \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist of many smaller clumps formed by gravitational instability, a hierarchical structure that persists in an idealized disk model by \citet{Behrendt19}.
+
+To understand the physical properties of MCCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MCCs in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
 
@@
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
-In \Sec{eqn}, we describe the method used to identify
-MCCs,
-and present the formalism within which we interpret the results.
+In \Sec{eqn}, we describe the method used to identify MCCs, and present the formalism within which we interpret the results.
 In \Sec{results}, we present the results and characteristic properties of the MCCs.
@@
 \section{Physical Background}\label{sec:Back}
-%mm2 [revised paragraph]
-We begin by introducing some empirical relations commonly mentioned in
-observational studies of molecular clouds in the literature, as well
-as describing the gravitational instability of galactic disks, which
-might be driving MCC formation. These concepts will be used in the subsequent analysis of our simulations.
+We begin by introducing some empirical relations commonly mentioned in observational studies of molecular clouds in the literature, as well as describing the gravitational instability of galactic disks, which might be driving MCC formation.
+These concepts will be used in the subsequent analysis of our simulations.
 
 \subsection{Larson's Relations and Virial Parameter}\label{sec:PVE}
-\citet{Larson81a} discussed a number of relations among Galactic
-molecular cloud
-properties, namely the linewidth-size, density-size, and mass-size relations.
+
+\citet{Larson81a} discussed a number of relations among Galactic molecular cloud properties, namely the linewidth-size, density-size, and mass-size relations.
 Larson relations are routinely used for comparing properties of molecular structures in different galactic environments.
-They also represent a useful framework to analyze our results as they
-have been argued to arise from the interplay between gravity and
-% mm2 turbulence encoded in the
-    velocity dispersion given by
-virial theorem
-(note, however, the alternative interpretation involving gravitational collapse by
-e.g., \citealt{Ballesteros-Paredes11a}).
+They also represent a useful framework to analyze our results as they have been argued to arise from the interplay between gravity and velocity dispersion given by virial theorem (note, however, the alternative interpretation involving gravitational collapse by e.g., \citealt{Ballesteros-Paredes11a}).
 
@@
 Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions.
-%mm Neglecting magnetic field and
 Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
@@
 
-Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between
-$\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a
-virialized cloud, since $\sigma_{\rm
-  gas}^2/R\propto\Sigma$.
-% mm2
-    \citep{Heyer09a} pointed out that the original size-linewidth
-    relation implies constant surface density in this interpretation.
-    The limited dynamic range in column density of CO observations
-    appears to account for this \citep[see also][]{Ballesteros-Paredes11a}.
-Deviations from this relation are
-% mm2 usually
-        often
-attributed to a significant contribution from external pressure as per
-Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a,
-  Hughes13b, Meidt13a}). Similar conclusions are also reached from the
+Based on Equation~\ref{eqn:SVE}, a one-to-one mapping between $\sigma_{\rm gas}^2/R$ and $\Sigma$ is therefore expected for a virialized cloud, since $\sigma_{\rm gas}^2/R\propto\Sigma$.
+%
+\citep{Heyer09a} pointed out that the original size-linewidth relation implies constant surface density in this interpretation.
+The limited dynamic range in column density of CO observations appears to account for this \citep[see also][]{Ballesteros-Paredes11a}.
+%
+Deviations from this relation are often attributed to a significant contribution from external pressure as per Equation~\ref{eqn:v0} (see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).
+Similar conclusions are also reached from the
 analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.
@@
 
-In cases where a stellar component plays an important role in the
-dynamics, the virial parameter becomes
+In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
 %mm2 [citation or derivation needed?]   ***********
@@
 
-%\subsection{Gravitational Instabilities}\label{sec:Q}
 \subsection{Toomre stability analysis}\label{sec:Q}
@@
 A frequently used observable proxy for $Q$ is the ratio of disk circular velocity to root-mean-square velocity dispersion $v_{\rm circ}/\sigma_{\rm disk}$ \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
-% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
 %
@@
 \end{equation}
-with $x$ indicating either gas or stars.
-% Note that w/ thickness, there's the a self-gravity dilution term in the dispersion relation, which in effect reduceds the surface gravity in the vertical direction.
-As such, it is easier to be stable against gravitaional instability.
-Thus, the criterion for instability $Q$ is reduced.
-%
-The combined effect of gas and stars can then be accounted for by writing
+with $x$ indicating either gas or stars. The combined effect of gas and stars can then be accounted for by writing
 \begin{equation}\label{eqn:q_eff}
@@
 sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
+%
 The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}.
@@
 
-Star formation is modeled using an H$_2$-based prescription of the
-Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar
-tracks from \ncode{starburst99} and include stellar feedback from
-supernovae (SNe) as well as winds from OB and asymptotic giant branch
-stars. Coupling to the gas is implemented via a sub-grid model for
-blastwaves, which accounts for radiative energy losses inside the
-cell. The remaining energy is injected into the ISM in
-%mm2 kinetic and thermal energy forms. Via feedback processes the gas
-%can acquire energy in
-both thermal and non-thermal form \citep{Agertz13a}; the latter is
-a term that mimics unresolved turbulence. The non-thermal energy is
-not affected by radiative cooling but rather is dissipated on the eddy
-turn-over time scale \citep{Maclow99a}. See \citet{Pallottini17b} for
-further details.
-%mm2 [moved down to unify discussion of non-thermal energy]
+Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar
+tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
+Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
+%
+The remaining energy is injected into the ISM in both thermal and non-thermal form \citep{Agertz13a}; the latter is a term that mimics unresolved turbulence.
+The non-thermal energy is not affected by radiative cooling but rather is dissipated on the eddy turn-over time scale \citep{Maclow99a}.
+See \citet{Pallottini17b} for further details.
+%
 Radiation pressure on dust and gas is also included. Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{Pallottini19a, Decataldo19a}.
@@
 
-One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which
-is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
-%mm2 [the first three lines of the following sentence were commented
-%out, but not the last line.  Since it makes sense, and the following sentence starts with
-%Meanwhile, I have recovered the entire sentence.] 
-This is advantageous especially at early cosmic epochs, when the
-densest structures are beginning to form; gas is constantly being
-accreted onto the central galaxy from the cosmic web and 
-%mm2  \section{•} atellite
-             satellite
-galaxies, thereby leading to bursts of \SF.
+One of the main advantages of studying galaxies in simulations is that we can examine how their dynamical properties evolve with time, which is interesting in order to understand the physical processes that determine the morphology and dynamical properties of galaxies, which in turn affect their \SF.
+%
+This is advantageous especially at early cosmic epochs, when the densest structures are beginning to form; gas is constantly being accreted onto the central galaxy from the cosmic web and satellite galaxies, thereby leading to bursts of \SF.
+%
 Meanwhile, tidal forces resulting from interactions with these surrounding galaxies can disrupt the main disk and arms, likely leading to different dynamical states for the molecular structures compared to more evolved galaxies found at a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive ones).
-% mainly expecting differences in alpha_vir, sigma, M_cl.
-%mm [delete para break]
+%
 The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 4 Myr within 3.5 kpc from the galaxy center of mass.
@@
 
-% mm2 [move this sentence up to give sections in order]
 In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
@@
 We note that this process is the three-dimensional analog to identifying molecular structures based on the noise levels in position-position-velocity (PPV) maps that observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN.
-This is commonly done by
-identifying clumps based on/after applying S/N-clipping, using tools
-such as the \ncode{aips} tasks \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; (e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a})).
-%
-%We note that, owing to the nature of \obs, such structures are identified in position-position-velocity (PPV) space, whereas in simulations, one has the full 6D spatial-kinematic information, and can therefore cleanly identify structures directly using the density field in position-position-position (PPP) space.
+This is commonly done by identifying clumps based on/after applying S/N-clipping, using tools such as the \ncode{aips} tasks \ncode{serch}, \ncode{clumpfind}, and \ncode{cprops}; (e.g., \citealt{Williams94a, Oka01a, Rosolowsky06a, Rosolowsky08a, DonovanMeyer13a})).
+%
 Existing studies find a good correspondence in the dynamical properties extracted in PPV- versus PPP-space for well-isolated structures (\citealt{Ballesteros-Paredes02a, Heitsch09a, Shetty10a, Beaumont13a, Pan15a}, but see \citealt{Ballesteros-Paredes02a} and \citealt{Shetty10a} for a discussion on caveats and limitations).
-% large scale structure in PPP may be identified as numerous lower mass structures in the PPV cube due to gradients in the LOS and conversly, superposition when spatially distinct components with the same velocity are "merged" into one component in the PPV space when observed along the LOS (see Fig.
-1 of Beaumount13a).
-(may be worth putting more thoughts on this after the report is due).
 
@@
 %
-In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs
-are selected at $n_{\rm cut} \leq n_{\rm H2}$.
+In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs are selected at $n_{\rm cut} \leq n_{\rm H2}$.
 We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
-% We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).
 Note that with these choices we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest 
-$n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc
-(bottom panels) over all the considered evolutionary stages of \flower
-traced in the simulation. Note that the scales shown on the $y$-axes
-are different between the top and bottom panels, as fewer MCCs are
-identified at higher $n_{\rm cut}$.
-%mm2: [still needs to be done]
+\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
+Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
 \AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
@@
 
-%mm2 We start by considering the MCC distributions in terms of their
-     We start by considering the distributions of MCC
-molecular gas mass, radius, and gas mass fraction, which we define as
+We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
 \begin{equation}
@@
 %
-We show in \Fig{dist} the distributions
-%mm2 considering all the evolutionary stages of \flower and dividing the sample in
-%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
-%cut}$\eq18.96\,\cc, lower panels) density cuts 
-      from the combination of the three considered evolution stages.
-      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
-      (top panels) and a high cut \footnote{The highest density
-        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
-        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
-        densest structure. However, not all evolutionary stages
-        considered have at least one MCC at this highest density
-        threshold, so we consider MCCs identified with the second
-        highest density threshold instead.}.
- of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
-%
-Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
-whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
-
-% address the biggest MCC = molecular disk of \flower
-%mm2 [This figure would be better with a color bar rather than the
-%prominent stars at the bottom...]
+We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
+We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
+%
+Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
+
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures
-identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
-%
-Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded 
-in the discussion of MCC dynamics in the remainder of this paper. 
+\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
+The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
+%
+Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower.
+These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper.
 \label{fig:stellarRatio16}}
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
-to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
-identified as a single component at low $n_{\rm cut}$. This main disk
-component
-% mm2 occupy the top right   [left not right!]
-          occupies the top left
-corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
+This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
 The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
@@
 
-\subsection{Single Evolutionary Stage}  \label{sec:singless}
+\subsection{Single Evolutionary Stage}\label{sec:singless}
 
@@
 \caption{
-Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation
-(middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for
-MCCs (star symbols) identified in the two most extreme evolutionary
-stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
-$n_{\rm cut}$, as illustrated by the colorbar shown on the right.
-Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs
-since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
+%
+Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
+%
+Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}.
+%
 Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
-The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for
-the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
+%
+The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for the gas to be in equilibrium, see Equation~\ref{eqn:v0}.
 Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
-Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
-MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
-and \citet{Kauffmann17b}.
+Swinbank11a, Leroy15a, Kauffmann17a,Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
 \label{fig:larsons_single}}
@@
 Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
-disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
+%
+The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
+%
 Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
@@
 
-% middle
 While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
-disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
-explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
-influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
+The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
+On the other hand, the MCCs in this phase are mostly stable, with
 virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

### 2019-07-04 WRITEUP/ms.tex
more revisions to 5; fixed a compile error

--- 2019-07-04 WRITEUP/ms.tex
@@
 % address the biggest MCC = molecular disk of \flower
-%mm2 [This figure would be better with a color bar rather than the
-%prominent stars at the bottom...]
+%mm2 [This and following figures would be better with the  color bar
+%from Figure 7 rather than the prominent stars at the bottom...]
 \begin{figure}
@@
           occupies the top left
-corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
-The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+corner of \Fig{stellarRatio16}, with a low gas mass fraction of
+$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
+dominated by bulk
+% mm2 motions,
+rotational motion,
+as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
 %
-Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
-%
-For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.
+Excluding the structure corresponding to the molecular disk, the
+velocity dispersions of most MCCs in the accreting phase of \flower
+are dominated by turbulent motions, 
+% mm2 . On the other hand, [the first hand is missing]
+  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
+  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
+%mm2 in the quiescent disk-like phase.
+%
+For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.
 
@@
 \caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures 
-identified across all $n_{\rm cut}$, as shown using the same color-coding as \Fig{stellarRatio16}.
+identified across all values of $n_{\rm cut}$, shown using the same color-coding as \Fig{stellarRatio16}.
 %
@@
 MCCs (star symbols) identified in the two most extreme evolutionary
-stages of \flower\ --- accreting (left) and starburst (right). Star symbols are color-coded by density thresholds
+stages of \flower---accreting (left) and starburst (right). Star symbols are color-coded by density threshold
 $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
@@
 Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
-Swinbank11a, Leroy15a, Kauffmann17a}, % black dot = extragalactic GMCs in quiescent environments
+  Swinbank11a, Leroy15a, Kauffmann17a},
+% mm2
+    and \citet{Kauffmann17b}.
+% black dot = extragalactic GMCs in quiescent environments
 MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
-and \citet{Kauffmann17b}.
+%mm2 [this was dangling here.  I moved it up to the citation list.] and \citet{Kauffmann17b}.
 \label{fig:larsons_single}}
@@
 \includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
-\caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right).
+\caption{Same as \Fig{larsons_single}, except star symbols are showing
+  molecular gas structures identified across all evolutionary stages
+  traced in our simulation,
+  color-coded by the SFR of \flower in those stages (see colorbar on the right).
 Left panels show structures identified using a low density threshold of $n_{\rm cut}$\eq0.53\,\cc and the right panels show those identified using a high density threshold of $n_{\rm cut}$\eq18.96\,\cc.
-The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular 
+The biggest MCCs identified at the low density threshold, occupying the top right corner of the top left panel, correspond to the molecular 
 disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel). 
-Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
+Notably fewer MCCs populate the right panels because there are only a few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
 The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
@@
 
-Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}). 
+Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower---the accreting and starburst phases (see \Sec{sfh}). 
 These properties are plotted in \Fig{larsons_single} together with observational results of nearby and $z$\,$\simeq$2 molecular structures for comparison.
 
-During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+During the accreting phase, MCCs in \flower\ are characterized by
+large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
 These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
@@
 influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
-virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
+virial parameter comparable to some of the molecular structures
+observed in the Milky Way,
+% mm2 but the former is
+     though the MCCs are
+     more massive.
 
@@
 
-If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
-(i.e., if virialization is a universal property of molecular clouds with negligible surface pressure), 
-one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at a given gas mass surface density $\Sigma$. 
-The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental properties of 
-molecular clouds. Previous studies suggest that the observed mass-size relation of molecular clouds 
+%mm2 [fiddled with tenses and plurals]
+If constant column density (Larson's third relation) were truly a
+fundamental property of molecular clouds,
+% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+% mm2 (i.e., 
+   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, 
+one would expect a single point in the $\sigma_{\rm
+  gas}^2/R$--$\Sigma$ relation at
+% mm a given gas
+    that
+mass surface density $\Sigma$. 
+The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of 
+molecular clouds
+% mm2 [maybe this is excessive, but if we are discussing the issue it
+% seems worth citing.]
+     in agreement with \citet{Heyer09a}.
+Previous studies suggest that the observed mass-size relation of molecular clouds 
 is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of 
@@
 of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
-ultra-luminous IR galaxies (ULIRGs) \citep{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
+ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
 % LMC: 0.01 g cm^-2

### 2019-07-04 WRITEUP/ms.tex

--- 2019-07-04 WRITEUP/ms.tex
@@
 %
-We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
-We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
+We show in \Fig{dist} the distributions
+%mm2 considering all the evolutionary stages of \flower and dividing the sample in
+%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
+%cut}$\eq18.96\,\cc, lower panels) density cuts 
+      from the combination of the three considered evolution stages.
+      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
+      (top panels) and a high cut \footnote{The highest density
+        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
+        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
+        densest structure. However, not all evolutionary stages
+        considered have at least one MCC at this highest density
+        threshold, so we consider MCCs identified with the second
+        highest density threshold instead.}.
+ of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
 %
-Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
+Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
+whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
 
+% address the biggest MCC = molecular disk of \flower
+%mm2 [This and following figures would be better with the  color bar
+%from Figure 7 rather than the prominent stars at the bottom...]
 \begin{figure}
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
-This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
-The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
+to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
+identified as a single component at low $n_{\rm cut}$. This main disk
+component
+% mm2 occupy the top right   [left not right!]
+          occupies the top left
+corner of \Fig{stellarRatio16}, with a low gas mass fraction of
+$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
+dominated by bulk
+% mm2 motions,
+rotational motion,
+as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
 %
-Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
-On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
+Excluding the structure corresponding to the molecular disk, the
+velocity dispersions of most MCCs in the accreting phase of \flower
+are dominated by turbulent motions, 
+% mm2 . On the other hand, [the first hand is missing]
+  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
+  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
+%mm2 in the quiescent disk-like phase.
 %
-For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.
+For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.
 
@@
 Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
-Swinbank11a, Leroy15a, Kauffmann17a,Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
+Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
 \label{fig:larsons_single}}
@@
 
-During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+During the accreting phase, MCCs in \flower\ are characterized by
+large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
 These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
@@
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
-The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MCCs in this phase are mostly stable, with
-virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
+disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
+explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
+influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
+virial parameter comparable to some of the molecular structures
+observed in the Milky Way,
+% mm2 but the former is
+     though the MCCs are
+     more massive.
 

### 2019-07-04 WRITEUP/ms.tex
minor fix and wording edits with AF

--- 2019-07-04 WRITEUP/ms.tex
@@
 \begin{abstract}
-We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization using cosmological zoom-in simulation.
+We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
 We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
 using an H$_2$ density-based clump finder. 
-We compare their mass, size, velocity dispersion, gas surface density, and virial parameter to \obs and perform Toomre-Q stability 
-analysis to understand the origin and dynamical properties of MCC.
+We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
 %
-In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\simeq45-100$\,pc, 
-which are comparable to nearby spirals and starburst galaxies. 
-MCCs are highly supersonic and supported by non-thermal turbulence, with velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
-and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way).
-That said, their velocity dispersion and gas surface density are comparable to nearby and $z$\ssim2 gas-rich starburst galaxies.
+In \flower, the typical MCC mass and size are $10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
+which are comparable to those found in nearby spirals and starburst galaxies. 
+MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
+and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
+similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
 %
-We identify gravitationally unstable MCCs via Toomre $Q_{\rm eff}$ analysis and
-the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
-MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have lower $\alpha_{\rm vir}$ 
-and $Q_{\rm eff}$ values, % indicative of instability to collapse. 
-where star formation is expected to take place within the clumps and cores on even smaller scales, as non-thermal energy 
-quickly dissipates. % and the gas structures are no longer supported by turbulence.
-%
-As such, detailed studies on the star-forming gas dynamics at EoR requires a spatial resolution of $\lesssim$40\,pc, which is 
+In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs.
+We find that MCCs are globally stable in the main disk of \flower.
+Densest regions where \SF is expected to take place in
+clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
+Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc 
+($\simeq$\,0$\farcs$01), which is 
 within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
@@
 
-\subsection{Larson's Relations and Virial Parameter}\label{sec:PVE}
+\subsection{Larson's Relations}\label{sec:PVE}
 
@@
 
-\subsection{Toomre stability analysis}\label{sec:Q}
+\subsection{Toomre Stability}\label{sec:Q}
 
 The onset of gravitational instability is tightly connected to \SF
-%mm2 [added Martin & Kennicutt 2001]
 \citep[e.g.,][]{Kennicutt89a, Martin01, Wang94a, Li05b, Li06a}.
@@
 \end{equation}
-\citep{Romeo92a}.
+\citep{Romeo92a},
+where $\altomega$ is the galactic radius.
 In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively.
@@
 %
-Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel. \AP{please change $\rm Kpc$ to $\rm kpc$}
+Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
 \label{fig:MCC}
@@
 
-\subsection{Molecular Cloud Complex Properties} \label{sec:distribution}
+\subsection{MCC Properties} \label{sec:distribution}
 
@@
 
-\subsection{Distributions of MCC Basic Properties
-  % mm2 and Outlier
-} \label{sec:dist}
+\subsection{MCC Basic Properties} \label{sec:dist}
 \begin{figure*}[htbp]
@@
 Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
-\AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
 \label{fig:dist}}
@@
 %--------------------------------------------------------------------------
-\section{Discussions}\label{sec:diss}
+\section{Discussion}\label{sec:diss}
 
-\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}
+\subsection{Synthetic vs Observed MCC Properties} \label{sec:diss1}
 
@@
 
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B \,{\rm K}\,{\rm cm}^{-3})\in[7, 9]$, with a median of 7.6.
+The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges in $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
 Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
@@
 
-The large ($>$\,2) virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
+The large virial parameters ($\alpha_{\rm vir}>$\,2) seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
 %
@@
 On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
-
-If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase?
-Such tension in the interpretation is understood as follows.
-%
-First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. This in turn would enable
-sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
-% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF.
-These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
-Further, the SFR of \flower is very bursty and high SFR stages are only transient.
-%
-Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy.
-This re-iterates the statement about low $Q$ above.
 
@@
 
-The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, after excluding the 
+High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
+This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
+central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that 
+funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, 
+the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. 
+The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive 
+MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
+
+The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, which is a proxy to different tracers used in observations. 
+For instance, ......
+after excluding the 
 most massive molecular structure identified (which correspond to the main disk of \flower). 
@@
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
-The Next Generation VLA (ngVLA) in the 2030s could in principle enable imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission. 
+The Next Generation VLA (ngVLA) in the 2030s will enable imaging of molecular gas down to $\sim$\,200\,pc \citep{Casey18a} blah blah blah \DL{editing}.
 % 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
@@
 \section*{Acknowledgements}
-We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
+We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
 %

### 2019-07-04 WRITEUP/ms.tex
added Krumholz & Burkhart 2018, possibly in the wrong place...

--- 2019-07-04 WRITEUP/ms.tex
@@
 We investigate possible variations in the dynamics of the molecular structures of \flower 
-by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
+by adopting different
+% mm2 sets
+    values
+of $n_{\rm cut}$ % in identifying the MCCs
 to test the robustness of our results against the choice of density threshold. 
-That is, how sensitive are the structure properties, and thus, the 
-results presented in \Sec{singless} dependent on the choice of density thresholds.
+That is, how sensitively are the structure properties, and thus, the 
+results presented in \Sec{singless}, dependent on the choice of density thresholds?
 
@@
 %--------------------------------------------------------------------------
-\section{Discussions}\label{sec:diss}
-
-\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}
+\section{Discussion}\label{sec:diss}
+
+\subsection{
+  % mm2 Comparing MCC Observable Quantities to Observations
+  Comparison to Observations
+} \label{sec:diss1}
 
@@
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
-However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
-are limited by the spatial resolution. 
-%
-The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+However, the sizes of MCCs are almost a factor of two smaller. This
+% mm2 likely suggest
+    suggests 
+that the sizes of \highz molecular gas structures reported in the literature
+are
+% mm2
+   probably
+limited by the spatial resolution. 
+%
+The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
 Such high velocity dispersion
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
+%mm2
+   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
+   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
+   higher velocities likely being produced by Toomre instability driven radial inflow.
 

### 2019-07-04 WRITEUP/ms.tex
into conclusions

@@
 component
-% mm2 occupy the top right   [left not right!]
+%mm2 occupy the top right   [left not right!]
           occupies the top left
@@
 dominated by bulk
-% mm2 motions,
+%mm2 motions,
 rotational motion,
@@
 are dominated by turbulent motions, 
-% mm2 . On the other hand, [the first hand is missing]
+%mm2 . On the other hand, [the first hand is missing]
   while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
@@
 observed in the Milky Way,
-% mm2 but the former is
+%mm2 but the former is
      though the MCCs are
@@
 % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
-% mm2 (i.e., 
+%mm2 (i.e., 
    and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, 
@@
 molecular clouds
-% mm2 [maybe this is excessive, but if we are discussing the issue it
+%mm2 [maybe this is excessive, but if we are discussing the issue it
 % seems worth citing.]
@@
 by adopting different
-% mm2 sets
+%mm2 sets
     values
@@
 However, the sizes of MCCs are almost a factor of two smaller. This
-% mm2 likely suggest
+%mm2 likely suggest
     suggests 
@@
 are
-% mm2
+%mm2
    probably
@@
 
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges in $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
-Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
+In our simulated galaxy, the high pressure MCCs
+%mm2 of \flower
+are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
 %
@@
 % different evolutionary stages
-We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr.
+%mm2 [rearranged]
+We do not find any major quantitative differences  (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr.
 However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
@@
 Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations.
-This can be understood since stars in \flower dominates the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
+This can be understood since stars in \flower dominate the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
 In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$
@@
 This demonstrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures.
-This consideration is especially relevant for the relatively evolved and enriched systems at high redshift, that are preferentially being imaged at high resolution with ALMA.
+This consideration is especially relevant for the relatively evolved and enriched systems at high redshift that are preferentially being imaged at high resolution with ALMA.
 In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$.
@@
 The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, which is a proxy to different tracers used in observations.
+%mm2 [needs cleanup]
 For instance, ......
 after excluding the 
-most massive molecular structure identified (which correspond to the main disk of \flower). 
+most massive molecular structure identified (which corresponds to the main disk of \flower). 
 The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 

### 2019-07-04 WRITEUP/ms.tex
minor edits to conclusion

--- 2019-07-04 WRITEUP/ms.tex
@@
 %
-In \flower, the typical MCC mass and size are $10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
+In \flower, the typical MCC mass and size are $M_{\rm gas}\simeq10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
 which are comparable to those found in nearby spirals and starburst galaxies. 
@@
 We show in \Fig{dist} the distributions
-%mm2 considering all the evolutionary stages of \flower and dividing the sample in
-%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
-%cut}$\eq18.96\,\cc, lower panels) density cuts 
       from the combination of the three considered evolution stages.
@@
 We investigate possible variations in the dynamics of the molecular structures of \flower 
-by adopting different
-% mm2 sets
-    values
-of $n_{\rm cut}$ % in identifying the MCCs
+by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
 to test the robustness of our results against the choice of density threshold. 
-That is, how sensitively are the structure properties, and thus, the 
-results presented in \Sec{singless}, dependent on the choice of density thresholds?
+That is, how sensitive are the structure properties, and thus, the 
+results presented in \Sec{singless} dependent on the choice of density thresholds.
 
@@
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
-However, the sizes of MCCs are almost a factor of two smaller. This
-% mm2 likely suggest
-    suggests 
-that the sizes of \highz molecular gas structures reported in the literature
-are
-% mm2
-   probably
-limited by the spatial resolution. 
+However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
+are limited by the spatial resolution. 
 %
-The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
 Such high velocity dispersion
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%mm2
-   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
-   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
-   higher velocities likely being produced by Toomre instability driven radial inflow.
 
@@
 
-%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
-%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
-%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
-%can be understood by acknowledging the fact that a given MCC in \flower
-%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
-%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
-%predictions for CO line emission in the work presented by
-%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
-%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
-%that the MCCs in our simulation have lower column densities than the
-%star-forming cores observed in the Milky Way, which are
-%observationally well-resolved within an MCC, and indeed, have
-%sufficient column density to form CO.
-%
-%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
-%This makes sense from simply the fact that smaller MCCs have smaller masses.
-%However, what does it mean for them to lie on the same locus?
-%
-%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
-%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
-%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
-%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
-%%If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds,
-%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
-%%regions of massive \SF.
-%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
-%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
-%%  point on that relationship, at the constant $\Sigma$ value.  }
-%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
-%with a certain tracer (e.g., \citealt{Ballesteros11}).
-%That is, it is solely a result of $\rho\propto M R^{-3}$.
-%For instance, \citet{Ballesteros02a} show that the density
-%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-%two-dimensional space; the latter is done in \obs.
-%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
-%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
-%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
-%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
-%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
-%% since $M$ would then scale as $R^{3}$.
-%% naturally display a linear relationship in $\log M - \log R$ plot.
-%
-%% the widespread in density for a given R.
-%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
-%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
-%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
-%Following \citet{Ballesteros02a}'s argument, we expect the density
-%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
-%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
-%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$.
-%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
-%
-%\begin{figure}
-%\centering
-%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
-%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
-%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
-%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
-%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower.
-%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
-%\label{fig:n}}
-%\vspace{0.5em}
-%\end{figure}
-
 \subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}
-
 \begin{figure*}
@@
 
-High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
-This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
-central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that 
-funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, 
-the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. 
-The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive 
-MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
-
-The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, which is a proxy to different tracers used in observations. 
-For instance, ......
-after excluding the 
-most massive molecular structure identified (which correspond to the main disk of \flower). 
-The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 
-and breaks down into smaller MCCs at higher density thresholds, with a typical size of $R\simeq\,50$\,pc.
-%
-The typical mass of MCCs is $10^{6.5}$\,\Msun.
+Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc
+and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 
-% We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
-%observed in the Milky Way disk, the Galactic center, and
-%gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations.
-%This comparison is done for different evolutionary stages of \flower.
+High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
+This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
+central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that 
+funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, 
+the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. 
+The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive 
+MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
 
@@
 Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
-Such MCCs identified in the denser regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
 
@@
 This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
-%
-%% end
-%Determining the multi-phase ISM properties of early galaxies
-%is a critical piece to understanding the evolution and
-%assembly history of galaxies, since they set the pace
-%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
-%While observations leveraging the combination of spatial-spectral imaging of
-%multi-band continuum and spectral line emission are crucial,
-%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
-%% are expected to have molecular gas structures on sub-kpc scales. 
-% Higher resolution imaging of molecular gas 
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
-The Next Generation VLA (ngVLA) in the 2030s will enable imaging of molecular gas down to $\sim$\,200\,pc \citep{Casey18a} blah blah blah \DL{editing}.
-% 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
+% Due to effect of the cosmic microwave background (CMB),
+Resolving the molecular gas at the EoR on similar resolution can have achieved by observing the higher-$J$ transitions of the CO 
+lines using the Next Generation VLA (ngVLA) in the 2030s.
+% 0.005" highest freq
 On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

### 2019-07-04 WRITEUP/ms.tex

@@
 are dominated by turbulent motions,
-% mm2 . On the other hand, [the first hand is missing]
+%mm2 . On the other hand, [the first hand is missing]
   while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
@@
 % or the roughly linear relationship between $\rho$ and $R$ of MCCs.
-% mm2 (i.e., 
+%mm2 (i.e.,
    and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure,
@@
 We investigate possible variations in the dynamics of the molecular structures of \flower
-by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
+by adopting different
+%mm2 sets
+    values
+of $n_{\rm cut}$ % in identifying the MCCs
 to test the robustness of our results against the choice of density threshold.
-That is, how sensitive are the structure properties, and thus, the 
-results presented in \Sec{singless} dependent on the choice of density thresholds.
+That is, how sensitively are the structure properties, and thus, the
+results presented in \Sec{singless}, dependent on the choice of density thresholds?
 
@@
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
-are limited by the spatial resolution. 
+However, the sizes of MCCs are almost a factor of two smaller. This
+%mm2 likely suggest
+    suggests
+that the sizes of \highz molecular gas structures reported in the literature
+are
+%mm2
+   probably
+limited by the spatial resolution.
 %
-The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
 Such high velocity dispersion
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
+%mm2
+   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
+   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
+   higher velocities likely being produced by Toomre instability driven radial inflow.
 
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges in $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
-Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
+In our simulated galaxy, the high pressure MCCs
+%mm2 of \flower
+are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
 %
@@
 This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
-Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
-% Due to effect of the cosmic microwave background (CMB),
+Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. % Due to effect of the cosmic microwave background (CMB),
 Resolving the molecular gas at the EoR on similar resolution can have achieved by observing the higher-$J$ transitions of the CO

### 2019-07-04 WRITEUP/ms.tex
edited ngvla sentence

@@
 This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
-%%
-%Low-$Q$ sets the regions that fragments
-% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
-%
-%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with
-% higher gas mass surface densities and velocity dispersions.
 This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
-Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. % Due to effect of the cosmic microwave background (CMB),
-Resolving the molecular gas at the EoR on similar resolution can have achieved by observing the higher-$J$ transitions of the CO
-lines using the Next Generation VLA (ngVLA) in the 2030s.
+Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
+With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
 % 0.005" highest freq
-On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
-%These predictions can in turn be
-%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
-%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
-%\SF since the cosmic dark ages.
+In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
 

### 2019-07-04 plotSS.py
xlabel

@@ -118,7 +118,7 @@ def plot_dis_allSS(minss=16, maxss=28, pattern1='0.32', pattern2='18.96',
     weights = np.ones_like(allmass11)/float(len(allmass11))
     ax[0, 0].hist(allmass11, bins=np.arange(min(allmass11), max(allmass11) +binwidth, binwidth), weights=weights)
 #     ax[0, 0].set_title(r'$n_{\rm cut}$ = %s [cm$^{-3}$]' % pattern1)
-    ax[0, 0].set_title(r'$\log M_{\rm cl}$ [M$_{\odot}]$', fontsize=20)
+    ax[0, 0].set_title(r'$\log M_{\rm gas}$ [M$_{\odot}]$', fontsize=20)
     ax[0, 0].set_ylabel(r'$N$', fontsize=20)
     ax[0, 0].set_xlim([5.7, 8.5])
     ax[0, 0].set_xticklabels([])

### 2019-07-04 WRITEUP/ms.tex

@@
 
-%mm2 [fiddled with tenses and plurals]
 If constant column density (Larson's third relation) were truly a
 fundamental property of molecular clouds,
-% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
-%mm2 (i.e.,
-   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure,
-one would expect a single point in the $\sigma_{\rm
-  gas}^2/R$--$\Sigma$ relation at
-% mm a given gas
-    that
+and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that
 mass surface density $\Sigma$.
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of
-molecular clouds
-%mm2 [maybe this is excessive, but if we are discussing the issue it
-% seems worth citing.]
-     in agreement with \citet{Heyer09a}.
+molecular clouds in agreement with \citet{Heyer09a}.
 Previous studies suggest that the observed mass-size relation of molecular clouds
@@
 column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
-%For instance, \citet{Ballesteros02a} show that the density
-%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
-%two-dimensional space; the latter is done in \obs.
-%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
-%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
-%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
-%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
-%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
-%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).
-
-%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
-%\citep{Larson81a, McKee07a}.
-%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
-%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
-%the mass-size relation is also known as the constant column density relation and has been
-%proposed as a fundamental property of molecular clouds on different physical scales.
-%
-%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
-%\begin{equation}
-%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
-%\end{equation}
-%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
-%\begin{equation}\label{eqn:constantcolumndensity}
-%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
-%\end{equation}
-%where we adopt $\mu = 2.5$ as the mean molecular weight.
-%
-%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
-%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
-%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
-%Further discussions on the interpretation of this is provided in \Sec{MR}.
-%%
-%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
-%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
-5 therein]{Behrens18a}
 
@@
 %
-% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
-%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
-%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
-%This is consistent with our physical intuition of gas instability leading to \SF.
 
@@
 %
-%For instance, the cluster of points found at the lowest density threshold,
-%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28},
-%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
-%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$,
-%MCCs identified at lower density in the outskirts of \flower
-%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
-%%
-%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.
-
-%
 The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
@@
 In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-%%
-%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
 The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller. This
-%mm2 likely suggest
-    suggests
-that the sizes of \highz molecular gas structures reported in the literature
-are
-%mm2
-   probably
-limited by the spatial resolution.
+However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
+are probably limited by the spatial resolution.
 %
@@
 %mm2
-   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
+   This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to
    feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
@@
 In our simulated galaxy, the high pressure MCCs
-%mm2 of \flower
 are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
@@
 
-% different evolutionary stages
-%mm2 [rearranged]
 We do not find any major quantitative differences (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr.

### 2019-07-04 WRITEUP/ms.tex
added ngvla link, minor edits to caption, removed gas-only alphavir

@@
 %
-Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}.
+% Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16})
+% \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}.
 %
@@
 explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential
-influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with
+influences the overall stability.
+On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with
 virial parameter comparable to some of the molecular structures
-observed in the Milky Way,
-%mm2 but the former is
-     though the MCCs are
-     more massive.
+observed in the Milky Way, though the MCCs are more massive.
 
@@
 We investigate possible variations in the dynamics of the molecular structures of \flower
-by adopting different
-%mm2 sets
-    values
-of $n_{\rm cut}$ % in identifying the MCCs
+by adopting different values of $n_{\rm cut}$
 to test the robustness of our results against the choice of density threshold.
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%mm2
    This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to
@@
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
-With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
+With the Next Generation VLA (ngVLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
 % 0.005" highest freq

### 2019-07-04 WRITEUP/ms.tex
some more cleaning

--- 2019-07-04 WRITEUP/ms.tex
@@
 We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
-We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'')
-using an H$_2$ density-based clump finder.
+We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
+%
 We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
-%
-In \flower, the typical MCC mass and size are $M_{\rm gas}\simeq10^{6.5}$\,\Msun and $R\simeq45-100$\,pc,
-which are comparable to those found in nearby spirals and starburst galaxies.
-MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
-and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
-similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
+In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies.
+MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
 %
@@
 We find that MCCs are globally stable in the main disk of \flower.
-Densest regions where \SF is expected to take place in
-clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
-Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc
-($\simeq$\,0$\farcs$01), which is
-within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
+Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
+%
+Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
 \end{abstract}
@@
 In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
-%mm2 [citation or derivation needed?]   ***********
 \begin{equation}
@@
 
-Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar
-tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
+Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
+We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
 Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
@@
 \caption{
-    {\it Top}: Star formation history of \flower. {\it Bottom}:
-    projected stellar mass distribution during {\it (a)} an early
-    accreting phase;  {\it (b)} a major starburst following a merger
-    event; and {\it (c)} a relatively quiescent post-starburst
-    phase.
-\label{fig:SFH}}
+    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
+    %
+    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
+    \label{fig:SFH}
+   }
 \end{figure*}
@@
 
-In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics
-by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
+In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
 %
@@
 %
-We show in \Fig{dist} the distributions
-      from the combination of the three considered evolution stages.
-      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
-      (top panels) and a high cut \footnote{The highest density
-        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
-        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
-        densest structure. However, not all evolutionary stages
-        considered have at least one MCC at this highest density
-        threshold, so we consider MCCs identified with the second
-        highest density threshold instead.}.
+We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
+We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.}.
 of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
-to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
-identified as a single component at low $n_{\rm cut}$. This main disk
-component
-%mm2 occupy the top right   [left not right!]
-          occupies the top left
-corner of \Fig{stellarRatio16}, with a low gas mass fraction of
-$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
-dominated by bulk
-%mm2 motions,
-rotational motion,
-as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
+This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
+The velocity dispersion of such a structure is dominated by bulk rotational motion, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
 %
-Excluding the structure corresponding to the molecular disk, the
-velocity dispersions of most MCCs in the accreting phase of \flower
-are dominated by turbulent motions,
-%mm2 . On the other hand, [the first hand is missing]
-  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
-  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
-%mm2 in the quiescent disk-like phase.
+Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
 %
@@
 
-During the accreting phase, MCCs in \flower\ are characterized by
-large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
 These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
@@
 %
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main
-disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
-explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential
-influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with
-virial parameter comparable to some of the molecular structures
-observed in the Milky Way,
-%mm2 but the former is
-     though the MCCs are
-     more massive.
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
+The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
+On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.
 
@@
 % Starburst
-In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however,
-MCCs in the starburst phase span a wider range in gas surface density
-(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
+In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
+%
 That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
-The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
-of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby
-ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
+The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
 % LMC: 0.01 g cm^-2
@@
 
-We investigate possible variations in the dynamics of the molecular structures of \flower
-by adopting different
-%mm2 sets
-    values
-of $n_{\rm cut}$ % in identifying the MCCs
-to test the robustness of our results against the choice of density threshold.
-That is, how sensitively are the structure properties, and thus, the
-results presented in \Sec{singless}, dependent on the choice of density thresholds?
+\AP{let us recall to make the not about different molecular tracers also here}
+We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
+That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?
 
 The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
-As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
-corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher
-$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$
- since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
-Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$
-(see top panels of \Fig{alpha16-28}).
+As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
+%
+Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}).
 At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
@@
 The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
-This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
-nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
+This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
 
 At the highest density cut, only the densest gas structures are identified.
-The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more
-unstable against collapse (see middle right panel of \Fig{alpha16-28}).
+The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
 
@@
 In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
-spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
-are probably limited by the spatial resolution.
+%
+The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
+However, the sizes of MCCs are almost a factor of two smaller.
+This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
 %
 The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion
-in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%mm2
-   This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to
-   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
-   higher velocities likely being produced by Toomre instability driven radial inflow.
+%
+This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.
 
@@
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs
-are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+In our simulated galaxy, the high pressure MCCs are found throughout the disk.
+This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
 %
@@
 \subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}
+
 \begin{figure*}
@@
 \caption{
-Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and
-their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
-Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols
-as an illustrative example.
+Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
+Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
 \label{fig:sigma}}
@@
 Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
-%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
 Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
 %
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region}
-reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations
-in relatively evolved and enriched systems at high redshifts.
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}
@@
 This can be understood since stars in \flower dominate the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$
-of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
+In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$ of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
@@
 
-% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}
-
 %--------------------------------------------------------------------------
@@
 
-Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc
-and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively.
+Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
-This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
-central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that
-funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand,
-the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
-The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive
-MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
-
+This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}.
+In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}).
+On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
+The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
+%
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
@@
 
-% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures.
 We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
@@
 Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
-
 % Toomre:
@@
 This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
+
 This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
+%
 With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.

### 2019-07-04 WRITEUP/ms.tex

@@
 The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.
+On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter comparable to some of the molecular structures
+observed in the Milky Way, though the MCCs are more massive.
 
@@
 \AP{let us recall to make the not about different molecular tracers also here}
+
 We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
@@
 %
-The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller.
-This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
-%
 The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%
+
 This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.
@@
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
-%
-With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
+With the Next Generation VLA (ngVLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
 % 0.005" highest freq
@@
 
-%==============================================================================
+%-------------------------------------------------------
 %                                Back matters
-%==============================================================================
+%-------------------------------------------------------
 % ACKNOWLEDGEMENTS

### 2019-07-04 plot_modules/plot_cloud_prop.py
add cbar

@@ -585,7 +585,6 @@ def plot_stuff(xstr, ystr, ls='', markersize=10,
             # uncomment below to get ncut in legend
             # for paper, we commented this out since we show it as colorbar in other figures.
             # legend_h.append(h)
-
         else:
             if xstr == "gas sd per ff" and ystr == "sfr sd":
                 _x = np.log10(_x)
@@ -818,6 +817,38 @@ def plot_stuff(xstr, ystr, ls='', markersize=10,
     ax.tick_params(axis='both', which='both')   # direction='in'
     plt.minorticks_on()
     plt.tight_layout()
+
+    if xstr == 'fgas' and ystr == 'cloud mass':
+        # add a cbar to the top of figure
+        abc = np.array(map(float, psuedo_keys))
+
+        if not sfrlabel:
+            c = np.linspace(min(abc), max(abc), 10)
+        else:
+
+            c = np.linspace(min(np.array(sfr.values())), max(sfr.values()))
+
+        import matplotlib as mpl
+        from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
+
+        norm = mpl.colors.Normalize(vmin=c.min(), vmax=c.max())
+        _cmap = mpl.cm.ScalarMappable(norm=norm, cmap=cm)
+        _cmap.set_array([])
+
+        ax_divider = make_axes_locatable(ax)
+        cax = ax_divider.append_axes("top", size="7%", pad="2%")
+        cbar = fig.colorbar(_cmap, ticks=c, # fraction=0.04, # aspect=10,
+                            # ax=axes.ravel().tolist(),
+                            orientation="horizontal",
+                            cax=cax)
+        cax.xaxis.set_ticks_position("top")
+        cbar.ax.tick_params(length=6, labelsize=legendFontSize)
+        if sfrlabel:
+            label = r'SFR [M$_{\odot}$~yr$^{-1}$]'
+        else:
+            label = r'$n_{\rm cut}$ [cm$^{-3}$]'
+        cbar.set_label(label, fontsize=20)
+        cbar.ax.xaxis.set_label_position('top')
 
     if save:
         name_out = ystr.replace(' ', '-') + '_' + \

### 2019-07-04 plotSS.py
remove gas-only alpha vir

@@ -352,4 +352,4 @@ if __name__ == '__main__':
                               tickwidth=2,
                               labelsize=25,
                               ticklabsize=20,
-                              saveFig=True)
+                              saveFig=True, overplotGasAlpha=False)

### 2019-07-04 plotsingleSS.py

@@ -205,4 +205,4 @@ if __name__ == '__main__':
                               tickwidth=2,
                               labelsize=25,
                               ticklabsize=20,
-                              saveFig=True)
+                              saveFig=True, overplotGasAlpha=False)

### 2019-07-04 WRITEUP/ms.tex

@@
 We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
-We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.}.
-of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
+We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
 %
@@
 
-\AP{let us recall to make the not about different molecular tracers also here}
+\AP{let us recall to make the note about different molecular tracers also here}
 
@@
 In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-%
+
+The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
+spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
+However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
+are probably limited by the spatial resolution.
 The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
@@
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-
+% 
 This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

### 2019-07-05 WRITEUP/ms.tex
mm's comment on cbar instead of legend
Finished my main revisions

--- 2019-07-04 WRITEUP/ms.tex
@@
 We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
-We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
+We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
+using an H$_2$ density-based clump finder. 
+We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
 %
-We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
-In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies.
-MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
+In \flower, the typical MCC mass and size are $10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
+which are comparable to those found in nearby spirals and starburst galaxies. 
+MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
+and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
+similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
 %
@@
 We find that MCCs are globally stable in the main disk of \flower.
-Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
-%
-Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
+Densest regions where \SF is expected to take place in
+clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
+Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc 
+($\simeq$\,0$\farcs$01), which is 
+within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
 \end{abstract}
@@
 In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
+%mm2 [citation or derivation needed?]   ***********
 \begin{equation}
@@
 
-Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
-We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
+Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar
+tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) as well as winds from OB and asymptotic giant branch stars.
 Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell.
@@
 \caption{
-    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
-    %
-    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
-    \label{fig:SFH}
-   }
+    {\it Top}: Star formation history of \flower. {\it Bottom}:
+    projected stellar mass distribution during {\it (a)} an early
+    accreting phase;  {\it (b)} a major starburst following a merger
+    event; and {\it (c)} a relatively quiescent post-starburst
+    phase.
+\label{fig:SFH}}
 \end{figure*}
@@
 
-In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
+In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics 
+by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
 %
@@
 %
-We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
-We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.}.
+We show in \Fig{dist} the distributions
+%mm2 considering all the evolutionary stages of \flower and dividing the sample in
+%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
+%cut}$\eq18.96\,\cc, lower panels) density cuts 
+      from the combination of the three considered evolution stages.
+      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
+      (top panels) and a high cut \footnote{The highest density
+        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
+        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
+        densest structure. However, not all evolutionary stages
+        considered have at least one MCC at this highest density
+        threshold, so we consider MCCs identified with the second
+        highest density threshold instead.}.
  of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
-This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
-The velocity dispersion of such a structure is dominated by bulk rotational motion, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
+to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
+identified as a single component at low $n_{\rm cut}$. This main disk
+component
+%mm2 occupy the top right   [left not right!]
+          occupies the top left
+corner of \Fig{stellarRatio16}, with a low gas mass fraction of
+$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
+dominated by bulk
+%mm2 motions,
+rotational motion,
+as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
 %
-Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
+Excluding the structure corresponding to the molecular disk, the
+velocity dispersions of most MCCs in the accreting phase of \flower
+are dominated by turbulent motions, 
+%mm2 . On the other hand, [the first hand is missing]
+  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
+  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
+%mm2 in the quiescent disk-like phase.
 %
@@
 
-During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+During the accreting phase, MCCs in \flower\ are characterized by
+large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
 These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
@@
 % 
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
-The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.
+The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
+disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
+explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
+influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
+virial parameter comparable to some of the molecular structures
+observed in the Milky Way,
+%mm2 but the former is
+     though the MCCs are
+     more massive.
 
@@
 
+%mm2 [fiddled with tenses and plurals]
 If constant column density (Larson's third relation) were truly a
 fundamental property of molecular clouds,
-and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that
+% or the roughly linear relationship between $\rho$ and $R$ of MCCs.
+%mm2 (i.e., 
+   and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, 
+one would expect a single point in the $\sigma_{\rm
+  gas}^2/R$--$\Sigma$ relation at
+% mm a given gas
+    that
 mass surface density $\Sigma$. 
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of 
-molecular clouds in agreement with \citet{Heyer09a}.
+molecular clouds
+%mm2 [maybe this is excessive, but if we are discussing the issue it
+% seems worth citing.]
+     in agreement with \citet{Heyer09a}.
 Previous studies suggest that the observed mass-size relation of molecular clouds 
@@
 column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
+%For instance, \citet{Ballesteros02a} show that the density
+%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
+%two-dimensional space; the latter is done in \obs.
+%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
+%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
+%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
+%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
+%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+%% since $M$ would then scale as $R^{3}$ (ånd naturally display a linear relationship in $\log M - \log R$ plot).
+
+%Larson's third relation describes the relationship between observed masses and sizes of molecular cloud structures
+%\citep{Larson81a, McKee07a}.
+%Since cloud mass in observational studies is sometimes derived by integrating over the mass surface density,
+%which is related to the column density ($N_H$), % that is obtainable from extinction maps ($A_V$),
+%the mass-size relation is also known as the constant column density relation and has been
+%proposed as a fundamental property of molecular clouds on different physical scales.
+%
+%By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as
+%\begin{equation}
+%A_V = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
+%\end{equation}
+%Assuming spherical symmetry, the mass of an MCC can then be expressed as a function of $A_V$ and its size $R$
+%\begin{equation}\label{eqn:constantcolumndensity}
+%M_{\rm gas} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
+%\end{equation}
+%where we adopt $\mu = 2.5$ as the mean molecular weight.
+%
+%We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
+%Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
+%Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
+%Further discussions on the interpretation of this is provided in \Sec{MR}.
+%%
+%%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
+%%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig.
+5 therein]{Behrens18a}
 
 % Starburst
-In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
-%
+In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, 
+MCCs in the starburst phase span a wider range in gas surface density 
+(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
 That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
-The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
+The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
+of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby 
+ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
 % LMC: 0.01 g cm^-2
@@
 %
+% Due to a time delay between cloud collapse and \SF, we also compare the virial parameter of MCCs in the pre-starburst phase and post-starburst phase.
+%\Fig{alphaEvol} shows that most MCCs in the pre-starburst phase have even lower virial parameter than in the starburst phase. On the other hand,
+%the virial parameter of MCCs in the post-starburst phase is higher than in both the pre-starburst and the starburst phase.
+%This is consistent with our physical intuition of gas instability leading to \SF.
 
@@
 
-\AP{let us recall to make the not about different molecular tracers also here}
-We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
-That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?
+We investigate possible variations in the dynamics of the molecular structures of \flower 
+by adopting different
+%mm2 sets
+    values
+of $n_{\rm cut}$ % in identifying the MCCs
+to test the robustness of our results against the choice of density threshold. 
+That is, how sensitively are the structure properties, and thus, the 
+results presented in \Sec{singless}, dependent on the choice of density thresholds?
 
 The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
-As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
-%
-Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}).
+As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
+corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher 
+$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ 
+ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
+Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ 
+(see top panels of \Fig{alpha16-28}). 
 At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
 %
+%For instance, the cluster of points found at the lowest density threshold, 
+%occupying the top right corner of the linewidth-size relation in the top left panel of \Fig{alpha16-28}, 
+%are broken down into smaller MCCs at the highest density threshold (see top right panel of the same figure\footnote{Note
+%that while the biggest MCCs are broken into smaller MCCs at higher $n_{\rm cut}$, 
+%MCCs identified at lower density in the outskirts of \flower
+%typically do not reach the density thresholds as $n_{\rm cut}$ increases. Hence, there are fewer MCCs at the highest density threshold.}).
+%%
+%These MCCs are smaller in size, and thus, occupy the leftward in the top right panel.
+
+%
 The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
-This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
+This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
+nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
 
 At the highest density cut, only the densest gas structures are identified.
-The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
+The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more 
+unstable against collapse (see middle right panel of \Fig{alpha16-28}).
 
@@
 In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
-%
-The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller.
-This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
+%%
+%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
+The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
+spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
+However, the sizes of MCCs are almost a factor of two smaller. This
+%mm2 likely suggest
+    suggests 
+that the sizes of \highz molecular gas structures reported in the literature
+are
+%mm2
+   probably
+limited by the spatial resolution. 
 %
 The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+Such high velocity dispersion
+in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
-%
-This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.
+%mm2
+   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
+   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
+   higher velocities likely being produced by Toomre instability driven radial inflow.
 
@@
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+In our simulated galaxy, the high pressure MCCs
+%mm2 of \flower
+are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
 %
@@
 
+% different evolutionary stages
+%mm2 [rearranged]
 We do not find any major quantitative differences  (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr.
@@
 This is expected for \SF to proceed.
+
+%\subsection{Is the Mass-Size Relation an Observational Artifact?} \label{sec:MR}
+%The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
+%by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
+%can be understood by acknowledging the fact that a given MCC in \flower
+%does not necessary contain CO\footnote{This is because CO forms deeper in molecular clouds and
+%our simulation does not have enough resolution to directly form CO. In fact, to form CO and make
+%predictions for CO line emission in the work presented by
+%\citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
+%That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag demonstrates
+%that the MCCs in our simulation have lower column densities than the
+%star-forming cores observed in the Milky Way, which are
+%observationally well-resolved within an MCC, and indeed, have
+%sufficient column density to form CO.
+%
+%In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
+%This makes sense from simply the fact that smaller MCCs have smaller masses.
+%However, what does it mean for them to lie on the same locus?
+%
+%The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
+%an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
+%%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
+%%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
+%%If constant column density (Larson's third relation) is truly a fundamental properties of molecular clouds,
+%%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
+%%regions of massive \SF.
+%%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
+%%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
+%%  point on that relationship, at the constant $\Sigma$ value.  }
+%However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
+%with a certain tracer (e.g., \citealt{Ballesteros11}).
+%That is, it is solely a result of $\rho\propto M R^{-3}$.
+%For instance, \citet{Ballesteros02a} show that the density
+%of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
+%two-dimensional space; the latter is done in \obs.
+%When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
+%line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
+%They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
+%observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
+%observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
+%% since $M$ would then scale as $R^{3}$.
+%% naturally display a linear relationship in $\log M - \log R$ plot.
+%
+%% the widespread in density for a given R.
+%We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
+%As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
+%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+%Following \citet{Ballesteros02a}'s argument, we expect the density
+%of MCCs to be independent of the cloud size (since they are identified in 3D-space).
+%On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
+%we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$.
+%As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.
+%
+%\begin{figure}
+%\centering
+%\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
+%\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
+%At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
+%form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
+%See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower.
+%For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
+%\label{fig:n}}
+%\vspace{0.5em}
+%\end{figure}
 
@@
 \caption{
-Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
-Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
+Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and
+their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
+Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols
+as an illustrative example.
 \label{fig:sigma}}
@@
 Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
+%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
 Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
 %
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} 
+reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations 
+in relatively evolved and enriched systems at high redshifts. 
 \label{fig:Qeff}}
@@
 This can be understood since stars in \flower dominate the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$ of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
+In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$
+of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
@@
 
+% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}
+
 %--------------------------------------------------------------------------
@@
 
-Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively.
+High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
+This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
+central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that 
+funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, 
+the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. 
+The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive 
+MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
+
+The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, which is a proxy to different tracers used in observations.
+%mm2 [needs cleanup]
+For instance, ......
+after excluding the 
+most massive molecular structure identified (which corresponds to the main disk of \flower). 
+The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 
+and breaks down into smaller MCCs at higher density thresholds, with a typical size of $R\simeq\,50$\,pc.
+%
+The typical mass of MCCs is $10^{6.5}$\,\Msun.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 
-High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
-This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}.
-In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}).
-On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
-The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
-%
+% We compare several observable quantities that reflect the dynamics of MCCs in \flower to those
+%observed in the Milky Way disk, the Galactic center, and
+%gas-rich starburst galaxies in the local Universe, and at the peak epoch of cosmic \SF in the context of the Larson's relations.
+%This comparison is done for different evolutionary stages of \flower.
+
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
@@
 
+% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures. 
 We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
@@
 Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
+Such MCCs identified in the denser regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable against collapse.
+
 % Toomre:
@@
 This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
+%%
+%Low-$Q$ sets the regions that fragments 
+% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
+%
+%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with 
+% higher gas mass surface densities and velocity dispersions.
 
 This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
+%
+%% end
+%Determining the multi-phase ISM properties of early galaxies
+%is a critical piece to understanding the evolution and
+%assembly history of galaxies, since they set the pace
+%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
+%While observations leveraging the combination of spatial-spectral imaging of
+%multi-band continuum and spectral line emission are crucial,
+%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
+%% are expected to have molecular gas structures on sub-kpc scales. 
+% Higher resolution imaging of molecular gas 
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
-%
-With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
-% 0.005" highest freq
-In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
+The Next Generation VLA (ngVLA) in the 2030s will enable imaging of molecular gas down to $\sim$\,200\,pc \citep{Casey18a} blah blah blah \DL{editing}.
+% 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
+On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics, and subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
+%These predictions can in turn be
+%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
+%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
+%\SF since the cosmic dark ages.
 
@@
 %
-We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
+% mm2 We acknowledge use of the
+
+\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}}
 %

### 2019-07-05 WRITEUP/ms.tex

--- 2019-07-04 WRITEUP/ms.tex
@@
 \begin{abstract}
-We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
+We study the properties of molecular cloud complexes (MCCs) at the epoch of reionization using cosmological zoom-in simulations.
 We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
@@
 %
-Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
+Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
+and the Next Generation Very Large Array.
+%mm2 (ngVLA).
 \end{abstract}
@@
 
-To understand the physical properties of MCCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MCCs in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).
+To understand the physical properties of MCCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MCCs in prototypical (i.e., $L^*$) galaxies in the epoch of reionization (EoR).
 
@@
 
-% address the biggest MCC = molecular disk of \flower
-%mm2 [This and following figures would be better with the  color bar
-%from Figure 7 rather than the prominent stars at the bottom...]
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
-\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$.
+\caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar).
 The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
@@
 
-This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
+This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
-With the Next Generation VLA (ngVLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
+With the Next Generation VLA%
+%mm2 (ngVLA
+\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
 % 0.005" highest freq
-In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
+In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics, and
+% mm2 subject to
+    dependent on
+the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
 
-%-------------------------------------------------------
 %                                Back matters

### 2019-07-05 WRITEUP/ms.tex
ncut subsection and obs

--- 2019-07-04 WRITEUP/ms.tex
@@
 
-\AP{let us recall to make the note about different molecular tracers also here}
-
 We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.
 That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds? 
+Observationally, this effect would be mimicked by e.g., adopting different molecular gas tracers since they have different critical densities.
 

### 2019-07-05 WRITEUP/ms.tex
syntax

--- 2019-07-05 WRITEUP/ms.tex
@@
 Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
-With the Next Generation VLA%
-%mm2 (ngVLA
-\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
+With the Next Generation VLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
 % 0.005" highest freq
-In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics, and
-% mm2 subject to
-    dependent on
+In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and depend on
 the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
@@
 %
-% mm2 We acknowledge use of the
-
-\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}}
-%
-%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
+\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and yt \citep{Smith09a,Turk11a}}
 

### 2019-07-05 WRITEUP/arxiv1/ms.tex
minor wording

--- 2019-07-05 WRITEUP/ms.tex
@@
 % --------------------------------------------
-%mm2 edits of 3 Jul 19 marked like this M-MML
-% AP: I have some compatibility issues with the new style (i.e. \section does not work)
-\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
+\documentclass[iop]{emulateapj}
 
-%\def\altomega{r_{\rm disk}}
 \def\altomega{\varpi}
-
 \usepackage{amsmath}
-
-\usepackage{comment}
+\usepackage{xcolor}
 
 \input{preamble}
-\slugcomment{To be Submitted.}
+\slugcomment{Submitted to ApJ.}
 
@@
 \makeatother
-
-\usepackage{xcolor}
-\definecolor{apcolor}{HTML}{b3003b}
-\definecolor{dlcolor}{HTML}{FF7F00}
-\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
-\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
-\definecolor{afcolor}{HTML}{b3443c}
-\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
-\definecolor{mmcolor}{HTML}{006600}
-\newcommand{\MM}[1]{({\bf \color{mmcolor} MM: #1})}
-
-% it can be instead included as
-% \graphicspath{{Fig/}}
-% so that plots are automatically searched for in the given path
-\def\figpath{./Fig}
 
@@
 and the Next Generation Very Large Array.
-%mm2 (ngVLA).
 \end{abstract}
@@
 Similar conclusions are also reached from the
-analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.][]{grisdale:2018}.
+analysis of clouds forming in a Milky-Way like galaxy simulated with a $\simeq 4\,{\rm pc}$ resolution \citep[i.e.,][]{grisdale:2018}.
 
@@
 This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight.
-The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e.
-sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
+The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
 %
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{sfh.pdf}
 \caption{
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{hist_test_16.pdf}
 \caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
@@
  \centering
-  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
+  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{combined.pdf}
 \caption{
@@
 The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$.
-The effective size is defined assuming spherical geometry, i.e.
-$R \equiv (3 V /4 \pi)^{1/3}$.
+The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
 %
@@
 In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
-Therefore, when calculating global quantities for MCS, we always perform a mass-weighting.
+Therefore, when calculating the global quantities of MCCs, we always perform a mass-weighting.
 Since we operate on data on a uni-grid, this is equivalent to density averaged quantities.
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{minmaxNcut_basicDistributions.pdf}
 \caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
+\includegraphics[width=0.5\textwidth]{cloud-mass_fgas.pdf}
 \caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar).
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{ss16-28-veldisp.pdf}
 \caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{3by2_clumpProp_ss16-ss22.png}
 \caption{
@@
 Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
-%
-% Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16})
-% \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}.
 %
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{3by2_clumpProp_allss}
 \caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right).
@@
 \centering
-\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
+\includegraphics[width=0.9\textwidth]{{ss16_toomre_combined_2by2_0_2.0}.pdf}
 \caption{
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{{ss16_toomre_combined_3by1_0_1.2}.pdf}
 \caption{
@@
 
-Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $R\simeq\,50$\,pc and $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun, respectively.
+Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun and $R\simeq\,50$\,pc, respectively.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
-%
+
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.
@@
 This also implies that \obs with spatial resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
-Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands.
+Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the highest frequency bands.
 With the Next Generation VLA\footnote{\url{http://library.nrao.edu/public/memos/ngvla/NGVLA\_21.pdf}}, which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
@@
 
+% ------------------------------------------------------------------------
 %                                Back matters
-%-------------------------------------------------------
+%--------------------------------------------------------------------------
 % ACKNOWLEDGEMENTS
@@
 %
+The Flatiron Institute is funded by the Simons Foundation.
 This research has made use of NASA's Astrophysics Data System Bibliographic Services.

### 2019-07-05 present/IAU/proceeding.tex
finalized

% IAU_Sample.tex -- sample pages for Proceedings IAU Symposium document class
% (based on v1.0 cca2esam.tex)
% v1.04 released 17 May 2004 by TechBooks
%% small changes and additions made by KAvdH/IAU 4 June 2004
% Copyright (2004) International Astronomical Union
% Minor updates made for WriteLatex.com by Martyn Bristow
% ...Downloaded from http://www.iau.org/static/scientific_meetings/authors/ June 2014
\NeedsTeXFormat{LaTeX2e}

\documentclass{iau}
\usepackage{graphicx}
\include{preamble}

\title[Dynamical Properties of MC in Galaxies at the EoR] %% give here short title %%
{Dynamical Properties of Molecular Cloud Complexes at the Epoch of Reionization}

\author[Leung et al.]   %% give here short author list %%
{T. K. Daisy Leung$^{1, 2}$
%%  \thanks{Present address: Fluid Mech Inc., 24 The Street, Lagos, Nigeria.},
Andrea Pallottini$^{3, 4}$, 
Andrea Ferrara$^{4, 5}$
\and Mordecai-Mark Mac Low$^{2, 6}$}

\affiliation{
$^1$ Department of Astronomy, Cornell University, NY, USA; email: {\tt tleung@astro.cornell.edu} \\[\affilskip]
$^2$ Center for Computational Astrophysics, Flatiron Institute, NY, USA \\ [\affilskip]
$^3$ Centro Fermi, Rome, Italy \\ [\affilskip]
$^4$ Scuola Normale Superiore, Pisa, Italy \\[\affilskip]
$^5$ Kavli Institute for the Physics and Mathematics of the Universe (IPMU), \\
        University of Tokyo, Japan\\ [\affilskip]
$^6$ American Museum of Natural History, NY, USA}

\pubyear{2019}
\volume{352} 
% \pagerange{??}
% \date{?? and in revised form ??}
\setcounter{page}{1}
\jname{Uncovering early galaxy evolution in the ALMA and JWST era}
% \editors{A.C. Editor, B.D. Editor \& C.E. Editor, eds.}
\begin{document}

\maketitle

\vspace{-.2em}
\begin{abstract}
The Atacama Large (Sub-)millimeter Array (ALMA) has provided glimpse of the interstellar medium (ISM) properties of galaxies
at the Epoch of Reionization (EoR); however, detailed understanding of their internal structure is still lacking.
We present properties of molecular cloud complexes (MCCs) in a prototypical galaxy at this epoch
studied in cosmological zoom-in simulations \citep{Leung19c}. 
Typical MCC mass and size are comparable to nearby spirals and starburst galaxies 
($M_{\rm cl}$\ssim10$^{6.5}$\,\Msun and $R\,\simeq$\,45--100\,pc).
MCCs are highly supersonic, with velocity dispersion of $\sigma_{\rm gas}\simeq$\,20 -- 100\,\kms and pressure of log($P/k_B$)\,$\simeq$\,7.6\,K\,cm$^{-3}$,
which are comparable to gas-rich starburst galaxies. 
 In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead have lower virial parameter and 
Toomre-$Q$ values. Detailed studies of the star-forming gas dynamics at the EoR thus require a spatial resolution of $<$\,40 pc
($\simeq$\,0.01$^{\prime\prime}$), which is within reach of ALMA, to complement studies of stellar populations at EoR 
using the James Webb Space Telescope ({\it JWST}).
\keywords{galaxies: high-redshift --
          galaxies: ISM, 
          galaxies: evolution, 
          ISM: structure,
          ISM: kinematics and dynamics
          ISM: clouds}
\end{abstract}

\firstsection % if your document starts with a section,
              % remove some space above using this command.
\vspace{-.66em}\section{Introduction}
Early galaxies have higher molecular gas fractions, star formation rate, and smaller sizes 
than present-day galaxies \citep[e.g.,][]{Bouwens11a, Decarli16a, Decarli17a, Leung19c}. 
As such, they are expected to be significantly more ionized, with more intense and harder interstellar radiation fields.
Their metallicity and dust content are also expected to be lower, which 
in turn affect the thermal and chemical state of the multi-phase ISM. 
Here, we pose the question: {\it what are the physical properties of molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}

\vspace{-1.em}
\section{Cosmological Zoom-in Simulations: \ncode{Serra} }

The simulations used are briefly summarized here (see \citealt{Pallottini17a, Pallottini17b} for details).
\ncode{Serra} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques, 
covering a comoving box of 20\,Mpc $h$\pmOne in size and zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$. 
The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, 
and is spatially refined with the finest cell size of $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., comparable to the size of local giant molecular clouds.
Our model includes a non-equilibrium chemical network \citep{Grassi14a,Bovino16a}, where 
abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme \citep{Pallottini17a}.
The main zoom galaxy (\flower) is a Lyman-break galaxy at $z\simeq$\,6, with a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.

\vspace{-1.2em}
\section{Physical Properties and Stability of $z\sim$\,6 Molecular Gas}

The typical size and mass of MCCs are $R\simeq\,50$\,pc and $M_{\rm cl}\simeq10^{6.5}$\,\Msun, comparable to massive molecular structures observed 
in nearby star-forming and starburst galaxies \citep[e.g.,][]{Leroy15a}.
MCCs are highly supersonic with an average Mach number of $\bar{\mathcal{M}}\simeq6$.
Their velocity dispersion and gas surface density are systematically higher than Milky Way clouds, but comparable to $z$\ssim2 starburst galaxies
\citep[e.g.,][]{Swinbank11a}.
High pressure ($\bar{P}\simeq10^{7.6}$\,K\,\cc) MCCs are found throughout the disk of \flower and
result from extra-planar flows and high velocity accretion/SN-driven outflows.

We also perform virial analysis, as motivated by \obs, to assess the stability of MCCs. 
Virial parameter is lowest for MCCs in the densest regions, some of which are located in regions with 
Toomre $Q_{\rm eff}\lesssim1$. These MCCs are unstable against collapse, where \SF is expected to take place within 
their gas {\it clumps} and {\it cores} on scales $\lesssim$\,40\,pc as energy quickly dissipates.

% Toomre:
Contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations 
($Q_{\rm eff}$), especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also non-negligible. This illustrates the importance of accounting for both effects when examining the stability of molecular gas structures in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
%

\vspace{-1.2em}
\section{Summary and Outlook}

We study the origin and dynamical properties of MCCs in prototypical galaxies at the EoR in numerical simulations to provide a framework within which upcoming \obs can be compared against to aid in the interpretation. 
% MCCs in the first galaxies are highly turbulent due to strong stellar feedback and violent cold gas accretion from the IGM --- 
Details of our findings are reported in \citet{Leung19c}. 
Concerning the topic of this symposium, our results imply that spatially resolution better than $\simeq$40\,pc are needed to examine 
the truly star-forming structures, and thus, \SF in the first galaxies. Such resolution is within reach of ALMA and 
will complement studies of stellar population in the first galaxies using {\it JWST}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                            Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.em}
\begin{thebibliography}{}

\bibitem[{{Bouwens} {et~al.}(2011){Bouwens}, {Illingworth}, {Labbe}, {Oesch},
  {Trenti}, {Carollo}, {van Dokkum}, {Franx}, {Stiavelli}, {Gonz{\'a}lez},
  {Magee}, \& {Bradley}}]{Bouwens11a}
{Bouwens}, R.~J., {Illingworth}, G.~D., {Labbe}, I., {et~al.} 2011,
  \href{http://dx.doi.org/10.1038/nature09717}{\JournalTitle{\nat}, 469, 504}

\bibitem[{{Bovino} {et~al.}(2016){Bovino}, {Grassi}, {Capelo}, {Schleicher}, \&
  {Banerjee}}]{Bovino16a}
{Bovino}, S., {Grassi}, T., {Capelo}, P.~R., {Schleicher}, D.~R.~G., \&
  {Banerjee}, R. 2016,
  \href{http://dx.doi.org/10.1051/0004-6361/201628158}{\JournalTitle{\aap},
  590, A15}

\bibitem[{{Decarli} {et~al.}(2016){Decarli}, {Walter}, {Aravena}, {Carilli},
  {Bouwens}, {da Cunha}, {Daddi}, {Ivison}, {Popping}, {Riechers}, {Smail},
  {Swinbank}, {Weiss}, {Anguita}, {Assef}, {Bauer}, {Bell}, {Bertoldi},
  {Chapman}, {Colina}, {Cortes}, {Cox}, {Dickinson}, {Elbaz},
  {G{\'o}nzalez-L{\'o}pez}, {Ibar}, {Infante}, {Hodge}, {Karim}, {Le Fevre},
  {Magnelli}, {Neri}, {Oesch}, {Ota}, {Rix}, {Sargent}, {Sheth}, {van der Wel},
  {van der Werf}, \& {Wagg}}]{Decarli16a}
{Decarli}, R., {Walter}, F., {Aravena}, M., {et~al.} 2016,
  \href{http://dx.doi.org/10.3847/1538-4357/833/1/69}{\JournalTitle{\apj}, 833,
  69}

  \bibitem[{{Decarli} {et~al.}(2017){Decarli}, {Walter}, {Venemans},
  {Ba{\~n}ados}, {Bertoldi}, {Carilli}, {Fan}, {Farina}, {Mazzucchelli},
  {Riechers}, {Rix}, {Strauss}, {Wang}, \& {Yang}}]{Decarli17a}
{Decarli}, R., {Walter}, F., {Venemans}, B.~P., {et~al.} 2017,
  \href{http://dx.doi.org/10.1038/nature22358}{\JournalTitle{\nat}, 545, 457}

 \bibitem[{{Grassi} {et~al.}(2014){Grassi}, {Bovino}, {Schleicher}, {Prieto},
  {Seifried}, {Simoncini}, \& {Gianturco}}]{Grassi14a}
{Grassi}, T., {Bovino}, S., {Schleicher}, D.~R.~G., {et~al.} 2014,
  \href{http://dx.doi.org/10.1093/mnras/stu114}{\JournalTitle{\mnras}, 439,
  2386}

  \bibitem[{{Leroy} {et~al.}(2015){Leroy}, {Bolatto}, {Ostriker}, {Rosolowsky},
  {Walter}, {Warren}, {Donovan Meyer}, {Hodge}, {Meier}, {Ott}, {Sandstrom},
  {Schruba}, {Veilleux}, \& {Zwaan}}]{Leroy15a}
{Leroy}, A.~K., {Bolatto}, A.~D., {Ostriker}, E.~C., {et~al.} 2015,
  \href{http://dx.doi.org/10.1088/0004-637X/801/1/25}{\JournalTitle{\apj}, 801,
  25}

\bibitem[{{Leung} {et~al.}(2019){Leung}, {Riechers}, {Baker}, {Clements},
  {Cooray}, {Hayward}, {Ivison}, {Neri}, {Omont}, {P{\'e}rez-Fournon}, {Scott},
  \& {Wardlow}}]{Leung19a}
{Leung}, T.~K.~D., {Riechers}, D.~A., {Baker}, A.~J., {et~al.} 2019a,
  \href{http://dx.doi.org/10.3847/1538-4357/aaf860}{\JournalTitle{\apj}, 871,
  85}

\bibitem[{Leung} {et~al.}(2019c)]{Leung19c}      % \elal\ ()
{Leung, T.~K.~D., Pallottini, A., Ferrara, A., \& Mac Low, M.-M.} 2019c,
\href{http://dx.doi.org/0}{\JournalTitle{\apj}}, Submitted

\bibitem[{{Pallottini} {et~al.}(2017{\natexlab{b}}){Pallottini}, {Ferrara},
  {Gallerani}, {Vallini}, {Maiolino}, \& {Salvadori}}]{Pallottini17a}
{Pallottini}, A., {Ferrara}, A., {Gallerani}, S., {et~al.} 2017{\natexlab{b}},
  \href{http://dx.doi.org/10.1093/mnras/stw2847}{\JournalTitle{\mnras}, 465,
  2540}

\bibitem[{{Pallottini} {et~al.}(2017{\natexlab{a}}){Pallottini}, {Ferrara},
  {Bovino}, {Vallini}, {Gallerani}, {Maiolino}, \& {Salvadori}}]{Pallottini17b}
{Pallottini}, A., {Ferrara}, A., {Bovino}, S., {et~al.} 2017{\natexlab{a}},
  \href{http://dx.doi.org/10.1093/mnras/stx1792}{\JournalTitle{\mnras}, 471,
  4128}

\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011,
  \href{http://dx.doi.org/10.1088/0004-637X/742/1/11}{\JournalTitle{\apj}, 742,
  11}

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                            Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{acknowledgements}
%TKDL acknowledges financial support from the Simons Foundation and the IAU. 
%\end{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                            Discussion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{discussion}
%\discuss{person}{blah}
%\discuss{person}{Indeed}
%\end{discussion}

\end{document}

### 2019-07-05 WRITEUP/ms.tex
cleanup for submission
line trimming

@@
 % --------------------------------------------
-%mm2 edits of 3 Jul 19 marked like this M-MML
-% AP: I have some compatibility issues with the new style (i.e. \section does not work)
-\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
+\documentclass[iop]{emulateapj}
+%\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
 
-%\def\altomega{r_{\rm disk}}
 \def\altomega{\varpi}
-
 \usepackage{amsmath}
-
-\usepackage{comment}
 
@@
 
-\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
+\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA;}
 \email{tleung@astro.cornell.edu}
@@
 %
-Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
-and the Next Generation Very Large Array.
-%mm2 (ngVLA).
+Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array and the Next Generation Very Large Array.
 \end{abstract}
@@
 This gas fuels \SF and feeds central supermassive black holes.
-Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
-part of this material.
+Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some part of this material.
 %
@@
 \end{equation}
-where $\ddot{\mathcal{I}}$ is the second time derivative of the
-Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
-the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and
-$\mathcal{W}$ is the gravitational energy.
+where $\ddot{\mathcal{I}}$ is the second time derivative of the Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and $\mathcal{W}$ is the gravitational energy.
 %
@@
 %
-On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases
-$Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
-As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.  % 0.67 * 2
+On the other hand, including the contribution of the stellar component promotes gravitational instability, and thus increases $Q_{\rm crit}$, more-so if the stars have low velocity dispersion.
+As a rule of thumb, $Q_{\rm crit}\eq1.34$ for $Q_{\rm gas}$\eq$Q_\star$.
 
@@
 %
-% Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16})
-% \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}.
-%
 Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
@@
 
-If constant column density (Larson's third relation) were truly a
-fundamental property of molecular clouds,
-and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that
-mass surface density $\Sigma$.
-The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of
-molecular clouds in agreement with \citet{Heyer09a}.
-Previous studies suggest that the observed mass-size relation of molecular clouds
-is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of
-column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
+If constant column density (Larson's third relation) were truly a fundamental property of molecular clouds, and if virial equilibrium were a universal property of molecular clouds with negligible surface pressure, one would expect a single point in the $\sigma_{\rm gas}^2/R$--$\Sigma$ relation at that mass surface density $\Sigma$.
+The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen here suggests that column density is not a fundamental property of molecular clouds in agreement with \citet{Heyer09a}.
+%
+Previous studies suggest that the observed mass-size relation of molecular clouds is solely a result of $\rho\propto M R^{-3}$ and may be an artifact of the limited range of column densities a specific molecular line tracer is sensitive to \citep[see e.g.,][]{Ballesteros02a, Ballesteros11a}.
 
@@
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
-are probably limited by the spatial resolution.
+However, the sizes of MCCs are almost a factor of two smaller.
+This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
+%
 The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
@@
 %
-AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
-H2020/740120.
-% mm
-M-MML acknowledges partial support by the NSF through award
-AST18-15461, and hospitality from the Insitute for Theoretical
-Astrophysics at the University of Heidleberg.
+AF acknowledges support from the ERC Advanced Grant INTERSTELLAR H2020/740120.
+%
+M-MML acknowledges partial support by the NSF through award AST18-15461, and hospitality from the Insitute for Theoretical Astrophysics at the University of Heidleberg.
 %
@@
 %
+The Flatiron Institute is funded by the Simons Foundation.
 This research has made use of NASA's Astrophysics Data System Bibliographic Services.
 %
-\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and yt \citep{Smith09a,Turk11a}}
+\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PYMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{YT} \citep{Smith09a,Turk11a}}
 

### 2020-01-27 WRITEUP/ms_referee.tex
init

--- 2019-07-05 WRITEUP/arxiv1/ms.tex
@@
 % --------------------------------------------
-\documentclass[iop]{emulateapj}
+\IfFileExists{emulateapjlegacy.cls}{\documentclass[iop]{emulateapjlegacy}}{\documentclass[iop]{emulateapj}}
 
@@
 \usepackage{amsmath}
-\usepackage{xcolor}
 
 \input{preamble}
-\slugcomment{Submitted to ApJ.}
+\slugcomment{To be Submitted.}
 
@@
 \makeatother
+
+\usepackage{xcolor}
+\definecolor{apcolor}{HTML}{b3003b}
+\definecolor{dlcolor}{HTML}{FF7F00}
+\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
+\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
+\definecolor{afcolor}{HTML}{b3443c}
+\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
+\definecolor{mmcolor}{HTML}{006600}
+\newcommand{\MM}[1]{({\bf \color{mmcolor} MM: #1})}
+
+% it can be instead included as
+% \graphicspath{{Fig/}}
+% so that plots are automatically searched for in the given path
+\def\figpath{./Fig}
 
@@
 Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM).
+
 Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
-%
 Even in the local Universe, where detailed \obs can be made, variations in molecular cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
@@
 At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
+{\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures, 
+and morphologies of galaxies out to the EoR and their importance on providing 
+the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}. 
+Compared to the zoom-in galaxies presented in these work, 
+the simulation used here focuses on an LBG galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite 
+(see \citealt{Pallottini19a} for a detailed comparison between these cosmological zoom-in simulations).
+}
+
 %
@@
 \end{equation}
-where $M_\star$ is the stellar mass within the MCC volume.
+where $M_\star$ is the stellar mass {\bf enclosed} within the MCC volume.
 
@@
 In our stability analysis, we account for the combined effect of gas and stars \citep[derived exactly by][]{Rafikov01a}, and for the non-negligible disk thickness.
-This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a}.
+This is done by adopting an approximation for an effective two-component $Q_{\rm eff}$ parameter \citep[i.e.,][see also \citealt{Inoue16a}]{Romeo11a, Romeo13a}.
 %
@@
 		\begin{array}{lccr}
-			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\ [1.25em]
-			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}        & & & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r
-\\
+			{\displaystyle 0.8 + 0.7\left(\frac{\sigma_{z}}{\sigma_{r}}\right)}      && & \mbox{if\ } \sigma_z \gtrsim 0.5 \times \sigma_r \\ [1.25em]
+			{\displaystyle 1 + 0.6\left(\frac{\sigma_{z}}{\sigma_{r}}\right)^2}        & & & \mbox{if\ } \sigma_z \lesssim 0.5 \times \sigma_r \\
 		\end{array}
@@
 The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size.
-The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$.
+The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$
+at {\bf $z$\eq6}.
 The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
@@
 The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
-%
-The models include a non-equilibrium chemical network following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}.
-Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
+
+The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, 
+and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium 
+formation of molecular hydrogen scheme described by \citet{Pallottini17a}. 
+{\bf In the simulation, the UV radiation field is assumed to be uniform spatially. 
+Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription, 
+while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as 
+part of \ncode{Krome}. % (see \citealt{Bovino16a}). 
+We do not assume a clumping factor in the chemistry solver (cf. \citet[][]{Lupi20a}, i.e., $C_\rho$\eq1).
+In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
+% (Section 2.1.1 of \citealt{Pallottini17b})}.
 
@@
 The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following.
-\flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
-\flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
+\flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
+{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+\flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
 %
@@
 The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
+{\bf The stellar-to-halo mass ratio of \flower ($M_\star/M_{\rm DM}$\eq0.07) is 
+between?? those from abundance matching reported by \citet{Moster13a},
+but higher than those reported based on other zoom-in simulations at similar redshifts 
+(e.g., \citealt{Ceverino17a, Katz17a}, and \citealt{Behroozi19a}). This can result from different feedback implementations.
+}
 
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{sfh.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
 \caption{
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{hist_test_16.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
 \caption{Normalized distribution of molecular gas density of \flower during the accreting phase shown in \Fig{SFH}{\em
@@
  \centering
-  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{combined.pdf}
+  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
 \caption{
@@
 The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
-%
+%!TEX encoding = UTF-8 Unicode
 Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
@@
 \end{equation}
-where the sum is done for the cells indexed by $i$ composing the MCC. We can use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
+where the sum is done for the cells indexed by $i$ composing the MCC. 
+We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
 %
-The bulk velocity dispersion is
+%The bulk velocity dispersion is
+%\begin{equation}
+%\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
+%\end{equation}
+{\bf The bulk velocity dispersion is 
 \begin{equation}
-\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
+\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,,
 \end{equation}
+where \Eq{defineaverage} is applied to each velocity component.
+}
 %
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{minmaxNcut_basicDistributions.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
 \caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
@@
 
-We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
+We start by considering the distributions of MCC {\bf total gas mass ($M_{\rm gas}$), radius ($R$), and gas mass fraction ($f_{\rm gas}$)}, 
+which we define as
 \begin{equation}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{cloud-mass_fgas.pdf}
+\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
 \caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar).
@@
 This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
-The velocity dispersion of such a structure is dominated by bulk rotational motion, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The velocity dispersion of such a structure is dominated by
+{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity (see \citealt{Kohandel19a} for kinematical analysis of \flower).}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{ss16-28-veldisp.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-veldisp.pdf}
 \caption{Gas velocity dispersions resulting from bulk versus turbulent motions for molecular structures
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{3by2_clumpProp_ss16-ss22.png}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
 \caption{
@@
 Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
-Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
+Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phase have lower $\alpha_{\rm vir}$ than in the accreting phase.
 \label{fig:larsons_single}}
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{3by2_clumpProp_allss}
+\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
 \caption{Same as \Fig{larsons_single}, except star symbols are showing molecular gas structures identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages (see colorbar on the right).
@@
 The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter comparable to some of the molecular structures
-observed in the Milky Way, though the MCCs are more massive.
+On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
+of the Milky Way but higher than what is typically observed in the Milky Way}, though the MCCs are more massive.
+{\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
 
@@
 
-At the highest density cut, only the densest gas structures are identified.
+At the highest density cut, only the densest gas structures are identified\footnote{\bf{In the simulation, the 
+densest molecular regions reaches gas density of $n_{\rm gas}$\ssim10$^3$\,\cc, which is comparable to the critical density 
+of low-$J$ CO lines (see e.g., \citealt{Vallini18a}); however, we emphasize that we do not resolve the internal structure of molecular clouds
+at the resolution of the simulation.}}.
 The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
@@
 
-The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{{ss16_toomre_combined_2by2_0_2.0}.pdf}
+\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
 \caption{
@@
 \centering
-\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{{ss16_toomre_combined_3by1_0_1.2}.pdf}
+\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
 \caption{
@@
 This can be understood since stars in \flower dominate the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
-In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$ of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
+% In fact, this is also illustrated by the differences seen between $\alpha_{\rm vir}$ and $\alpha_{\rm vir, tot}$ of the most massive structure (i.e., the gas disk of \flower; see \Fig{larsons_single}).
 Similarly, contribution from the thickness of the disk is important in \flower since its disk is warped and has a scale height-to-radius ratio of $h/r_{\rm gal}$\ssim150\,pc/1\,kpc\,$\simeq$\,0.15.
@@
 The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
-
+%
 The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}.

### 2020-01-28 WRITEUP/ms_referee.tex
re-circulate

@@
 The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
-{\bf The stellar-to-halo mass ratio of \flower ($M_\star/M_{\rm DM}$\eq0.07) is 
-between?? those from abundance matching reported by \citet{Moster13a},
-but higher than those reported based on other zoom-in simulations at similar redshifts 
-(e.g., \citealt{Ceverino17a, Katz17a}, and \citealt{Behroozi19a}). This can result from different feedback implementations.
+{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}$\eq0.07.
+Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}).
+The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
 }
@@
 The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
-Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
+Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MCCs are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
+This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures.
 %
-In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}.
-On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}.
+{\bf While MCCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MCCs in the local merger-driven ULIRGs}
+are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}).
+{\bf As shown
+by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MCCS of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows.
 The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2.
@@
 \caption{
-Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower.
+Toomre $Q$ maps derived from the {\bf central region} of \flower.
 Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively.
@@
 %
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
+Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in {\bf this} relatively evolved and enriched systems at high redshifts.
 \label{fig:Qeff}}

### 2020-01-31 WRITEUP/ms_referee.tex
AP minor comments

@@
 while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as 
-part of \ncode{Krome}. % (see \citealt{Bovino16a}). 
-We do not assume a clumping factor in the chemistry solver (cf. \citet[][]{Lupi20a}, i.e., $C_\rho$\eq1).
+part of the \ncode{Krome} network. % (see \citealt{Bovino16a}). 
+We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
 In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
@@
 The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
-{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}$\eq0.07.
+{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
 Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}).
@@
 On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
-of the Milky Way but higher than what is typically observed in the Milky Way}, though the MCCs are more massive.
-{\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
+of the Milky Way but higher than its average value}, though the MCCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
 
@@
 
-The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure in these high density regions.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.

### 2020-01-31 WRITEUP/ms_referee.tex
minor notation

@@
 The velocity dispersion of such a structure is dominated by
-{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity (see \citealt{Kohandel19a} for kinematical analysis of \flower).}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).

### 2020-02-07 WRITEUP/ms_referee.tex
final edits

@@
 \citestyle{aa}
-\shorttitle{Dynamical Properties of MCCs in Galaxies at the EoR}
+\shorttitle{Dynamical Properties of MGCs in Galaxies at the EoR}
 \shortauthors{Leung et al.}
@@
 \begin{document}
-\title{Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization}
+\title{Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization}
 
@@
 \begin{abstract}
-We study the properties of molecular cloud complexes (MCCs) at the epoch of reionization using cosmological zoom-in simulations.
-We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
+We study the properties of molecular-forming gas clumps (MGCs) at the epoch of reionization using cosmological zoom-in simulations.
+We identify MGCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
 %
 We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
-In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies.
-MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
+In \flower, the typical MGC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies.
+MGCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
 %
-In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs.
-We find that MCCs are globally stable in the main disk of \flower.
-Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
+In addition, we perform stability analysis to understand the origin and dynamical properties of MGCs.
+We find that MGCs are globally stable in the main disk of \flower.
+Densest regions where \SF is expected to take place in {\bf clouds} and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
 %
@@
 Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}.
-Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of molecular cloud complexes (MCCs) that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
-Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
+Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of
+{\bf dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{{\bf Note that by clumps, 
+we refer to kiloparsec-scale gas concentrations in galaxies, rather than molecular gas concentrations small than molecular clouds 
+and containing cores.}}; 
+MGCs)} that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+Some theoretical works argue that the migration of such giant massive clumps through disks is largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
 
@@
 Even in the local Universe, where detailed \obs can be made, variations in molecular cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).
-Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of molecular cloud structures in early galaxies, and how do they differ from those found in local \galpop?}
+Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of
+MGCs in early galaxies, and how do they differ from those found in local \galpop?}
 %
@@
 {\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
-and morphologies of galaxies out to the EoR and their importance on providing
+and morphologies of galaxies out to the epoch of reionization (EoR) and their importance for providing
 the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}.
-Compared to the zoom-in galaxies presented in these work,
-the simulation used here focuses on an LBG galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
-(see \citealt{Pallottini19a} for a detailed comparison between these cosmological zoom-in simulations).
+Compared to the zoom-in galaxies presented in these works,
+the simulation used here focuses on a Lyman-break galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
+(see \citealt{Pallottini19a} for a comparison between these zoom-in simulations).
+Most notably, we include a non-equilibrium thermo-chemical network to follow the formation of H$_2$, which is 
+crucial to examining the properties of MGCs.
 }
@@
 %
-On the theoretical side, a schematic investigation by \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist of many smaller clumps formed by gravitational instability, a hierarchical structure that persists in an idealized disk model by \citet{Behrendt19}.
+On the theoretical side, a schematic investigation by \citet{Behrendt16} revealed that kiloparsec-scale clumps likely consist of many smaller clouds formed by gravitational instability, a hierarchical structure that persists in an idealized disk model by \citet{Behrendt19}.
 
-To understand the physical properties of MCCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MCCs in prototypical (i.e., $L^*$) galaxies in the epoch of reionization (EoR).
+To understand the physical properties of MGCs in early galaxies, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming MGCs in prototypical (i.e., $L^*$) galaxies in the EoR.
 
@@
 In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower).
-In \Sec{eqn}, we describe the method used to identify MCCs, and present the formalism within which we interpret the results.
-In \Sec{results}, we present the results and characteristic properties of the MCCs.
+In \Sec{eqn}, we describe the method used to identify MGCs, and present the formalism within which we interpret the results.
+In \Sec{results}, we present the results and characteristic properties of the MGCs.
 We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
@@
 \section{Physical Background}\label{sec:Back}
-We begin by introducing some empirical relations commonly mentioned in observational studies of molecular clouds in the literature, as well as describing the gravitational instability of galactic disks, which might be driving MCC formation.
+We begin by introducing some empirical relations commonly mentioned in observational studies of molecular clouds in the literature, as well as describing the gravitational instability of galactic disks, which might be driving MGC formation.
 These concepts will be used in the subsequent analysis of our simulations.
@@
 Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
-the gas, $\mathcal{T}_{\rm ext}$ is external pressure support, and
+the gas {\bf (including thermal, turbulent, and bulk motions)}, $\mathcal{T}_{\rm ext}$ is external pressure support, and
 $\mathcal{W}$ is the gravitational energy.
@@
 \end{equation}
-where $M_\star$ is the stellar mass {\bf enclosed} within the MCC volume.
+where $M_\star$ is the stellar mass {\bf enclosed} within the MGC volume.
 
@@
 Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
-while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as
+while the formation rate on dust grain is computed following \citet{Jura75a}. Photo-dissociation via Lyman-Werner photons is included as
 part of the \ncode{Krome} network. % (see \citealt{Bovino16a}).
@@
 {\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
-Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}).
+Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun (see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}).
 The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
@@
 
-In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MCC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
+In \Sec{dist}, we show the importance of rotation support from large-scale motions in the MGC dynamics by comparing their properties in the disturbed phase of \flower and in the disk-like ordered phase.
 %
@@
 These phases correspond to (a) an intensely accreting phase and (b) a starburst phase (\Fig{SFH}).
-We are interested in determining whether MCC properties are sensitive to these different dynamical conditions.
-For completeness, we also show relationships of MCC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).
+We are interested in determining whether MGC properties are sensitive to these different dynamical conditions.
+For completeness, we also show relationships of MGC properties examined for other evolutionary stages traced in the simulation (see \Sec{ncut}).
 
-\section{Molecular Cloud Complexes}\label{sec:eqn}
+\section{Molecular-forming Gas Clumps}\label{sec:eqn}
 
@@
 \caption{
-Examples of MCCs identified in \flower by our clump finder.
+Examples of MGCs identified in \flower by our clump finder.
 %
@@
 Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
-\label{fig:MCC}
+\label{fig:MGC}
 }
@@
 %
-In each evolutionary stage, we identify MCCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MCCs are selected at $n_{\rm cut} \leq n_{\rm H2}$.
+In each evolutionary stage, we identify MGCs by applying density cuts to the {\em H$_2$ density} distribution, i.e., MGCs are selected at $n_{\rm cut} \leq n_{\rm H2}$.
 We select 10 equally-spaced cuts in H$_2$ density in log scale: ${(n_{\rm cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 18.96, 31.62]$.
-Note that with these choices we are including MCCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
+Note that with these choices we are including MGCs that are not fully molecular ($n = 0.5 n_{\rm H2}$).
 
-To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MCC}).
+To visually display the clump finding procedure, we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps (\Fig{MGC}).
 Since the molecular structures are identified in the 3D H$_2$ density field, they can appear as overlapping structures depending on the viewing angle; thus we also plot them in different projections so that the identification can be more easily appreciated.
@@
 
-\subsection{MCC Properties} \label{sec:distribution}
+\subsection{MGC Properties} \label{sec:distribution}
 
@@
 
-The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$.
+The mass of an MGC is calculated from the uniformly-gridded 3D density field, integrating over the MGC volume $V$.
 The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
 %
-The full velocity dispersion of MCCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
+The full velocity dispersion of MGCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
 \begin{equation}
@@
 %
-In \obs of MCCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
-Therefore, when calculating the global quantities of MCCs, we always perform a mass-weighting.
+In \obs of MGCs, the linewidth contribution of dense gas exceeds that from the diffuse gas.
+Therefore, when calculating the global quantities of MGCs, we always perform a mass-weighting.
 Since we operate on data on a uni-grid, this is equivalent to density averaged quantities.
-In general, for the quantity $x$ in a MCC we write
+In general, for the quantity $x$ in a MGC we write
 \begin{equation}\label{eqn:defineaverage}
@@
 \end{equation}
-where the sum is done for the cells indexed by $i$ composing the MCC.
+where the sum is done for the cells indexed by $i$ composing the MGC.
 We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
@@
 
-\subsection{MCC Basic Properties} \label{sec:dist}
+\subsection{MGC Basic Properties} \label{sec:dist}
 \begin{figure*}[htbp]
@@
 \includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
-\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
-Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
+\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MGCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation.
+Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MGCs are identified at higher $n_{\rm cut}$.
 \label{fig:dist}}
@@
 
-We start by considering the distributions of MCC {\bf total gas mass ($M_{\rm gas}$), radius ($R$), and gas mass fraction ($f_{\rm gas}$)},
-which we define as
+We start by considering the distributions of MGC {\bf total gas mass $M_{\rm gas}$, radius $R$, and gas mass fraction}
 \begin{equation}
@@
 We show in \Fig{dist} the distributions from the combination of the three considered evolution stages.
-We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
-However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
+We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MGC mass of the order of 10$^{5.5}$\,\Msun for the densest structure.
+However, not all evolutionary stages considered have at least one MGC at this highest density threshold, so we consider MGCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
 %
-Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
+Overall, the mass of all MGCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
 whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.
@@
 \includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
-\caption{Cloud mass and gas mass ratio of MCCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar).
+\caption{Cloud mass and gas mass ratio of MGCs identified in the accreting phase of \flower using different $n_{\rm cut}$ (see colorbar).
 The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
@@
 Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower.
-These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper.
+These disk/arm structures are excluded in the discussion of MGC dynamics in the remainder of this paper.
 \label{fig:stellarRatio16}}
@@
 
-The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$.
+The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MGC}), which is identified as a single component at low $n_{\rm cut}$.
 This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$.
 The velocity dispersion of such a structure is dominated by
-{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
-The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
+{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MGCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MGC}).
 %
-Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
+Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MGCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MGCs.
 %
-For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.
+For these reasons, the most massive MGCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.
 
-Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
+Considering only the MGCs identified at the highest density threshold, the mass of MGCs is $\simeq10^{6.5}$\,\Msun.
 We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
@@
 see \citet{grisdale:2017,grisdale:2019} for the importance of feedback in shaping the properties of clouds forming in local simulated galaxies.
-That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
+That said, the similar mass range found in MGCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).
 
@@
 Top and bottom panels show structures identified in the accreting phase and the quiescent phase, respectively.
-The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MCC}).
+The accreting phase of \flower displays a more disturbed morphology compared to the quiescent phase, which displays a disk-like morphology (see \Fig{MGC}).
 %
@@
 %
-Velocity dispersion from turbulent motions dominates over bulk motions for MCCs in the accreting phase, whereas
-$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MCCs in the quiescent disk-like phase.
+Velocity dispersion from turbulent motions dominates over bulk motions for MGCs in the accreting phase, whereas
+$\sigma_{\rm bulk}$ is comparable to $\sigma_{\rm NT}$ for some MGCs in the quiescent disk-like phase.
 \label{fig:vv}}
@@
 
-The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
+The local sound speed of all MGCs identified is typically much smaller than their non-thermal (turbulent) velocities,
 as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$.
-In particular, the average Mach number for MCCs identified at the highest density threshold is $\bar{\mathcal{M}}\,\simeq6$.
+In particular, the average Mach number for MGCs identified at the highest density threshold is $\bar{\mathcal{M}}\,\simeq6$.
 This is consistent with the analysis done in \citet{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
@@
 \caption{
-Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
+Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MGCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
 %
@@
 Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a,
-Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phase have lower $\alpha_{\rm vir}$ than in the accreting phase.
+Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MGCs in the starburst phase have lower $\alpha_{\rm vir}$ than in the accreting phase.
 \label{fig:larsons_single}}
@@
 %
-The biggest MCCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular disk and arms of \flower, and are broken down into smaller MCCs at higher density thresholds (see top right panel).
+The biggest MGCs identified at lowest density thresholds, occupying the top right corner of the top left panel, correspond to the molecular disk and arms of \flower, and are broken down into smaller MGCs at higher density thresholds (see top right panel).
 %
-Notably less MCCs in the right panels owing to the fact that only few MCCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
+Notably less MGCs in the right panels owing to the fact that only few MGCs with neighboring cells reaching high H$_2$ densities of $n_{\rm cut}\simeq$19\,\cc.
 The high velocity dispersion in \flower is largely driven by non-thermal pressure (see \Fig{vv}).
@@
 
-Here, we focus on the MCC properties in the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
+Here, we focus on the MGC properties in the two most extreme evolutionary stages of \flower\ --- the accreting and starburst phases (see \Sec{sfh}).
 These properties are plotted in \Fig{larsons_single} together with observational results of nearby and $z$\,$\simeq$2 molecular structures for comparison.
 
-During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
+During the accreting phase, MGCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc).
 These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.
 
-While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
+While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MGCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
 %
-The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}).
+The biggest MGC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MGC} and \Sec{distribution}).
 The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
-of the Milky Way but higher than its average value}, though the MCCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
+On the other hand, the MGCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MGCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
+of the Milky Way but higher than its average value}, though the MGCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
 
 % PVE
-Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MCCs in the accreting phase of \flower in the bottom left panels of \Fig{larsons_single}.
+Motivated by observational studies, we also plot the $\sigma_{\rm gas}^2/R$ ratio and gas surface density of MGCs in the accreting phase of \flower in the bottom left panels of \Fig{larsons_single}.
 In the same plot, we show those observed in the Galactic Ring Survey (GRS) of the Milky Way \citep{Heyer09a} for comparison.
 Dashed lines in the figure show the loci along which the annotated external pressures are needed for any molecular clouds in equilibrium to have certain linewidths for a given set of surface densities (see \Sec{PVE}).
-At a given gas surface density, MCCs display a range of $\sigma_{\rm gas}^2/R$.
+At a given gas surface density, MGCs display a range of $\sigma_{\rm gas}^2/R$.
 Such variation in $\sigma_{\rm gas}^2/R$ is observed in GMCs in the central and outer part of the Milky Way \citep{Oka01a, Heyer09a}.
@@
 % Starburst
-In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
+In the starburst phase, MGCs have velocity dispersion and sizes similar to those in the accreting phase; however, MGCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
 %
-That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
-The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
+That is, MGCs in the starburst phase are more susceptible to collapse, as expected.
+The gas surface density of MGCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
 % LMC: 0.01 g cm^-2
@@
 
-The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
-As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
+The sizes of MGCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
+As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MGCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MGCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
 %
-Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}).
-At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
+Second, excluding such structure, some MGCs are further broken down into smaller MGCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}).
+At the resolution limit of our simulation, most MGCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
 %
-The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
-This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
+The gas velocity dispersion $\sigma_{\rm gas}$ of MGCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
+This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MGCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.
 
@@
 at the resolution of the simulation.}}.
-The virial parameter of these MCCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
+The virial parameter of these MGCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
 
@@
 
-\subsection{Synthetic vs Observed MCC Properties} \label{sec:diss1}
+\subsection{Synthetic vs Observed MGC Properties} \label{sec:diss1}
 
-In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
+In this section, we compare the observable quantities of MGCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
 
-The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
+The velocity dispersion of MGCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
 spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
-However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
+However, the sizes of MGCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
 are probably limited by the spatial resolution.
-The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
-Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
+The velocity dispersions of some MGCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$.
+Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MGCs; \Sec{distribution}).
 In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
@@
 
-The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure in these high density regions.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure in these high density regions.}} of MGCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
-In our simulated galaxy, the high pressure MCCs are found throughout the disk.
+In our simulated galaxy, the high pressure MGCs are found throughout the disk.
 This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures.
 %
-{\bf While MCCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MCCs in the local merger-driven ULIRGs}
+{\bf While MGCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MGCs in the local merger-driven ULIRGs}
 are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}).
 {\bf As shown
-by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MCCS of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows.
-The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2.
+by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MGCs of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows.
+The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MGCs observed in gas-rich star-forming galaxies at $z$\ssim2.
 For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.
 
-We do not find any major quantitative differences (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr.
-However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
+We do not find any major quantitative differences (see \Fig{larsons_single}) in the MGCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr.
+However, MGCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase.
 This is expected for \SF to proceed.
 
-\subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}
+\subsection{Toomre Parameter and Stability of MGCs} \label{sec:Qeff}
 
@@
 Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
-Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
+Center of mass positions of MGCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
 \label{fig:sigma}}
@@
 %
-Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
-Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
+Positions of MGCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
+Some MGCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
 %
-Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in {\bf this} relatively evolved and enriched systems at high redshifts.
+The close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that the stellar component plays an important role in governing the stability of MGCs against $m=0$  perturbations in {\bf this} relatively evolved and enriched system at high redshifts.
 \label{fig:Qeff}}
@@
 We define Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ in \Sec{Q}.
-Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MCCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
+Maps of the corresponding Toomre $Q$ are shown in \Fig{Qeff} (see also \Fig{h2density} for example of MGCs identified in this evolutionary stage of \flower using different $n_{\rm cut}$).
 
-Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MCCs against perturbations.
+Close resemblance of the $Q_{\rm eff}$ and $Q_{\star}$ maps indicates that contributions from the stellar component play an important role in governing the stability of the MGCs against perturbations.
 This can be understood since stars in \flower dominate the central part of the galaxy in mass, so their gravitational potential provides a non-negligible contribution to the instability.
@@
 %
-That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
-Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MCCs are consistent with $Q_{\rm eff} > 1$.
+That is, some MGCs are found in regions of $Q_{\rm gas}$\ssim1, which is consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable.
+Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the thickness of its disk (via $\sigma_z$, i.e., $Q_{\rm eff}$; see Equation~\ref{eqn:q_eff}), some of these MGCs are consistent with $Q_{\rm eff} > 1$.
 %
@@
 
-The large virial parameters ($\alpha_{\rm vir}>$\,2) seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
+The large virial parameters ($\alpha_{\rm vir}>$\,2) seen in some MGCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
 %
@@
 %
-Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
-On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
+Thus, the high virial parameter found for some MGCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
+On the other hand, MGCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.
 
@@
 While it is possible to obtain sensitive and high fidelity imaging that reveals their gas and dust morphology on sub-kpc scales and even smaller, such \obs remain challenging; logistically, data from multiple cycles pushing to increasing resolution and sensitivity are needed.
-As such, observational studies of MCCs on such scales are still missing in the literature.
+As such, observational studies of MGCs on such scales are still missing in the literature.
 %
-In this work, we aim to understand the origin and dynamical properties of MCCs in prototypical galaxies at the EoR in numerical simulations to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
+In this work, we aim to understand the origin and dynamical properties of MGCs in prototypical galaxies at the EoR in numerical simulations to provide a framework within which upcoming \obs can be compared against to aid in the interpretation.
 
-We study the dynamics of MCCs and their temporal evolution in \flower, a \z$\sim$\,6 prototypical galaxy obtained from the state-of-the-art cosmological zoom-in simulations \ncode{Serra}, which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by UV radiation and metal lines, and detailed stellar feedback.
+We study the dynamics of MGCs and their temporal evolution in \flower, a \z$\sim$\,6 prototypical galaxy obtained from the state-of-the-art cosmological zoom-in simulations \ncode{Serra}, which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by UV radiation and metal lines, and detailed stellar feedback.
 %
-We use a three-dimensional clump-finding algorithm to identify MCCs.
+We use a three-dimensional clump-finding algorithm to identify MGCs.
 We decompose the molecular structures into non-overlapping objects by using a set of H$_2$ density contours ($n_{\rm cut}$) at multiple evolutionary stages, in particular focusing on the accreting phase, starburst phase, and quiescent phase.
-We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, \sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.
+We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M}, \sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MGC and perform a Toomre-$Q$ stability analysis on \flower.
 
-Excluding the main structure (disk of \flower) identified, the typical mass and size of MCC is $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun and $R\simeq\,50$\,pc, respectively.
+Excluding the main structure (disk of \flower) identified, the typical mass and size of MGC is $M_{\rm gas}\simeq\,10^{6.5}$\,\Msun and $R\simeq\,50$\,pc, respectively.
 Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
-That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
+That said, the similar mass range found in MGCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
 On the other hand, the gas velocity dispersion
@@
 
-Velocity dispersion and gas surface density of MCCs of \flower are systematically higher than Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
-These MCCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
+Velocity dispersion and gas surface density of MGCs of \flower are systematically higher than Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
+These MGCs are, in fact, highly supersonic, with high Mach number of $\bar{\mathcal{M}}\simeq6$.
 Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies.
-A comparison between the bulk and non-thermal velocity dispersions of MCCs indicates that MCCs
+A comparison between the bulk and non-thermal velocity dispersions of MGCs indicates that MGCs
 are supported by turbulence motions.
 
-High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
+High pressure MGCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
 This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}.
-In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}).
-On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
-The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
+In ULIRGs, MGCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}).
+On the other hand, the highly turbulent MGCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
+The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MGCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
 %
@@
 
-We perform virial analysis, as motivated by \obs, to assess the stability of MCCs.
-On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
-Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
+We perform virial analysis, as motivated by \obs, to assess the stability of MGCs.
+On average, the virial parameter of MGCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF.
+Similarly, the virial parameter of MGCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
 % Toomre:
-Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower.
+Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MGCs against axisymmetric perturbations, especially in the central part of \flower.
 Similarly, stabilizing effect due to the thickness of its disk is also non-negligible.

### 2020-04-18 WRITEUP/ms_referee2.tex
round 2

--- 2020-02-07 WRITEUP/ms_referee.tex
@@
 {\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
-Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun (see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}).
+Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
+(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
+This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
+Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025 
+is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
+0.01--0.05 in the same mass range from direct abundance matching 
+(see the Appendix therein). 
+Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}. 
 The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
@@
 
+{\bf As seen in \Sec{dist}, the cuts used to identify the molecular structures are based on the H$_2$ number density, which ranges from 
+n$_{\rm H2}$\ssim0.1\,--\,30\,\cc. We do not explicitly use a minimum H$_2$ fraction to select the structures. 
+Among the various cuts, two physical regimes are identified, corresponding to materials in the disk/interarm material and MGCs (see Fig. 5). 
+The former with n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter with 
+n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Fig. 5 of \citet{Pallottini17b} 
+for details\footnote{In particular, with their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}). 
+Considering that $f_{\rm H2}$\eq$\rho_{\rm H2} / \rho_{\rm H,total}$\eq$\rho_{\rm H2}/(\mu \rho_{\rm gas})$\eq
+$m_{\rm H2} n_{\rm H2} / m_p~\mu~n_{\rm gas}$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$, 
+for the disk/interarm, $f_{\rm H2}$\ssim14\% and for the MCCs, $f_{\rm H2}$\ssim28\%. 
+Note that for the lowest value of the H2 cuts, this fraction might be lower; however, 
+removing regions selected with such cuts yields no qualitative change to the physical interpretation resulting from the analysis.}
+
 We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold.

### 2020-04-19 WRITEUP/ms_referee2.tex
remove boldface from 1st round

@@
 We find that MGCs are globally stable in the main disk of \flower.
-Densest regions where \SF is expected to take place in {\bf clouds} and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
+Densest regions where \SF is expected to take place in clouds and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
 %
@@
 Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of
-{\bf dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{{\bf Note that by clumps, 
+dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{Note that by clumps, 
 we refer to kiloparsec-scale gas concentrations in galaxies, rather than molecular gas concentrations small than molecular clouds 
-and containing cores.}}; 
-MGCs)} that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
+and containing cores.}; 
+MGCs) that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
 Some theoretical works argue that the migration of such giant massive clumps through disks is largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.
@@
 At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
-{\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
+High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
 and morphologies of galaxies out to the epoch of reionization (EoR) and their importance for providing
@@
 crucial to examining the properties of MGCs.
-}
 
@@
 Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
-the gas {\bf (including thermal, turbulent, and bulk motions)}, $\mathcal{T}_{\rm ext}$ is external pressure support, and
+the gas (including thermal, turbulent, and bulk motions), $\mathcal{T}_{\rm ext}$ is external pressure support, and
 $\mathcal{W}$ is the gravitational energy.
@@
 \end{equation}
-where $M_\star$ is the stellar mass {\bf enclosed} within the MGC volume.
+where $M_\star$ is the stellar mass enclosed within the MGC volume.
 
@@
 formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
-{\bf In the simulation, the UV radiation field is assumed to be uniform spatially.
+In the simulation, the UV radiation field is assumed to be uniform spatially.
 Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
@@
 We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
-In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
+In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.
 % (Section 2.1.1 of \citealt{Pallottini17b})}.
@@
 The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
-{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
+The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
 Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
-(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
+(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{{\bf The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
 This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
@@
 (see the Appendix therein). 
-Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}. 
+Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}.} 
 The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
-}
 
@@
 %\end{equation}
-{\bf The bulk velocity dispersion is
+The bulk velocity dispersion is
 \begin{equation}
@@
 where \Eq{defineaverage} is applied to each velocity component.
-}
 %
@@
 
-We start by considering the distributions of MGC {\bf total gas mass $M_{\rm gas}$, radius $R$, and gas mass fraction}
+We start by considering the distributions of MGC total gas mass $M_{\rm gas}$, radius $R$, and gas mass fraction
 \begin{equation}
@@
 The velocity dispersion of such a structure is dominated by
-{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MGCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
+the bulk motion term\footnote{The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}, as shown in \Fig{vv}, where we compare the velocity dispersions of MGCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower.
 The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MGC}).
@@
 The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability.
-On the other hand, the MGCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MGCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
-of the Milky Way but higher than its average value}, though the MGCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}
+On the other hand, the MGCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MGCs is comparable to the {\em total} virial parameter.}, with virial parameter  within the range observed in the molecular structures
+of the Milky Way but higher than its average value, though the MGCs are more massive. 
+The higher than typical MW value is linked to the higher turbulence of these systems.
 
@@
 
-At the highest density cut, only the densest gas structures are identified\footnote{\bf{In the simulation, the
+At the highest density cut, only the densest gas structures are identified\footnote{In the simulation, the
 densest molecular regions reaches gas density of $n_{\rm gas}$\ssim10$^3$\,\cc, which is comparable to the critical density
 of low-$J$ CO lines (see e.g., \citealt{Vallini18a}); however, we emphasize that we do not resolve the internal structure of molecular clouds
-at the resolution of the simulation.}}.
+at the resolution of the simulation.}.
 The virial parameter of these MGCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
@@
 
-The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure in these high density regions.}} of MGCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
+The total pressure\footnote{Non-thermal pressure dominates the total pressure in these high density regions.} of MGCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$.
 Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}.
 In our simulated galaxy, the high pressure MGCs are found throughout the disk.
-This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures.
+This difference likely stems from the different physical mechanisms giving rise to the highly turbulent nature of these molecular structures.
 %
-{\bf While MGCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MGCs in the local merger-driven ULIRGs}
-are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}).
-{\bf As shown
-by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MGCs of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows.
+While MGCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MGCs in the local merger-driven ULIRGs
+are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; see \Sec{Qeff} for Toomre-$Q$ analysis on \flower).
+As shown
+by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MGCs of \flower result from extra-planar flows and higher velocity accretion/SN-driven outflows.
 The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MGCs observed in gas-rich star-forming galaxies at $z$\ssim2.

### 2020-04-20 WRITEUP/ms_referee2.tex
w/ MMM edits

@@
 The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$
-at {\bf $z$\eq6}.
+at $z$\eq6.
 The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$.
@@
 \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
-{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
-\flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
+$M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc.
+\flower has a stellar mass of $M_\star\simeq$\,2.6\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
 %
@@
 (see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{{\bf The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07.
-This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
+This is a factor of about three higher than the typical value inferred by abundance matching models, which typically give values of $\sim0.02$.
 Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025
-is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
+for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find
 0.01--0.05 in the same mass range from direct abundance matching
 (see the Appendix therein).
-Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}.} 
+As another example, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, also differing by a factor three from \citet{Behroozi13b}, though in opposite direction}.}
 The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
@@
 Among the various cuts, two physical regimes are identified, corresponding to materials in the disk/interarm material and MGCs (see Fig. 5).
-The former with n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter with 
-n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Fig. 5 of \citet{Pallottini17b} 
-for details\footnote{In particular, with their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}). 
+The former have n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter have
+n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Figs. 5 and 6 of \citet{Pallottini17b}
+for details\footnote{In particular, their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}).
 Considering that $f_{\rm H2}$\eq$\rho_{\rm H2} / \rho_{\rm H,total}$\eq$\rho_{\rm H2}/(\mu \rho_{\rm gas})$\eq
-$m_{\rm H2} n_{\rm H2} / m_p~\mu~n_{\rm gas}$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$, 
-for the disk/interarm, $f_{\rm H2}$\ssim14\% and for the MCCs, $f_{\rm H2}$\ssim28\%. 
-Note that for the lowest value of the H2 cuts, this fraction might be lower; however, 
+$m_{\rm H2} n_{\rm H2} / (m_p\,\mu\,n_{\rm gas})$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$,
+for the disk/interarm region $f_{\rm H2}$\ssim14\%, while for the MGCs $f_{\rm H2}$\ssim28\%.
+Note that for the lowest value of the H$_2$ cuts, these fractions might be lower; however,
 removing regions selected with such cuts yields no qualitative change to the physical interpretation resulting from the analysis.}
@@
 \section*{Acknowledgements}
-We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
+We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, Caitlin Casey for useful discussions, and the referee for providing constructive
+comments on the manuscript.
 %
